### 2021-07-15 _drafts/walthroughWeb.Rmd
setup

---
layout: page
title: blah
output:
  github_document:
    pandoc_args:  --mathjax
  #  md_document:
#    variant: markdown_github

  preserve_yaml: true
bibliography: [../references/attacks.bib]
csl: [../references/apa-6th-edition.csl]
---

```{r , echo = FALSE, eval = TRUE}
knitr::opts_knit$set(base.dir = "/home/rafal/UG/UGprojects/redditAttacks",
base.url = "https://rfl-urbaniak.github.io/redditAttacks/")
knitr::opts_chunk$set(fig.path = "images/")
```

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
#opts_knit$set(root.dir = "../")
options(knitr.kable.NA = '')

library(tidyverse)
library(knitr)
library(kableExtra)
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

\noindent \textbf{Abstract.}
We conduct a large scale data-driven analysis of the effects of online personal attacks on social media user activity. First, we perform a thorough overview of the literature on the influence of social media on user behavior, especially on the impact that negative and aggressive behaviors, such as harassment and cyberbullying, have on users’ engagement in online media platforms. The majority of previous research were  small-scale self-reported studies, which is their limitation. This motivates our data-driven study. We perform a large-scale analysis of messages from Reddit, a discussion website, for a period of two weeks, involving 182,528 posts or comments to posts by 148,317 users. To efficiently collect and analyze the data we apply a high-precision personal attack detection technology. We analyze the obtained data from three perspectives: (i) classical statistical methods, (ii) Bayesian estimation, and (iii) model-theoretic analysis. The three perspectives agree: personal attacks decrease the victims’ activity.
The results can be interpreted as an important signal to social media platforms and policy makers that leaving personal attacks unmoderated is quite likely to disengage the users and in effect depopulate the platform. On the other hand, application of cyberviolence detection technology in combination with various mitigation techniques could improve and strengthen the user community. As more of our lives is taking place online, keeping the virtual space inclusive for all users becomes an important problem which online media platforms need to face.

Remark. In what follows, we sometimes display key pieces of code and explain what it does. Some not too fascinating pieces of code are supressed, but the reader can look them up in the associated .Rmd file and compile their own version.

#Technology applied for personal attack detection

For the need of this research we define personal attack as any kind of abusive remark made in relation to a person (ad hominem) rather than to the content of the argument expressed by that person in a discussion. The definition of ‘personal attack’ subsumes the use of specific terms which compare other people to animals or objects or making nasty insinuations without providing evidence. Three examples of typical personal attacks are as follows.

- *You are legit mentally retarded homie.*
- *Eat a bag of dicks, fuckstick.*
- *Fuck off with your sensitivity you douche.*

The detection of personal attacks was performed using  Samurai, a proprietary technology of Samurai Labs.^[[https://www.samurailabs.ai/](https://www.samurailabs.ai/), described in [@ptaszynski2018cyberbullying;@wroczynski2019system].]

The following figure illustrates how the input text ("ccant believ he sad ur an id10+...!") is processed step-by-step utilizing both statistical and symbolic methods.

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../images/example-eps-converted-to.pdf}
    \caption{Example of processing of one sentence by the applied Samurai technology.}
    \label{fig:samuraiexample}
\end{figure}

In practice, it means that a whole variety of constructions can be detected without the need to construct a fixed list of dictionary words defined \textit{a priori}. Due to utilizing symbolic components that oversee statistical components, {\textsf Samurai} recognizes complex linguistic phenomena (such as indirect speech, rhetorical figures or counter-factual expressions) to distinguish personal attacks from normal communication, greatly reducing the number of false alarms as compared to others systems used for violence detection. An example of comparison can be seen in Figure \ref{fig:samuraiexample}, and a full benchmark was presented in [@ptaszynski2018cyberbullying].

The detection models utilized in this research were designed to detect personal attacks targeted against a second person (e.g. interlocutor, original author of a post) and a third person/group (e.g., other participants in the conversation, people not involved in the conversation, social groups, professional groups), except public figures (e.g. politicians, celebrities). 
With regards to symbolic component of the system, by "models" we mean separate rules (such as, specifying a candidate for the presence of personal attack, such as the aggressive word "idiot," which is further disambiguated with a syntactic rule of citation, e.g., "[he$\vert$she$\vert$they] said [SUBJECT] [PREDICATE]") or sets of rules, as seen in Figure \ref{fig:samuraiexample}, e.g. normalization model contains rules for transcription normalization, citation detection model contains rules for citation, etc. With regards to the statistical component, by "models" refer to machine learning models trained on large data to classify an entry into one of the categories (e.g., true personal attack, or false positive).

Moreover, the symbolic component of the system uses two types of symbolic rules, namely "narrow rules" and "wide rules." The former have smaller coverage (e.g., are triggered less often), but detect messages containing personal attacks with high precision.\footnote{Precision is defined traditionally as the ratio of correctly detected instances among all detected instances.} The latter, have wider coverage, but their precision is lower. 
We decided to set apart the "narrow" and "wide" subgroups of the detection models in order to increase the granularity of the analysis. Firstly, we took only the detection models designed to detect personal attacks targeted against second person. Secondly, we used these models on a dataset of 320,000 Reddit comments collected on 2019/05/06.
Thirdly, we randomly picked at most hundred returned results for each low-level model. Low-level models are responsible for detecting low-level categories. Similarly, mid-level models detect mid-level categories, by combining several low-level models, etc. (Some models are triggered very often while others rarely, so using all instances would create too much bias). There were 390 low-level models but many of them returned in less than 100 results. We verified them manually with the help of expert annotators trained in detection of personal attacks and selected only those models that achieved at least 90\% of precision. The models with fewer than 100 returned results were excluded from the selection. After this step, the "narrow" subgroup contained 43 out of 390 low-level models. Finally, we tested 
all of the "narrow" models on a large dataset of 477,851 Reddit comments collected between 2019/06/01 and 2019/08/31 from two subreddits (r/MensRights and r/TooAfraidToAsk). Each result of the "narrow" models was verified manually by a trained annotator and the "narrow" models collectively achieved over 93.3\% of precision. We also tested the rest of the "wide" models on random samples of 100 results for each model (from the previous dataset of 320,000 Reddit comments) and we excluded the models that achieved less than 80\% precision. The models with fewer than 100 results were not excluded from the "wide" group. In this simple setup we detected 24,251 texts containing "wide" attacks, where:

\begin{itemize}
\item  5,717 (23.6\%) contained personal attacks against second person detected by the "narrow" models,
\item  8,837 (36.4\%) contained personal attacks against second person detected by "wide" models
% the models other than "narrow",
\item  10,023 (41.3\%) contained personal attacks against third persons / groups.
The sum exceeds 100\% because some of the comments contained personal attacks against both second person and third person / groups. For example, a comment ``Fu$\ast\ast$ you a$\ast\ast$hole, you know that girls from this school are real bit$\ast\ast$es" contains both types of personal attack.
\end{itemize}

The sum exceeds 100\% because some of the comments contained personal attacks against both second person and third person / groups. For example, a comment ``Fu$\ast\ast$ you a$\ast\ast$hole, you know that girls from this school are real bit$\ast\ast$es" contains both types of personal attack.

Additionally, from the original data of 320,000 Reddit posts we extracted and annotated 6,769 Reddit posts as either a personal attack (1) or not (0). To assure that the extracted additional dataset contains a percentage of Personal Attacks sufficient to perform the evaluation, the Reddit posts were extracted with an assumption that each post contains at least one word of a general negative connotation. Our dictionary of such words contains 6,412 instances, and includes a wide range of negative words, such as nouns (e.g., "racist", "death", "idiot", "hell"), verbs (e.g., "attack", "kill", "destroy", "suck"), adjectives (e.g., "old", "thick", "stupid", "sick"), or adverbs (e.g., "spitefully", "tragically", "disgustingly"). In the 6,769 additionally annotated Reddit samples there were 957 actual Personal Attacks (14\%), from which Samurai correctly assigned 709 (true positives) and missed 248 (false negatives), which accounts for 74\% of the Recall rate.
Finally, we performed another additional experiment in which, we used Samurai to annotate completely new 10,000 samples from Discord messages that did not contain Personal Attacks but contained vulgar words. The messages were manually checked by two trained annotators and one additional super-annotator. The result of Samurai on this additional dataset was a 2\% of false positive rate, with exactly 202 cases misclassified as personal attacks. This accounts for specificity rate of 98\%.

\section{Study design, data collection, and dataset description}

The raw datasets used have been obtained by \textsf{Samurai Labs}, who were able to collect \textsf{Reddit} posts and comments without \textsf{Reddit} moderation or comment removal. All content was downloaded from the data stream provided by \url{pushshift.io} which enabled full data dump from Reddit in real-time. The advantage of using it was access to unmoderated data.\footnote{As of August 20th, the service is not available. For now, one possible way is to use an API provided by Reddit with a constraint:  Reddit allows for 600 requests every 10 minutes. 10 minutes might be a short time in the case of moderators' reaction, but is enough for AutoModerator or other automated moderation to exert their force, thus leading to a moderated, and therefore incomplete dataset.} Further, \textsf{Samurai Labs} deployed their personal attacks recognition algorithms to identify personal attacks.

In the study,   experimental manipulation of the crucial independent variables (personal attacks of various form)   to assess their effect on the dependent variable (users’ change in activity)  would be unethical and against the goal of Samurai Labs, which is to detect and _prevent_ online violence. While such a lack of control is a weakness as compared to typical experiments in psychology, our sample was both much larger and much more varied than the usual WEIRD (western, educated, and from industrialized, rich, and democratic countries) groups used in psychology. Notice, however, that the majority of Reddit users  are based in U.S. For instance,  [@wise2006moderation] examined  59 undergraduates from a political science class at a major Midwestern university in the USA, [@zong2019social] studied 251 students and faculty members from China who are users of WeChat, and  [@valkenburg2006friend] surveyed  881 young users (10-19yo.) of a Dutch SNS called CU2.

Because of the preponderance of personal attacks  online, we could use the real-life data from Reddit and use the following study design:

1. All the raw data, comprising of daily lists of posts and comments (some of which were used in the study) with time-stamps and author and target user names, have been obtained by  Samurai Labs, who also applied their personal attack detection algorithm to them, adding two more variables: narrow and wide. These were the raw datasets used in further analysis.

2.  Practical limitations allowed for data collection for  around two continuous weeks (day 0 $\pm$ 7 days). First, we randomly selected one weekend day and one working day. These were June 27, 2020 (Saturday, S) and July 02, 2020 (Thursday, R). The activity on those days was used to   assign users to groups in the following manner. We picked one weekend and one non-weekend day to correct for activity shifts over the weekend (the data indeed revealed slightly higher activity over the weekends, no other week-day related pattern was observed). We could not investigate (or correct for) monthly activity variations, because the access to unmoderated data was limited.

3.  For each of these days, a random sample of 100,000 posts or comments have been drawn from all content posted on Reddit.  Each of these datasets went through preliminary user-name based bots removal. This is a simple search for typical phrases included in user names, such as "Auto", "auto", "Bot", or "bot".

For instance, for our initial thursdayClean datased, this proceeds like this:

\scriptsize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
thursdayClean <- thursdayClean[!grepl("Auto", thursdayClean$author, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("auto", thursdayClean$author, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("Auto", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("auto", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("bot", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("Bot", thursdayClean$receiver, fixed=TRUE),]
```
\normalsize

4. In some cases, content had been  deleted by the user or removed by Reddit  --- in such cases the dataset only contained information that some content had been  posted but was later removed; since we could not access the content  of such posts or comments and evaluate them for personal attacks, we also excluded them from the study.

 Again, this was a fairly straightforward use of grepl:

\scriptsize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
thursdayClean <- thursdayClean[!grepl("none", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("None", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("<MISSING>", thursdayClean$receiver, fixed=TRUE),]
thursdayClean <- thursdayClean[!grepl("[deleted]", thursdayClean$receiver, fixed=TRUE),]
```
\normalsize

5. This left us with  92,943 comments or posts by 75,516 users  for \textsf{R} and 89,585 comments by 72,801 users  for \textsf{S}. While we didn't directly track whether content was a post or a comment, we paid attention as to whether a piece of content was a reply to a post or not (the working assumption was that personal attacks on posts might have different impact than attacks on comments). Quite consistently, 46\% of content were comments on posts on both days.

6.  On these two  days respectively,  1359 \textsf{R} users ($1.79\%$) received at least one \textsf{narrow} attack, 35 of them received more than one ($0.046\%$). 302 of \textsf{S} users ($0.39\%$) received at least one \textsf{narrow} attack and 3 of them more than one \textsf{narrow} on that day ($0.003\%$). These numbers  are estimates for a single day, and therefore if the chance of obtaining at least one \textsf{narrow} attack in a day is $1.79\%$, assuming the binomial distribution, the estimated probability of obtaining at least one \textsf{narrow} attack in a week is 11.9\% in a week and 43\% in a month.

\scriptsize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
100  * round(1-dbinom(0,7,prob = 1359/75516),3)` #week
100 * round(1-dbinom(0,31,prob = 1359/75516),3)` #month
```
\normalsize

7. To ensure a sufficient sample size, we decided not to draw a random sub-sample from the \textsf{wide > 1} or \textsf{narrow > 1} class comprising 340 users, and  included all of them in the Thursday treatment group (\textsf{Rtreatment}). Other users were randomly sampled from \textsf{wide > 0} and added to \textsf{Rtreatment}, so that the group count was 1000.

8. An analogous strategy was followed for \textsf{S}. 1338 users belonged to \textsf{wide > 0}, 27 to \textsf{wide > 1}, 329 to \textsf{narrow > 0} and 3 to \textsf{narrow > 1}. The total of 344 \textsf{wide > 1} or \textsf{narrow > 1} users was enriched with sampled \textsf{wide > 0} users to obtain the \textsf{Streatment} group of 1000 users.

9. The preliminary \textsf{Rcontrol}/\textsf{Scontrol}  groups of 1500 users each were constructed by sampling 1500 users who posted comments on the respective days but did not receive any recognized attacks. The group sizes for control groups are higher, because after obtaining further information we intended to eliminate those who received any attacks  before the group selection day (and for practical reasons we could only  obtain data for this period after the groups were selected).

10.  For each of these groups new  dataset was prepared, containing all posts or comments made by the users during the period of $\pm 7$ days from the selection day (337,015 for \textsf{Rtreatment}, 149,712 for \textsf{Rcontrol}, 227,980 for \textsf{Streatment} and 196,999 for \textsf{Scontrol}) and all comments made to their posts or comments (621,486 for \textsf{Rtreatment}, 170,422 for \textsf{Rcontrol}, 201,614 for \textsf{Streatment} and 204,456 for \textsf{Scontrol}), after checking for uniqueness these jointly were 951,949 comments for \textsf{Rtreatment}, 318,542 comments for \textsf{Rcontrol}, 404,535 comments for \textsf{Streatment}, and 380,692 comments for \textsf{Scontrol}). The need to collect all comments to the content posted by our group members was crucial. We needed this information because we needed to check all such comments for personal attacks to obtain an adequate count of attacks received by our group members. In fact, this turned out to be the most demanding part of data collection.

11.  All these were wrangled into the frequency form, with (1) numbers of  attacks as recognized by  \textsf{narrow} or \textsf{wide} algorithm (in the dataset  we call these \textsf{high} and \textsf{low} respectively), (2) distinction between \textsf{attack on comment} and \textsf{attack on post}), and (3) activity counts for each day of the study, (4) with added joint counts for the \textsf{befor}e and \textsf{after} periods. Frequency data for users outside of the control or treatment groups were removed.

12.  With the frequency form at hand, we could look at outliers. We used a fairly robust measure.\footnote{The classic outlier detection method takes a datapoint to be an outlier if it is at least two standard deviations from the mean. This method is not robust, because it is susceptible to the masking problem: adding an even more extreme outlier  to the data may easily make an outlier look normal. The boxplot rule that we used replaces standard deviation with the interquartile range which is much less sensitive to outliers.}  For each of the weekly counts of \textsf{low, high} and \textsf{activity} we calculated the interquartile range (\textsf{IQR}), as the absolute distance between the first and the third quartile and identified as outliers those users which landed at least $1.5\times \textsf{IQR}$ from the respective mean.  These resulted in a list of 534 "powerusers" which we suspected of being bots (even though we already removed users whose names suggested they were bots) --- all of them were manually checked by \textsf{Samurai Labs}. Those identified as bots (only 15 of them) or missing (29 of them) were removed. It was impossible to establish whether the missing users were bots; there are also two main reasons why a user might be missing: (a) account suspended, and (b) user deleted. We decided not to include the users who went missing in our study, because they would artificially increase the activity drop during the period and because we didn't suspect any of the user deletions to be caused by personal attacks directed against them (although someone might have deleted the account because they were attacked, these were power-users who have a high probability of having been attacked quite a few  times before, so this scenario is unlikely).

13.  The frequency form of the control sets data was used to remove those users who were attacked in the \textsf{before} period (894 out of 1445 for \textsf{R}, and  982 out of 1447 for \textsf{S}   remained).

14.  A few more unusual data points needed to be removed, because they turned out to be users whose comments contained large numbers of third-person personal attacks which in fact supported them. Since we were interested in the impact of personal attacks directed against a user on the user's activity, such unusual cases would distort the results.  Six were authors of posts or comments which received more than 60 \textsf{wide only} attacks each. Upon inspection, all of them supported the original users. For instance,  two of them  were third-person comments about not wearing a mask or sneezing in public, not attacks on these users. Another example is  a female  who asked for advice about her husband: the comments were supportive of her and critical of the husband. Two users with weekly activity count change higher than 500 were removed -- they did not seem to be bots but very often they posted copy-pasted content and their activity patterns were highly irregular with changes most likely attributable to some other factors than attacks received. The same holds for a young user we removed from the study who displayed activity change near 1000. She   commented on her own activity during that period as very unusual and involving 50 hrs without sleeping. Her activity drop afterwards is very likely attributable to other factors than receiving a personal attack.

15. 86 users who did not post anything in the \textsf{before} period were also removed.

16. In the end, \textsf{R} and \textsf{S} were aligned, centering around the selection day (day 8) and the studied group comprised 3673 users.

\footnotesize
```{r, echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
#note we load the data here
data <- read.csv("../datasets/quittingFinalAnon.csv")[,-1]
table(data$group)
```
\normalsize

A few first lines of the resulting anonymized dataset from which we removed separate day counts. Note that in the code "low" corresponds to "wide" (for "low precision") and "high" to "narrow" attacks (for "high precision"). The variables are: (low attacks, high attacks, low  attacks on posts, how  attacks on posts, authored content posted) and retained summary columns.

- \textsf{user} contains anonymous user numbers.
- \textsf{sumLowBefore} contains the sum of \textsf{wide}  attacks in days 1-7. \textsf{sumHighBefore} the sum of \textsf{narrow} (attacks in the same period. 
- \textsf{Pl} and \textsf{Ph} code \textsf{wide} and \textsf{narrow} attacks on posts (we wanted to verify the additional sub-hypothesis that  attacks on a post might have more impact than attacks on comments).

- \textsf{activityBefore} and \textsf{activityAfter} count comments or posts during days seven days before and seven days after. The intuition is, these shouldn't change much if personal attacks have  no impact on activity.

- \textsf{group} and \textsf{treatment} include information about which group a user belongs to.

```{r,,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
dataDisp <- data[,c(1,77:85)]
head(dataDisp)
```
\normalsize

First, we visually explore our dataset by looking at the relationship between the number of received attacks vs. the activity change counted as the difference of weekly counts of posts or comments authored  in the second (\textsf{after}) and in the first  week (\textsf{before}). We do this for \textsf{narrow} attacks (Fig. \ref{fig:highPlots}), \textsf{wide} attacks (Fig. \ref{fig:lowPlots}), where a weaker, but still negative impact, can be observed, and  then we   take a look at the impact of those attacks which were recognized as \textsf{wide only} (Fig. \ref{fig:lowOnlyPlots}). The distinction between wide and narrow pertains only to the choice of attack recognition algorithm and does not directly translate into how offensive an attack was, except that \textsf{wide} attacks also include third-person ones.  Here, the direction of impact is less clear: while the tendency is negative for low numbers of attacks, non-linear smoothing suggests that  higher numbers mostly third-person personal attacks seem positively correlated with activity change. This might suggest that while being attacked has negative impact on a user's activity, having your post "supported" by other users' third-person attacks has a more motivating effect. We will look at this issue in a later section, when we analyze the dataset using regression.

The visualisations in Figure \ref{fig:highPlots} should be understood as follows. Each point is a user. The $x$-axis represents a number of attacks they received in the \textsf{before} period (so that, for instance, users with 0 wide attacks are the members of the control group), and  the $y$-axis represents the difference between their activity count \textsf{before} and \textsf{after}. We can see that most of the users received 0 attacks before (these are our control group members), with the rest of the group receiving 1, 2, 3, etc. attacks in the \textsf{before} period with decreasing frequency. The blue line represents linear regression suggesting negative correlation. The gray line is constructed using generalized additive mode (gam) smoothing, which is  a fairly standard smoothing method for large datasets (it is more sensitive to local tendencies and yet avoids overfitting). The parameters of the gam model (including the level of smoothing) are chosen by their predictive accuracy.\footnote{See  the documentation of \textsf{gam} of the \textsf{mgcv} packages for details: \url{https://www.rdocumentation.org/packages/mgcv/versions/1.8-33/topics/gam}.}  Shades indicate the 95\% confidence level interval for predictions from the linear model.

\footnotesize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300}
library(ggthemes)
th <- theme_tufte()
highPlot <- ggplot(data, aes(x = sumHighBefore, y = activityDiff))+geom_jitter(size=0.8, alpha = 0.3)+
  geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", 
              size = 0.7, alpha = 0.8)+
  scale_x_continuous(breaks = 0:max(data$sumHighBefore),
  limits = c(-1,max(data$sumHighBefore)))+ylim(c(-300,300))+
  geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+   xlab("narrow attacks before")+ ylab("activity change after")+
labs(title = "Impact of narrow attacks on activity", subtitle = "weekly counts, n=3673")+
  geom_segment(aes(x = -1, y = -100, xend = 9, yend = -100), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ 
  geom_segment(aes(x = -1, y = 100, xend = 9, yend = 100), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+
  geom_segment(aes(x = -1, y = -100, xend = -1, yend = 100), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ 
  geom_segment(aes(x = 9, y = -100, xend = 9, yend = 100), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+th

highPlotZoomed <- 
ggplot(data, aes(x = sumHighBefore, y = activityDiff))+geom_jitter(size=1, alpha = 0.2)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th+scale_x_continuous(breaks = 0:max(data$sumHighBefore),limits = c(-1,9))+ylim(c(-100,100))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+ xlab("narrow attacks before")+ ylab("activity change after")+labs(title = "Impact of narrow attacks on activity", subtitle = "weekly counts, zoomed in")+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)
```
\normalsize

```{r highPlot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
highPlot
```

```{r highPlotZoomed,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
highPlotZoomed
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lowPlot <- ggplot(data, aes(x = sumLowBefore, y = activityDiff))+geom_jitter(size=0.8, alpha = 0.3)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+ xlab("wide attacks before")+ ylab("activity change after")+labs(title = "Impact of wide attacks on activity", subtitle = "weekly counts, n=3673") + geom_segment(aes(x = -1, y = -150, xend = 15, yend = -150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = -1, y = 150, xend = 15, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = -1, y = -150, xend = -1, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = 15, y = -150, xend = 15, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+xlim(c(-1,max(data$sumLowBefore)))

lowPlotZoomed <- ggplot(data, aes(x = sumLowBefore, y = activityDiff))+geom_jitter(size=1, alpha = 0.2)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th+scale_x_continuous(breaks = 0:max(data$sumLowBefore),limits = c(-1,15))+ylim(c(-150,150))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+ xlab("wide attacks before")+ ylab("activity change after")+labs(title = "Impact of wide attacks on activity", subtitle = "weekly counts, zoomed in")+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)
```

```{r lowPlot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowPlot
```

```{r lowPlotZoomed,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowPlotZoomed
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lowOnlyPlot <- ggplot(data, aes(x = (sumLowBefore - sumHighBefore), y = activityDiff))+geom_jitter(size=0.8, alpha = 0.3)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+ xlab("wide only attacks before")+ ylab("activity change after")+labs(title = "Impact of wide only attacks on activity", subtitle = "weekly counts, n=3673") + geom_segment(aes(x = -1, y = -150, xend = 15, yend = -150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = -1, y = 150, xend = 15, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = -1, y = -150, xend = -1, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+ geom_segment(aes(x = 15, y = -150, xend = 15, yend = 150), lty = 3, size = 0.1, color = "gray71", alpha = 0.2)+xlim(c(-1,max(data$sumLowBefore)))

lowOnlyPlotZoomed <- ggplot(data, aes(x = (sumLowBefore - sumHighBefore), y = activityDiff))+geom_jitter(size=1, alpha = 0.2)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th+scale_x_continuous(breaks = 0:max(data$sumLowBefore),limits = c(-1,15))+ylim(c(-150,150))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)+ xlab("wide only attacks before")+ ylab("activity change after")+labs(title = "Impact of wide only attacks on activity", subtitle = "weekly counts, zoomed in")+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)
```

```{r lowOnlyPlot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowOnlyPlot
```

```{r lowOnlyPlotZoomed,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowOnlyPlotZoomed
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
rescale <- function(diff,act){
diff/act
}
data$activityScore <- rescale(data$activityDiff,data$activityBefore)

propPlotHigh <- ggplot(data, aes(x = sumHighBefore, y = activityScore))+geom_jitter(size=0.8, alpha = 0.3)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th + xlab("narrow attacks before")+ ylab("proportional activity change")+labs(title = "Impact of narrow attacks on proportional activity", subtitle = "n=3673")+scale_y_continuous(limits = c(-1,10))+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)+scale_x_continuous(breaks = 1:15, limits = c(-1,10))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)

propPlotLow <- ggplot(data, aes(x = sumLowBefore, y = activityScore))+geom_jitter(size=0.8, alpha = 0.3)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th + xlab("wide attacks before")+ ylab("proportional activity change")+labs(title = "Impact of wide attacks on proportional activity", subtitle = "n=3673")+scale_y_continuous(limits = c(-1,10))+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)+scale_x_continuous(breaks = 1:15, limits = c(-1,10))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)

propPlotLowOnly <- ggplot(data, aes(x = sumLowBefore-sumHighBefore, y = activityScore))+geom_jitter(size=0.8, alpha = 0.3)+geom_smooth(method = "lm",color = "skyblue", fill= "skyblue", size = 0.7, alpha = 0.8)+th + xlab("wide only attacks before")+ ylab("proportional activity change")+labs(title = "Impact of wide only attacks on proportional activity", subtitle = "n=3673")+scale_y_continuous(limits = c(-1,10))+geom_hline(yintercept = 0, col = "red", size = 0.2, lty = 3)+scale_x_continuous(breaks = 1:15, limits = c(-1,10))+geom_smooth(color = "grey", size = 0.4, lty = 2, alpha = 0.2)

```

```{r propPlotHigh,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
propPlotHigh
```

```{r propPlotLow,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
propPlotLow
```

```{r propPlotLowOnly,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
propPlotLowOnly
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message= FALSE, warning= FALSE}
counts <- t(table(data$sumHighBefore)) 
counts <- rbind(counts,counts)
counts[1,] <- as.numeric(colnames(counts))
colnames(counts) <- NULL
rownames(counts) <-  c("no. of attacks", "count")
counts
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message= FALSE, warning= FALSE}
attacks <- 0:8 
max <- max(attacks)
low <- numeric(max+1)
high <- numeric(max+1)
m <- numeric(max+1)
p <- numeric(max+1)
t <- list()

for(attacks in attacks){
t[[attacks+1]] <- t.test(data[data$sumHighBefore == attacks,]$activityDiff)

low[attacks+1] <- t[[attacks+1]]$conf.int[1]
high[attacks+1] <- t[[attacks+1]]$conf.int[2]
m[attacks+1] <- t[[attacks+1]]$estimate
p[attacks+1] <- t[[attacks+1]]$p.value
}
highTable<-as.data.frame(round(rbind(0:8,low, m, high, p),3))
rownames(highTable) <- c("attacks","CIlow","estimated m", "CIhigh", "p-value")
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
highTableLong <- round(data.frame(attacks = 0:8, low, m, high, p),3)

highTableBar <- ggplot(highTableLong)+ geom_bar(aes(x=attacks,y=m), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=low, ymax=high), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("mean activity change")+
  geom_text(aes(x=attacks, y=low-20,
                label=p), size = 2)+labs(title = "Mean impact of narrow attacks on  weekly activity", subtitle = "with 95% confidence intervals and p-values")+
  scale_x_continuous(labels = 0:8, breaks= 0:8)

highTableBar6 <- ggplot(highTableLong[highTableLong$attacks < 6 ,])+ 
  geom_bar(aes(x=attacks,y=m), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=low, ymax=high), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("mean activity change")+
  geom_text(aes(x=attacks, y=low-20,label=p), size = 2)+
      labs(title = "Mean impact of narrow attacks <6 on  weekly activity",
       subtitle = "with 95% confidence intervals and p-values")+
  scale_x_continuous(labels = 0:5, breaks= 0:5)

highTableBar3 <- ggplot(highTableLong[highTableLong$attacks < 3 ,])+ geom_bar(aes(x=attacks,y=m), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=low, ymax=high), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("mean activity change")+
  geom_text(aes(x=attacks, y=low-5, label=p), size = 2)+
    labs(title = "Mean impact of narrow attacks <3 on  weekly activity", subtitle = "with 95% confidence intervals and p-values")+scale_x_continuous(labels = 0:2, breaks= 0:2)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message= FALSE, warning= FALSE}
attacks <- 0:8
max <- max(attacks)
lowL <- numeric(max+1)
highL <- numeric(max+1)
mL <- numeric(max+1)
pL <- numeric(max+1)
tL <- list()

for(attacks in attacks){
tL[[attacks+1]] <- t.test(data[data$sumLowBefore == attacks,]$activityDiff)

lowL[attacks+1] <- t[[attacks+1]]$conf.int[1]
highL[attacks+1] <- t[[attacks+1]]$conf.int[2]
mL[attacks+1] <- t[[attacks+1]]$estimate
pL[attacks+1] <- t[[attacks+1]]$p.value
}
lowTable<-as.data.frame(round(rbind(0:8,lowL, mL, highL, pL),3))
rownames(lowTable) <- c("attacks","CIlow","estimated m", "CIhigh", "p-value")

attacks <- 0:8
max <- max(attacks)
lowLo <- numeric(max+1)
highLo <- numeric(max+1)
mLo <- numeric(max+1)
pLo <- numeric(max+1)
tLo <- list()

for(attacks in attacks){
tLo[[attacks+1]] <- t.test(data[data$sumLowBefore -
                data$sumHighBefore == attacks,]$activityDiff)

lowLo[attacks+1] <- t[[attacks+1]]$conf.int[1]
highLo[attacks+1] <- t[[attacks+1]]$conf.int[2]
mLo[attacks+1] <- t[[attacks+1]]$estimate
pLo[attacks+1] <- t[[attacks+1]]$p.value
}
lowOnlyTable<-as.data.frame(round(rbind(0:8,lowLo, mLo, highLo, pLo),3))
rownames(lowTable) <- c("attacks","CIlow","estimated m", "CIhigh", "p-value")

```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lowTableLong <- round(data.frame(attacks = 0:8, lowL, mL, highL, pL),3)

lowTableBar <- ggplot(lowTableLong)+ geom_bar(aes(x=attacks,y=m), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=low, ymax=high), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("wide attacks")+ylab("mean activity change")+
  geom_text(aes(x=attacks, y=low-20,
                label=round(p,3)), size = 2)+labs(title = "Mean impact of wide attacks on  weekly activity", subtitle = "with 95% confidence intervals and p-values")+scale_x_continuous(labels = 0:8, breaks= 0:8)

lowOnlyTableLong <- round(data.frame(attacks = 0:8, lowLo, mLo, highLo, pLo),3)

lowOnlyTableBar <- ggplot(lowOnlyTableLong)+ geom_bar(aes(x=attacks,y=m), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=low, ymax=high), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("wide only attacks")+ylab("mean activity change")+
  geom_text(aes(x=attacks, y=low-20,
                label=round(p,3)), size = 2)+labs(title = "Mean impact of wide only attacks on  weekly activity", subtitle = "with 95% confidence intervals and p-values")+scale_x_continuous(labels = 0:8, breaks= 0:8)
```

T-test based estimates for activity change divided by numbers of narrow attacks received:

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
highTable
```

T-test based estimates for activity change divided by numbers of wide attacks received:

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lowTable
```

T-test based estimates for activity change divided by numbers of wide only attacks  received:

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lowOnlyTable
```

```{r highTableBar,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
highTableBar
```

```{r highTableBar6,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
highTableBar6
```

```{r highTableBar3,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
highTableBar3
```

```{r lowTableBar,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowTableBar
```

```{r lowOnlyTableBar,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
lowOnlyTableBar
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
h6 <- data[data$sumHighBefore == 6,]
h7 <- data[data$sumHighBefore == 7,]
h8 <- data[data$sumHighBefore == 8,]

# power for 6 attacks
a <- mean(data$activityDiff)
s <- sd(h7$activityDiff)
n <- 8
error <- qt(0.975,df=n-1)*s/sqrt(n)
left <- a-error
right <- a+error
assumed <- a - 80
tleft <- (left-assumed)/(s/sqrt(n))
tright <- (right-assumed)/(s/sqrt(n))
p <- pt(tright,df=n-1)-pt(tleft,df=n-1)
power6 <- 1-p
power6

# power for 7 attacks
a <- mean(data$activityDiff)
s <- sd(h7$activityDiff)
n <- 8
error <- qt(0.975,df=n-1)*s/sqrt(n)
left <- a-error
right <- a+error
assumed <- a - 80
tleft <- (left-assumed)/(s/sqrt(n))
tright <- (right-assumed)/(s/sqrt(n))
p <- pt(tright,df=n-1)-pt(tleft,df=n-1)
power7 <-1-p
power7

# power for 8 attacks
a <- mean(data$activityDiff)
s <- sd(h8$activityDiff)
n <- 4
error <- qt(0.975,df=n-1)*s/sqrt(n)
left <- a-error
right <- a+error
assumed <- a - 80
tleft <- (left-assumed)/(s/sqrt(n))
tright <- (right-assumed)/(s/sqrt(n))
p <- pt(tright,df=n-1)-pt(tleft,df=n-1)
power8 <- 1-p
power8
```

robabilities that this effect would be discovered by a single sample t-test for 6, 7, and 8 attacks are `r round(c(power6,power7,power8),3)`, and so tests for higher numbers of attacks are underpowered.

We run single t-tests on different groups to estimate different means and we don't use t-test for hypothesis testing. To alleviate concerns about multiple testing and increased risk of type I error,  we also  performed an  ANOVA tests, which strongly suggest non-random correlation between the numbers of attacks and activity change. 
 Furthermore,  80 comparison rows in Tukey's Honest Significance Test [@Tukey1949] have conservatively adjusted p-value below 0.05.

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE,warning=FALSE}
highAnova <- aov(activityDiff ~ as.factor(sumHighBefore), data = data)
lowAnova <- aov(activityDiff ~ as.factor(sumLowBefore), data = data)
lowOnlyAnova <- aov(activityDiff ~ as.factor(sumLowBefore-sumHighBefore), data = data)

library(descr,quietly=TRUE)
library(pander,quietly=TRUE)
library(papeR,quietly=TRUE)
sh <- xtable(summary(highAnova))
rownames(sh) <- c("narrow","residuals")
sh 
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
sl <- xtable(summary(lowAnova))
rownames(sl) <- c("narrow","residuals")
sl
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
so <- xtable(summary(lowOnlyAnova))
rownames(so) <- c("narrow","residuals")
so 
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",fig.margin=TRUE}
means <- numeric(10000)
for(run in 1:10000){
means[run] <- mean(sample(data[data$sumHighBefore==2,]$activityDiff,30))
}
distr <- ggplot(data[data$sumHighBefore==2,],aes(x = activityDiff)) + geom_histogram(bins = 100)+th+
  ggtitle("Distribution of activityDiff for narrow attacks before = 2")

sampDistr <- ggplot() + geom_histogram(aes(x = means),bins = 100)+th+ggtitle("Simulated sampling distribution for the same  with n=30 and 10 000 runs")
```

```{r distr,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE,  dpi = 300, message = FALSE, warning = FALSE, fig.width= 5}
distr
```

```{r sampDistr,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE,  dpi = 300, message = FALSE, warning = FALSE, fig.width= 6}
sampDistr
```

- $p$-values and confidence intervals are sensitive to undesirable factors, such as stopping intention in experiment design [@Kruschke2015].

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE, message=FALSE}
library(BEST)
priorsWide <- list(muM = 0, muSD = 50)
priorsInformed <- list(muM = -1.11, muSD = 44.47)
priorsFit <- list(muM = -1.11, muSD = 7.5)
```

```{r priorWide,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
priorWide <- ggplot(data = data.frame(x = c(-200, 200)), aes(x)) +
  stat_function(fun = dnorm, args = list(mean = 0, sd = 50)) + ylab("") +
  scale_y_continuous(breaks = NULL)+th+xlab("expected activity change")+labs(title = "Wide prior", subtitle ="Normal prior with m = 0, sd = 50")
priorWide
```

```{r priorFit,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
priorFit <- ggplot(data = data.frame(x = c(-100, 100)), aes(x)) +
  stat_function(fun = dnorm, args = list(mean = -1.11, sd = 7.5)) + ylab("") +
  scale_y_continuous(breaks = NULL)+th+xlab("expected activity change")+
  labs(title = "Fitted prior, zoomed in", subtitle ="Normal prior with m = 0, sd = 10, empirical distribution in gray")+
  geom_density(data = data, aes(x=activityDiff), col = "grey", alpha = 0.6)+xlim(c(-80,80))
priorFit
```

```{r priorInformative,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
priorInformative <- ggplot(data = data.frame(x = c(-200, 200)), aes(x)) +
  stat_function(fun = dnorm, args = list(mean = -1.11, sd = 44.47)) + ylab("") +
  scale_y_continuous(breaks = NULL)+th+xlab("expected activity change")+
  labs(title = "Informative prior", subtitle ="Normal prior with m = -1.11 and sd = 44.47")
priorInformative
```

```{r priorFitted,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
priorFitted <- ggplot(data = data.frame(x = c(-100, 100)), aes(x)) +
  stat_function(fun = dnorm, args = list(mean = -1.11, sd = 7.5)) + ylab("") +
  scale_y_continuous(breaks = NULL)+th+xlab("expected activity change")+
  labs(title = "Fitted prior", subtitle ="Normal prior with m = 0, sd = 10, empirical distribution in gray")+
  geom_density(data = data, aes(x=activityDiff), col = "grey", alpha = 0.6)+xlim(c(-200,200))
priorFitted
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
sh0 <- data[data$sumHighBefore==0,]$activityDiff
sh1 <- data[data$sumHighBefore==1,]$activityDiff
sh2 <- data[data$sumHighBefore==2,]$activityDiff
sh3 <- data[data$sumHighBefore==3,]$activityDiff
sh4 <- data[data$sumHighBefore==4,]$activityDiff
sh5 <- data[data$sumHighBefore==5,]$activityDiff
sh6 <- data[data$sumHighBefore==6,]$activityDiff
sh7 <- data[data$sumHighBefore==7,]$activityDiff
sh8 <- data[data$sumHighBefore==8,]$activityDiff
```

```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} 
mc3w <- BESTmcmc(sh3,priors = priorsWide)
plotPostPred(mc3w)
```

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} 
#load("analysis/bayesianChains.RData")
load("../datasets/bayesianChainsCompatible.RDa")
```

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
plotPostPred(mc3w)
```

Next, we print some information about the object we obtained:

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
print(mc3w)
```

```{r convergencePlot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
ggplot()+geom_line(aes(x=1:length(mc3w$mu[1:100]),y = mc3w$mu[1:100]), alpha=0.7)+th+xlab("initial steps in the chain")+ylab("potential parameter")+
  labs(title = "Convergence plot for first 100 steps in MCMC", subtitle = "Wide prior, three attacks")
```

We can also inspect the chain diagnostics:

```{r chainDiagnostics,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
conv <- mc3w$mu[seq(1,length(mc3w$mu), by = 50)]
ggplot()+geom_line(aes(x=1:length(conv),y = conv), alpha=0.7)+th+xlab("steps in the selection")+ylab("potential parameter")+
  labs(title = "Convergence plot for every 50th step in MCMC", subtitle = "Wide prior, three attacks")
```

```{r collapsed,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
plot(mc3w)
```

Visual inspection of Figure \ref{fig:mw3plot} reveals that the most visited locations (potential mean activity drops) center around slightly less than minus twenty. In fact, 
the mean of those visited potential  means is -24.476 (although this does not have to be the mean of the sample, which in our case is 
`r  mean(sh3)`; rather it is the result of a compromise between the data and the prior). The median is very close. The new elements are HDIlo and HDIup, the limits of the \emph{Highest Density Inverval}: the range of values that are most credible and cover 95\% of the distribution. The Values within the 95% HDI are more credible than values outside the HDI, and the values inside it have a total probability of 95\%. Crucially, these can be interpreted as posterior probabilities of various mean candidates being the population means based on the data, which makes HDI much unlike standard confidence intervals.

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
#prepare data and plot densities
bayesianWideDF <- data.frame(a0 = mc0w$mu,a1 = mc1w$mu, a2 =mc2w$mu,a3 = mc3w$mu, 
              a4 = mc4w$mu, a5 = mc5w$mu, a6 = mc6w$mu, a7 = mc7w$mu,a8 = mc8w$mu)
bayesianWideDF$prior <- rnorm(nrow(bayesianWideDF), mean = 0, sd = 50)
BayesianWideDFLong <- gather(bayesianWideDF)
BayesianWideDFLong$key <- as.factor(BayesianWideDFLong$key)
BayesianWideDensities <- ggplot(BayesianWideDFLong, aes(x=value, group = key,
                         color = key, fill = key))+
  geom_density(alpha=0.2)+th+xlab("activity change")+scale_fill_discrete(name = "group",
  labels = c("0 attacks", "1 attack", "2 attacks", "3 attacks", "4 attacks", "5 attacks",
             "6 attacks","7 attacks", "8 attacks",  "prior")) + 
  guides(color = FALSE, size = FALSE)+ylim(c(0,0.11))+xlim(c(-90,60))+
  labs(title = "Impact of data on wide prior", 
  subtitle="narrow attacks vs. activity change")

#extract means and HDI limits from the mcmc objects
wideMeans <- numeric(9)
wideLow <- numeric(9)
wideHigh <- numeric(9)
for (i in 1:9){
wideMeans[i] <-  eval(parse(text = paste("summary(mc",i-1,"w)[1]",sep="")))
wideLow[i] <- eval(parse(text = paste("summary(mc",i-1,"w)[21]",sep="")))
wideHigh[i] <- eval(parse(text = paste("summary(mc",i-1,"w)[26]",sep="")))
}

#order the data and make the barplot  
wideBayesTable <- round(data.frame(attacks = 0:8, wideLow, wideMeans,wideHigh),3)
wideBayesBar <- ggplot(wideBayesTable)+ geom_bar(aes(x=attacks,y=wideMeans), 
                                        stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=wideLow, ymax=wideHigh), 
                 width=0.4, colour="seashell3",
  alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("activity change")+
  geom_text(aes(x=attacks+0.24, y=wideMeans-3, label=round(wideMeans,1)), size = 3)+scale_x_continuous(labels = 0:8, breaks= 0:8)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
bayesianFittedDF <- data.frame(a0 = mc0f$mu,a1 = mc1f$mu, a2 =mc2f$mu,a3 = mc3f$mu, a4 = mc4f$mu, a5 = mc5f$mu, a6 = mc6f$mu, a7 = mc7f$mu,a8 = mc8f$mu)
bayesianFittedDF$prior <- rnorm(nrow(bayesianFittedDF), mean = -1.11, sd = 7.5)
BayesianFittedDFLong <- gather(bayesianFittedDF)
BayesianFittedDFLong$key <- as.factor(BayesianFittedDFLong$key)
BayesianFittedDensities <- ggplot(BayesianFittedDFLong, aes(x=value, group = key, color = key, fill = key))+
  geom_density(alpha=0.2)+th+xlab("activity change")+scale_fill_discrete(name = "group",labels = c("0 attacks", "1 attack", "2 attacks", "3 attacks", 
  "4 attacks", "5 attacks", "6 attacks","7 attacks", "8 attacks",  "prior")) + 
  guides(color = FALSE, size = FALSE)+ylim(c(0,0.12))+xlim(c(-35,20))+
  labs(title = "Impact of data on fitted prior", subtitle="narrow attacks vs. activity change")

fittedMeans <- numeric(9)
fittedLow <- numeric(9)
fittedHigh <- numeric(9)

for (i in 1:9){
  fittedMeans[i] <-  eval(parse(text = paste("summary(mc",i-1,"f)[1]",sep="")))
  fittedLow[i] <- eval(parse(text = paste("summary(mc",i-1,"f)[21]",sep="")))
  fittedHigh[i] <- eval(parse(text = paste("summary(mc",i-1,"f)[26]",sep="")))
}

fittedBayesTable <- round(data.frame(attacks = 0:8, fittedLow, fittedMeans,fittedHigh),3)
fittedBayesBar <- ggplot(fittedBayesTable)+ geom_bar(aes(x=attacks,y=fittedMeans), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=fittedLow, ymax=fittedHigh), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("activity change")+
  geom_text(aes(x=attacks+0.25, y=fittedMeans-1,
                label=round(fittedMeans,1)), size = 3)+scale_x_continuous(labels = 0:8, breaks= 0:8)

#______________________________
bayesianInformativeDF <- data.frame(a0 = mc0i$mu,a1 = mc1i$mu, a2 =mc2i$mu,a3 = mc3i$mu, a4 = mc4i$mu, a5 = mc5i$mu, a6 = mc6i$mu, a7 = mc7i$mu,a8 = mc8i$mu)
bayesianInformativeDF$prior <- rnorm(nrow(bayesianInformativeDF), mean = -1.11, sd = 44.47)
BayesianInformativeDFLong <- gather(bayesianInformativeDF)
BayesianInformativeDFLong$key <- as.factor(BayesianInformativeDFLong$key)
BayesianInvormativeDensities <- ggplot(BayesianInformativeDFLong, aes(x=value, group = key, color = key, fill = key))+geom_density(alpha=0.2)+th+xlab("activity change")+scale_fill_discrete(name = "group",labels = c("0 attacks", "1 attack", "2 attacks", "3 attacks", 
                        "4 attacks", "5 attacks", "6 attacks","7 attacks", "8 attacks",  "prior")) + guides(color = FALSE, size = FALSE)+ylim(c(0,0.11))+xlim(c(-90,50))+labs(title = "Impact of data on Informative prior", subtitle="narrow attacks vs. activity change")

InformativeMeans <- numeric(9)
InformativeLow <- numeric(9)
InformativeHigh <- numeric(9)

for (i in 1:9){
  InformativeMeans[i] <-  eval(parse(text = paste("summary(mc",i-1,"i)[1]",sep="")))
  InformativeLow[i] <- eval(parse(text = paste("summary(mc",i-1,"i)[21]",sep="")))
  InformativeHigh[i] <- eval(parse(text = paste("summary(mc",i-1,"i)[26]",sep="")))
}

InformativeBayesTable <- round(data.frame(attacks = 0:8, InformativeLow, InformativeMeans,InformativeHigh),3)

InformativeBayesBar <- ggplot(InformativeBayesTable)+ geom_bar(aes(x=attacks,y=InformativeMeans), stat="identity", fill = "skyblue", alpha= 0.5)+
  geom_errorbar( aes(x=attacks, ymin=InformativeLow, ymax=InformativeHigh), width=0.4, colour="seashell3", alpha=0.9, size=0.3)+th+xlab("narrow attacks")+ylab("activity change")+
  geom_text(aes(x=attacks+0.25, y=InformativeMeans-3,
                label=round(InformativeMeans,1)), size = 3)+scale_x_continuous(labels = 0:8, breaks= 0:8)
```

```{r BayesianWideDensities,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
BayesianWideDensities
```

```{r wideBayesBar,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
wideBayesBar
```

```{r BayesianFittedDensities,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
BayesianFittedDensities
```

```{r fittedBayesBar,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
fittedBayesBar
```

```{r BayesianInvormativeDensitie,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
BayesianInvormativeDensities
```

```{r InformativeBayesBar,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
InformativeBayesBar 
```

```{r sds,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
sds <- c(sd(sh0),sd(sh1),sd(sh2),sd(sh3),sd(sh4),sd(sh5),sd(sh6),sd(sh7),sd(sh8))
attacks <- 0:8

ggplot()+ geom_bar(aes(x=attacks,y=round(sds,2)), stat="identity", fill = "skyblue", alpha= 0.5)+
th+xlab("narrow attacks")+ylab("standard deviation of activity change")+scale_x_continuous(breaks = 0:8, labels = 0:8)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE,warning=FALSE}
library(MASS)
library(vcd)
library(lmtest)
library(countreg)
library(pscl)
library(stats)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
activityAfterTab <-table(factor(data$activityAfter,
                levels = 0:max(data$activityAfter)))
activityAfterDf <- as.data.frame(activityAfterTab)
activityAfterDf$Var1 <- as.integer(activityAfterDf$Var1)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
activityDistr <- ggplot(activityAfterDf, aes(x = Var1, y  = Freq))+ geom_bar( stat="identity")+scale_x_continuous(breaks = seq(0,1000, by = 50))+th+labs(title="Distribution of activityAfter")+xlab("activityAfter")+ylab("count")

activityDistrRestr <- ggplot(activityAfterDf, aes(x = Var1, y  = Freq))+ geom_bar( stat="identity")+scale_x_continuous(breaks = seq(0,100, by = 10), limits = c(0,100))+th+labs(title="Distribution of activityAfter", subtitle = "x restricted to 0-100")+xlab("activityAfter")+ylab("count")
```

```{r activityDistr,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
activityDistr
```

```{r activityDistrRes,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", dpi = 300, message = FALSE, warning = FALSE}
activityDistrRestr
```

```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
activityFitPois <- goodfit(activityAfterTab, type = "poisson")
unlist(activityFitPois$par)
summary(activityFitPois)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
activityFitPois <- goodfit(activityAfterTab, type = "poisson")
poissonFitPlot <- ggplot(activityAfterDf, aes(x = Var1, y  = Freq))+ geom_bar( stat="identity", alpha=0.6)+
  scale_x_continuous(breaks = seq(0,100, by = 10), 
                     limits = c(0,100))+th+labs(title="activityAfter with fitted best Poisson model predictions", subtitle = "x restricted to 0-100")+xlab("activityAfter")+ylab("count")+geom_point(aes(x = Var1,y=activityFitPois$fitted), colour="darksalmon", size = 0.5, alpha = 0.5)
```

```{r poissonFitPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
poissonFitPlot
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
activityFitNbin <- goodfit(activityAfterTab, type = "nbinom")
summary(activityFitNbin)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
activityFitNbin <- goodfit(activityAfterTab, type = "nbinom")
poissonNbinPlot2 <- ggplot(activityAfterDf, aes(x = Var1, y  = Freq))+ geom_bar( stat="identity", alpha = 0.5)+scale_x_continuous(breaks = seq(0,100, by = 10), limits = c(0,100))+th+labs(title="activityAfter with fitted best negative binomial model predictions", subtitle = "x restricted to 0-100")+xlab("activityAfter")+ylab("count")+geom_point(aes(x = Var1,y=activityFitNbin$fitted), colour="darksalmon", size = 0.5, alpha = 0.8)
```

```{r poissonNbinPlot2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning=FALSE,message=FALSE}
poissonNbinPlot2
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE,warning=FALSE}
data$sumLowOnlyBefore <- data$sumLowBefore - data$sumHighBefore

fullModelZINbin <-zeroinfl(activityAfter~sumLowOnlyBefore+
    sumHighBefore+sumPlBefore+ sumPhBefore+ activityBefore,
    data = data, dist = "negbin")

fullModelHNbin <- hurdle(activityAfter~sumLowOnlyBefore+
  sumHighBefore+sumPlBefore+ sumPhBefore+ activityBefore,
  data= data, dist = "negbin")

fullModelZIpois <-zeroinfl(activityAfter~sumLowOnlyBefore+
  sumHighBefore+sumPlBefore+ sumPhBefore+ activityBefore,
  data = data, dist = "poisson")

fullModelHpois <- hurdle(activityAfter~sumLowOnlyBefore+
  sumHighBefore+sumPlBefore+ sumPhBefore+ activityBefore, 
  data = data, dist = "poisson")
```

```{r,echo=TRUE,include =TRUE, eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
fullModelZINbinRoot <- countreg::rootogram(fullModelZINbin,
          max=100, main="Zero-inflated negative binomial")

fullModelHNbinRoot <- countreg::rootogram(fullModelHNbin, max=100, main="Hurdle negative binomial")

fullModelZIpoisRoot <- countreg::rootogram(fullModelZIpois, max=100, main="Zero-inflated Poisson")

fullModelHpoisRoot <- countreg::rootogram(fullModelHpois, max=100, main="Hurdle Poisson")
```

```{r fullModelZINbinRoot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(fullModelZINbinRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Zero-inflated negative binomial")
```

```{r fullModelHNbinRoot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(fullModelHNbinRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Hurdle negative binomial")
```

```{r fullModelZIpoisRoot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(fullModelZIpoisRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Zero-inflated Poisson")
```

```{r fullModelHpoisRoot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(fullModelHpoisRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Hurdle Poisson")
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 vuong(fullModelZINbin, fullModelHNbin)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE}
logLik(fullModelZINbin)
AIC(fullModelZINbin)

logLik(fullModelHNbin)
AIC(fullModelHNbin)
```

There seem to be some reasons to prefer the zero-inflated model, but the score differences are not too impressive, both likelihood ratios are Akaike scores are very close (note: we want to minimize AIC and maximize log likelihood).

To move on we need to modify  the variables,  because some of the counts included others. This was not a problem so far, but now we will be looking in detail at their roles jointly, and so it is important to not count various things multiple times.

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
#select variables of interest
dataModeling <- data %>% dplyr::select(sumLowOnlyBefore, sumHighBefore,
              sumPlBefore, sumPhBefore, activityBefore, activityAfter)

#sum narrow now becomes sum of narrow attacks on comments
dataModeling$sumHighBefore <- dataModeling$sumHighBefore - 
  dataModeling$sumPhBefore

#sum wide only now becomes sum of wide only on comments
dataModeling$sumLowOnlyBefore <- dataModeling$sumLowOnlyBefore -
  dataModeling$sumPlBefore

#sum of wide on posts now becomes sum of wide only on posts
dataModeling$sumPlBefore <- dataModeling$sumPlBefore -
  dataModeling$sumPhBefore
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning=FALSE, message= FALSE}
ZNBfull <- zeroinfl(activityAfter~., 
                    data = dataModeling, dist = "negbin")
ZNBactivity <- zeroinfl(activityAfter~activityBefore, 
                    data = dataModeling, dist = "negbin")
HNBfull <- hurdle(activityAfter~., 
                    data = dataModeling, dist = "negbin")
HNBactivity <- hurdle(activityAfter~activityBefore, 
                    data = dataModeling, dist = "negbin")

#now take a look at this
summary(dataModeling$activityAfter)
```

The outcome variable has third quartile of weekly activity count in the \textsf{after} period at 38, and we are mostly interested in predictive accuracy where most of the users are placed. Therefore, we  look at what happens with these models up to 40.

```{r,echo=TRUE,include =TRUE, eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
ZNBfullRoot <- countreg::rootogram(ZNBfull,
          max=40, main="Zero-inflated negative binomial")

ZNBactivityRoot <- countreg::rootogram(ZNBactivity, max=40, main="Hurdle negative binomial")

HNBfullRoot <- countreg::rootogram(HNBfull, max=40, main="Zero-inflated Poisson")

HNBactivityRoot <- countreg::rootogram(HNBactivity, max=40, main="Hurdle Poisson")
```

```{r ZNBfullRoot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(ZNBfullRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Zero-inflated negative binomial (all variables)")
```

```{r HNBfullRoot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(HNBfullRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Hurdle negative binomial (all variables)")
```

```{r ZNBactivityRoot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(ZNBactivityRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Zero-inflated negative binomial (activity only)")
```

```{r HNBactivityRoot,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
autoplot(HNBactivityRoot, alpha = 0.5)+th+ylab("Square root of couts")+ggtitle("Hurdle negative binomial (activity only)")
```

Finally, Akaike Information Criterion [@Akaike1974model] provides an  estimator of out-of-sample prediction error and penalizes more complex models. As long as we evaluate models with respect to the same data, the ones with lower Akaike score should be chosen.  Even with penalty for the additional variables, the full model receives better score (although the difference is not very large, 29,081 vs. 29,085).

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
library(lmtest)
likHNBactivity <- logLik(HNBactivity)
likHNBfull <- logLik(HNBfull)
(teststat <- -2 * (as.numeric(likHNBactivity)-as.numeric(likHNBfull)))
df <- 13 - 5
(p.val <- pchisq(teststat, df = df, lower.tail = FALSE))
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
lrtest(HNBactivity,HNBfull)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
waldtest(HNBactivity,HNBfull)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
AIC(HNBactivity)
AIC(HNBfull)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message=FALSE, warning = FALSE}
HNBfull
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
expCoef <- as.data.frame(round((exp(coef((HNBfull)))),3))
colnames(expCoef) <- c("Odds ratios")
expCoef
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
sumLowOnlyBefore <- rep(mean(dataModeling$sumLowOnlyBefore),4001)
sumHighBefore <- rep(mean(dataModeling$sumHighBefore),4001)
sumPlBefore <- rep(mean(dataModeling$sumPlBefore),4001)
sumPhBefore <- rep(mean(dataModeling$sumPhBefore),4001)
activityBefore <- rep(mean(dataModeling$activityBefore),4001)
activityAfter <- rep(mean(dataModeling$activityAfter),4001)

baseEffDf <- data.frame(sumLowOnlyBefore,sumHighBefore,sumPlBefore,
                        sumPhBefore,activityBefore,activityAfter)

effSizePlot <- function(columnno,range = 40,by = 5){
EffDf <- baseEffDf
EffDf[,columnno] <- 0:4000
EffDf$prediction <- predict(HNBfull,EffDf)
ggplot(EffDf, aes(x = EffDf[,columnno], y  = prediction))+
  geom_smooth(alpha = 0.5, col = "skyblue", se = FALSE)+
  scale_x_continuous(breaks = seq(0,range, by = by),
  limits = c(-1,range))+th+ylab("predicted activity")
}

effLO <- effSizePlot(1,500,50)    #low only
effH  <- effSizePlot(2,50,5)      #narrow on comments
effPl <- effSizePlot(3,100,10)    #pl
effPh <- effSizePlot(4, 50,5)     #ph
effA  <- effSizePlot(5,200,20)    #abefore
```

```{r effLO,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effLO+ggtitle("Predicted (hurdle) effect of wide only attacks on comments")+xlab("wide only attacks")
```

```{r effH,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effH+ggtitle("Predicted (hurdle) effect of narrow attacks on comments")+xlab("narrow attacks")
```

```{r effPl,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effPl+ggtitle("Predicted (hurdle) effect of wide attacks on posts")+xlab("wide attacks")
```

```{r effPh,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effPh+ggtitle("Predicted (hurdle) effect of narrow attacks on posts")+xlab("narrow attacks")
```

```{r effA,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effA+ggtitle("Predicted (hurdle) effect of previous activity")+xlab("activity before")
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
effSizePlotZ <- function(columnno,range = 40,by = 5){
  EffDf <- baseEffDf
  EffDf[,columnno] <- 0:4000
  EffDf$prediction <- predict(ZNBfull,EffDf)
  ggplot(EffDf, aes(x = EffDf[,columnno], y  = prediction))+
    geom_smooth(alpha = 0.5, col = "skyblue", se = FALSE)+
    scale_x_continuous(breaks = seq(0,range, by = by),
                       limits = c(-1,range))+th+ylab("predicted activity")
}

effLOZ <- effSizePlotZ(1,500,50)    #wide only
effHZ  <- effSizePlotZ(2,50,5)      #high on comments
effPlZ <- effSizePlotZ(3,100,10)    #pl
effPhZ <- effSizePlotZ(4, 50,5)     #ph
effAZ  <- effSizePlotZ(5,200,20)    #abefore

```

```{r effLOZ,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effLOZ+ggtitle("Predicted (zero-inflated) effect of wide only attacks on comments")+xlab("wide only attacks")
```

```{r effHZ,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effHZ+ggtitle("Predicted (zero-inflated) effect of narrow attacks on comments")+xlab("narrow attacks")
```

```{r effPlZ,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effPlZ+ggtitle("Predicted (zero-inflated) effect of wide attacks on posts")+xlab("wide attacks")
```

```{r effPhZ,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effPhZ+ggtitle("Predicted (zero-inflated) effect of narrow attacks on posts")+xlab("narrow attacks")
```

```{r effAZ,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
effAZ+ggtitle("Predicted (zero-inflated) effect of previous activity")+xlab("activity before")
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
EffSumHighTable <- baseEffDf[0:20,]
EffSumHighTable[,4] <- 0:19
EffSumHighTable$prediction <- predict(HNBfull,EffSumHighTable)
EffTablePosts <- rbind(EffSumHighTable$sumPhBefore,round(EffSumHighTable$prediction))
rownames(EffTablePosts) <- c("attacks","expected activity")
EffTablePosts
```

One might have reasoned about our previous analyses as follows:  attacks in the before period correlate with activity before, and it is activity before that is the real predictor of activity after. This could be supported by observing that the $p$-value for the hurdle model is really low for activity before.  Pearson correlation coefficient for narrow attacks before and activity before is $r(3671)\approx$ `r round( cor(data$sumHighBefore,data$activityBefore),3)` and   $r(3671)\approx$ 
`r round(cor(data$sumHighBefore,data$activityAfter),3)` for activity after. However, activity before is a much better correlate of activity after, $r(3671)\approx$ 
`r round(cor(data$activityBefore,data$activityAfter),3)` --- all correlations with $p$-value $<2.2e-16$, and regression analysis (inspect the effect plots) indicates that activity before and high attacks before actually go in the opposite directions.

\footnotesize
```{r mean1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
attacksb <- 0:8 
maxb <- max(attacks)
lowb <- numeric(max+1)
highb <- numeric(max+1)
mb <- numeric(max+1)
pb <- numeric(max+1)
tb <- list()

for(attacks in attacksb){
  t[[attacks+1]] <- t.test(data[data$sumHighBefore == attacks,]$activityBefore)

  lowb[attacks+1] <- t[[attacks+1]]$conf.int[1]
  highb[attacks+1] <- t[[attacks+1]]$conf.int[2]
  mb[attacks+1] <- t[[attacks+1]]$estimate
  pb[attacks+1] <- t[[attacks+1]]$p.value
}
highTableb<-as.data.frame(round(rbind(0:8,lowb, mb, highb, pb),3))
rownames(highTableb) <- c("attacks","CIlow","estimatedm", "CIhigh", "p-value")

before <- as.data.frame(t(highTableb))

attacksa <- 0:8 
maxa <- max(attacksa)
lowa <- numeric(max+1)
higha <- numeric(max+1)
ma <- numeric(max+1)
pa <- numeric(max+1)
ta <- list()
for(attacks in attacksa){
  ta[[attacks+1]] <- t.test(data[data$sumHighBefore == attacks,]$activityAfter)
  lowa[attacks+1] <- ta[[attacks+1]]$conf.int[1]
  higha[attacks+1] <- ta[[attacks+1]]$conf.int[2]
  ma[attacks+1] <- ta[[attacks+1]]$estimate
  pa[attacks+1] <- ta[[attacks+1]]$p.value
}
highTablea<-as.data.frame(round(rbind(0:8,lowa, ma, higha, pa),3))
rownames(highTablea) <- c("attacks","CIlow","estimatedm", "CIhigh", "p-value")
after <- as.data.frame(t(highTablea))

ggplot(before, aes(x = attacks, y = estimatedm))+geom_point()+ geom_errorbar(aes(ymin=CIlow, ymax=CIhigh), width=.2,size=0.2,
                                                                             position=position_dodge(0.05))+th+xlab("narrow attacks")+ylab("mean activity")+geom_line(data = after, aes(x = attacks, y = estimatedm), color = "skyblue")+geom_errorbar(data = after, aes(ymin=CIlow, ymax=CIhigh), width=.3,size=0.2,color = "skyblue",  position=position_dodge(0.05))

```

```{r mean2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
attacksb <- 0:8 
maxb <- max(attacks)
lowb <- numeric(max+1)
highb <- numeric(max+1)
mb <- numeric(max+1)
pb <- numeric(max+1)
tb <- list()

for(attacks in attacksb){
  t[[attacks+1]] <- t.test(data[data$sumHighBefore == attacks,]$activityBefore)

  lowb[attacks+1] <- t[[attacks+1]]$conf.int[1]
  highb[attacks+1] <- t[[attacks+1]]$conf.int[2]
  mb[attacks+1] <- t[[attacks+1]]$estimate
  pb[attacks+1] <- t[[attacks+1]]$p.value
}
highTableb<-as.data.frame(round(rbind(0:8,lowb, mb, highb, pb),3))
rownames(highTableb) <- c("attacks","CIlow","estimatedm", "CIhigh", "p-value")

before <- as.data.frame(t(highTableb))

attacksa <- 0:8 
maxa <- max(attacksa)
lowa <- numeric(max+1)
higha <- numeric(max+1)
ma <- numeric(max+1)
pa <- numeric(max+1)
ta <- list()
for(attacks in attacksa){
  ta[[attacks+1]] <- t.test(data[data$sumHighBefore == attacks,]$activityAfter)
  lowa[attacks+1] <- ta[[attacks+1]]$conf.int[1]
  higha[attacks+1] <- ta[[attacks+1]]$conf.int[2]
  ma[attacks+1] <- ta[[attacks+1]]$estimate
  pa[attacks+1] <- ta[[attacks+1]]$p.value
}
highTablea<-as.data.frame(round(rbind(0:8,lowa, ma, higha, pa),3))
rownames(highTablea) <- c("attacks","CIlow","estimatedm", "CIhigh", "p-value")
after <- as.data.frame(t(highTablea))

ggplot(before, aes(x = attacks, y = estimatedm))+geom_point()+ geom_errorbar(aes(ymin=CIlow, ymax=CIhigh), width=.2,size=0.2,                                                                         position=position_dodge(0.05))+th+xlab("narrow attacks")+ylab("mean activity")+geom_line(data = after, aes(x = attacks, y = estimatedm), color = "skyblue")+geom_errorbar(data = after, aes(ymin=CIlow, ymax=CIhigh), width=.3,size=0.2,color = "skyblue",  position=position_dodge(0.05))
```

```{r regressionToMean,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
h0 <- data[data$sumHighBefore == 0,]
h1 <- data[data$sumHighBefore == 1,]
h2 <- data[data$sumHighBefore == 2,]
h3 <- data[data$sumHighBefore == 3,]
h4 <- data[data$sumHighBefore == 4,]

distance <- function(x) { x - mean(data$sumHighBefore)}

library(gridExtra)
grid.arrange(ggplot(h0, aes(x = distance(activityBefore),y = activityDiff))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("0 narrow attacks")+ylab("activity change"),
ggplot(h2, aes(x = distance(activityBefore),y = activityDiff))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("2 narrow attacks")+ylab("activity change"),
ggplot(h3, aes(x = distance(activityBefore),y = activityDiff))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("3 narrow attacks")+ylab("activity change"),
ggplot(h4, aes(x = distance(activityBefore),y = activityDiff))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("4 narrow attacks")+ylab("activity change"))
```

First, in an inspection of the control group, the smoothing might suggest some correlation between the distance from the mean and the activity drop. However,  the sharp cut-off at the bottom  is there because one cannot drop their activity below the previous activity level. So users closer to the mean didn't even have the lower options available, and this restriction might be partially responsible for the smoothing line going downwards. Moreover, Spearman correlation between the distance from the mean and the activity change is `r round(cor(h0$activityBefore,h0$activityDiff, method = "spearman"),3)`, which is fairly weak. Pearson's $\rho$ is not very different (
`r round(cor(h0$activityBefore,h0$activityDiff),3)`), but we need to be careful here, because the relation doesn't seem very linear ($p$-values for correlation tests are both $<0.001$). If, however, we follow this line of reasoning,  the distance from the mean would explain only $R^2 =$ 
`r round(cor(h0$activityBefore,h0$activityDiff)^2,3)` of the variability in the activity change in the control group.

```{r regressionToMean2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
h0 <- data[data$sumHighBefore == 0,]
h1 <- data[data$sumHighBefore == 1,]
h2 <- data[data$sumHighBefore == 2,]
h3 <- data[data$sumHighBefore == 3,]
h4 <- data[data$sumHighBefore == 4,]

distance <- function(x) { x - mean(data$sumHighBefore)}

library(gridExtra)
grid.arrange(ggplot(h0, aes(x = distance(activityBefore),y = activityScore))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("0 narrow attacks")+ylab("proportional activity change"),
ggplot(h2, aes(x = distance(activityBefore),y = activityScore))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("2 narrow attacks")+ylab("proportional activity change"),
ggplot(h3, aes(x = distance(activityBefore),y = activityScore))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("3 narrow attacks")+ylab("proportional activity change"),
ggplot(h4, aes(x = distance(activityBefore),y = activityScore))+geom_point(alpha=0.3,size=1, position = "jitter")+geom_smooth(size=0.5, alpha = 0.5)+th+xlab("distance from sample mean"
)+ggtitle("4 narrow attacks")+ylab("proportional activity change"))
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
iqr0 <- data[data$sumHighBefore == 0 & data$activityBefore <= 44,]
iqr1 <- data[data$sumHighBefore == 1 & data$activityBefore <= 44,]
iqr2 <- data[data$sumHighBefore == 2 & data$activityBefore <= 44,]
iqr3 <- data[data$sumHighBefore == 3 & data$activityBefore <= 44,]
iqr4 <- data[data$sumHighBefore == 4 & data$activityBefore <= 44,]

t.test(iqr0$activityScore)
t.test(iqr1$activityScore)
t.test(iqr2$activityScore)
t.test(iqr3$activityScore)
t.test(iqr4$activityScore)
```

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message=FALSE, warning= FALSE}
library(rstatix)
data$fhigh <- as.factor(data$sumHighBefore)
data %>% anova_test(activityDiff ~ activityBefore + fhigh)
```

### 2021-07-15 paperDraft/paperDraft.Rmd
setup

---
title: "Nesta attacks study"
author: "Patrycja Tempska and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: true
    df_print: kable 
    keep_tex: true
    includes:
      in_header:
        - Rafal_latex6.sty
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: [../references/attacks.bib]
csl: [../references/apa-6th-edition.csl] 
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
```

\tableofcontents

# Section

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
2+2 #use this formatting for chunks
```
\normalsize

# Section 2

#  References {-}

\vspace{-3mm}

### 2021-07-15 paperDraft/paperDraft.tex
setup

\documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Nesta attacks study},
            pdfauthor={Patrycja Tempska and Rafal Urbaniak},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

%\documentclass{article}

% %packages
 \usepackage{booktabs}

\usepackage{multirow}

\usepackage{graphicx}
\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{etex}
%\usepackage{yfonts}
\usepackage{marvosym}
\usepackage[notextcomp]{kpfonts}
\usepackage{nicefrac}
\newcommand*{\QED}{\hfill \footnotesize {\sc Q.e.d.}}
\usepackage{floatrow}

\usepackage[textsize=footnotesize]{todonotes}
%\linespread{1.5}

\setlength{\parindent}{10pt}
\setlength{\parskip}{1pt}

%language
\usepackage{times}
\usepackage{t1enc}
%\usepackage[utf8x]{inputenc}
%\usepackage[polish]{babel}
%\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[scaled=0.88]{helvet}

%AMS
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{geometry}
 \geometry{a4paper,left=35mm,top=20mm,}

%environments
\newtheorem{fact}{Fact}

%abbreviations
\newcommand{\ra}{\rangle}
\newcommand{\la}{\langle}
\newcommand{\n}{\neg}
\newcommand{\et}{\wedge}
\newcommand{\jt}{\rightarrow}
\newcommand{\ko}[1]{\forall  #1\,}
\newcommand{\ro}{\leftrightarrow}
\newcommand{\exi}[1]{\exists\, {_{#1}}}
\newcommand{\pr}[1]{\mathsf{P}(#1)}
\newcommand{\cost}{\mathsf{cost}}

\newcommand{\odds}{\mathsf{Odds}}
\newcommand{\ind}{\mathsf{Ind}}
\newcommand{\nf}[2]{\nicefrac{#1\,}{#2}}
\newcommand{\R}[1]{\texttt{#1}}
\newcommand{\prr}[1]{\mbox{$\mathtt{P}_{prior}(#1)$}}
\newcommand{\prp}[1]{\mbox{$\mathtt{P}_{posterior}(#1)$}}

\newtheorem{q}{\color{blue}Question}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

%technical intermezzo
%---------------------

\newcommand{\intermezzoa}{
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Starts}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}\nopagebreak 
	}

\newcommand{\intermezzob}{\nopagebreak 
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Ends}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}
	}
%--------------------

\newtheorem*{reply*}{Reply}
\usepackage{enumitem}
\newcommand{\question}[1]{\begin{enumerate}[resume,leftmargin=0cm,labelsep=0cm,align=left]
\item #1
\end{enumerate}}

\usepackage{float}

% \setbeamertemplate{blocks}[rounded][shadow=true]
% \setbeamertemplate{itemize items}[ball]
% \AtBeginPart{}
% \AtBeginSection{}
% \AtBeginSubsection{}
% \AtBeginSubsubsection{}
% \setlength{\emergencystretch}{0em}
% \setlength{\parskip}{0pt}

\usepackage[authoryear]{natbib}

%\bibliographystyle{apalike}

\title{Nesta attacks study}
\author{Patrycja Tempska and Rafal Urbaniak}
\date{}

\begin{document}
\maketitle

\tableofcontents

\section{Section}\label{section}

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\DecValTok{2}\OperatorTok{+}\DecValTok{2} \CommentTok{#use this formatting for chunks}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 4
\end{verbatim}

\normalsize

\section{Section 2}\label{section-2}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\vspace{-3mm}

\end{document}

### 2021-07-15 paperDraft/meanOfMeans.R

@@ -1,0 +1,85 @@
+
+library(ggplot2)
+library(ggthemes)
+library(gridExtra)
+
+set.seed(123)
+t1 <- data.frame(A  = rnorm(5,1,0.05), B = rnorm(5,1,0.05))
+t2 <- data.frame(A  = rnorm(5,1,0.05), B = rnorm(5,1,0.05))
+
+t3 <- data.frame(A  = rnorm(5,1,0.05), B = rnorm(5,1,0.05))
+t4 <- data.frame(A  = rnorm(5,1,0.05), B = rnorm(5,1,0.05))
+
+
+t1Plot <- ggplot(t1)+geom_point(aes(y = 0, x = A), size = 2)+geom_point(aes(y = 0.1, x = B), col = "skyblue", size = 2)+theme_tufte()+xlab("distance")+scale_y_continuous(limits = c(-.05,.15),breaks = c(0,0.1), labels = c("A","B"))+ylab("group") + geom_vline(aes(xintercept = mean(A)), size = 0.3) + geom_vline(aes(xintercept = mean(B)), size = 0.3, col = "skyblue") +ggtitle("Distances for term t1")
+
+t2Plot <- ggplot(t2)+geom_point(aes(y = 0, x = A), size = 2)+geom_point(aes(y = 0.1, x = B), col = "skyblue", size = 2)+theme_tufte()+xlab("distance")+scale_y_continuous(limits = c(-.05,.15),breaks = c(0,0.1), labels = c("A","B"))+ylab("group") + geom_vline(aes(xintercept = mean(A)), size = 0.3) + geom_vline(aes(xintercept = mean(B)), size = 0.3, col = "skyblue") +ggtitle("Distances for term t2")
+
+
+t3Plot <- ggplot(t3)+geom_point(aes(y = 0, x = A), size = 2)+geom_point(aes(y = 0.1, x = B), col = "skyblue", size = 2)+theme_tufte()+xlab("distance")+scale_y_continuous(limits = c(-.05,.15),breaks = c(0,0.1), labels = c("A","B"))+ylab("group") + geom_vline(aes(xintercept = mean(A)), size = 0.3) + geom_vline(aes(xintercept = mean(B)), size = 0.3, col = "skyblue") +ggtitle("Distances for term t3")
+
[…]

### 2021-08-02 paperDraft/paperDraft.Rmd
Just a small change as a test.
abstract made and first few paragraphs added extra bibliography

@@
   pdf_document:
-    number_sections: true
+    number_sections: yes
     df_print: kable
-    keep_tex: true
+    keep_tex: yes
     includes:
-      in_header:
-        - Rafal_latex6.sty
+      in_header: Rafal_latex6.sty
+  html_document:
+    df_print: paged
+  word_document: default
 classoption: dvipsnames,enabledeprecatedfontcommands
@@
 urlcolor: blue
-bibliography: [../references/attacks.bib]
-csl: [../references/apa-6th-edition.csl] 
+bibliography: ../references/attacks.bib
+csl: ../references/apa-6th-edition.csl
 ---
@@
 library(gridExtra)
+
 ```
@@
 
-# Section
+# Section Abstract
+This article describes an experimental intervention study based in a naturalistic, digital setting (Q&A forum - Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
+Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
+Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks.
+Volunteers after receiving notifications employed interventions based on norm or empathy promotion.
+We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' user significantly decreased.
 
@@
 # Section 2
+Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys, it remains a common hindrance for people engaging with social media in their everyday lives.
+The situation got exacerbated amidst the COVID19 pandemic, during which a majority of our social life moved to cyberspace.
+During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content\footnote{\href {https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}}, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.
+According to a report conducted by company L1ght \footnote{\href {https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}}, hate speech directed towards China and the Chinese went up by 900% on Twitter.
+Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord.
+
+But alongside the growing need for even more efficient and proactive moderation, the capacity to put it into life did not go hand in hand, forcing companies and policymakers to rethink the current model of moderation processes and workforce.
+Due to the COVID19 restrictions including social distancing, a lot of those serving the role of moderators had to be sent home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}} without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA).
+
+gerrard2020covid19
 

### 2021-08-02 paperDraft/paperDraft.tex
abstract made and first few paragraphs added extra bibliography

@@
-\documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[
+  10pt,
+  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
@@
   linkcolor=Maroon,
+  filecolor=Maroon,
   citecolor=Blue,
   urlcolor=blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{color}
@@
 \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
 \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
 \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
 %\documentclass{article}
@@
 %\bibliographystyle{apalike}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-\section{Section}\label{section}
+\hypertarget{section-abstract}{%
+\section{Section Abstract}\label{section-abstract}}
 
-\vspace{1mm} \footnotesize
+This article describes an experimental intervention study based in a
+naturalistic, digital setting (Q\&A forum - Reddit), utilizing a
+collective intelligence approach to content moderation and reduction of
+the level of verbal aggression among a selected group of Reddit users
+who regularly attack other community members. Collective Intelligence in
+this sense means exploring the collaboration between human and machine
+intelligence to develop solutions to social challenges. Artificial
+Intelligence was used to detect verbal aggression (personal attacks) and
+notify human volunteers about attacks. Volunteers after receiving
+notifications employed interventions based on norm or empathy promotion.
+We find that only those who were sanctioned with norms-inducing
+interventions had their personal attacks' user significantly decreased.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\DecValTok{2}\OperatorTok{+}\DecValTok{2} \CommentTok{#use this formatting for chunks}
+\DecValTok{2}\SpecialCharTok{+}\DecValTok{2} \CommentTok{\#use this formatting for chunks}
 \end{Highlighting}
@@
 
-\section{Section 2}\label{section-2}
+\hypertarget{section-2}{%
+\section{Section 2}\label{section-2}}
 
-\section*{References}\label{references}
+Although much effort has been made in order to tackle the problem of
+verbal aggression and harassment online, looking at various reports and
+surveys, it remains a common hindrance for people engaging with social
+media in their everyday lives. The situation got exacerbated amidst the
+COVID19 pandemic, during which a majority of our social life moved to
+cyberspace. During this shift, there was an increase in cyberbullying
+attitudes and perpetration (Barlett, Simmers, Roth, \& Gentile (2021)),
+90\% increase in public reports of illegal online
+content\footnote{\href {https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}},
+including 114\% increase in non-consensual sharing of intimate images,
+30\% increase in cyberbullying, as well as 40\% of increase in adults
+reporting online harassment. According to a report conducted by company
+L1ght \textbackslash footnote\{\textbackslash href
+\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\},
+hate speech directed towards China and the Chinese went up by 900\% on
+Twitter. Gaming platforms were in the spotlight as well, with a 40\%
+increase in toxicity on Discord.
+
+But alongside the growing need for even more efficient and proactive
+moderation, the capacity to put it into life did not go hand in hand,
+forcing companies and policymakers to rethink the current model of
+moderation processes and workforce. Due to the COVID19 restrictions
+including social distancing, a lot of those serving the role of
+moderators had to be sent
+home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}}
+without the ability to work remotely because of the constraints
+affiliated with restrictive non-disclosure agreements (NDA).
+
+gerrard2020covid19
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}
@@
 
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-barlett2021comparing}{}%
+Barlett, C. P., Simmers, M. M., Roth, B., \& Gentile, D. (2021).
+Comparing cyberbullying prevalence and process before and during the
+COVID-19 pandemic. \emph{The Journal of Social Psychology}, 1--11.
+
+\end{CSLReferences}
+
 \end{document}

### 2021-08-07 paperDraft/paperDraft.Rmd
developed the section on moderation landscape (for automated methods)

@@
 
-# Section 2
+# Introduction
 Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys, it remains a common hindrance for people engaging with social media in their everyday lives.
@@
 
-But alongside the growing need for even more efficient and proactive moderation, the capacity to put it into life did not go hand in hand, forcing companies and policymakers to rethink the current model of moderation processes and workforce.
-Due to the COVID19 restrictions including social distancing, a lot of those serving the role of moderators had to be sent home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}} without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA).
+But alongside the growing need for even more efficient and proactive moderation, the capacity to execute it did not go hand in hand, forcing companies and policymakers to rethink the current model of moderation processes and workforce.
+Due to the COVID19 restrictions including social distancing, a lot of those serving the role of moderators had to be sent home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}} without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA) among others.
+Curtailing the moderators' workforce was accompanied by more agency given to algorithms and AI-based moderation.
+Those changes, as argued by @gerrard2020covid19, can be seen as a serious red flag in terms of safety for all users on online platforms.
 
-gerrard2020covid19
+# Automated versus Human-based Moderation
+The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around technology performance (@macavaney2019hate, @schmidt2017survey).
+State-of-the-art solutions are mostly governed by statistical methods including deep learning and machine learning (@lecun2015deep, @sejnowski2020unreasonable, @jordan2015machine).
+Their performance is inherently tied to the amount of data being fed to the system and the quality of its annotation.
+At different stages of the process, from datasets gathering and preparation, annotation to the training or algorithms themselves, biases seem to be omnipresent (@binns2017like, @geva2019we @mehrabi2021survey).
+Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love").
+Generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training are an important shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic).
+As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, creations of models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
+This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public.
+Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike.
+First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
+Second, inability for successful identification of the sources of empirical gains (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
+Third, "mathiness" - the use obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
+Last but not least - misuse of language.
+This includes suggestive definitions without proper explanation of what they mean in the context (e.g.
+inflating good performance in simple NLP tasks to human-level natural understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g.
+consciousness).
+
+Yet another obstacle in the process is the lack of gold standard in dataset creation and taxonomies of abusive language being used for instance in the process of annotating different datasets.
+Frequently people obtain data from various sources and do not follow any universally used instructions when it comes to its annotation, leading to discrepancies between various datasets being tagged within one domain (e.g.
+hate speech).
+Lack of expert annotators and proper annotation criteria and instructions are also widespread, with the common practice hiring untrained workers from Mechanical Turk or other crowdsourcing platforms.
+
+Although there are some initiatives developed in response, most notably, functional tests for Hate Speech Detection Models created by @rottger2020hatecheck, or the Online Safety Data Initiative (OSDI) LINK https://onlinesafetydata.blog.gov.uk/about-us/, focused on projects related to improving access to data, standardizing the description of online harms, as well as creating tools and benchmarks for evaluation of technologies focused on safety, much effort must be made before wider adoption of such solutions comes into force.
 

### 2021-08-07 paperDraft/paperDraft.tex
developed the section on moderation landscape (for automated methods)

@@
 
-\hypertarget{section-2}{%
-\section{Section 2}\label{section-2}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 But alongside the growing need for even more efficient and proactive
-moderation, the capacity to put it into life did not go hand in hand,
-forcing companies and policymakers to rethink the current model of
-moderation processes and workforce. Due to the COVID19 restrictions
-including social distancing, a lot of those serving the role of
-moderators had to be sent
+moderation, the capacity to execute it did not go hand in hand, forcing
+companies and policymakers to rethink the current model of moderation
+processes and workforce. Due to the COVID19 restrictions including
+social distancing, a lot of those serving the role of moderators had to
+be sent
 home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}}
 without the ability to work remotely because of the constraints
-affiliated with restrictive non-disclosure agreements (NDA).
+affiliated with restrictive non-disclosure agreements (NDA) among
+others. Curtailing the moderators' workforce was accompanied by more
+agency given to algorithms and AI-based moderation. Those changes, as
+argued by Gerrard (2020), can be seen as a serious red flag in terms of
+safety for all users on online platforms.
 
-gerrard2020covid19
+\hypertarget{automated-versus-human-based-moderation}{%
+\section{Automated versus Human-based
+Moderation}\label{automated-versus-human-based-moderation}}
+
+The hindrances and threats that go along with the Artificial
+Intelligence-based methods for moderation have been widely debated, with
+the most critical discussions revolving around technology performance
+(MacAvaney et al. (2019), Schmidt \& Wiegand (2017)). State-of-the-art
+solutions are mostly governed by statistical methods including deep
+learning and machine learning (LeCun, Bengio, \& Hinton (2015),
+Sejnowski (2020), Jordan \& Mitchell (2015)). Their performance is
+inherently tied to the amount of data being fed to the system and the
+quality of its annotation. At different stages of the process, from
+datasets gathering and preparation, annotation to the training or
+algorithms themselves, biases seem to be omnipresent (Binns, Veale, Van
+Kleek, \& Shadbolt (2017), Geva, Goldberg, \& Berant (2019) Mehrabi,
+Morstatter, Saxena, Lerman, \& Galstyan (2021)). Users' of online
+services are also creative in their strategies to circumvent automated
+content moderation systems and as shown by Gröndahl, Pajola, Juuti,
+Conti, \& Asokan (2018), current techniques are vulnerable to the most
+common evasion attacks like word changes (inseting typos and leetspeak),
+word-boundary changes (inserting or removing whitespace), or word
+appending (appending common or non-hateful words like ``love'').
+Generalisability of the models - an ability to perform well on datasets
+coming from sources other than the one used for training are an
+important shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \&
+Gambäck (2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \&
+Weld (2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
+(2020) in practice, creations of models often lacks thorough error
+analysis and legitimate experimental methodology, which can result in
+non-reproducibility. This is also connected with a potential lack of
+thorough understanding of the limitations of the models and spurious
+conclusions being made to a wider public. Specifically, @Lipton \&
+Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
+the current research paradigm in the industry and academia alike. First,
+the inability to draw a clear distinction between speculation and
+explanation, with the first one often being disguised as the second.
+Second, inability for successful identification of the sources of
+empirical gains (whether it was problem formulation, optimization of the
+heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
+another aspect). Third, ``mathiness'' - the use obscure language and
+often covering weak argumentation with the alluring but often apparent
+depth of technical jargon. Last but not least - misuse of language. This
+includes suggestive definitions without proper explanation of what they
+mean in the context (e.g.~inflating good performance in simple NLP tasks
+to human-level natural understanding), overloading the papers with
+technical terminology, or suitcase words (those words that can encompass
+a variety of meanings, e.g.~consciousness).
+
+Yet another obstacle in the process is the lack of gold standard in
+dataset creation and taxonomies of abusive language being used for
+instance in the process of annotating different datasets. Frequently
+people obtain data from various sources and do not follow any
+universally used instructions when it comes to its annotation, leading
+to discrepancies between various datasets being tagged within one domain
+(e.g.~hate speech). Lack of expert annotators and proper annotation
+criteria and instructions are also widespread, with the common practice
+hiring untrained workers from Mechanical Turk or other crowdsourcing
+platforms.
+
+Although there are some initiatives developed in response, most notably,
+functional tests for Hate Speech Detection Models created by Röttger et
+al. (2020), or the Online Safety Data Initiative (OSDI) LINK
+\url{https://onlinesafetydata.blog.gov.uk/about-us/}, focused on
+projects related to improving access to data, standardizing the
+description of online harms, as well as creating tools and benchmarks
+for evaluation of technologies focused on safety, much effort must be
+made before wider adoption of such solutions comes into force.
 
@@
 
+\leavevmode\hypertarget{ref-binns2017like}{}%
+Binns, R., Veale, M., Van Kleek, M., \& Shadbolt, N. (2017). Like
+trainer, like bot? Inheritance of bias in algorithmic content
+moderation. \emph{International Conference on Social Informatics},
+405--415. Springer.
+
+\leavevmode\hypertarget{ref-gerrard2020covid19}{}%
+Gerrard, Y. (2020). \textless? covid19?\textgreater{} The COVID-19
+mental health content moderation conundrum. \emph{Social Media+
+Society}, \emph{6}(3), 2056305120948186.
+
+\leavevmode\hypertarget{ref-geva2019we}{}%
+Geva, M., Goldberg, Y., \& Berant, J. (2019). Are we modeling the task
+or the annotator? An investigation of annotator bias in natural language
+understanding datasets. \emph{arXiv Preprint arXiv:1908.07898}.
+
+\leavevmode\hypertarget{ref-grondahl2018all}{}%
+Gröndahl, T., Pajola, L., Juuti, M., Conti, M., \& Asokan, N. (2018).
+All you need is" love" evading hate speech detection. \emph{Proceedings
+of the 11th ACM Workshop on Artificial Intelligence and Security},
+2--12.
+
+\leavevmode\hypertarget{ref-jordan2015machine}{}%
+Jordan, M. I., \& Mitchell, T. M. (2015). Machine learning: Trends,
+perspectives, and prospects. \emph{Science}, \emph{349}(6245), 255--260.
+
+\leavevmode\hypertarget{ref-lecun2015deep}{}%
+LeCun, Y., Bengio, Y., \& Hinton, G. (2015). Deep learning.
+\emph{Nature}, \emph{521}(7553), 436--444.
+
+\leavevmode\hypertarget{ref-lipton2019troubling}{}%
+Lipton, Z. C., \& Steinhardt, J. (2019). Troubling trends in machine
+learning scholarship: Some ML papers suffer from flaws that could
+mislead the public and stymie future research. \emph{Queue},
+\emph{17}(1), 45--77.
+
+\leavevmode\hypertarget{ref-macavaney2019hate}{}%
+MacAvaney, S., Yao, H.-R., Yang, E., Russell, K., Goharian, N., \&
+Frieder, O. (2019). Hate speech detection: Challenges and solutions.
+\emph{PloS One}, \emph{14}(8), e0221152.
+
+\leavevmode\hypertarget{ref-mehrabi2021survey}{}%
+Mehrabi, N., Morstatter, F., Saxena, N., Lerman, K., \& Galstyan, A.
+(2021). A survey on bias and fairness in machine learning. \emph{ACM
+Computing Surveys (CSUR)}, \emph{54}(6), 1--35.
+
+\leavevmode\hypertarget{ref-musgrave2020metric}{}%
+Musgrave, K., Belongie, S., \& Lim, S.-N. (2020). A metric learning
+reality check. \emph{European Conference on Computer Vision}, 681--699.
+Springer.
+
+\leavevmode\hypertarget{ref-rosa2019automatic}{}%
+Rosa, H., Pereira, N., Ribeiro, R., Ferreira, P. C., Carvalho, J. P.,
+Oliveira, S., \ldots{} Trancoso, I. (2019). Automatic cyberbullying
+detection: A systematic review. \emph{Computers in Human Behavior},
+\emph{93}, 333--345.
+
+\leavevmode\hypertarget{ref-rottger2020hatecheck}{}%
+Röttger, P., Vidgen, B., Nguyen, D., Waseem, Z., Margetts, H., \&
+Pierrehumbert, J. (2020). Hatecheck: Functional tests for hate speech
+detection models. \emph{arXiv Preprint arXiv:2012.15606}.
+
+\leavevmode\hypertarget{ref-schmidt2017survey}{}%
+Schmidt, A., \& Wiegand, M. (2017). A survey on hate speech detection
+using natural language processing. \emph{Proceedings of the Fifth
+International Workshop on Natural Language Processing for Social Media},
+1--10.
+
+\leavevmode\hypertarget{ref-sejnowski2020unreasonable}{}%
+Sejnowski, T. J. (2020). The unreasonable effectiveness of deep learning
+in artificial intelligence. \emph{Proceedings of the National Academy of
+Sciences}, \emph{117}(48), 30033--30038.
+
+\leavevmode\hypertarget{ref-swamy2019studying}{}%
+Swamy, S. D., Jamatia, A., \& Gambäck, B. (2019). Studying
+generalisability across abusive language detection datasets.
+\emph{Proceedings of the 23rd Conference on Computational Natural
+Language Learning (CoNLL)}, 940--950.
+
+\leavevmode\hypertarget{ref-wu2019errudite}{}%
+Wu, T., Ribeiro, M. T., Heer, J., \& Weld, D. S. (2019). Errudite:
+Scalable, reproducible, and testable error analysis. \emph{Proceedings
+of the 57th Annual Meeting of the Association for Computational
+Linguistics}, 747--763.
+
+\leavevmode\hypertarget{ref-yin2021towards}{}%
+Yin, W., \& Zubiaga, A. (2021). Towards generalisable hate speech
+detection: A review on obstacles and solutions. \emph{PeerJ Computer
+Science}, \emph{7}, e598.
+
 \end{CSLReferences}

### 2021-08-11 paperDraft/paperDraft.Rmd
theoretical intro - on moderation expanded

@@
 
+At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms.
+On Facebook, there are more than 3B comments and likes daily (https://martech.org/facebook-3-2-billion-likes-comments-every-day/), 500M tweets are sent daily on Twitter (https://www.oberlo.com/blog/twitter-statistics), and over 2B comments made by users of Reddit in 2020 (https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/) which is almost 3M comments made daily.
+With this amount of content, it's either impossible or extremely costly to scale the moderation workforce.
+One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being.
+Being submersed in the cyber-Augean stables takes a toll on many people.
+As examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs.
+Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases.
+This can lead to serious psychological damage, like depression, or PTSD (@roberts2014behind).
+Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job (https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health).
+Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.
+There is yet another aspect here - what moderators deal with is mostly content reported by humans.
+And as shown in various studies and reports, a lot of children, teens or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).
+
+# Pro-active and reactive moderation
+
+#Collective Intelligence Approach
+
+#Experimental Design
+
+#Results
+
 #  References {-}

### 2021-08-11 paperDraft/paperDraft.tex
theoretical intro - on moderation expanded

@@
 
+At the same time, only automated methods can scan through the massive
+amount of content being generated every day on different platforms. On
+Facebook, there are more than 3B comments and likes daily
+(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
+500M tweets are sent daily on Twitter
+(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
+comments made by users of Reddit in 2020
+(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
+which is almost 3M comments made daily. With this amount of content,
+it's either impossible or extremely costly to scale the moderation
+workforce. One can also have doubts about the ethical aspects of hiring
+workers who are often unaware of how this kind of task will affect their
+well-being. Being submersed in the cyber-Augean stables takes a toll on
+many people. As examined by Roberts (2014) \& Roberts (2016), workers
+who are hired for such tasks are often low-status and low-wage,
+isolated, and asked to keep what they've seen in secret under
+restrictive NDAs. Screening through the reported user-generated content
+is connected with exposure to violent and deeply disturbing materials,
+with child pornography, murders, or suicides as examples of the most
+extreme cases. This can lead to serious psychological damage, like
+depression, or PTSD (Roberts (2014)). Some of the employees filed a
+lawsuit against Facebook and as a result, the company agreed to pay
+\$52M in compensation for mental health issues developed during the job
+(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
+Taking into consideration that Facebook employs 15K moderators
+(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
+and most likely more are needed to keep up with the growing amount of
+content, with the parallel considerations about the negative effects of
+content moderation on mental health, a collaboration between humans and
+machines in this area seems inevitable. There is yet another aspect here
+- what moderators deal with is mostly content reported by humans. And as
+shown in various studies and reports, a lot of children, teens or even
+adults do not report cyberbullying or harassment online (LINKS:
+\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
+; \url{https://www.adl.org/free-to-play-2020} ;
+\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).
+
+\hypertarget{pro-active-and-reactive-moderation}{%
+\section{Pro-active and reactive
+moderation}\label{pro-active-and-reactive-moderation}}
+
+\#Collective Intelligence Approach
+
+\#Experimental Design
+
+\#Results
+
 \hypertarget{references}{%
@@
 
+\leavevmode\hypertarget{ref-roberts2014behind}{}%
+Roberts, S. T. (2014). \emph{Behind the screen: The hidden digital labor
+of commercial content moderation}. University of Illinois at
+Urbana-Champaign.
+
+\leavevmode\hypertarget{ref-roberts2016commercial}{}%
+Roberts, S. T. (2016). \emph{Commercial content moderation: Digital
+laborers' dirty work}.
+
 \leavevmode\hypertarget{ref-rosa2019automatic}{}%

### 2021-08-11 paperDraft/paperDraft.Rmd
started work on experimental design

@@
 
-#Collective Intelligence Approach
+# Collective Intelligence Approach to Counter-speech
 
-#Experimental Design
+# Experimental Design
+This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
+We formed treatment and control groups based on three main criteria:
+1.
+During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
+Thus, we needed approximately 200 attacks daily generated by the treatment groups.
+2. Recruitment of users who regularly attack others was necessary to measure the effect of interventions at the end.
+3. Recruitment of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+First, we spent 9 weeks for preliminary Reddit's monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring.
+As mentioned, sustained activity was crucial to minimize the risk users becoming inactive during the course of the study.
+Next, we have calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day - 1.94 attacks daily per person on average).
+Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per group).
+The rest (304 people) were selected as our control group.
 
-#Results
+Three groups were formed - two treatment groups (195 people in each) and one control group (304 people).
+The first treatment group received counter-speech interventions based on normative influence, while the second one received interventions based on empathetic influence.
+Users in the control group did not receive any intervention.
+
+The duration of the experiment, 6 months, was divided into three 2-months periods.
+The first two months served as a monitoring period to properly select groups and establish baselines.
+The next 2 months served as treatment period, during which groups received counter-speech comments from volunteers, in response to personal attacks detected by the Artificial Intelligence-based system.
+The last 2-months served as the post-treatment monitoring period to gather the data needed to evaluate the effectiveness of interventions.
+
+Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others.
+E.g. Insulting others is against Reddit's policy. 
+Hey there, we do not call each other like that here.
+Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both. They are designed to evoke an empathetic response. 
+E.g. There is a human being on the other side who might be hurt by your words.
+I see you are frustrated but remember the human.
+
+Cyberviolence was defined in this experiment as a personal attack - any kind of verbal harassment, insult, or threat directed against the interlocutor in a text-based conversation online.
+Those were detected using Samurai Labs' cyberviolence detection system.
+
+The following hypotheses were formulated:
+
+H1: If a group of human volunteers notified by an AI-based cyberviolence detection system about cyberviolence generated by the treatment group users (cyberviolence will be defined as a personal attack, harassment, or a threat targeted against an interlocutor) responds with counter-speech interventions, this will result in a decreased cyberviolence level for the whole group after the intervention period.
+
+H2: If two groups receive different types of interventions (empathy-based or normative), then the decrease in cyberviolence will be larger in the case of normative interventions in comparison to the empathy-based ones.
+
+# Results
 

### 2021-08-11 paperDraft/paperDraft.tex
started work on experimental design

@@
 
-\#Collective Intelligence Approach
+\hypertarget{collective-intelligence-approach-to-counter-speech}{%
+\section{Collective Intelligence Approach to
+Counter-speech}\label{collective-intelligence-approach-to-counter-speech}}
 
-\#Experimental Design
+\hypertarget{experimental-design}{%
+\section{Experimental Design}\label{experimental-design}}
 
-\#Results
+This was a 6-months field experiment in a digital setting conducted on a
+popular Q\&A and news forum, Reddit (www.reddit.com). We formed
+treatment and control groups based on three main criteria: 1. During the
+intervention period, we have expected to have 20 active volunteers at
+any given time, each willing to conduct 10 interventions daily. Thus, we
+needed approximately 200 attacks daily generated by the treatment
+groups. 2. Recruitment of users who regularly attack others was
+necessary to measure the effect of interventions at the end. 3.
+Recruitment of users who were active during the whole preliminary
+monitoring period was necessary to minimize the risk of attrition during
+the study. First, we spent 9 weeks for preliminary Reddit's monitoring
+period to recruit only those users who generate at least one personal
+attack per week and were active during the whole period of the
+monitoring. As mentioned, sustained activity was crucial to minimize the
+risk users becoming inactive during the course of the study. Next, we
+have calculated the daily average number of personal attacks generated
+by the group who met the above criteria (which resulted in 357 attacks
+per day - 1.94 attacks daily per person on average). Knowing that we
+need around 200 attacks daily (just enough so our volunteers can keep up
+with the volume) we have randomly selected 390 people for our study
+groups (195 per group). The rest (304 people) were selected as our
+control group.
+
+Three groups were formed - two treatment groups (195 people in each) and
+one control group (304 people). The first treatment group received
+counter-speech interventions based on normative influence, while the
+second one received interventions based on empathetic influence. Users
+in the control group did not receive any intervention.
+
+The duration of the experiment, 6 months, was divided into three
+2-months periods. The first two months served as a monitoring period to
+properly select groups and establish baselines. The next 2 months served
+as treatment period, during which groups received counter-speech
+comments from volunteers, in response to personal attacks detected by
+the Artificial Intelligence-based system. The last 2-months served as
+the post-treatment monitoring period to gather the data needed to
+evaluate the effectiveness of interventions.
+
+Normative interventions can refer either to general social norms of
+civility and respect, community standards, a particular subreddit rule,
+or a descriptive norm among others. E.g. Insulting others is against
+Reddit's policy. Hey there, we do not call each other like that here.
+Empathetic interventions can refer to the emotional state of the
+recipient or the sender of the attack or both. They are designed to
+evoke an empathetic response. E.g. There is a human being on the other
+side who might be hurt by your words. I see you are frustrated but
+remember the human.
+
+Cyberviolence was defined in this experiment as a personal attack - any
+kind of verbal harassment, insult, or threat directed against the
+interlocutor in a text-based conversation online. Those were detected
+using Samurai Labs' cyberviolence detection system.
+
+The following hypotheses were formulated:
+
+H1: If a group of human volunteers notified by an AI-based cyberviolence
+detection system about cyberviolence generated by the treatment group
+users (cyberviolence will be defined as a personal attack, harassment,
+or a threat targeted against an interlocutor) responds with
+counter-speech interventions, this will result in a decreased
+cyberviolence level for the whole group after the intervention period.
+
+H2: If two groups receive different types of interventions
+(empathy-based or normative), then the decrease in cyberviolence will be
+larger in the case of normative interventions in comparison to the
+empathy-based ones.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
 

### 2021-08-17 paperDraft/paperDraft.Rmd
theoretical part expanded - reactive vs pro-active moderation

@@
 Volunteers after receiving notifications employed interventions based on norm or empathy promotion.
-We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' user significantly decreased.
+We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' level significantly decreased.
 
@@
 Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love").
-Generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training are an important shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic).
+Lack of generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic).
 As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, creations of models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
@@
 This includes suggestive definitions without proper explanation of what they mean in the context (e.g.
-inflating good performance in simple NLP tasks to human-level natural understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g.
+inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g.
 consciousness).
@@
 One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being.
-Being submersed in the cyber-Augean stables takes a toll on many people.
-As examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs.
+Being submersed in the cyber-Augean stables takes a toll on many - as examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs.
 Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases.
@@
 Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.
-There is yet another aspect here - what moderators deal with is mostly content reported by humans.
-And as shown in various studies and reports, a lot of children, teens or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).
 
 # Pro-active and reactive moderation
+There are different approaches when it comes to the moderation of online content.
+One can follow the workflow of reactive moderation, which happens once the content is published.
+Harmful messages can be either reported by the users of the platforms or automated methods and then sent for review to moderators.
+A set of actions can be then taken depending on the platform and their community guidelines - on the content or user level.
+A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them.
+Depending on the type and amount of infraction, a particular user can be warned, muted or shadowbanned, or banned from further participation in the community for a period of time.
+The weakness of the reactive method is that the damage is done.
+Whoever is the recipient of the abusive message has the chance to see it and potentially suffer (@hoff2009cyberbullying, @keipi2016online, Wwachs2019associations).
+Yet another weakness connected with relying solely on human reports is the content that is harmful but unreported by a receipted or any bystander.
+Although the exact scale of unreported content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).
+
+Yet another type of moderation can be distinguished as pro-active or pre-moderation.
+In pre-moderation, automated methods are either based on Artificial Intelligence or other less sophisticated tools (e.g.
+blacklists) and can screen the content before it gets published.
+If a type of harmful message gets detected, it can be removed before reaching the recipient.
+Due to the aforementioned dubious performance of state-of-the-art statistical methods, particularly low precision, they are rarely used autonomously.
+
+Pro-active moderation can be utilized using AI or other methods to promote socially positive engagement.
+Instead of or in the combination with punitive solutions like privileges restriction, one can induce empathy or community norms with counter-speech.
+Counter speech as described by Dangerous Speech Project (https://dangerousspeech.org/counterspeech/) is "any direct response to hateful or harmful speech which seeks to undermine it".
+As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male).
+In a study conducted by @bilewicz2021artificial, a bot
+...
 

### 2021-08-17 paperDraft/paperDraft.tex
theoretical part expanded - reactive vs pro-active moderation

@@
 We find that only those who were sanctioned with norms-inducing
-interventions had their personal attacks' user significantly decreased.
+interventions had their personal attacks' level significantly decreased.
 
@@
 word-boundary changes (inserting or removing whitespace), or word
-appending (appending common or non-hateful words like ``love'').
-Generalisability of the models - an ability to perform well on datasets
-coming from sources other than the one used for training are an
-important shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \&
-Gambäck (2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \&
-Weld (2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
+appending (appending common or non-hateful words like ``love''). Lack of
+generalisability of the models - an ability to perform well on datasets
+coming from sources other than the one used for training is a serious
+shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \& Gambäck
+(2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \& Weld
+(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
 (2020) in practice, creations of models often lacks thorough error
@@
 mean in the context (e.g.~inflating good performance in simple NLP tasks
-to human-level natural understanding), overloading the papers with
-technical terminology, or suitcase words (those words that can encompass
-a variety of meanings, e.g.~consciousness).
+to human-level understanding), overloading the papers with technical
+terminology, or suitcase words (those words that can encompass a variety
+of meanings, e.g.~consciousness).
 
@@
 well-being. Being submersed in the cyber-Augean stables takes a toll on
-many people. As examined by Roberts (2014) \& Roberts (2016), workers
-who are hired for such tasks are often low-status and low-wage,
-isolated, and asked to keep what they've seen in secret under
-restrictive NDAs. Screening through the reported user-generated content
-is connected with exposure to violent and deeply disturbing materials,
-with child pornography, murders, or suicides as examples of the most
-extreme cases. This can lead to serious psychological damage, like
-depression, or PTSD (Roberts (2014)). Some of the employees filed a
-lawsuit against Facebook and as a result, the company agreed to pay
-\$52M in compensation for mental health issues developed during the job
+many - as examined by Roberts (2014) \& Roberts (2016), workers who are
+hired for such tasks are often low-status and low-wage, isolated, and
+asked to keep what they've seen in secret under restrictive NDAs.
+Screening through the reported user-generated content is connected with
+exposure to violent and deeply disturbing materials, with child
+pornography, murders, or suicides as examples of the most extreme cases.
+This can lead to serious psychological damage, like depression, or PTSD
+(Roberts (2014)). Some of the employees filed a lawsuit against Facebook
+and as a result, the company agreed to pay \$52M in compensation for
+mental health issues developed during the job
 (\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
@@
 content moderation on mental health, a collaboration between humans and
-machines in this area seems inevitable. There is yet another aspect here
-- what moderators deal with is mostly content reported by humans. And as
-shown in various studies and reports, a lot of children, teens or even
-adults do not report cyberbullying or harassment online (LINKS:
+machines in this area seems inevitable.
+
+\hypertarget{pro-active-and-reactive-moderation}{%
+\section{Pro-active and reactive
+moderation}\label{pro-active-and-reactive-moderation}}
+
+There are different approaches when it comes to the moderation of online
+content. One can follow the workflow of reactive moderation, which
+happens once the content is published. Harmful messages can be either
+reported by the users of the platforms or automated methods and then
+sent for review to moderators. A set of actions can be then taken
+depending on the platform and their community guidelines - on the
+content or user level. A harmful message can be deleted, made invisible
+to other users, or certain profanities can be altered with special signs
+to censor them. Depending on the type and amount of infraction, a
+particular user can be warned, muted or shadowbanned, or banned from
+further participation in the community for a period of time. The
+weakness of the reactive method is that the damage is done. Whoever is
+the recipient of the abusive message has the chance to see it and
+potentially suffer (Hoff \& Mitchell (2009), Keipi, Näsi, Oksanen, \&
+Räsänen (2016), Wwachs2019associations). Yet another weakness connected
+with relying solely on human reports is the content that is harmful but
+unreported by a receipted or any bystander. Although the exact scale of
+unreported content is not known, various self-report studies show that a
+lot of children, teens, or even adults do not report cyberbullying or
+harassment online (LINKS:
 \url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
@@
 
-\hypertarget{pro-active-and-reactive-moderation}{%
-\section{Pro-active and reactive
-moderation}\label{pro-active-and-reactive-moderation}}
+Yet another type of moderation can be distinguished as pro-active or
+pre-moderation. In pre-moderation, automated methods are either based on
+Artificial Intelligence or other less sophisticated tools
+(e.g.~blacklists) and can screen the content before it gets published.
+If a type of harmful message gets detected, it can be removed before
+reaching the recipient. Due to the aforementioned dubious performance of
+state-of-the-art statistical methods, particularly low precision, they
+are rarely used autonomously.
+
+Pro-active moderation can be utilized using AI or other methods to
+promote socially positive engagement. Instead of or in the combination
+with punitive solutions like privileges restriction, one can induce
+empathy or community norms with counter-speech. Counter speech as
+described by Dangerous Speech Project
+(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
+response to hateful or harmful speech which seeks to undermine it.'' As
+examined by Munger (2017), counter-speech can be effective in the
+reduction of racist tweets (although only in the condition in which a
+white male with high followers was approaching another white male). In a
+study conducted by Bilewicz et al. (2021), a bot \ldots{}
 
@@
 
+\leavevmode\hypertarget{ref-bilewicz2021artificial}{}%
+Bilewicz, M., Tempska, P., Leliwa, G., Dowgiałło, M., Tańska, M.,
+Urbaniak, R., \& Wroczyński, M. (2021). Artificial intelligence against
+hate: Intervention reducing verbal aggression in the social network
+environment. \emph{Aggressive Behavior}, \emph{47}(3), 260--266.
+
 \leavevmode\hypertarget{ref-binns2017like}{}%
@@
 
+\leavevmode\hypertarget{ref-hoff2009cyberbullying}{}%
+Hoff, D. L., \& Mitchell, S. N. (2009). Cyberbullying: Causes, effects,
+and remedies. \emph{Journal of Educational Administration}.
+
 \leavevmode\hypertarget{ref-jordan2015machine}{}%
@@
 perspectives, and prospects. \emph{Science}, \emph{349}(6245), 255--260.
+
+\leavevmode\hypertarget{ref-keipi2016online}{}%
+Keipi, T., Näsi, M., Oksanen, A., \& Räsänen, P. (2016). \emph{Online
+hate and harmful content: Cross-national perspectives}. Taylor \&
+Francis.
 
@@
 Computing Surveys (CSUR)}, \emph{54}(6), 1--35.
+
+\leavevmode\hypertarget{ref-munger2017tweetment}{}%
+Munger, K. (2017). Tweetment effects on the tweeted: Experimentally
+reducing racist harassment. \emph{Political Behavior}, \emph{39}(3),
+629--649.
 

### 2021-08-18 paperDraft/paperDraft.Rmd
theoretical intro expanded - proactive/reactive moderation

@@
 As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male).
-In a study conducted by @bilewicz2021artificial, a bot
+In a study conducted by @bilewicz2021artificial, a bot disguised as a Reddit user, equipped with normative and empathetic interventions, significantly decreased the amount of personal attacks generated on Reddit.
+In yet another study by @mivskolci2020countering, this technique was not effective in changing the behavior of the users (counter-speech here aimed at reducing the prejudice against Roma minority in Slovakia), but encouraged bystanders to express pro-Roma comments on specific Facebook posts.
+Counter-speech also has been shown to have the potential to increase civility online in studies conducted by @friess2021collective, @molina2018role, @han2018civility.
 ...
@@
 
-# Experimental Design
+# Experimental Design and data collection
 This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 

### 2021-08-18 paperDraft/paperDraft.tex
theoretical intro expanded - proactive/reactive moderation

@@
 white male with high followers was approaching another white male). In a
-study conducted by Bilewicz et al. (2021), a bot \ldots{}
+study conducted by Bilewicz et al. (2021), a bot disguised as a Reddit
+user, equipped with normative and empathetic interventions,
+significantly decreased the amount of personal attacks generated on
+Reddit. In yet another study by Miškolci, Kováčová, \& Rigová (2020),
+this technique was not effective in changing the behavior of the users
+(counter-speech here aimed at reducing the prejudice against Roma
+minority in Slovakia), but encouraged bystanders to express pro-Roma
+comments on specific Facebook posts. Counter-speech also has been shown
+to have the potential to increase civility online in studies conducted
+by Friess, Ziegele, \& Heinbach (2021), Molina \& Jennings (2018), Han,
+Brazeal, \& Pennington (2018). \ldots{}
 
@@
 
-\hypertarget{experimental-design}{%
-\section{Experimental Design}\label{experimental-design}}
+\hypertarget{experimental-design-and-data-collection}{%
+\section{Experimental Design and data
+collection}\label{experimental-design-and-data-collection}}
 
@@
 
+\leavevmode\hypertarget{ref-friess2021collective}{}%
+Friess, D., Ziegele, M., \& Heinbach, D. (2021). Collective civic
+moderation for deliberation? Exploring the links between citizens'
+organized engagement in comment sections and the deliberative quality of
+online discussions. \emph{Political Communication}, 1--23.
+
 \leavevmode\hypertarget{ref-gerrard2020covid19}{}%
@@
 2--12.
+
+\leavevmode\hypertarget{ref-han2018civility}{}%
+Han, S.-H., Brazeal, L. M., \& Pennington, N. (2018). Is civility
+contagious? Examining the impact of modeling in online political
+discussions. \emph{Social Media+ Society}, \emph{4}(3),
+2056305118793404.
 
@@
 Computing Surveys (CSUR)}, \emph{54}(6), 1--35.
+
+\leavevmode\hypertarget{ref-mivskolci2020countering}{}%
+Miškolci, J., Kováčová, L., \& Rigová, E. (2020). Countering hate speech
+on facebook: The case of the roma minority in slovakia. \emph{Social
+Science Computer Review}, \emph{38}(2), 128--146.
+
+\leavevmode\hypertarget{ref-molina2018role}{}%
+Molina, R. G., \& Jennings, F. J. (2018). The role of civility and
+metacommunication in facebook discussions. \emph{Communication Studies},
+\emph{69}(1), 42--66.
 

### 2021-08-19 oldCleanup/RcontrolCleanup.R
added old cleanup

@@ -1,0 +1,80 @@
+library(data.table)
+library(tidyverse)
+library(ggplot2)
+library(scales)
+
+#_________ load files, select & rename columns, inspect attacks
+#we load twice to be able to inspect raw data at all times
+RcontrolAttacks <- as.data.frame(fread("Rcontrol_attacks_final.txt",quote = ""))
+RcontrolAttacksRaw <- as.data.frame(fread("Rcontrol_attacks_final.txt",quote = ""))
+
+
+# rename columns, use camelCase throughout the project!!
+colnames(RcontrolAttacks) <-  c("id", "utc", "author","text","subreddit", "parentID","link", "high", "low","rules", "receiver", "replyToPost")
+colnames(RcontrolAttacksRaw) <-  c("id", "utc", "author","text","subreddit", "parentID","link", "high", "low","rules", "receiver", "replyToPost")
+
+
+#take a look
+head(RcontrolAttacks)
+
+
+# remove columns not used in the aggregation
+RcontrolAttacksClean <-  RcontrolAttacks %>% select(-c(text,parentID,link,rules)) 
+
+#inspect again
+head(RcontrolAttacksClean)
+
+#convert time stamps to dates
+RcontrolAttacksClean$day <- as.Date(as.POSIXct(RcontrolAttacksClean$utc, origin="1970-01-01"))
+
+
+#inspect
+head(RcontrolAttacksClean)
+
+#double check the time range
+min(RcontrolAttacksClean$day)
+max(RcontrolAttacksClean$day) 
+
+
+#take a look at at distribution in time to look for anomalies
+ggplot(RcontrolAttacksClean, aes(x=day))+geom_histogram(bins = 15)+
+  scale_x_date(date_breaks = "days" , date_labels = "%d.%m")+
+  geom_vline(xintercept = as.Date("2020-07-02"))+ theme_minimal(base_size = 8)
+
+
+#save file for further use
+write.csv(RcontrolAttacksClean,"RcontrolAttacksClean.csv")
+
+#________________________________
+#now, similar cleaning for the comments; will rbind with removing duplicates later on
+RcontrolComments <- as.data.frame(fread("Rcontrol_comments_final.txt",quote = ""))
+
+head(RcontrolComments)
+
[…]

### 2021-08-19 oldCleanup/RcontrolToFrequency.R

@@ -1,0 +1,254 @@
+library(dplyr)
+library(tidyverse)
+library(WRS2)
+
+#load list of sampled users with bots removed
+RcontrolList<- read.csv("RcontrolListNoBots.csv",header=TRUE)[,1]
+
+#load the dataset
+RcontrolAttacks <- read.csv("RcontrolAttacksClean.csv")
+
+#load the comments dataset
+RcontrolCommentsNoRepeats <- read.csv("RcontrolCommentsNoRepeats.csv")
+
+#rbind
+RcontrolAll <- rbind(RcontrolAttacks,RcontrolCommentsNoRepeats)
+
+head(RcontrolAll)
+nrow(RcontrolAll)
+
+#double check to remove duplicates by ID
+RcontrolUnique <- RcontrolAll %>% distinct(RcontrolAll$id, .keep_all=TRUE)
+
+head(RcontrolUnique)
+
+#now drop the additional id column
+RcontrolUnique <- RcontrolUnique[,-11]
+
+#check length and colnames
+nrow(RcontrolUnique)
+colnames(RcontrolUnique)
+
+#rename for brevity
+Rcontrol <- RcontrolUnique
+
+#inspect 
+head(Rcontrol)
+
+#now we tabulate attacks of two types by day and receiver [mind your head! this is for attacks received, you need to do something slighlty different if you want activity counts and if you split by weeks etc]
+#_____ counting received: rl - received low, rh - received high,  rpl - received to post low, rph  - received to post high
+
+RcontrolFreqL <- xtabs(low  ~ receiver + day, data = Rcontrol)
+RcontrolFreqH <- xtabs(high  ~ receiver + day, data = Rcontrol)
+RcontrolFreqPl <- xtabs(low * replyToPost  ~ receiver + day, data = Rcontrol)
+RcontrolFreqPh <- xtabs(high * replyToPost  ~ receiver + day, data = Rcontrol)
+RcontrolFreqA <- xtabs(~ author + day, data = Rcontrol)
+
+
+
+head(RcontrolFreqL)
+head(RcontrolFreqH)
+head(RcontrolFreqPl)
+head(RcontrolFreqPh)
+head(RcontrolFreqA)
+
+# add day numbers pated after attack type as colnames
+colnames(RcontrolFreqL) <- paste("l",1:15,sep="")
[…]

### 2021-08-23 paperDraft/paperDraft.Rmd
typos fixed, changes implemented suggested by Rafal, webpages bibliography changed

@@
 # Introduction
-Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys, it remains a common hindrance for people engaging with social media in their everyday lives.
-The situation got exacerbated amidst the COVID19 pandemic, during which a majority of our social life moved to cyberspace.
-During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content\footnote{\href {https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}}, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.
-According to a report conducted by company L1ght \footnote{\href {https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}}, hate speech directed towards China and the Chinese went up by 900% on Twitter.
-Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord.
+Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys \todo{refs}, it remains a common hindrance for people engaging with social media in their everyday lives.
+The problem got exacerbated in the midst of the COVID19 pandemic \todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace.
+During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content @grant_2021, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.} According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter.
+Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord \footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.
 
 But alongside the growing need for even more efficient and proactive moderation, the capacity to execute it did not go hand in hand, forcing companies and policymakers to rethink the current model of moderation processes and workforce.
-Due to the COVID19 restrictions including social distancing, a lot of those serving the role of moderators had to be sent home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}} without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA) among others.
+Due to the COVID19 restrictions including social distancing, a lot of those serving the role of moderators had to be sent home [@bhattacharya] without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA) among others.
 Curtailing the moderators' workforce was accompanied by more agency given to algorithms and AI-based moderation.
@@
 # Automated versus Human-based Moderation
-The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around technology performance (@macavaney2019hate, @schmidt2017survey).
-State-of-the-art solutions are mostly governed by statistical methods including deep learning and machine learning (@lecun2015deep, @sejnowski2020unreasonable, @jordan2015machine).
+The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around technology performance [@macavaney2019hate; @schmidt2017survey].
+State-of-the-art solutions are mostly governed by statistical methods including deep learning and machine learning [@lecun2015deep; @sejnowski2020unreasonable; @jordan2015machine].
 Their performance is inherently tied to the amount of data being fed to the system and the quality of its annotation.
-At different stages of the process, from datasets gathering and preparation, annotation to the training or algorithms themselves, biases seem to be omnipresent (@binns2017like, @geva2019we @mehrabi2021survey).
-Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love").
-Lack of generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic).
-As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, creations of models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
+\todo{This deserves a developed paragraph with examples}At different stages of the process, from data gathering and preparation, annotation to the training or algorithms themselves, biases seem to be omnipresent [@binns2017like, @geva2019we @mehrabi2021survey].
+
+\todo{This deserves a developed paragraph with examples}Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love").
+
+\todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic].
+As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
 This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public.
 Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike.
-First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
-Second, inability for successful identification of the sources of empirical gains (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
-Third, "mathiness" - the use obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
-Last but not least - misuse of language.
+First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second\todo{give an example}.
+Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect)\todo{give an example}.
+Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon\todo{Give an example}.
+Last but not least---misuse of language\todo{Give an example}.
 This includes suggestive definitions without proper explanation of what they mean in the context (e.g.
-inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g.
+inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g.
 consciousness).
@@
 Yet another obstacle in the process is the lack of gold standard in dataset creation and taxonomies of abusive language being used for instance in the process of annotating different datasets.
-Frequently people obtain data from various sources and do not follow any universally used instructions when it comes to its annotation, leading to discrepancies between various datasets being tagged within one domain (e.g.
+Frequently people obtain data from various sources and do not follow any universally used instructions when it comes to annotation, leading to discrepancies between various datasets being tagged within one domain (e.g.
 hate speech).
-Lack of expert annotators and proper annotation criteria and instructions are also widespread, with the common practice hiring untrained workers from Mechanical Turk or other crowdsourcing platforms.
+Lack of expert annotators and proper annotation criteria and instructions are also widespread, with the common practice of hiring untrained workers from Mechanical Turk or other crowdsourcing platforms.
 
-Although there are some initiatives developed in response, most notably, functional tests for Hate Speech Detection Models created by @rottger2020hatecheck, or the Online Safety Data Initiative (OSDI) LINK https://onlinesafetydata.blog.gov.uk/about-us/, focused on projects related to improving access to data, standardizing the description of online harms, as well as creating tools and benchmarks for evaluation of technologies focused on safety, much effort must be made before wider adoption of such solutions comes into force.
+Although there are some initiatives developed in response, most notably, functional tests for Hate Speech Detection Models created by @rottger2020hatecheck, or the Online Safety Data Initiative (OSDI) [@onlinesafetydata], focused on projects related to improving access to data, standardizing the description of online harms, as well as creating tools and benchmarks for evaluation of technologies focused on safety, much effort must be made before wider adoption of such solutions comes into force.
 
 At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms.
-On Facebook, there are more than 3B comments and likes daily (https://martech.org/facebook-3-2-billion-likes-comments-every-day/), 500M tweets are sent daily on Twitter (https://www.oberlo.com/blog/twitter-statistics), and over 2B comments made by users of Reddit in 2020 (https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/) which is almost 3M comments made daily.
+On Facebook, there are more than 3B comments and likes daily [@noauthor_facebook:_2012], 500M tweets are sent daily on Twitter [@noauthor_10_2021], and over 2B comments made by users of Reddit in 2020 [@noauthor_reddit_nodate] which is almost 3M comments made daily.
 With this amount of content, it's either impossible or extremely costly to scale the moderation workforce.
 One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being.
-Being submersed in the cyber-Augean stables takes a toll on many - as examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs.
+Being submersed in the cyber-Augean stables takes a toll on many---as examined by @roberts2014behind & @roberts2016commercial.
+Workers hired for such tasks are often low-status and low-wage, isolated and asked to keep what they've seen in secret under restrictive NDAs.
+This in turn makes the research in the area extremely difficult, since moderators are not allowed to talk about their work conditions or any other related subject.
+Those who decided to break the NDA are risking a penalty.
 Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases.
-This can lead to serious psychological damage, like depression, or PTSD (@roberts2014behind).
-Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job (https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health).
-Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.
+This can lead to serious psychological damage, such as depression, or PTSD [@roberts2014behind].
+Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job [@newton_facebook_2020].
+Taking into consideration that Facebook employs 15K moderators [@koetsier_report] and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.
 
@@
 Harmful messages can be either reported by the users of the platforms or automated methods and then sent for review to moderators.
-A set of actions can be then taken depending on the platform and their community guidelines - on the content or user level.
+A set of actions can be then taken depending on the platform and their community guidelines---on the content or user level.
 A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them.
@@
 The weakness of the reactive method is that the damage is done.
-Whoever is the recipient of the abusive message has the chance to see it and potentially suffer (@hoff2009cyberbullying, @keipi2016online, Wwachs2019associations).
+Whoever is the recipient of the abusive message has the chance to see it and potentially suffer [@hoff2009cyberbullying, @keipi2016online, @wachs2019associations].
 Yet another weakness connected with relying solely on human reports is the content that is harmful but unreported by a receipted or any bystander.
-Although the exact scale of unreported content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).
+Although the exact scale of unreported content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online [@noauthor_:game_nodate; @noauthor_free_nodate; @french_as_2021].
 
@@
 Pro-active moderation can be utilized using AI or other methods to promote socially positive engagement.
-Instead of or in the combination with punitive solutions like privileges restriction, one can induce empathy or community norms with counter-speech.
-Counter speech as described by Dangerous Speech Project (https://dangerousspeech.org/counterspeech/) is "any direct response to hateful or harmful speech which seeks to undermine it".
+Instead of or in the combination with punitive solutions such as privileges restriction, one can induce empathy or community norms with counter-speech.
+Counter speech as described by Dangerous Speech Project [@noauthor_counterspeech_2017] is "any direct response to hateful or harmful speech which seeks to undermine it".
 As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male).
@@
 Thus, we needed approximately 200 attacks daily generated by the treatment groups.
-2. Recruitment of users who regularly attack others was necessary to measure the effect of interventions at the end.
-3. Recruitment of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
-First, we spent 9 weeks for preliminary Reddit's monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring.
-As mentioned, sustained activity was crucial to minimize the risk users becoming inactive during the course of the study.
-Next, we have calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day - 1.94 attacks daily per person on average).
-Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per group).
+2. Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
+3. Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+First, we spent 9 weeks for preliminary monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring.
+As mentioned, sustained activity was crucial to minimize the risk of users becoming inactive during the course of the study.
+Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
+Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per intervention type).
 The rest (304 people) were selected as our control group.
-
-Three groups were formed - two treatment groups (195 people in each) and one control group (304 people).
-The first treatment group received counter-speech interventions based on normative influence, while the second one received interventions based on empathetic influence.
-Users in the control group did not receive any intervention.
+The first treatment group received normative counter-speech interventions, while the second one received empathetic interventions. Users in the control group did not receive any intervention.
 

### 2021-08-23 paperDraft/paperDraft.tex
typos fixed, changes implemented suggested by Rafal, webpages bibliography changed

@@
 verbal aggression and harassment online, looking at various reports and
-surveys, it remains a common hindrance for people engaging with social
-media in their everyday lives. The situation got exacerbated amidst the
-COVID19 pandemic, during which a majority of our social life moved to
-cyberspace. During this shift, there was an increase in cyberbullying
-attitudes and perpetration (Barlett, Simmers, Roth, \& Gentile (2021)),
-90\% increase in public reports of illegal online
-content\footnote{\href {https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}},
-including 114\% increase in non-consensual sharing of intimate images,
-30\% increase in cyberbullying, as well as 40\% of increase in adults
-reporting online harassment. According to a report conducted by company
-L1ght \textbackslash footnote\{\textbackslash href
-\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\{\url{https://l1ght.com/Toxicity_during_coronavirus_Report-L1ght.pdf}\}\},
-hate speech directed towards China and the Chinese went up by 900\% on
+surveys \todo{refs}, it remains a common hindrance for people engaging
+with social media in their everyday lives. The problem got exacerbated
+in the midst of the COVID19 pandemic \todo{is it less coloquial now?},
+during which a majority of our social life moved to cyberspace. During
+this shift, there was an increase in cyberbullying attitudes and
+perpetration (Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase
+in public reports of illegal online content Grant (2021), including
+114\% increase in non-consensual sharing of intimate images, 30\%
+increase in cyberbullying, as well as 40\% of increase in adults
+reporting online
+harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
+According to a report conducted by company L1ght (L1ght, 2020), hate
+speech directed towards China and the Chinese went up by 900\% on
 Twitter. Gaming platforms were in the spotlight as well, with a 40\%
-increase in toxicity on Discord.
+increase in toxicity on Discord
+\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.
 
@@
 social distancing, a lot of those serving the role of moderators had to
-be sent
-home\footnote{\href {https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}}
-without the ability to work remotely because of the constraints
-affiliated with restrictive non-disclosure agreements (NDA) among
-others. Curtailing the moderators' workforce was accompanied by more
-agency given to algorithms and AI-based moderation. Those changes, as
-argued by Gerrard (2020), can be seen as a serious red flag in terms of
-safety for all users on online platforms.
+be sent home (Bhattacharya, 2021) without the ability to work remotely
+because of the constraints affiliated with restrictive non-disclosure
+agreements (NDA) among others. Curtailing the moderators' workforce was
+accompanied by more agency given to algorithms and AI-based moderation.
+Those changes, as argued by Gerrard (2020), can be seen as a serious red
+flag in terms of safety for all users on online platforms.
 
@@
 the most critical discussions revolving around technology performance
-(MacAvaney et al. (2019), Schmidt \& Wiegand (2017)). State-of-the-art
+(MacAvaney et al., 2019; Schmidt \& Wiegand, 2017). State-of-the-art
 solutions are mostly governed by statistical methods including deep
-learning and machine learning (LeCun, Bengio, \& Hinton (2015),
-Sejnowski (2020), Jordan \& Mitchell (2015)). Their performance is
-inherently tied to the amount of data being fed to the system and the
-quality of its annotation. At different stages of the process, from
-datasets gathering and preparation, annotation to the training or
-algorithms themselves, biases seem to be omnipresent (Binns, Veale, Van
-Kleek, \& Shadbolt (2017), Geva, Goldberg, \& Berant (2019) Mehrabi,
-Morstatter, Saxena, Lerman, \& Galstyan (2021)). Users' of online
+learning and machine learning (Jordan \& Mitchell, 2015; LeCun, Bengio,
+\& Hinton, 2015; Sejnowski, 2020). Their performance is inherently tied
+to the amount of data being fed to the system and the quality of its
+annotation. \todo{This deserves a developed paragraph with examples}At
+different stages of the process, from data gathering and preparation,
+annotation to the training or algorithms themselves, biases seem to be
+omnipresent Mehrabi, Morstatter, Saxena, Lerman, \& Galstyan (2021).
+
+\todo{This deserves a developed paragraph with examples}Users' of online
 services are also creative in their strategies to circumvent automated
@@
 word-boundary changes (inserting or removing whitespace), or word
-appending (appending common or non-hateful words like ``love''). Lack of
-generalisability of the models - an ability to perform well on datasets
+appending (appending common or non-hateful words like ``love'').
+
+\todo{This deserves a developed paragraph with examples}Lack of
+generalisability of the models---an ability to perform well on datasets
 coming from sources other than the one used for training is a serious
-shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \& Gambäck
-(2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \& Weld
+shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
+2019; Yin \& Zubiaga, 2021). As shown by Wu, Ribeiro, Heer, \& Weld
 (2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
-(2020) in practice, creations of models often lacks thorough error
-analysis and legitimate experimental methodology, which can result in
-non-reproducibility. This is also connected with a potential lack of
+(2020) in practice, the development of such models often lacks thorough
+error analysis and legitimate experimental methodology, which can result
+in non-reproducibility. This is also connected with a potential lack of
 thorough understanding of the limitations of the models and spurious
@@
 the inability to draw a clear distinction between speculation and
-explanation, with the first one often being disguised as the second.
-Second, inability for successful identification of the sources of
-empirical gains (whether it was problem formulation, optimization of the
-heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
-another aspect). Third, ``mathiness'' - the use obscure language and
-often covering weak argumentation with the alluring but often apparent
-depth of technical jargon. Last but not least - misuse of language. This
-includes suggestive definitions without proper explanation of what they
-mean in the context (e.g.~inflating good performance in simple NLP tasks
-to human-level understanding), overloading the papers with technical
-terminology, or suitcase words (those words that can encompass a variety
-of meanings, e.g.~consciousness).
+explanation, with the first one often being disguised as the
+second\todo{give an example}. Second, the inability of successful
+identification of the sources of performance improvement (whether it was
+problem formulation, optimization of the heuristics, data-preprocessing,
+hyperparameter tuning, or perhaps yet another
+aspect)\todo{give an example}. Third, ``mathiness''---the use of obscure
+language and often covering weak argumentation with the alluring but
+often apparent depth of technical jargon\todo{Give an example}. Last but
+not least---misuse of language\todo{Give an example}. This includes
+suggestive definitions without proper explanation of what they mean in
+the context (e.g.~inflating good performance in simple NLP tasks to
+human-level understanding), overloading the papers with technical
+terminology, or suitcase words (words that can encompass a variety of
+meanings, e.g.~consciousness).
 
@@
 people obtain data from various sources and do not follow any
-universally used instructions when it comes to its annotation, leading
-to discrepancies between various datasets being tagged within one domain
+universally used instructions when it comes to annotation, leading to
+discrepancies between various datasets being tagged within one domain
 (e.g.~hate speech). Lack of expert annotators and proper annotation
 criteria and instructions are also widespread, with the common practice
-hiring untrained workers from Mechanical Turk or other crowdsourcing
+of hiring untrained workers from Mechanical Turk or other crowdsourcing
 platforms.
@@
 functional tests for Hate Speech Detection Models created by Röttger et
-al. (2020), or the Online Safety Data Initiative (OSDI) LINK
-\url{https://onlinesafetydata.blog.gov.uk/about-us/}, focused on
-projects related to improving access to data, standardizing the
-description of online harms, as well as creating tools and benchmarks
-for evaluation of technologies focused on safety, much effort must be
-made before wider adoption of such solutions comes into force.
+al. (2020), or the Online Safety Data Initiative (OSDI) (\emph{About the
+Online Safety Data Initiative}, n.d.), focused on projects related to
+improving access to data, standardizing the description of online harms,
+as well as creating tools and benchmarks for evaluation of technologies
+focused on safety, much effort must be made before wider adoption of
+such solutions comes into force.
 
@@
 Facebook, there are more than 3B comments and likes daily
-(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
-500M tweets are sent daily on Twitter
-(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
-comments made by users of Reddit in 2020
-(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
-which is almost 3M comments made daily. With this amount of content,
-it's either impossible or extremely costly to scale the moderation
-workforce. One can also have doubts about the ethical aspects of hiring
-workers who are often unaware of how this kind of task will affect their
-well-being. Being submersed in the cyber-Augean stables takes a toll on
-many - as examined by Roberts (2014) \& Roberts (2016), workers who are
-hired for such tasks are often low-status and low-wage, isolated, and
-asked to keep what they've seen in secret under restrictive NDAs.
-Screening through the reported user-generated content is connected with
-exposure to violent and deeply disturbing materials, with child
-pornography, murders, or suicides as examples of the most extreme cases.
-This can lead to serious psychological damage, like depression, or PTSD
-(Roberts (2014)). Some of the employees filed a lawsuit against Facebook
-and as a result, the company agreed to pay \$52M in compensation for
-mental health issues developed during the job
-(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
-Taking into consideration that Facebook employs 15K moderators
-(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
-and most likely more are needed to keep up with the growing amount of
-content, with the parallel considerations about the negative effects of
-content moderation on mental health, a collaboration between humans and
-machines in this area seems inevitable.
+({``Facebook,''} 2012), 500M tweets are sent daily on Twitter (\emph{10
+{Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in 2021
+{[}{Infographic}{]}}, 2021), and over 2B comments made by users of
+Reddit in 2020 ({``Reddit in 2020,''} 2020) which is almost 3M comments
+made daily. With this amount of content, it's either impossible or
+extremely costly to scale the moderation workforce. One can also have
+doubts about the ethical aspects of hiring workers who are often unaware
+of how this kind of task will affect their well-being. Being submersed
+in the cyber-Augean stables takes a toll on many---as examined by
+Roberts (2014) \& Roberts (2016). Workers hired for such tasks are often
+low-status and low-wage, isolated and asked to keep what they've seen in
+secret under restrictive NDAs. This in turn makes the research in the
+area extremely difficult, since moderators are not allowed to talk about
+their work conditions or any other related subject. Those who decided to
+break the NDA are risking a penalty. Screening through the reported
+user-generated content is connected with exposure to violent and deeply
+disturbing materials, with child pornography, murders, or suicides as
+examples of the most extreme cases. This can lead to serious
+psychological damage, such as depression, or PTSD (Roberts, 2014). Some
+of the employees filed a lawsuit against Facebook and as a result, the
+company agreed to pay \$52M in compensation for mental health issues
+developed during the job (Newton, 2020). Taking into consideration that
+Facebook employs 15K moderators (Koetsier, 2020) and most likely more
+are needed to keep up with the growing amount of content, with the
+parallel considerations about the negative effects of content moderation
+on mental health, a collaboration between humans and machines in this
+area seems inevitable.
 
@@
 sent for review to moderators. A set of actions can be then taken
-depending on the platform and their community guidelines - on the
+depending on the platform and their community guidelines---on the
 content or user level. A harmful message can be deleted, made invisible
@@
 the recipient of the abusive message has the chance to see it and
-potentially suffer (Hoff \& Mitchell (2009), Keipi, Näsi, Oksanen, \&
-Räsänen (2016), Wwachs2019associations). Yet another weakness connected
+potentially suffer Wachs et al. (2019). Yet another weakness connected
 with relying solely on human reports is the content that is harmful but
@@
 lot of children, teens, or even adults do not report cyberbullying or
-harassment online (LINKS:
-\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
-; \url{https://www.adl.org/free-to-play-2020} ;
-\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).
+harassment online ({``Free to {Play}?''} 2020; French, 2021; {``In,''}
+2017).
 
@@
 promote socially positive engagement. Instead of or in the combination
-with punitive solutions like privileges restriction, one can induce
+with punitive solutions such as privileges restriction, one can induce
 empathy or community norms with counter-speech. Counter speech as
-described by Dangerous Speech Project
-(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
-response to hateful or harmful speech which seeks to undermine it.'' As
-examined by Munger (2017), counter-speech can be effective in the
-reduction of racist tweets (although only in the condition in which a
-white male with high followers was approaching another white male). In a
-study conducted by Bilewicz et al. (2021), a bot disguised as a Reddit
-user, equipped with normative and empathetic interventions,
-significantly decreased the amount of personal attacks generated on
-Reddit. In yet another study by Miškolci, Kováčová, \& Rigová (2020),
-this technique was not effective in changing the behavior of the users
-(counter-speech here aimed at reducing the prejudice against Roma
-minority in Slovakia), but encouraged bystanders to express pro-Roma
-comments on specific Facebook posts. Counter-speech also has been shown
-to have the potential to increase civility online in studies conducted
-by Friess, Ziegele, \& Heinbach (2021), Molina \& Jennings (2018), Han,
-Brazeal, \& Pennington (2018). \ldots{}
+described by Dangerous Speech Project ({``Counterspeech {{}} {Dangerous}
+{Speech} {Project},''} 2017) is ``any direct response to hateful or
+harmful speech which seeks to undermine it.'' As examined by Munger
+(2017), counter-speech can be effective in the reduction of racist
+tweets (although only in the condition in which a white male with high
+followers was approaching another white male). In a study conducted by
+Bilewicz et al. (2021), a bot disguised as a Reddit user, equipped with
+normative and empathetic interventions, significantly decreased the
+amount of personal attacks generated on Reddit. In yet another study by
+Miškolci, Kováčová, \& Rigová (2020), this technique was not effective
+in changing the behavior of the users (counter-speech here aimed at
+reducing the prejudice against Roma minority in Slovakia), but
+encouraged bystanders to express pro-Roma comments on specific Facebook
+posts. Counter-speech also has been shown to have the potential to
+increase civility online in studies conducted by Friess, Ziegele, \&
+Heinbach (2021), Molina \& Jennings (2018), Han, Brazeal, \& Pennington
+(2018). \ldots{}
 
@@
 needed approximately 200 attacks daily generated by the treatment
-groups. 2. Recruitment of users who regularly attack others was
+groups. 2. Identification of users who regularly attack others was
 necessary to measure the effect of interventions at the end. 3.
-Recruitment of users who were active during the whole preliminary
+Identification of users who were active during the whole preliminary
 monitoring period was necessary to minimize the risk of attrition during
-the study. First, we spent 9 weeks for preliminary Reddit's monitoring
-period to recruit only those users who generate at least one personal
-attack per week and were active during the whole period of the
-monitoring. As mentioned, sustained activity was crucial to minimize the
-risk users becoming inactive during the course of the study. Next, we
-have calculated the daily average number of personal attacks generated
-by the group who met the above criteria (which resulted in 357 attacks
-per day - 1.94 attacks daily per person on average). Knowing that we
-need around 200 attacks daily (just enough so our volunteers can keep up
-with the volume) we have randomly selected 390 people for our study
-groups (195 per group). The rest (304 people) were selected as our
-control group.
-
-Three groups were formed - two treatment groups (195 people in each) and
-one control group (304 people). The first treatment group received
-counter-speech interventions based on normative influence, while the
-second one received interventions based on empathetic influence. Users
-in the control group did not receive any intervention.
+the study. First, we spent 9 weeks for preliminary monitoring period to
+recruit only those users who generate at least one personal attack per
+week and were active during the whole period of the monitoring. As
+mentioned, sustained activity was crucial to minimize the risk of users
+becoming inactive during the course of the study. Next, we calculated
+the daily average number of personal attacks generated by the group who
+met the above criteria (which resulted in 357 attacks per day, 1.94
+attacks daily per person on average). Knowing that we need around 200
+attacks daily (just enough so our volunteers can keep up with the
+volume) we have randomly selected 390 people for our study groups (195
+per intervention type). The rest (304 people) were selected as our
+control group. The first treatment group received normative
+counter-speech interventions, while the second one received empathetic
+interventions. Users in the control group did not receive any
+intervention.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-noauthor_10_2021}{}%
+\emph{10 {Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in
+2021 {[}{Infographic}{]}}. (2021). Retrieved from
+\url{https://www.oberlo.com/blog/twitter-statistics}
+
+\leavevmode\hypertarget{ref-onlinesafetydata}{}%
+\emph{About the online safety data initiative}. (n.d.).
+
 \leavevmode\hypertarget{ref-barlett2021comparing}{}%
@@
 COVID-19 pandemic. \emph{The Journal of Social Psychology}, 1--11.
+
+\leavevmode\hypertarget{ref-bhattacharya}{}%
+Bhattacharya, A. (2021). How {Covid}-19 lockdowns weakened {Facebook}'s
+content moderation algorithms. Retrieved from
+\url{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}
 
@@
 405--415. Springer.
+
+\leavevmode\hypertarget{ref-noauthor_counterspeech_2017}{}%
+Counterspeech {{}} {Dangerous} {Speech} {Project}. (2017). Retrieved
+from \url{https://dangerousspeech.org/counterspeech/}
+
+\leavevmode\hypertarget{ref-noauthor_facebook:_2012}{}%
+Facebook: 3.2 {Billion} {Likes} \& {Comments} {Every} {Day}. (2012).
+Retrieved from
+\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}
+
+\leavevmode\hypertarget{ref-noauthor_free_nodate}{}%
+Free to {Play}? {Hate}, {Harassment} and {Positive} {Social}
+{Experience} in {Online} {Games} 2020. (2020). Retrieved from
+\url{https://www.adl.org/free-to-play-2020}
+
+\leavevmode\hypertarget{ref-french_as_2021}{}%
+French, C. (2021). As the pandemic forces us online, {LGBTQ2S}+ teens
+deal with cyberbullying. Retrieved from
+\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
 
@@
 
+\leavevmode\hypertarget{ref-grant_2021}{}%
+Grant, J. (2021). Australia's eSafety commissioner targets abuse online
+as covid-19 supercharges cyberbullying \textbar{} the strategist.
+Retrieved from
+\url{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}
+
 \leavevmode\hypertarget{ref-grondahl2018all}{}%
@@
 
+\leavevmode\hypertarget{ref-noauthor_:game_nodate}{}%
+In:{Game} {Abuse}. (2017). Retrieved from
+\url{https://www.ditchthelabel.org/research-papers/ingame-abuse/}
+
 \leavevmode\hypertarget{ref-jordan2015machine}{}%
@@
 Francis.
+
+\leavevmode\hypertarget{ref-koetsier_report}{}%
+Koetsier, J. (2020). Report: {Facebook} {Makes} 300,000 {Content}
+{Moderation} {Mistakes} {Every} {Day}. Retrieved from
+\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/}
+
+\leavevmode\hypertarget{ref-noauthor_l1ght_2020}{}%
+L1ght. (2020). L1ght releases groundbreaking report on corona-related
+hate speech and online toxicity. Retrieved from
+\url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}
 
@@
 
+\leavevmode\hypertarget{ref-newton_facebook_2020}{}%
+Newton, C. (2020). Facebook will pay \$52 million in settlement with
+moderators who developed {PTSD} on the job. Retrieved from
+\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}
+
+\leavevmode\hypertarget{ref-noauthor_reddit_nodate}{}%
+Reddit in 2020. (2020). Retrieved from
+\url{https://www.reddit.com/r/blog/comments/k967mm/reddit_in_2020/}
+
 \leavevmode\hypertarget{ref-roberts2014behind}{}%
@@
 
+\leavevmode\hypertarget{ref-wachs2019associations}{}%
+Wachs, S., Wright, M. F., Sittichai, R., Singh, R., Biswal, R., Kim, E.,
+\ldots{} others. (2019). Associations between witnessing and
+perpetrating online hate in eight countries: The buffering effects of
+problem-focused coping. \emph{International Journal of Environmental
+Research and Public Health}, \emph{16}(20), 3992.
+
 \leavevmode\hypertarget{ref-wu2019errudite}{}%

### 2021-08-24 paperDraft/paperDraft.Rmd
User identification process described in detail

@@
 We formed treatment and control groups based on three main criteria:
-1.
-During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+ \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
 Thus, we needed approximately 200 attacks daily generated by the treatment groups.
-2. Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
-3. Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
-First, we spent 9 weeks for preliminary monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring.
-As mentioned, sustained activity was crucial to minimize the risk of users becoming inactive during the course of the study.
-Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
-Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per intervention type).
-The rest (304 people) were selected as our control group.
-The first treatment group received normative counter-speech interventions, while the second one received empathetic interventions. Users in the control group did not receive any intervention.
+\item Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
+\item Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+ \end{enumerate}
+
+User identification process:
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
+   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
+This resulted in the identification of 93966 users.
+   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
+This resulted in the removal of 388 users, thus 93578 were left on our list.
+   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
+As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
+This step resulted in the removal of users below the third quartile (Q3).
+20124 users were left in our group.
+   \item Moving forward, we removed users who generated less than 14 comments in given week.
+We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
+This resulted in the removal of 2192 users, so 17932 were left.
+   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
+This means inclusion in the sample above the 1st quartile.
+4422 users were removed, leaving us with a group of 13510.
+   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
+During this period we have monitored the activity of the identified group of 13510 users and applied the next selection criteria to make sure we select the regularly active and attacking users.
+   \item The period of monitoring was divided into weeks.
+We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
+Thus, we have taken into consideration only 6 full weeks for the period.
+   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
+First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criteria led to only 255 users left, which was not enough for the study.
+Less restrictive criteria (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
+   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
+   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
+The rest was delegated as a control group (304 users).
+
+ \end{enumerate}
 

### 2021-08-24 paperDraft/paperDraft.tex
User identification process described in detail

@@
 popular Q\&A and news forum, Reddit (www.reddit.com). We formed
-treatment and control groups based on three main criteria: 1. During the
-intervention period, we have expected to have 20 active volunteers at
-any given time, each willing to conduct 10 interventions daily. Thus, we
-needed approximately 200 attacks daily generated by the treatment
-groups. 2. Identification of users who regularly attack others was
-necessary to measure the effect of interventions at the end. 3.
-Identification of users who were active during the whole preliminary
-monitoring period was necessary to minimize the risk of attrition during
-the study. First, we spent 9 weeks for preliminary monitoring period to
-recruit only those users who generate at least one personal attack per
-week and were active during the whole period of the monitoring. As
-mentioned, sustained activity was crucial to minimize the risk of users
-becoming inactive during the course of the study. Next, we calculated
-the daily average number of personal attacks generated by the group who
-met the above criteria (which resulted in 357 attacks per day, 1.94
-attacks daily per person on average). Knowing that we need around 200
-attacks daily (just enough so our volunteers can keep up with the
-volume) we have randomly selected 390 people for our study groups (195
-per intervention type). The rest (304 people) were selected as our
-control group. The first treatment group received normative
-counter-speech interventions, while the second one received empathetic
-interventions. Users in the control group did not receive any
-intervention.
+treatment and control groups based on three main criteria:
+\renewcommand{\labelenumii}{\Roman{enumii}}
+
+\begin{enumerate}
+ \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
+Thus, we needed approximately 200 attacks daily generated by the treatment groups.
+\item Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
+\item Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+ \end{enumerate}
+
+User identification process:
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
+   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
+This resulted in the identification of 93966 users.
+   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
+This resulted in the removal of 388 users, thus 93578 were left on our list.
+   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
+As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
+This step resulted in the removal of users below the third quartile (Q3).
+20124 users were left in our group.
+   \item Moving forward, we removed users who generated less than 14 comments in given week.
+We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
+This resulted in the removal of 2192 users, so 17932 were left.
+   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
+This means inclusion in the sample above the 1st quartile.
+4422 users were removed, leaving us with a group of 13510.
+   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
+During this period we have monitored the activity of the identified group of 13510 users and applied the next selection criteria to make sure we select the regularly active and attacking users.
+   \item The period of monitoring was divided into weeks.
+We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
+Thus, we have taken into consideration only 6 full weeks for the period.
+   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
+First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criteria led to only 255 users left, which was not enough for the study.
+Less restrictive criteria (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
+   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
+   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
+The rest was delegated as a control group (304 users).
+
+ \end{enumerate}
 

### 2021-08-25 paperDraft/paperDraft.Rmd
theoretical intro improved

@@
 # Introduction
-Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys \todo{refs}, it remains a common hindrance for people engaging with social media in their everyday lives.
-The problem got exacerbated in the midst of the COVID19 pandemic \todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace.
+Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives.
+The problem got exacerbated in the midst of the COVID19 pandemic\todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace.
 During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content @grant_2021, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.} According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter.
@@
 \todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic].
+
 As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
 This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public.
-Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike.
-First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second\todo{give an example}.
-Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect)\todo{give an example}.
-Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon\todo{Give an example}.
+Specifically, @lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike.
+First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
+For instance, in a paper from 2017 [@steinhardt2017certified], Jacob Steinhardt, the author of @lipton2019troubling, admitted to stating that “the high dimensionality and abundance of irrelevant features...
+give the attacker more room to construct attacks” - although no experiments were conducted to measure what is the effect of dimensionality of the neural network on its attackability.
+Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
+As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stemed from hyperparameter tuning [@melis2017state].
+As mentioned by @lipton2019troubling, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
+Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
+Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with irrelevant theorem to amplify the empirical results.
+They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm---the main subject of a paper.
 Last but not least---misuse of language\todo{Give an example}.
@@
 inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g.
-consciousness).
+consciousness)
 
@@
 This can lead to serious psychological damage, such as depression, or PTSD [@roberts2014behind].
+Although there are certain initiatives being developed or introduced to reduce the emotional impact of the moderation, like stylistic alterations to a content (applying grayscale or blurring to images) [@karunakaran2019testing], workplace wellness programs, clinical support, or psychological training [@steiger2021psychological], none of the methods can eliminate the psychological distress completely.
 Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job [@newton_facebook_2020].
+Also as described by @parks2019dirty, the work is often performed under time pressure, reviewing 25K pieces of content per day.
+Spending on average three to five seconds on each image reported for moderation might not lead to the most thoughtful decisions and as shown @stepanikova2012racial, high time pressure can amplify human biases.
 Taking into consideration that Facebook employs 15K moderators [@koetsier_report] and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.
@@
 # Collective Intelligence Approach to Counter-speech
+Traditionally collective intelligence has been defined as "a group or a team’s combined capacity and capability to perform a wide variety of tasks and solve diverse problems" [@noauthor_collective_nodate].
+In our paper and in the theoretical underpinnings of the experiment itself, we will be relying on a collective intelligence scope proposed by Nesta, an innovation foundation (https://www.nesta.org.uk), which focuses on a collaboration between human and machine intelligence to develop innovative solutions to social challenges.
+(Gdzieś stopka(?): Samurai Labs has been one of the 15 recipients of the second round of collective intelligence grants awarded by Nesta: https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/)
+
+The main objective of the experiment was to test whether the level of verbal aggression (personal attacks) of a group of users' regularly attacking others on Reddit can be significantly decreased by community-driven, counter-speech interventions conducted by volunteers in partnership with Artificial Intelligence.
+Instead of using negative motivation system, the assumption was to test a positive one - convincing vrbally violent users to refrain from using cyberviolence based on peer-pressure regulation and experiential learning of a positive set of norms and empathy.
+Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its' members.
+Volunteers, after receiving a notification on Slack (perhaps say more about those processes and infrastructure), could then react with the proper intervention.
+Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence - utilizing human + machine intelligence.
+
+In the end, what we were able to compare was the following: the effectiveness of the existing Reddit moderation system (predominantly grounded in a punitive authoritarian paradigm) versus the existing moderation system combined with collective intelligence - Artificial Intelligence supported with a crowd of volunteers - who introduced the element of  positive peer-pressure.
 

### 2021-08-25 paperDraft/paperDraft.tex
theoretical intro improved

@@
 verbal aggression and harassment online, looking at various reports and
-surveys \todo{refs}, it remains a common hindrance for people engaging
-with social media in their everyday lives. The problem got exacerbated
-in the midst of the COVID19 pandemic \todo{is it less coloquial now?},
-during which a majority of our social life moved to cyberspace. During
-this shift, there was an increase in cyberbullying attitudes and
-perpetration (Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase
-in public reports of illegal online content Grant (2021), including
-114\% increase in non-consensual sharing of intimate images, 30\%
-increase in cyberbullying, as well as 40\% of increase in adults
-reporting online
+surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
+Vogels, 2021), it remains a common hindrance for people engaging with
+social media in their everyday lives. The problem got exacerbated in the
+midst of the COVID19 pandemic\todo{is it less coloquial now?}, during
+which a majority of our social life moved to cyberspace. During this
+shift, there was an increase in cyberbullying attitudes and perpetration
+(Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase in public
+reports of illegal online content Grant (2021), including 114\% increase
+in non-consensual sharing of intimate images, 30\% increase in
+cyberbullying, as well as 40\% of increase in adults reporting online
 harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
@@
 shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
-2019; Yin \& Zubiaga, 2021). As shown by Wu, Ribeiro, Heer, \& Weld
-(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
-(2020) in practice, the development of such models often lacks thorough
-error analysis and legitimate experimental methodology, which can result
-in non-reproducibility. This is also connected with a potential lack of
+2019; Yin \& Zubiaga, 2021).
+
+As shown by Wu, Ribeiro, Heer, \& Weld (2019), Lipton \& Steinhardt
+(2019), and Musgrave, Belongie, \& Lim (2020) in practice, the
+development of such models often lacks thorough error analysis and
+legitimate experimental methodology, which can result in
+non-reproducibility. This is also connected with a potential lack of
 thorough understanding of the limitations of the models and spurious
-conclusions being made to a wider public. Specifically, @Lipton \&
+conclusions being made to a wider public. Specifically, Lipton \&
 Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
@@
 the inability to draw a clear distinction between speculation and
-explanation, with the first one often being disguised as the
-second\todo{give an example}. Second, the inability of successful
-identification of the sources of performance improvement (whether it was
-problem formulation, optimization of the heuristics, data-preprocessing,
-hyperparameter tuning, or perhaps yet another
-aspect)\todo{give an example}. Third, ``mathiness''---the use of obscure
-language and often covering weak argumentation with the alluring but
-often apparent depth of technical jargon\todo{Give an example}. Last but
-not least---misuse of language\todo{Give an example}. This includes
+explanation, with the first one often being disguised as the second. For
+instance, in a paper from 2017 (Steinhardt, Koh, \& Liang, 2017), Jacob
+Steinhardt, the author of Lipton \& Steinhardt (2019), admitted to
+stating that ``the high dimensionality and abundance of irrelevant
+features\ldots{} give the attacker more room to construct attacks'' -
+although no experiments were conducted to measure what is the effect of
+dimensionality of the neural network on its attackability. Second, the
+inability of successful identification of the sources of performance
+improvement (whether it was problem formulation, optimization of the
+heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
+another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil
+Blunsom, some improvements in language modeling which originally were
+ascribed to complex innovations in the architecture of the network,
+stemed from hyperparameter tuning (Melis, Dyer, \& Blunsom, 2017). As
+mentioned by Lipton \& Steinhardt (2019), there is a tremendous value
+coming from the thorough understanding of a particular method, and a
+variety of techniques are vital in the process (like ablation,
+robustness checks, qualitative error analysis) for the benefit of the
+whole community. Third, ``mathiness''---the use of obscure language and
+often covering weak argumentation with the alluring but often apparent
+depth of technical jargon. Again Jacob Steinhardt admitted infusing his
+2015 paper co-authored with Percy Liang (Steinhardt \& Liang, 2015) with
+irrelevant theorem to amplify the empirical results. They discussed
+``staged strong Doeblin chains'' which actually had limited pertinence
+to the learning algorithm---the main subject of a paper. Last but not
+least---misuse of language\todo{Give an example}. This includes
 suggestive definitions without proper explanation of what they mean in
@@
 terminology, or suitcase words (words that can encompass a variety of
-meanings, e.g.~consciousness).
+meanings, e.g.~consciousness)
 
@@
 examples of the most extreme cases. This can lead to serious
-psychological damage, such as depression, or PTSD (Roberts, 2014). Some
-of the employees filed a lawsuit against Facebook and as a result, the
-company agreed to pay \$52M in compensation for mental health issues
-developed during the job (Newton, 2020). Taking into consideration that
-Facebook employs 15K moderators (Koetsier, 2020) and most likely more
-are needed to keep up with the growing amount of content, with the
-parallel considerations about the negative effects of content moderation
-on mental health, a collaboration between humans and machines in this
-area seems inevitable.
+psychological damage, such as depression, or PTSD (Roberts, 2014).
+Although there are certain initiatives being developed or introduced to
+reduce the emotional impact of the moderation, like stylistic
+alterations to a content (applying grayscale or blurring to images)
+(Karunakaran \& Ramakrishan, 2019), workplace wellness programs,
+clinical support, or psychological training (Steiger, Bharucha,
+Venkatagiri, Riedl, \& Lease, 2021), none of the methods can eliminate
+the psychological distress completely. Some of the employees filed a
+lawsuit against Facebook and as a result, the company agreed to pay
+\$52M in compensation for mental health issues developed during the job
+(Newton, 2020). Also as described by Parks (2019), the work is often
+performed under time pressure, reviewing 25K pieces of content per day.
+Spending on average three to five seconds on each image reported for
+moderation might not lead to the most thoughtful decisions and as shown
+Stepanikova (2012), high time pressure can amplify human biases. Taking
+into consideration that Facebook employs 15K moderators (Koetsier, 2020)
+and most likely more are needed to keep up with the growing amount of
+content, with the parallel considerations about the negative effects of
+content moderation on mental health, a collaboration between humans and
+machines in this area seems inevitable.
 
@@
 Counter-speech}\label{collective-intelligence-approach-to-counter-speech}}
+
+Traditionally collective intelligence has been defined as ``a group or a
+team's combined capacity and capability to perform a wide variety of
+tasks and solve diverse problems'' ({``Collective {Intelligence},''}
+n.d.). In our paper and in the theoretical underpinnings of the
+experiment itself, we will be relying on a collective intelligence scope
+proposed by Nesta, an innovation foundation
+(\url{https://www.nesta.org.uk}), which focuses on a collaboration
+between human and machine intelligence to develop innovative solutions
+to social challenges. (Gdzieś stopka(?): Samurai Labs has been one of
+the 15 recipients of the second round of collective intelligence grants
+awarded by Nesta:
+\url{https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/})
+
+The main objective of the experiment was to test whether the level of
+verbal aggression (personal attacks) of a group of users' regularly
+attacking others on Reddit can be significantly decreased by
+community-driven, counter-speech interventions conducted by volunteers
+in partnership with Artificial Intelligence. Instead of using negative
+motivation system, the assumption was to test a positive one -
+convincing vrbally violent users to refrain from using cyberviolence
+based on peer-pressure regulation and experiential learning of a
+positive set of norms and empathy. Algorithms developed for the
+detection of personal attacks were used to monitor the activity of
+experimental groups and notify volunteers about all attacks generated by
+its' members. Volunteers, after receiving a notification on Slack
+(perhaps say more about those processes and infrastructure), could then
+react with the proper intervention. Such an approach served as a
+distributed bottom-up voluntary model of moderation based on collective
+intelligence - utilizing human + machine intelligence.
+
+In the end, what we were able to compare was the following: the
+effectiveness of the existing Reddit moderation system (predominantly
+grounded in a punitive authoritarian paradigm) versus the existing
+moderation system combined with collective intelligence - Artificial
+Intelligence supported with a crowd of volunteers - who introduced the
+element of positive peer-pressure.
 
@@
 
+\leavevmode\hypertarget{ref-noauthor_collective_nodate}{}%
+Collective {Intelligence}. (n.d.). Retrieved from
+\url{https://www.oxford-review.com/oxford-review-encyclopaedia-terms/collective-intelligence/}
+
 \leavevmode\hypertarget{ref-noauthor_counterspeech_2017}{}%
@@
 
+\leavevmode\hypertarget{ref-karunakaran2019testing}{}%
+Karunakaran, S., \& Ramakrishan, R. (2019). Testing stylistic
+interventions to reduce emotional impact of content moderation workers.
+\emph{Proceedings of the AAAI Conference on Human Computation and
+Crowdsourcing}, \emph{7}, 50--58.
+
 \leavevmode\hypertarget{ref-keipi2016online}{}%
@@
 \url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}
+
+\leavevmode\hypertarget{ref-Zachary_hate}{}%
+Laub, Z. (2019). Hate {Speech} on {Social} {Media}: {Global}
+{Comparisons}. Retrieved from
+\url{https://www.cfr.org/backgrounder/hate-speech-social-media-global-comparisons}
 
@@
 Computing Surveys (CSUR)}, \emph{54}(6), 1--35.
+
+\leavevmode\hypertarget{ref-melis2017state}{}%
+Melis, G., Dyer, C., \& Blunsom, P. (2017). On the state of the art of
+evaluation in neural language models. \emph{arXiv Preprint
+arXiv:1707.05589}.
 
@@
 \url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}
+
+\leavevmode\hypertarget{ref-parks2019dirty}{}%
+Parks, L. (2019). Dirty data: Content moderation, regulatory
+outsourcing, and the cleaners. \emph{Film Quarterly}, \emph{73}(1),
+11--18.
 
@@
 
+\leavevmode\hypertarget{ref-sorrentino2019epidemiology}{}%
+Sorrentino, A., Baldry, A. C., Farrington, D. P., \& Blaya, C. (2019).
+Epidemiology of cyberbullying across europe: Differences between
+countries and genders. \emph{Educational Sciences: Theory \& Practice},
+\emph{19}(2).
+
+\leavevmode\hypertarget{ref-steiger2021psychological}{}%
+Steiger, M., Bharucha, T. J., Venkatagiri, S., Riedl, M. J., \& Lease,
+M. (2021). The psychological well-being of content moderators.
+\emph{Proceedings of the 2021 CHI Conference on Human Factors in
+Computing Systems, CHI}, \emph{21}.
+
+\leavevmode\hypertarget{ref-steinhardt2017certified}{}%
+Steinhardt, J., Koh, P. W., \& Liang, P. (2017). Certified defenses for
+data poisoning attacks. \emph{Proceedings of the 31st International
+Conference on Neural Information Processing Systems}, 3520--3532.
+
+\leavevmode\hypertarget{ref-steinhardt2015learning}{}%
+Steinhardt, J., \& Liang, P. (2015). Learning fast-mixing models for
+structured prediction. \emph{International Conference on Machine
+Learning}, 1063--1072. PMLR.
+
+\leavevmode\hypertarget{ref-stepanikova2012racial}{}%
+Stepanikova, I. (2012). Racial-ethnic biases, time pressure, and medical
+decisions. \emph{Journal of Health and Social Behavior}, \emph{53}(3),
+329--343.
+
 \leavevmode\hypertarget{ref-swamy2019studying}{}%
@@
 Language Learning (CoNLL)}, 940--950.
+
+\leavevmode\hypertarget{ref-vogels_state_2021}{}%
+Vogels, E. A. (2021). The {State} of {Online} {Harassment}. Retrieved
+from
+\url{https://www.pewresearch.org/internet/2021/01/13/the-state-of-online-harassment/}
 

### 2021-08-26 oldCleanup/cuttingBeforeAfter.R
note on cutting dates

@@ -1,0 +1,36 @@
+
+
+user1 <- c(0,0, 0, 1, 0, 1, 0, 0, 0)
+user2 <- c(0,0, 0, 0,  1, 1, 1, 0, 0)
+
+
+users <- list(user1, user2)
+
+starts <- numeric(length(users))
+ends <- numeric(length(users))
+for(i in 1: length(users)){
+starts[i] <- min(which(users[[i]] !=0 ))-2
+ends[i] <-  max(which(users[[i]] !=0 ))+2
+}
+
+starts
+ends
+
+cleanedUsers <- list()
+for(i in 1: length(users)){
+cleanedUsers[[i]] <- users[[i]][starts[i]:ends[i]]
+}
+
+
+cleanedUsers
+
+usersDF <- do.call("rbind", cleanedUsers)
+
+
+usersDF
+
+
+
+
+
+

### 2021-08-27 paperDraft/paperDraft.Rmd
typos fixed, some minor changes proposed by Rafal made

@@
 # Section Abstract
-This article describes an experimental intervention study based in a naturalistic, digital setting (Q&A forum - Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
+This article describes an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
 Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
@@
 Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives.
-The problem got exacerbated in the midst of the COVID19 pandemic\todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace.
-During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content @grant_2021, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.} According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter.
-Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord \footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.
+The problem got exacerbated in the midst of the COVID19 pandemic, during which the majority of our social life moved to cyberspace.
+During this shift, there was an increase in cyberbullying attitudes and perpetration [@barlett2021comparing], 90% increase in public reports of illegal online content [@grant_2021], including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.
+According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter.
+Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord \footnote{In both reports, the increase is reported as a relative change between the year 2019 and 2020, with no absolute indicators.}.
 
@@
 
-\todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic].
+\todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---the ability to perform well on datasets coming from sources other than the one used for training---is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic].
 
 As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
-This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public.
+This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being announced to a wider public.
 Specifically, @lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike.
-First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+\item First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
 For instance, in a paper from 2017 [@steinhardt2017certified], Jacob Steinhardt, the author of @lipton2019troubling, admitted to stating that “the high dimensionality and abundance of irrelevant features...
 give the attacker more room to construct attacks” - although no experiments were conducted to measure what is the effect of dimensionality of the neural network on its attackability.
-Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
-As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stemed from hyperparameter tuning [@melis2017state].
+\item Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
+As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stem from hyperparameter tuning [@melis2017state].
 As mentioned by @lipton2019troubling, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
-Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
-Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with irrelevant theorem to amplify the empirical results.
+\item Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
+Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with an irrelevant theorem to amplify the empirical results.
 They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm---the main subject of a paper.
-Last but not least---misuse of language\todo{Give an example}.
+\item Last but not least---misuse of language\todo{Give an example}.
 This includes suggestive definitions without proper explanation of what they mean in the context (e.g.
@@
 consciousness)
+ \end{enumerate}
 
@@
 A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them.
-Depending on the type and amount of infraction, a particular user can be warned, muted or shadowbanned, or banned from further participation in the community for a period of time.
+Depending on the type and amount of infraction, a particular user can be warned, muted, shadowbanned, or banned from further participation in the community for a period of time.
 The weakness of the reactive method is that the damage is done.
@@
 The main objective of the experiment was to test whether the level of verbal aggression (personal attacks) of a group of users' regularly attacking others on Reddit can be significantly decreased by community-driven, counter-speech interventions conducted by volunteers in partnership with Artificial Intelligence.
-Instead of using negative motivation system, the assumption was to test a positive one - convincing vrbally violent users to refrain from using cyberviolence based on peer-pressure regulation and experiential learning of a positive set of norms and empathy.
+Instead of using negative motivation system, the assumption was to test a positive one - convincing verbally violent users to refrain from using cyberviolence based on peer-pressure regulation and experiential learning of a positive set of norms and empathy.
 Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its' members.
-Volunteers, after receiving a notification on Slack (perhaps say more about those processes and infrastructure), could then react with the proper intervention.
-Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence - utilizing human + machine intelligence.
+Volunteers, after receiving a notification on Slack, could then react with a proper intervention.
+Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence---utilizing human + machine intelligence.
 
-In the end, what we were able to compare was the following: the effectiveness of the existing Reddit moderation system (predominantly grounded in a punitive authoritarian paradigm) versus the existing moderation system combined with collective intelligence - Artificial Intelligence supported with a crowd of volunteers - who introduced the element of  positive peer-pressure.
-
-# Experimental Design and data collection
-This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
-We formed treatment and control groups based on three main criteria:
-\renewcommand{\labelenumii}{\Roman{enumii}}
- \begin{enumerate}
- \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
-Thus, we needed approximately 200 attacks daily generated by the treatment groups.
-\item Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
-\item Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
- \end{enumerate}
-
-User identification process:
-\renewcommand{\labelenumii}{\Roman{enumii}}
- \begin{enumerate}
-   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
-   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
-This resulted in the identification of 93966 users.
-   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
-This resulted in the removal of 388 users, thus 93578 were left on our list.
-   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
-As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
-This step resulted in the removal of users below the third quartile (Q3).
-20124 users were left in our group.
-   \item Moving forward, we removed users who generated less than 14 comments in given week.
-We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
-This resulted in the removal of 2192 users, so 17932 were left.
-   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
-This means inclusion in the sample above the 1st quartile.
-4422 users were removed, leaving us with a group of 13510.
-   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
-During this period we have monitored the activity of the identified group of 13510 users and applied the next selection criteria to make sure we select the regularly active and attacking users.
-   \item The period of monitoring was divided into weeks.
-We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
-Thus, we have taken into consideration only 6 full weeks for the period.
-   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
-First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criteria led to only 255 users left, which was not enough for the study.
-Less restrictive criteria (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
-   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
-   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
-The rest was delegated as a control group (304 users).
-
- \end{enumerate}
-
-The duration of the experiment, 6 months, was divided into three 2-months periods.
-The first two months served as a monitoring period to properly select groups and establish baselines.
-The next 2 months served as treatment period, during which groups received counter-speech comments from volunteers, in response to personal attacks detected by the Artificial Intelligence-based system.
-The last 2-months served as the post-treatment monitoring period to gather the data needed to evaluate the effectiveness of interventions.
+In the end, what we were able to compare was the following: the effectiveness of the existing Reddit moderation system (predominantly grounded in a punitive authoritarian paradigm) versus the existing moderation system combined with collective intelligence---Artificial Intelligence supported with a crowd of volunteers---who introduced the element of  positive peer-pressure.
 
@@
 
+# Experimental Design and data collection
+This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
+We formed treatment and control groups based on three main criteria:
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+ \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
+Thus, we needed approximately 200 attacks daily generated by the treatment groups.
+\item The identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
+\item The identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+ \end{enumerate}
+
+User identification process:
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
+   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
+This resulted in the identification of 93966 users.
+   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
+This resulted in the removal of 388 users, thus 93578 were left on our list.
+   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
+As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
+This step resulted in the removal of users below the third quartile (Q3).
+20124 users were left in our group.
+   \item Moving forward, we removed users who generated less than 14 comments in this week.
+We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
+This resulted in the removal of 2192 users, so 17932 were left.
+   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
+This means the inclusion in the sample of users above the 1st quartile.
+4422 users were removed, leaving us with a group of 13510.
+   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
+During this period we have monitored the activity of the identified group of 13510 users and applied further selection criteria to make sure we select those who were regularly active and attacked other users.
+   \item The period of monitoring was divided into weeks.
+We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
+Thus, we have taken into consideration only 6 full weeks for the period.
+   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
+First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criterion led to only 255 users left, which was not enough for the study.
+The less restrictive criterion (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
+   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
+   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
+The rest was delegated as a control group (304 users).
+
+ \end{enumerate}
+
+The duration of the experiment, 6 months, was divided into three 2-months periods.
+The first two months served as a monitoring period to properly select groups and establish baselines.
+The next 2 months served as treatment period, during which groups received counter-speech comments from volunteers, in response to personal attacks detected by the Artificial Intelligence-based system.
+The last 2-months served as the post-treatment monitoring period to gather the data needed to evaluate the effectiveness of interventions.
+
 # Results

### 2021-08-27 paperDraft/paperDraft.tex
typos fixed, some minor changes proposed by Rafal made

@@
 
-This article describes an experimental intervention study based in a
-naturalistic, digital setting (Q\&A forum - Reddit), utilizing a
+This article describes an experimental intervention study conducted in a
+naturalistic, digital setting (Q\&A forum on Reddit), utilizing a
 collective intelligence approach to content moderation and reduction of
@@
 social media in their everyday lives. The problem got exacerbated in the
-midst of the COVID19 pandemic\todo{is it less coloquial now?}, during
-which a majority of our social life moved to cyberspace. During this
-shift, there was an increase in cyberbullying attitudes and perpetration
-(Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase in public
-reports of illegal online content Grant (2021), including 114\% increase
-in non-consensual sharing of intimate images, 30\% increase in
-cyberbullying, as well as 40\% of increase in adults reporting online
-harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
-According to a report conducted by company L1ght (L1ght, 2020), hate
-speech directed towards China and the Chinese went up by 900\% on
-Twitter. Gaming platforms were in the spotlight as well, with a 40\%
-increase in toxicity on Discord
-\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.
+midst of the COVID19 pandemic, during which the majority of our social
+life moved to cyberspace. During this shift, there was an increase in
+cyberbullying attitudes and perpetration (Barlett, Simmers, Roth, \&
+Gentile, 2021), 90\% increase in public reports of illegal online
+content (Grant, 2021), including 114\% increase in non-consensual
+sharing of intimate images, 30\% increase in cyberbullying, as well as
+40\% of increase in adults reporting online harassment. According to a
+report conducted by company L1ght (L1ght, 2020), hate speech directed
+towards China and the Chinese went up by 900\% on Twitter. Gaming
+platforms were in the spotlight as well, with a 40\% increase in
+toxicity on Discord
+\footnote{In both reports, the increase is reported as a relative change between the year 2019 and 2020, with no absolute indicators.}.
 
@@
 \todo{This deserves a developed paragraph with examples}Lack of
-generalisability of the models---an ability to perform well on datasets
-coming from sources other than the one used for training is a serious
+generalisability of the models---the ability to perform well on datasets
+coming from sources other than the one used for training---is a serious
 shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
@@
 thorough understanding of the limitations of the models and spurious
-conclusions being made to a wider public. Specifically, Lipton \&
+conclusions being announced to a wider public. Specifically, Lipton \&
 Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
-the current research paradigm in the industry and academia alike. First,
-the inability to draw a clear distinction between speculation and
-explanation, with the first one often being disguised as the second. For
-instance, in a paper from 2017 (Steinhardt, Koh, \& Liang, 2017), Jacob
-Steinhardt, the author of Lipton \& Steinhardt (2019), admitted to
-stating that ``the high dimensionality and abundance of irrelevant
-features\ldots{} give the attacker more room to construct attacks'' -
-although no experiments were conducted to measure what is the effect of
-dimensionality of the neural network on its attackability. Second, the
-inability of successful identification of the sources of performance
-improvement (whether it was problem formulation, optimization of the
-heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
-another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil
-Blunsom, some improvements in language modeling which originally were
-ascribed to complex innovations in the architecture of the network,
-stemed from hyperparameter tuning (Melis, Dyer, \& Blunsom, 2017). As
-mentioned by Lipton \& Steinhardt (2019), there is a tremendous value
-coming from the thorough understanding of a particular method, and a
-variety of techniques are vital in the process (like ablation,
-robustness checks, qualitative error analysis) for the benefit of the
-whole community. Third, ``mathiness''---the use of obscure language and
-often covering weak argumentation with the alluring but often apparent
-depth of technical jargon. Again Jacob Steinhardt admitted infusing his
-2015 paper co-authored with Percy Liang (Steinhardt \& Liang, 2015) with
-irrelevant theorem to amplify the empirical results. They discussed
-``staged strong Doeblin chains'' which actually had limited pertinence
-to the learning algorithm---the main subject of a paper. Last but not
-least---misuse of language\todo{Give an example}. This includes
-suggestive definitions without proper explanation of what they mean in
-the context (e.g.~inflating good performance in simple NLP tasks to
-human-level understanding), overloading the papers with technical
-terminology, or suitcase words (words that can encompass a variety of
-meanings, e.g.~consciousness)
+the current research paradigm in the industry and academia alike.
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+\item First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second.
+For instance, in a paper from 2017 [@steinhardt2017certified], Jacob Steinhardt, the author of @lipton2019troubling, admitted to stating that “the high dimensionality and abundance of irrelevant features...
+give the attacker more room to construct attacks” - although no experiments were conducted to measure what is the effect of dimensionality of the neural network on its attackability.
+\item Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
+As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stem from hyperparameter tuning [@melis2017state].
+As mentioned by @lipton2019troubling, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
+\item Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
+Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with an irrelevant theorem to amplify the empirical results.
+They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm---the main subject of a paper.
+\item Last but not least---misuse of language\todo{Give an example}.
+This includes suggestive definitions without proper explanation of what they mean in the context (e.g.
+inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g.
+consciousness)
+ \end{enumerate}
 
@@
 to censor them. Depending on the type and amount of infraction, a
-particular user can be warned, muted or shadowbanned, or banned from
+particular user can be warned, muted, shadowbanned, or banned from
 further participation in the community for a period of time. The
@@
 motivation system, the assumption was to test a positive one -
-convincing vrbally violent users to refrain from using cyberviolence
+convincing verbally violent users to refrain from using cyberviolence
 based on peer-pressure regulation and experiential learning of a
@@
 experimental groups and notify volunteers about all attacks generated by
-its' members. Volunteers, after receiving a notification on Slack
-(perhaps say more about those processes and infrastructure), could then
-react with the proper intervention. Such an approach served as a
+its' members. Volunteers, after receiving a notification on Slack, could
+then react with a proper intervention. Such an approach served as a
 distributed bottom-up voluntary model of moderation based on collective
-intelligence - utilizing human + machine intelligence.
+intelligence---utilizing human + machine intelligence.
 
@@
 grounded in a punitive authoritarian paradigm) versus the existing
-moderation system combined with collective intelligence - Artificial
-Intelligence supported with a crowd of volunteers - who introduced the
+moderation system combined with collective intelligence---Artificial
+Intelligence supported with a crowd of volunteers---who introduced the
 element of positive peer-pressure.
-
-\hypertarget{experimental-design-and-data-collection}{%
-\section{Experimental Design and data
-collection}\label{experimental-design-and-data-collection}}
-
-This was a 6-months field experiment in a digital setting conducted on a
-popular Q\&A and news forum, Reddit (www.reddit.com). We formed
-treatment and control groups based on three main criteria:
-\renewcommand{\labelenumii}{\Roman{enumii}}
-
-\begin{enumerate}
- \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
-Thus, we needed approximately 200 attacks daily generated by the treatment groups.
-\item Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
-\item Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
- \end{enumerate}
-
-User identification process:
-
-\renewcommand{\labelenumii}{\Roman{enumii}}
- \begin{enumerate}
-   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
-   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
-This resulted in the identification of 93966 users.
-   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
-This resulted in the removal of 388 users, thus 93578 were left on our list.
-   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
-As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
-This step resulted in the removal of users below the third quartile (Q3).
-20124 users were left in our group.
-   \item Moving forward, we removed users who generated less than 14 comments in given week.
-We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
-This resulted in the removal of 2192 users, so 17932 were left.
-   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
-This means inclusion in the sample above the 1st quartile.
-4422 users were removed, leaving us with a group of 13510.
-   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
-During this period we have monitored the activity of the identified group of 13510 users and applied the next selection criteria to make sure we select the regularly active and attacking users.
-   \item The period of monitoring was divided into weeks.
-We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
-Thus, we have taken into consideration only 6 full weeks for the period.
-   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
-First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criteria led to only 255 users left, which was not enough for the study.
-Less restrictive criteria (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
-   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
-   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
-The rest was delegated as a control group (304 users).
-
- \end{enumerate}
-
-The duration of the experiment, 6 months, was divided into three
-2-months periods. The first two months served as a monitoring period to
-properly select groups and establish baselines. The next 2 months served
-as treatment period, during which groups received counter-speech
-comments from volunteers, in response to personal attacks detected by
-the Artificial Intelligence-based system. The last 2-months served as
-the post-treatment monitoring period to gather the data needed to
-evaluate the effectiveness of interventions.
 
@@
 empathy-based ones.
+
+\hypertarget{experimental-design-and-data-collection}{%
+\section{Experimental Design and data
+collection}\label{experimental-design-and-data-collection}}
+
+This was a 6-months field experiment in a digital setting conducted on a
+popular Q\&A and news forum, Reddit (www.reddit.com). We formed
+treatment and control groups based on three main criteria:
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+ \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily.
+Thus, we needed approximately 200 attacks daily generated by the treatment groups.
+\item The identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
+\item The identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+ \end{enumerate}
+
+User identification process:
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
+   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe.
+This resulted in the identification of 93966 users.
+   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
+This resulted in the removal of 388 users, thus 93578 were left on our list.
+   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice).
+As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions.
+This step resulted in the removal of users below the third quartile (Q3).
+20124 users were left in our group.
+   \item Moving forward, we removed users who generated less than 14 comments in this week.
+We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)).
+This resulted in the removal of 2192 users, so 17932 were left.
+   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
+This means the inclusion in the sample of users above the 1st quartile.
+4422 users were removed, leaving us with a group of 13510.
+   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks).
+During this period we have monitored the activity of the identified group of 13510 users and applied further selection criteria to make sure we select those who were regularly active and attacked other users.
+   \item The period of monitoring was divided into weeks.
+We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data).
+Thus, we have taken into consideration only 6 full weeks for the period.
+   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified.
+First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criterion led to only 255 users left, which was not enough for the study.
+The less restrictive criterion (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
+   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
+   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
+The rest was delegated as a control group (304 users).
+
+ \end{enumerate}
+
+The duration of the experiment, 6 months, was divided into three
+2-months periods. The first two months served as a monitoring period to
+properly select groups and establish baselines. The next 2 months served
+as treatment period, during which groups received counter-speech
+comments from volunteers, in response to personal attacks detected by
+the Artificial Intelligence-based system. The last 2-months served as
+the post-treatment monitoring period to gather the data needed to
+evaluate the effectiveness of interventions.
 
@@
 
-\leavevmode\hypertarget{ref-melis2017state}{}%
-Melis, G., Dyer, C., \& Blunsom, P. (2017). On the state of the art of
-evaluation in neural language models. \emph{arXiv Preprint
-arXiv:1707.05589}.
-
 \leavevmode\hypertarget{ref-mivskolci2020countering}{}%
@@
 
-\leavevmode\hypertarget{ref-steinhardt2017certified}{}%
-Steinhardt, J., Koh, P. W., \& Liang, P. (2017). Certified defenses for
-data poisoning attacks. \emph{Proceedings of the 31st International
-Conference on Neural Information Processing Systems}, 3520--3532.
-
-\leavevmode\hypertarget{ref-steinhardt2015learning}{}%
-Steinhardt, J., \& Liang, P. (2015). Learning fast-mixing models for
-structured prediction. \emph{International Conference on Machine
-Learning}, 1063--1072. PMLR.
-
 \leavevmode\hypertarget{ref-stepanikova2012racial}{}%

### 2021-08-30 bayesianAnalysis/causalThinking.R
added causal thinking and priors

@@ -1,0 +1,95 @@
+library(dagitty)
+library(rethinking)
+#A: activity
+#H: hate
+#I: intervention
+
+#B, D, A: before, during, after
+#T, C: type, count
+
+
+large <- dagitty("
+    dag{
+    AB -> AD -> AA
+    AB -> HB -> HD -> HA
+    AD -> HD
+    AA -> HA
+    IT -> HD
+    IT -> AD
+    IT -> AA
+    IT -> HA
+    IC -> HD
+    IC -> AD
+    IC -> AA
+    IC -> HA
+    } 
+  ")
+
+
+
+drawdag(large)
+
+
+adjustmentSets(large, exposure = c("IC", "IT"), outcome = "HA")
+
+adjustmentSets(large, exposure = c("IC", "IT"), outcome = "HA", effect = "direct")
+
+
+
+impliedConditionalIndependencies(large)
+
+
+
+small <- dagitty("
+    dag{
+    AB ->  AA
+    AB -> HB -> HA
+    AA -> HA
+    I -> AA
+    I -> HA
+    } 
+  ")
+
+drawdag(small)
+
+adjustmentSets(small, exposure = c("I"), outcome = "HA")
+
+
+adjustmentSets(small, exposure = c("I"), outcome = "HA", effect = "direct")
+
+
+
+
+impliedConditionalIndependencies(large)
+
+
+hidden <- dagitty("
+    dag{
+    UA [unobserved]
+    UH [unobserved]
+    AB ->  HB
+    AA -> HA
+    I -> AA
+    I -> HA
+    UA -> AB
+    UA -> AA
+    UH -> HB
+    UH -> HA
+    } 
+  ")
+
+
+drawdag(hidden)
+
+adjustmentSets(hidden, exposure = c("I"), outcome = "HA", effect = "total")
+adjustmentSets(hidden, exposure = c("I"), outcome = "HA", effect = "direct")
+
+
+
+impliedConditionalIndependencies(hidden)
+
+
+paths(hidden, from = "I", to = "HA", limit = 100)
+
+
+

### 2021-08-30 bayesianAnalysis/priorsSelection.R

@@ -1,0 +1,32 @@
+library(ggpubr)
+library(ggplot2)
+library(ggthemes)
+
+
+sim <- seq(0,400,by = 1)
+p <- ggplot(data = data.frame(count = sim), 
+            mapping = aes(x = count))+theme_tufte()
+
+
+
+priorHA <-  function(x) dcauchy(x,1,22)
+p + stat_function(fun = priorHA)+xlim(c(0,20))+ggtitle("Prior for hate after")
+
+priorHB <-  function(x) dcauchy(x,1,22)
+p + stat_function(fun = priorHA)+xlim(c(0,20))+ggtitle("Prior for hate before")
+
+
+priorAB <- function(x) dcauchy(x,23,22)
+p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
+
+priorAB <- function(x) dnorm(x,23,30)
+p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
+
+priorAA <- function(x) dcauchy(x,23,22)
+p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
+
+priorAA <- function(x) dnorm(x,23,30)
+p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
+
+
+

### 2021-09-02 bayesianAnalysis/bayesianChapterClean.Rmd
started bayesian analysis, ignore datasets

---
title: "A bayesian method of cosine-based word2vec bias"
author: "Alicja Dobrzeniecka and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: true
    df_print: kable 
    keep_tex: true
    includes:
      in_header:
        - Rafal_latex6.sty
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: LP-SEP-FINAL6.bib
csl: apa-5th-edition.csl
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')
```

We start with loading the libraries needed for the analysis.

\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
library(ggplot2)
library(ggthemes)
library(rethinking)
library(tidyverse)
library(ggpubr)
library(kableExtra)
library(dplyr)
library(ggExtra)
library(cowplot)
```
\normalsize

# Walkthrough with the religion dataset

We will use the choice of protected words and stereotypical predicates used in REF. This is a decent point of departure,  not only we want to compare our method to that of REF, but also because this data format is fairly general (as contrasted, say, with a set up for binary stereotypes). Note also that the method we develop here  can fairly easily be  run  for different stereotypization patterns.  Let's start  with  explaining the method and its deployment using a dataset obtained for the religion-related protected words.

Let's load, clean a bit and inspect the head of the religion dataset we prepared.  In order to obtain this  dataset, we  calculated the cosine distance between each protected word and each word from both the bias-related attribute groups, which were used in the original study, and to neutral and human control attributes which we added  as control groups.  For instance, for religion, the bias-related predicates (coming from the original study in REF) include muslim bias attributes, jew bias attributes, christian bias attributes (see a list in the APPENDIX).

We decided to add control groups in the form of two classes --- neutral words and human-related words. Without a proper control group it is quite hard to compare the resulting cosine distances and decide on their significance in bias detection. We prepared approximately 300\todo{FIX later} more or less neutral words to double-check the prima-facie neutral hypothesis that their cosine similarity to the protected words will oscillate around 0 (that is, the distances will be around 1). This provides us with a  more reliable point of reference. Moreover, we added human attributes that are associated with people in general to investigate  whether the smaller cosine distance between protected words and stereotypes can result  simply from the fact that the stereotype predicates  are associated with humans. For two control groups, we have randomly drawn 300 words that do not express any property usually attributed to humans, and human attributes. \todo{describe once the words are selected}

<!-- In other words, we took each protected word and in nested iteration calculated all of the cosine distances between the word and all available harmful stereotypes, neutral words, and human ones, which resulted with approximately 333 cosine distances per each protected word. -->

\vspace{1mm}
\footnotesize

```{r religionTableHead,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religion <- read.csv("cosineAnalysis/datasets/religionReddit.csv")[-1]
colnames(religion) <- c("protectedWord","wordToCompare","wordClass",
                        "cosineDistance","cosineSimilarity","connection")
levels(religion$wordClass) <- c("christian","human","jewish","muslim","neutral")
head(religion)  %>%  kable(format = "latex",booktabs=T,
                      linesep = "",  escape = FALSE, 
                      caption = "Head of the religion dataset.") %>%
                      kable_styling(latex_options=c("scale_down"))
```
\normalsize

 The `protectedWord` column contains words from a protected class that (in a perfect world according to the assumptions of the orignal study) should not be associated with  harmful stereotypes. `wordToCompare` contains attributes, including stereotypes and control group words. For each row we compute the cosine distances between a given protected  word and a given attribute word. `wordClass` tells us  which class an attribute is supposed to be stereotypically associated with, that is, whether the  word from `wordToCompare` is associated stereotypically with jews, christians or muslims, or whether it belongs to a control group. `cosineDistance` is simply a calculation of the cosine distance between protected word and atrribute.  `cosineSimilarity`  contains the result of substracting cosine distance from 1. `connection` contains information about  the relation type between a protected word and an attribute. If the attribute is e.g. a harmful jewish stereotype and the protected word is also from the judaism group,  the connection has value `associated`.  If the attribute is still stereotypically jewish, but the protected word comes from another religion, the connection is labelled as  `different`. If the attribute belongs to  a neutral group then the connection is labelled as `none` and if an attribute belongs to the `human` class, then the connection is labelled as `human`.

First let's take a look at the empirical distribution of distances by the connection type, initially ignoring the human control class for now.

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religionNoHumans <- religion[religion$connection !="human",]

ggplot(religionNoHumans, aes(x =  cosineDistance, fill = connection, color = connection ))+geom_density(alpha=0.6,size = .2)+theme_tufte()+ggtitle("Empirical distribution of cosine distances (religion), no human attributes.")+ scale_fill_manual(values = c("orangered4","chartreuse4","gray"))+scale_x_continuous(breaks = seq(0.3,1.5, by = 0.1))+xlab("cosine distance")+ scale_color_manual(values = c("orangered4","chartreuse4","gray"))
```
\normalsize

The first impression is that while  there is a  shift for  associated words towards smaller cosine distances as compared to the neutral words, slightly surprisingly a slightly weaker shift in the same direction is visible for attributes associated with different stereotypes. Moreover,  the empirical distributions overlap to alarge extent and the  means grouped by connection type do not seem too far from each other. In fact, as there is a lot of  variety in the consine distances (as we will soon see), abd we need to gauge the uncertaintly involved, and  to look more carefully at individual protected words to get a better idea of how the cosine distance distribution changes for different attribute groups and different protected classes.   Now, let's add the human attributes to the picture:

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
ggplot(religion, aes(x =  cosineDistance, fill = connection, color = connection))+geom_density(alpha=0.6,size = .2)+theme_tufte()+ggtitle("Empirical distribution of cosine distances (religion)")+ scale_fill_manual(values = c("orangered4","chartreuse4", "skyblue", "gray"))+scale_x_continuous(breaks = seq(0.3,1.5, by = 0.1))+xlab("cosine distance")+ scale_color_manual(values = c("orangered4","chartreuse4","skyblue","gray"))
```
\normalsize

\noindent Notice that the distribution for `human` (even though we did our best not to include in it any stereotype-related atributes) is left-skewed, with much overlap with `associated` and `different`, which illustrates the need to take being associated with humans as an important predictor.

Our focus lies in  `connection` as a predictor. Morever, later on we'll be interested in looking at the protected words separately, and at protected words split by connection. For technical reasons it is useful to represent these factors as integer vectors.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religion$con <- as.integer(religion$connection)
religion$pw <- as.integer(religion$protectedWord)
religion$pwFactor <- factor(paste0(religion$protectedWord, religion$connection))
religion$pwIndex <- as.integer(religion$pwFactor)
```
\normalsize

<!-- For technical reasons it is useful to represent an $n$-level factor with $n-1$ binary vectors. `connection` in this case has four levels. -->

<!-- \vspace{1mm} -->
<!-- \footnotesize -->
<!-- ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} -->
<!-- religion$associated <- ifelse(religion$connection == "associated", 1, 0) -->
<!-- religion$different <- ifelse(religion$connection == "different", 1, 0) -->
<!-- religion$human <- ifelse(religion$connection == "human" |religion$connection == "associated"| -->
<!--                            religion$connection == "different", 1, 0)   -->
<!-- ```   -->
<!-- \normalsize -->

A short script, `cleanDataset` to make this faster, so equivalently:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
source("cosineAnalysis/functions/cleanDataset.R")
religion <- read.csv("cosineAnalysis/datasets/religionReddit.csv")[-1]
religion <- cleanDataset(religion,c("christian","human","jewish","muslim","neutral"))
```
\normalsize

For now, let's focus on five protected words related to islam ("imam","islam","mosque","muslim", and "quran"). The word list associates with islam  four stereotypical attributes ("violent", "terrorist", "uneducated" and "dirty").  First, we select and plot the empirical distributions for these protected words.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message =FALSE, warning = FALSE}
library(tidyverse)
muslimWords <- c("imam","islam","mosque","muslim","quran")
muslim <- religion %>% filter(protectedWord %in% muslimWords)
ggplot(muslim, aes(x =  cosineDistance, fill = connection, color = connection))+
  geom_density(alpha=0.6,size = .2)+ 
  scale_fill_manual(values = c("orangered4","chartreuse4", "skyblue", "gray"))+
  scale_x_continuous(breaks = seq(0.3,1.5, by = 0.1))+xlab("cosine distance")+
  scale_color_manual(values = c("orangered4","chartreuse4","skyblue","gray"))+
  theme_tufte()+ggtitle("Empirical distribution of distances (muslim)")
```
\normalsize

\noindent Once we focus on words related to islam, the associated bias seems to be stronger than in the whole dataset.  This is a  step towards illustrating that the distribution of bias is uneven.

Now, say we want to look at a single protected word. Since the dataset also contains comparison multiple control neutral and  human attributes, we randomly select only 5 from `none` and 5 from `human` control groups of those for the visualisation purposes.

\vspace{1mm}
\footnotesize
```{r tableMuslimActive,echo=TRUE,eval=TRUE,fig.align = "center",cache=FALSE, fig.show = "hold", out.width = "100%"}
library(tidyverse)
muslimClass <- muslim %>% filter(protectedWord == "muslim")
neutralSample <- sample_n(filter(muslimClass,connection == "none"), 5)
humanSample <- sample_n(filter(muslimClass,connection == "human"), 5)
muslimVis <- muslimClass %>% filter(connection != "none" & connection !="human")
muslimVis <- rbind(muslimVis,neutralSample,humanSample)

#we plug in our visualisation script
source("cosineAnalysis/functions/visualisationTools.R")
#two arguments: dataset and protected word
visualiseProtected(muslimVis,"muslim")
```
\normalsize

Note that the distance between the grey point and the other points is proportional to cosine distance, the non-grey point size is proportional to cosine similarity to the protected word, and color groups by the connection type.  So for `muslim` it seems that the stereotypes coming from the word list are fairly well visible. To give you some taste of how uneven the dataset is, compare this to what happens with `priest`.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
library(tidyverse)
priestClass <- religion %>% filter(protectedWord == "priest")
neutralSample <- sample_n(filter(priestClass,connection == "none"), 5)
humanSample <- sample_n(filter(priestClass,connection == "human"), 5)
priestVis <- priestClass %>% filter(connection != "none" & connection !="human")
priestVis <- rbind(priestVis,neutralSample,humanSample)

#we plug in our visualisation script
source("cosineAnalysis/functions/visualisationTools.R")
#two arguments: dataset and protected word
visualiseProtected(priestVis,"priest")
```
\normalsize

\noindent Here you can see that some human attributes are closer than stereotype attributes, and that there is no clear reason to claim that `associated` attributes are closer than `different`  or `human` attributes. This, again, illustrates the need of case-by-case analysis with  control groups.

The general idea now is that the word lists provided in different pieces of research are just samples of attributes associates with various stereotypes and should be treated as such: the uncertaintly involved and the sample sizes should have clear impact on our estimates.

We will now think of cosine distance as the output variable, and 
will build a few bayesian models to compare. First, we just build a baseline model which estimates cosine distance to the attributes separately for each protected word. The underlying idea is that different protected words migh in general have different relations to all the attributes and this relations should be our point of departure.

Here is the intution behind the mathematical Bayesian model involved. Our outcome variable is `cosine difference`, which we take to me normally distributed around the predicted mean for a given protected word (that is, we assume the residuals are normally distributed). The simplest  model specification is:

\begin{align}
cosineDistance_i  & \sim dnorm(\mu_i, \sigma) \\
\mu_i & = m_{pw} \\
m_{pw} & ~ dnorm(1,.5) \\
\sigma &\sim  dcauchy(0,1)
\end{align}

That is, we assume the estimated means might be different for diferent protected words and our prior for the mean and the overal standard deviation are normal with mean 1 and sd=.5 and half-cauchy with parameters `0,1`. Further on we'll also estimate additional impact the connection type may have. For this impact we take a slightly skeptical prior centered around 0 distributed normally with sd = 1. These are fairly weak and slightly skeptical regularizing priors, which can be illustrated as follows:

\vspace{2mm}

```{r priorsVis,echo=FALSE,eval=TRUE,fig.align = "center",cache=FALSE, fig.show = "hold", out.width = "100%", fig.caption = "Regularizing priors for the bayesian models."}
library(ggpubr)
sim <- seq(-1,1,by = 0.001)
dis <- 1-sim

p <- ggplot(data = data.frame(distance = dis), 
            mapping = aes(x = distance))+theme_tufte()

none <- function(x) dnorm(x,1,.5)
cau <- function(x) dcauchy(x,0,1)
par <- function(x) dnorm(x,0,1)

noneG <- p + stat_function(fun = none)+xlim(c(-0.5,2.5))+ggtitle("Prior for mean distances")
parG <- p + stat_function(fun = par)+xlim(c(-2,2))+xlab("distance change")+ggtitle("Prior for coefficients")
cauG <- p + stat_function(fun = cau)+xlim(c(0,2))+ggtitle("Prior for standard deviation")+xlab("distance change")
ggarrange(noneG,cauG, parG, ncol = 1)
```

Now we can define and compile the baseline model. Its  parameters will have a posterior distribution obtained using either Hamiltionian Monte Carlo methods (STAN) available through the `rethinking` package.

\vspace{1mm}
\footnotesize
```{r religionBaseline,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
library(rethinking)
options(buildtools.check = function(action) TRUE )
religionBaseline <- ulam(
  alist(
    cosineDistance ~ dnorm(mu,sigma),
    mu <- m[pw],
    m[pw] ~ dnorm(1,.5),
    sigma ~ dcauchy(0,1)
  ),
  data = religion,
  chains=2 , iter=4000 , warmup=1000,
  start= list(mu = 1, co = 0, sigma= .3),
  log_lik = TRUE, cores=4
)
saveRDS(religionBaseline, file = "cosineAnalysis/models/religionBaseline.rds")
```
\normalsize

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religionBaseline <- readRDS(file = "cosineAnalysis/models/religionBaseline.rds")
```
\normalsize

The only reason we need it is the evaluation of connection as a predictor. Does including it in o the model improve the situation? To investigate this, let's now build a model according to the following specification:

\begin{align}
cosineDistance_i  & \sim dnorm(\mu_i, \sigma) \\
\mu_i & = m_{pw} + co_{con}\\
m_{pw} & ~ dnorm(1,.5) \\
co_{con} & ~ dnorm(0,1) \\
\sigma &\sim  dcauchy(0,1)
\end{align}

\noindent The idea now is that each connection type comes with its own coefficient $co$ that has impact on mean distances for protected words taken separately.

\vspace{1mm}
\footnotesize
```{r Coefsmodel,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
library(rethinking)
options(buildtools.check = function(action) TRUE )
religionCoefs <- ulam(
  alist(
    cosineDistance ~ dnorm(mu,sigma),
    mu <- m[pw] + co[con],
    m[pw] ~ dnorm(1,.5),
    co[con] ~dnorm(0,.5),
    sigma ~ dcauchy(0,1)
  ),
  data = religion,
  chains=2 , iter=8000 , warmup=1000, 
  log_lik = TRUE
)
```
\normalsize

\vspace{1mm}
\footnotesize
```{r load religionCoefs,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
#getwd()
religionCoefs <- readRDS("cosineAnalysis/models/religionCoefs.rds")
```
\normalsize

\noindent First, let's see if this model is really better in terms of the Widely Acceptable Information Criterion (WAIC):

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
compareBaseline <- print(round(compare(religionBaseline, religionCoefs)), 3)
saveRDS(compareBaseline, "cosineAnalysis/calculations/compareBaseline.rds")
compareBaseline <- readRDS("cosineAnalysis/calculations/compareBaseline.rds")
compareBaseline
```
\normalsize

Clearly, it should be given weight 1 as compared to the baseline model. So far, we've learned that the connection type actually has predictive value. Let's take a look at the coefficient estimates:

 \vspace{1mm}
 \footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
precisCoefs <- print(precis(religionCoefs, depth =2, pars= "co" ))
saveRDS(precisCoefs, "cosineAnalysis/calculations/precisCoefs.rds")
precisCoefs <- readRDS("cosineAnalysis/calculations/precisCoefs.rds")
precisCoefs
```
 \normalsize

\noindent Let's plot them together with their highest posterior density invervals, for the three topic groups.

\begin{center}
\begin{figure}[!htb]\centering
   \begin{minipage}{0.48\textwidth}
  \includegraphics[width=8cm]{../cosineAnalysis/images/religionCoeffs.jpeg}
   \end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/religionGoogleCoeffs.jpeg}
   \end{minipage}

  \begin{minipage}{0.48\textwidth}
\includegraphics[width=8cm]{../cosineAnalysis/images/genderCoeffs.jpeg}
\end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/genderGoogleCoeffs.jpeg}
   \end{minipage}

  \begin{minipage}{0.48\textwidth}
\includegraphics[width=8cm]{../cosineAnalysis/images/raceCoeffs.jpeg}
\end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/raceGoogleCoeffs.jpeg}
   \end{minipage}
\end{figure}

\end{center}

\noindent What should strike us is that while the mean estimates of the coefficients indeed do differ a bit, usually the highest posterior density invervals all include zero, and so we do not have strong reasons to say that, say, as far as the whole religion dataset is involved, being associated indeed is connected  with lower cosine distance. A second striking observation is that the estimated impact for associated stereotypes is quite often not too different from the estimated impact of attributes associated with different stereotypes, and both are sometimes not too far from the estimated impact for simply human attributes.  In general, once the uncertainty involved is taken seriously by using control groups and statistical uncertainty estimation that does not dispose of pointwise data, the picture which focuses only on differences between means of means is too simplistic.

But this doesn't mean important differences for some protected words are not there. For one thing, if you start with a word list that is very uneven, the actually not so bad status of some of the protected words might mask  a pretty bad situation in which some other protected words are. For comparison, let's see what a model focused on words related to islam tells us.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religion <- read.csv("cosineAnalysis/datasets/religionReddit.csv")[-1]
colnames(religion) <- c("protectedWord","wordToCompare","wordClass",
                        "cosineDistance","cosineSimilarity","connection")
levels(religion$wordClass) <- c("christian","human","jewish","muslim","neutral")
muslimWords <- c("imam","islam","mosque","muslim","quran")
muslim <- religion %>% filter(protectedWord %in% muslimWords)

muslim$protectedWord <- droplevels(muslim$protectedWord)

muslim$pw <- as.integer(muslim$protectedWord)
muslim$con <- as.integer(muslim$connection)
muslim$pwFactor <- factor(paste0(muslim$protectedWord, muslim$connection))
muslim$pwIndex <- as.integer(muslim$pwFactor)

islamCoefs <- ulam(
  alist(
    cosineDistance ~ dnorm(mu,sigma),
    mu <- m[pw] + co[con],
    m[pw] ~ dnorm(1,.5),
    co[con] ~dnorm(0,.5),
    sigma ~ dcauchy(0,1)
  ),
  data = muslim,
  chains=2 , iter=10000 , warmup=1000, cores = 4,
  log_lik = TRUE
)
```
\normalsize

\footnotesize
```{r load islamCoefs,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
islamCoefs <- readRDS("cosineAnalysis/models/islamCoefs.rds")
```

 \vspace{1mm}
 \footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
islamCoefs <- print(precis(islamCoefs, depth =2, pars= "co" ))
saveRDS(islamCoefs, "cosineAnalysis/calculations/islamCoefs.rds")
islamCoefs <- readRDS("cosineAnalysis/calculations/islamCoefs.rds")
islamCoefs
```

\begin{center}
\includegraphics[width=8cm]{../cosineAnalysis/images/islamCoeffs.jpeg}
\end{center}

\normalsize

While muslim words were unusual in the sense that the disparity between associated attributes and others is stronger, the evidence is still not conclusive. This is because the variation even within islam-related words is large enough (and sample sizes sufficiently small) for all the highest posterior density invervals to still include zeros.

So, it seems, taking a closer look does seem to make a difference. The question is, what happens if we do take a close look at the level of protected words?

#  Protected-word level analysis

Let's turn then to data analysis that takes a look at protected words separately. This time for each combination of a protected word and a connection status we will have a separate mean cosine distance estimate, each coming with its own highest posterior density interval. This means we will use indices that are result from all such combinations (and then we will split them up in the model precis to build visualisation, feel free to look at the `visualiseStats.R` script for details).

\vspace{1mm}
\footnotesize
```{r build religionSeparate,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
options(buildtools.check = function(action) TRUE ) #removes install pop-up request
religion$pwFactor <- factor(paste0(religion$protectedWord, "-", religion$connection))
religion$pwIndex <- as.integer(religion$pwFactor)

religionSeparate <- ulam(
  alist(
    cosineDistance ~ dnorm(mu,sigma),
    mu <- c[pwIndex],
    c[pwIndex] ~ dnorm(1,.5),
    sigma ~ dcauchy(0,1)
  ),
  data = religion,
  chains=2 , iter=10000 , warmup=1000,
  start=list(no = 1, a = 0, d = 0, sigma= .3), log_lik =  TRUE
)
```
\normalsize

```{r load religionSeparate,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
#getwd()
religionSeparate <- readRDS("cosineAnalysis/models/religionSeparate.rds")
```

\noindent Let's see if the individualized model does better than the previous models in light of WAIC which does add penalty for the number of parameters.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
compareBaselineCoefsSeparate <- print(round(compare(religionBaseline, religionCoefs, religionSeparate)), 3)
saveRDS(compareBaselineCoefsSeparate, "cosineAnalysis/calculations/compareBaselineCoefsSeparate.rds")
compareBaselineCoefsSeparate <- readRDS("cosineAnalysis/calculations/compareBaselineCoefsSeparate.rds")
compareBaselineCoefsSeparate
```
\normalsize

Great, it seems that we do want to prefer this model, despite its relative complication. Now, what does it tell us about the protected words? Let's visualise the predicted means together with 89\% highest posterior density intervals.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
source("cosineAnalysis/functions/visualiseStats.R")
religion$pwFactor <- factor(paste0(religion$protectedWord, "-", religion$connection))
religion$pwIndex <- as.integer(religion$pwFactor)
visReligionReddit <- visualisePWestimates(data = religion, model = religionSeparate)+
  ggtitle("Religion (Reddit)")
png(file="cosineAnalysis/images/visReligionReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visReligionReddit
dev.off()
```
\normalsize

Before we move to a discussion, let's perform analogous analyses for the remaining types of supposed bias: gender and race (the model building is analogous, so here we just load the pre-compiled results).

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
source("cosineAnalysis/functions/visualiseStats.R")
gender <- read.csv("cosineAnalysis/datasets/genderReddit.csv")[-1] 
gender <- cleanDataset(gender,c("human","man","neutral","woman"))
gender$pwFactor <- factor(paste0(gender$protectedWord, "-", gender$connection))
gender$pwIndex <- as.integer(gender$pwFactor)
genderSeparate <- readRDS("cosineAnalysis/models/genderSeparate.rds")
visGenderReddit <- visualisePWestimates(data = gender, model = genderSeparate)+
  ggtitle("Gender (Reddit)")
png(file="cosineAnalysis/images/visGenderReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visGenderReddit
dev.off()
```
\normalsize

\footnotesize
```{r raceReddit,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
race <- read.csv("cosineAnalysis/datasets/raceReddit.csv")[-1]
race <- cleanDataset(race,c("asian","black","caucasian","human","neutral"))
race$pwFactor <- factor(paste0(race$protectedWord, "-", race$connection))
race$pwIndex <- as.integer(race$pwFactor)
raceSeparate <- readRDS("cosineAnalysis/models/raceSeparate.rds")
visRaceReddit <- visualisePWestimates(data = race, model = raceSeparate)+
  ggtitle("Race (Reddit)")
png(file="cosineAnalysis/images/visRaceReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visRaceReddit
dev.off()
```

# Application to Google word2vec

\todo{Explain where you took the embedding from, cite publications first announcing it.}

<!-- \vspace{1mm} -->
<!-- \footnotesize -->
<!-- ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} -->
<!-- religionGoogle <- read.csv("cosineAnalysis/datasets/religionGoogle.csv")[-1] -->
<!-- religionGoogle <- cleanDataset(religionGoogle,c("christian","human","jewish","muslim","neutral")) -->
<!-- religionGoogleModel <- readRDS("cosineAnalysis/datasets/religionGoogleModel.rds") -->
<!-- religionGoogle$pwFactor <- factor(paste0(religionGoogle$protectedWord, "-", religionGoogle$connection)) -->
<!-- religionGoogle$pwIndex <- as.integer(religion$pwFactor) -->
<!-- visualisePWestimates(data = religionGoogle, model = religionGoogleModel) -->
<!-- ``` -->

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
religionGoogle <- read.csv("cosineAnalysis/datasets/religionGoogle.csv")[-1]
religionGoogle <- cleanDataset(religionGoogle,c("christian","human","jewish","muslim","neutral"))
religionGoogleModel <- readRDS("cosineAnalysis/models/religionGoogleModel.rds")
religionGoogle$pwFactor <- factor(paste0(religionGoogle$protectedWord, "-", religionGoogle$connection))
religionGoogle$pwIndex <- as.integer(religion$pwFactor)
visReligionGoogle <- visualisePWestimates(data = religionGoogle, model = religionGoogleModel)+
  ggtitle("Religion (Google)")
png(file="cosineAnalysis/images/visReligionGoogle.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visReligionGoogle
dev.off()
```

\normalsize

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
genderGoogle <- read.csv("cosineAnalysis/datasets/genderGoogle.csv")[-1]
genderGoogle <- cleanDataset(genderGoogle,c("human","man","neutral","woman"))
genderGoogleModel <- readRDS("cosineAnalysis/models/genderGoogleModel.rds")
genderGoogle$pwFactor <- factor(paste0(genderGoogle$protectedWord, "-", genderGoogle$connection))
genderGoogle$pwIndex <- as.integer(gender$pwFactor)
visGenderGoogle <- visualisePWestimates(data = genderGoogle, model = genderGoogleModel)+
ggtitle("Gender (Google)")
png(file="cosineAnalysis/images/visGenderGoogle.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visGenderGoogle
dev.off()
```
\normalsize

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
raceGoogle <- read.csv("cosineAnalysis/datasets/raceGoogle.csv")[-1]
raceGoogle <- cleanDataset(raceGoogle,c("asian","black","caucasian","human","neutral"))
raceGoogleModel <- readRDS("cosineAnalysis/models/raceGoogleModel.rds")
raceGoogle$pwFactor <- factor(paste0(raceGoogle$protectedWord, "-", raceGoogle$connection))
raceGoogle$pwIndex <- as.integer(raceGoogle$pwFactor)
visRaceGoogle <- visualisePWestimates(data = raceGoogle, model = raceGoogleModel)+
ggtitle("Race (Google)")
png(file="cosineAnalysis/images/visRaceGoogle.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visRaceGoogle
dev.off()
```
\normalsize

# The role of debiasing

\todo{describe which debiasing you used and how it was advertised in the paper}

First, let's look at coefficient estimated for the whole datasets, as compared to their estimation prior to debiasing:

\begin{center}
\begin{figure}[!htb]\centering
   \begin{minipage}{0.48\textwidth}
  \includegraphics[width=8cm]{../cosineAnalysis/images/religionCoeffs.jpeg}
   \end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/debiasedReligionRedditCoeffs.jpeg}
   \end{minipage}

  \begin{minipage}{0.48\textwidth}
\includegraphics[width=8cm]{../cosineAnalysis/images/genderCoeffs.jpeg}
\end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/debiasedGenderRedditCoeffs.jpeg}
   \end{minipage}

  \begin{minipage}{0.48\textwidth}
\includegraphics[width=8cm]{../cosineAnalysis/images/raceCoeffs.jpeg}
\end{minipage}
   \begin {minipage}{0.48\textwidth}
    \includegraphics[width=8cm]{../cosineAnalysis/images/debiasedRaceRedditCoeffs.jpeg}
   \end{minipage}
\end{figure}

\end{center}

\todo{comment on this}

Some points to discuss:

- humans in religion got closer (should they?)

- change in Gender is really minor, still zero out of HPDI range, note how different is very similar

- small improvement in race, at the price of moving neutral terms closer

Now, perhaps, the effects of debiasing will be better appreciated if we look at the level of protected words. After all, the hope is, the situation of extremely ill-positioned protected words have improved?

\newpage

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
debiasedReligionReddit <- read.csv("cosineAnalysis/datasets/debiasedReligionReddit.csv")[-1]
debiasedReligionReddit <- cleanDataset(debiasedReligionReddit,c("christian","human","jewish","muslim","neutral"))
debiasedReligionRedditModel <- readRDS("cosineAnalysis/models/debiasedReligionRedditModel.rds")
debiasedReligionReddit$pwFactor <- factor(paste0(debiasedReligionReddit$protectedWord, "-", debiasedReligionReddit$connection))
debiasedReligionReddit$pwIndex <- as.integer(debiasedReligionReddit$pwFactor)
visDebReligionReddit <- visualisePWestimates(data = debiasedReligionReddit, model = debiasedReligionRedditModel)+
  ggtitle("Religion (Reddit, debiased)")
png(file="cosineAnalysis/images/visDebReligionReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visDebReligionReddit
dev.off()
```

\normalsize

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
debiasedGenderReddit <- read.csv("cosineAnalysis/datasets/debiasedGenderReddit.csv")[-1]
debiasedGenderReddit <- cleanDataset(debiasedGenderReddit,c("human","man","neutral","woman"))
debiasedGenderRedditModel <- readRDS("cosineAnalysis/models/debiasedGenderRedditModel.rds")
debiasedGenderReddit$pwFactor <- factor(paste0(debiasedGenderReddit$protectedWord, "-", debiasedGenderReddit$connection))
debiasedGenderReddit$pwIndex <- as.integer(debiasedGenderReddit$pwFactor)
visDebGenderReddit <- visualisePWestimates(data = debiasedGenderReddit, model = debiasedGenderRedditModel)+
ggtitle("Gender (Reddit, debiased)")
png(file="cosineAnalysis/images/visDebGenderReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visDebGenderReddit
dev.off()
```
\normalsize

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
debiasedRaceReddit <- read.csv("cosineAnalysis/datasets/debiasedRaceReddit.csv")[-1]
debiasedRaceReddit <- cleanDataset(debiasedRaceReddit,c("asian","black","caucasian","human","neutral"))
debiasedRaceRedditModel <- readRDS("cosineAnalysis/models/debiasedRaceRedditModel.rds")
debiasedRaceReddit$pwFactor <- factor(paste0(debiasedRaceReddit$protectedWord, "-", debiasedRaceReddit$connection))
debiasedRaceReddit$pwIndex <- as.integer(debiasedRaceReddit$pwFactor)
visDebRaceReddit <- visualisePWestimates(data = debiasedRaceReddit, model = debiasedRaceRedditModel)+
ggtitle("Race (Reddit, debiased)")
png(file="cosineAnalysis/images/visDebRaceReddit.png", 
      units="in", 
      width=6, 
      height=6, 
      pointsize = 1,
      res=400)
visDebRaceReddit
dev.off()
```
\normalsize

Points to discuss:

- in religion, `human` got closer

- in gender, not much difference, different and associated are fairly close and much closer than the others, while humans got further

- in race the assiociated got moved away but now for some the different ones got much closer

### 2021-09-02 bayesianAnalysis/causalThinking.R

@@ -7,89 +7,121 @@ library(rethinking)
 #B, D, A: before, during, after
 #T, C: type, count
 
-
-large <- dagitty("
+dag <- dagitty("
     dag{
-    AB -> AD -> AA
-    AB -> HB -> HD -> HA
-    AD -> HD
-    AA -> HA
-    IT -> HD
-    IT -> AD
-    IT -> AA
-    IT -> HA
-    IC -> HD
-    IC -> AD
-    IC -> AA
-    IC -> HA
-    } 
-  ")
+        AD -> HD -> IC
+        U [unobserved]
+        U -> AD
+        U -> HD
+        U -> AC
+        U -> HC
+        AC -> HC
+        IC -> AC
+        IC -> HC
+        IT -> AC
+        IT -> HC
+        }")
+
+
+drawdag(dag)
+
+
+paths(dag, from = c("IC"), to = "HC")
 
 
 
-drawdag(large)
-
-
-adjustmentSets(large, exposure = c("IC", "IT"), outcome = "HA")
-
-adjustmentSets(large, exposure = c("IC", "IT"), outcome = "HA", effect = "direct")
+paths(dag, from = c("IC"), to = "AC")
 
 
 
-impliedConditionalIndependencies(large)
+impliedConditionalIndependencies(dag)
 
+adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "HC")
 
-
-small <- dagitty("
-    dag{
-    AB ->  AA
-    AB -> HB -> HA
-    AA -> HA
-    I -> AA
-    I -> HA
-    } 
-  ")
-
-drawdag(small)
-
-adjustmentSets(small, exposure = c("I"), outcome = "HA")
-
-
-adjustmentSets(small, exposure = c("I"), outcome = "HA", effect = "direct")
+adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AC")
 
 
 
 
-impliedConditionalIndependencies(large)
-
-
-hidden <- dagitty("
-    dag{
-    UA [unobserved]
-    UH [unobserved]
-    AB ->  HB
-    AA -> HA
-    I -> AA
-    I -> HA
-    UA -> AB
-    UA -> AA
-    UH -> HB
-    UH -> HA
-    } 
-  ")
-
-
-drawdag(hidden)
-
-adjustmentSets(hidden, exposure = c("I"), outcome = "HA", effect = "total")
-adjustmentSets(hidden, exposure = c("I"), outcome = "HA", effect = "direct")
[…]

### 2021-09-02 bayesianAnalysis/priorsSelection.R

@@ -7,26 +7,20 @@ sim <- seq(0,400,by = 1)
 p <- ggplot(data = data.frame(count = sim), 
             mapping = aes(x = count))+theme_tufte()
 
+xdnorm <- seq(-4,4,by = 0.01)
+pd <- ggplot(data = data.frame(change = xdnorm), 
+            mapping = aes(x = change))+theme_tufte()
 
 
-priorHA <-  function(x) dcauchy(x,1,22)
-p + stat_function(fun = priorHA)+xlim(c(0,20))+ggtitle("Prior for hate after")
+priorHD <-  function(x) dcauchy(x,1,22)
+p + stat_function(fun = priorHD)+xlim(c(0,20))+ggtitle("Prior for hate during")
 
-priorHB <-  function(x) dcauchy(x,1,22)
-p + stat_function(fun = priorHA)+xlim(c(0,20))+ggtitle("Prior for hate before")
+priorAC <- function(x) dnorm(x,0,1)
+pd + stat_function(fun = priorAC)+ggtitle("Prior for activity change")
 
+priorHC <- function(x) dnorm(x,0,1)
+pd + stat_function(fun = priorHC)+ggtitle("Prior for change in attacks")
 
-priorAB <- function(x) dcauchy(x,23,22)
-p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
-
-priorAB <- function(x) dnorm(x,23,30)
-p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
-
-priorAA <- function(x) dcauchy(x,23,22)
-p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
-
-priorAA <- function(x) dnorm(x,23,30)
-p + stat_function(fun = priorAB)+xlim(c(0,100))+ggtitle("Prior for activity before")
 
 
 

### 2021-09-02 bayesianAnalysis/causalThinking.R
r

@@ -7,6 +7,8 @@ library(rethinking)
 #B, D, A: before, during, after
 #T, C: type, count
 
+par( mfrow=c(1,1) )
+
 dag <- dagitty("
     dag{
         AD -> HD -> IC
@@ -32,14 +34,12 @@ paths(dag, from = c("IC"), to = "HC")
 
 paths(dag, from = c("IC"), to = "AC")
 
-
-
 impliedConditionalIndependencies(dag)
+
 
 adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "HC")
 
 adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AC")
-
 
 
 
@@ -49,8 +49,6 @@ adjustmentSets(dag, exposure = c("IC"), outcome = "AC", effect = "direct")
 
 
 adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "HC", effect = "direct")
-
-
 
 
 
@@ -99,6 +97,7 @@ paths(dag2, from = c("IC"), to = "AC")
 
 
 impliedConditionalIndependencies(dag2)
+impliedConditionalIndependencies(dag)
 
 adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "HC")
 

### 2021-09-02 bayesianAnalysis/priorsSelection.R

@@ -1,6 +1,7 @@
 library(ggpubr)
 library(ggplot2)
 library(ggthemes)
+library("fitdistrplus")
 
 
 sim <- seq(0,400,by = 1)
@@ -12,14 +13,45 @@ pd <- ggplot(data = data.frame(change = xdnorm),
             mapping = aes(x = change))+theme_tufte()
 
 
-priorHD <-  function(x) dcauchy(x,1,22)
-p + stat_function(fun = priorHD)+xlim(c(0,20))+ggtitle("Prior for hate during")
-
 priorAC <- function(x) dnorm(x,0,1)
 pd + stat_function(fun = priorAC)+ggtitle("Prior for activity change")
 
 priorHC <- function(x) dnorm(x,0,1)
 pd + stat_function(fun = priorHC)+ggtitle("Prior for change in attacks")
+
+
+
+getwd()
+extraComments <- read.csv("datasets/extraCommentsFinal.csv")
+extraCommentsA <- rowSums(extraComments[2:11])
+extraCommentsB <- rowSums(extraComments[12:22])
+extraCommentsDiff <- extraCommentsA - extraCommentsB
+extraCommentsDiffS <- standardize(extraCommentsDiff)
+ggplot()+geom_histogram(aes(x=extraCommentsDiffS))
+AC <- function(x)dnorm(x,0,1.32)
+ggplot()+geom_histogram(aes(x=extraCommentsDiffS,y=..count../sum(..count..)), bins = 30)+
+        stat_function(fun = AC)+stat_function(fun=priorAC, color = "red")
+
+
+getwd()
+extraHate <- read.csv("datasets/extraHateFinal.csv")
+extraHateA <- rowSums(extraHate[2:11])
+extraHateB <- rowSums(extraHate[12:22])
+extraHateDiff <- extraHateA - extraHateB
+extraHateDiffS <- standardize(extraHateDiff)
+ggplot()+geom_histogram(aes(x=extraHateDiffS))
+HC <- function(x)dnorm(x,0,1.62)
+ggplot()+geom_histogram(aes(x=extraHateDiffS,y=..count../sum(..count..)))+
+  stat_function(fun = HC)+stat_function(fun=priorHC, color = "red")
+
+
+
+
+
+
+
+
+
 
 
 

### 2021-09-03 cleanup/furthercleaning.R
cleaning done

@@ -1,0 +1,276 @@
+library(dplyr)
+library(tidyverse)
+library(WRS2)
+library(purrr)
+library(rethinking)
+
+
+
+AllClean <- readRDS(file = "datasets/RAWNESTA/AllClean.rds")
+AllHate <- readRDS(file = "datasets/RAWNESTA/HateClean.rds")
+
+#AllHate <- read.csv("HateClean.csv")
+#AllClean <- read.csv("AllClean.csv")
+#usernames is a dataset of usernames identified for a study - I'm going to remove all users which do not belong to this list later on
+usernames <- read.csv("usernames.csv", header=FALSE)
+
+head(AllHate) #attacks only
+head(AllClean) #comments 
+head(usernames)
+nrow(AllHate)
+nrow(AllClean)
+nrow(usernames)
+
+
+colnames(usernames) <-  c("author")
+head(usernames)
+
+
+#filtering out rows which include usernames other than the one in "usernames" -- selecting study group members
+Hate <- AllHate[AllHate$author %in% usernames$author, ]
+head(Hate)
+nrow(Hate)
+#same for comments
+Comments <- AllClean[AllClean$author %in% usernames$author, ]
+head(Comments)
+nrow(Comments)
+
+
+
+
+#count unique
+n_distinct(Hate$author) #693 - YEAH! This is the exact number of users selected for study, so the above formula worked 
+n_distinct(Comments$author) #693
+
+
+HateFreq <- xtabs(~ author + day, data = Hate) 
+CommentsFreq <- xtabs(~ author + day, data = Comments)
+
+head(HateFreq) #also 693 rows, hell yeah!
+nrow(HateFreq)
+head(CommentsFreq)
+nrow(CommentsFreq)
+
+length(colnames(HateFreq))
+
+length(colnames(CommentsFreq))
+
+which(!(colnames(CommentsFreq) %in%  colnames(HateFreq)))
+
+
+colnames(CommentsFreq)[22]
+
+colnames(HateFreq)
+
+CommentsFreq <- CommentsFreq[,-22]
+
+
+
+mean(colnames(CommentsFreq) == colnames(HateFreq))
+
+
+
+#from table to dataframe
+Hate <- spread(as.data.frame(HateFreq),day,Freq)
+head(Hate)
+nrow(Hate)
+
+Comments <- spread(as.data.frame(CommentsFreq),day,Freq)
+head(Comments)
+nrow(Comments)
+
+
+#----------------------------------------------
[…]

### 2021-09-03 cleanup/interventionscleanup.R

@@ -1,0 +1,212 @@
+library(tidyverse)
+library(dplyr)
+library(purrr)
+library(WRS2)
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+interventions <- read.csv("datasets/RAWNESTA/interventions.csv")
+head(interventions)
+head(summaries)
+str(interventions)
+interventions$day <-  as.Date(as.POSIXct(interventions$day, origin="1970-01-01"))
+colnames(interventions)[5] <- "author"
+
+min(interventions$day)
+max(interventions$day)
+
+#sum wrong interventions
+nrow(interventions) #1661
+sum(interventions[, 'wrong'], na.rm = TRUE) #23 wrong interventions (out of 1662)
+
+#checking how many users received at least one intervention - 307
+n_distinct(interventions$user) 
+
+#checking whether no typos were made in usernames in intervention file
+usernames <- read.csv("datasets/RAWNESTA/usernames.csv", header=FALSE)
+colnames(usernames) <-  c("author")
+head(usernames)
+mean(interventions$author %in% usernames$author)
+#no interventions with users not on the list
+
+
+nrow(interventions) #1661 interventions (1 less than step before, ok)
+sum(interventions[, 'wrong'], na.rm = TRUE) #23 wrong, nothing has changed here
+
+sum(interventions$emp) #770
+sum(interventions$norm) #887
+
+
+#select those usernames who received wrong intervention
+wrongTreat <- filter(interventions, wrong=="1")
+head(wrongTreat)
+nrow(wrongTreat) #23 correct
+
+wrongTreat$author
+wrongTreat$author[duplicated(wrongTreat$author)]
+
+wrongUsers <- as.character(unique(wrongTreat$author)) #19
+wrongUsers
+sum(wrongUsers %in% summaries$author) #11 to be removed
+
+
+
+all <- readRDS(file = "datasets/RAWNESTA/AllClean.rds")
+hate <- readRDS(file = "datasets/RAWNESTA/HateClean.rds")
+
+sum(wrongUsers %in% all$author) #11 to be removed
+sum(wrongUsers %in% hate$author) #11 to be removed
+
+
+usersDeleted <- read.csv("datasets/RAWNESTA/nesta_deleted.csv", header=FALSE)
+
+nrow(usersDeleted)
+usersSuspended <- read.csv("datasets/RAWNESTA/nesta_suspended.csv", header=FALSE)
+nrow(usersSuspended)
+
[…]

### 2021-09-03 visualisations/exploration.R

@@ -1,0 +1,88 @@
+library(ggplot2)
+library(ggthemes)
+library(ggpubr)
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+
+
+head(summaries)
+
+#barplot of interventions
+ggplot(summaries[summaries$group != "control",], aes(x = IC))+geom_bar()+theme_tufte()+
+  xlab("interventions received")+labs(title = "Intervention counts in treatment groups")+
+  scale_x_continuous(breaks = seq(0,40,5))
+
+ggsave("images/interventionsBar.pdf", width = 20, height = 10, units = "cm", dpi = 450)  
+
+
+
+ggplot(summaries, aes(x=AdiffS, fill = group))+geom_density(alpha= 0.3)+theme_tufte()+xlim(c(-1,1))
+
+mean(summaries$AdiffS)
+
+
+ReturnMax<-function(numvec){
+  dens <- density(numvec)
+  return(dens$x[which.max(dens$y)][1])
+         }
+
+
+
+maxControlS <- ReturnMax(summaries[summaries$group == "control",]$AdiffS)
+maxEmpathyS <- ReturnMax(summaries[summaries$group == "empathy",]$AdiffS)
+maxNormativeS <- ReturnMax(summaries[summaries$group == "normative",]$AdiffS)
+
+densAdiffCS <- ggplot(summaries[summaries$group == "control",], aes(x=AdiffS))+geom_density(alpha= 0.2)+theme_tufte()+xlim(c(-1,1))+geom_vline(xintercept = maxControlS, alpha = 0.3)+
+  theme(axis.title.y=element_blank(), axis.text.y=element_blank(),axis.ticks.y=element_blank())+ggtitle("Control")+xlab("standard deviation from the mean")
+
+densAdiffES <- ggplot(summaries[summaries$group == "empathy",], aes(x=AdiffS))+geom_density(alpha= 0.2)+theme_tufte()+xlim(c(-1,1))+geom_vline(xintercept = maxEmpathyS, alpha = 0.3)+
+  theme(axis.title.y=element_blank(), axis.text.y=element_blank(),axis.ticks.y=element_blank())+ggtitle("Empathy")+xlab("standard deviation from the mean")
+
+densAdiffNS <-
+  ggplot(summaries[summaries$group == "normative",], aes(x=AdiffS))+geom_density(alpha= 0.2)+theme_tufte()+xlim(c(-1,1))+geom_vline(xintercept = maxNormativeS, alpha  = 0.3)+
[…]

### 2021-09-03 visualisations/visualisePeriods.R

@@ -1,0 +1,58 @@
+library(ggplot2)
+library(ggthemes)
+
+
+getwd()
+Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
+Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
+
+
+dates <- colnames(Hate)[-1]
+dates <- as.Date(dates)
+
+
+
+startDate <- dates[1]
+interventionDate <- "2020-07-09"
+observationDate <- "2020-09-10"
+end <- dates[length(dates)]
+
+periods<- numeric(length(dates))
+periods <- ifelse(dates < interventionDate,"pre-treatment",periods)
+periods <- ifelse(dates >= interventionDate & dates < observationDate,"treatment",periods)
+periods <- ifelse(dates >= observationDate,"post-treatment",periods)
+periods
+
+
+length(periods)
+length(dates)
+
+points <- rep(1,length(dates))
+
+
+dateDF <- data.frame(dates,periods, points)
+
+
+idx <- c(1, diff(dateDF$dates))
+i2 <- c(1,which(idx != 1), nrow(dateDF)+1)
+dateDF$grp <- rep(1:length(diff(i2)), diff(i2))
+
+#dateDF
+
+
+
+ggplot(dateDF, aes(x=dates, y = points, color = periods, group = grp))+geom_line(alpha = 0.8, size = 1)+theme_tufte()+ theme(axis.title.y=element_blank(), axis.text.y=element_blank(),
+        axis.ticks.y=element_blank(),axis.title.x=element_blank(), plot.caption = element_text(hjust = 0.5,  face= "italic"))+
+#  scale_x_date(date_labels = "%b %d",date_breaks = "2 weeks", limits = c(init-10,end+10))+
+  scale_x_date(date_labels = "%b %d", breaks = c(init, as.Date(startDate), as.Date(interventionDate), as.Date(observationDate), end), limits = c(init-10,end+10))+
+  geom_vline(xintercept = dates[which(dates == startDate)], lty =2, size =.2, alpha=0.5)+
+  geom_vline(xintercept = dates[which(dates == interventionDate)], lty= 2, size = .2, alpha=0.5)+
+  geom_vline(xintercept = dates[which(dates == observationDate)], lty = 2, size =.2, alpha=0.5 )+ylim(c(0.95,1.05))+ geom_vline(xintercept = as.Date(end), lty =2, size =.2, alpha=0.5)+
[…]

### 2021-09-03 visualisations/exploration.R
added scatterplot

@@ -85,4 +85,9 @@ ggsave("images/CCS.pdf", width = 20, height = 15, units = "cm", dpi = 450)
 
 
 
+summaries[summaries$IC != 0,]
+
+ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-2,2))
+
+
 

### 2021-09-03 visualisations/exploration.R
visualisations

@@ -87,7 +87,10 @@ ggsave("images/CCS.pdf", width = 20, height = 15, units = "cm", dpi = 450)
 
 summaries[summaries$IC != 0,]
 
-ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-2,2))
+ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-1,1))
+
+
+ggplot(summaries, aes(x = IC, y = Adiff, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-100,100))
 
 
 

### 2021-09-07 bayesianAnalysis/bayesianModels.R
finished building interaction models

@@ -1,0 +1,408 @@
+source("utils/plotPriors.R")
+
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+head(summaries)
+
+precis(summaries)
+
+summaries$ABw <- (summaries$AB/81)*7
+summaries$CBw <- (summaries$CB/81)*7
+summaries$AAw <- (summaries$AB/72)*7
+summaries$CAw <- (summaries$CB/72)*7
+summaries$ADw <- (summaries$AD/62)*7
+summaries$CDw <- (summaries$CD/62)*7
+summaries$Adiffw <- summaries$AAw - summaries$ABw
+summaries$Cdiffw <- summaries$CAw - summaries$CBw
+
+
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+
+summary(summaries$AAS)
+
+#null model: AA
+
+
+#prior plot
+set.seed(2971)
+N <- 300
+mu <- rnorm(N, 0, 0.5) 
+ggplot()+geom_density(aes(x = mu))+theme_tufte()
+
+ggplot()+geom_density(aes(x = mu))
+
+
+nullModel <- quap(
+          alist(
+          AAS ~ dnorm( mu, sigma ),
+          mu ~ dnorm (0,0.5),
+          sigma  ~ dexp(1)
+          ), 
+          data = summaries  
+          )
+
+
+
+
+precis(nullModel)
+
+postNullModel <- extract.samples(nullModel, n = 1e4 )
+
+precis(postNullModel)
+
+
+
+#only ADS 
+ADSModel <- quap(
+  alist(
+    AAS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS,
+    a ~ dnorm (0,0.5),
+    bADS ~ dnorm(0,0.2),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+precis(ADSModel)
+
+
+compare(nullModel,ADSModel)
+
+# priors for ADS model
[…]

### 2021-09-07 bayesianAnalysis/predictionsInteractions.R

@@ -1,0 +1,93 @@
+source("utils/plotPriors.R")
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+
+
+
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+summaries$groupID <-  as.integer( as.factor(summaries$group) )
+
+
+
+LotsOfInteractionsModel3 <- quap(
+  alist(
+    AAS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,0.5),
+    bADS[groupID] ~ dnorm(0,.5),
+    bADSIC ~ dnorm(0,.5),
+    bCBS[groupID] ~ dnorm(0,.5),
+    bIT[groupID] ~ dnorm(0,.5),
+    bIC[groupID] ~ dnorm(0,.5),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+
+
+head(summaries)
+
+
+
+
+
+mean(summaries$IC[summaries$groupID != 1])
+
+ADS <- seq(-2,-1, by = 0.1)
+CBS <- seq(-2,-1, by = 0.1)
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+
+predictions <-  link(LotsOfInteractionsModel3,data = data)
+predictions.mean <- apply( predictions , 2 , mean )
+predictionsDF <- cbind(data,predictions.mean)
+predictionsDF
+ggplot(predictionsDF)+geom_point(aes(x = groupID, y = predictions.mean))
+
+
+ADS <- seq(-2,2, by = 0.1) 
+groupID <- 2
+IC <- 1
+data <- expand.grid(ADS = ADS,groupID = groupID,IC =  IC)
+
+predictions <-  link(LotsOfInteractionsModel,data = data)
+predictions.mean <- apply( predictions , 2 , mean )
+predictionsDF <- cbind(data,predictions.mean)
[…]

### 2021-09-07 bayesianAnalysis/priorsSelection.R

@@ -16,6 +16,34 @@ pd <- ggplot(data = data.frame(change = xdnorm),
 priorAC <- function(x) dnorm(x,0,1)
 pd + stat_function(fun = priorAC)+ggtitle("Prior for activity change")
 
+
+priorA <- function(x) dcauchy(x,2,10)
+pd + stat_function(fun = priorA)+ggtitle("Prior for attacks")+xlim(c(0,60))+xlab("weekly attacks")
+
+
+sigmas <- rexp(100,3)
+ggplot()+ geom_density(aes(x=sigmas))+ggtitle("Prior for sd")+xlab("sd")
+
+priorb <- function(x) dnorm(x,0,.5)
+pd + stat_function(fun = priorb)+ggtitle("Prior for activity change")
+
+
+
+aa <- rpois(100,3)
+ggplot()+ geom_density(aes(x=aa))+ggtitle("Prior for sd")+xlab("sd")
+
+
+aa <- rlnorm(1e4,0,1)
+ggplot()+ geom_density(aes(x=aa))+ggtitle("Prior for attacks")+xlab("sd")+xlim(0,2)
+
+b <- rlnorm( 1e4 , 0 , 1 )
+dens( b , xlim=c(0,5) , adj=0.1 )
+
+
+
+
+?dexp
+
 priorHC <- function(x) dnorm(x,0,1)
 pd + stat_function(fun = priorHC)+ggtitle("Prior for change in attacks")
 

### 2021-09-07 utils/plotPriors.R

@@ -1,0 +1,24 @@
+library(reshape2)
+library(ggplot2)
+library(ggthemes)
+library(ggpubr)
+library(rethinking)
+library(dplyr)
+library(tidyverse)
+library(WRS2)
+library(purrr)
+
+
+visualisePriors <- function(model, dataAsList, N = 100)
+{
+  prior <- extract.prior( model, n = N )
+  mu <- link( model , post=prior, data=dataAsList)  
+  mut <- as.data.frame(t(mu))
+  mutLong <- melt(mut)
+  mutLong$x <- rep(c(-3,3),N)
+  ggplot(mutLong)+geom_line(aes(x = x, y = value, group = variable), alpha = 0.2)+theme_tufte()+xlab(names(data)[1])
+}
+
+#visualisePriors(100,ABSModel, list(ABS = c(-3,3)))
+
+

### 2021-09-07 visualisations/exploration.R

@@ -7,6 +7,45 @@ summaries <- readRDS(file = "datasets/Summaries.rds")
 
 head(summaries)
 
+
+
+# weekly averages
+#days: 81 (pre-treatment), 62 (treatment), 72 (post-treatment)
+
+head(summaries)
+summaries$ABw <- (summaries$AB/81)*7
+summaries$CBw <- (summaries$CB/81)*7
+summaries$AAw <- (summaries$AB/72)*7
+summaries$CAw <- (summaries$CB/72)*7
+
+summaries$Adiffw <- summaries$AAw - summaries$ABw
+summaries$Cdiffw <- summaries$CAw - summaries$CBw
+
+
+
+mean(summaries$AAw)
+mean(summaries$ABw)
+
+
+#barplot of attacks
+
+ggplot(summaries, aes(x = ABw, fill = "before"), alpha = 0.6, bins = 80)+geom_histogram()+theme_tufte() +geom_histogram(aes(x = AAw, fill = "after"), alpha = 0.6, bins = 80)+  xlab("attacks")+labs(title = "Attacks before & after", subtitle = "(weekly averages)")
+
+
+
+ggplot(summaries, aes(x = Adiffw, fill = group), alpha = 0.6, bins = 160)+geom_density(alpha=0.3)
+
+ggplot(summaries, aes(x = Adiffw, fill = group,  y = stat(count / sum(count))), alpha = 0.6, bins = 160)+geom_histogram()+theme_tufte()+  xlab("attacks")+labs(title = "Change in attacks", subtitle = "(weekly averages)")+facet_wrap(~group, ncol = 1)
+
+
+
+ggplot()+theme_tufte() +geom_histogram(aes(x = ACprop, fill = summaries$group, y  = stat(count / sum(count)), group = summaries$group), alpha = 0.4, bins = 80)+  xlab("attacks")+labs(title = "Proportional change in attacks by group")+geom_vline(xintercept = 1, size = 0.2)+xlim(c(0,3))+ylim(c(0,.2))
+
+
+
+
+
+
 #barplot of interventions
 ggplot(summaries[summaries$group != "control",], aes(x = IC))+geom_bar()+theme_tufte()+
   xlab("interventions received")+labs(title = "Intervention counts in treatment groups")+

### 2021-09-08 visualisations/visualisePeriods.R
visualisations for periods

@@ -13,8 +13,8 @@ dates <- as.Date(dates)
 
 
 startDate <- dates[1]
-interventionDate <- "2020-07-09"
-observationDate <- "2020-09-10"
+interventionDate <- "2020-07-08"
+observationDate <- "2020-09-09"
 end <- dates[length(dates)]
 
 periods<- numeric(length(dates))
@@ -24,18 +24,72 @@ periods <- ifelse(dates >= observationDate,"post-treatment",periods)
 periods
 
 
+
 length(periods)
 length(dates)
 
-points <- rep(1,length(dates))
 
 
-dateDF <- data.frame(dates,periods, points)
+hateTS <- as.data.frame(colSums(Hate[,-1]))
+hateTS$date <- as.Date(rownames(hateTS))
+rownames(hateTS) <- NULL
+colnames(hateTS) <- c("attacks","date")
+head(hateTS)
+hateTS$periods <- periods
 
 
-idx <- c(1, diff(dateDF$dates))
-i2 <- c(1,which(idx != 1), nrow(dateDF)+1)
-dateDF$grp <- rep(1:length(diff(i2)), diff(i2))
+interventions <- readRDS(file = "datasets/interventions.rds")
+
+interventionsTS <- as.data.frame(table(interventions$day))
+
+interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
+
+colnames(interventionsTS) <- c("date", "interventions")
+
+interventionsTS
+
+periodsDF <- merge(x = hateTS, y = interventionsTS, by = "date", all.x = TRUE)
+
+idx <- c(1, diff(periodsDF$date))
+i2 <- c(1,which(idx != 1), nrow(periodsDF)+1)
+periodsDF$grp <- rep(1:length(diff(i2)), diff(i2))
+
+periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "treatment"] <- 0
+
+periodsDF
+
+ggplot(periodsDF)+
+  geom_line(aes(x=date, y = attacks, group = grp),
+             alpha = 0.8, size = .6)+
+  geom_line(aes(x=date, y = interventions, group = grp),
+            alpha = 0.8, size = .6)+
+  geom_vline(xintercept = startDate, lty =2, size =.2, alpha=0.5)+
+  geom_vline(xintercept = as.Date(interventionDate), lty =2, size =.2, alpha=0.5)+
+  geom_vline(xintercept =  as.Date(observationDate), lty = 2, size =.2, alpha=0.5 )+
[…]

### 2021-09-08 paperDraft/paperDraft.Rmd

@@
 ---
-title: "Nesta attacks study"
+title: "Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online"
 author: "Patrycja Tempska and Rafal Urbaniak"
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
-2+2 #use this formatting for chunks
-```
+
 \normalsize
@@
 
-Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others.
-E.g. Insulting others is against Reddit's policy. 
-Hey there, we do not call each other like that here.
-Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both. They are designed to evoke an empathetic response. 
-E.g. There is a human being on the other side who might be hurt by your words.
-I see you are frustrated but remember the human.
+\textbf{Empathetic interventions}
+In the first treatment condition, volunteers were encouraged to send empathy-inducing messages focusing either on the target of verbal aggression (e.g.
+„Hey such words might hurt the other person”), stressing the common humanity aspect that we call share („We are all humans of flesh and blood”), or even infusing the intervention with the emphatic response to the attacker (Hey I understand your strong emotions…”).
+At the core of the empathetic interventions, we put forth the notion that goes back to David Hume and Adam Smith.
+The first one conceived empathy (at the time referred to as sympathy) as mirroring the emotional state of another person.
+In the academic psychological literature, similar phenomenon was distinguished and coined in the term emotional contagion
+(https://www.sciencedirect.com/topics/psychology/emotional-contagion): "the process in which an observed behavioral change in one individual leads to the reflexive production of the same behavior by other individuals in close proximity, with the likely outcome of converging emotionally".
+For Adam Smith, sympathy consisted of visualizing how the sympathetic person would feel in the particular circumstances of the other --- thus here the process was based not so much on mirroring, but rather projecting my imagination of what it is like to be that person in a certain moment).
+Without further delving into the differentiation between those two, sympathy in both accounts is crucial in the constitution of human beings as social and moral creatures (https://plato.stanford.edu/entries/empathy/).
+It enables the emotional connection to others and concern for their well-being.
+In the psychological literature, various kinds of empathetic responses were distinguished - the aforementioned emotional contagion, affective/proper empathy, sympathy, personal distress or cognitive empathy ((https://plato.stanford.edu/entries/empathy/).
+During the experiment, we couldn’t observe or measure whether the empathetic response indeed was evoked.
+Also, interventions that stated that "such words might hurt the other person" have the underlying assumption that the receiver of the attack might be hurt, but in reality that might not even be the case.
+Intuitively, and following the argumentation of Thomas Nagel in “What is it like to be a bat?” one can only imagine what it is like - but for me - to be a bat or to be a receiver of the attack.
+To each observed or imagined experience there is an array of subjective quality to actually experiencing it and in this way receiving a particular message might be met with a unique reception by each conscious being.
+Also, full epistemic access to the mind and body of another is impossible.
+But even though such access is impossible and putting aside the broad spectrum of phenomena related to empathetic response, our goal was by utilizing interventions referring to empathy in various forms, changing the behavior of the attacker - convincing him to refrain from using verbal aggression towards others.
+Whether the message indeed gave rise to empathy was not of importance - one can imagine a hypothetical scenario of a successful intervention in which the attacker changed his behavior long-term and stopped attacking others, hopefully as a result of interventions, but the  empathetic response was not even evoked.
+The behavioral change could be induced by other motivations - e.g.
+unwillingness from the exclusion from the community.
+Thus the goal is not to evoke empathy, but through empathetic interventions - substantially limiting the use of verbal aggression.
+
+\textbf{Normative interventions}
+Normative interventions were grounded in broadly defined norms and normative theories expressed via various means - either specific community guidelines imposed by Reddit or through ethics - deontology, virtue ethics.
+Whatever the strategy was used, it was supposed to express the unacceptability of verbal aggression in a direct or non-direct way.
+
+A more direct approach referred to deontology in which „actions are good or bad according to a clear set of rules” (https://ethics.org.au/ethics-explainer-deontology/).
+Such interventions could state that „we have a duty to respect each other during the discussions", „we have a moral obligation to act in a civil manner while participating in online communities”, „we shouldn’t use ad personam in here”.
+The basic assumption behind those interventions is that there is something we ought to do or are morally required to do - and such actions are the right actions.
+There are also actions we ought not to do - and such actions are morally wrongful.
+This line of thinking can be traced back to Immanuel Kant who thought that all universal moral obligations can stem from categorical imperative: “act only in accordance with that maxim through which you can at the same time will that it become a universal law” (Groundwork of the Metaphysic of Morals).
+
+Yet other interventions were encouraged to be expressed in the light of virtue ethics and stressed the importance of adhering to or practicing certain virtues.
+Such a message was assumed to motivate the moral agent in the process of positive reinforcement and create a feeling of the desirability of certain behaviors, e.g.
+„capacity to be respectful in a heated discussion is a virtue and requires hard work”.
+The core assumption here is that the virtue itself is not genetically inherited but is rather a potential or a disposition of a character that can be practice and mastered like a practical skill (even though as mentioned by Natasza Szutta in [cite her book about virtue ethics] virtues and practical skills share some fundamental differences).
+NS distinguished two types of virtues - affective and cognitive.
+Affective virtues encompass the emotions and feelings that play an important and positive role in morality and can act as a support in the course of becoming a virtuous man.
+A cognitive virtue relates to the intellectual aspect in which one knows how to act in certain situations and understands the rules of morally rightful actions (e.g.
+what is kindness and how a kind man acts).
+Here, just as in the case of empathetic interventions, any attempts to measure whether the target of the intervention in the case of a positive outcome (behavioral change) indeed acted in a virtuous way.
+A virtue of kindness may manifest itself in particular behaviors but as such cannot be identified with the virtuous deed, as highlighted by Natasza Szutta.
+Although again, the goal of the experiment itself was to change the behavior of the attackers, and measuring whether particular messages contributed to more flourishing individuals in terms of virtue development and character creation lies beyond the scope of this work.
+Interventions could affect people either way - stimulate their moral reflections or limit their attacks due to consequentialist way of thinking and fear of potential outcomes (e.g.
+being excluded from the community).
+
+Additionally, Reddit created their social etiquette called "Rediquette" (https://www.reddithelp.com/hc/en-us/articles/205926439) which is "an informal expression of the values of many redditors, as written by redditors themselves." All users are encouraged to abide by it and moderators of communities (called subreddits) existing as a part of the platform have the authority to exclude its members based either on the basis of breaking the rules of the reddiquette or any other local rules imposed by specific subreddit.
+Volunteers were encouraged to refer to those norms as well, citing specific points, for instance, "Hey there, have you read the reddiquette?
+It says remember the human".
+or "Let's recall the reddiquette and adhere to the same standards of behavior online that you follow in real life".
+
+As we have seen, those two categories of interventions - normative and empathetic - encompass a whole variety of categories within.
+One might think that it would be useful to construct a more diverse set of treatment conditions in which we test each of the ethics or empathy differentiation separately - e.g.
+one for virtue ethics, deontology, perhaps utilitarian approach, empathy toward the receiver of the attack, empathy towards the attacker, so on and so forth.
+Additionally, different types of interventions could be tested and tailored depending on the spectrum on which one can be found in the foundations of moral reasoning, as proposed by Jonathan Haidt: Care/Harm, Fairness/Cheating, Loyalty/Betrayal, Authority/Subversion, Sanctity/Degradation, and Liberty/Oppression (J.
+Haidt, The Righteous Mind).
+Albeit for the sake of the sanity of our volunteers, we decided to create only two but broad categories and let them decide based on the context of the conversation, how they want to respond to the attacker.
 

### 2021-09-08 paperDraft/paperDraft.tex

@@
 \hypersetup{
-  pdftitle={Nesta attacks study},
+  pdftitle={Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online},
   pdfauthor={Patrycja Tempska and Rafal Urbaniak},
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 
-\title{Nesta attacks study}
+\title{Investigating the impact of interventionist causal approach on
+the study of verbal aggression and discrimination online}
 \author{Patrycja Tempska and Rafal Urbaniak}
@@
 \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DecValTok{2}\SpecialCharTok{+}\DecValTok{2} \CommentTok{\#use this formatting for chunks}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 4
-\end{verbatim}
 
@@
 
-Normative interventions can refer either to general social norms of
-civility and respect, community standards, a particular subreddit rule,
-or a descriptive norm among others. E.g. Insulting others is against
-Reddit's policy. Hey there, we do not call each other like that here.
-Empathetic interventions can refer to the emotional state of the
-recipient or the sender of the attack or both. They are designed to
-evoke an empathetic response. E.g. There is a human being on the other
-side who might be hurt by your words. I see you are frustrated but
-remember the human.
+\textbf{Empathetic interventions} In the first treatment condition,
+volunteers were encouraged to send empathy-inducing messages focusing
+either on the target of verbal aggression (e.g.~„Hey such words might
+hurt the other person''), stressing the common humanity aspect that we
+call share („We are all humans of flesh and blood''), or even infusing
+the intervention with the emphatic response to the attacker (Hey I
+understand your strong emotions\ldots''). At the core of the empathetic
+interventions, we put forth the notion that goes back to David Hume and
+Adam Smith. The first one conceived empathy (at the time referred to as
+sympathy) as mirroring the emotional state of another person. In the
+academic psychological literature, similar phenomenon was distinguished
+and coined in the term emotional contagion
+(\url{https://www.sciencedirect.com/topics/psychology/emotional-contagion}):
+``the process in which an observed behavioral change in one individual
+leads to the reflexive production of the same behavior by other
+individuals in close proximity, with the likely outcome of converging
+emotionally.'' For Adam Smith, sympathy consisted of visualizing how the
+sympathetic person would feel in the particular circumstances of the
+other --- thus here the process was based not so much on mirroring, but
+rather projecting my imagination of what it is like to be that person in
+a certain moment). Without further delving into the differentiation
+between those two, sympathy in both accounts is crucial in the
+constitution of human beings as social and moral creatures
+(\url{https://plato.stanford.edu/entries/empathy/}). It enables the
+emotional connection to others and concern for their well-being. In the
+psychological literature, various kinds of empathetic responses were
+distinguished - the aforementioned emotional contagion, affective/proper
+empathy, sympathy, personal distress or cognitive empathy
+((\url{https://plato.stanford.edu/entries/empathy/}). During the
+experiment, we couldn't observe or measure whether the empathetic
+response indeed was evoked. Also, interventions that stated that ``such
+words might hurt the other person'' have the underlying assumption that
+the receiver of the attack might be hurt, but in reality that might not
+even be the case. Intuitively, and following the argumentation of Thomas
+Nagel in ``What is it like to be a bat?'' one can only imagine what it
+is like - but for me - to be a bat or to be a receiver of the attack. To
+each observed or imagined experience there is an array of subjective
+quality to actually experiencing it and in this way receiving a
+particular message might be met with a unique reception by each
+conscious being. Also, full epistemic access to the mind and body of
+another is impossible. But even though such access is impossible and
+putting aside the broad spectrum of phenomena related to empathetic
+response, our goal was by utilizing interventions referring to empathy
+in various forms, changing the behavior of the attacker - convincing him
+to refrain from using verbal aggression towards others. Whether the
+message indeed gave rise to empathy was not of importance - one can
+imagine a hypothetical scenario of a successful intervention in which
+the attacker changed his behavior long-term and stopped attacking
+others, hopefully as a result of interventions, but the empathetic
+response was not even evoked. The behavioral change could be induced by
+other motivations - e.g.~unwillingness from the exclusion from the
+community. Thus the goal is not to evoke empathy, but through empathetic
+interventions - substantially limiting the use of verbal aggression.
+
+\textbf{Normative interventions} Normative interventions were grounded
+in broadly defined norms and normative theories expressed via various
+means - either specific community guidelines imposed by Reddit or
+through ethics - deontology, virtue ethics. Whatever the strategy was
+used, it was supposed to express the unacceptability of verbal
+aggression in a direct or non-direct way.
+
+A more direct approach referred to deontology in which „actions are good
+or bad according to a clear set of rules''
+(\url{https://ethics.org.au/ethics-explainer-deontology/}). Such
+interventions could state that „we have a duty to respect each other
+during the discussions``, „we have a moral obligation to act in a civil
+manner while participating in online communities,'' „we shouldn't use ad
+personam in here''. The basic assumption behind those interventions is
+that there is something we ought to do or are morally required to do -
+and such actions are the right actions. There are also actions we ought
+not to do - and such actions are morally wrongful. This line of thinking
+can be traced back to Immanuel Kant who thought that all universal moral
+obligations can stem from categorical imperative: ``act only in
+accordance with that maxim through which you can at the same time will
+that it become a universal law'' (Groundwork of the Metaphysic of
+Morals).
+
+Yet other interventions were encouraged to be expressed in the light of
+virtue ethics and stressed the importance of adhering to or practicing
+certain virtues. Such a message was assumed to motivate the moral agent
+in the process of positive reinforcement and create a feeling of the
+desirability of certain behaviors, e.g.~„capacity to be respectful in a
+heated discussion is a virtue and requires hard work''. The core
+assumption here is that the virtue itself is not genetically inherited
+but is rather a potential or a disposition of a character that can be
+practice and mastered like a practical skill (even though as mentioned
+by Natasza Szutta in {[}cite her book about virtue ethics{]} virtues and
+practical skills share some fundamental differences). NS distinguished
+two types of virtues - affective and cognitive. Affective virtues
+encompass the emotions and feelings that play an important and positive
+role in morality and can act as a support in the course of becoming a
+virtuous man. A cognitive virtue relates to the intellectual aspect in
+which one knows how to act in certain situations and understands the
+rules of morally rightful actions (e.g.~what is kindness and how a kind
+man acts). Here, just as in the case of empathetic interventions, any
+attempts to measure whether the target of the intervention in the case
+of a positive outcome (behavioral change) indeed acted in a virtuous
+way. A virtue of kindness may manifest itself in particular behaviors
+but as such cannot be identified with the virtuous deed, as highlighted
+by Natasza Szutta. Although again, the goal of the experiment itself was
+to change the behavior of the attackers, and measuring whether
+particular messages contributed to more flourishing individuals in terms
+of virtue development and character creation lies beyond the scope of
+this work. Interventions could affect people either way - stimulate
+their moral reflections or limit their attacks due to consequentialist
+way of thinking and fear of potential outcomes (e.g.~being excluded from
+the community).
+
+Additionally, Reddit created their social etiquette called
+``Rediquette''
+(\url{https://www.reddithelp.com/hc/en-us/articles/205926439}) which is
+``an informal expression of the values of many redditors, as written by
+redditors themselves.'' All users are encouraged to abide by it and
+moderators of communities (called subreddits) existing as a part of the
+platform have the authority to exclude its members based either on the
+basis of breaking the rules of the reddiquette or any other local rules
+imposed by specific subreddit. Volunteers were encouraged to refer to
+those norms as well, citing specific points, for instance, ``Hey there,
+have you read the reddiquette? It says remember the human.'' or ``Let's
+recall the reddiquette and adhere to the same standards of behavior
+online that you follow in real life.''
+
+As we have seen, those two categories of interventions - normative and
+empathetic - encompass a whole variety of categories within. One might
+think that it would be useful to construct a more diverse set of
+treatment conditions in which we test each of the ethics or empathy
+differentiation separately - e.g.~one for virtue ethics, deontology,
+perhaps utilitarian approach, empathy toward the receiver of the attack,
+empathy towards the attacker, so on and so forth. Additionally,
+different types of interventions could be tested and tailored depending
+on the spectrum on which one can be found in the foundations of moral
+reasoning, as proposed by Jonathan Haidt: Care/Harm, Fairness/Cheating,
+Loyalty/Betrayal, Authority/Subversion, Sanctity/Degradation, and
+Liberty/Oppression (J. Haidt, The Righteous Mind). Albeit for the sake
+of the sanity of our volunteers, we decided to create only two but broad
+categories and let them decide based on the context of the conversation,
+how they want to respond to the attacker.
 

### 2021-09-08 visualisations/visualisePeriods.R
weekly attacks

@@ -58,6 +58,7 @@ periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "t
 
 periodsDF
 
+
 ggplot(periodsDF)+
   geom_line(aes(x=date, y = attacks, group = grp),
              alpha = 0.8, size = .6)+
@@ -83,15 +84,30 @@ ggplot(periodsDF)+
   annotate("text", label = "attacks:", x = as.Date(startDate)-30, y = 215, hjust =0 )
 
 
+ggsave("images/periods.pdf", width = 20, height = 15, units = "cm", dpi = 450)  
 
 
 
+periodsDF$weekdays <-  weekdays(as.Date(periodsDF$date))
+
+library(lubridate)
+periodsDF$weeks <-  week(as.Date(periodsDF$date))
 
 
+periodsDF$weekdays <- as.factor(periodsDF$weekdays)
+levels(periodsDF$weekdays) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday",
+                                "Saturday", "Sunday")
 
-periodsDF
 
-dateDF
+ggplot(periodsDF)+
+  geom_smooth(aes(x = weekdays, y = attacks, group =1))+
+  geom_line(aes(x = weekdays, y = attacks, group = weeks),alpha = 0.1)+
+  theme_tufte()+labs(title="Weekly attacks over six months", subtitle = "No weekly patterns")+xlab("")+
+  ylab("count")
+
+
+ggsave("images/weeklyPatterns.pdf", width = 20, height = 15, units = "cm", dpi = 450)  
+
 
 
 
@@ -106,9 +122,6 @@ periods <- ggplot(dateDF, aes(x=dates, y = points, color = periods, group = grp)
   labs(title = "Data collection periods", subtitle = "no line at data gaps", caption = "days with data: 81 (pre-treatment), 62 (treatment), 72 (post-treatment)")+
   scale_color_discrete(breaks=c("pre-treatment", "treatment", "post-treatment"))
 
-ggsave("images/periods.pdf", width = 20, height = 6, units = "cm", dpi = 450)  
-
-  
 
 table(periods)
 

### 2021-09-08 paperDraft/paperDraft.Rmd
some paragraphs added about causality from old writings - it's still chaotic though, need to improve

@@
 # Section Abstract 
-This article describes an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
+This article \todo{hm not sure whether abstract is neccessary in BA thesis but I will leave it here for now} describes an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
 Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
@@
 # Introduction
+
+We live in a world in which there is an abundance of data.
+Paraphrasing the phrase coined by Clive Humby, "data is the new oil" --- data has displaced oil and become the world’s most valuable resource.
+Albeit there are some fundamental differences between the two assets.
+Oil belongs to a very limited and finite resource, while data is growing at an exponential rate (cite: https://cloudtweaks.com/2015/03/how-much-data-is-produced-every-day/).
+The value of oil does not depend on its amount or the refinery processes - it's rather constant at a particular dynamic of market's supply and demand.
+Data and its value, on the contrary, is inherently tied to its amount and the "refinery process" - various tools and techniques for its discovery and analysis.
+In some cases, certain techniques can be used only if one has a sufficient (meaning enormous) data at one's disposal --- e.g.
+statistical methods like machine learning and deep learning \todo{@article{lecun2015deep,
+  title={Deep learning},
+  author={LeCun, Yann and Bengio, Yoshua and Hinton, Geoffrey},
+  journal={nature},
+  volume={521},
+  number={7553},
+  pages={436--444},
+  year={2015},
+  publisher={Nature Publishing Group}
+}}. 
+In the last couple of years, more and more researchers started to research and developed tools for causal discovery and inference.
+Unfortunately, although thinking in causal terms seems to be our inherent human capacity and one of our basic cognitive abilities, that is not necessarily the case with the majority of toolkits and statistical models developed to draw insight and correlations from data.
+In classical statistics, which is stripped of causality-related terms and reasoning, one cannot speak about causal effects, unless one deals with a randomized controlled experiment.
+This comprises one of the limits of the classical paradigm in statistics (among others such as arbitrary thresholds of statistical significance, p-hacking, disregard of prior information, and others which we will not discuss here).
+But often scientists conduct the so-called cross-sectional research, in which no variable is manipulated.
+In the language and toolkit of classical statistics in such cases we cannot conduct any causal inference.
+What we can measure using those methods is correlation, and, as frequently repeated, “correlation does not imply causation”.
+Correlation can be positive, negative, or there can be no correlation at all.
+A positive one implies that the increase of the value of one variable will influence the increase of another variables’ value.
+A negative correlation means that the change in values of two variables will diverge into separate directions --- one will increase and one will decrease alongside the first one.
+We can measure the strength of the correlation using various mathematical methods, where 1 or -1 means we are dealing with perfect correlation --- the value of one variable changes proportional to the value of another variable.
+But even though causation is necessarily connected with correlation, as already mentioned --- not every correlation implies causation.
+And as we will see, ignoring the causal story behind the data and relationships between the variables might lead to far-reaching consequences.
+Drawing false causal conclusions out of data can lead to false accusations of discrimination (...here I will add something more once I decide which examples to choose).
+This is especially problematic if we take into consideration the fact that statisticians and people in general naturally think in causal terms and spurious interpretations of studies occur frequently.
+On the other hand, a conservative approach of many classical statisticians led to a long-living debate on whether smoking causes cancer, lasting for over 20 years (to check).
+One of the reasons for such a fierce debate was the lack of a causal framework, which was still in its infancy at that time.
+Framework of tools with which we could validate or invalidate assumptions about the existence of the potential confounder - a vari- able causing both craving cigarettes and lung cancer (e.g.
+some genetic factor), creating a spurious correlation between cigarettes and lung cancer.
+Modeling causality and moving beyond traditional statistics is a relatively young endeavor.
+One of the pioneers of the work on causality is Judea Pearl.
+As he describes, causality and traditional statistics are governed by opposing ways of thinking.
+While statistics might be described as “study of methods of the reduction of data” (quoted here was Fischer I think, need to check), causality requires the incorporation of an extra layer - the understanding or prior knowl- edge (assumptions) about the process that generate the data in the first place.
+Classical statistics might be described here as a “model-free approach,” just as Artificial Intelligence methods based on machine learning/deep learning, in which no prior knowledge can be taken into account.
+
+In this paper, I will show how mathematical methods for causality modeling can be applied to discover how different variables affect each other, moving beyond traditional correlation.
+Data used for analysis comes from an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
+Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
+Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks.
+Volunteers after receiving notifications employed interventions grounded in philosophy.
+There were two broad categories - one based on norms (deontology, virtue ethics among others) and second based on empathy (inspired by notions of David Hume and Adam Smith).
+
 Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives.

### 2021-09-08 paperDraft/paperDraft.tex
some paragraphs added about causality from old writings - it's still chaotic though, need to improve

@@
 
-This article describes an experimental intervention study conducted in a
+This article
+\todo{hm not sure whether abstract is neccessary in BA thesis but I will leave it here for now}
+describes an experimental intervention study conducted in a
 naturalistic, digital setting (Q\&A forum on Reddit), utilizing a
@@
 \section{Introduction}\label{introduction}}
+
+We live in a world in which there is an abundance of data. Paraphrasing
+the phrase coined by Clive Humby, ``data is the new oil'' --- data has
+displaced oil and become the world's most valuable resource. Albeit
+there are some fundamental differences between the two assets. Oil
+belongs to a very limited and finite resource, while data is growing at
+an exponential rate (cite:
+\url{https://cloudtweaks.com/2015/03/how-much-data-is-produced-every-day/}).
+The value of oil does not depend on its amount or the refinery processes
+- it's rather constant at a particular dynamic of market's supply and
+demand. Data and its value, on the contrary, is inherently tied to its
+amount and the ``refinery process'' - various tools and techniques for
+its discovery and analysis. In some cases, certain techniques can be
+used only if one has a sufficient (meaning enormous) data at one's
+disposal --- e.g.~statistical methods like machine learning and deep
+learning \todo{@article{lecun2015deep,
+  title={Deep learning},
+  author={LeCun, Yann and Bengio, Yoshua and Hinton, Geoffrey},
+  journal={nature},
+  volume={521},
+  number={7553},
+  pages={436--444},
+  year={2015},
+  publisher={Nature Publishing Group}
+}}. In the last couple of years, more and more researchers started to
+research and developed tools for causal discovery and inference.
+Unfortunately, although thinking in causal terms seems to be our
+inherent human capacity and one of our basic cognitive abilities, that
+is not necessarily the case with the majority of toolkits and
+statistical models developed to draw insight and correlations from data.
+In classical statistics, which is stripped of causality-related terms
+and reasoning, one cannot speak about causal effects, unless one deals
+with a randomized controlled experiment. This comprises one of the
+limits of the classical paradigm in statistics (among others such as
+arbitrary thresholds of statistical significance, p-hacking, disregard
+of prior information, and others which we will not discuss here). But
+often scientists conduct the so-called cross-sectional research, in
+which no variable is manipulated. In the language and toolkit of
+classical statistics in such cases we cannot conduct any causal
+inference. What we can measure using those methods is correlation, and,
+as frequently repeated, ``correlation does not imply causation.''
+Correlation can be positive, negative, or there can be no correlation at
+all. A positive one implies that the increase of the value of one
+variable will influence the increase of another variables' value. A
+negative correlation means that the change in values of two variables
+will diverge into separate directions --- one will increase and one will
+decrease alongside the first one. We can measure the strength of the
+correlation using various mathematical methods, where 1 or -1 means we
+are dealing with perfect correlation --- the value of one variable
+changes proportional to the value of another variable. But even though
+causation is necessarily connected with correlation, as already
+mentioned --- not every correlation implies causation. And as we will
+see, ignoring the causal story behind the data and relationships between
+the variables might lead to far-reaching consequences. Drawing false
+causal conclusions out of data can lead to false accusations of
+discrimination (\ldots here I will add something more once I decide
+which examples to choose). This is especially problematic if we take
+into consideration the fact that statisticians and people in general
+naturally think in causal terms and spurious interpretations of studies
+occur frequently. On the other hand, a conservative approach of many
+classical statisticians led to a long-living debate on whether smoking
+causes cancer, lasting for over 20 years (to check). One of the reasons
+for such a fierce debate was the lack of a causal framework, which was
+still in its infancy at that time. Framework of tools with which we
+could validate or invalidate assumptions about the existence of the
+potential confounder - a vari- able causing both craving cigarettes and
+lung cancer (e.g.~some genetic factor), creating a spurious correlation
+between cigarettes and lung cancer. Modeling causality and moving beyond
+traditional statistics is a relatively young endeavor. One of the
+pioneers of the work on causality is Judea Pearl. As he describes,
+causality and traditional statistics are governed by opposing ways of
+thinking. While statistics might be described as ``study of methods of
+the reduction of data'' (quoted here was Fischer I think, need to
+check), causality requires the incorporation of an extra layer - the
+understanding or prior knowl- edge (assumptions) about the process that
+generate the data in the first place. Classical statistics might be
+described here as a ``model-free approach,'' just as Artificial
+Intelligence methods based on machine learning/deep learning, in which
+no prior knowledge can be taken into account.
+
+In this paper, I will show how mathematical methods for causality
+modeling can be applied to discover how different variables affect each
+other, moving beyond traditional correlation. Data used for analysis
+comes from an experimental intervention study conducted in a
+naturalistic, digital setting (Q\&A forum on Reddit), utilizing a
+collective intelligence approach to content moderation and reduction of
+the level of verbal aggression among a selected group of Reddit users
+who regularly attack other community members. Collective Intelligence in
+this sense means exploring the collaboration between human and machine
+intelligence to develop solutions to social challenges. Artificial
+Intelligence was used to detect verbal aggression (personal attacks) and
+notify human volunteers about attacks. Volunteers after receiving
+notifications employed interventions grounded in philosophy. There were
+two broad categories - one based on norms (deontology, virtue ethics
+among others) and second based on empathy (inspired by notions of David
+Hume and Adam Smith).
 

### 2021-09-09 bayesianModelsDiff.R
bayesian models of diff

@@ -253,6 +253,21 @@ LotsOfInteractionsModel3Props <- quap(
 
 
 
+LotsOfInteractionsModel3PropsUlam <- ulam(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,0.5),
+    bADS[groupID] ~ dnorm(0,.5),
+    bADSIC ~ dnorm(0,.5),
+    bCBS[groupID] ~ dnorm(0,.5),
+    bIT[groupID] ~ dnorm(0,.5),
+    bIC[groupID] ~ dnorm(0,.5),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
 
 precis(LotsOfInteractionsModel3Props, depth = 2)
 

### 2021-09-09 bayesianAnalysis/predictionsInteractions.R
interaction plots

@@ -10,6 +10,7 @@ summaries$AAS <- standardize(summaries$AA)
 summaries$CAS <- standardize(summaries$CA)
 summaries$CDS <- standardize(summaries$CD)
 summaries$ADS <- standardize(summaries$AD)
+summaries$group <- as.factor(summaries$group)
 summaries$groupID <-  as.integer( as.factor(summaries$group) )
 
 
@@ -19,11 +20,27 @@ LotsOfInteractionsModel3 <- quap(
     AAS ~ dnorm( mu, sigma ),
     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
     a ~ dnorm (0,0.5),
-    bADS[groupID] ~ dnorm(0,.5),
-    bADSIC ~ dnorm(0,.5),
-    bCBS[groupID] ~ dnorm(0,.5),
-    bIT[groupID] ~ dnorm(0,.5),
-    bIC[groupID] ~ dnorm(0,.5),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+
+LotsOfInteractionsModel3ulam <- ulam(
+  alist(
+    AAS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,0.5),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
     sigma  ~ dexp(1)
   ), 
   data = summaries
@@ -31,63 +48,141 @@ LotsOfInteractionsModel3 <- quap(
 
 
 
-head(summaries)
-
-
-
-
-
-mean(summaries$IC[summaries$groupID != 1])
-
-ADS <- seq(-2,-1, by = 0.1)
[…]

### 2021-09-09 bayesianModelsDiff.R

@@ -12,13 +12,6 @@ summaries$CDS <- standardize(summaries$CD)
 summaries$ADS <- standardize(summaries$AD)
 summaries$groupID <-  as.integer( as.factor(summaries$group) )
 
-summaries$ApropS <- standardize(summaries$AA/summaries$AB)
-
-
-ggplot(summaries)+geom_histogram(aes(x=ApropS, fill = group), bins = 100)
-
-
-head(summaries)
 
 
 

### 2021-09-09 predictionInteractionsProps.R

@@ -1,0 +1,384 @@
+source("utils/plotPriors.R")
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+summaries$group <- as.factor(summaries$group)
+summaries$groupID <-  as.integer( as.factor(summaries$group) )
+summaries$ApropS <- standardize(summaries$AA/summaries$AB)
+
+
+ggplot()+geom_histogram(aes(x=summaries$AdiffS))
+
+noChange <-(0 - mean(summaries$Adiff))/sd(summaries$Adiff)
+averageChange <- mean(summaries$Adiff[summaries$group == "control"])
+
+
+# InteractionsModelDiff <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ), 
+#   data = summaries
+# )
+
+#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")
+
+InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
+
+# 
+# InteractionsModelDiffSD1 <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+#     a ~ dnorm (0,1),
+#     bADS[groupID] ~ dnorm(0,1),
[…]

### 2021-09-09 predictionInteractionsProps.R
r

@@ -37,6 +37,9 @@ averageChange <- mean(summaries$Adiff[summaries$group == "control"])
 
 InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
 
+
+precis(InteractionsModelDiff, depth = 2)
+
 # 
 # InteractionsModelDiffSD1 <- ulam(
 #   alist(

### 2021-09-09 visualisations/exploration.R

@@ -132,4 +132,11 @@ ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+geom_jit
 ggplot(summaries, aes(x = IC, y = Adiff, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-100,100))
 
 
+ggplot(summaries, aes(x = IC, y = Adiff, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2, method = "lm")+xlim(c(0,20))+ylim(c(-50,50))
+
+ggplot(summaries, aes(x = IC, y = Adiff, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2)+xlim(c(0,20))+ylim(c(-50,50))
+
+
+
+ggplot(summaries, aes(x = IC, y = Adiff, color = group, fill = group))+geom_jitter(alpha = 0.6)+theme_tufte()+geom_smooth(alpha = 0.2)+xlim(c(0,20))+ylim(c(-100,100))
 

### 2021-09-09 paperDraft/paperDraft.Rmd
changes made to philosophical grounding of intevrentions

@@
 ---
-title: "Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online"
+title: "Investigating the impact of interventionist causal approach on the study of verbal aggression online"
 author: "Patrycja Tempska and Rafal Urbaniak"
@@
 
-# Section Abstract 
-This article \todo{hm not sure whether abstract is neccessary in BA thesis but I will leave it here for now} describes an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
-Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
-Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks.
-Volunteers after receiving notifications employed interventions based on norm or empathy promotion.
-We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' level significantly decreased.
-
 \vspace{1mm}
@@
 We live in a world in which there is an abundance of data.
-Paraphrasing the phrase coined by Clive Humby, "data is the new oil" --- data has displaced oil and become the world’s most valuable resource.
+Referring the phrase coined by Clive Humby, "data is the new oil" --- data has displaced oil and become the world’s most valuable resource.
 Albeit there are some fundamental differences between the two assets.
@@
 }}. 
-In the last couple of years, more and more researchers started to research and developed tools for causal discovery and inference.
+In the last couple of years, more and more industry and academia representatives alike started to research and develop tools for causal discovery and inference.
 Unfortunately, although thinking in causal terms seems to be our inherent human capacity and one of our basic cognitive abilities, that is not necessarily the case with the majority of toolkits and statistical models developed to draw insight and correlations from data.
@@
 But even though causation is necessarily connected with correlation, as already mentioned --- not every correlation implies causation.
-And as we will see, ignoring the causal story behind the data and relationships between the variables might lead to far-reaching consequences.
-Drawing false causal conclusions out of data can lead to false accusations of discrimination (...here I will add something more once I decide which examples to choose).
 This is especially problematic if we take into consideration the fact that statisticians and people in general naturally think in causal terms and spurious interpretations of studies occur frequently.
-On the other hand, a conservative approach of many classical statisticians led to a long-living debate on whether smoking causes cancer, lasting for over 20 years (to check).
+On the other hand, a conservative approach of many classical statisticians led to a long-living debate on whether smoking causes cancer, lasting for over 20 years.
 One of the reasons for such a fierce debate was the lack of a causal framework, which was still in its infancy at that time.
-Framework of tools with which we could validate or invalidate assumptions about the existence of the potential confounder - a vari- able causing both craving cigarettes and lung cancer (e.g.
+Framework of tools with which we could validate or invalidate assumptions about the existence of the potential confounder --- a variable causing both craving cigarettes and lung cancer (e.g.
 some genetic factor), creating a spurious correlation between cigarettes and lung cancer.
@@
 As he describes, causality and traditional statistics are governed by opposing ways of thinking.
-While statistics might be described as “study of methods of the reduction of data” (quoted here was Fischer I think, need to check), causality requires the incorporation of an extra layer - the understanding or prior knowl- edge (assumptions) about the process that generate the data in the first place.
+While statistics might be described as “study of methods of the reduction of data”, causality requires the incorporation of an extra layer --- the understanding or prior knowledge (assumptions) about the process that generate the data in the first place.
 Classical statistics might be described here as a “model-free approach,” just as Artificial Intelligence methods based on machine learning/deep learning, in which no prior knowledge can be taken into account.
 
-In this paper, I will show how mathematical methods for causality modeling can be applied to discover how different variables affect each other, moving beyond traditional correlation.
-Data used for analysis comes from an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
+In this paper, I will show how mathematical methods for process modeling which includes assumptions about causal connections can be applied to discover how different variables affect each other, moving beyond classical statistics.
+Looking at the analysis from two perspectives --- traditional (classical, frequentist statistics) and bayesian -- we will see the advantage of the second paradigm in learning about the world based on the data we have at our disposal.
+Data used for analysis concerned in this paper comes from an experimental intervention study conducted in a naturalistic, digital setting (Q&A forum on Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members.
 Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges.
 Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks.
-Volunteers after receiving notifications employed interventions grounded in philosophy.
-There were two broad categories - one based on norms (deontology, virtue ethics among others) and second based on empathy (inspired by notions of David Hume and Adam Smith).
+Volunteers after receiving notifications employed interventions inspired in its underlying principles in philosophy and psychology.
+There were two broad categories of interventions - one based on norms (deontology, virtue ethics among others) and the second based on empathy (inspired by notions of David Hume and Adam Smith).
 
-Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives.
+One might also wonder about the motivations for conducting such an experiment.
+Much effort has been made in order to tackle the problem of verbal aggression and harassment online, but looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives.
 The problem got exacerbated in the midst of the COVID19 pandemic, during which the majority of our social life moved to cyberspace.
@@
 Those changes, as argued by @gerrard2020covid19, can be seen as a serious red flag in terms of safety for all users on online platforms.
+That is why in the paper I will also try to sketch a landscape of current moderation techniques through a critical lens.
 
@@
 In our paper and in the theoretical underpinnings of the experiment itself, we will be relying on a collective intelligence scope proposed by Nesta, an innovation foundation (https://www.nesta.org.uk), which focuses on a collaboration between human and machine intelligence to develop innovative solutions to social challenges.
-(Gdzieś stopka(?): Samurai Labs has been one of the 15 recipients of the second round of collective intelligence grants awarded by Nesta: https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/)
 
@@
 \textbf{Empathetic interventions}
-In the first treatment condition, volunteers were encouraged to send empathy-inducing messages focusing either on the target of verbal aggression (e.g.
+In the first treatment condition, volunteers were asked to send empathy-inducing messages focusing either on the target of verbal aggression (e.g.
 „Hey such words might hurt the other person”), stressing the common humanity aspect that we call share („We are all humans of flesh and blood”), or even infusing the intervention with the emphatic response to the attacker (Hey I understand your strong emotions…”).
@@
 (https://www.sciencedirect.com/topics/psychology/emotional-contagion): "the process in which an observed behavioral change in one individual leads to the reflexive production of the same behavior by other individuals in close proximity, with the likely outcome of converging emotionally".
+
 For Adam Smith, sympathy consisted of visualizing how the sympathetic person would feel in the particular circumstances of the other --- thus here the process was based not so much on mirroring, but rather projecting my imagination of what it is like to be that person in a certain moment).
@@
 It enables the emotional connection to others and concern for their well-being.
+The interventions were supposed to serve the role of empathetic response enablers --- reminding the person in front of the screen that there is a real human being on the other side.
+
 In the psychological literature, various kinds of empathetic responses were distinguished - the aforementioned emotional contagion, affective/proper empathy, sympathy, personal distress or cognitive empathy ((https://plato.stanford.edu/entries/empathy/).
-During the experiment, we couldn’t observe or measure whether the empathetic response indeed was evoked.
+During the experiment, we could not observe or measure whether the empathetic response indeed was evoked.
+The study was conducted in a digital setting --- interventions were most likely read in the private space, in front of personal computers or smartphones.
+Even if we would change the setting to a lab, differentiating and measuring empathy is not trivial if not impossible (to check).
+
 Also, interventions that stated that "such words might hurt the other person" have the underlying assumption that the receiver of the attack might be hurt, but in reality that might not even be the case.
-Intuitively, and following the argumentation of Thomas Nagel in “What is it like to be a bat?” one can only imagine what it is like - but for me - to be a bat or to be a receiver of the attack.
+Intuitively, and following the argumentation of Thomas Nagel in “What is it like to be a bat?” one can only imagine what it is like --- but for me --- to be a bat or to be a receiver of the attack.
 To each observed or imagined experience there is an array of subjective quality to actually experiencing it and in this way receiving a particular message might be met with a unique reception by each conscious being.
 Also, full epistemic access to the mind and body of another is impossible.
-But even though such access is impossible and putting aside the broad spectrum of phenomena related to empathetic response, our goal was by utilizing interventions referring to empathy in various forms, changing the behavior of the attacker - convincing him to refrain from using verbal aggression towards others.
-Whether the message indeed gave rise to empathy was not of importance - one can imagine a hypothetical scenario of a successful intervention in which the attacker changed his behavior long-term and stopped attacking others, hopefully as a result of interventions, but the  empathetic response was not even evoked.
-The behavioral change could be induced by other motivations - e.g.
+
+But even though such access is impossible and putting aside the broad spectrum of phenomena related to empathetic response, our goal was by utilizing interventions referring to empathy in various forms, changing the behavior of the attacker --- convincing him to refrain from using verbal aggression towards others.
+Whether the message indeed gave rise to empathy was not of importance --- one can imagine a hypothetical scenario of a successful intervention in which the attacker changed his behavior long-term and stopped attacking others, hopefully as a result of interventions, but the empathetic response was not even evoked.
+The behavioral change could be induced by other motivations --- e.g.
 unwillingness from the exclusion from the community.
-Thus the goal is not to evoke empathy, but through empathetic interventions - substantially limiting the use of verbal aggression.
+Thus the goal is not to evoke empathy, but through empathetic interventions --- substantially limit the use of verbal aggression among study group members.
 
 \textbf{Normative interventions}
-Normative interventions were grounded in broadly defined norms and normative theories expressed via various means - either specific community guidelines imposed by Reddit or through ethics - deontology, virtue ethics.
+In the second treatment condition, volunteers were asked to send norms-inducing messages written on the grounds of deontology (e.g.
+„we have a duty to respect each other during the discussions"), virtue ethics (e.g.
+„capacity to be respectful in a heated discussion is a virtue and requires hard work”) or Reddit's community guideline (e.g.
+"Let's recall the reddiquette and adhere to the same standards of behavior online that you follow in real life").
+
 Whatever the strategy was used, it was supposed to express the unacceptability of verbal aggression in a direct or non-direct way.
-
 A more direct approach referred to deontology in which „actions are good or bad according to a clear set of rules” (https://ethics.org.au/ethics-explainer-deontology/).
-Such interventions could state that „we have a duty to respect each other during the discussions", „we have a moral obligation to act in a civil manner while participating in online communities”, „we shouldn’t use ad personam in here”.
-The basic assumption behind those interventions is that there is something we ought to do or are morally required to do - and such actions are the right actions.
-There are also actions we ought not to do - and such actions are morally wrongful.
+The basic assumption behind those interventions is that there is something we ought to do or are morally required to do --- and such actions are the right actions.
+There are also actions we ought not to do --- and such actions are morally wrongful.
 This line of thinking can be traced back to Immanuel Kant who thought that all universal moral obligations can stem from categorical imperative: “act only in accordance with that maxim through which you can at the same time will that it become a universal law” (Groundwork of the Metaphysic of Morals).
 
-Yet other interventions were encouraged to be expressed in the light of virtue ethics and stressed the importance of adhering to or practicing certain virtues.
-Such a message was assumed to motivate the moral agent in the process of positive reinforcement and create a feeling of the desirability of certain behaviors, e.g.
-„capacity to be respectful in a heated discussion is a virtue and requires hard work”.
+In the psychological literature, Robert B.
+Cialdini distinguished three types of norms that he found to be effective in guiding human action: descriptive norms (focused on the perception of how the majority of people would behave), injunctive (based on the perception of how the majority of people would approve or disapprove certain conduct), or personal norms (based on the perception of how a particular person would approve or disapprove certain behavior) CITE: https://www.sciencedirect.com/science/article/abs/pii/S0065260108603305.
+Although interventions written on the grounds of duties and deontology cannot be reduced to any of the above, since following Hume's guillotine --- from the fact that the majority of people are respectful does not follow the normative statement of civility --- I hoped that expressing a universal normative statement will be even more powerful and potentially spawn an interpretation of social acceptability or unacceptability of certain behavior.
+
+Yet other interventions in normative group were encouraged to be expressed in the light of virtue ethics and stressed the importance of adhering to or practicing certain virtues.
+Such a message was assumed to motivate the moral agent in the process of positive reinforcement and create a feeling of the desirability of certain behaviors, like kindness and civility.
 The core assumption here is that the virtue itself is not genetically inherited but is rather a potential or a disposition of a character that can be practice and mastered like a practical skill (even though as mentioned by Natasza Szutta in [cite her book about virtue ethics] virtues and practical skills share some fundamental differences).
@@
 what is kindness and how a kind man acts).
+
 Here, just as in the case of empathetic interventions, any attempts to measure whether the target of the intervention in the case of a positive outcome (behavioral change) indeed acted in a virtuous way.
@@
 It says remember the human".
-or "Let's recall the reddiquette and adhere to the same standards of behavior online that you follow in real life".
 
@@
 Haidt, The Righteous Mind).
-Albeit for the sake of the sanity of our volunteers, we decided to create only two but broad categories and let them decide based on the context of the conversation, how they want to respond to the attacker.
+Albeit for the sake of the sanity of our volunteers, we decided to create only two but broad categories and let volunteers decide based on the context of the conversation, how they want to respond to the attacker.
 

### 2021-09-09 paperDraft/paperDraft.tex
changes made to philosophical grounding of intevrentions

--- 2021-09-08 paperDraft/paperDraft.tex
@@
 \hypersetup{
-  pdftitle={Investigating the impact of interventionist causal approach on the study of verbal aggression and discrimination online},
+  pdftitle={Investigating the impact of interventionist causal approach on the study of verbal aggression online},
   pdfauthor={Patrycja Tempska and Rafal Urbaniak},
@@
 \title{Investigating the impact of interventionist causal approach on
-the study of verbal aggression and discrimination online}
+the study of verbal aggression online}
 \author{Patrycja Tempska and Rafal Urbaniak}
@@
 
-\hypertarget{section-abstract}{%
-\section{Section Abstract}\label{section-abstract}}
-
-This article describes an experimental intervention study conducted in a
-naturalistic, digital setting (Q\&A forum on Reddit), utilizing a
-collective intelligence approach to content moderation and reduction of
-the level of verbal aggression among a selected group of Reddit users
-who regularly attack other community members. Collective Intelligence in
-this sense means exploring the collaboration between human and machine
-intelligence to develop solutions to social challenges. Artificial
-Intelligence was used to detect verbal aggression (personal attacks) and
-notify human volunteers about attacks. Volunteers after receiving
-notifications employed interventions based on norm or empathy promotion.
-We find that only those who were sanctioned with norms-inducing
-interventions had their personal attacks' level significantly decreased.
-
 \vspace{1mm}
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Although much effort has been made in order to tackle the problem of
-verbal aggression and harassment online, looking at various reports and
-surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
+\textbackslash section Introduction
+
+We live in a world in which there is an abundance of data. Referring the
+phrase coined by Clive Humby, ``data is the new oil'' --- data has
+displaced oil and become the world's most valuable resource. Albeit
+there are some fundamental differences between the two assets. Oil
+belongs to a very limited and finite resource, while data is growing at
+an exponential rate (cite:
+\url{https://cloudtweaks.com/2015/03/how-much-data-is-produced-every-day/}).
+The value of oil does not depend on its amount or the refinery processes
+- it's rather constant at a particular dynamic of market's supply and
+demand. Data and its value, on the contrary, is inherently tied to its
+amount and the ``refinery process'' - various tools and techniques for
+its discovery and analysis. In some cases, certain techniques can be
+used only if one has a sufficient (meaning enormous) data at one's
+disposal --- e.g.~statistical methods like machine learning and deep
+learning \todo{@article{lecun2015deep,
+  title={Deep learning},
+  author={LeCun, Yann and Bengio, Yoshua and Hinton, Geoffrey},
+  journal={nature},
+  volume={521},
+  number={7553},
+  pages={436--444},
+  year={2015},
+  publisher={Nature Publishing Group}
+}}. In the last couple of years, more and more industry and academia
+representatives alike started to research and develop tools for causal
+discovery and inference. Unfortunately, although thinking in causal
+terms seems to be our inherent human capacity and one of our basic
+cognitive abilities, that is not necessarily the case with the majority
+of toolkits and statistical models developed to draw insight and
+correlations from data. In classical statistics, which is stripped of
+causality-related terms and reasoning, one cannot speak about causal
+effects, unless one deals with a randomized controlled experiment. This
+comprises one of the limits of the classical paradigm in statistics
+(among others such as arbitrary thresholds of statistical significance,
+p-hacking, disregard of prior information, and others which we will not
+discuss here). But often scientists conduct the so-called
+cross-sectional research, in which no variable is manipulated. In the
+language and toolkit of classical statistics in such cases we cannot
+conduct any causal inference. What we can measure using those methods is
+correlation, and, as frequently repeated, ``correlation does not imply
+causation.'' Correlation can be positive, negative, or there can be no
+correlation at all. A positive one implies that the increase of the
+value of one variable will influence the increase of another variables'
+value. A negative correlation means that the change in values of two
+variables will diverge into separate directions --- one will increase
+and one will decrease alongside the first one. We can measure the
+strength of the correlation using various mathematical methods, where 1
+or -1 means we are dealing with perfect correlation --- the value of one
+variable changes proportional to the value of another variable. But even
+though causation is necessarily connected with correlation, as already
+mentioned --- not every correlation implies causation. This is
+especially problematic if we take into consideration the fact that
+statisticians and people in general naturally think in causal terms and
+spurious interpretations of studies occur frequently. On the other hand,
+a conservative approach of many classical statisticians led to a
+long-living debate on whether smoking causes cancer, lasting for over 20
+years. One of the reasons for such a fierce debate was the lack of a
+causal framework, which was still in its infancy at that time. Framework
+of tools with which we could validate or invalidate assumptions about
+the existence of the potential confounder --- a variable causing both
+craving cigarettes and lung cancer (e.g.~some genetic factor), creating
+a spurious correlation between cigarettes and lung cancer. Modeling
+causality and moving beyond traditional statistics is a relatively young
+endeavor. One of the pioneers of the work on causality is Judea Pearl.
+As he describes, causality and traditional statistics are governed by
+opposing ways of thinking. While statistics might be described as
+``study of methods of the reduction of data,'' causality requires the
+incorporation of an extra layer --- the understanding or prior knowledge
+(assumptions) about the process that generate the data in the first
+place. Classical statistics might be described here as a ``model-free
+approach,'' just as Artificial Intelligence methods based on machine
+learning/deep learning, in which no prior knowledge can be taken into
+account.
+
+In this paper, I will show how mathematical methods for process modeling
+which includes assumptions about causal connections can be applied to
+discover how different variables affect each other, moving beyond
+classical statistics. Looking at the analysis from two perspectives ---
+traditional (classical, frequentist statistics) and bayesian -- we will
+see the advantage of the second paradigm in learning about the world
+based on the data we have at our disposal. Data used for analysis
+concerned in this paper comes from an experimental intervention study
+conducted in a naturalistic, digital setting (Q\&A forum on Reddit),
+utilizing a collective intelligence approach to content moderation and
+reduction of the level of verbal aggression among a selected group of
+Reddit users who regularly attack other community members. Collective
+Intelligence in this sense means exploring the collaboration between
+human and machine intelligence to develop solutions to social
+challenges. Artificial Intelligence was used to detect verbal aggression
+(personal attacks) and notify human volunteers about attacks. Volunteers
+after receiving notifications employed interventions inspired in its
+underlying principles in philosophy and psychology. There were two broad
+categories of interventions - one based on norms (deontology, virtue
+ethics among others) and the second based on empathy (inspired by
+notions of David Hume and Adam Smith).
+
+One might also wonder about the motivations for conducting such an
+experiment. Much effort has been made in order to tackle the problem of
+verbal aggression and harassment online, but looking at various reports
+and surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
 Vogels, 2021), it remains a common hindrance for people engaging with
@@
 Those changes, as argued by Gerrard (2020), can be seen as a serious red
-flag in terms of safety for all users on online platforms.
+flag in terms of safety for all users on online platforms. That is why
+in the paper I will also try to sketch a landscape of current moderation
+techniques through a critical lens.
 
@@
 between human and machine intelligence to develop innovative solutions
-to social challenges. (Gdzieś stopka(?): Samurai Labs has been one of
-the 15 recipients of the second round of collective intelligence grants
-awarded by Nesta:
-\url{https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/})
+to social challenges.
 
@@
 \textbf{Empathetic interventions} In the first treatment condition,
-volunteers were encouraged to send empathy-inducing messages focusing
-either on the target of verbal aggression (e.g.~„Hey such words might
-hurt the other person''), stressing the common humanity aspect that we
-call share („We are all humans of flesh and blood''), or even infusing
-the intervention with the emphatic response to the attacker (Hey I
+volunteers were asked to send empathy-inducing messages focusing either
+on the target of verbal aggression (e.g.~„Hey such words might hurt the
+other person''), stressing the common humanity aspect that we call share
+(„We are all humans of flesh and blood''), or even infusing the
+intervention with the emphatic response to the attacker (Hey I
 understand your strong emotions\ldots''). At the core of the empathetic
@@
 individuals in close proximity, with the likely outcome of converging
-emotionally.'' For Adam Smith, sympathy consisted of visualizing how the
-sympathetic person would feel in the particular circumstances of the
-other --- thus here the process was based not so much on mirroring, but
-rather projecting my imagination of what it is like to be that person in
-a certain moment). Without further delving into the differentiation
+emotionally.''
+
+For Adam Smith, sympathy consisted of visualizing how the sympathetic
+person would feel in the particular circumstances of the other --- thus
+here the process was based not so much on mirroring, but rather
+projecting my imagination of what it is like to be that person in a
+certain moment). Without further delving into the differentiation
 between those two, sympathy in both accounts is crucial in the
@@
 (\url{https://plato.stanford.edu/entries/empathy/}). It enables the
-emotional connection to others and concern for their well-being. In the
-psychological literature, various kinds of empathetic responses were
-distinguished - the aforementioned emotional contagion, affective/proper
-empathy, sympathy, personal distress or cognitive empathy
-((\url{https://plato.stanford.edu/entries/empathy/}). During the
-experiment, we couldn't observe or measure whether the empathetic
-response indeed was evoked. Also, interventions that stated that ``such
-words might hurt the other person'' have the underlying assumption that
-the receiver of the attack might be hurt, but in reality that might not
-even be the case. Intuitively, and following the argumentation of Thomas
-Nagel in ``What is it like to be a bat?'' one can only imagine what it
-is like - but for me - to be a bat or to be a receiver of the attack. To
-each observed or imagined experience there is an array of subjective
-quality to actually experiencing it and in this way receiving a
-particular message might be met with a unique reception by each
-conscious being. Also, full epistemic access to the mind and body of
-another is impossible. But even though such access is impossible and
-putting aside the broad spectrum of phenomena related to empathetic
-response, our goal was by utilizing interventions referring to empathy
-in various forms, changing the behavior of the attacker - convincing him
-to refrain from using verbal aggression towards others. Whether the
-message indeed gave rise to empathy was not of importance - one can
-imagine a hypothetical scenario of a successful intervention in which
-the attacker changed his behavior long-term and stopped attacking
-others, hopefully as a result of interventions, but the empathetic
-response was not even evoked. The behavioral change could be induced by
-other motivations - e.g.~unwillingness from the exclusion from the
-community. Thus the goal is not to evoke empathy, but through empathetic
-interventions - substantially limiting the use of verbal aggression.
-
-\textbf{Normative interventions} Normative interventions were grounded
-in broadly defined norms and normative theories expressed via various
-means - either specific community guidelines imposed by Reddit or
-through ethics - deontology, virtue ethics. Whatever the strategy was
-used, it was supposed to express the unacceptability of verbal
-aggression in a direct or non-direct way.
-
-A more direct approach referred to deontology in which „actions are good
+emotional connection to others and concern for their well-being. The
+interventions were supposed to serve the role of empathetic response
+enablers --- reminding the person in front of the screen that there is a
+real human being on the other side.
+
+In the psychological literature, various kinds of empathetic responses
+were distinguished - the aforementioned emotional contagion,
+affective/proper empathy, sympathy, personal distress or cognitive
+empathy ((\url{https://plato.stanford.edu/entries/empathy/}). During the
+experiment, we could not observe or measure whether the empathetic
+response indeed was evoked. The study was conducted in a digital setting
+--- interventions were most likely read in the private space, in front
+of personal computers or smartphones. Even if we would change the
+setting to a lab, differentiating and measuring empathy is not trivial
+if not impossible (to check).
+
+Also, interventions that stated that ``such words might hurt the other
+person'' have the underlying assumption that the receiver of the attack
+might be hurt, but in reality that might not even be the case.
+Intuitively, and following the argumentation of Thomas Nagel in ``What
+is it like to be a bat?'' one can only imagine what it is like --- but
+for me --- to be a bat or to be a receiver of the attack. To each
+observed or imagined experience there is an array of subjective quality
+to actually experiencing it and in this way receiving a particular
+message might be met with a unique reception by each conscious being.
+Also, full epistemic access to the mind and body of another is
+impossible.
+
+But even though such access is impossible and putting aside the broad
+spectrum of phenomena related to empathetic response, our goal was by
+utilizing interventions referring to empathy in various forms, changing
+the behavior of the attacker --- convincing him to refrain from using
+verbal aggression towards others. Whether the message indeed gave rise
+to empathy was not of importance --- one can imagine a hypothetical
+scenario of a successful intervention in which the attacker changed his
+behavior long-term and stopped attacking others, hopefully as a result
+of interventions, but the empathetic response was not even evoked. The
+behavioral change could be induced by other motivations ---
+e.g.~unwillingness from the exclusion from the community. Thus the goal
+is not to evoke empathy, but through empathetic interventions ---
+substantially limit the use of verbal aggression among study group
+members.
+
+\textbf{Normative interventions} In the second treatment condition,
+volunteers were asked to send norms-inducing messages written on the
+grounds of deontology (e.g.~„we have a duty to respect each other during
+the discussions``), virtue ethics (e.g.~„capacity to be respectful in a
+heated discussion is a virtue and requires hard work'') or Reddit's
+community guideline (e.g.~``Let's recall the reddiquette and adhere to
+the same standards of behavior online that you follow in real life'').
+
+Whatever the strategy was used, it was supposed to express the
+unacceptability of verbal aggression in a direct or non-direct way. A
+more direct approach referred to deontology in which „actions are good
 or bad according to a clear set of rules''
-(\url{https://ethics.org.au/ethics-explainer-deontology/}). Such
-interventions could state that „we have a duty to respect each other
-during the discussions``, „we have a moral obligation to act in a civil
-manner while participating in online communities,'' „we shouldn't use ad
-personam in here''. The basic assumption behind those interventions is
-that there is something we ought to do or are morally required to do -
-and such actions are the right actions. There are also actions we ought
-not to do - and such actions are morally wrongful. This line of thinking
-can be traced back to Immanuel Kant who thought that all universal moral
-obligations can stem from categorical imperative: ``act only in
-accordance with that maxim through which you can at the same time will
-that it become a universal law'' (Groundwork of the Metaphysic of
-Morals).
-
-Yet other interventions were encouraged to be expressed in the light of
-virtue ethics and stressed the importance of adhering to or practicing
-certain virtues. Such a message was assumed to motivate the moral agent
-in the process of positive reinforcement and create a feeling of the
-desirability of certain behaviors, e.g.~„capacity to be respectful in a
-heated discussion is a virtue and requires hard work''. The core
-assumption here is that the virtue itself is not genetically inherited
-but is rather a potential or a disposition of a character that can be
-practice and mastered like a practical skill (even though as mentioned
-by Natasza Szutta in {[}cite her book about virtue ethics{]} virtues and
-practical skills share some fundamental differences). NS distinguished
-two types of virtues - affective and cognitive. Affective virtues
-encompass the emotions and feelings that play an important and positive
-role in morality and can act as a support in the course of becoming a
-virtuous man. A cognitive virtue relates to the intellectual aspect in
-which one knows how to act in certain situations and understands the
-rules of morally rightful actions (e.g.~what is kindness and how a kind
-man acts). Here, just as in the case of empathetic interventions, any
-attempts to measure whether the target of the intervention in the case
-of a positive outcome (behavioral change) indeed acted in a virtuous
-way. A virtue of kindness may manifest itself in particular behaviors
-but as such cannot be identified with the virtuous deed, as highlighted
-by Natasza Szutta. Although again, the goal of the experiment itself was
-to change the behavior of the attackers, and measuring whether
-particular messages contributed to more flourishing individuals in terms
-of virtue development and character creation lies beyond the scope of
-this work. Interventions could affect people either way - stimulate
-their moral reflections or limit their attacks due to consequentialist
-way of thinking and fear of potential outcomes (e.g.~being excluded from
-the community).
+(\url{https://ethics.org.au/ethics-explainer-deontology/}). The basic
+assumption behind those interventions is that there is something we
+ought to do or are morally required to do --- and such actions are the
+right actions. There are also actions we ought not to do --- and such
+actions are morally wrongful. This line of thinking can be traced back
+to Immanuel Kant who thought that all universal moral obligations can
+stem from categorical imperative: ``act only in accordance with that
+maxim through which you can at the same time will that it become a
+universal law'' (Groundwork of the Metaphysic of Morals).
+
+In the psychological literature, Robert B. Cialdini distinguished three
+types of norms that he found to be effective in guiding human action:
+descriptive norms (focused on the perception of how the majority of
+people would behave), injunctive (based on the perception of how the
+majority of people would approve or disapprove certain conduct), or
+personal norms (based on the perception of how a particular person would
+approve or disapprove certain behavior) CITE:
+\url{https://www.sciencedirect.com/science/article/abs/pii/S0065260108603305}.
+Although interventions written on the grounds of duties and deontology
+cannot be reduced to any of the above, since following Hume's guillotine
+--- from the fact that the majority of people are respectful does not
+follow the normative statement of civility --- I hoped that expressing a
+universal normative statement will be even more powerful and potentially
+spawn an interpretation of social acceptability or unacceptability of
+certain behavior.
+
+Yet other interventions in normative group were encouraged to be
+expressed in the light of virtue ethics and stressed the importance of
+adhering to or practicing certain virtues. Such a message was assumed to
+motivate the moral agent in the process of positive reinforcement and
+create a feeling of the desirability of certain behaviors, like kindness
+and civility. The core assumption here is that the virtue itself is not
+genetically inherited but is rather a potential or a disposition of a
+character that can be practice and mastered like a practical skill (even
+though as mentioned by Natasza Szutta in {[}cite her book about virtue
+ethics{]} virtues and practical skills share some fundamental
+differences). NS distinguished two types of virtues - affective and
+cognitive. Affective virtues encompass the emotions and feelings that
+play an important and positive role in morality and can act as a support
+in the course of becoming a virtuous man. A cognitive virtue relates to
+the intellectual aspect in which one knows how to act in certain
+situations and understands the rules of morally rightful actions
+(e.g.~what is kindness and how a kind man acts).
+
+Here, just as in the case of empathetic interventions, any attempts to
+measure whether the target of the intervention in the case of a positive
+outcome (behavioral change) indeed acted in a virtuous way. A virtue of
+kindness may manifest itself in particular behaviors but as such cannot
+be identified with the virtuous deed, as highlighted by Natasza Szutta.
+Although again, the goal of the experiment itself was to change the
+behavior of the attackers, and measuring whether particular messages
+contributed to more flourishing individuals in terms of virtue
+development and character creation lies beyond the scope of this work.
+Interventions could affect people either way - stimulate their moral
+reflections or limit their attacks due to consequentialist way of
+thinking and fear of potential outcomes (e.g.~being excluded from the
+community).
 
@@
 those norms as well, citing specific points, for instance, ``Hey there,
-have you read the reddiquette? It says remember the human.'' or ``Let's
-recall the reddiquette and adhere to the same standards of behavior
-online that you follow in real life.''
+have you read the reddiquette? It says remember the human.''
 
@@
 of the sanity of our volunteers, we decided to create only two but broad
-categories and let them decide based on the context of the conversation,
-how they want to respond to the attacker.
+categories and let volunteers decide based on the context of the
+conversation, how they want to respond to the attacker.
 

### 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
starting technical report

---
title: "Bayesian analysis of the NESTA study of interventions against  verbal aggression online"
author: "Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex6.sty
  html_document:
    df_print: paged
  word_document: default
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)

mykable <- function(object) {kable(object, "latex", booktabs = T) %>% kable_styling(latex_options = "striped",font_size = 9)}

#kable(table(data$group), "latex", booktabs = T, col.names = c("Group", "n")) %>% 
#  kable_styling(latex_options = c("striped","HOLD_position"),font_size = 9) 
```

\tableofcontents

# Exploration

Load the dataset and take a look first.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
summaries <- read.csv(file = "datasets/Summaries.csv")
head(summaries) %>% kable( "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "scale_down") ,font_size = 9)
```
\normalsize

The basic variables we are dealing with are in the following table.

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
variable <- c("AB", "AD", "AA", "CB", "CD", "CA", "group", "IC")
explanation <- c("attacks before (pre-treatment)", "attacks during (the treatment period)",
                 "attacks after (post-treatment)", "comments before", "comments during",
                 "comments after", "treatment group", "intervention count")
vars <- data.frame(variable, explanation)
mykable(vars)
```

Further variables are defined in terms of those, in particular, we will be predicting \textsf{AdiffS} which is the standardized difference  \textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized difference \textsf{CA}-\textsf{CB}. Before we proceed, we will also standardize the predictors, and add a numerical index for the group:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
summaries$ABS <- standardize(summaries$AB)
summaries$CBS <- standardize(summaries$CB)
summaries$AAS <- standardize(summaries$AA)
summaries$CAS <- standardize(summaries$CA)
summaries$CDS <- standardize(summaries$CD)
summaries$ADS <- standardize(summaries$AD)
summaries$group <- as.factor(summaries$group)
summaries$groupID <-  as.integer( as.factor(summaries$group) )
```
\normalsize

First, let's take a look at the distribution of \textsf{IC} in the treatment groups:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
ggplot(summaries[summaries$group != "control",], aes(x = IC, fill = group))+
  geom_bar()+theme_tufte()+
  xlab("interventions received")+
  labs(title = "Intervention counts in treatment groups")+
  scale_x_continuous(breaks = seq(0,40,5))
```
\normalsize

\todo{Note there were much more empathetic interventions, this needs an explanation}

Second, when we look at the distribution of standardized difference in attacks, when restricted to (-1,1), the peaks of distributions are shifted a bit, with lowest median for the normative group, but not too much:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
violAdiffS <- ggplot(summaries, aes(x=group, y = AdiffS))+
  geom_violin() +theme_tufte() 
violJoint <- ggarrange(violAdiffS+ggtitle("whole range"),
              violAdiffS + ylim(c(-1,1))+geom_boxplot(width = .2)+
              ggtitle("restricted to (-1,1)")) 
violJointTitled <- annotate_figure(violJoint, 
  top = text_grob("Empirical distribution of change in attacks (standardized)",
                  size = 12))
violJointTitled
```
\normalsize

Analogous plot for comments does not reveal this slight downward shift for normative, but otherwise the visualisation migth suggest no strong impact of interventions on attacks, and no impact on comments.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
violCdiffS <- ggplot(summaries, aes(x=group, y = CdiffS))+
  geom_violin() +theme_tufte() 
violJointC <- ggarrange(violCdiffS+ggtitle("whole range"),
              violCdiffS + ylim(c(-1,1))+geom_boxplot(width = .2)+
              ggtitle("restricted to (-1,1)")) 
violJointCTitled <- annotate_figure(violJoint, 
  top = text_grob("Empirical distribution of change in comments (standardized)",
                  size = 12))
violJointCTitled
```
\normalsize

However, plotting changes against intervention counts reveals that restricting attention to various activity levels drastically changes the regression lines.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
icplot1 <- ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-2,2))+
  ggtitle("sd restricted to (-2,2)")+
  theme(legend.position = c(0.65, 0.1))

icplot2 <-  ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-1,1))+ggtitle("sd restricted to (-1,1)")+
  theme(legend.position = c(0.65, 0.1))

icplotJoint <- ggarrange(icplot1, icplot2) 
icplotTitled <- annotate_figure(icplotJoint, 
  top = text_grob("Change in attacks (standardized) vs interventions received",  size = 12))
icplotTitled
```
\normalsize

Some interactions are also suggested by the differences in linear smoothing when attention is restricted when it comes to change in comments.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
icCplot1 <- ggplot(summaries, aes(x = IC, y = CdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-2,2))+
  ggtitle("sd restricted to (-2,2)")+
  theme(legend.position = c(0.65, 0.1))

icCplot2 <-  ggplot(summaries, aes(x = IC, y = CdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-1,1))+ggtitle("sd restricted to (-1,1)")+
  theme(legend.position = c(0.65, 0.1))

icCplotJoint <- ggarrange(icCplot1, icCplot2) 
icCplotTitled <- annotate_figure(icCplotJoint, 
  top = text_grob("Change in comments (standardized) vs interventions received",
   size = 12))
icCplotTitled
```
\normalsize

This suggests we should keep an eye out for interactions in the analysis, and that the intial comparison of means or medians between groups might be misleading if the effects in different volume groups are different and cancel each other.

Now, let's inspect correlations between the variables involved in the model:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
summariesCorr <- select(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)
ggcorr(summariesCorr, method = c("pairwise"),
       digits = 4, low = "steelblue", mid = "white",
       high = "darkred", midpoint =0,
       geom = "tile", label = TRUE, label_size=4, label_round =2, layout.exp =1,
       label_alpha = FALSE,hjust = 0.75)

```
\normalsize

This tells us that almost no predictors are strongly correlated, except for pairs \textsf{CBS}-\textsf{CDS}, so we drop CDS from the analysis and avoid using them  in the same model to avoid multicolinearity issues. These are just comments during the intervention period, which, unsurprisingly are also a good proxy for comments before and comments after.

# Causal inference

To identify the right variables to condition (or not condition) on to identify the causal effect of the interventions, we first need to think about the causal structure of the problem. Here's a plausible causal structure that we will be working with:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
dag <- dagitty("
  dag{
  CDS -> ADS -> IC  ons
               U [unobserved]   
               U -> CBS -> ABS  
               U -> ABS        
               U -> CDS -> ADS  
               U -> ADS         
               U -> CAS -> AAS    
               U -> AAS                        
               IC -> AAS        
               IC -> CAS        
               IT -> CAS        
               IT -> AAS
               CBS -> CDS -> CAS
               ABS -> ADS -> AAS
               }")
set.seed(123)
drawdag(dag)
```
\normalsize

Comments during impact attacks during, which trigger interventions.
Unmeasured user features cause comments before, which impact attacks before, and also    attacks before directly. Comments during (their impact on ADS is areadly included)  impact attacks during during directly and  comments after, which impact attacks after and   attacks after directly.  Intervention count impacts attacks after  and comments after. The same directions of impact are included for intervention type. Finally, comments through time are connected causally, and so are attacks.

We already know not to condition on CDS if we condition on CAS or CBS. What else? \textsf{IT} has no bacwkard paths, but \textsf{IC} does. Let's identify all paths from \textsf{IC} to \textsf{AAS}:

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
paths(dag, from = c("IC"), to = "AAS")
```
\normalsize

Crucially, all backdoor paths go through \textsf{ADS}, which then becomes either a fork or a pipe, so all backdoor paths can be closed by conditioning on \textsf{ADS}. Moreover there is only one directed indirect path, it goes through \textsf{CAS}, so we should not condition on it if we are to identify causal effect on attacks mediated by impact on comments (unless we care about the direct effect of \textsf{IC}  and \textsf{IT} on \textsf{AAS}, but that's a separate question). This is in line with the adjustment set identified algorithmically, and the same move makes sense when we want to predict \textsf{CAS}.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS")
adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "CAS")
```
\normalsize

It's open season for other variables, and our decision to include them in the model will be guided by information-theoretic criteria of predictive power.

# Bayesian models and their priors

We will focus on a class of additive models where the outcome variable is normally distributed around the predicted mean, which is a linear function of predictors (possibly with some interactions). To spoil the story, we will end up using a model, whose specification is as follows:

\begin{align*}
\mathsf{AdiffS} & \sim Norm(\mu, \sigma)\\
mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{ADS}] + \beta_{\mathsf{IT}}[\mathsf{group}] +
 \beta_{IC}[\mathsf{group}]\times \mathsf{IC} + b_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}] \times \mathsf{CBS}
\end{align*}

<!-- # InteractionsModelDiff <- ulam( -->
<!-- #   alist( -->
<!-- #     AdiffS ~ dnorm( mu, sigma ), -->
<!-- #     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS, -->
<!-- #     a ~ dnorm (0,0.3), -->
<!-- #     bADS[groupID] ~ dnorm(0,.3), -->
<!-- #     bADSIC ~ dnorm(0,.3), -->
<!-- #     bCBS[groupID] ~ dnorm(0,.3), -->
<!-- #     bIT[groupID] ~ dnorm(0,.3), -->
<!-- #     bIC[groupID] ~ dnorm(0,.3), -->
<!-- #     sigma  ~ dexp(1) -->
<!-- #   ),  -->
<!-- #   data = summaries -->
<!-- # ) -->

#  References {-}

\vspace{-3mm}

### 2021-09-10 bayesianAnalysis/bayesianReport.tex
starting technical report

\documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Bayesian analysis of the NESTA study of interventions against verbal aggression online},
            pdfauthor={Rafal Urbaniak},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

%\documentclass{article}

% %packages
 \usepackage{booktabs}

\usepackage{multirow}

\usepackage{graphicx}

\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{etex}
%\usepackage{yfonts}
\usepackage{marvosym}
\usepackage[notextcomp]{kpfonts}
\usepackage{nicefrac}
\newcommand*{\QED}{\hfill \footnotesize {\sc Q.e.d.}}
\usepackage{floatrow}

\usepackage[textsize=footnotesize]{todonotes}
%\linespread{1.5}
\usepackage{pdfpages}
\setlength{\parindent}{10pt}
\setlength{\parskip}{1pt}

%language
\usepackage{times}
\usepackage{t1enc}
%\usepackage[utf8x]{inputenc}
%\usepackage[polish]{babel}
%\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[scaled=0.88]{helvet}

%AMS
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{geometry}
 \geometry{a4paper,left=35mm,top=20mm,}

%environments
\newtheorem{fact}{Fact}

%abbreviations
\newcommand{\ra}{\rangle}
\newcommand{\la}{\langle}
\newcommand{\n}{\neg}
\newcommand{\et}{\wedge}
\newcommand{\jt}{\rightarrow}
\newcommand{\ko}[1]{\forall  #1\,}
\newcommand{\ro}{\leftrightarrow}
\newcommand{\exi}[1]{\exists\, {_{#1}}}
\newcommand{\pr}[1]{\mathsf{P}(#1)}
\newcommand{\cost}{\mathsf{cost}}

\newcommand{\odds}{\mathsf{Odds}}
\newcommand{\ind}{\mathsf{Ind}}
\newcommand{\nf}[2]{\nicefrac{#1\,}{#2}}
\newcommand{\R}[1]{\texttt{#1}}
\newcommand{\prr}[1]{\mbox{$\mathtt{P}_{prior}(#1)$}}
\newcommand{\prp}[1]{\mbox{$\mathtt{P}_{posterior}(#1)$}}

\newtheorem{q}{\color{blue}Question}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

%technical intermezzo
%---------------------

\newcommand{\intermezzoa}{
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Starts}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}\nopagebreak 
	}

\newcommand{\intermezzob}{\nopagebreak 
	\begin{minipage}[c]{13cm}
	\begin{center}\rule{10cm}{0.4pt}

	\tiny{\sc Optional Content Ends}

	\vspace{-1mm}

	\rule{10cm}{0.4pt}\end{center}
	\end{minipage}
	}
%--------------------

\newtheorem*{reply*}{Reply}
\usepackage{enumitem}
\newcommand{\question}[1]{\begin{enumerate}[resume,leftmargin=0cm,labelsep=0cm,align=left]
\item #1
\end{enumerate}}

\usepackage{float}

% \setbeamertemplate{blocks}[rounded][shadow=true]
% \setbeamertemplate{itemize items}[ball]
% \AtBeginPart{}
% \AtBeginSection{}
% \AtBeginSubsection{}
% \AtBeginSubsubsection{}
% \setlength{\emergencystretch}{0em}
% \setlength{\parskip}{0pt}

\usepackage[authoryear]{natbib}

%\bibliographystyle{apalike}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Bayesian analysis of the NESTA study of interventions against verbal
aggression online}
\author{Rafal Urbaniak}
\date{}

\begin{document}
\maketitle

\tableofcontents

\section{Exploration}\label{exploration}

Load the dataset and take a look first.

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summaries <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\DataTypeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
\KeywordTok{head}\NormalTok{(summaries) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{kable}\NormalTok{( }\StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }\StringTok{"scale_down"}\NormalTok{) ,}\DataTypeTok{font_size =} \DecValTok{9}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabular}{rlrrrrrrrrrrlr}
\toprule
X & author & AB & AD & AA & CB & CD & CA & Adiff & Cdiff & AdiffS & CdiffS & group & IC\\
\midrule
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{\_swf} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{720} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{-19} & \cellcolor{gray!6}{-692} & \cellcolor{gray!6}{-0.0245122} & \cellcolor{gray!6}{-0.3501491} & \cellcolor{gray!6}{normative} & \cellcolor{gray!6}{1}\\
2 & -Allergic & 24 & 24 & 8 & 1614 & 1451 & 1237 & -16 & -377 & 0.0719197 & 0.1057675 & normative & 3\\
\cellcolor{gray!6}{3} & \cellcolor{gray!6}{-funny-username-} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{847} & \cellcolor{gray!6}{497} & \cellcolor{gray!6}{721} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-126} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{0.4690535} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
4 & -Johnny- & 18 & 2 & 8 & 1465 & 408 & 684 & -10 & -781 & 0.2647835 & -0.4789637 & empathy & 2\\
\cellcolor{gray!6}{5} & \cellcolor{gray!6}{1secwhileiyeet3} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{1384} & \cellcolor{gray!6}{198} & \cellcolor{gray!6}{120} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-1264} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{-1.1780359} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
\addlinespace
6 & 20CharsIsNotEnough & 16 & 10 & 25 & 779 & 907 & 972 & 9 & 193 & 0.8755188 & 0.9307596 & empathy & 4\\
\bottomrule
\end{tabular}}
\endgroup{}
\end{table}

\normalsize

The basic variables we are dealing with are in the following table.

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{ll}
\toprule
variable & explanation\\
\midrule
\cellcolor{gray!6}{AB} & \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD & attacks during (the treatment period)\\
\cellcolor{gray!6}{AA} & \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB & comments before\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
\addlinespace
CA & comments after\\
\cellcolor{gray!6}{group} & \cellcolor{gray!6}{treatment group}\\
IC & intervention count\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

Further variables are defined in terms of those, in particular, we will
be predicting \textsf{AdiffS} which is the standardized difference
\textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized
difference \textsf{CA}-\textsf{CB}. Before we proceed, we will also
standardize the predictors, and add a numerical index for the group:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summaries}\OperatorTok{$}\NormalTok{ABS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AB)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{CBS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CB)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{AAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AA)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{CAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CA)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{CDS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CD)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{ADS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AD)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
\NormalTok{summaries}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{  }\KeywordTok{as.integer}\NormalTok{( }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group) )}
\end{Highlighting}
\end{Shaded}

\normalsize

First, let's take a look at the distribution of \textsf{IC} in the
treatment groups:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{(summaries[summaries}\OperatorTok{$}\NormalTok{group }\OperatorTok{!=}\StringTok{ "control"}\NormalTok{,], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_bar}\NormalTok{()}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions received"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Intervention counts in treatment groups"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}\DataTypeTok{breaks =} \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{40}\NormalTok{,}\DecValTok{5}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-4-1} \end{center}

\normalsize

\todo{Note there were much more empathetic interventions, this needs an explanation}

Second, when we look at the distribution of standardized difference in
attacks, when restricted to (-1,1), the peaks of distributions are
shifted a bit, with lowest median for the normative group, but not too
much:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{violAdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
\NormalTok{violJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violAdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
\NormalTok{              violAdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Removed 58 rows containing non-finite values (stat_ydensity).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 58 rows containing non-finite values (stat_boxplot).
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{violJointTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in attacks (standardized)"}\NormalTok{,}
                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
\NormalTok{violJointTitled}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-5-1} \end{center}

\normalsize

Analogous plot for comments does not reveal this slight downward shift
for normative, but otherwise the visualisation migth suggest no strong
impact of interventions on attacks, and no impact on comments.

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{violCdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ CdiffS))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
\NormalTok{violJointC <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violCdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
\NormalTok{              violCdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Removed 90 rows containing non-finite values (stat_ydensity).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 90 rows containing non-finite values (stat_boxplot).
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{violJointCTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in comments (standardized)"}\NormalTok{,}
                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
\NormalTok{violJointCTitled}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}

\normalsize

However, plotting changes against intervention counts reveals that
restricting attention to various activity levels drastically changes the
regression lines.

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{icplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}

\NormalTok{icplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}

\NormalTok{icplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icplot1, icplot2) }
\NormalTok{icplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icplotJoint, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in attacks (standardized) vs interventions received"}\NormalTok{,  }\DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
\NormalTok{icplotTitled}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}

\normalsize

Some interactions are also suggested by the differences in linear
smoothing when attention is restricted when it comes to change in
comments.

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{icCplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}

\NormalTok{icCplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}

\NormalTok{icCplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icCplot1, icCplot2) }
\NormalTok{icCplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icCplotJoint, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in comments (standardized) vs interventions received"}\NormalTok{,}
   \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
\NormalTok{icCplotTitled}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}

\normalsize

This suggests we should keep an eye out for interactions in the
analysis, and that the intial comparison of means or medians between
groups might be misleading if the effects in different volume groups are
different and cancel each other.

Now, let's inspect correlations between the variables involved in the
model:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{summariesCorr <-}\StringTok{ }\KeywordTok{select}\NormalTok{(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)}
\KeywordTok{ggcorr}\NormalTok{(summariesCorr, }\DataTypeTok{method =} \KeywordTok{c}\NormalTok{(}\StringTok{"pairwise"}\NormalTok{),}
       \DataTypeTok{digits =} \DecValTok{4}\NormalTok{, }\DataTypeTok{low =} \StringTok{"steelblue"}\NormalTok{, }\DataTypeTok{mid =} \StringTok{"white"}\NormalTok{,}
       \DataTypeTok{high =} \StringTok{"darkred"}\NormalTok{, }\DataTypeTok{midpoint =}\DecValTok{0}\NormalTok{,}
       \DataTypeTok{geom =} \StringTok{"tile"}\NormalTok{, }\DataTypeTok{label =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{label_size=}\DecValTok{4}\NormalTok{, }\DataTypeTok{label_round =}\DecValTok{2}\NormalTok{, }\DataTypeTok{layout.exp =}\DecValTok{1}\NormalTok{,}
       \DataTypeTok{label_alpha =} \OtherTok{FALSE}\NormalTok{,}\DataTypeTok{hjust =} \FloatTok{0.75}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}

\normalsize

This tells us that almost no predictors are strongly correlated, except
for pairs \textsf{CBS}-\textsf{CDS}, so we drop CDS from the analysis
and avoid using them in the same model to avoid multicolinearity issues.
These are just comments during the intervention period, which,
unsurprisingly are also a good proxy for comments before and comments
after.

\section{Causal inference}\label{causal-inference}

To identify the right variables to condition (or not condition) on to
identify the causal effect of the interventions, we first need to think
about the causal structure of the problem. Here's a plausible causal
structure that we will be working with:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dag <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
\StringTok{  dag\{}
\StringTok{  CDS -> ADS -> IC  ons}
\StringTok{               U [unobserved]   }
\StringTok{               U -> CBS -> ABS  }
\StringTok{               U -> ABS        }
\StringTok{               U -> CDS -> ADS  }
\StringTok{               U -> ADS         }
\StringTok{               U -> CAS -> AAS    }
\StringTok{               U -> AAS                        }
\StringTok{               IC -> AAS        }
\StringTok{               IC -> CAS        }
\StringTok{               IT -> CAS        }
\StringTok{               IT -> AAS}
\StringTok{               CBS -> CDS -> CAS}
\StringTok{               ABS -> ADS -> AAS}
\StringTok{               \}"}\NormalTok{)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\KeywordTok{drawdag}\NormalTok{(dag)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-10-1} \end{center}

\normalsize

Comments during impact attacks during, which trigger interventions.
Unmeasured user features cause comments before, which impact attacks
before, and also attacks before directly. Comments during (their impact
on ADS is areadly included) impact attacks during during directly and
comments after, which impact attacks after and attacks after directly.
Intervention count impacts attacks after and comments after. The same
directions of impact are included for intervention type. Finally,
comments through time are connected causally, and so are attacks.

We already know not to condition on CDS if we condition on CAS or CBS.
What else? \textsf{IT} has no bacwkard paths, but \textsf{IC} does.
Let's identify all paths from \textsf{IC} to \textsf{AAS}:

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{paths}\NormalTok{(dag, }\DataTypeTok{from =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{), }\DataTypeTok{to =} \StringTok{"AAS"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## $paths
##  [1] "IC -> AAS"                                              
##  [2] "IC -> CAS -> AAS"                                       
##  [3] "IC -> CAS <- CDS -> ADS -> AAS"                         
##  [4] "IC -> CAS <- CDS -> ADS <- ABS <- CBS <- U -> AAS"      
##  [5] "IC -> CAS <- CDS -> ADS <- ABS <- U -> AAS"             
##  [6] "IC -> CAS <- CDS -> ADS <- U -> AAS"                    
##  [7] "IC -> CAS <- CDS <- CBS -> ABS -> ADS -> AAS"           
##  [8] "IC -> CAS <- CDS <- CBS -> ABS -> ADS <- U -> AAS"      
##  [9] "IC -> CAS <- CDS <- CBS -> ABS <- U -> AAS"             
## [10] "IC -> CAS <- CDS <- CBS -> ABS <- U -> ADS -> AAS"      
## [11] "IC -> CAS <- CDS <- CBS <- U -> AAS"                    
## [12] "IC -> CAS <- CDS <- CBS <- U -> ABS -> ADS -> AAS"      
## [13] "IC -> CAS <- CDS <- CBS <- U -> ADS -> AAS"             
## [14] "IC -> CAS <- CDS <- U -> AAS"                           
## [15] "IC -> CAS <- CDS <- U -> ABS -> ADS -> AAS"             
## [16] "IC -> CAS <- CDS <- U -> ADS -> AAS"                    
## [17] "IC -> CAS <- CDS <- U -> CBS -> ABS -> ADS -> AAS"      
## [18] "IC -> CAS <- IT -> AAS"                                 
## [19] "IC -> CAS <- U -> AAS"                                  
## [20] "IC -> CAS <- U -> ABS -> ADS -> AAS"                    
## [21] "IC -> CAS <- U -> ABS <- CBS -> CDS -> ADS -> AAS"      
## [22] "IC -> CAS <- U -> ADS -> AAS"                           
## [23] "IC -> CAS <- U -> CBS -> ABS -> ADS -> AAS"             
## [24] "IC -> CAS <- U -> CBS -> CDS -> ADS -> AAS"             
## [25] "IC -> CAS <- U -> CDS -> ADS -> AAS"                    
## [26] "IC -> CAS <- U -> CDS <- CBS -> ABS -> ADS -> AAS"      
## [27] "IC <- ADS -> AAS"                                       
## [28] "IC <- ADS <- ABS <- CBS -> CDS -> CAS -> AAS"           
## [29] "IC <- ADS <- ABS <- CBS -> CDS -> CAS <- IT -> AAS"     
## [30] "IC <- ADS <- ABS <- CBS -> CDS -> CAS <- U -> AAS"      
## [31] "IC <- ADS <- ABS <- CBS -> CDS <- U -> AAS"             
## [32] "IC <- ADS <- ABS <- CBS -> CDS <- U -> CAS -> AAS"      
## [33] "IC <- ADS <- ABS <- CBS -> CDS <- U -> CAS <- IT -> AAS"
## [34] "IC <- ADS <- ABS <- CBS <- U -> AAS"                    
## [35] "IC <- ADS <- ABS <- CBS <- U -> CAS -> AAS"             
## [36] "IC <- ADS <- ABS <- CBS <- U -> CAS <- IT -> AAS"       
## [37] "IC <- ADS <- ABS <- CBS <- U -> CDS -> CAS -> AAS"      
## [38] "IC <- ADS <- ABS <- CBS <- U -> CDS -> CAS <- IT -> AAS"
## [39] "IC <- ADS <- ABS <- U -> AAS"                           
## [40] "IC <- ADS <- ABS <- U -> CAS -> AAS"                    
## [41] "IC <- ADS <- ABS <- U -> CAS <- IT -> AAS"              
## [42] "IC <- ADS <- ABS <- U -> CBS -> CDS -> CAS -> AAS"      
## [43] "IC <- ADS <- ABS <- U -> CBS -> CDS -> CAS <- IT -> AAS"
## [44] "IC <- ADS <- ABS <- U -> CDS -> CAS -> AAS"             
## [45] "IC <- ADS <- ABS <- U -> CDS -> CAS <- IT -> AAS"       
## [46] "IC <- ADS <- CDS -> CAS -> AAS"                         
## [47] "IC <- ADS <- CDS -> CAS <- IT -> AAS"                   
## [48] "IC <- ADS <- CDS -> CAS <- U -> AAS"                    
## [49] "IC <- ADS <- CDS <- CBS -> ABS <- U -> AAS"             
## [50] "IC <- ADS <- CDS <- CBS -> ABS <- U -> CAS -> AAS"      
## [51] "IC <- ADS <- CDS <- CBS -> ABS <- U -> CAS <- IT -> AAS"
## [52] "IC <- ADS <- CDS <- CBS <- U -> AAS"                    
## [53] "IC <- ADS <- CDS <- CBS <- U -> CAS -> AAS"             
## [54] "IC <- ADS <- CDS <- CBS <- U -> CAS <- IT -> AAS"       
## [55] "IC <- ADS <- CDS <- U -> AAS"                           
## [56] "IC <- ADS <- CDS <- U -> CAS -> AAS"                    
## [57] "IC <- ADS <- CDS <- U -> CAS <- IT -> AAS"              
## [58] "IC <- ADS <- U -> AAS"                                  
## [59] "IC <- ADS <- U -> ABS <- CBS -> CDS -> CAS -> AAS"      
## [60] "IC <- ADS <- U -> ABS <- CBS -> CDS -> CAS <- IT -> AAS"
## [61] "IC <- ADS <- U -> CAS -> AAS"                           
## [62] "IC <- ADS <- U -> CAS <- IT -> AAS"                     
## [63] "IC <- ADS <- U -> CBS -> CDS -> CAS -> AAS"             
## [64] "IC <- ADS <- U -> CBS -> CDS -> CAS <- IT -> AAS"       
## [65] "IC <- ADS <- U -> CDS -> CAS -> AAS"                    
## [66] "IC <- ADS <- U -> CDS -> CAS <- IT -> AAS"              
## 
## $open
##  [1]  TRUE  TRUE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE
## [13] FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE FALSE
## [25] FALSE FALSE  TRUE  TRUE FALSE FALSE FALSE FALSE FALSE  TRUE  TRUE FALSE
## [37]  TRUE FALSE  TRUE  TRUE FALSE  TRUE FALSE  TRUE FALSE  TRUE FALSE FALSE
## [49] FALSE FALSE FALSE  TRUE  TRUE FALSE  TRUE  TRUE FALSE  TRUE FALSE FALSE
## [61]  TRUE FALSE  TRUE FALSE  TRUE FALSE
\end{verbatim}

\normalsize

Crucially, all backdoor paths go through \textsf{ADS}, which then
becomes either a fork or a pipe, so all backdoor paths can be closed by
conditioning on \textsf{ADS}. Moreover there is only one directed
indirect path, it goes through \textsf{CAS}, so we should not condition
on it if we are to identify causal effect on attacks mediated by impact
on comments (unless we care about the direct effect of \textsf{IC} and
\textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
line with the adjustment set identified algorithmically, and the same
move makes sense when we want to predict \textsf{CAS}.

\vspace{1mm} \footnotesize

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AAS"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## { ADS }
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CAS"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## { ADS }
\end{verbatim}

\normalsize

It's open season for other variables, and our decision to include them
in the model will be guided by information-theoretic criteria of
predictive power.

\section{Bayesian models and their
priors}\label{bayesian-models-and-their-priors}

We will focus on a class of additive models where the outcome variable
is normally distributed around the predicted mean, which is a linear
function of predictors (possibly with some interactions). To spoil the
story, we will end up using a model, whose specification is as follows:

\begin{align*}
\mathsf{AdiffS} & \sim Norm(\mu, \sigma)\\
mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{ADS}] + \beta_{\mathsf{IT}}[\mathsf{group}] +
 \beta_{IC}[\mathsf{group}]\times \mathsf{IC} + b_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}] \times \mathsf{CBS}
\end{align*}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\vspace{-3mm}

\end{document}

### 2021-09-10 predictionInteractionsProps.R

@@ -9,7 +9,7 @@ summaries$CDS <- standardize(summaries$CD)
 summaries$ADS <- standardize(summaries$AD)
 summaries$group <- as.factor(summaries$group)
 summaries$groupID <-  as.integer( as.factor(summaries$group) )
-summaries$ApropS <- standardize(summaries$AA/summaries$AB)
+#summaries$ApropS <- standardize(summaries$AA/summaries$AB)
 
 
 ggplot()+geom_histogram(aes(x=summaries$AdiffS))

### 2021-09-10 visualisations/exploration.R

@@ -21,6 +21,17 @@ summaries$CAw <- (summaries$CB/72)*7
 summaries$Adiffw <- summaries$AAw - summaries$ABw
 summaries$Cdiffw <- summaries$CAw - summaries$CBw
 
+summaries <- readRDS(file = "datasets/Summaries.rds")
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+summaries$group <- as.factor(summaries$group)
+summaries$groupID <-  as.integer( as.factor(summaries$group) )
+#summaries$ApropS <- standardize(summaries$AA/summaries$AB)
+
 
 
 mean(summaries$AAw)
@@ -47,11 +58,11 @@ ggplot()+theme_tufte() +geom_histogram(aes(x = ACprop, fill = summaries$group, y
 
 
 #barplot of interventions
-ggplot(summaries[summaries$group != "control",], aes(x = IC))+geom_bar()+theme_tufte()+
+ggplot(summaries[summaries$group != "control",], aes(x = IC, fill = group))+geom_bar()+theme_tufte()+
   xlab("interventions received")+labs(title = "Intervention counts in treatment groups")+
   scale_x_continuous(breaks = seq(0,40,5))
 
-ggsave("images/interventionsBar.pdf", width = 20, height = 10, units = "cm", dpi = 450)  
+ggsave("images/interventionsBar.jpeg", width = 20, height = 10, units = "cm", dpi = 450)  
 
 
 
@@ -123,6 +134,14 @@ annotate_figure(densJoint1, top = text_grob("Standardized difference in comments
 ggsave("images/CCS.pdf", width = 20, height = 15, units = "cm", dpi = 450)  
 
 
+#how about violin ploits
+
+violAdiffS <- ggplot(summaries, aes(x=group, y = AdiffS))+geom_violin() +theme_tufte()
+violJoint <- ggarrange(violAdiffS+ggtitle("whole range"),violAdiffS + ylim(c(-1,1))+geom_boxplot(width = .2)+ggtitle("restricted to (-1,1)"), ncol = 2)
[…]

### 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
pushing bayesian analysis report further

@@
 library(dagitty)
+library(reshape)
 
@@
 \todo{Note there were much more empathetic interventions, this needs an explanation}
+
+\todo{Question: intervention counts by group}
 
@@
 \begin{align*}
-\mathsf{AdiffS} & \sim Norm(\mu, \sigma)\\
-mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{ADS}] + \beta_{\mathsf{IT}}[\mathsf{group}] +
- \beta_{IC}[\mathsf{group}]\times \mathsf{IC} + b_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}] \times \mathsf{CBS}
+\mathsf{AdiffS} & \sim \textsf{Norm}(\mu, \sigma)\\
+mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
+ \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS}\\
+ \alpha & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{ADS}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{group}_i} & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{IC}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{ADSIC}} & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{CBS}}[\mathsf{group}_i]& \sim \textsf{Norm}(0,.3)\\
 \end{align*}
+
+That is, we take the resulting mean to be the result of the general average ($\alpha$) and the impact of the following coefficients: group-specific coefficient for \textsf{ADS}, group coefficient, group-specific coefficient for \textsf{IC}, interaction coefficient for \textsf{ADS} and \textsf{IC}, and group-specific coeffient for \textsf{CBS}.
+This is plausible prima facie which group a user belongs to might have impact on  how attacks during the treatment is related to attacks after, the role  of the intervention count, and the role of comments before.
+Moreover, the levels of agressive behavior displayed by the user during treament might have impact on the role played by the intervention count.
+Later on we will see that there are information-theoretic reasons to include these interactions.
+
+Now for the priors.
+One might be suspicious of $\sigma =.3$ we employed and suggest using standard normal distributions with $\sigma = 1$ instead.
+However, a quick prior predictive check shows that this results in insanely wide priors that are competely unrealistic.
+(For computational reasons, instead of running the simulations, we load pre-compiled models, but we include the code used to build them).
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
+# building model with sd=1
+# InteractionsModelDiffSD1 <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+
+#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+#     a ~ dnorm (0,1),
+#     bADS[groupID] ~ dnorm(0,1),
+#     bADSIC ~ dnorm(0,1),
+#     bCBS[groupID] ~ dnorm(0,1),
+#     bIT[groupID] ~ dnorm(0,1),
+#     bIC[groupID] ~ dnorm(0,1),
+#     sigma  ~ dexp(1)
+#   ), 
+#   data = summaries
+# )
+# 
+# saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")
+InteractionsModelDiffSD1 <- readRDS(file = "models/InteractionsModelDiffSD1.rds")
+
+#now model with prior sd = .3
+# InteractionsModelDiff <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
+#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ), 
+#   data = summaries
+# )
+
+#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")
+
+InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
+
+##prior predictive checks sd =1
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link( InteractionsModelDiffSD1 , post=prior , data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+
+priorGroupsSD1 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+
+  theme_tufte()+xlab("")+
+  labs(title = "Simulated priors by group",
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = 1)")+
+  ylab("change in attacks (standardized)")
+
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 0:20
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link(InteractionsModelDiffSD1 , post=prior , data=data ) 
+mu.mean <- apply( mu , 2, mean )
+mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
+priorDF <- cbind(data, mu.mean, mu.HPDI)
+priorDF$groupID <- as.factor(groupID)
+levels(priorDF$groupID) <- c("control", "empathy", "normative")
+colnames(priorDF)[2]<- "group"
+
+priorICSD1  <- ggplot(priorDF, aes(x = IC, y  = mu.mean,  fill = group))+
+  geom_line()+geom_ribbon(aes(ymin = X.0.89, ymax = X0.89.), alpha = 0.2)+
+  theme_tufte()+ylab("change in attacks (standardized)")+
+  labs(title = "Simulated priors for AAS vs IC",
+      subtitle = "(at ADS = CBS = 0, sd = 1)")+xlab("interventions")
+
+priorJoint1 <- ggarrange(priorGroupsSD1,priorICSD1, ncol = 2) 
+priorJoint1Titled <- annotate_figure(priorJoint1, 
+  top = text_grob("Predictive priors with sd=1 are insanely wide",
+                  size = 14))
+priorJoint1Titled
+```
+\normalsize
+
+Some experimentation leads to the value of $\sigma =3$, which leads to the following priors:
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
+#prior predictive check sd =.3
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiff, n = 1e4)
+mu <- link(InteractionsModelDiff , post=prior , data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+head(muLong)
+
+priorGroupSD03 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+theme_tufte()+
+  xlab("")+
+  labs(title = "Simulated priors  by group", 
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = .3)")+
+  ylab("change in attacks (standarized)")
+
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link( InteractionsModelDiffSD1 , post=prior , data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+head(muLong)
+
+priorICSD03 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+
+  theme_tufte()+xlab("")+
+  labs(title = "Simulated priors by group", 
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = 1)")+
+  ylab("change in attacks (standardized)")
+
+priorJoint03 <- ggarrange(priorGroupSD03,priorICSD03, ncol = 2) 
+priorJoint03Titled <- annotate_figure(priorJoint03, 
+  top = text_grob("Predictive priors with sd=.3 seem sensible",
+                  size = 14))
+priorJoint03Titled
+```
+\normalsize
+
+Now, some model diagnostics before we move on.
+What we are witnessing is (1) stationarity (the chains stay mostly in the most probable regions), (2) good mixing (they explore a range of options in the beginning), and (3) convergence (they stabilize as they progress).
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results = "hide"}
+traceplot( InteractionsModelDiff )
+```
+\normalsize
+
+Finally, let's inspect the distribution of residuals. That is, we calculate all predictions, their distance from the actual values, and inspect the distribution of the distances:
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results = "hide"}
+mu <- link(InteractionsModelDiff)
+mu_mean <- apply( mu , 2 , mean )
+mu_resid <- summaries$AdiffS - mu_mean
+ggplot()+geom_density(aes(x = mu_resid))+theme_tufte()+
+  ggtitle("Residuals are approximately normally distributed")
+```
+\normalsize
 

### 2021-09-10 bayesianAnalysis/bayesianReport.tex
pushing bayesian analysis report further

@@
 \begin{align*}
-\mathsf{AdiffS} & \sim Norm(\mu, \sigma)\\
-mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{ADS}] + \beta_{\mathsf{IT}}[\mathsf{group}] +
- \beta_{IC}[\mathsf{group}]\times \mathsf{IC} + b_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}] \times \mathsf{CBS}
+\mathsf{AdiffS} & \sim \textsf{Norm}(\mu, \sigma)\\
+mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
+ \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS}\\
+ \alpha & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{ADS}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{group}_i} & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{IC}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{ADSIC}} & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{CBS}}[\mathsf{group}_i]& \sim \textsf{Norm}(0,.3)\\
 \end{align*}
+
+That is, we take the resulting mean to be the result of the general
+average (\(\alpha\)) and the impact of the following coefficients:
+group-specific coefficient for \textsf{ADS}, group coefficient,
+group-specific coefficient for \textsf{IC}, interaction coefficient for
+\textsf{ADS} and \textsf{IC}, and group-specific coeffient for
+\textsf{CBS}. This is plausible prima facie which group a user belongs
+to might have impact on how attacks during the treatment is related to
+attacks after, the role of the intervention count, and the role of
+comments before. Moreover, the levels of agressive behavior displayed by
+the user during treament might have impact on the role played by the
+intervention count. Later on we will see that there are
+information-theoretic reasons to include these interactions.
+
+Now for the priors. One might be suspicious of \(\sigma =.3\) we
+employed and suggest using standard normal distributions with
+\(\sigma = 1\) instead. However, a quick prior predictive check shows
+that this results in insanely wide priors that are competely
+unrealistic. (For computational reasons, instead of running the
+simulations, we load pre-compiled models, but we include the code used
+to build them).
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# building model with sd=1}
+\CommentTok{# InteractionsModelDiffSD1 <- ulam(}
+\CommentTok{#   alist(}
+\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
+\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+}
+\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
+\CommentTok{#     a ~ dnorm (0,1),}
+\CommentTok{#     bADS[groupID] ~ dnorm(0,1),}
+\CommentTok{#     bADSIC ~ dnorm(0,1),}
+\CommentTok{#     bCBS[groupID] ~ dnorm(0,1),}
+\CommentTok{#     bIT[groupID] ~ dnorm(0,1),}
+\CommentTok{#     bIC[groupID] ~ dnorm(0,1),}
+\CommentTok{#     sigma  ~ dexp(1)}
+\CommentTok{#   ), }
+\CommentTok{#   data = summaries}
+\CommentTok{# )}
+\CommentTok{# }
+\CommentTok{# saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")}
+\NormalTok{InteractionsModelDiffSD1 <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiffSD1.rds"}\NormalTok{)}
+
+\CommentTok{#now model with prior sd = .3}
+\CommentTok{# InteractionsModelDiff <- ulam(}
+\CommentTok{#   alist(}
+\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
+\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +}
+\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
+\CommentTok{#     a ~ dnorm (0,0.3),}
+\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bADSIC ~ dnorm(0,.3),}
+\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     sigma  ~ dexp(1)}
+\CommentTok{#   ), }
+\CommentTok{#   data = summaries}
+\CommentTok{# )}
+
+\CommentTok{#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")}
+
+\NormalTok{InteractionsModelDiff <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiff.rds"}\NormalTok{)}
+
+\NormalTok{##prior predictive checks sd =1}
+\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
+\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
+\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
+\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
+\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+
+\NormalTok{priorGroupsSD1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{,}
+  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{IC <-}\StringTok{ }\DecValTok{0}\OperatorTok{:}\DecValTok{20}
+\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+
+\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## recompiling to avoid crashing R session
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{mu.mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{, mean )}
+\NormalTok{mu.HPDI <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI )))}
+\NormalTok{priorDF <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data, mu.mean, mu.HPDI)}
+\NormalTok{priorDF}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(groupID)}
+\KeywordTok{levels}\NormalTok{(priorDF}\OperatorTok{$}\NormalTok{groupID) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{)}
+\KeywordTok{colnames}\NormalTok{(priorDF)[}\DecValTok{2}\NormalTok{]<-}\StringTok{ "group"}
+
+\NormalTok{priorICSD1  <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(priorDF, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y  =}\NormalTok{ mu.mean,  }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_line}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_ribbon}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ X.}\FloatTok{0.89}\NormalTok{, }\DataTypeTok{ymax =}\NormalTok{ X0.}\FloatTok{89.}\NormalTok{), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors for AAS vs IC"}\NormalTok{,}
+      \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, sd = 1)"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions"}\NormalTok{)}
+
+\NormalTok{priorJoint1 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupsSD1,priorICSD1, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
+\NormalTok{priorJoint1Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint1, }
+  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=1 are insanely wide"}\NormalTok{,}
+                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+\NormalTok{priorJoint1Titled}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
+
+\normalsize
+
+Some experimentation leads to the value of \(\sigma =3\), which leads to
+the following priors:
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{#prior predictive check sd =.3}
+\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
+\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiff, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
+\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
+\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
+\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\KeywordTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorGroupSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
+\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors  by group"}\NormalTok{, }
+  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = .3)"}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standarized)"}\NormalTok{)}
+
+\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
+\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
+\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
+\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
+\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
+\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\KeywordTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorICSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{, }
+  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{priorJoint03 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupSD03,priorICSD03, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
+\NormalTok{priorJoint03Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint03, }
+  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=.3 seem sensible"}\NormalTok{,}
+                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+\NormalTok{priorJoint03Titled}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
+
+\normalsize
+
+Now, some model diagnostics before we move on. What we are witnessing is
+(1) stationarity (the chains stay mostly in the most probable regions),
+(2) good mixing (they explore a range of options in the beginning), and
+(3) convergence (they stabilize as they progress).
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{traceplot}\NormalTok{( InteractionsModelDiff )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
+
+\normalsize
+
+Finally, let's inspect the distribution of residuals. That is, we
+calculate all predictions, their distance from the actual values, and
+inspect the distribution of the distances:
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff)}
+\NormalTok{mu_mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , mean )}
+\NormalTok{mu_resid <-}\StringTok{ }\NormalTok{summaries}\OperatorTok{$}\NormalTok{AdiffS }\OperatorTok{-}\StringTok{ }\NormalTok{mu_mean}
+\KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
+
+\normalsize
 

### 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
bayesian report

@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r treatmentHist,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 ggplot(summaries[summaries$group != "control",], aes(x = IC, fill = group))+
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r violEmpiricalAdiff,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 violAdiffS <- ggplot(summaries, aes(x=group, y = AdiffS))+
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r violEpmiricalCdiff,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 violCdiffS <- ggplot(summaries, aes(x=group, y = CdiffS))+
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
+```{r ic,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
 icplot1 <- ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
+```{r icc,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
 icCplot1 <- ggplot(summaries, aes(x = IC, y = CdiffS, color = group, fill = group))+
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r correlations,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 summariesCorr <- select(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r dag1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
 dag <- dagitty("
@@
 
-# Bayesian models and their priors
+In fact, we will be predicting the difference between attacks before and after, and the difference between comments, before and after.
+Let's add them to the dag to double-check our selection of variables.
+
+```{r dag2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+dag2 <- dagitty("
+  dag{
+                CDS -> ADS -> IC  ons
+                U [unobserved]   
+                U -> CBS -> ABS  
+                U -> ABS        
+                U -> CDS -> ADS  
+                U -> ADS         
+                U -> CAS -> AAS    
+                U -> AAS                        
+                IC -> AAS        
+                IC -> CAS        
+                IT -> CAS        
+                IT -> AAS
+                CBS -> CDS -> CAS
+                ABS -> ADS -> AAS
+                ABS -> AdiffS
+                AAS -> AdiffS
+                CBS -> CdiffS
+                CAS -> CdiffS
+                }")
+set.seed(123)
+drawdag(dag2)
+adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "AdiffS")
+adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "CdiffS")
+```
+
+# Bayesian models, priors and diagnostics
 

### 2021-09-10 bayesianAnalysis/bayesianReport.tex
bayesian report

@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-4-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-5-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-10-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
 
@@
 
-\section{Bayesian models and their
-priors}\label{bayesian-models-and-their-priors}
+In fact, we will be predicting the difference between attacks before and
+after, and the difference between comments, before and after. Let's add
+them to the dag to double-check our selection of variables.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{dag2 <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
+\StringTok{  dag\{}
+\StringTok{                CDS -> ADS -> IC  ons}
+\StringTok{                U [unobserved]   }
+\StringTok{                U -> CBS -> ABS  }
+\StringTok{                U -> ABS        }
+\StringTok{                U -> CDS -> ADS  }
+\StringTok{                U -> ADS         }
+\StringTok{                U -> CAS -> AAS    }
+\StringTok{                U -> AAS                        }
+\StringTok{                IC -> AAS        }
+\StringTok{                IC -> CAS        }
+\StringTok{                IT -> CAS        }
+\StringTok{                IT -> AAS}
+\StringTok{                CBS -> CDS -> CAS}
+\StringTok{                ABS -> ADS -> AAS}
+\StringTok{                ABS -> AdiffS}
+\StringTok{                AAS -> AdiffS}
+\StringTok{                CBS -> CdiffS}
+\StringTok{                CAS -> CdiffS}
+\StringTok{                \}"}\NormalTok{)}
+\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+\KeywordTok{drawdag}\NormalTok{(dag2)}
+\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## { ADS }
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CdiffS"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## { ADS }
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
+
+\section{Bayesian models, priors and
+diagnostics}\label{bayesian-models-priors-and-diagnostics}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
 
@@
 \NormalTok{mu_resid <-}\StringTok{ }\NormalTok{summaries}\OperatorTok{$}\NormalTok{AdiffS }\OperatorTok{-}\StringTok{ }\NormalTok{mu_mean}
-\KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}
+\KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
 

### 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
comparing models

@@
 \mathsf{AdiffS} & \sim \textsf{Norm}(\mu, \sigma)\\
-mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
+\mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
@@
 ggplot()+geom_density(aes(x = mu_resid))+theme_tufte()+
-  ggtitle("Residuals are approximately normally distributed")
+  ggtitle("Residuals are approximately normally distributed")+xlab("residuals")
 ```
@@
 
+# Model selection
+
+How did we get to this fairly complicated model though?
+Once preliminary causal considerations guided our restrictions on variable selection, we proceed by building models of increasing complexity, and comparing them in terms of Widely Acceptable Information Criterion.
+The models differ mostly in the underlying linear formulae.
+For computational ease we will here use quadratic approximations, while in the final analysis we will deploy Hamiltionian Monte Carlo.
+The names are meant to decode the model structure: the predictors are listed before dashes, whereas interactions are listed after dashes.
+
+\begin{align}
+\tag{Null}  \mu_i & = \alpha\\
+\tag{ADS}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS}\\
+\tag{ADSIC}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
+\tag{IT}  \mu_i & = \beta_{\mathsf{group}[i]} \\
+\tag{ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]}\\
+\tag{ADSITIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
+\tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITIT-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
+\tag{ADSITIC-ADSIT-ICIT-ADSIC}   \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS}  + \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \\ & \nonumber  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} +
+ \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{CBS}} \times \mathsf{CBS} \\
+\tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber \end{align}
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+null <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu ~ dnorm (0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries  
+)
+
+ADS <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS+ bIC * IC,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    bIC ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+IT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  bIT[groupID] ,
+    bIT[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSIT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID],
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC_ADSIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIT_ADSIC_ADSIT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSIT_ADSIT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] ,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    #bADSIC ~ dnorm(0,.5),
+    bIT[groupID] ~ dnorm(0,.3),
+    #bIC ~ dnorm(0,.5),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC_ADSIT_ICIT_ADSIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
+      bADSIC * ADS * IC,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITICCBS_ITIC_ADSIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS *CBS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+Final <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+```
+\normalsize
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+comparison<- compare(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,ADSITIT_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ICIT_ADSIC,ADSITICCBS_ITIC_ADSIC,Final)
+plot(comparison)
+```
+\normalsize
+
 #  References {-}

### 2021-09-10 bayesianAnalysis/bayesianReport.tex
comparing models

@@
 \KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}
+\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"residuals"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
+
+\normalsize
+
+\section{Model selection}\label{model-selection}
+
+How did we get to this fairly complicated model though? Once preliminary
+causal considerations guided our restrictions on variable selection, we
+proceed by building models of increasing complexity, and comparing them
+in terms of Widely Acceptable Information Criterion. The models differ
+mostly in the underlying linear formulae. For computational ease we will
+here use quadratic approximations, while in the final analysis we will
+deploy Hamiltionian Monte Carlo. The names are meant to decode the model
+structure: the predictors are listed before dashes, whereas interactions
+are listed after dashes.
+
+\begin{align}
+\tag{Null}  \mu_i & = \alpha\\
+\tag{ADS}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS}\\
+\tag{ADSIC}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
+\tag{IT}  \mu_i & = \beta_{\mathsf{group}[i]} \\
+\tag{ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]}\\
+\tag{ADSITIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
+\tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITIT-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
+\tag{ADSITIC-ADSIT-ICIT-ADSIC}   \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS}  + \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \\ & \nonumber  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} +
+ \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{CBS}} \times \mathsf{CBS} \\
+\tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber \end{align}
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{null <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries  }
+\NormalTok{)}
+
+\NormalTok{ADS <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS}\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{IT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{bIT[groupID] ,}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID],}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIT_ADSIC_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] ,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{#bADSIC ~ dnorm(0,.5),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{#bIC ~ dnorm(0,.5),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC_ADSIT_ICIT_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICCBS_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS }\OperatorTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{Final <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,ADSITIT_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ICIT_ADSIC,ADSITICCBS_ITIC_ADSIC,Final)}
+\KeywordTok{plot}\NormalTok{(comparison)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
 

### 2021-09-10 bayesianModelsDiff.R

@@ -17,7 +17,7 @@ summaries$groupID <-  as.integer( as.factor(summaries$group) )
 
 nullModelProps <- quap(
   alist(
-    ApropS ~ dnorm( mu, sigma ),
+    AdiffS ~ dnorm( mu, sigma ),
     mu ~ dnorm (0,0.5),
     sigma  ~ dexp(1)
   ), 

### 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
comparing models

@@
 comparison<- compare(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,ADSITIT_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ICIT_ADSIC,ADSITICCBS_ITIC_ADSIC,Final)
+data.frame(comparison )
 plot(comparison)

### 2021-09-13 bayesianAnalysis/bayesianReport.Rmd
comparing models

--- 2021-09-10 bayesianAnalysis/bayesianReport.Rmd
@@
 
-Some experimentation leads to the value of $\sigma =3$, which leads to the following priors:
+Some experimentation leads to the value of $\sigma =.3$, which leads to the following priors:
 
@@
 \tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITIT-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITIC-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
 \tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
  \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
-\tag{ADSITIC-ADSIT-ICIT-ADSIC}   \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
- \mathsf{ADS}  + \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \\ & \nonumber  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} +
- \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{CBS}} \times \mathsf{CBS} \\
+\tag{ADSITIC-ADSIT-ITIC-ADSIC}   \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times \mathsf{ADS} + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ \nonumber & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS}  + \beta_{\mathsf{group}[i]} +   \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ & \nonumber  + \beta_{\mathsf{CBS}} \times \mathsf{CBS} +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}  \\
 \tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
- & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber \end{align}
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber\\
+ \tag{tooFAr} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} + \beta_{\mathsf{CBSIC}}\times
+ \mathsf{CBS} \times \mathsf{IC}\end{align}
 
@@
 
-ADSITIT_ADSIC_ADSIT <- quap(
+ADSITIC_ADSIC_ADSIT <- quap(
   alist(
@@
 
-ADSITIC_ADSIT_ICIT_ADSIC <- quap(
+ADSITIC_ADSIT_ITIC_ADSIC <- quap(
   alist(
@@
 
+tooFar <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC, 
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+     bCBSIC ~ dnorm(0, .3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
 ```
@@
 ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
-comparison<- compare(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,ADSITIT_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ICIT_ADSIC,ADSITICCBS_ITIC_ADSIC,Final)
+comparison<- compare(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,
+                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,
+                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)
+mykable(data.frame(comparison )) 
 plot(comparison)
@@
 
+The three models that stand out  differ in including $\mathsf{CBS}$ as a predictor.
+Moreover the final model includes an interaction between  treatment group and $\mathsf{CBS}$.
+Adding a further interaction between $\mathsf{CBS}$ and $\mathsf{IC}$ takes us too far.
+$WAIC$-based weighing assigns the weight of $83\%$ to the final model, and the standard errors for the difference in WAIC for the top three models is fairly low,  so we will employ the top model ($\mathsf{Final}$) in   further analyses.
+
 #  References {-}

### 2021-09-13 bayesianAnalysis/bayesianReport.tex
comparing models

@@
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
 \documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{xcolor}
+\usepackage{hyperref}
 \hypersetup{
@@
             linkcolor=Maroon,
+            filecolor=Maroon,
             citecolor=Blue,
@@
 \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
 \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
 \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-\section{Exploration}\label{exploration}
+\hypertarget{exploration}{%
+\section{Exploration}\label{exploration}}
 
@@
 
-\vspace{1mm} \footnotesize
+\vspace{1mm}
+\footnotesize
 
@@
 \end{table}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
-
 \normalsize
@@
 
-\section{Causal inference}\label{causal-inference}
+\hypertarget{causal-inference}{%
+\section{Causal inference}\label{causal-inference}}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
-
 \normalsize
@@
 
+\hypertarget{bayesian-models-priors-and-diagnostics}{%
 \section{Bayesian models, priors and
-diagnostics}\label{bayesian-models-priors-and-diagnostics}
+diagnostics}\label{bayesian-models-priors-and-diagnostics}}
 
@@
 
-\NormalTok{##prior predictive checks sd =1}
+\CommentTok{##prior predictive checks sd =1}
 \NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
-
-\normalsize
-
-Some experimentation leads to the value of \(\sigma =3\), which leads to
-the following priors:
-
-\vspace{1mm} \footnotesize
+\normalsize
+
+Some experimentation leads to the value of \(\sigma =.3\), which leads
+to the following priors:
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
-
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
-
-\normalsize
-
-\section{Model selection}\label{model-selection}
+\normalsize
+
+\hypertarget{model-selection}{%
+\section{Model selection}\label{model-selection}}
 
@@
 \tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITIT-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITIC-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
 \tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
  \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
-\tag{ADSITIC-ADSIT-ICIT-ADSIC}   \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  + \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
- \mathsf{ADS}  + \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  + \\ & \nonumber  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} +
- \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{CBS}} \times \mathsf{CBS} \\
+\tag{ADSITIC-ADSIT-ITIC-ADSIC}   \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times \mathsf{ADS} + \beta_{\mathsf{group}[i]} +  
+\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ \nonumber & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
+\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
+ \mathsf{ADS}  + \beta_{\mathsf{group}[i]} +   \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ & \nonumber  + \beta_{\mathsf{CBS}} \times \mathsf{CBS} +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}  \\
 \tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
- & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber \end{align}
-
-\vspace{1mm} \footnotesize
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber\\
+ \tag{tooFAr} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} + \beta_{\mathsf{CBSIC}}\times
+ \mathsf{CBS} \times \mathsf{IC}\end{align}
+
+\vspace{1mm}
+\footnotesize
 
@@
 
-\NormalTok{ADSITIT_ADSIC_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+\NormalTok{ADSITIC_ADSIC_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
   \KeywordTok{alist}\NormalTok{(}
@@
 
-\NormalTok{ADSITIC_ADSIT_ICIT_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+\NormalTok{ADSITIC_ADSIT_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
   \KeywordTok{alist}\NormalTok{(}
@@
 \NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,ADSITIT_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ICIT_ADSIC,ADSITICCBS_ITIC_ADSIC,Final)}
+
+\NormalTok{tooFar <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC, }
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{     bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,}
+\NormalTok{                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,}
+\NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
+\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison )) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}[H]
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\begin{tabular}{lrrrrrr}
+\toprule
+  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
+\midrule
+\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8393664}\\
+tooFar & 1189.257 & 90.39801 & 4.616272 & 2.884162 & 29.81499 & 0.0834720\\
+\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0771616}\\
+null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
+\cellcolor{gray!6}{IT} & \cellcolor{gray!6}{1345.879} & \cellcolor{gray!6}{144.64185} & \cellcolor{gray!6}{161.237934} & \cellcolor{gray!6}{132.478842} & \cellcolor{gray!6}{19.27433} & \cellcolor{gray!6}{0.0000000}\\
+\addlinespace
+ADSIT & 1348.714 & 142.29377 & 164.072877 & 130.485213 & 23.06652 & 0.0000000\\
+\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
+ADSIT\_ADSIT & 1351.571 & 154.69385 & 166.930496 & 140.429304 & 31.91506 & 0.0000000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
+ADSITIC & 1353.603 & 147.38084 & 168.962571 & 134.581071 & 28.54365 & 0.0000000\\
+\addlinespace
+\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1353.939} & \cellcolor{gray!6}{147.29717} & \cellcolor{gray!6}{169.298374} & \cellcolor{gray!6}{134.821036} & \cellcolor{gray!6}{26.91553} & \cellcolor{gray!6}{0.0000000}\\
+ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.442} & \cellcolor{gray!6}{155.55820} & \cellcolor{gray!6}{170.800602} & \cellcolor{gray!6}{140.950680} & \cellcolor{gray!6}{34.03861} & \cellcolor{gray!6}{0.0000000}\\
+\bottomrule
+\end{tabular}
+\endgroup{}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \KeywordTok{plot}\NormalTok{(comparison)}
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
-
-\normalsize
-
-\section*{References}\label{references}
+\normalsize
+
+The three models that stand out differ in including \(\mathsf{CBS}\) as
+a predictor. Moreover the final model includes an interaction between
+treatment group and \(\mathsf{CBS}\). Adding a further interaction
+between \(\mathsf{CBS}\) and \(\mathsf{IC}\) takes us too far.
+\(WAIC\)-based weighing assigns the weight of \(83\%\) to the final
+model, and the standard errors for the difference in WAIC for the top
+three models is fairly low, so we will employ the top model
+(\(\mathsf{Final}\)) in further analyses.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}

### 2021-09-13 bayesianAnalysis/bayesianReport.Rmd
comparing models

@@
 
+# Inspecting the model and effect sizes
+
+We start by using the \textsf{Final} model formula to build a model, this time using Hamiltionian Monte Carlo.
+We leave the code commented out and load a pre-compiled model for computational convenience
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+# FinalHMC <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +
+#     bIC[groupID] * IC + bADSIC * ADS * IC+
+#     bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ),
+#   data = summaries
+# )
+# saveRDS(FinalHMC, file = "models/FinalHMC.rds")
+
+FinalHMC <- readRDS(file = "models/FinalHMC.rds")
+```
+\normalsize
+First, let's take a look at the best model coefficients.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+precis(FinalHMC, depth = 2)
+plot(precis(FinalHMC, depth = 2))
+```
+\normalsize
+
+These, however, are notoriously hard to interpret in models with interactions. For this reason, it is better to plot predicted effects for various combinations of predictors.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+visGroup <- function (model, ADS, CBS, xmin =2, ymax = -3)
+{
+groupID <- 1:3
+IC <- 5 
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+posterior <- extract.samples(model, n = 1e5)
+mu <- link( model, data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+means <-  round(apply(mu , 2 , mean ), 2)
+mu_HPDI <- round(apply( mu , 2 , HPDI ),2)
+means <- as.data.frame(means)
+means$group <- rownames(means)
+rownames(means) <- NULL
+meansDisp <- cbind(means,t(as.data.frame(mu_HPDI)))
+meansDisp <- meansDisp[,c(1,3,4)]
+
+plot <- ggplot(muLong)+geom_violin(aes(x = group, y = AdiffS), alpha = 0.2)+
+  xlab("")+
+  labs(title = paste("ADS=", ADS, ", CBS=",  CBS, ", IC=5", sep = ""))+
+  theme_tufte(base_size = 6)
+#+ 
+#  annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
+return(plot)
+}
+
+visGroupA2C_2 <- visGroup(model = FinalHMC, ADS = 2,CBS = -2 , ymax = -2)
+visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
+visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2, ymax = -3.5 )
+
+visGroupA0C_2 <- visGroup(model = FinalHMC, ADS = 0,CBS = -2 , ymax = -2)
+visGroupA0C0 <- visGroup(model = FinalHMC, ADS = 0,CBS = 0 )
+visGroupA0C2 <-  visGroup(model = FinalHMC, ADS = 0,CBS = 2, ymax = -4 )
+
+visGroupA2C_2 <-  visGroup(model = FinalHMC, ADS = 2,CBS = -2 , ymax = -2)
+visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
+visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2, ymax = -4 )
+
+visGroupJoint <- ggarrange(visGroupA2C_2 , visGroupA2C0,visGroupA2C2, 
+          visGroupA0C_2, visGroupA0C0, visGroupA0C2,
+          visGroupA2C_2, visGroupA2C0, visGroupA2C2, ncol =3, nrow = 3)
+
+visGroupJoint
+```
+\normalsize
+
 #  References {-}

### 2021-09-13 bayesianAnalysis/bayesianReport.tex
comparing models

@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
 \documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \usepackage{unicode-math}
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 }{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{xcolor}
-\usepackage{hyperref}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
 \hypersetup{
@@
             linkcolor=Maroon,
-            filecolor=Maroon,
             citecolor=Blue,
@@
 \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
 \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
 \newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-\hypertarget{exploration}{%
-\section{Exploration}\label{exploration}}
+\section{Exploration}\label{exploration}
 
@@
 
-\vspace{1mm}
-\footnotesize
+\vspace{1mm} \footnotesize
 
@@
 \end{table}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
+
 \normalsize
@@
 
-\hypertarget{causal-inference}{%
-\section{Causal inference}\label{causal-inference}}
+\section{Causal inference}\label{causal-inference}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
+
 \normalsize
@@
 
-\hypertarget{bayesian-models-priors-and-diagnostics}{%
 \section{Bayesian models, priors and
-diagnostics}\label{bayesian-models-priors-and-diagnostics}}
+diagnostics}\label{bayesian-models-priors-and-diagnostics}
 
@@
 
-\CommentTok{##prior predictive checks sd =1}
+\NormalTok{##prior predictive checks sd =1}
 \NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
+
 \normalsize
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
-\normalsize
-
-\hypertarget{model-selection}{%
-\section{Model selection}\label{model-selection}}
+
+\normalsize
+
+\section{Model selection}\label{model-selection}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
+
 \normalsize
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
+\section{Inspecting the model and effect
+sizes}\label{inspecting-the-model-and-effect-sizes}
+
+We start by using the \textsf{Final} model formula to build a model,
+this time using Hamiltionian Monte Carlo. We leave the code commented
+out and load a pre-compiled model for computational convenience
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# FinalHMC <- ulam(}
+\CommentTok{#   alist(}
+\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
+\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +}
+\CommentTok{#     bIC[groupID] * IC + bADSIC * ADS * IC+}
+\CommentTok{#     bCBS[groupID] *CBS,}
+\CommentTok{#     a ~ dnorm (0,0.3),}
+\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bADSIC ~ dnorm(0,.3),}
+\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     sigma  ~ dexp(1)}
+\CommentTok{#   ),}
+\CommentTok{#   data = summaries}
+\CommentTok{# )}
+\CommentTok{# saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
+
+\NormalTok{FinalHMC <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/FinalHMC.rds"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+First, let's take a look at the best model coefficients.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+0.0414089\\
+\hline
+0.1979211\\
+\hline
+0.2484756\\
+\hline
+-0.1097667\\
+\hline
+-0.0042060\\
+\hline
+-0.5142899\\
+\hline
+-0.0919148\\
+\hline
+-0.5302840\\
+\hline
+-0.0212337\\
+\hline
+0.1482970\\
+\hline
+-0.0686005\\
+\hline
+-0.0037630\\
+\hline
+-0.0117801\\
+\hline
+0.0118155\\
+\hline
+0.7945882\\
+\hline
+\end{tabular}
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+0.1562753\\
+\hline
+0.0568494\\
+\hline
+0.1546028\\
+\hline
+0.1014546\\
+\hline
+0.0051643\\
+\hline
+0.0414267\\
+\hline
+0.1245614\\
+\hline
+0.1088835\\
+\hline
+0.1630179\\
+\hline
+0.1857528\\
+\hline
+0.1776783\\
+\hline
+0.3161707\\
+\hline
+0.0256771\\
+\hline
+0.0185521\\
+\hline
+0.0277774\\
+\hline
+\end{tabular}
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+-0.2037740\\
+\hline
+0.1086423\\
+\hline
+0.0036955\\
+\hline
+-0.2678764\\
+\hline
+-0.0122338\\
+\hline
+-0.5776731\\
+\hline
+-0.2965873\\
+\hline
+-0.7023272\\
+\hline
+-0.2603815\\
+\hline
+-0.1246834\\
+\hline
+-0.3448157\\
+\hline
+-0.5084313\\
+\hline
+-0.0529960\\
+\hline
+-0.0192521\\
+\hline
+0.7535960\\
+\hline
+\end{tabular}
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+0.2796946\\
+\hline
+0.2907669\\
+\hline
+0.4942282\\
+\hline
+0.0628934\\
+\hline
+0.0040408\\
+\hline
+-0.4463925\\
+\hline
+0.1059034\\
+\hline
+-0.3593766\\
+\hline
+0.2295494\\
+\hline
+0.4367149\\
+\hline
+0.2099344\\
+\hline
+0.4981378\\
+\hline
+0.0290304\\
+\hline
+0.0412303\\
+\hline
+0.8434971\\
+\hline
+\end{tabular}
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+228.1593\\
+\hline
+768.4216\\
+\hline
+526.1494\\
+\hline
+418.0876\\
+\hline
+361.1195\\
+\hline
+722.3116\\
+\hline
+671.6673\\
+\hline
+823.7157\\
+\hline
+219.0190\\
+\hline
+304.7859\\
+\hline
+295.3412\\
+\hline
+829.2326\\
+\hline
+488.1809\\
+\hline
+612.3810\\
+\hline
+693.5845\\
+\hline
+\end{tabular}
+\centering
+\begin{tabular}[t]{r}
+\hline
+x\\
+\hline
+0.9980513\\
+\hline
+1.0013137\\
+\hline
+0.9995921\\
+\hline
+0.9980791\\
+\hline
+0.9983620\\
+\hline
+0.9991926\\
+\hline
+0.9998084\\
+\hline
+0.9980583\\
+\hline
+0.9980137\\
+\hline
+0.9980345\\
+\hline
+0.9980482\\
+\hline
+1.0011451\\
+\hline
+0.9994090\\
+\hline
+0.9986804\\
+\hline
+0.9982674\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{plot}\NormalTok{(}\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
+
+\normalsize
+
+These, however, are notoriously hard to interpret in models with
+interactions. For this reason, it is better to plot predicted effects
+for various combinations of predictors.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visGroup <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, }\DataTypeTok{xmin =}\DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-3}\NormalTok{)}
+\NormalTok{\{}
+\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{IC <-}\StringTok{ }\DecValTok{5} 
+\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+\NormalTok{posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
+\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
+\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\NormalTok{means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
+\NormalTok{mu_HPDI <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
+\NormalTok{means <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(means)}
+\NormalTok{means}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{rownames}\NormalTok{(means)}
+\KeywordTok{rownames}\NormalTok{(means) <-}\StringTok{ }\OtherTok{NULL}
+\NormalTok{meansDisp <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(mu_HPDI)))}
+\NormalTok{meansDisp <-}\StringTok{ }\NormalTok{meansDisp[,}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
+
+\NormalTok{plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS, }\StringTok{", IC=5"}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{6}\NormalTok{)}
+\CommentTok{#+ }
+\CommentTok{#  annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
+\KeywordTok{return}\NormalTok{(plot)}
+\NormalTok{\}}
+
+\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \FloatTok{-3.5}\NormalTok{ )}
+
+\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}
+
+\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}
+
+\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\NormalTok{ , visGroupA2C0,visGroupA2C2, }
+\NormalTok{          visGroupA0C_}\DecValTok{2}\NormalTok{, visGroupA0C0, visGroupA0C2,}
+\NormalTok{          visGroupA2C_}\DecValTok{2}\NormalTok{, visGroupA2C0, visGroupA2C2, }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visGroupJoint}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
+
+\normalsize
+
+\section*{References}\label{references}
 \addcontentsline{toc}{section}{References}

### 2021-09-13 predictionInteractionsProps.R

@@ -17,6 +17,27 @@ ggplot()+geom_histogram(aes(x=summaries$AdiffS))
 noChange <-(0 - mean(summaries$Adiff))/sd(summaries$Adiff)
 averageChange <- mean(summaries$Adiff[summaries$group == "control"])
 
+# FinalHMC <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS + 
+#     bIT[groupID] + bIC[groupID] * IC + 
+#       bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ),
+#   data = summaries
+# )
+
+# saveRDS(FinalHMC, file = "models/FinalHMC.rds")
+
+FinalHMC <- readRDS(file = "models/FinalHMC.rds")
+
 
 # InteractionsModelDiff <- ulam(
 #   alist(
@@ -151,25 +172,58 @@ ggsave("images/priorsIC03.pdf", width = 20, height = 15, units = "cm", dpi = 450
 
 #now moving to posteriors, first by group
 #first by group for ADS = CBS = 0
+
+model <- FinalHMC
 ADS <- 0
 CBS <- 0
+xmin <-  2
+ymax <- -3
+
+visGroup <- function (model, ADS, CBS, xmin =2, ymax = -3)
+{
 groupID <- 1:3
 IC <- 5 
 data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
-data
-posterior <- extract.samples(InteractionsModelDiff, n = 1e5)
-mu <- link( InteractionsModelDiff, data=data ) 
-head(mu)
+posterior <- extract.samples(model, n = 1e5)
+mu <- link( model, data=data ) 
 colnames(mu) <- levels(summaries$group)
 muLong <- melt(mu)
 colnames(muLong) <- c("id", "group", "AdiffS")
-head(muLong)
-means <-  apply(mu , 2 , mean )
+means <-  round(apply(mu , 2 , mean ), 2)
[…]

### 2021-09-13 bayesianAnalysis/predictionsInteractions.R
laptop

@@ -1,5 +1,18 @@
 source("utils/plotPriors.R")
 
+
+library(ggplot2)
+library(ggthemes)
+library(gridExtra)
+library(kableExtra)
+library(viridis)
+library(rethinking)
+library(ggpubr)
+library(tidyverse)
+library(GGally)
+library(dagitty)
+library(reshape)
+
 summaries <- readRDS(file = "datasets/Summaries.rds")
 
 
@@ -46,7 +59,29 @@ LotsOfInteractionsModel3ulam <- ulam(
   data = summaries
 )
 
+# FinalHMC <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +
+#     bIC[groupID] * IC + bADSIC * ADS * IC+
+#     bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ),
+#   data = summaries
+# )
+# 
+# getwd()
+# saveRDS(FinalHMC, file = "models/FinalHMC.rds")
 
+FinalHMC <- readRDS(file = "models/FinalHMC.rds")
+
+traceplot(FinalHMC)
 
 #prior predictive check
 summary(summaries)

### 2021-09-14 bayesianAnalysis/bayesianReport.Rmd
adding contrasts

--- 2021-09-13 bayesianAnalysis/bayesianReport.Rmd
@@
 mykable <- function(object) {kable(object, "latex", booktabs = T) %>% kable_styling(latex_options = "striped",font_size = 9)}
+
+removeX <-   theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+removeY <-   theme(axis.title.y=element_blank(),
+                   axis.text.y=element_blank(),
+                   axis.ticks.y=element_blank())
 
@@
 
+# Inspecting the model and effect sizes
+
+We start by using the \textsf{Final} model formula to build a model, this time using Hamiltionian Monte Carlo.
+We leave the code commented out and load a pre-compiled model for computational convenience
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+# FinalHMC <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +
+#     bIC[groupID] * IC + bADSIC * ADS * IC+
+#     bCBS[groupID] *CBS,
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     sigma  ~ dexp(1)
+#   ),
+#   data = summaries
+# )
+# saveRDS(FinalHMC, file = "models/FinalHMC.rds")
+
+FinalHMC <- readRDS(file = "models/FinalHMC.rds")
+```
+\normalsize
+First, let's take a look at the best model coefficients.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+precis(FinalHMC, depth = 2)
+plot(precis(FinalHMC, depth = 2))
+```
+\normalsize
+
+These, however, are notoriously hard to interpret in models with interactions. For this reason, it is better to plot predicted effects for various combinations of predictors.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
+
+visGroup <- function (model, ADS, CBS, xmin =2, ymax = -3)
+{
+groupID <- 1:3
+IC <- 5 
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+posterior <- extract.samples(model, n = 1e5)
+mu <- link( model, data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+means <-  round(apply(mu , 2 , mean ), 2)
+mu_HPDI <- round(apply( mu , 2 , HPDI ),2)
+means <- as.data.frame(means)
+means$group <- rownames(means)
+rownames(means) <- NULL
+meansDisp <- cbind(means,t(as.data.frame(mu_HPDI)))
+meansDisp <- meansDisp[,c(1,3,4)]
+
+plot <- ggplot(muLong)+geom_violin(aes(x = group, y = AdiffS), alpha = 0.2)+
+  xlab("")+
+  labs(title = paste("ADS=", ADS, ", CBS=",  CBS,  sep = ""))+
+  theme_tufte()+ylim(c(-4,4))
+#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
+return(plot)
+}
+
+visGroupA2C_2 <- visGroup(model = FinalHMC, ADS = 2,CBS = -2)
+visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
+visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2)
+
+visGroupA0C_2 <- visGroup(model = FinalHMC, ADS = 0,CBS = -2 )
+visGroupA0C0 <- visGroup(model = FinalHMC, ADS = 0,CBS = 0 )
+visGroupA0C2 <-  visGroup(model = FinalHMC, ADS = 0,CBS = 2)
+
+visGroupA2C_2 <-  visGroup(model = FinalHMC, ADS = 2,CBS = -2 )
+visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
+visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2 )
+
+visGroupJoint <- ggarrange(visGroupA2C_2+removeX + ggtitle("CBS = -2")+ylab("ADS = 2") , visGroupA2C0+theme_void()+ ggtitle("CBS = 0"),visGroupA2C2+theme_void()+ ggtitle("CBS = 2"), 
+          visGroupA0C_2+removeX+ylab("ADS = 0")+ggtitle(""), visGroupA0C0+theme_void()+ggtitle(""), visGroupA0C2+theme_void()+ggtitle(""),
+          visGroupA2C_2+ylab("ADS = -2")+ggtitle(""), visGroupA2C0+removeY+ggtitle(""), visGroupA2C2+removeY+ggtitle(""), ncol =3, nrow = 3)
+
+visGroupJoint2 <- annotate_figure(visGroupJoint, 
+  top = text_grob("(range restricted to (-4,4), IC at the rounded mean = 5)",
+                  size = 10))
+visGroupJoint3 <- annotate_figure(visGroupJoint2, 
+  top = text_grob("Predicted change in attacks by activity type and treatment groups (standardized)",
+                  size = 12))
+
+visGroupJoint3 
+```
+\normalsize
+
+To gain more clarity, let's look at predicted contrasts, here understood as distances from the control group mean, by activity types, first versus CBS, then versus ADS.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE}
+visContrastsCBS <- function(model = FinalHMC, ADS = ADS , IC =  5,
+                            CBS = seq(-3,3,by  = 0.1))
+  {
+  groupID <- 1:3
+  data <- expand.grid(ADS, groupID, IC , CBS)
+  colnames(data) <- c("ADS", "groupID", "IC", "CBS")
+  posterior <- extract.samples(model, n = 1e5)
+  link( model, data=data ) 
+  mu <- link( model, data=data ) 
+  means <-  round(apply(mu , 2 , mean ), 4)
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrast <- cbind(data,means,t(as.data.frame(HPDIs)))
+
+  ones <- 3 * (1:(nrow(visContrast)/3))-2
+  twos <- 3 * (1:(nrow(visContrast)/3))-1
+  threes <- 3 * (1:(nrow(visContrast)/3))
+
+  colnames(visContrast)[c(6,7)] <- c("low", "high")
+  contrast <- numeric(nrow(visContrast))
+  cLow <- numeric(nrow(visContrast))
+  cHigh <- numeric(nrow(visContrast))
+  for(i in threes){
+  contrast[i] <- visContrast$means[i] - visContrast$means[i-2]  
+  }
+  for(i in twos){
+  contrast[i] <- visContrast$means[i] - visContrast$means[i-1]  
+  }
+  visContrast$contrast <- contrast
+  visContrast$shift <-  visContrast$contrast - visContrast$means
+  for(i in ones){
+  visContrast$shift[i] <- 0
+  }
+  visContrast$cLow <- visContrast$low + visContrast$shift
+  visContrast$cHigh <- visContrast$high + visContrast$shift
+
+  visContrast$group = rep(c("control", "empathy", "normative"), 
+                          nrow(visContrast)/3)
+
+  visContrastTreatment <- visContrast[groupID !=1,]
+
+  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, color = group ))+
+            geom_pointrange(mapping = 
+        aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5) +theme_tufte())
+}
+
+visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
+      ggtitle("ADS=-2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS=0")+
+        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS=2")+
+        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.1)), ncol = 3)
+
+visContrastCBSJoint2 <- annotate_figure(visContrastCBSJoint, 
+      top = text_grob("(range restricted to (-2.5,2.5), IC at the rounded mean = 5)",
+                                size = 10))
+visContrastCBSJoint3 <- annotate_figure(visContrastCBSJoint2, 
+top = text_grob("Predicted distance from the control group mean vs. CBS  (standardized)",
+                                size = 12))
+
+visContrastCBSJoint3
+```
+\normalsize
+
 #  References {-}

### 2021-09-14 bayesianAnalysis/bayesianReport.tex
adding contrasts

@@
 \StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS, }\StringTok{", IC=5"}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{6}\NormalTok{)}
-\CommentTok{#+ }
-\CommentTok{#  annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS,  }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
+\CommentTok{#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
 \KeywordTok{return}\NormalTok{(plot)}
@@
 
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}
 \NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \FloatTok{-3.5}\NormalTok{ )}
-
-\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
 \NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}
-
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
 \NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}
-
-\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\NormalTok{ , visGroupA2C0,visGroupA2C2, }
-\NormalTok{          visGroupA0C_}\DecValTok{2}\NormalTok{, visGroupA0C0, visGroupA0C2,}
-\NormalTok{          visGroupA2C_}\DecValTok{2}\NormalTok{, visGroupA2C0, visGroupA2C2, }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visGroupJoint}
+\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{ )}
+
+\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{) , visGroupA2C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),visGroupA2C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{), }
+\NormalTok{          visGroupA0C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{          visGroupA2C_}\DecValTok{2}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C0}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C2}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visGroupJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint, }
+  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-4,4), IC at the rounded mean = 5)"}\NormalTok{,}
+                  \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visGroupJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint2, }
+  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted change in attacks by activity type and treatment groups (standardized)"}\NormalTok{,}
+                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visGroupJoint3 }
 \end{Highlighting}
@@
 \begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
+
+\normalsize
+
+To gain more clarity, let's look at predicted contrasts, here understood
+as distances from the control group mean, by activity types, first
+versus CBS, then versus ADS.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsCBS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =}\NormalTok{ ADS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{,}
+                            \DataTypeTok{CBS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\NormalTok{  \{}
+\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(ADS, groupID, IC , CBS)}
+  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+  \KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrast <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
+\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
+\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
+
+  \KeywordTok{colnames}\NormalTok{(visContrast)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrast <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cLow <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cHigh <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrast}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                          \KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+
+\NormalTok{  visContrastTreatment <-}\StringTok{ }\NormalTok{visContrast[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
+        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{\}}
+
+\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
+\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=-2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=0"}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=2"}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.1}\NormalTok{)), }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visContrastCBSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint, }
+      \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastCBSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint2, }
+\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. CBS  (standardized)"}\NormalTok{,}
+                                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastCBSJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
 

### 2021-09-14 predictionInteractionsProps.R

@@ -1,5 +1,14 @@
 source("utils/plotPriors.R")
 
+removeX <-   theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+
+removeY <-   theme(axis.title.y=element_blank(),
+                   axis.text.y=element_blank(),
+                   axis.ticks.y=element_blank())
+
+
 summaries <- readRDS(file = "datasets/Summaries.rds")
 summaries$ABS <- standardize(summaries$AB)
 summaries$CBS <- standardize(summaries$CB)
@@ -199,117 +208,185 @@ meansDisp <- meansDisp[,c(1,3,4)]
 
 plot <- ggplot(muLong)+geom_violin(aes(x = group, y = AdiffS), alpha = 0.2)+
   xlab("")+
-  labs(title = paste("ADS=", ADS, ", CBS=",  CBS, ", IC=5", sep = ""))+
-  theme_tufte()+ 
-  annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
+  labs(title = paste("ADS=", ADS, ", CBS=",  CBS,  sep = ""))+
+  theme_tufte()+ylim(c(-4,4))
+#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
 return(plot)
 }
 
 
-visGroupA2C_2 <- visGroup(model = FinalHMC, ADS = 2,CBS = -2 , ymax = -2)
+visGroupA2C_2 <- visGroup(model = FinalHMC, ADS = 2,CBS = -2)
 visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
-visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2, ymax = -3.5 )
+visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2)
 
-visGroupA0C_2 <- visGroup(model = FinalHMC, ADS = 0,CBS = -2 , ymax = -2)
+visGroupA0C_2 <- visGroup(model = FinalHMC, ADS = 0,CBS = -2 )
 visGroupA0C0 <- visGroup(model = FinalHMC, ADS = 0,CBS = 0 )
-visGroupA0C2 <-  visGroup(model = FinalHMC, ADS = 0,CBS = 2, ymax = -4 )
[…]

### 2021-09-14 bayesianAnalysis/bayesianReport.Rmd
dfirst draft of bayesian analysis done

@@
             geom_pointrange(mapping = 
-        aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5) +theme_tufte())
+        aes(ymin = cLow, ymax = cHigh), size = .05, 
+        fatten = .1, alpha = .5,
+        position = position_dodge(width = .8))+
+          theme_tufte())
 }
@@
 visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
-      ggtitle("ADS=-2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
-          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS=0")+
-        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
-        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS=2")+
-        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.1)), ncol = 3)
+      ggtitle("ADS = -2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS = 0")+
+        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
+        removeY,
+        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS = 2")+
+        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.15))+
+        removeY, ncol = 3)
 
@@
 
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold",out.width = "100%", warning = FALSE, message = FALSE}
+
+visContrastsADS <- function(model = FinalHMC, CBS = CBS , IC =  5, 
+                            ADS = seq(-3,3,by  = 0.1))
+{
+  data <- expand.grid(CBS, groupID, IC , ADS)
+  colnames(data) <- c("CBS", "groupID", "IC", "ADS")
+  posterior <- extract.samples(model, n = 1e5)
+  mu <- link( model, data=data ) 
+  means <-  round(apply(mu , 2 , mean ), 4)
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrastADS <- cbind(data,means,t(as.data.frame(HPDIs)))
+
+  ones <- 3 * (1:(nrow(visContrastADS)/3))-2
+  twos <- 3 * (1:(nrow(visContrastADS)/3))-1
+  threes <- 3 * (1:(nrow(visContrastADS)/3))
+
+  colnames(visContrastADS)[c(6,7)] <- c("low", "high")
+  contrastADS <- numeric(nrow(visContrastADS))
+  for(i in threes){
+    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-2]  
+  }
+  for(i in twos){
+    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-1]  
+  }
+  visContrastADS$contrast <- contrastADS
+  visContrastADS$shift <-  visContrastADS$contrast - visContrastADS$means
+  for(i in ones){
+    visContrastADS$shift[i] <- 0
+  }
+  visContrastADS$cLow <- visContrastADS$low + visContrastADS$shift
+  visContrastADS$cHigh <- visContrastADS$high + visContrastADS$shift
+
+  visContrastADS$group = rep(c("control", "empathy", "normative"), 
+                             nrow(visContrastADS)/3)
+  visContrastTreatmentADS <- visContrastADS[groupID !=1,]
+
+  return(ggplot(visContrastTreatmentADS, aes(x = ADS, y = contrast, color = group ))+
+  geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .05,
+                  fatten = .1, alpha = .5, 
+                  position = position_dodge(width = .8)) +theme_tufte())
+}
+
+visContrastADSJoint <- ggarrange(visContrastsADS(FinalHMC,CBS = -2)+ggtitle("CBS = -2")
+                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+                                 visContrastsADS(FinalHMC,CBS = 0)+ggtitle("CBS = 0")
+                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
+                                   removeY,
+                                 visContrastsADS(FinalHMC,CBS = 2)+ggtitle("CBS = 2")
+                                 +ylim(c(-2.5,2.5))+
+                                   theme(legend.position = c(0.75, 0.15))+
+                                   removeY, ncol = 3)
+
+visContrastADSJoint2 <- annotate_figure(visContrastADSJoint, 
+top = text_grob("(range restricted to (-2.5,2.5), IC at the rounded mean = 5)",
+                                                        size = 10))
+visContrastADSJoint3 <- annotate_figure(visContrastADSJoint2, 
+top = text_grob("Predicted distance from the control group mean vs. ADS (standardized)",
+                                                        size = 12))
+
+visContrastADSJoint3
+```
+\normalsize
+
+Now, let's inspect the impact of intervention counts by treatment type by looking at contrasts (distances from the control group mean) with 89% HPDIs by IC.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
+visContrastsIC <- function(model = FinalHMC, CBS = CBS , IC =  seq(0,30,by = 1), ADS = ADS)
+{
+  groupID <- 1:3
+  data <- expand.grid(CBS, groupID, IC , ADS)
+  data
+  colnames(data) <- c("CBS", "groupID", "IC", "ADS")
+  posterior <- extract.samples(model, n = 1e5)
+  mu <- link( model, data=data ) 
+  means <-  round(apply(mu , 2 , mean ), 4)
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrastIC <- cbind(data,means,t(as.data.frame(HPDIs)))
+
+  ones <- 3 * (1:(nrow(visContrastIC)/3))-2
+  twos <- 3 * (1:(nrow(visContrastIC)/3))-1
+  threes <- 3 * (1:(nrow(visContrastIC)/3))
+
+  colnames(visContrastIC)[c(6,7)] <- c("low", "high")
+  contrastIC <- numeric(nrow(visContrastIC))
+  for(i in threes){
+    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-2]  
+  }
+  for(i in twos){
+    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-1]  
+  }
+  visContrastIC$contrast <- contrastIC
+  visContrastIC$shift <-  visContrastIC$contrast - visContrastIC$means
+  for(i in ones){
+    visContrastIC$shift[i] <- 0
+  }
+  visContrastIC$cLow <- visContrastIC$low + visContrastIC$shift
+  visContrastIC$cHigh <- visContrastIC$high + visContrastIC$shift
+
+  visContrastIC$group = rep(c("control", "empathy", "normative"), nrow(visContrastIC)/3)
+  visContrastTreatmentIC <- visContrastIC[groupID !=1,]
+
+  return(ggplot(visContrastTreatmentIC, aes(x = IC, y = contrast, color = group ))+
+    geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5)+
+    ylim(c(-2,2)) +theme_tufte())
+}
+
+visContrastsICJoint <- ggarrange(
+visContrastsIC(ADS = 2, CBS = -2)+removeX+ 
+               theme(legend.position = c(0.3, 0.9),
+                     legend.key.size = unit(.3, 'cm'),
+                     legend.key.height = unit(.3, 'cm'),
+                     legend.key.width = unit(.3, 'cm'),
+                     legend.title= element_blank())+
+  ggtitle("CBS = -2")+
+  ylab("ADS = 2"),
+    visContrastsIC(ADS = 2, CBS = 0)+removeY+removeX+ scale_color_discrete(guide=FALSE)+
+  ggtitle("CBS = 0"),
+    visContrastsIC(ADS = 2, CBS = 2)+removeY+removeX+ggtitle("CBS = 2")+ scale_color_discrete(guide=FALSE),
+visContrastsIC(ADS = 0, CBS = -2)+removeX+ scale_color_discrete(guide=FALSE)+
+  ylab("ADS = 0"),
+    visContrastsIC(ADS = 0, CBS = 0)+removeY+removeX+ 
+  scale_color_discrete(guide=FALSE),
+    visContrastsIC(ADS = 0, CBS = 2)+removeY+removeX+ scale_color_discrete(guide=FALSE),  
+visContrastsIC(ADS = -2, CBS = -2)+ scale_color_discrete(guide=FALSE)+
+  ylab("ADS = -2"),
+    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE),
+    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE), 
+ncol = 3, nrow = 3
+)
+
+visContrastsICJoint2 <- annotate_figure(visContrastsICJoint, 
+top = text_grob("(range restricted to (-3,3))", 
+                size = 10))
+visContrastsICJoint3 <- annotate_figure(visContrastsICJoint2, 
+ top = text_grob("Predicted distance from the control group mean vs. IC (standardized)",
+                size = 12))
+
+visContrastsICJoint3
+```
+\normalsize
+
 #  References {-}

### 2021-09-14 bayesianAnalysis/bayesianReport.tex
dfirst draft of bayesian analysis done

@@
 \StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
-        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{, }
+        \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{,}
+        \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{))}\OperatorTok{+}
+\StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
 \NormalTok{\}}
@@
 \NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
-\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=-2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=0"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=2"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.1}\NormalTok{)), }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
+\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\NormalTok{removeY,}
+        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
+\StringTok{        }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
 
@@
 
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsADS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{, }
+                            \DataTypeTok{ADS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\NormalTok{\{}
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
+  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastADS <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
+\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
+\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
+
+  \KeywordTok{colnames}\NormalTok{(visContrastADS)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastADS <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastADS}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrastADS}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                             \KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentADS <-}\StringTok{ }\NormalTok{visContrastADS[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{,}
+                  \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{, }
+                  \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{\}}
+
+\NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
+                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
+                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{                                   }\NormalTok{removeY,}
+                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
+                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}
+\StringTok{                                   }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
+\StringTok{                                   }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visContrastADSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint, }
+\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastADSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint2, }
+\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. ADS (standardized)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastADSJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
+
+\normalsize
+
+Now, let's inspect the impact of intervention counts by treatment type
+by looking at contrasts (distances from the control group mean) with
+89\% HPDIs by IC.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsIC <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{30}\NormalTok{,}\DataTypeTok{by =} \DecValTok{1}\NormalTok{), }\DataTypeTok{ADS =}\NormalTok{ ADS)}
+\NormalTok{\{}
+\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
+\NormalTok{  data}
+  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastIC <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
+\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
+\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
+
+  \KeywordTok{colnames}\NormalTok{(visContrastIC)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastIC <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastIC}
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrastIC}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentIC <-}\StringTok{ }\NormalTok{visContrastIC[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{    }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{)}\OperatorTok{+}
+\StringTok{    }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{\}}
+
+\NormalTok{visContrastsICJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}
+\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
+\StringTok{               }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.3}\NormalTok{, }\FloatTok{0.9}\NormalTok{),}
+                     \DataTypeTok{legend.key.size =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
+                     \DataTypeTok{legend.key.height =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
+                     \DataTypeTok{legend.key.width =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
+                     \DataTypeTok{legend.title=} \KeywordTok{element_blank}\NormalTok{())}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),  }
+\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{), }
+\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}
+\NormalTok{)}
+
+\NormalTok{visContrastsICJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint, }
+\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-3,3))"}\NormalTok{, }
+                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastsICJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint2, }
+ \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. IC (standardized)"}\NormalTok{,}
+                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastsICJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-17-1} \end{center}
+
+\normalsize
+
 \section*{References}\label{references}

### 2021-09-14 predictionInteractionsProps.R

@@ -344,11 +344,6 @@ visContrastsADS <- function(model = FinalHMC, CBS = CBS , IC =  5, ADS = seq(-3,
 
 
 
-visContrastsADS(FinalHMC,CBS = -2)
-visContrastsADS(FinalHMC,CBS = 0)
-visContrastsADS(FinalHMC,CBS = 2)
-
-
 
 
 
@@ -367,6 +362,86 @@ visContrastADSJoint3 <- annotate_figure(visContrastADSJoint2,
 
 
 visContrastADSJoint3
+
+
+
+
+
+
+#NOW IC
+
+
+ADS <- 0
+CBS <- 0
+IC <-  seq(0,40,by = 1)
+model <- FinalHMC
+
+
+visContrastsIC <- function(model = FinalHMC, CBS = CBS , IC =  seq(0,30,by = 1), ADS = ADS)
+{
+  groupID <- 1:3
+  data <- expand.grid(CBS, groupID, IC , ADS)
+  data
+  colnames(data) <- c("CBS", "groupID", "IC", "ADS")
+  posterior <- extract.samples(model, n = 1e5)
+  mu <- link( model, data=data ) 
+  means <-  round(apply(mu , 2 , mean ), 4)
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrastIC <- cbind(data,means,t(as.data.frame(HPDIs)))
+  
+  ones <- 3 * (1:(nrow(visContrastIC)/3))-2
+  twos <- 3 * (1:(nrow(visContrastIC)/3))-1
+  threes <- 3 * (1:(nrow(visContrastIC)/3))
+  
+  colnames(visContrastIC)[c(6,7)] <- c("low", "high")
+  contrastIC <- numeric(nrow(visContrastIC))
+  for(i in threes){
+    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-2]  
+  }
+  for(i in twos){
+    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-1]  
+  }
+  visContrastIC$contrast <- contrastIC
+  visContrastIC$shift <-  visContrastIC$contrast - visContrastIC$means
+  for(i in ones){
+    visContrastIC$shift[i] <- 0
+  }
+  visContrastIC$cLow <- visContrastIC$low + visContrastIC$shift
+  visContrastIC$cHigh <- visContrastIC$high + visContrastIC$shift
+  
[…]

### 2021-09-14 bayesianAnalysis/commentsAnalysis.R
stated comments

@@ -1,0 +1,328 @@
+library(ggplot2)
+library(ggthemes)
+library(gridExtra)
+library(kableExtra)
+library(viridis)
+library(rethinking)
+library(ggplot2)
+library(ggpubr)
+library(tidyverse)
+library(GGally)
+library(dagitty)
+library(reshape)
+
+
+
+removeX <-   theme(axis.title.x=element_blank(),
+                   axis.text.x=element_blank(),
+                   axis.ticks.x=element_blank())
+
+removeY <-   theme(axis.title.y=element_blank(),
+                   axis.text.y=element_blank(),
+                   axis.ticks.y=element_blank())
+
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+summaries$group <- as.factor(summaries$group)
+summaries$groupID <-  as.integer( as.factor(summaries$group) )
+
+
+head(summaries)
+
+
+cNull <- quap(
+  alist(
+    CdiffS ~ dnorm( mu, sigma ),
+    mu ~ dnorm (0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries  
+)
+
+
+cADS <- quap(
+  alist(
+    CdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+
+cADSIC <- quap(
+  alist(
+    CdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS+ bIC * IC,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    bIC ~ dnorm(0,0.3),
[…]

### 2021-09-16 bayesianAnalysis/bayesianReport.tex
direct effect

@@
 \StringTok{  dag\{}
-\StringTok{  CDS -> ADS -> IC  ons}
+\StringTok{  CDS -> ADS -> IC  }
 \StringTok{               U [unobserved]   }
@@
 \StringTok{               \}"}\NormalTok{)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+\KeywordTok{coordinates}\NormalTok{(dag)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## $x
+## AAS ABS ADS CAS CBS CDS  IC  IT   U 
+##  NA  NA  NA  NA  NA  NA  NA  NA  NA 
+## 
+## $y
+## AAS ABS ADS CAS CBS CDS  IC  IT   U 
+##  NA  NA  NA  NA  NA  NA  NA  NA  NA
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{coordinates}\NormalTok{( dag ) <-}\StringTok{ }\KeywordTok{list}\NormalTok{( }\DataTypeTok{x=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{CDS=}\DecValTok{1}\NormalTok{,}\DataTypeTok{ADS=}\DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{,}
+                    \DataTypeTok{AAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{U =} \FloatTok{.5}\NormalTok{) ,}
+\DataTypeTok{y=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS =}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS =} \DecValTok{1}\NormalTok{,}\DataTypeTok{CDS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{ADS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{1}\NormalTok{, }
+    \DataTypeTok{IT =} \FloatTok{.3}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{.7}\NormalTok{, }\DataTypeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{) )}
 \KeywordTok{drawdag}\NormalTok{(dag)}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
 
@@
 \textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
-line with the adjustment set identified algorithmically, and the same
-move makes sense when we want to predict \textsf{CAS}.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AAS"}\NormalTok{)}
+line with the adjustment set identified algorithmically.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AAS"}\NormalTok{, }\DataTypeTok{type =} \StringTok{"all"}\NormalTok{)}
 \end{Highlighting}
@@
 ## { ADS }
+## { ABS, ADS }
+## { ADS, CBS }
+## { ABS, ADS, CBS }
+## { ADS, CDS }
+## { ABS, ADS, CDS }
+## { ADS, CBS, CDS }
+## { ABS, ADS, CBS, CDS }
+## { ADS, U }
+## { ABS, ADS, U }
+## { ADS, CBS, U }
+## { ABS, ADS, CBS, U }
+## { ADS, CDS, U }
+## { ABS, ADS, CDS, U }
+## { ADS, CBS, CDS, U }
+## { ABS, ADS, CBS, CDS, U }
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CAS"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## { ADS }
-\end{verbatim}
-
-\normalsize
-
-It's open season for other variables, and our decision to include them
-in the model will be guided by information-theoretic criteria of
-predictive power.
+\normalsize
 
@@
 \StringTok{  dag\{}
-\StringTok{                CDS -> ADS -> IC  ons}
+\StringTok{                CDS -> ADS -> IC  }
 \StringTok{                U [unobserved]   }
@@
 \StringTok{                \}"}\NormalTok{)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+\KeywordTok{coordinates}\NormalTok{( dag2 ) <-}\StringTok{ }\KeywordTok{list}\NormalTok{( }\DataTypeTok{x=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{CDS=}\DecValTok{1}\NormalTok{,}\DataTypeTok{ADS=}\DecValTok{1}\NormalTok{,}
+    \DataTypeTok{CAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{U =} \FloatTok{.5}\NormalTok{, }\DataTypeTok{AdiffS=} \FloatTok{2.5}\NormalTok{, }\DataTypeTok{CdiffS =} \FloatTok{2.5}\NormalTok{) ,}
+\DataTypeTok{y=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS =}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS =} \DecValTok{1}\NormalTok{,}\DataTypeTok{CDS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{ADS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{.3}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{.7}\NormalTok{, }\DataTypeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{, }\DataTypeTok{CdiffS =} \FloatTok{-.2}\NormalTok{,  }\DataTypeTok{AdiffS =} \FloatTok{1.2}\NormalTok{) )}
+
 \KeywordTok{drawdag}\NormalTok{(dag2)}
-\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{)}
+\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{, }\DataTypeTok{type =} \StringTok{"canonical"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-## { ADS }
+## { ABS, ADS, CBS, CDS }
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CdiffS"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## { ADS }
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
+
+Finding a maximal sensible set (canonical) of covariates suggests
+inlcuding \textsf{CDS} and \textsf{ABS}. As already discussed, we do not
+include \textsf{CDS} because of its strong correlation with
+\textsf{CBS}. We also do not condition on \textsf{ABS}---not only
+because it has a pretty strong correlation with another predictor
+(\textsf{ADS}), but rather mainly because it is used to define the
+output variable. In such a set-up, of course that a model including
+\textsf{ABS} would have better predictive power, but since a
+definitional connection is present, thinking that its inclusion in the
+model tells us something about causality would be misled.
+
+It's open season for the other variables (and interactions between
+them), and our decision to include them in the model will be guided by
+information-theoretic criteria of predictive power.
 
@@
 
-\begin{table}[H]
+\begin{table}
 \centering\begingroup\fontsize{9}{11}\selectfont
@@
 \midrule
-\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8393664}\\
-tooFar & 1189.257 & 90.39801 & 4.616272 & 2.884162 & 29.81499 & 0.0834720\\
-\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0771616}\\
+\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8345169}\\
+tooFar & 1189.123 & 90.35400 & 4.481669 & 2.882584 & 29.76051 & 0.0887673\\
+\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0767158}\\
 null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
@@
 \cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
-ADSIT\_ADSIT & 1351.571 & 154.69385 & 166.930496 & 140.429304 & 31.91506 & 0.0000000\\
+ADSIT\_ADSIT & 1350.941 & 153.88118 & 166.300056 & 139.579270 & 32.04695 & 0.0000000\\
 \cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
@@
 \addlinespace
-\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1353.939} & \cellcolor{gray!6}{147.29717} & \cellcolor{gray!6}{169.298374} & \cellcolor{gray!6}{134.821036} & \cellcolor{gray!6}{26.91553} & \cellcolor{gray!6}{0.0000000}\\
+\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1355.210} & \cellcolor{gray!6}{148.15271} & \cellcolor{gray!6}{170.568848} & \cellcolor{gray!6}{135.609996} & \cellcolor{gray!6}{27.22326} & \cellcolor{gray!6}{0.0000000}\\
 ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
@@
 \CommentTok{# saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
+
+\CommentTok{#saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
 

### 2021-09-16 bayesianAnalysis/bayesianReport2.Rmd
direct effect

--- 2021-09-14 bayesianAnalysis/bayesianReport.Rmd
@@
 \footnotesize
-```{r dag1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r dag1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%"}
 dag <- dagitty("
   dag{
-  CDS -> ADS -> IC  ons
+  CDS -> ADS -> IC  
                U [unobserved]   
@@
                }")
-set.seed(123)
+coordinates(dag)
+coordinates( dag ) <- list( x=c(CBS=0,ABS=0,CDS=1,ADS=1, CAS = 2,
+                    AAS = 2, IT = 1.5, IC = 1.5, U = .5) ,
+y=c(CBS =0,ABS = 1,CDS = 0,ADS = 1, CAS = 0, AAS = 1, 
+    IT = .3, IC = .7, U =.5) )
 drawdag(dag)
@@
 Moreover there is only one directed indirect path, it goes through \textsf{CAS}, so we should not condition on it if we are to identify causal effect on attacks mediated by impact on comments (unless we care about the direct effect of \textsf{IC}  and \textsf{IT} on \textsf{AAS}, but that's a separate question).
-This is in line with the adjustment set identified algorithmically, and the same move makes sense when we want to predict \textsf{CAS}.
+This is in line with the adjustment set identified algorithmically.
 
@@
 ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
-adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS")
-adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "CAS")
-```
-\normalsize
-
-It's open season for other variables, and our decision to include them in the model will be guided by information-theoretic criteria of predictive power.
+adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS", type = "all")
+```
+\normalsize
+
+The situation is different when it comes to evaluating the *direct* effect of intervention. Then, we also need to block indirect causal paths from the intervention to the outcome.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS", effect = "direct")
+```
+\normalsize
+
+For such an evaluation we need to also condition on \textsf{CAS}, which is what we will do when we turn to the study of the direct effects of the interventions.
 
@@
 
-```{r dag2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+```{r dag2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%"}
 dag2 <- dagitty("
   dag{
-                CDS -> ADS -> IC  ons
+                CDS -> ADS -> IC  
                 U [unobserved]   
@@
                 }")
-set.seed(123)
+coordinates( dag2 ) <- list( x=c(CBS=0,ABS=0,CDS=1,ADS=1,
+    CAS = 2, AAS = 2, IT = 1.5, IC = 1.5, U = .5, AdiffS= 2.5, CdiffS = 2.5) ,
+y=c(CBS =0,ABS = 1,CDS = 0,ADS = 1, CAS = 0, AAS = 1, IT = .3, IC = .7, U =.5, CdiffS = -.2,  AdiffS = 1.2) )
+
 drawdag(dag2)
-adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "AdiffS")
-adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "CdiffS")
-```
+adjustmentSets(dag2, exposure = c("IC", "IT"), outcome = "AdiffS", type = "canonical")
+```
+
+Finding a maximal sensible set (canonical) of covariates suggests inlcuding \textsf{CDS} and \textsf{ABS}.
+As already discussed, we do not include \textsf{CDS} because of its strong correlation with \textsf{CBS}.
+We also do not condition on \textsf{ABS}---not only because it has a pretty strong correlation with another predictor (\textsf{ADS}), but rather mainly because it is used to define the output variable.
+In such a set-up, of course that a model including \textsf{ABS} would have better predictive power, but since a definitional connection is present, thinking that its inclusion in the model tells us something about causality  would be misled.
+
+It's open season for the  other variables (and interactions between them), and our decision to include them in the model will be guided by information-theoretic criteria of predictive power.
 
@@
 # saveRDS(FinalHMC, file = "models/FinalHMC.rds")
+
+#saveRDS(FinalHMC, file = "models/FinalHMC.rds")
 

### 2021-09-16 bayesianAnalysis/bayesianReport3.Rmd
direct effect

--- 2021-09-16 bayesianAnalysis/bayesianReport2.Rmd
@@
 
-The situation is different when it comes to evaluating the *direct* effect of intervention. Then, we also need to block indirect causal paths from the intervention to the outcome.
-
-\vspace{1mm}
-\footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
-adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS", effect = "direct")
-```
-\normalsize
-
+The situation is different when it comes to evaluating the *direct* effect of intervention.
+Then, we also need to block indirect causal paths from the intervention to the outcome.
 For such an evaluation we need to also condition on \textsf{CAS}, which is what we will do when we turn to the study of the direct effects of the interventions.
@@
 
-# Bayesian models, priors and diagnostics
-
 We will focus on a class of additive models where the outcome variable is normally distributed around the predicted mean, which is a linear function of predictors (possibly with some interactions).
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
+```{r priors1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
 # building model with sd=1
@@
 \footnotesize
-```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
+```{r priors03,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results= "hide"}
 #prior predictive check sd =.3
@@
 \normalsize
-
-<!-- # InteractionsModelDiff <- ulam( -->
-<!-- #   alist( -->
-<!-- #     AdiffS ~ dnorm( mu, sigma ), -->
-<!-- #     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + bADSIC * ADS * IC+ bCBS[groupID] *CBS, -->
-<!-- #     a ~ dnorm (0,0.3), -->
-<!-- #     bADS[groupID] ~ dnorm(0,.3), -->
-<!-- #     bADSIC ~ dnorm(0,.3), -->
-<!-- #     bCBS[groupID] ~ dnorm(0,.3), -->
-<!-- #     bIT[groupID] ~ dnorm(0,.3), -->
-<!-- #     bIC[groupID] ~ dnorm(0,.3), -->
-<!-- #     sigma  ~ dexp(1) -->
-<!-- #   ),  -->
-<!-- #   data = summaries -->
-<!-- # ) -->
 
@@
                      ADSITICCBS_ITIC_ADSIC,Final, tooFar)
-mykable(data.frame(comparison )) 
+mykable(round(data.frame(comparison ),3)) 
 plot(comparison)
@@
 ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
-precis(FinalHMC, depth = 2)
+mykable(data.frame(precis(FinalHMC, depth = 2)))
 plot(precis(FinalHMC, depth = 2))
@@
 
-  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, color = group ))+
-            geom_pointrange(mapping = 
-        aes(ymin = cLow, ymax = cHigh), size = .05, 
-        fatten = .1, alpha = .5,
-        position = position_dodge(width = .8))+
+  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, fill = group ))+
+           geom_line(se = FALSE)+
+            geom_ribbon(mapping = 
+        aes(ymin = cLow, ymax = cHigh),  
+         alpha = .3)+
           theme_tufte())
@@
 visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
-      ggtitle("ADS = -2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+      ggtitle("ADS = -2")+ylim(c(-2.5,2.5))+ scale_fill_discrete(guide=FALSE),
           visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS = 0")+
-        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
+        ylim(c(-2.5,2.5))+ scale_fill_discrete(guide=FALSE)+
         removeY,
@@
 
-  return(ggplot(visContrastTreatmentADS, aes(x = ADS, y = contrast, color = group ))+
-  geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .05,
-                  fatten = .1, alpha = .5, 
-                  position = position_dodge(width = .8)) +theme_tufte())
+  return(ggplot(visContrastTreatmentADS, aes(x = ADS, y = contrast, fill = group ))+
+           geom_line(se = FALSE) +
+  geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), 
+       alpha = .3) +theme_tufte())
 }
@@
 visContrastADSJoint <- ggarrange(visContrastsADS(FinalHMC,CBS = -2)+ggtitle("CBS = -2")
-                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
+                                 +ylim(c(-2.5,2.5))+ scale_fill_discrete(guide=FALSE),
                                  visContrastsADS(FinalHMC,CBS = 0)+ggtitle("CBS = 0")
-                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
+                                 +ylim(c(-2.5,2.5))+ scale_fill_discrete(guide=FALSE)+
                                    removeY,
@@
 Now, let's inspect the impact of intervention counts by treatment type by looking at contrasts (distances from the control group mean) with 89% HPDIs by IC.
+Notice the predicted effect of \textsf{IC} is weaker than group membership, so for visibility the $y$-axis has a smaller range.
+Also, not enough data was available to reliably estimate uncertainty for \textsf{IC} above 20, hence the restriction on the $x$-axis (arleady at lower values, lack of estimates is visible for the more extreme  covariate settings).
 
@@
 ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
-visContrastsIC <- function(model = FinalHMC, CBS = CBS , IC =  seq(0,30,by = 1), ADS = ADS)
+visContrastsIC <- function(model = FinalHMC, CBS = CBS ,
+                           IC =  seq(0,20,by = 1), ADS = ADS)
 {
@@
 
-  visContrastIC$group = rep(c("control", "empathy", "normative"), nrow(visContrastIC)/3)
+  visContrastIC$group = rep(c("control", "empathy", "normative"),
+                            nrow(visContrastIC)/3)
   visContrastTreatmentIC <- visContrastIC[groupID !=1,]
 
-  return(ggplot(visContrastTreatmentIC, aes(x = IC, y = contrast, color = group ))+
-    geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5)+
-    ylim(c(-2,2)) +theme_tufte())
+  return(ggplot(visContrastTreatmentIC, aes(x = IC, y = contrast, fill = group ))+
+           geom_line(se=FALSE)+
+    geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = .3)+
+    ylim(c(-2,2)) +theme_tufte()+geom_hline(yintercept = 0, lty =2, size = 0.1))
 }
@@
   ylab("ADS = 2"),
-    visContrastsIC(ADS = 2, CBS = 0)+removeY+removeX+ scale_color_discrete(guide=FALSE)+
+    visContrastsIC(ADS = 2, CBS = 0)+removeY+removeX+ scale_fill_discrete(guide=FALSE)+
   ggtitle("CBS = 0"),
-    visContrastsIC(ADS = 2, CBS = 2)+removeY+removeX+ggtitle("CBS = 2")+ scale_color_discrete(guide=FALSE),
-visContrastsIC(ADS = 0, CBS = -2)+removeX+ scale_color_discrete(guide=FALSE)+
+    visContrastsIC(ADS = 2, CBS = 2)+removeY+removeX+ggtitle("CBS = 2")+ scale_fill_discrete(guide=FALSE),
+visContrastsIC(ADS = 0, CBS = -2)+removeX+ scale_fill_discrete(guide=FALSE)+
   ylab("ADS = 0"),
     visContrastsIC(ADS = 0, CBS = 0)+removeY+removeX+ 
-  scale_color_discrete(guide=FALSE),
-    visContrastsIC(ADS = 0, CBS = 2)+removeY+removeX+ scale_color_discrete(guide=FALSE),  
-visContrastsIC(ADS = -2, CBS = -2)+ scale_color_discrete(guide=FALSE)+
+  scale_fill_discrete(guide=FALSE),
+    visContrastsIC(ADS = 0, CBS = 2)+removeY+removeX+ scale_fill_discrete(guide=FALSE),  
+visContrastsIC(ADS = -2, CBS = -2)+ scale_fill_discrete(guide=FALSE)+
   ylab("ADS = -2"),
-    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE),
-    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE), 
+    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_fill_discrete(guide=FALSE),
+    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_fill_discrete(guide=FALSE), 
 ncol = 3, nrow = 3
@@
 
+# Direct effect
+
+Models for the evaluation of direct effect need to close the indirect causal path from the treatment variables to the output, and they do so by conditioning on \textsf{CAS}.
+Again, we face model selection.
+We repeat all the model structures from the previous section, except for now, each model is extended with \textsf{CAS} as a predictor.
+This time the model structure we called \textsf{tooFar} turns out to do better.
+We also consider extending it with interactions between \textsf{CAS} and \textsf{IT} and \textsf{IC} (jointly and separately), but this results in no further improvement.
+
+\vspace{1mm}
+\footnotesize
+```{r comparisonDirectModels,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+nullDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries  
+)
+
+ADSDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS+ bIC * IC+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    bIC ~ dnorm(0,0.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ITDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  bIT[groupID] + bCAS * CAS,
+    bIT[groupID] ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID]+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC_ADSICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bADSIC ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC_ADSIC_ADSITDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSIT_ADSITDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    #bADSIC ~ dnorm(0,.5),
+    bIT[groupID] ~ dnorm(0,.3),
+    #bIC ~ dnorm(0,.5),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITIC_ADSIT_ITIC_ADSICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
+      bADSIC * ADS * IC + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSITICCBS_ITIC_ADSICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS *CBS + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+FinalDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+tooFarDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS * CAS, 
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    bCBSIC ~ dnorm(0, .3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+tooFarDirect_CASIT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS[groupID] * CAS, 
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS[groupID] ~ dnorm(0,0.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    bCBSIC ~ dnorm(0, .3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+tooFarDirect_CASIC <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS * CAS + bCASIC * CAS * IC, 
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS ~ dnorm(0,0.3),
+    bCASIC ~ dnorm(0,0.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    bCBSIC ~ dnorm(0, .3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+tooFarDirect_CASIC_CASIT <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS[groupID] * CAS + bCASIC * CAS * IC, 
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCAS[groupID] ~ dnorm(0,0.3),
+    bCASIC ~ dnorm(0,0.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    bCBSIC ~ dnorm(0, .3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+comparisonDirect<- compare(nullDirect,ADSDirect,ADSICDirect,ITDirect,ADSITDirect,ADSITICDirect,ADSITIC_ADSICDirect, ADSITIC_ADSIC_ADSITDirect,ADSIT_ADSITDirect,ADSITIC_ADSIT_ITIC_ADSICDirect,
+                     ADSITICCBS_ITIC_ADSICDirect,FinalDirect, tooFarDirect,tooFarDirect_CASIT,
+                     tooFarDirect_CASIC,tooFarDirect_CASIC_CASIT)
+
+mykable(round(data.frame(comparisonDirect),3))%>% kable_styling(latex_options = c("striped","scale_down"),font_size = 9)
+
+plot(comparisonDirect)
+
+```
+\normalsize
+
+Let's build a Hamiltonian Monte Carlo with the same formula:
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+
+# tooFarDirectHMC <- ulam(
+#   alist(
+#     AdiffS ~ dnorm( mu, sigma ),
+#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + 
+#       bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS * CAS, 
+#     a ~ dnorm (0,0.3),
+#     bADS[groupID] ~ dnorm(0,.3),
+#     bADSIC ~ dnorm(0,.3),
+#     bCAS ~ dnorm(0,0.3),
+#     bCBS[groupID] ~ dnorm(0,.3),
+#     bIT[groupID] ~ dnorm(0,.3),
+#     bIC[groupID] ~ dnorm(0,.3),
+#     bCBSIC ~ dnorm(0, .3),
+#     sigma  ~ dexp(1)
+#   ), 
+#   data = summaries
+# )
+
+#saveRDS(tooFarDirectHMC, file = "models/tooFarDirectHMC.rds")
+
+tooFarDirectHMC <- readRDS(file = "models/tooFarDirectHMC.rds")
+```
+\normalsize
+
+For a big picture, let's look at predicted direct effect by group and user activity profile.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
+
+visGroupDirect <- function (model, ADS, CBS, CAS, xmin =2, ymax = -3)
+{
+  groupID <- 1:3
+  IC <- 5 
+  data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, CAS = CAS, IC =  IC)
+  posterior <- extract.samples(model, n = 1e5)
+  mu <- link( model, data=data ) 
+  colnames(mu) <- levels(summaries$group)
+  muLong <- melt(mu)
+  colnames(muLong) <- c("id", "group", "AdiffS")
+  means <-  round(apply(mu , 2 , mean ), 2)
+  mu_HPDI <- round(apply( mu , 2 , HPDI ),2)
+  means <- as.data.frame(means)
+  means$group <- rownames(means)
+  rownames(means) <- NULL
+  meansDisp <- cbind(means,t(as.data.frame(mu_HPDI)))
+  meansDisp <- meansDisp[,c(1,3,4)]
+
+  plot <- ggplot(muLong)+geom_violin(aes(x = group, y = AdiffS), alpha = 0.2)+
+    xlab("")+
+    labs(title = paste("ADS=", ADS, ", CBS=",  CBS, ", CAS=", CAS,  sep = ""))+
+    theme_tufte()+ylim(c(-4,4))
+  #+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
+  return(plot)
+}
+
+visGroupDirect2_2_2 <-  visGroupDirect(model = tooFarDirectHMC, ADS = 2,CBS = -2, CAS = -2)
+visGroupDirect200 <-  visGroupDirect(model = tooFarDirectHMC, ADS = 2,CBS = 0, CAS = 0)
+visGroupDirect222 <- visGroupDirect(model = tooFarDirectHMC, ADS = 2,CBS = 2, CAS = 2)
+
+visGroupDirect0_2_2 <-  visGroupDirect(model = tooFarDirectHMC, ADS = 0,CBS = -2, CAS = -2)
+visGroupDirect000 <-  visGroupDirect(model = tooFarDirectHMC, ADS = 0,CBS = 0, CAS = 0)
+visGroupDirect022 <- visGroupDirect(model = tooFarDirectHMC, ADS = 0,CBS = 2, CAS = 2)
+
+visGroupDirect_2_2_2 <-  visGroupDirect(model = tooFarDirectHMC, ADS = -2,CBS = -2, CAS = -2)
+visGroupDirect_200 <-  visGroupDirect(model = tooFarDirectHMC, ADS = -2,CBS = 0, CAS = 0)
+visGroupDirect_222 <- visGroupDirect(model = tooFarDirectHMC, ADS = -2,CBS = 2, CAS = 2)
+
+visGroupDirectJoint <- ggarrange(visGroupDirect2_2_2+removeX +ylab("ADS = 2")+ggtitle("CBS = CAS = -2"),
+                                 visGroupDirect200+removeX+removeY+ ggtitle("CBS = CAS = 0"),
+                                 visGroupDirect222+removeX+removeY+ ggtitle("CBS = CAS = 2") ,
+                        visGroupDirect0_2_2+removeX + ggtitle("")+ylab("ADS = 0"),
+                                visGroupDirect000+removeX+removeY+ ggtitle(""),
+                                visGroupDirect022+removeX+removeY+ ggtitle(""),
+                        visGroupDirect_2_2_2+removeX+ylab("ADS = -2")+ ggtitle(""),
+                                  visGroupDirect_200+removeX+removeY+ ggtitle(""),
+                        visGroupDirect_222+removeX+removeY+ ggtitle("")
+                                 ,ncol =3, nrow = 3)
+
+visGroupDirectJoint2 <- annotate_figure(visGroupDirectJoint, 
+                                  top = text_grob("(range restricted to (-4,4), IC at the rounded mean = 5)",
+                                                  size = 10))
+visGroupJoint3 <- annotate_figure(visGroupDirectJoint2, 
+                                  top = text_grob("Predicted direct effect of treatment group by activity profile (standardized)",
+                                                  size = 12))
+
+visGroupJoint3
+```
+\normalsize
+
+Now, predicted direct effect of five interventions vs. \textsf{CBS}, for three user activity profiles.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+visContrastsCBSDirect <- function(model = FinalHMC, ADS = ADS , CAS= CAS, IC =  5,
+                            CBS = seq(-3,3,by  = 0.1)){
+  groupID <- 1:3
+  data <- expand.grid(ADS, groupID, CAS, IC , CBS)
+  colnames(data) <- c("ADS", "groupID", "CAS", "IC", "CBS")
+  posterior <- extract.samples(model, n = 1e5)
+  link( model, data=data ) 
+  mu <- link( model, data=data )
+
+  means <-  round(apply(mu , 2 , mean ), 4)
+
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrast <- cbind(data,means,t(as.data.frame(HPDIs)))
+
+  ones <- 3 * (1:(nrow(visContrast)/3))-2
+  twos <- 3 * (1:(nrow(visContrast)/3))-1
+  threes <- 3 * (1:(nrow(visContrast)/3))
+
+  colnames(visContrast)[c(7,8)] <- c("low", "high")
+
+  contrast <- numeric(nrow(visContrast))
+  cLow <- numeric(nrow(visContrast))
+  cHigh <- numeric(nrow(visContrast))
+  for(i in threes){
+    contrast[i] <- visContrast$means[i] - visContrast$means[i-2]  
+  }
+  for(i in twos){
+    contrast[i] <- visContrast$means[i] - visContrast$means[i-1]  
+  }
+  visContrast$contrast <- contrast
+  visContrast$shift <-  visContrast$contrast - visContrast$means
+  for(i in ones){
+    visContrast$shift[i] <- 0
+  }
+  visContrast$cLow <- visContrast$low + visContrast$shift
+  visContrast$cHigh <- visContrast$high + visContrast$shift
+
+  visContrast$group = rep(c("control", "empathy", "normative"), 
+                          nrow(visContrast)/3)
+
+  visContrastTreatment <- visContrast[groupID !=1,]
+
+  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, fill = group ))+
+           geom_line(se = FALSE)+
+           geom_ribbon(mapping = 
+                         aes(ymin = cLow, ymax = cHigh),  
+                       alpha = .3)+
+           theme_tufte()+ylim(c(-3.5,3.5)))
+}
+
+visContrastDirect <-  ggarrange(visContrastsCBSDirect(model = tooFarDirect,ADS = -2, CAS = -2, IC = 5)+ggtitle("ADS = CAS = -2")+ scale_fill_discrete(guide=FALSE),
+          visContrastsCBSDirect(model = tooFarDirect,ADS = 0, CAS = 0, IC = 5) +ggtitle("ADS = CAS = 0")+ scale_fill_discrete(guide=FALSE)+removeY,
+          visContrastsCBSDirect(model = tooFarDirect,ADS = 2, CAS = 2, IC = 5) +ggtitle("ADS = CAS = 2")+ scale_fill_discrete(guide=FALSE)+removeY
+          ,ncol =3)
+
+visContrastDirect2 <- annotate_figure(visContrastDirect, 
+                                        top = text_grob("(range restricted to (-3.5,3.5), IC at the rounded mean = 5)",
+                                                        size = 10))
+visContrastDirect3 <- annotate_figure(visContrastDirect2, 
+                                        top = text_grob("Predicted direct effect distance from the control group mean vs. CBS  (standardized)",
+                                                        size = 12))
+
+visContrastDirect3
+```
+\normalsize
+
+Now contrasts against \textsf{ADS}, for three user profiles:
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+
+visContrastsADSDirect <- function(model = FinalHMC, CBS = CBS , CAS = CAS, IC =  5, 
+                            ADS = seq(-3,3,by  = 0.1))
+{
+  data <- expand.grid(CBS, groupID, CAS, IC , ADS)
+  colnames(data) <- c("CBS", "groupID", "CAS", "IC", "ADS")
+  posterior <- extract.samples(model, n = 1e5)
+  mu <- link( model, data=data ) 
+  means <-  round(apply(mu , 2 , mean ), 4)
+  HPDIs <- round(apply( mu , 2 , HPDI ),4)
+  visContrastADS <- cbind(data,means,t(as.data.frame(HPDIs)))
+
+  ones <- 3 * (1:(nrow(visContrastADS)/3))-2
+  twos <- 3 * (1:(nrow(visContrastADS)/3))-1
+  threes <- 3 * (1:(nrow(visContrastADS)/3))
+
+  colnames(visContrastADS)[c(7,8)] <- c("low", "high")
+  contrastADS <- numeric(nrow(visContrastADS))
+  for(i in threes){
+    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-2]  
+  }
+  for(i in twos){
+    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-1]  
+  }
+  visContrastADS$contrast <- contrastADS
+  visContrastADS$shift <-  visContrastADS$contrast - visContrastADS$means
+  for(i in ones){
+    visContrastADS$shift[i] <- 0
+  }
+  visContrastADS$cLow <- visContrastADS$low + visContrastADS$shift
+  visContrastADS$cHigh <- visContrastADS$high + visContrastADS$shift
+
+  visContrastADS$group = rep(c("control", "empathy", "normative"), 
+                             nrow(visContrastADS)/3)
+  visContrastTreatmentADS <- visContrastADS[groupID !=1,]
+
+  return(ggplot(visContrastTreatmentADS, aes(x = ADS, y = contrast, fill = group ))+
+           geom_line(se = FALSE) +
+           geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), 
+                       alpha = .3) +theme_tufte())
+}
+
+visContrastADSDirectJoint <- ggarrange(
+  visContrastsADSDirect(tooFarDirect,CBS = -2, CAS = -2)+ggtitle("CBS = CAS = -2")+ylim(c(-3,3))+ scale_fill_discrete(guide=FALSE),
+  visContrastsADSDirect(tooFarDirect, CBS = 0, CAS = 0)+ggtitle("CBS = CAS = 0")+ylim(c(-3,3))+ scale_fill_discrete(guide=FALSE),
+  visContrastsADSDirect(tooFarDirect, CBS = 2, CAS = 2)+ggtitle("CBS = CAS = 2")+ylim(c(-3,3))+ scale_fill_discrete(guide=FALSE),
+  ncol =3)
+
+visContrastADSDirectJoint2 <- annotate_figure(visContrastADSDirectJoint, 
+                                        top = text_grob("(range restricted to (-3,3), IC at the rounded mean = 5)",
+                                                        size = 10))
+visContrastADSDirectJoint3 <- annotate_figure(visContrastADSDirectJoint2, 
+                                        top = text_grob("Predicted direct effect distance from the control group mean vs. ADS (standardized)",
+                                                        size = 12))
+
+visContrastADSDirectJoint3
+```
+\normalsize
+
 #  References {-}

### 2021-09-16 bayesianAnalysis/bayesianReport3.tex
direct effect

--- 2021-09-16 bayesianAnalysis/bayesianReport.tex
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/treatmentHist-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEmpiricalAdiff-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEpmiricalCdiff-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/ic-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/icc-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/correlations-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag1-1} \end{center}
 
@@
 
+The situation is different when it comes to evaluating the \emph{direct}
+effect of intervention. Then, we also need to block indirect causal
+paths from the intervention to the outcome. For such an evaluation we
+need to also condition on \textsf{CAS}, which is what we will do when we
+turn to the study of the direct effects of the interventions.
+
 In fact, we will be predicting the difference between attacks before and
@@
 
-\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag2-1} \end{center}
 
@@
 information-theoretic criteria of predictive power.
-
-\section{Bayesian models, priors and
-diagnostics}\label{bayesian-models-priors-and-diagnostics}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors1-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors03-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-7-1} \end{center}
 
@@
 \NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
-\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison )) }
+\KeywordTok{mykable}\NormalTok{(}\KeywordTok{round}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison ),}\DecValTok{3}\NormalTok{)) }
 \end{Highlighting}
@@
 \midrule
-\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8345169}\\
-tooFar & 1189.123 & 90.35400 & 4.481669 & 2.882584 & 29.76051 & 0.0887673\\
-\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0767158}\\
-null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
-\cellcolor{gray!6}{IT} & \cellcolor{gray!6}{1345.879} & \cellcolor{gray!6}{144.64185} & \cellcolor{gray!6}{161.237934} & \cellcolor{gray!6}{132.478842} & \cellcolor{gray!6}{19.27433} & \cellcolor{gray!6}{0.0000000}\\
+\cellcolor{gray!6}{tooFar} & \cellcolor{gray!6}{1185.575} & \cellcolor{gray!6}{89.393} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{27.846} & \cellcolor{gray!6}{0.487}\\
+Final & 1185.657 & 89.827 & 0.082 & 2.594 & 27.614 & 0.467\\
+\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1190.304} & \cellcolor{gray!6}{87.920} & \cellcolor{gray!6}{4.729} & \cellcolor{gray!6}{6.055} & \cellcolor{gray!6}{25.882} & \cellcolor{gray!6}{0.046}\\
+null & 1345.358 & 145.805 & 159.783 & 134.039 & 18.061 & 0.000\\
+\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1347.281} & \cellcolor{gray!6}{142.655} & \cellcolor{gray!6}{161.706} & \cellcolor{gray!6}{131.261} & \cellcolor{gray!6}{21.935} & \cellcolor{gray!6}{0.000}\\
 \addlinespace
-ADSIT & 1348.714 & 142.29377 & 164.072877 & 130.485213 & 23.06652 & 0.0000000\\
-\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
-ADSIT\_ADSIT & 1350.941 & 153.88118 & 166.300056 & 139.579270 & 32.04695 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC & 1353.603 & 147.38084 & 168.962571 & 134.581071 & 28.54365 & 0.0000000\\
+IT & 1347.916 & 146.200 & 162.341 & 134.462 & 20.545 & 0.000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1348.366} & \cellcolor{gray!6}{150.638} & \cellcolor{gray!6}{162.791} & \cellcolor{gray!6}{136.811} & \cellcolor{gray!6}{27.604} & \cellcolor{gray!6}{0.000}\\
+ADSIT & 1350.067 & 144.264 & 164.492 & 132.764 & 23.985 & 0.000\\
+\cellcolor{gray!6}{ADSIT\_ADSIT} & \cellcolor{gray!6}{1351.139} & \cellcolor{gray!6}{154.826} & \cellcolor{gray!6}{165.564} & \cellcolor{gray!6}{141.033} & \cellcolor{gray!6}{31.062} & \cellcolor{gray!6}{0.000}\\
+ADSIC & 1351.343 & 145.539 & 165.768 & 133.454 & 25.443 & 0.000\\
 \addlinespace
-\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1355.210} & \cellcolor{gray!6}{148.15271} & \cellcolor{gray!6}{170.568848} & \cellcolor{gray!6}{135.609996} & \cellcolor{gray!6}{27.22326} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.442} & \cellcolor{gray!6}{155.55820} & \cellcolor{gray!6}{170.800602} & \cellcolor{gray!6}{140.950680} & \cellcolor{gray!6}{34.03861} & \cellcolor{gray!6}{0.0000000}\\
+\cellcolor{gray!6}{ADSITIC} & \cellcolor{gray!6}{1353.020} & \cellcolor{gray!6}{147.645} & \cellcolor{gray!6}{167.445} & \cellcolor{gray!6}{135.441} & \cellcolor{gray!6}{26.884} & \cellcolor{gray!6}{0.000}\\
+ADSITIC\_ADSIT\_ITIC\_ADSIC & 1355.187 & 154.826 & 169.613 & 140.659 & 34.652 & 0.000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIC\_ADSIT} & \cellcolor{gray!6}{1356.479} & \cellcolor{gray!6}{157.522} & \cellcolor{gray!6}{170.905} & \cellcolor{gray!6}{143.538} & \cellcolor{gray!6}{34.533} & \cellcolor{gray!6}{0.000}\\
 \bottomrule
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-9-1} \end{center}
 
@@
 \begin{Highlighting}[]
-\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)}
+\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)))}
 \end{Highlighting}
@@
 \begin{table}
-
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.0414089\\
-\hline
-0.1979211\\
-\hline
-0.2484756\\
-\hline
--0.1097667\\
-\hline
--0.0042060\\
-\hline
--0.5142899\\
-\hline
--0.0919148\\
-\hline
--0.5302840\\
-\hline
--0.0212337\\
-\hline
-0.1482970\\
-\hline
--0.0686005\\
-\hline
--0.0037630\\
-\hline
--0.0117801\\
-\hline
-0.0118155\\
-\hline
-0.7945882\\
-\hline
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\begin{tabular}{lrrrrrr}
+\toprule
+  & mean & sd & X5.5. & X94.5. & n\_eff & Rhat4\\
+\midrule
+\cellcolor{gray!6}{a} & \cellcolor{gray!6}{0.0414089} & \cellcolor{gray!6}{0.1562753} & \cellcolor{gray!6}{-0.2037740} & \cellcolor{gray!6}{0.2796946} & \cellcolor{gray!6}{228.1593} & \cellcolor{gray!6}{0.9980513}\\
+bADS[1] & 0.1979211 & 0.0568494 & 0.1086423 & 0.2907669 & 768.4216 & 1.0013137\\
+\cellcolor{gray!6}{bADS[2]} & \cellcolor{gray!6}{0.2484756} & \cellcolor{gray!6}{0.1546028} & \cellcolor{gray!6}{0.0036955} & \cellcolor{gray!6}{0.4942282} & \cellcolor{gray!6}{526.1494} & \cellcolor{gray!6}{0.9995921}\\
+bADS[3] & -0.1097667 & 0.1014546 & -0.2678764 & 0.0628934 & 418.0876 & 0.9980791\\
+\cellcolor{gray!6}{bADSIC} & \cellcolor{gray!6}{-0.0042060} & \cellcolor{gray!6}{0.0051643} & \cellcolor{gray!6}{-0.0122338} & \cellcolor{gray!6}{0.0040408} & \cellcolor{gray!6}{361.1195} & \cellcolor{gray!6}{0.9983620}\\
+\addlinespace
+bCBS[1] & -0.5142899 & 0.0414267 & -0.5776731 & -0.4463925 & 722.3116 & 0.9991926\\
+\cellcolor{gray!6}{bCBS[2]} & \cellcolor{gray!6}{-0.0919148} & \cellcolor{gray!6}{0.1245614} & \cellcolor{gray!6}{-0.2965873} & \cellcolor{gray!6}{0.1059034} & \cellcolor{gray!6}{671.6673} & \cellcolor{gray!6}{0.9998084}\\
+bCBS[3] & -0.5302840 & 0.1088835 & -0.7023272 & -0.3593766 & 823.7157 & 0.9980583\\
+\cellcolor{gray!6}{bIT[1]} & \cellcolor{gray!6}{-0.0212337} & \cellcolor{gray!6}{0.1630179} & \cellcolor{gray!6}{-0.2603815} & \cellcolor{gray!6}{0.2295494} & \cellcolor{gray!6}{219.0190} & \cellcolor{gray!6}{0.9980137}\\
+bIT[2] & 0.1482970 & 0.1857528 & -0.1246834 & 0.4367149 & 304.7859 & 0.9980345\\
+\addlinespace
+\cellcolor{gray!6}{bIT[3]} & \cellcolor{gray!6}{-0.0686005} & \cellcolor{gray!6}{0.1776783} & \cellcolor{gray!6}{-0.3448157} & \cellcolor{gray!6}{0.2099344} & \cellcolor{gray!6}{295.3412} & \cellcolor{gray!6}{0.9980482}\\
+bIC[1] & -0.0037630 & 0.3161707 & -0.5084313 & 0.4981378 & 829.2326 & 1.0011451\\
+\cellcolor{gray!6}{bIC[2]} & \cellcolor{gray!6}{-0.0117801} & \cellcolor{gray!6}{0.0256771} & \cellcolor{gray!6}{-0.0529960} & \cellcolor{gray!6}{0.0290304} & \cellcolor{gray!6}{488.1809} & \cellcolor{gray!6}{0.9994090}\\
+bIC[3] & 0.0118155 & 0.0185521 & -0.0192521 & 0.0412303 & 612.3810 & 0.9986804\\
+\cellcolor{gray!6}{sigma} & \cellcolor{gray!6}{0.7945882} & \cellcolor{gray!6}{0.0277774} & \cellcolor{gray!6}{0.7535960} & \cellcolor{gray!6}{0.8434971} & \cellcolor{gray!6}{693.5845} & \cellcolor{gray!6}{0.9982674}\\
+\bottomrule
 \end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.1562753\\
-\hline
-0.0568494\\
-\hline
-0.1546028\\
-\hline
-0.1014546\\
-\hline
-0.0051643\\
-\hline
-0.0414267\\
-\hline
-0.1245614\\
-\hline
-0.1088835\\
-\hline
-0.1630179\\
-\hline
-0.1857528\\
-\hline
-0.1776783\\
-\hline
-0.3161707\\
-\hline
-0.0256771\\
-\hline
-0.0185521\\
-\hline
-0.0277774\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
--0.2037740\\
-\hline
-0.1086423\\
-\hline
-0.0036955\\
-\hline
--0.2678764\\
-\hline
--0.0122338\\
-\hline
--0.5776731\\
-\hline
--0.2965873\\
-\hline
--0.7023272\\
-\hline
--0.2603815\\
-\hline
--0.1246834\\
-\hline
--0.3448157\\
-\hline
--0.5084313\\
-\hline
--0.0529960\\
-\hline
--0.0192521\\
-\hline
-0.7535960\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.2796946\\
-\hline
-0.2907669\\
-\hline
-0.4942282\\
-\hline
-0.0628934\\
-\hline
-0.0040408\\
-\hline
--0.4463925\\
-\hline
-0.1059034\\
-\hline
--0.3593766\\
-\hline
-0.2295494\\
-\hline
-0.4367149\\
-\hline
-0.2099344\\
-\hline
-0.4981378\\
-\hline
-0.0290304\\
-\hline
-0.0412303\\
-\hline
-0.8434971\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-228.1593\\
-\hline
-768.4216\\
-\hline
-526.1494\\
-\hline
-418.0876\\
-\hline
-361.1195\\
-\hline
-722.3116\\
-\hline
-671.6673\\
-\hline
-823.7157\\
-\hline
-219.0190\\
-\hline
-304.7859\\
-\hline
-295.3412\\
-\hline
-829.2326\\
-\hline
-488.1809\\
-\hline
-612.3810\\
-\hline
-693.5845\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.9980513\\
-\hline
-1.0013137\\
-\hline
-0.9995921\\
-\hline
-0.9980791\\
-\hline
-0.9983620\\
-\hline
-0.9991926\\
-\hline
-0.9998084\\
-\hline
-0.9980583\\
-\hline
-0.9980137\\
-\hline
-0.9980345\\
-\hline
-0.9980482\\
-\hline
-1.0011451\\
-\hline
-0.9994090\\
-\hline
-0.9986804\\
-\hline
-0.9982674\\
-\hline
-\end{tabular}
+\endgroup{}
 \end{table}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-11-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-12-1} \end{center}
 
@@
 
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
-        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{, }
-        \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{,}
-        \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{))}\OperatorTok{+}
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{            }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} 
+        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh),  }
+         \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{)}\OperatorTok{+}
 \StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
@@
 \NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
-\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
           \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
 \StringTok{        }\NormalTok{removeY,}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-13-1} \end{center}
 
@@
 
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{,}
-                  \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{, }
-                  \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }
+       \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
 \NormalTok{\}}
@@
 \NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
                                  \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
 \StringTok{                                   }\NormalTok{removeY,}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-14-1} \end{center}
 
@@
 by looking at contrasts (distances from the control group mean) with
-89\% HPDIs by IC.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsIC <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{30}\NormalTok{,}\DataTypeTok{by =} \DecValTok{1}\NormalTok{), }\DataTypeTok{ADS =}\NormalTok{ ADS)}
+89\% HPDIs by IC. Notice the predicted effect of \textsf{IC} is weaker
+than group membership, so for visibility the \(y\)-axis has a smaller
+range. Also, not enough data was available to reliably estimate
+uncertainty for \textsf{IC} above 20, hence the restriction on the
+\(x\)-axis (arleady at lower values, lack of estimates is visible for
+the more extreme covariate settings).
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsIC <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS ,}
+                           \DataTypeTok{IC =}  \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{20}\NormalTok{,}\DataTypeTok{by =} \DecValTok{1}\NormalTok{), }\DataTypeTok{ADS =}\NormalTok{ ADS)}
 \NormalTok{\{}
@@
 
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{),}
+                            \KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
 \NormalTok{  visContrastTreatmentIC <-}\StringTok{ }\NormalTok{visContrastIC[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
 
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{    }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{)}\OperatorTok{+}
-\StringTok{    }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{    }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{)}\OperatorTok{+}
+\StringTok{    }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lty =}\DecValTok{2}\NormalTok{, }\DataTypeTok{size =} \FloatTok{0.1}\NormalTok{))}
 \NormalTok{\}}
@@
 \StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
 \StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
 \StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
     \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),  }
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{  }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),  }
+\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
 \StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{), }
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{), }
 \DataTypeTok{ncol =} \DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-17-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-15-1} \end{center}
+
+\normalsize
+
+\section{Direct effect}\label{direct-effect}
+
+Models for the evaluation of direct effect need to close the indirect
+causal path from the treatment variables to the output, and they do so
+by conditioning on \textsf{CAS}. Again, we face model selection. We
+repeat all the model structures from the previous section, except for
+now, each model is extended with \textsf{CAS} as a predictor. This time
+the model structure we called \textsf{tooFar} turns out to do better. We
+also consider extending it with interactions between \textsf{CAS} and
+\textsf{IT} and \textsf{IC} (jointly and separately), but this results
+in no further improvement.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{nullDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries  }
+\NormalTok{)}
+
+\NormalTok{ADSDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSICDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS}\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ITDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID]}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC_ADSICDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC_ADSIC_ADSITDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT_ADSITDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{#bADSIC ~ dnorm(0,.5),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{#bIC ~ dnorm(0,.5),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC_ADSIT_ITIC_ADSICDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICCBS_ITIC_ADSICDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{FinalDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS,}
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS, }
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect_CASIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{CAS, }
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect_CASIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS }\OperatorTok{*}\StringTok{ }\NormalTok{CAS }\OperatorTok{+}\StringTok{ }\NormalTok{bCASIC }\OperatorTok{*}\StringTok{ }\NormalTok{CAS }\OperatorTok{*}\StringTok{ }\NormalTok{IC, }
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCASIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect_CASIC_CASIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
+  \KeywordTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
+\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bCAS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{CAS }\OperatorTok{+}\StringTok{ }\NormalTok{bCASIC }\OperatorTok{*}\StringTok{ }\NormalTok{CAS }\OperatorTok{*}\StringTok{ }\NormalTok{IC, }
+\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCASIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
+\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \DataTypeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{comparisonDirect<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(nullDirect,ADSDirect,ADSICDirect,ITDirect,ADSITDirect,ADSITICDirect,ADSITIC_ADSICDirect, ADSITIC_ADSIC_ADSITDirect,ADSIT_ADSITDirect,ADSITIC_ADSIT_ITIC_ADSICDirect,}
+\NormalTok{                     ADSITICCBS_ITIC_ADSICDirect,FinalDirect, tooFarDirect,tooFarDirect_CASIT,}
+\NormalTok{                     tooFarDirect_CASIC,tooFarDirect_CASIC_CASIT)}
+
+\KeywordTok{mykable}\NormalTok{(}\KeywordTok{round}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparisonDirect),}\DecValTok{3}\NormalTok{))}\OperatorTok{%>%}\StringTok{ }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{,}\StringTok{"scale_down"}\NormalTok{),}\DataTypeTok{font_size =} \DecValTok{9}\NormalTok{)  }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\resizebox{\linewidth}{!}{
+\fontsize{9}{11}\selectfont
+\begin{tabular}{lrrrrrr}
+\toprule
+  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
+\midrule
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1044.746}} & \cellcolor{gray!6}{\cellcolor{gray!6}{83.935}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}} & \cellcolor{gray!6}{\cellcolor{gray!6}{NA}} & \cellcolor{gray!6}{\cellcolor{gray!6}{37.053}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.777}}\\
+FinalDirect & 1048.925 & 83.369 & 4.178 & 9.720 & 35.057 & 0.096\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect\_CASIT}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1049.258}} & \cellcolor{gray!6}{\cellcolor{gray!6}{85.612}} & \cellcolor{gray!6}{\cellcolor{gray!6}{4.512}} & \cellcolor{gray!6}{\cellcolor{gray!6}{4.952}} & \cellcolor{gray!6}{\cellcolor{gray!6}{38.533}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.081}}\\
+tooFarDirect\_CASIC & 1050.488 & 84.774 & 5.741 & 5.460 & 39.743 & 0.044\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect\_CASIC\_CASIT}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1058.089}} & \cellcolor{gray!6}{\cellcolor{gray!6}{86.136}} & \cellcolor{gray!6}{\cellcolor{gray!6}{13.343}} & \cellcolor{gray!6}{\cellcolor{gray!6}{9.164}} & \cellcolor{gray!6}{\cellcolor{gray!6}{42.266}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.001}}\\
+\addlinespace
+ADSITICCBS\_ITIC\_ADSICDirect & 1074.474 & 85.119 & 29.727 & 19.463 & 38.768 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSITIC\_ADSIC\_ADSITDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1362.118}} & \cellcolor{gray!6}{\cellcolor{gray!6}{126.956}} & \cellcolor{gray!6}{\cellcolor{gray!6}{317.371}} & \cellcolor{gray!6}{\cellcolor{gray!6}{89.380}} & \cellcolor{gray!6}{\cellcolor{gray!6}{55.637}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ITDirect & 1365.074 & 127.033 & 320.328 & 95.888 & 44.170 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSITIC\_ADSICDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1369.845}} & \cellcolor{gray!6}{\cellcolor{gray!6}{132.826}} & \cellcolor{gray!6}{\cellcolor{gray!6}{325.099}} & \cellcolor{gray!6}{\cellcolor{gray!6}{97.323}} & \cellcolor{gray!6}{\cellcolor{gray!6}{54.381}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+nullDirect & 1370.323 & 133.121 & 325.577 & 102.532 & 46.392 & 0.000\\
+\addlinespace
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSIT\_ADSITDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1371.846}} & \cellcolor{gray!6}{\cellcolor{gray!6}{136.213}} & \cellcolor{gray!6}{\cellcolor{gray!6}{327.100}} & \cellcolor{gray!6}{\cellcolor{gray!6}{99.520}} & \cellcolor{gray!6}{\cellcolor{gray!6}{59.273}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ADSITIC\_ADSIT\_ITIC\_ADSICDirect & 1372.257 & 134.925 & 327.511 & 98.383 & 61.847 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1372.713}} & \cellcolor{gray!6}{\cellcolor{gray!6}{131.716}} & \cellcolor{gray!6}{\cellcolor{gray!6}{327.966}} & \cellcolor{gray!6}{\cellcolor{gray!6}{100.481}} & \cellcolor{gray!6}{\cellcolor{gray!6}{50.297}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ADSITDirect & 1378.450 & 134.977 & 333.703 & 103.890 & 54.225 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSICDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1384.285}} & \cellcolor{gray!6}{\cellcolor{gray!6}{138.312}} & \cellcolor{gray!6}{\cellcolor{gray!6}{339.538}} & \cellcolor{gray!6}{\cellcolor{gray!6}{106.092}} & \cellcolor{gray!6}{\cellcolor{gray!6}{55.895}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+\addlinespace
+ADSITICDirect & 1385.248 & 140.784 & 340.502 & 108.633 & 58.695 & 0.000\\
+\bottomrule
+\end{tabular}}
+\endgroup{}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{plot}\NormalTok{(comparisonDirect)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/comparisonDirectModels-1} \end{center}
+
+\normalsize
+
+Let's build a Hamiltonian Monte Carlo with the same formula:
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# tooFarDirectHMC <- ulam(}
+\CommentTok{#   alist(}
+\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
+\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + }
+\CommentTok{#       bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS * CAS, }
+\CommentTok{#     a ~ dnorm (0,0.3),}
+\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bADSIC ~ dnorm(0,.3),}
+\CommentTok{#     bCAS ~ dnorm(0,0.3),}
+\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
+\CommentTok{#     bCBSIC ~ dnorm(0, .3),}
+\CommentTok{#     sigma  ~ dexp(1)}
+\CommentTok{#   ), }
+\CommentTok{#   data = summaries}
+\CommentTok{# )}
+
+\CommentTok{#saveRDS(tooFarDirectHMC, file = "models/tooFarDirectHMC.rds")}
+
+\NormalTok{tooFarDirectHMC <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/tooFarDirectHMC.rds"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+For a big picture, let's look at predicted direct effect by group and
+user activity profile.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visGroupDirect <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, CAS, }\DataTypeTok{xmin =}\DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-3}\NormalTok{)}
+\NormalTok{\{}
+\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{  IC <-}\StringTok{ }\DecValTok{5} 
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{CAS =}\NormalTok{ CAS, }\DataTypeTok{IC =}\NormalTok{  IC)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+  \KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
+\NormalTok{  muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
+  \KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
+\NormalTok{  mu_HPDI <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
+\NormalTok{  means <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(means)}
+\NormalTok{  means}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{rownames}\NormalTok{(means)}
+  \KeywordTok{rownames}\NormalTok{(means) <-}\StringTok{ }\OtherTok{NULL}
+\NormalTok{  meansDisp <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(mu_HPDI)))}
+\NormalTok{  meansDisp <-}\StringTok{ }\NormalTok{meansDisp[,}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
+
+\NormalTok{  plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
+\StringTok{    }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
+\StringTok{    }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS, }\StringTok{", CAS="}\NormalTok{, CAS,  }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
+\StringTok{    }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
+  \CommentTok{#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
+  \KeywordTok{return}\NormalTok{(plot)}
+\NormalTok{\}}
+
+\NormalTok{visGroupDirect2_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupDirect200 <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect222 <-}\StringTok{ }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirect0_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupDirect000 <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect022 <-}\StringTok{ }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirect_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{-2}\NormalTok{)}
+\NormalTok{visGroupDirect_}\DecValTok{200}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect_}\DecValTok{222}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroupDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirectHMC, }\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirectJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupDirect2_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = -2"}\NormalTok{),}
+\NormalTok{                                 visGroupDirect200}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 0"}\NormalTok{),}
+\NormalTok{                                 visGroupDirect222}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 2"}\NormalTok{) ,}
+\NormalTok{                        visGroupDirect0_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
+\NormalTok{                                visGroupDirect000}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                                visGroupDirect022}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                        visGroupDirect_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\NormalTok{_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                                  visGroupDirect_}\DecValTok{200}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                        visGroupDirect_}\DecValTok{222}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{)}
+\NormalTok{                                 ,}\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visGroupDirectJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupDirectJoint, }
+                                  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-4,4), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                  \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visGroupJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupDirectJoint2, }
+                                  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted direct effect of treatment group by activity profile (standardized)"}\NormalTok{,}
+                                                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visGroupJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-17-1} \end{center}
+
+\normalsize
+
+Now, predicted direct effect of five interventions vs. \textsf{CBS}, for
+three user activity profiles.
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsCBSDirect <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =}\NormalTok{ ADS , }\DataTypeTok{CAS=}\NormalTok{ CAS, }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{,}
+                            \DataTypeTok{CBS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))\{}
+\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(ADS, groupID, CAS, IC , CBS)}
+  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"CAS"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+  \KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+
+\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrast <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
+\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
+\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
+
+  \KeywordTok{colnames}\NormalTok{(visContrast)[}\KeywordTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+
+\NormalTok{  contrast <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cLow <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cHigh <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrast}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrast}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                          \KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+
+\NormalTok{  visContrastTreatment <-}\StringTok{ }\NormalTok{visContrast[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} 
+                         \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh),  }
+                       \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{)}\OperatorTok{+}
+\StringTok{           }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{3.5}\NormalTok{,}\FloatTok{3.5}\NormalTok{)))}
+\NormalTok{\}}
+
+\NormalTok{visContrastDirect <-}\StringTok{  }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBSDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirect,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{IC =} \DecValTok{5}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = -2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+          \KeywordTok{visContrastsCBSDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirect,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{IC =} \DecValTok{5}\NormalTok{) }\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = 0"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY,}
+          \KeywordTok{visContrastsCBSDirect}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ tooFarDirect,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{IC =} \DecValTok{5}\NormalTok{) }\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}
+\NormalTok{          ,}\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastDirect2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastDirect, }
+                                        \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-3.5,3.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastDirect3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastDirect2, }
+                                        \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted direct effect distance from the control group mean vs.
+CBS  (standardized)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastDirect3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-18-1} \end{center}
+
+\normalsize
+
+Now contrasts against \textsf{ADS}, for three user profiles:
+
+\vspace{1mm} \footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsADSDirect <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{CAS =}\NormalTok{ CAS, }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{, }
+                            \DataTypeTok{ADS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\NormalTok{\{}
+\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, CAS, IC , ADS)}
+  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"CAS"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
+\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastADS <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
+\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
+\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
+
+  \KeywordTok{colnames}\NormalTok{(visContrastADS)[}\KeywordTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastADS <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastADS}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrastADS}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                             \KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentADS <-}\StringTok{ }\NormalTok{visContrastADS[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{fill =}\NormalTok{ group ))}\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_line}\NormalTok{(}\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
+\StringTok{           }\KeywordTok{geom_ribbon}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }
+                       \DataTypeTok{alpha =} \FloatTok{.3}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{\}}
+
+\NormalTok{visContrastADSDirectJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}
+  \KeywordTok{visContrastsADSDirect}\NormalTok{(tooFarDirect,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+  \KeywordTok{visContrastsADSDirect}\NormalTok{(tooFarDirect, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 0"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+  \KeywordTok{visContrastsADSDirect}\NormalTok{(tooFarDirect, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
+  \DataTypeTok{ncol =}\DecValTok{3}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastADSDirectJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSDirectJoint, }
+                                        \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-3,3), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastADSDirectJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSDirectJoint2, }
+                                        \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted direct effect distance from the control group mean vs.
+ADS (standardized)"}\NormalTok{,}
+                                                        \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastADSDirectJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-19-1} \end{center}
 

### 2021-09-16 bayesianAnalysis/directEffect.R

@@ -1,0 +1,660 @@
+library(ggplot2)
+library(ggthemes)
+library(gridExtra)
+library(kableExtra)
+library(viridis)
+library(rethinking)
+library(ggplot2)
+library(ggpubr)
+library(tidyverse)
+library(GGally)
+library(dagitty)
+library(reshape)
+
+
+
+removeX <-   theme(axis.title.x=element_blank(),
+                   axis.text.x=element_blank(),
+                   axis.ticks.x=element_blank())
+
+removeY <-   theme(axis.title.y=element_blank(),
+                   axis.text.y=element_blank(),
+                   axis.ticks.y=element_blank())
+
+
+summaries <- readRDS(file = "datasets/Summaries.rds")
+summaries$ABS <- standardize(summaries$AB)
+summaries$CBS <- standardize(summaries$CB)
+summaries$AAS <- standardize(summaries$AA)
+summaries$CAS <- standardize(summaries$CA)
+summaries$CDS <- standardize(summaries$CD)
+summaries$ADS <- standardize(summaries$AD)
+summaries$group <- as.factor(summaries$group)
+summaries$groupID <-  as.integer( as.factor(summaries$group) )
+
+
+head(summaries)
+
+nullDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries  
+)
+
+ADSDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <-  a + bADS * ADS+ bCAS * CAS,
+    a ~ dnorm (0,0.3),
+    bADS ~ dnorm(0,0.3),
+    bCAS ~ dnorm(0,0.3),
+    sigma  ~ dexp(1)
+  ), 
+  data = summaries
+)
+
+ADSICDirect <- quap(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
[…]

### 2021-12-21 bayesianAnalysis/bayesianReport3.tex
started technical report

--- 2021-09-14 bayesianAnalysis/bayesianReport.tex
@@
-\documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  10pt,
+  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
+\title{Bayesian analysis of the NESTA study of interventions against
+verbal aggression online}
+\author{Rafal Urbaniak}
+\date{}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
   colorlinks=true,
-            linkcolor=Maroon,
-            citecolor=Blue,
-            urlcolor=blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={blue},
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{color}
@@
 \usepackage{xcolor}
-
-\title{Bayesian analysis of the NESTA study of interventions against verbal
-aggression online}
-\author{Rafal Urbaniak}
-\date{}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{summaries <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\DataTypeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(summaries) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{kable}\NormalTok{( }\StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }\StringTok{"scale_down"}\NormalTok{) ,}\DataTypeTok{font_size =} \DecValTok{9}\NormalTok{)}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{summaries }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(summaries) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{kable}\NormalTok{( }\StringTok{"latex"}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \FunctionTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }\StringTok{"scale\_down"}\NormalTok{) ,}\AttributeTok{font\_size =} \DecValTok{9}\NormalTok{)}
 \end{Highlighting}
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{ABS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AB)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CBS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CB)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{AAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AA)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CA)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CDS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CD)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{ADS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AD)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{  }\KeywordTok{as.integer}\NormalTok{( }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group) )}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ABS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AB)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CBS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CB)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{AAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AA)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CA)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CDS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CD)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ADS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AD)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}}  \FunctionTok{as.integer}\NormalTok{( }\FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group) )}
 \end{Highlighting}
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{ggplot}\NormalTok{(summaries[summaries}\OperatorTok{$}\NormalTok{group }\OperatorTok{!=}\StringTok{ "control"}\NormalTok{,], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_bar}\NormalTok{()}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions received"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Intervention counts in treatment groups"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}\DataTypeTok{breaks =} \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{40}\NormalTok{,}\DecValTok{5}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
-
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{ggplot}\NormalTok{(summaries[summaries}\SpecialCharTok{$}\NormalTok{group }\SpecialCharTok{!=} \StringTok{"control"}\NormalTok{,], }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_bar}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{"interventions received"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Intervention counts in treatment groups"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{40}\NormalTok{,}\DecValTok{5}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/treatmentHist-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{violAdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
-\NormalTok{violJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violAdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
-\NormalTok{              violAdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{violAdiffS }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{() }\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{() }
+\NormalTok{violJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(violAdiffS}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
+\NormalTok{              violAdiffS }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{geom\_boxplot}\NormalTok{(}\AttributeTok{width =}\NormalTok{ .}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}
+              \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"restricted to ({-}1,1)"}\NormalTok{)) }
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{violJointTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in attacks (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{violJointTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(violJoint, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in attacks (standardized)"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \NormalTok{violJointTitled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEmpiricalAdiff-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{violCdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ CdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
-\NormalTok{violJointC <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violCdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
-\NormalTok{              violCdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{violCdiffS }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{group, }\AttributeTok{y =}\NormalTok{ CdiffS))}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{() }\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{() }
+\NormalTok{violJointC }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(violCdiffS}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
+\NormalTok{              violCdiffS }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{geom\_boxplot}\NormalTok{(}\AttributeTok{width =}\NormalTok{ .}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}
+              \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"restricted to ({-}1,1)"}\NormalTok{)) }
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{violJointCTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in comments (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{violJointCTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(violJoint, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in comments (standardized)"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \NormalTok{violJointCTitled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/violEpmiricalCdiff-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{icplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icplot1, icplot2) }
-\NormalTok{icplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icplotJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in attacks (standardized) vs interventions received"}\NormalTok{,  }\DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{icplot1 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ AdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}2,2)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
+
+\NormalTok{icplot2 }\OtherTok{\textless{}{-}}  \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ AdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}1,1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
+
+\NormalTok{icplotJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(icplot1, icplot2) }
+\NormalTok{icplotTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(icplotJoint, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Change in attacks (standardized) vs interventions received"}\NormalTok{,  }\AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \NormalTok{icplotTitled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/ic-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{icCplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icCplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icCplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icCplot1, icCplot2) }
-\NormalTok{icCplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icCplotJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in comments (standardized) vs interventions received"}\NormalTok{,}
-   \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{icCplot1 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ CdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}2,2)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
+
+\NormalTok{icCplot2 }\OtherTok{\textless{}{-}}  \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ CdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}1,1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
+
+\NormalTok{icCplotJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(icCplot1, icCplot2) }
+\NormalTok{icCplotTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(icCplotJoint, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Change in comments (standardized) vs interventions received"}\NormalTok{,}
+   \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \NormalTok{icCplotTitled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/icc-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{summariesCorr <-}\StringTok{ }\KeywordTok{select}\NormalTok{(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)}
-\KeywordTok{ggcorr}\NormalTok{(summariesCorr, }\DataTypeTok{method =} \KeywordTok{c}\NormalTok{(}\StringTok{"pairwise"}\NormalTok{),}
-       \DataTypeTok{digits =} \DecValTok{4}\NormalTok{, }\DataTypeTok{low =} \StringTok{"steelblue"}\NormalTok{, }\DataTypeTok{mid =} \StringTok{"white"}\NormalTok{,}
-       \DataTypeTok{high =} \StringTok{"darkred"}\NormalTok{, }\DataTypeTok{midpoint =}\DecValTok{0}\NormalTok{,}
-       \DataTypeTok{geom =} \StringTok{"tile"}\NormalTok{, }\DataTypeTok{label =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{label_size=}\DecValTok{4}\NormalTok{, }\DataTypeTok{label_round =}\DecValTok{2}\NormalTok{, }\DataTypeTok{layout.exp =}\DecValTok{1}\NormalTok{,}
-       \DataTypeTok{label_alpha =} \OtherTok{FALSE}\NormalTok{,}\DataTypeTok{hjust =} \FloatTok{0.75}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
-
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{summariesCorr }\OtherTok{\textless{}{-}} \FunctionTok{select}\NormalTok{(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)}
+\FunctionTok{ggcorr}\NormalTok{(summariesCorr, }\AttributeTok{method =} \FunctionTok{c}\NormalTok{(}\StringTok{"pairwise"}\NormalTok{),}
+       \AttributeTok{digits =} \DecValTok{4}\NormalTok{, }\AttributeTok{low =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{mid =} \StringTok{"white"}\NormalTok{,}
+       \AttributeTok{high =} \StringTok{"darkred"}\NormalTok{, }\AttributeTok{midpoint =}\DecValTok{0}\NormalTok{,}
+       \AttributeTok{geom =} \StringTok{"tile"}\NormalTok{, }\AttributeTok{label =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{label\_size=}\DecValTok{4}\NormalTok{, }\AttributeTok{label\_round =}\DecValTok{2}\NormalTok{, }\AttributeTok{layout.exp =}\DecValTok{1}\NormalTok{,}
+       \AttributeTok{label\_alpha =} \ConstantTok{FALSE}\NormalTok{,}\AttributeTok{hjust =} \FloatTok{0.75}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/correlations-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{dag <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{dag }\OtherTok{\textless{}{-}} \FunctionTok{dagitty}\NormalTok{(}\StringTok{"}
 \StringTok{  dag\{}
-\StringTok{  CDS -> ADS -> IC  ons}
+\StringTok{  CDS {-}\textgreater{} ADS {-}\textgreater{} IC  }
 \StringTok{               U [unobserved]   }
-\StringTok{               U -> CBS -> ABS  }
-\StringTok{               U -> ABS        }
-\StringTok{               U -> CDS -> ADS  }
-\StringTok{               U -> ADS         }
-\StringTok{               U -> CAS -> AAS    }
-\StringTok{               U -> AAS                        }
-\StringTok{               IC -> AAS        }
-\StringTok{               IC -> CAS        }
-\StringTok{               IT -> CAS        }
-\StringTok{               IT -> AAS}
-\StringTok{               CBS -> CDS -> CAS}
-\StringTok{               ABS -> ADS -> AAS}
+\StringTok{               U {-}\textgreater{} CBS {-}\textgreater{} ABS  }
+\StringTok{               U {-}\textgreater{} ABS        }
+\StringTok{               U {-}\textgreater{} CDS {-}\textgreater{} ADS  }
+\StringTok{               U {-}\textgreater{} ADS         }
+\StringTok{               U {-}\textgreater{} CAS {-}\textgreater{} AAS    }
+\StringTok{               U {-}\textgreater{} AAS                        }
+\StringTok{               IC {-}\textgreater{} AAS        }
+\StringTok{               IC {-}\textgreater{} CAS        }
+\StringTok{               IT {-}\textgreater{} CAS        }
+\StringTok{               IT {-}\textgreater{} AAS}
+\StringTok{               CBS {-}\textgreater{} CDS {-}\textgreater{} CAS}
+\StringTok{               ABS {-}\textgreater{} ADS {-}\textgreater{} AAS}
 \StringTok{               \}"}\NormalTok{)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\KeywordTok{drawdag}\NormalTok{(dag)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
-
+\FunctionTok{coordinates}\NormalTok{(dag)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## $x
+## AAS ABS ADS CAS CBS CDS  IC  IT   U 
+##  NA  NA  NA  NA  NA  NA  NA  NA  NA 
+## 
+## $y
+## AAS ABS ADS CAS CBS CDS  IC  IT   U 
+##  NA  NA  NA  NA  NA  NA  NA  NA  NA
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{coordinates}\NormalTok{( dag ) }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{( }\AttributeTok{x=}\FunctionTok{c}\NormalTok{(}\AttributeTok{CBS=}\DecValTok{0}\NormalTok{,}\AttributeTok{ABS=}\DecValTok{0}\NormalTok{,}\AttributeTok{CDS=}\DecValTok{1}\NormalTok{,}\AttributeTok{ADS=}\DecValTok{1}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{,}
+                    \AttributeTok{AAS =} \DecValTok{2}\NormalTok{, }\AttributeTok{IT =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{IC =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{U =}\NormalTok{ .}\DecValTok{5}\NormalTok{) ,}
+\AttributeTok{y=}\FunctionTok{c}\NormalTok{(}\AttributeTok{CBS =}\DecValTok{0}\NormalTok{,}\AttributeTok{ABS =} \DecValTok{1}\NormalTok{,}\AttributeTok{CDS =} \DecValTok{0}\NormalTok{,}\AttributeTok{ADS =} \DecValTok{1}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{, }\AttributeTok{AAS =} \DecValTok{1}\NormalTok{, }
+    \AttributeTok{IT =}\NormalTok{ .}\DecValTok{3}\NormalTok{, }\AttributeTok{IC =}\NormalTok{ .}\DecValTok{7}\NormalTok{, }\AttributeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{) )}
+\FunctionTok{drawdag}\NormalTok{(dag)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag1-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{paths}\NormalTok{(dag, }\DataTypeTok{from =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{), }\DataTypeTok{to =} \StringTok{"AAS"}\NormalTok{)}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{paths}\NormalTok{(dag, }\AttributeTok{from =} \FunctionTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{), }\AttributeTok{to =} \StringTok{"AAS"}\NormalTok{)}
 \end{Highlighting}
@@
 \textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
-line with the adjustment set identified algorithmically, and the same
-move makes sense when we want to predict \textsf{CAS}.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AAS"}\NormalTok{)}
+line with the adjustment set identified algorithmically.
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{adjustmentSets}\NormalTok{(dag, }\AttributeTok{exposure =} \FunctionTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\AttributeTok{outcome =} \StringTok{"AAS"}\NormalTok{, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
 \end{Highlighting}
@@
 ## { ADS }
+## { ABS, ADS }
+## { ADS, CBS }
+## { ABS, ADS, CBS }
+## { ADS, CDS }
+## { ABS, ADS, CDS }
+## { ADS, CBS, CDS }
+## { ABS, ADS, CBS, CDS }
+## { ADS, U }
+## { ABS, ADS, U }
+## { ADS, CBS, U }
+## { ABS, ADS, CBS, U }
+## { ADS, CDS, U }
+## { ABS, ADS, CDS, U }
+## { ADS, CBS, CDS, U }
+## { ABS, ADS, CBS, CDS, U }
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CAS"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## { ADS }
-\end{verbatim}
-
-\normalsize
-
-It's open season for other variables, and our decision to include them
-in the model will be guided by information-theoretic criteria of
-predictive power.
+\normalsize
+
+The situation is different when it comes to evaluating the \emph{direct}
+effect of intervention. Then, we also need to block indirect causal
+paths from the intervention to the outcome. For such an evaluation we
+need to also condition on \textsf{CAS}, which is what we will do when we
+turn to the study of the direct effects of the interventions.
 
@@
 \begin{Highlighting}[]
-\NormalTok{dag2 <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
+\NormalTok{dag2 }\OtherTok{\textless{}{-}} \FunctionTok{dagitty}\NormalTok{(}\StringTok{"}
 \StringTok{  dag\{}
-\StringTok{                CDS -> ADS -> IC  ons}
+\StringTok{                CDS {-}\textgreater{} ADS {-}\textgreater{} IC  }
 \StringTok{                U [unobserved]   }
-\StringTok{                U -> CBS -> ABS  }
-\StringTok{                U -> ABS        }
-\StringTok{                U -> CDS -> ADS  }
-\StringTok{                U -> ADS         }
-\StringTok{                U -> CAS -> AAS    }
-\StringTok{                U -> AAS                        }
-\StringTok{                IC -> AAS        }
-\StringTok{                IC -> CAS        }
-\StringTok{                IT -> CAS        }
-\StringTok{                IT -> AAS}
-\StringTok{                CBS -> CDS -> CAS}
-\StringTok{                ABS -> ADS -> AAS}
-\StringTok{                ABS -> AdiffS}
-\StringTok{                AAS -> AdiffS}
-\StringTok{                CBS -> CdiffS}
-\StringTok{                CAS -> CdiffS}
+\StringTok{                U {-}\textgreater{} CBS {-}\textgreater{} ABS  }
+\StringTok{                U {-}\textgreater{} ABS        }
+\StringTok{                U {-}\textgreater{} CDS {-}\textgreater{} ADS  }
+\StringTok{                U {-}\textgreater{} ADS         }
+\StringTok{                U {-}\textgreater{} CAS {-}\textgreater{} AAS    }
+\StringTok{                U {-}\textgreater{} AAS                        }
+\StringTok{                IC {-}\textgreater{} AAS        }
+\StringTok{                IC {-}\textgreater{} CAS        }
+\StringTok{                IT {-}\textgreater{} CAS        }
+\StringTok{                IT {-}\textgreater{} AAS}
+\StringTok{                CBS {-}\textgreater{} CDS {-}\textgreater{} CAS}
+\StringTok{                ABS {-}\textgreater{} ADS {-}\textgreater{} AAS}
+\StringTok{                ABS {-}\textgreater{} AdiffS}
+\StringTok{                AAS {-}\textgreater{} AdiffS}
+\StringTok{                CBS {-}\textgreater{} CdiffS}
+\StringTok{                CAS {-}\textgreater{} CdiffS}
 \StringTok{                \}"}\NormalTok{)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\KeywordTok{drawdag}\NormalTok{(dag2)}
-\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{)}
+\FunctionTok{coordinates}\NormalTok{( dag2 ) }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{( }\AttributeTok{x=}\FunctionTok{c}\NormalTok{(}\AttributeTok{CBS=}\DecValTok{0}\NormalTok{,}\AttributeTok{ABS=}\DecValTok{0}\NormalTok{,}\AttributeTok{CDS=}\DecValTok{1}\NormalTok{,}\AttributeTok{ADS=}\DecValTok{1}\NormalTok{,}
+    \AttributeTok{CAS =} \DecValTok{2}\NormalTok{, }\AttributeTok{AAS =} \DecValTok{2}\NormalTok{, }\AttributeTok{IT =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{IC =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{U =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{AdiffS=} \FloatTok{2.5}\NormalTok{, }\AttributeTok{CdiffS =} \FloatTok{2.5}\NormalTok{) ,}
+\AttributeTok{y=}\FunctionTok{c}\NormalTok{(}\AttributeTok{CBS =}\DecValTok{0}\NormalTok{,}\AttributeTok{ABS =} \DecValTok{1}\NormalTok{,}\AttributeTok{CDS =} \DecValTok{0}\NormalTok{,}\AttributeTok{ADS =} \DecValTok{1}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{, }\AttributeTok{AAS =} \DecValTok{1}\NormalTok{, }\AttributeTok{IT =}\NormalTok{ .}\DecValTok{3}\NormalTok{, }\AttributeTok{IC =}\NormalTok{ .}\DecValTok{7}\NormalTok{, }\AttributeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{, }\AttributeTok{CdiffS =} \SpecialCharTok{{-}}\NormalTok{.}\DecValTok{2}\NormalTok{,  }\AttributeTok{AdiffS =} \FloatTok{1.2}\NormalTok{) )}
+
+\FunctionTok{drawdag}\NormalTok{(dag2)}
+\FunctionTok{adjustmentSets}\NormalTok{(dag2, }\AttributeTok{exposure =} \FunctionTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\AttributeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{, }\AttributeTok{type =} \StringTok{"canonical"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-## { ADS }
+## { ABS, ADS, CBS, CDS }
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"CdiffS"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## { ADS }
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
-
-\section{Bayesian models, priors and
-diagnostics}\label{bayesian-models-priors-and-diagnostics}
+\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport3_files/figure-latex/dag2-1} \end{center}
+
+Finding a maximal sensible set (canonical) of covariates suggests
+inlcuding \textsf{CDS} and \textsf{ABS}. As already discussed, we do not
+include \textsf{CDS} because of its strong correlation with
+\textsf{CBS}. We also do not condition on \textsf{ABS}---not only
+because it has a pretty strong correlation with another predictor
+(\textsf{ADS}), but rather mainly because it is used to define the
+output variable. In such a set-up, of course that a model including
+\textsf{ABS} would have better predictive power, but since a
+definitional connection is present, thinking that its inclusion in the
+model tells us something about causality would be misled.
+
+It's open season for the other variables (and interactions between
+them), and our decision to include them in the model will be guided by
+information-theoretic criteria of predictive power.
 
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# building model with sd=1}
-\CommentTok{# InteractionsModelDiffSD1 <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+}
-\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,1),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bADSIC ~ dnorm(0,1),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,1),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ), }
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-\CommentTok{# }
-\CommentTok{# saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")}
-\NormalTok{InteractionsModelDiffSD1 <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiffSD1.rds"}\NormalTok{)}
-
-\CommentTok{#now model with prior sd = .3}
-\CommentTok{# InteractionsModelDiff <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +}
-\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,0.3),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bADSIC ~ dnorm(0,.3),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ), }
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-
-\CommentTok{#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")}
-
-\NormalTok{InteractionsModelDiff <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiff.rds"}\NormalTok{)}
-
-\NormalTok{##prior predictive checks sd =1}
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-
-\NormalTok{priorGroupsSD1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{,}
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{0}\OperatorTok{:}\DecValTok{20}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# building model with sd=1}
+\CommentTok{\# InteractionsModelDiffSD1 \textless{}{-} ulam(}
+\CommentTok{\#   alist(}
+\CommentTok{\#     AdiffS \textasciitilde{} dnorm( mu, sigma ),}
+\CommentTok{\#     mu \textless{}{-} a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+}
+\CommentTok{\#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
+\CommentTok{\#     a \textasciitilde{} dnorm (0,1),}
+\CommentTok{\#     bADS[groupID] \textasciitilde{} dnorm(0,1),}
+\CommentTok{\#     bADSIC \textasciitilde{} dnorm(0,1),}
+\CommentTok{\#     bCBS[groupID] \textasciitilde{} dnorm(0,1),}
+\CommentTok{\#     bIT[groupID] \textasciitilde{} dnorm(0,1),}
+\CommentTok{\#     bIC[groupID] \textasciitilde{} dnorm(0,1),}
+\CommentTok{\#     sigma  \textasciitilde{} dexp(1)}
+\CommentTok{\#   ), }
+\CommentTok{\#   data = summaries}
+\CommentTok{\# )}
+\CommentTok{\# }
+\CommentTok{\# saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")}
+\NormalTok{InteractionsModelDiffSD1 }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/InteractionsModelDiffSD1.rds"}\NormalTok{)}
+
+\CommentTok{\#now model with prior sd = .3}
+\CommentTok{\# InteractionsModelDiff \textless{}{-} ulam(}
+\CommentTok{\#   alist(}
+\CommentTok{\#     AdiffS \textasciitilde{} dnorm( mu, sigma ),}
+\CommentTok{\#     mu \textless{}{-} a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +}
+\CommentTok{\#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
+\CommentTok{\#     a \textasciitilde{} dnorm (0,0.3),}
+\CommentTok{\#     bADS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bADSIC \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bCBS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIT[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIC[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     sigma  \textasciitilde{} dexp(1)}
+\CommentTok{\#   ), }
+\CommentTok{\#   data = summaries}
+\CommentTok{\# )}
+
+\CommentTok{\#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")}
+
+\NormalTok{InteractionsModelDiff }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/InteractionsModelDiff.rds"}\NormalTok{)}
+
+\DocumentationTok{\#\#prior predictive checks sd =1}
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+
+\NormalTok{priorGroupsSD1 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{,}
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{0}\SpecialCharTok{:}\DecValTok{20}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{mu.mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{, mean )}
-\NormalTok{mu.HPDI <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI )))}
-\NormalTok{priorDF <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data, mu.mean, mu.HPDI)}
-\NormalTok{priorDF}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(groupID)}
-\KeywordTok{levels}\NormalTok{(priorDF}\OperatorTok{$}\NormalTok{groupID) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{)}
-\KeywordTok{colnames}\NormalTok{(priorDF)[}\DecValTok{2}\NormalTok{]<-}\StringTok{ "group"}
-
-\NormalTok{priorICSD1  <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(priorDF, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y  =}\NormalTok{ mu.mean,  }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_line}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_ribbon}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ X.}\FloatTok{0.89}\NormalTok{, }\DataTypeTok{ymax =}\NormalTok{ X0.}\FloatTok{89.}\NormalTok{), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors for AAS vs IC"}\NormalTok{,}
-      \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, sd = 1)"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions"}\NormalTok{)}
-
-\NormalTok{priorJoint1 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupsSD1,priorICSD1, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
-\NormalTok{priorJoint1Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint1, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=1 are insanely wide"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{(InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{mu.mean }\OtherTok{\textless{}{-}} \FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{, mean )}
+\NormalTok{mu.HPDI }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{t}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI )))}
+\NormalTok{priorDF }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data, mu.mean, mu.HPDI)}
+\NormalTok{priorDF}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(groupID)}
+\FunctionTok{levels}\NormalTok{(priorDF}\SpecialCharTok{$}\NormalTok{groupID) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{)}
+\FunctionTok{colnames}\NormalTok{(priorDF)[}\DecValTok{2}\NormalTok{]}\OtherTok{\textless{}{-}} \StringTok{"group"}
+
+\NormalTok{priorICSD1  }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(priorDF, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y  =}\NormalTok{ mu.mean,  }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_line}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{geom\_ribbon}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ X.}\FloatTok{0.89}\NormalTok{, }\AttributeTok{ymax =}\NormalTok{ X0.}\FloatTok{89.}\NormalTok{), }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors for AAS vs IC"}\NormalTok{,}
+      \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{"interventions"}\NormalTok{)}
+
+\NormalTok{priorJoint1 }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(priorGroupsSD1,priorICSD1, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{) }
+\NormalTok{priorJoint1Titled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(priorJoint1, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=1 are insanely wide"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{14}\NormalTok{))}
 \NormalTok{priorJoint1Titled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors1-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{#prior predictive check sd =.3}
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiff, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(muLong)}
-
-\NormalTok{priorGroupSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors  by group"}\NormalTok{, }
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = .3)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standarized)"}\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(muLong)}
-
-\NormalTok{priorICSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{, }
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
-
-\NormalTok{priorJoint03 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupSD03,priorICSD03, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
-\NormalTok{priorJoint03Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint03, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=.3 seem sensible"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#prior predictive check sd =.3}
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiff, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{(InteractionsModelDiff , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorGroupSD03 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors  by group"}\NormalTok{, }
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = .3)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standarized)"}\NormalTok{)}
+
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorICSD03 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{, }
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{priorJoint03 }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(priorGroupSD03,priorICSD03, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{) }
+\NormalTok{priorJoint03Titled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(priorJoint03, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=.3 seem sensible"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{14}\NormalTok{))}
 \NormalTok{priorJoint03Titled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/priors03-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{traceplot}\NormalTok{( InteractionsModelDiff )}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
-
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{traceplot}\NormalTok{( InteractionsModelDiff )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-6-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff)}
-\NormalTok{mu_mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , mean )}
-\NormalTok{mu_resid <-}\StringTok{ }\NormalTok{summaries}\OperatorTok{$}\NormalTok{AdiffS }\OperatorTok{-}\StringTok{ }\NormalTok{mu_mean}
-\KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"residuals"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
-
-\normalsize
-
-\section{Model selection}\label{model-selection}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{(InteractionsModelDiff)}
+\NormalTok{mu\_mean }\OtherTok{\textless{}{-}} \FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , mean )}
+\NormalTok{mu\_resid }\OtherTok{\textless{}{-}}\NormalTok{ summaries}\SpecialCharTok{$}\NormalTok{AdiffS }\SpecialCharTok{{-}}\NormalTok{ mu\_mean}
+\FunctionTok{ggplot}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{geom\_density}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ mu\_resid))}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{"residuals"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-7-1} \end{center}
+\normalsize
+
+\hypertarget{model-selection}{%
+\section{Model selection}\label{model-selection}}
 
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{null <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries  }
-\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS}\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{IT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{bIT[groupID] ,}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID],}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIC_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIT_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] ,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-    \CommentTok{#bADSIC ~ dnorm(0,.5),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-    \CommentTok{#bIC ~ dnorm(0,.5),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIT_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITICCBS_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS }\OperatorTok{*}\NormalTok{CBS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{Final <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{tooFar <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC, }
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{     bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,}
-\NormalTok{                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,}
-\NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
-\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison )) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}[H]
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{null }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries  }
+\NormalTok{)}
+
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS}\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{IT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  bIT[groupID] ,}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID],}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSIC\_ADSIT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT\_ADSIT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] ,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{\#bADSIC \textasciitilde{} dnorm(0,.5),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{\#bIC \textasciitilde{} dnorm(0,.5),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSIT\_ITIC\_ADSIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICCBS\_ITIC\_ADSIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS }\SpecialCharTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{Final }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFar }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCBSIC }\SpecialCharTok{*}\NormalTok{ CBS }\SpecialCharTok{*}\NormalTok{ IC, }
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{     bCBSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{comparison}\OtherTok{\textless{}{-}} \FunctionTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC\_ADSIC,}
+\NormalTok{                     ADSITIC\_ADSIC\_ADSIT,ADSIT\_ADSIT,ADSITIC\_ADSIT\_ITIC\_ADSIC,}
+\NormalTok{                     ADSITICCBS\_ITIC\_ADSIC,Final, tooFar)}
+\FunctionTok{mykable}\NormalTok{(}\FunctionTok{round}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(comparison ),}\DecValTok{3}\NormalTok{)) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
 \centering\begingroup\fontsize{9}{11}\selectfont
@@
 \midrule
-\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8393664}\\
-tooFar & 1189.257 & 90.39801 & 4.616272 & 2.884162 & 29.81499 & 0.0834720\\
-\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0771616}\\
-null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
-\cellcolor{gray!6}{IT} & \cellcolor{gray!6}{1345.879} & \cellcolor{gray!6}{144.64185} & \cellcolor{gray!6}{161.237934} & \cellcolor{gray!6}{132.478842} & \cellcolor{gray!6}{19.27433} & \cellcolor{gray!6}{0.0000000}\\
+\cellcolor{gray!6}{tooFar} & \cellcolor{gray!6}{1185.575} & \cellcolor{gray!6}{89.393} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{27.846} & \cellcolor{gray!6}{0.487}\\
+Final & 1185.657 & 89.827 & 0.082 & 2.594 & 27.614 & 0.467\\
+\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1190.304} & \cellcolor{gray!6}{87.920} & \cellcolor{gray!6}{4.729} & \cellcolor{gray!6}{6.055} & \cellcolor{gray!6}{25.882} & \cellcolor{gray!6}{0.046}\\
+null & 1345.358 & 145.805 & 159.783 & 134.039 & 18.061 & 0.000\\
+\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1347.281} & \cellcolor{gray!6}{142.655} & \cellcolor{gray!6}{161.706} & \cellcolor{gray!6}{131.261} & \cellcolor{gray!6}{21.935} & \cellcolor{gray!6}{0.000}\\
 \addlinespace
-ADSIT & 1348.714 & 142.29377 & 164.072877 & 130.485213 & 23.06652 & 0.0000000\\
-\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
-ADSIT\_ADSIT & 1351.571 & 154.69385 & 166.930496 & 140.429304 & 31.91506 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC & 1353.603 & 147.38084 & 168.962571 & 134.581071 & 28.54365 & 0.0000000\\
+IT & 1347.916 & 146.200 & 162.341 & 134.462 & 20.545 & 0.000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1348.366} & \cellcolor{gray!6}{150.638} & \cellcolor{gray!6}{162.791} & \cellcolor{gray!6}{136.811} & \cellcolor{gray!6}{27.604} & \cellcolor{gray!6}{0.000}\\
+ADSIT & 1350.067 & 144.264 & 164.492 & 132.764 & 23.985 & 0.000\\
+\cellcolor{gray!6}{ADSIT\_ADSIT} & \cellcolor{gray!6}{1351.139} & \cellcolor{gray!6}{154.826} & \cellcolor{gray!6}{165.564} & \cellcolor{gray!6}{141.033} & \cellcolor{gray!6}{31.062} & \cellcolor{gray!6}{0.000}\\
+ADSIC & 1351.343 & 145.539 & 165.768 & 133.454 & 25.443 & 0.000\\
 \addlinespace
-\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1353.939} & \cellcolor{gray!6}{147.29717} & \cellcolor{gray!6}{169.298374} & \cellcolor{gray!6}{134.821036} & \cellcolor{gray!6}{26.91553} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.442} & \cellcolor{gray!6}{155.55820} & \cellcolor{gray!6}{170.800602} & \cellcolor{gray!6}{140.950680} & \cellcolor{gray!6}{34.03861} & \cellcolor{gray!6}{0.0000000}\\
+\cellcolor{gray!6}{ADSITIC} & \cellcolor{gray!6}{1353.020} & \cellcolor{gray!6}{147.645} & \cellcolor{gray!6}{167.445} & \cellcolor{gray!6}{135.441} & \cellcolor{gray!6}{26.884} & \cellcolor{gray!6}{0.000}\\
+ADSITIC\_ADSIT\_ITIC\_ADSIC & 1355.187 & 154.826 & 169.613 & 140.659 & 34.652 & 0.000\\
+\cellcolor{gray!6}{ADSITIC\_ADSIC\_ADSIT} & \cellcolor{gray!6}{1356.479} & \cellcolor{gray!6}{157.522} & \cellcolor{gray!6}{170.905} & \cellcolor{gray!6}{143.538} & \cellcolor{gray!6}{34.533} & \cellcolor{gray!6}{0.000}\\
 \bottomrule
@@
 \begin{Highlighting}[]
-\KeywordTok{plot}\NormalTok{(comparison)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
-
+\FunctionTok{plot}\NormalTok{(comparison)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-9-1} \end{center}
 \normalsize
@@
 
+\hypertarget{inspecting-the-model-and-effect-sizes}{%
 \section{Inspecting the model and effect
-sizes}\label{inspecting-the-model-and-effect-sizes}
+sizes}\label{inspecting-the-model-and-effect-sizes}}
 
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# FinalHMC <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +}
-\CommentTok{#     bIC[groupID] * IC + bADSIC * ADS * IC+}
-\CommentTok{#     bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,0.3),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bADSIC ~ dnorm(0,.3),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ),}
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-\CommentTok{# saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
-
-\NormalTok{FinalHMC <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/FinalHMC.rds"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# FinalHMC \textless{}{-} ulam(}
+\CommentTok{\#   alist(}
+\CommentTok{\#     AdiffS \textasciitilde{} dnorm( mu, sigma ),}
+\CommentTok{\#     mu \textless{}{-} a + bADS[groupID] * ADS +  bIT[groupID] +}
+\CommentTok{\#     bIC[groupID] * IC + bADSIC * ADS * IC+}
+\CommentTok{\#     bCBS[groupID] *CBS,}
+\CommentTok{\#     a \textasciitilde{} dnorm (0,0.3),}
+\CommentTok{\#     bADS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bADSIC \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bCBS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIT[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIC[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     sigma  \textasciitilde{} dexp(1)}
+\CommentTok{\#   ),}
+\CommentTok{\#   data = summaries}
+\CommentTok{\# )}
+\CommentTok{\# saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
+
+\CommentTok{\#saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
+
+\NormalTok{FinalHMC }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/FinalHMC.rds"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
 First, let's take a look at the best model coefficients.
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{mykable}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\FunctionTok{precis}\NormalTok{(FinalHMC, }\AttributeTok{depth =} \DecValTok{2}\NormalTok{)))}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\KeywordTok{plot}\NormalTok{(}\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
-
+\FunctionTok{plot}\NormalTok{(}\FunctionTok{precis}\NormalTok{(FinalHMC, }\AttributeTok{depth =} \DecValTok{2}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-11-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visGroup <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, }\DataTypeTok{xmin =}\DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-3}\NormalTok{)}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visGroup }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, }\AttributeTok{xmin =}\DecValTok{2}\NormalTok{, }\AttributeTok{ymax =} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{)}
 \NormalTok{\{}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5} 
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\NormalTok{means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
-\NormalTok{mu_HPDI <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
-\NormalTok{means <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(means)}
-\NormalTok{means}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{rownames}\NormalTok{(means)}
-\KeywordTok{rownames}\NormalTok{(means) <-}\StringTok{ }\OtherTok{NULL}
-\NormalTok{meansDisp <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(mu_HPDI)))}
-\NormalTok{meansDisp <-}\StringTok{ }\NormalTok{meansDisp[,}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
-
-\NormalTok{plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS,  }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
-\CommentTok{#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
-\KeywordTok{return}\NormalTok{(plot)}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5} 
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\NormalTok{means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
+\NormalTok{mu\_HPDI }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
+\NormalTok{means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(means)}
+\NormalTok{means}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{rownames}\NormalTok{(means)}
+\FunctionTok{rownames}\NormalTok{(means) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
+\NormalTok{meansDisp }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(mu\_HPDI)))}
+\NormalTok{meansDisp }\OtherTok{\textless{}{-}}\NormalTok{ meansDisp[,}\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
+
+\NormalTok{plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}\FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS), }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \FunctionTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS,  }\AttributeTok{sep =} \StringTok{""}\NormalTok{))}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
+\CommentTok{\#+   annotation\_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
+\FunctionTok{return}\NormalTok{(plot)}
 \NormalTok{\}}
 
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}
-\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
-
-\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
-\NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
-
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
-\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{ )}
-
-\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{) , visGroupA2C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),visGroupA2C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{), }
-\NormalTok{          visGroupA0C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
-\NormalTok{          visGroupA2C_}\DecValTok{2}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C0}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C2}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visGroupJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-4,4), IC at the rounded mean = 5)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visGroupJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint2, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted change in attacks by activity type and treatment groups (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{visGroupA2C\_2 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}
+\NormalTok{visGroupA2C0 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA2C2 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupA0C\_2 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{ )}
+\NormalTok{visGroupA0C0 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA0C2 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupA2C\_2 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{ )}
+\NormalTok{visGroupA2C0 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{ )}
+\NormalTok{visGroupA2C2 }\OtherTok{\textless{}{-}} \FunctionTok{visGroup}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{ )}
+
+\NormalTok{visGroupJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(visGroupA2C\_2}\SpecialCharTok{+}\NormalTok{removeX }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = {-}2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{) , visGroupA2C0}\SpecialCharTok{+}\FunctionTok{theme\_void}\NormalTok{()}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),visGroupA2C2}\SpecialCharTok{+}\FunctionTok{theme\_void}\NormalTok{()}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{), }
+\NormalTok{          visGroupA0C\_2}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C0}\SpecialCharTok{+}\FunctionTok{theme\_void}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C2}\SpecialCharTok{+}\FunctionTok{theme\_void}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{          visGroupA2C\_2}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = {-}2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C0}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C2}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), }\AttributeTok{ncol =}\DecValTok{3}\NormalTok{, }\AttributeTok{nrow =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visGroupJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visGroupJoint, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}4,4), IC at the rounded mean = 5)"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visGroupJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visGroupJoint2, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted change in attacks by activity type and treatment groups (standardized)"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-12-1} \end{center}
 \normalsize
@@
 
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsCBS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =}\NormalTok{ ADS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{,}
-                            \DataTypeTok{CBS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsCBS }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =}\NormalTok{ ADS , }\AttributeTok{IC =}  \DecValTok{5}\NormalTok{,}
+                            \AttributeTok{CBS =} \FunctionTok{seq}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\AttributeTok{by  =} \FloatTok{0.1}\NormalTok{))}
 \NormalTok{  \{}
-\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(ADS, groupID, IC , CBS)}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-  \KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrast <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrast)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrast <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
-\NormalTok{  cLow <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
-\NormalTok{  cHigh <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(ADS, groupID, IC , CBS)}
+  \FunctionTok{colnames}\NormalTok{(data) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+  \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrast }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data,means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{2}
+\NormalTok{  twos }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{1}
+\NormalTok{  threes }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}
+
+  \FunctionTok{colnames}\NormalTok{(visContrast)[}\FunctionTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrast }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cLow }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cHigh }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{  contrast[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}2}\NormalTok{]  }
 \NormalTok{  \}}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{  contrast[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}1}\NormalTok{]  }
 \NormalTok{  \}}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrast}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{contrast }\OtherTok{\textless{}{-}}\NormalTok{ contrast}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{shift }\OtherTok{\textless{}{-}}\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{contrast }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{shift[i] }\OtherTok{\textless{}{-}} \DecValTok{0}
 \NormalTok{  \}}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
-                          \KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-
-\NormalTok{  visContrastTreatment <-}\StringTok{ }\NormalTok{visContrast[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
-        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{, }
-        \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{,}
-        \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{))}\OperatorTok{+}
-\StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{cLow }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{low }\SpecialCharTok{+}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{shift}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{cHigh }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{high }\SpecialCharTok{+}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{group }\OtherTok{=} \FunctionTok{rep}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                          \FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{)}
+
+\NormalTok{  visContrastTreatment }\OtherTok{\textless{}{-}}\NormalTok{ visContrast[groupID }\SpecialCharTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{ggplot}\NormalTok{(visContrastTreatment, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ CBS, }\AttributeTok{y =}\NormalTok{ contrast, }\AttributeTok{fill =}\NormalTok{ group ))}\SpecialCharTok{+}
+           \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+            \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{mapping =} 
+        \FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ cLow, }\AttributeTok{ymax =}\NormalTok{ cHigh),  }
+         \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{3}\NormalTok{)}\SpecialCharTok{+}
+          \FunctionTok{theme\_tufte}\NormalTok{())}
 \NormalTok{\}}
 
-\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
-\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\NormalTok{removeY,}
-        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
-\StringTok{        }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visContrastCBSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint, }
-      \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
-                                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastCBSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint2, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. CBS  (standardized)"}\NormalTok{,}
-                                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{visContrastCBSJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(}\FunctionTok{visContrastsCBS}\NormalTok{(FinalHMC,}\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}
+      \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = {-}2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+          \FunctionTok{visContrastsCBS}\NormalTok{(FinalHMC,}\AttributeTok{ADS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\SpecialCharTok{+}
+        \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+\NormalTok{        removeY,}
+        \FunctionTok{visContrastsCBS}\NormalTok{(FinalHMC,}\AttributeTok{ADS =} \DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\SpecialCharTok{+}
+        \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\SpecialCharTok{+}
+\NormalTok{        removeY, }\AttributeTok{ncol =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visContrastCBSJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastCBSJoint, }
+      \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastCBSJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastCBSJoint2, }
+\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. CBS  (standardized)"}\NormalTok{,}
+                                \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
-
-\normalsize
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsADS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{, }
-                            \DataTypeTok{ADS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-13-1} \end{center}
+\normalsize
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsADS }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{CBS =}\NormalTok{ CBS , }\AttributeTok{IC =}  \DecValTok{5}\NormalTok{, }
+                            \AttributeTok{ADS =} \FunctionTok{seq}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\AttributeTok{by  =} \FloatTok{0.1}\NormalTok{))}
 \NormalTok{\{}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrastADS <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrastADS)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrastADS <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS))}
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
+  \FunctionTok{colnames}\NormalTok{(data) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastADS }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data,means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{2}
+\NormalTok{  twos }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{1}
+\NormalTok{  threes }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}
+
+  \FunctionTok{colnames}\NormalTok{(visContrastADS)[}\FunctionTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastADS }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS))}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{    contrastADS[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}2}\NormalTok{]  }
 \NormalTok{  \}}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{    contrastADS[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}1}\NormalTok{]  }
 \NormalTok{  \}}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastADS}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{contrast }\OtherTok{\textless{}{-}}\NormalTok{ contrastADS}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{shift }\OtherTok{\textless{}{-}}\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{contrast }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{    visContrastADS}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{    visContrastADS}\SpecialCharTok{$}\NormalTok{shift[i] }\OtherTok{\textless{}{-}} \DecValTok{0}
 \NormalTok{  \}}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
-                             \KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-\NormalTok{  visContrastTreatmentADS <-}\StringTok{ }\NormalTok{visContrastADS[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{,}
-                  \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{, }
-                  \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{cLow }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{low }\SpecialCharTok{+}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{shift}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{cHigh }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{high }\SpecialCharTok{+}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{group }\OtherTok{=} \FunctionTok{rep}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                             \FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentADS }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS[groupID }\SpecialCharTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ ADS, }\AttributeTok{y =}\NormalTok{ contrast, }\AttributeTok{fill =}\NormalTok{ group ))}\SpecialCharTok{+}
+           \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{mapping =} \FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ cLow, }\AttributeTok{ymax =}\NormalTok{ cHigh), }
+       \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{3}\NormalTok{) }\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{())}
 \NormalTok{\}}
 
-\NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{                                   }\NormalTok{removeY,}
-                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}
-\StringTok{                                   }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
-\StringTok{                                   }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visContrastADSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
-                                                        \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastADSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint2, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. ADS (standardized)"}\NormalTok{,}
-                                                        \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{visContrastADSJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(}\FunctionTok{visContrastsADS}\NormalTok{(FinalHMC,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = {-}2"}\NormalTok{)}
+                                 \SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+                                 \FunctionTok{visContrastsADS}\NormalTok{(FinalHMC,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
+                                 \SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+\NormalTok{                                   removeY,}
+                                 \FunctionTok{visContrastsADS}\NormalTok{(FinalHMC,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
+                                 \SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\SpecialCharTok{+}
+                                   \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\SpecialCharTok{+}
+\NormalTok{                                   removeY, }\AttributeTok{ncol =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visContrastADSJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastADSJoint, }
+\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastADSJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastADSJoint2, }
+\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. ADS (standardized)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
-
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-14-1} \end{center}
 \normalsize
@@
 by looking at contrasts (distances from the control group mean) with
-89\% HPDIs by IC.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsIC <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{30}\NormalTok{,}\DataTypeTok{by =} \DecValTok{1}\NormalTok{), }\DataTypeTok{ADS =}\NormalTok{ ADS)}
+89\% HPDIs by IC. Notice the predicted effect of \textsf{IC} is weaker
+than group membership, so for visibility the \(y\)-axis has a smaller
+range. Also, not enough data was available to reliably estimate
+uncertainty for \textsf{IC} above 20, hence the restriction on the
+\(x\)-axis (arleady at lower values, lack of estimates is visible for
+the more extreme covariate settings).
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsIC }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{CBS =}\NormalTok{ CBS ,}
+                           \AttributeTok{IC =}  \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{20}\NormalTok{,}\AttributeTok{by =} \DecValTok{1}\NormalTok{), }\AttributeTok{ADS =}\NormalTok{ ADS)}
 \NormalTok{\{}
-\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
+\NormalTok{  groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
 \NormalTok{  data}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrastIC <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrastIC)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrastIC <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC))}
+  \FunctionTok{colnames}\NormalTok{(data) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastIC }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data,means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastIC)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{2}
+\NormalTok{  twos }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastIC)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{1}
+\NormalTok{  threes }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastIC)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}
+
+  \FunctionTok{colnames}\NormalTok{(visContrastIC)[}\FunctionTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastIC }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastIC))}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
+\NormalTok{    contrastIC[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}2}\NormalTok{]  }
 \NormalTok{  \}}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
+\NormalTok{    contrastIC[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}1}\NormalTok{]  }
 \NormalTok{  \}}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastIC}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means}
+\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{contrast }\OtherTok{\textless{}{-}}\NormalTok{ contrastIC}
+\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{shift }\OtherTok{\textless{}{-}}\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{contrast }\SpecialCharTok{{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{means}
   \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{    visContrastIC}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
+\NormalTok{    visContrastIC}\SpecialCharTok{$}\NormalTok{shift[i] }\OtherTok{\textless{}{-}} \DecValTok{0}
 \NormalTok{  \}}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-\NormalTok{  visContrastTreatmentIC <-}\StringTok{ }\NormalTok{visContrastIC[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{    }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{)}\OperatorTok{+}
-\StringTok{    }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
+\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{cLow }\OtherTok{\textless{}{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{low }\SpecialCharTok{+}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{shift}
+\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{cHigh }\OtherTok{\textless{}{-}}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{high }\SpecialCharTok{+}\NormalTok{ visContrastIC}\SpecialCharTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastIC}\SpecialCharTok{$}\NormalTok{group }\OtherTok{=} \FunctionTok{rep}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{),}
+                            \FunctionTok{nrow}\NormalTok{(visContrastIC)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentIC }\OtherTok{\textless{}{-}}\NormalTok{ visContrastIC[groupID }\SpecialCharTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ contrast, }\AttributeTok{fill =}\NormalTok{ group ))}\SpecialCharTok{+}
+           \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{se=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+    \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{mapping =} \FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ cLow, }\AttributeTok{ymax =}\NormalTok{ cHigh), }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{3}\NormalTok{)}\SpecialCharTok{+}
+    \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{, }\AttributeTok{lty =}\DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.1}\NormalTok{))}
 \NormalTok{\}}
 
-\NormalTok{visContrastsICJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
-\StringTok{               }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.3}\NormalTok{, }\FloatTok{0.9}\NormalTok{),}
-                     \DataTypeTok{legend.key.size =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.key.height =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.key.width =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.title=} \KeywordTok{element_blank}\NormalTok{())}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),  }
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{), }
-\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}
-\NormalTok{)}
-
-\NormalTok{visContrastsICJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-3,3))"}\NormalTok{, }
-                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastsICJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint2, }
- \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. IC (standardized)"}\NormalTok{,}
-                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
+\NormalTok{visContrastsICJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(}
+\FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}
+               \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.3}\NormalTok{, }\FloatTok{0.9}\NormalTok{),}
+                     \AttributeTok{legend.key.size =} \FunctionTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{\textquotesingle{}cm\textquotesingle{}}\NormalTok{),}
+                     \AttributeTok{legend.key.height =} \FunctionTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{\textquotesingle{}cm\textquotesingle{}}\NormalTok{),}
+                     \AttributeTok{legend.key.width =} \FunctionTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{\textquotesingle{}cm\textquotesingle{}}\NormalTok{),}
+                     \AttributeTok{legend.title=} \FunctionTok{element\_blank}\NormalTok{())}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = {-}2"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+\FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}
+  \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),  }
+\FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = {-}2"}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+    \FunctionTok{visContrastsIC}\NormalTok{(}\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CBS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{), }
+\AttributeTok{ncol =} \DecValTok{3}\NormalTok{, }\AttributeTok{nrow =} \DecValTok{3}
+\NormalTok{)}
+
+\NormalTok{visContrastsICJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastsICJoint, }
+\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}3,3))"}\NormalTok{, }
+                \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastsICJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastsICJoint2, }
+ \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. IC (standardized)"}\NormalTok{,}
+                \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-17-1} \end{center}
-
-\normalsize
-
-\section*{References}\label{references}
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-15-1} \end{center}
+\normalsize
+
+\hypertarget{direct-effect}{%
+\section{Direct effect}\label{direct-effect}}
+
+Models for the evaluation of direct effect need to close the indirect
+causal path from the treatment variables to the output, and they do so
+by conditioning on \textsf{CAS}. Again, we face model selection. We
+repeat all the model structures from the previous section, except for
+now, each model is extended with \textsf{CAS} as a predictor. This time
+the model structure we called \textsf{tooFar} turns out to do better. We
+also consider extending it with interactions between \textsf{CAS} and
+\textsf{IT} and \textsf{IC} (jointly and separately), but this results
+in no further improvement.
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{nullDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries  }
+\NormalTok{)}
+
+\NormalTok{ADSDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSICDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS}\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ITDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID]}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSICDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSIC\_ADSITDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSIT\_ADSITDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{\#bADSIC \textasciitilde{} dnorm(0,.5),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+    \CommentTok{\#bIC \textasciitilde{} dnorm(0,.5),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITIC\_ADSIT\_ITIC\_ADSICDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{ADSITICCBS\_ITIC\_ADSICDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{FinalDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCBSIC }\SpecialCharTok{*}\NormalTok{ CBS }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS, }
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect\_CASIT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCBSIC }\SpecialCharTok{*}\NormalTok{ CBS }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bCAS[groupID] }\SpecialCharTok{*}\NormalTok{ CAS, }
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect\_CASIC }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCBSIC }\SpecialCharTok{*}\NormalTok{ CBS }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bCAS }\SpecialCharTok{*}\NormalTok{ CAS }\SpecialCharTok{+}\NormalTok{ bCASIC }\SpecialCharTok{*}\NormalTok{ CAS }\SpecialCharTok{*}\NormalTok{ IC, }
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCASIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{tooFarDirect\_CASIC\_CASIT }\OtherTok{\textless{}{-}} \FunctionTok{quap}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{      bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS }\SpecialCharTok{+}\NormalTok{ bCBSIC }\SpecialCharTok{*}\NormalTok{ CBS }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}\NormalTok{ bCAS[groupID] }\SpecialCharTok{*}\NormalTok{ CAS }\SpecialCharTok{+}\NormalTok{ bCASIC }\SpecialCharTok{*}\NormalTok{ CAS }\SpecialCharTok{*}\NormalTok{ IC, }
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCAS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCASIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, .}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ), }
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\NormalTok{comparisonDirect}\OtherTok{\textless{}{-}} \FunctionTok{compare}\NormalTok{(nullDirect,ADSDirect,ADSICDirect,ITDirect,ADSITDirect,ADSITICDirect,ADSITIC\_ADSICDirect, ADSITIC\_ADSIC\_ADSITDirect,ADSIT\_ADSITDirect,ADSITIC\_ADSIT\_ITIC\_ADSICDirect,}
+\NormalTok{                     ADSITICCBS\_ITIC\_ADSICDirect,FinalDirect, tooFarDirect,tooFarDirect\_CASIT,}
+\NormalTok{                     tooFarDirect\_CASIC,tooFarDirect\_CASIC\_CASIT)}
+
+\FunctionTok{mykable}\NormalTok{(}\FunctionTok{round}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(comparisonDirect),}\DecValTok{3}\NormalTok{))}\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \FunctionTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{,}\StringTok{"scale\_down"}\NormalTok{),}\AttributeTok{font\_size =} \DecValTok{9}\NormalTok{)  }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\resizebox{\linewidth}{!}{
+\fontsize{9}{11}\selectfont
+\begin{tabular}{lrrrrrr}
+\toprule
+  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
+\midrule
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1044.746}} & \cellcolor{gray!6}{\cellcolor{gray!6}{83.935}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}} & \cellcolor{gray!6}{\cellcolor{gray!6}{NA}} & \cellcolor{gray!6}{\cellcolor{gray!6}{37.053}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.777}}\\
+FinalDirect & 1048.925 & 83.369 & 4.178 & 9.720 & 35.057 & 0.096\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect\_CASIT}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1049.258}} & \cellcolor{gray!6}{\cellcolor{gray!6}{85.612}} & \cellcolor{gray!6}{\cellcolor{gray!6}{4.512}} & \cellcolor{gray!6}{\cellcolor{gray!6}{4.952}} & \cellcolor{gray!6}{\cellcolor{gray!6}{38.533}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.081}}\\
+tooFarDirect\_CASIC & 1050.488 & 84.774 & 5.741 & 5.460 & 39.743 & 0.044\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{tooFarDirect\_CASIC\_CASIT}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1058.089}} & \cellcolor{gray!6}{\cellcolor{gray!6}{86.136}} & \cellcolor{gray!6}{\cellcolor{gray!6}{13.343}} & \cellcolor{gray!6}{\cellcolor{gray!6}{9.164}} & \cellcolor{gray!6}{\cellcolor{gray!6}{42.266}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.001}}\\
+\addlinespace
+ADSITICCBS\_ITIC\_ADSICDirect & 1074.474 & 85.119 & 29.727 & 19.463 & 38.768 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSITIC\_ADSIC\_ADSITDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1362.118}} & \cellcolor{gray!6}{\cellcolor{gray!6}{126.956}} & \cellcolor{gray!6}{\cellcolor{gray!6}{317.371}} & \cellcolor{gray!6}{\cellcolor{gray!6}{89.380}} & \cellcolor{gray!6}{\cellcolor{gray!6}{55.637}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ITDirect & 1365.074 & 127.033 & 320.328 & 95.888 & 44.170 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSITIC\_ADSICDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1369.845}} & \cellcolor{gray!6}{\cellcolor{gray!6}{132.826}} & \cellcolor{gray!6}{\cellcolor{gray!6}{325.099}} & \cellcolor{gray!6}{\cellcolor{gray!6}{97.323}} & \cellcolor{gray!6}{\cellcolor{gray!6}{54.381}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+nullDirect & 1370.323 & 133.121 & 325.577 & 102.532 & 46.392 & 0.000\\
+\addlinespace
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSIT\_ADSITDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1371.846}} & \cellcolor{gray!6}{\cellcolor{gray!6}{136.213}} & \cellcolor{gray!6}{\cellcolor{gray!6}{327.100}} & \cellcolor{gray!6}{\cellcolor{gray!6}{99.520}} & \cellcolor{gray!6}{\cellcolor{gray!6}{59.273}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ADSITIC\_ADSIT\_ITIC\_ADSICDirect & 1372.257 & 134.925 & 327.511 & 98.383 & 61.847 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1372.713}} & \cellcolor{gray!6}{\cellcolor{gray!6}{131.716}} & \cellcolor{gray!6}{\cellcolor{gray!6}{327.966}} & \cellcolor{gray!6}{\cellcolor{gray!6}{100.481}} & \cellcolor{gray!6}{\cellcolor{gray!6}{50.297}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+ADSITDirect & 1378.450 & 134.977 & 333.703 & 103.890 & 54.225 & 0.000\\
+\cellcolor{gray!6}{\cellcolor{gray!6}{ADSICDirect}} & \cellcolor{gray!6}{\cellcolor{gray!6}{1384.285}} & \cellcolor{gray!6}{\cellcolor{gray!6}{138.312}} & \cellcolor{gray!6}{\cellcolor{gray!6}{339.538}} & \cellcolor{gray!6}{\cellcolor{gray!6}{106.092}} & \cellcolor{gray!6}{\cellcolor{gray!6}{55.895}} & \cellcolor{gray!6}{\cellcolor{gray!6}{0.000}}\\
+\addlinespace
+ADSITICDirect & 1385.248 & 140.784 & 340.502 & 108.633 & 58.695 & 0.000\\
+\bottomrule
+\end{tabular}}
+\endgroup{}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(comparisonDirect)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/comparisonDirectModels-1} \end{center}
+\normalsize
+
+Let's build a Hamiltonian Monte Carlo with the same formula:
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# tooFarDirectHMC \textless{}{-} ulam(}
+\CommentTok{\#   alist(}
+\CommentTok{\#     AdiffS \textasciitilde{} dnorm( mu, sigma ),}
+\CommentTok{\#     mu \textless{}{-} a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC + }
+\CommentTok{\#       bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC + bCAS * CAS, }
+\CommentTok{\#     a \textasciitilde{} dnorm (0,0.3),}
+\CommentTok{\#     bADS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bADSIC \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bCAS \textasciitilde{} dnorm(0,0.3),}
+\CommentTok{\#     bCBS[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIT[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bIC[groupID] \textasciitilde{} dnorm(0,.3),}
+\CommentTok{\#     bCBSIC \textasciitilde{} dnorm(0, .3),}
+\CommentTok{\#     sigma  \textasciitilde{} dexp(1)}
+\CommentTok{\#   ), }
+\CommentTok{\#   data = summaries}
+\CommentTok{\# )}
+
+\CommentTok{\#saveRDS(tooFarDirectHMC, file = "models/tooFarDirectHMC.rds")}
+
+\NormalTok{tooFarDirectHMC }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/tooFarDirectHMC.rds"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+For a big picture, let's look at predicted direct effect by group and
+user activity profile.
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visGroupDirect }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, CAS, }\AttributeTok{xmin =}\DecValTok{2}\NormalTok{, }\AttributeTok{ymax =} \SpecialCharTok{{-}}\DecValTok{3}\NormalTok{)}
+\NormalTok{\{}
+\NormalTok{  groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{  IC }\OtherTok{\textless{}{-}} \DecValTok{5} 
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{CAS =}\NormalTok{ CAS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+  \FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{  muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+  \FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
+\NormalTok{  mu\_HPDI }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
+\NormalTok{  means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(means)}
+\NormalTok{  means}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{rownames}\NormalTok{(means)}
+  \FunctionTok{rownames}\NormalTok{(means) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
+\NormalTok{  meansDisp }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(mu\_HPDI)))}
+\NormalTok{  meansDisp }\OtherTok{\textless{}{-}}\NormalTok{ meansDisp[,}\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
+
+\NormalTok{  plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}\FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS), }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\SpecialCharTok{+}
+    \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \FunctionTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS, }\StringTok{", CAS="}\NormalTok{, CAS,  }\AttributeTok{sep =} \StringTok{""}\NormalTok{))}\SpecialCharTok{+}
+    \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
+  \CommentTok{\#+   annotation\_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
+  \FunctionTok{return}\NormalTok{(plot)}
+\NormalTok{\}}
+
+\NormalTok{visGroupDirect2\_2\_2 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}
+\NormalTok{visGroupDirect200 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect222 }\OtherTok{\textless{}{-}} \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirect0\_2\_2 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}
+\NormalTok{visGroupDirect000 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect022 }\OtherTok{\textless{}{-}} \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \DecValTok{0}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirect\_2\_2\_2 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}
+\NormalTok{visGroupDirect\_200 }\OtherTok{\textless{}{-}}  \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{)}
+\NormalTok{visGroupDirect\_222 }\OtherTok{\textless{}{-}} \FunctionTok{visGroupDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirectHMC, }\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}\AttributeTok{CBS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{)}
+
+\NormalTok{visGroupDirectJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(visGroupDirect2\_2\_2}\SpecialCharTok{+}\NormalTok{removeX }\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = {-}2"}\NormalTok{),}
+\NormalTok{                                 visGroupDirect200}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 0"}\NormalTok{),}
+\NormalTok{                                 visGroupDirect222}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 2"}\NormalTok{) ,}
+\NormalTok{                        visGroupDirect0\_2\_2}\SpecialCharTok{+}\NormalTok{removeX }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
+\NormalTok{                                visGroupDirect000}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                                visGroupDirect022}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                        visGroupDirect\_2\_2\_2}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"ADS = {-}2"}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                                  visGroupDirect\_200}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
+\NormalTok{                        visGroupDirect\_222}\SpecialCharTok{+}\NormalTok{removeX}\SpecialCharTok{+}\NormalTok{removeY}\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{)}
+\NormalTok{                                 ,}\AttributeTok{ncol =}\DecValTok{3}\NormalTok{, }\AttributeTok{nrow =} \DecValTok{3}\NormalTok{)}
+
+\NormalTok{visGroupDirectJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visGroupDirectJoint, }
+                                  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}4,4), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                  \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visGroupJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visGroupDirectJoint2, }
+                                  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted direct effect of treatment group by activity profile (standardized)"}\NormalTok{,}
+                                                  \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visGroupJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-17-1} \end{center}
+\normalsize
+
+Now, predicted direct effect of five interventions vs.~\textsf{CBS}, for
+three user activity profiles.
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsCBSDirect }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{ADS =}\NormalTok{ ADS , }\AttributeTok{CAS=}\NormalTok{ CAS, }\AttributeTok{IC =}  \DecValTok{5}\NormalTok{,}
+                            \AttributeTok{CBS =} \FunctionTok{seq}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\AttributeTok{by  =} \FloatTok{0.1}\NormalTok{))\{}
+\NormalTok{  groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(ADS, groupID, CAS, IC , CBS)}
+  \FunctionTok{colnames}\NormalTok{(data) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"CAS"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+  \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+
+\NormalTok{  HPDIs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrast }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data,means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{2}
+\NormalTok{  twos }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{1}
+\NormalTok{  threes }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}
+
+  \FunctionTok{colnames}\NormalTok{(visContrast)[}\FunctionTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{)] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+
+\NormalTok{  contrast }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cLow }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
+\NormalTok{  cHigh }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrast))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrast[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrast[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{contrast }\OtherTok{\textless{}{-}}\NormalTok{ contrast}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{shift }\OtherTok{\textless{}{-}}\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{contrast }\SpecialCharTok{{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrast}\SpecialCharTok{$}\NormalTok{shift[i] }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{cLow }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{low }\SpecialCharTok{+}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{shift}
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{cHigh }\OtherTok{\textless{}{-}}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{high }\SpecialCharTok{+}\NormalTok{ visContrast}\SpecialCharTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrast}\SpecialCharTok{$}\NormalTok{group }\OtherTok{=} \FunctionTok{rep}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                          \FunctionTok{nrow}\NormalTok{(visContrast)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{)}
+
+\NormalTok{  visContrastTreatment }\OtherTok{\textless{}{-}}\NormalTok{ visContrast[groupID }\SpecialCharTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{ggplot}\NormalTok{(visContrastTreatment, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ CBS, }\AttributeTok{y =}\NormalTok{ contrast, }\AttributeTok{fill =}\NormalTok{ group ))}\SpecialCharTok{+}
+           \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}
+           \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{mapping =} 
+                         \FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ cLow, }\AttributeTok{ymax =}\NormalTok{ cHigh),  }
+                       \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{3}\NormalTok{)}\SpecialCharTok{+}
+           \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{3.5}\NormalTok{,}\FloatTok{3.5}\NormalTok{)))}
+\NormalTok{\}}
+
+\NormalTok{visContrastDirect }\OtherTok{\textless{}{-}}  \FunctionTok{ggarrange}\NormalTok{(}\FunctionTok{visContrastsCBSDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirect,}\AttributeTok{ADS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{IC =} \DecValTok{5}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = {-}2"}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+          \FunctionTok{visContrastsCBSDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirect,}\AttributeTok{ADS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{, }\AttributeTok{IC =} \DecValTok{5}\NormalTok{) }\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = 0"}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY,}
+          \FunctionTok{visContrastsCBSDirect}\NormalTok{(}\AttributeTok{model =}\NormalTok{ tooFarDirect,}\AttributeTok{ADS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{, }\AttributeTok{IC =} \DecValTok{5}\NormalTok{) }\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"ADS = CAS = 2"}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{)}\SpecialCharTok{+}\NormalTok{removeY}
+\NormalTok{          ,}\AttributeTok{ncol =}\DecValTok{3}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastDirect2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastDirect, }
+                                        \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}3.5,3.5), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastDirect3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastDirect2, }
+                                        \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted direct effect distance from the control group mean vs.
+CBS  (standardized)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastDirect3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-18-1} \end{center}
+\normalsize
+
+Now contrasts against \textsf{ADS}, for three user profiles:
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastsADSDirect }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{model =}\NormalTok{ FinalHMC, }\AttributeTok{CBS =}\NormalTok{ CBS , }\AttributeTok{CAS =}\NormalTok{ CAS, }\AttributeTok{IC =}  \DecValTok{5}\NormalTok{, }
+                            \AttributeTok{ADS =} \FunctionTok{seq}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\AttributeTok{by  =} \FloatTok{0.1}\NormalTok{))}
+\NormalTok{\{}
+\NormalTok{  data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(CBS, groupID, CAS, IC , ADS)}
+  \FunctionTok{colnames}\NormalTok{(data) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"CAS"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
+\NormalTok{  posterior }\OtherTok{\textless{}{-}} \FunctionTok{extract.samples}\NormalTok{(model, }\AttributeTok{n =} \FloatTok{1e5}\NormalTok{)}
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( model, }\AttributeTok{data=}\NormalTok{data ) }
+\NormalTok{  means }\OtherTok{\textless{}{-}}  \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
+\NormalTok{  HPDIs }\OtherTok{\textless{}{-}} \FunctionTok{round}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
+\NormalTok{  visContrastADS }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data,means,}\FunctionTok{t}\NormalTok{(}\FunctionTok{as.data.frame}\NormalTok{(HPDIs)))}
+
+\NormalTok{  ones }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{2}
+\NormalTok{  twos }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}\SpecialCharTok{{-}}\DecValTok{1}
+\NormalTok{  threes }\OtherTok{\textless{}{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{))}
+
+  \FunctionTok{colnames}\NormalTok{(visContrastADS)[}\FunctionTok{c}\NormalTok{(}\DecValTok{7}\NormalTok{,}\DecValTok{8}\NormalTok{)] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
+\NormalTok{  contrastADS }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(visContrastADS))}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
+\NormalTok{    contrastADS[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}2}\NormalTok{]  }
+\NormalTok{  \}}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
+\NormalTok{    contrastADS[i] }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i] }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means[i}\DecValTok{{-}1}\NormalTok{]  }
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{contrast }\OtherTok{\textless{}{-}}\NormalTok{ contrastADS}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{shift }\OtherTok{\textless{}{-}}\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{contrast }\SpecialCharTok{{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{means}
+  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
+\NormalTok{    visContrastADS}\SpecialCharTok{$}\NormalTok{shift[i] }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{  \}}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{cLow }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{low }\SpecialCharTok{+}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{shift}
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{cHigh }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{high }\SpecialCharTok{+}\NormalTok{ visContrastADS}\SpecialCharTok{$}\NormalTok{shift}
+
+\NormalTok{  visContrastADS}\SpecialCharTok{$}\NormalTok{group }\OtherTok{=} \FunctionTok{rep}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
+                             \FunctionTok{nrow}\NormalTok{(visContrastADS)}\SpecialCharTok{/}\DecValTok{3}\NormalTok{)}
+\NormalTok{  visContrastTreatmentADS }\OtherTok{\textless{}{-}}\NormalTok{ visContrastADS[groupID }\SpecialCharTok{!=}\DecValTok{1}\NormalTok{,]}
+
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ ADS, }\AttributeTok{y =}\NormalTok{ contrast, }\AttributeTok{fill =}\NormalTok{ group ))}\SpecialCharTok{+}
+           \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+}
+           \FunctionTok{geom\_ribbon}\NormalTok{(}\AttributeTok{mapping =} \FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ cLow, }\AttributeTok{ymax =}\NormalTok{ cHigh), }
+                       \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{3}\NormalTok{) }\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{())}
+\NormalTok{\}}
+
+\NormalTok{visContrastADSDirectJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(}
+  \FunctionTok{visContrastsADSDirect}\NormalTok{(tooFarDirect,}\AttributeTok{CBS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \SpecialCharTok{{-}}\DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = {-}2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+  \FunctionTok{visContrastsADSDirect}\NormalTok{(tooFarDirect, }\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 0"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+  \FunctionTok{visContrastsADSDirect}\NormalTok{(tooFarDirect, }\AttributeTok{CBS =} \DecValTok{2}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"CBS = CAS = 2"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{))}\SpecialCharTok{+} \FunctionTok{scale\_fill\_discrete}\NormalTok{(}\AttributeTok{guide=}\ConstantTok{FALSE}\NormalTok{),}
+  \AttributeTok{ncol =}\DecValTok{3}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+
+## Warning: Ignoring unknown parameters: se
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+
+## Warning: It is deprecated to specify `guide = FALSE` to remove a guide. Please
+## use `guide = "none"` instead.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{visContrastADSDirectJoint2 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastADSDirectJoint, }
+                                        \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"(range restricted to ({-}3,3), IC at the rounded mean = 5)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{10}\NormalTok{))}
+\NormalTok{visContrastADSDirectJoint3 }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(visContrastADSDirectJoint2, }
+                                        \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predicted direct effect distance from the control group mean vs.
+ADS (standardized)"}\NormalTok{,}
+                                                        \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
+
+\NormalTok{visContrastADSDirectJoint3}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{bayesianReport3_files/figure-latex/unnamed-chunk-19-1} \end{center}
+\normalsize
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}

### 2021-12-21 technicalReport/technicalReport2.Rmd
started technical report

---
title: "Bayesian analysis of the NESTA study of interventions against  verbal aggression online \\linebreak  Technical Report"
author: "Rafal Urbaniak"
output:
  pdf_document:
  number_sections: yes
df_print: kable
keep_tex: yes
includes:
  in_header: Rafal_latex6.sty
html_document:
  df_print: paged
word_document: default
classoption: dvipsnames, enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)

mykable <- function(object) {kable(object, "latex", booktabs = T) %>% kable_styling(latex_options = "striped",font_size = 9)}

removeX <-   theme(axis.title.x=element_blank(),
                   axis.text.x=element_blank(),
                   axis.ticks.x=element_blank())

removeY <-   theme(axis.title.y=element_blank(),
                   axis.text.y=element_blank(),
                   axis.ticks.y=element_blank())

knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 70), tidy = TRUE)

#kable(table(data$group), "latex", booktabs = T, col.names = c("Group", "n")) %>% 
#  kable_styling(latex_options = c("striped","HOLD_position"),font_size = 9) 
```

\tableofcontents

# Data and exploration

\vspace{1mm}
\scriptsize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = TRUE}
Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
summaries <- read.csv(file = "datasets/Summaries.csv")

dates <- colnames(Hate)[-1]
dates <- as.Date(dates)
startDate <- dates[1]
interventionDate <- "2020-07-08"
observationDate <- "2020-09-09"
end <- dates[length(dates)]

periods<- numeric(length(dates))
periods <- ifelse(dates < interventionDate,"pre-treatment",periods)
periods <- ifelse(dates >= interventionDate & dates < observationDate,"treatment",periods)
periods <- ifelse(dates >= observationDate,"post-treatment",periods)

hateTS <- as.data.frame(colSums(Hate[,-1]))
hateTS$date <- as.Date(rownames(hateTS))
rownames(hateTS) <- NULL
colnames(hateTS) <- c("attacks","date")
hateTS$periods <- periods

interventions <- readRDS(file = "datasets/interventions.rds")
interventionsTS <- as.data.frame(table(interventions$day))
interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
colnames(interventionsTS) <- c("date", "interventions")

periodsDF <- merge(x = hateTS, y = interventionsTS, by = "date", all.x = TRUE)

idx <- c(1, diff(periodsDF$date))
i2 <- c(1,which(idx != 1), nrow(periodsDF)+1)
periodsDF$grp <- rep(1:length(diff(i2)), diff(i2))

periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "treatment"] <- 0

periodsPlot <- ggplot(periodsDF)+
  geom_line(aes(x=date, y = attacks, group = grp),
             alpha = 0.8, size = .6)+
  geom_line(aes(x=date, y = interventions, group = grp),
            alpha = 0.8, size = .6)+
  geom_vline(xintercept = startDate, lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept = as.Date(interventionDate), lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept =  as.Date(observationDate), lty = 2, size =.2, alpha=0.5 )+
  geom_vline(xintercept = as.Date(end), lty =2, size =.2, alpha=0.5)+
  labs(title = "Attacks and interventions time series",
       subtitle = "no line at data gaps", 
       caption = "days with data: 81 (pre-treatment), 62 (treatment), 72 (post-treatment)")+
  theme_tufte() + theme(axis.title.x=element_blank(), 
      plot.caption = element_text(hjust = 0.5,  face= "italic"))+
  scale_x_date(date_labels = "%b %d", breaks = c(startDate, as.Date(startDate), as.Date(interventionDate), as.Date(observationDate), end), 
               limits = c(startDate-30,end+10))+ylab("count")+
  annotate("rect", xmin = as.Date(interventionDate), xmax = as.Date(observationDate), ymin = -1, ymax = 360,
           alpha = .2,fill = "darkgreen")+ylim(c(-1,370))+
  annotate("text", label = "pre-treatment", x = as.Date(startDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "treatment", x = as.Date(interventionDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "post-treatment", x = as.Date(observationDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "interventions:", x = as.Date(interventionDate)-52, y = 15, hjust =0 )+
  annotate("text", label = "attacks:", x = as.Date(startDate)-30, y = 215, hjust =0 )

periodsDF$weekdays <-  weekdays(as.Date(periodsDF$date))
periodsDF$weeks <-  week(as.Date(periodsDF$date))

periodsDF$weekdays <- as.factor(periodsDF$weekdays)
levels(periodsDF$weekdays) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday",
                                "Saturday", "Sunday")
weeksPlot <- ggplot(periodsDF)+
  geom_smooth(aes(x = weekdays, y = attacks, group =1))+
  geom_line(aes(x = weekdays, y = attacks, group = weeks),alpha = 0.1)+
  theme_tufte()+labs(title="Weekly attacks over six months", subtitle = "No weekly patterns")+xlab("")+
  ylab("count")
```
\normalsize

For the duration of the project we selected `r length(unique(summaries$author))` Reddit users and tracked their activity, starting on `r `startDate`, beginning the intervention period on `r interventionDate`, leading to a further observation period starting on  `r observationDate` and ending on  `r end`. The time series of attacks observed and of interventions conducted can be inspected in Figure \ref{fig:periodsPlot}.

\begin{figure}
```{r periodsPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
periodsPlot
```
\caption{Daily sums of attacks and interventions throughout the three experimental periods.}
\label{fig:periodsPlot}
\end{figure}

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
#head(summaries) %>% kable( "latex", booktabs = T) %>% 
#  kable_styling(latex_options = c("striped", "scale_down") ,font_size = 9)

```
\normalsize

The basic variables we are dealing with are in the following table.

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
variable <- c("AB", "AD", "AA", "CB", "CD", "CA", "group", "IC")
explanation <- c("attacks before (pre-treatment)", "attacks during (the treatment period)",
                 "attacks after (post-treatment)", "comments before", "comments during",
                 "comments after", "treatment group", "intervention count")
vars <- data.frame(variable, explanation)
mykable(vars)
```

### 2021-12-21 technicalReport/technicalReport3.Rmd
started technical report

---
title: "Bayesian analysis of the NESTA study of interventions against  verbal aggression online \\linebreak  Technical Report"
author: "Rafal Urbaniak"
output:
  pdf_document:
  number_sections: yes
df_print: kable
keep_tex: yes
includes:
  in_header: Rafal_latex7.sty
html_document:
  df_print: paged
word_document: default
classoption: dvipsnames, enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)

mykable <- function(object) {kable(object, "latex", booktabs = T,linesep = "") %>% kable_styling(latex_options = "striped",font_size = 9)}

removeX <-   theme(axis.title.x=element_blank(),
                   axis.text.x=element_blank(),
                   axis.ticks.x=element_blank())

removeY <-   theme(axis.title.y=element_blank(),
                   axis.text.y=element_blank(),
                   axis.ticks.y=element_blank())

knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 70), tidy = TRUE)

#kable(table(data$group), "latex", booktabs = T, col.names = c("Group", "n")) %>% 
#  kable_styling(latex_options = c("striped","HOLD_position"),font_size = 9) 
```

\tableofcontents

# Data and exploration

\vspace{1mm}
\scriptsize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = TRUE}
Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
summaries <- read.csv(file = "datasets/Summaries.csv")

dates <- colnames(Hate)[-1]
dates <- as.Date(dates)
startDate <- dates[1]
interventionDate <- "2020-07-08"
observationDate <- "2020-09-09"
end <- dates[length(dates)]

periods<- numeric(length(dates))
periods <- ifelse(dates < interventionDate,"pre-treatment",periods)
periods <- ifelse(dates >= interventionDate & dates < observationDate,"treatment",periods)
periods <- ifelse(dates >= observationDate,"post-treatment",periods)

hateTS <- as.data.frame(colSums(Hate[,-1]))
hateTS$date <- as.Date(rownames(hateTS))
rownames(hateTS) <- NULL
colnames(hateTS) <- c("attacks","date")
hateTS$periods <- periods

interventions <- readRDS(file = "datasets/interventions.rds")
interventionsTS <- as.data.frame(table(interventions$day))
interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
colnames(interventionsTS) <- c("date", "interventions")

periodsDF <- merge(x = hateTS, y = interventionsTS, by = "date", all.x = TRUE)

idx <- c(1, diff(periodsDF$date))
i2 <- c(1,which(idx != 1), nrow(periodsDF)+1)
periodsDF$grp <- rep(1:length(diff(i2)), diff(i2))

periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "treatment"] <- 0

periodsPlot <- ggplot(periodsDF)+
  geom_line(aes(x=date, y = attacks, group = grp),
             alpha = 0.8, size = .6)+
  geom_line(aes(x=date, y = interventions, group = grp),
            alpha = 0.8, size = .6)+
  geom_vline(xintercept = startDate, lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept = as.Date(interventionDate), lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept =  as.Date(observationDate), lty = 2, size =.2, alpha=0.5 )+
  geom_vline(xintercept = as.Date(end), lty =2, size =.2, alpha=0.5)+
  labs(title = "Attacks and interventions time series",
       subtitle = "no line at data gaps", 
       caption = "days with data: 81 (pre-treatment), 62 (treatment), 72 (post-treatment)")+
  theme_tufte() + theme(axis.title.x=element_blank(), 
      plot.caption = element_text(hjust = 0.5,  face= "italic"))+
  scale_x_date(date_labels = "%b %d", breaks = c(startDate, as.Date(startDate), as.Date(interventionDate), as.Date(observationDate), end), 
               limits = c(startDate-30,end+10))+ylab("count")+
  annotate("rect", xmin = as.Date(interventionDate), xmax = as.Date(observationDate), ymin = -1, ymax = 360,
           alpha = .2,fill = "darkgreen")+ylim(c(-1,370))+
  annotate("text", label = "pre-treatment", x = as.Date(startDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "treatment", x = as.Date(interventionDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "post-treatment", x = as.Date(observationDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "interventions:", x = as.Date(interventionDate)-55, y = 15, hjust =0 )+
  annotate("text", label = "attacks:", x = as.Date(startDate)-30, y = 215, hjust =0 )

periodsDF$weekdays <-  weekdays(as.Date(periodsDF$date))
periodsDF$weeks <-  week(as.Date(periodsDF$date))

periodsDF$weekdays <- as.factor(periodsDF$weekdays)
levels(periodsDF$weekdays) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday",
                                "Saturday", "Sunday")
weeksPlot <- ggplot(periodsDF)+
  geom_smooth(aes(x = weekdays, y = attacks, group =1))+
  geom_line(aes(x = weekdays, y = attacks, group = weeks),alpha = 0.1)+
  theme_tufte()+labs(title="Personal attacks throught weekdays (six months)", subtitle = "No weekly patterns")+xlab("")+
  ylab("count")
```
\normalsize

For the duration of the project we selected `r length(unique(summaries$author))` Reddit users and tracked their activity (with some breaks resulting from API restrictions and technical issues, which were mostly sorted out in the observation period), starting on `r `startDate`, beginning the intervention period on `r interventionDate`, leading to a further observation period starting on  `r observationDate` and ending on  `r end`. The time series of attacks observed and of interventions conducted can be inspected in Figure \ref{fig:periodsPlot}.

\begin{figure}[H]
```{r periodsPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
periodsPlot
```
\caption{Daily sums of attacks and interventions throughout the three experimental periods, with GAM smoothing (blue).}
\label{fig:periodsPlot}
\end{figure}

Interestingly, no weekly patterns of overall aggressive behavior seem apparent, as can be seen from plotting multiple weeks alongside, as in Figure \ref{fig:weeksPlot}.

\begin{figure}[H]
```{r weeksPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
weeksPlot
```
\caption{Attack sums from all  weeks in the experimental period plotted against week days. No pattern seems to arise.}
\label{fig:weeksPlot}
\end{figure}

We analyzed the data from two perspective: we ran a before-and after analysis, comparing the summarized aggression levels before and after the intervention period (with various additional predictors), and a time-series perspective, which took a more fine-grained perspective. For now, we will focus on  the Bayesian before-and-after analysis, for which the data were  cleaned and converted into a summarized form, involving the variables listed in Table \ref{tab:baaVars}.

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
variable <- c("AB", "AD", "AA", "CB", "CD", "CA", "group", "IC")
explanation <- c("attacks before (pre-treatment)", "attacks during (the treatment period)",
                 "attacks after (post-treatment)", "comments before", "comments during",
                 "comments after", "treatment group", "intervention count")
vars <- data.frame(variable, explanation)
#mykable(vars)
```
\normalsize

\begin{table}
\centering
\begin{tabular}{ll}
\toprule
variable & explanation\\
\midrule
\cellcolor{gray!6}{AB} & \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD & attacks during (the treatment period)\\
\cellcolor{gray!6}{AA} & \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB & comments before\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
CA & comments after\\
\cellcolor{gray!6}{group} & \cellcolor{gray!6}{treatment group}\\
IC & intervention count\\
\bottomrule
\end{tabular}

\caption{Variables involved in the before-and-after analysis.}
\label{tab:baaVars}
\end{table}

Further variables were defined in terms of those, in particular, we will be predicting \textsf{AdiffS} which is the standardized difference  \textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized difference \textsf{CA}-\textsf{CB}. The predictors were also standardized (and named $\langle$variable\char`_name$\rangle$S),  and  a numerical index for the group (\textsf{groupID})  has been introduced.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
summaries$ABS <- standardize(summaries$AB)
summaries$CBS <- standardize(summaries$CB)
summaries$AAS <- standardize(summaries$AA)
summaries$CAS <- standardize(summaries$CA)
summaries$CDS <- standardize(summaries$CD)
summaries$ADS <- standardize(summaries$AD)
summaries$group <- as.factor(summaries$group)
summaries$groupID <-  as.integer( as.factor(summaries$group) )
```
\normalsize

The distribution of \textsf{IC} in the treatment groups is visualized in Figure \ref{fig:interventionsDistro}. Note that the distributions are somewhat different, even though the total intervention counts are similar (`r  colSums(table(summaries$IC, summaries$group))["empathy"]` for empathy and  `r colSums(table(summaries$IC, summaries$group))["normative"]` for normative). The issue is discussed in Section XXXXX.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
interventionsDistro <- ggplot(summaries[summaries$group != "control",], aes(x = IC, fill = group))+
  geom_bar()+theme_tufte()+
  xlab("interventions received")+
  labs(title = "Intervention counts in treatment groups")+
  scale_x_continuous(breaks = seq(0,40,5))
```
\normalsize

\begin{figure}[H]
```{r interventionsDistro,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
interventionsDistro
```
\caption{Distribution of daily interventions, by treatment group.}
\label{fig:interventionsDistro}
\end{figure}

Second, when we look at the distribution of standardized difference in attacks, when restricted to (-1,1), the peaks of distributions are shifted a bit between the groups, with lowest median for the normative group, but the differences seem minor (Figure \ref{fig:violJoint}).  This might suggest no impact of the interventions, but this conclusion would be too hasty, as the impact of  other predictor variables and interactions involved can mask actual associations. We will take a closer look at this issue in our analysis.

\vspace{1mm}
\footnotesize
```{r violEmpiricalAdiff,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
violAdiffS <- ggplot(summaries, aes(x=group, y = AdiffS))+
  geom_violin() +theme_tufte() +theme(plot.title.position = "plot")
violJoint <- ggarrange(violAdiffS+ggtitle("whole range"),
              violAdiffS + ylim(c(-1,1))+geom_boxplot(width = .2)+
              ggtitle("restricted to (-1,1)"))   +theme(plot.title.position = "plot")
violJointTitled <- annotate_figure(violJoint, 
  top = text_grob("Empirical distribution of change in attacks (standardized)",
                  size = 12))
```
\normalsize

\begin{figure}[H]
```{r violJoint,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
violJointTitled
```
\caption{Empirical distribution of change in attacks, by treatment group.}
\label{fig:violJoint}
\end{figure}

To see how this masking can occur, let's inspect  changes in attacks against intervention counts. It turns out that  restricting attention to various activity levels results in fairly strong changes to  the regression lines (Figure \ref{fig:linearShift}).

\vspace{1mm}
\footnotesize
```{r ic,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
icplot1 <- ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+ theme(plot.title.position = "plot") +
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-2,2))+
  ggtitle("sd restricted to (-2,2)")+
  theme(legend.position = c(0.65, 0.2))

icplot2 <-  ggplot(summaries, aes(x = IC, y = AdiffS, color = group, fill = group))+
  geom_jitter(alpha = 0.6, size =.8)+theme_tufte()+theme(plot.title.position = "plot") +
  geom_smooth(alpha = 0.2, method = "lm")+
  xlim(c(0,25))+ylim(c(-1,1))+ggtitle("sd restricted to (-1,1)")+
  theme(legend.position = c(0.65, 0.2))

icplotJoint <- ggarrange(icplot1, icplot2) 
icplotTitled <- annotate_figure(icplotJoint, 
  top = text_grob("Change in attacks (standardized) vs interventions received",  size = 12))
```
\normalsize

\begin{figure}
```{r fig:linearShift,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
icplotTitled  
```
\caption{Change in attacks vs intervention counts by treatment group, jittered with  linear smoothing.}
\label{fig:linearShift}
\end{figure}

Some interactions are also suggested by the differences in linear smoothing when attention is restricted when it comes to change in comments.

<!-- \vspace{1mm} -->
<!-- \footnotesize -->
<!-- ```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} -->
<!-- #head(summaries) %>% kable( "latex", booktabs = T) %>%  -->
<!-- #  kable_styling(latex_options = c("striped", "scale_down") ,font_size = 9) -->

<!-- ``` -->
<!-- \normalsize -->

### 2021-12-21 technicalReport/technicalReport4.Rmd
started technical report

--- 2021-12-21 technicalReport/technicalReport3.Rmd
@@
 To see how this masking can occur, let's inspect  changes in attacks against intervention counts.
-It turns out that  restricting attention to various activity levels results in fairly strong changes to  the regression lines (Figure \ref{fig:linearShift}).
+It turns out that  restricting attention to various aggression levels in fairly strong changes to  the regression lines (Figure \ref{fig:linearShift}).
+This suggests we should keep an eye out for interactions in the analysis, and that the initial comparison of means or medians between groups might be misleading if the effects in different volume groups are different and cancel each other.
 
@@
 ```
-\caption{Change in attacks vs intervention counts by treatment group, jittered with  linear smoothing.}
+\caption{Change in attacks vs intervention counts by treatment group, jittered with  linear smoothing. Change of range of aggression levels results in different linear smoothings.}
 \label{fig:linearShift}
@@
 
-Some interactions are also suggested by the differences in linear smoothing when attention is restricted when it comes to change in comments.
+Let's now inspect  correlations between the variables involved in the model (Figure \ref{fig:correlations}).
+Almost no predictors are strongly correlated, except for  \textsf{CBS}, \textsf{CAS} and  \textsf{CDS}.
+We are not interested in using \textsf{CAS} as a predictor, as it occurs \emph{after} the interventions,  and we drop \textsf{CDS} from the analysis, generally   avoiding using these variables in the same model to avoid statistical issues resulting from multicolinearity.
+In fact, it is no surprise that  users' general activity in a period is   a decent proxy for their general activity in other periods.
+
+\begin{figure}[H]
+```{r correlations,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
+summariesCorr <- select(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)
+ggcorr(summariesCorr, method = c("pairwise"),
+       digits = 4, low = "steelblue", mid = "white",
+       high = "darkred", midpoint =0,
+       geom = "tile", label = TRUE, label_size=4, label_round =2, layout.exp =1,
+       label_alpha = FALSE,hjust = 0.75)
+```
+\caption{Correlations between predictors used in the before-and-after analysis.}
+\label{fig:correlations}
+\end{figure}
+
+# Causal inference and variable selection
+
+To identify the right variables to condition (or not condition) on to identify the causal effect of the interventions, we first need to think about the causal structure of the problem.
+A plausible causal structure that we will be working with is visualized in Figure \ref{fig:causal}.
+Comments during impact attacks during, which trigger interventions.
+Unmeasured user features cause comments before, which impact attacks before, and also    attacks before directly.
+Comments during (their impact on ADS is already included)  impact attacks during during directly and  comments after, which impact attacks after and   attacks after directly.
+Intervention count impacts attacks after  and comments after.
+The same directions of impact are included for intervention type.
+Finally, comments through time are connected causally, and so are attacks.
+
+\vspace{1mm}
+\footnotesize
+```{r dag1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%"}
+dag <- dagitty("
+  dag{
+  CDS -> ADS -> IC  
+               U [unobserved]   
+               U -> CBS -> ABS  
+               U -> ABS        
+               U -> CDS -> ADS  
+               U -> ADS         
+               U -> CAS -> AAS    
+               U -> AAS                        
+               IC -> AAS        
+               IC -> CAS        
+               IT -> CAS        
+               IT -> AAS
+               CBS -> CDS -> CAS
+               ABS -> ADS -> AAS
+               }")
+coordinates( dag ) <- list( x=c(CBS=0,ABS=0,CDS=1,ADS=1, CAS = 2,
+                    AAS = 2, IT = 1.5, IC = 1.5, U = .5) ,
+y=c(CBS =0,ABS = 1,CDS = 0,ADS = 1, CAS = 0, AAS = 1, 
+    IT = .3, IC = .7, U =.5) )
+```
+\normalsize
+
+\begin{figure}[H]
+```{r,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
+drawdag(dag)  
+```
+\caption{A causal model used in the before-and-after analysis.}
+\label{fig:causal}
+\end{figure}
+
+We already know not to condition on CDS if we condition on CAS or CBS (multicolinearity).
+What else can we learn from the causal model?
+\textsf{IT} has no backdoor paths, but \textsf{IC} does, so we need to make sure these are closed to avoid including spurious correlations in our analysis.
+There are in fact 65 different paths from \textsf{IC} to \textsf{AAC}.
+Crucially,  all backdoor paths go through \textsf{ADS}, which then becomes either a fork or a pipe, so all backdoor paths can be closed by conditioning on \textsf{ADS}.
+Moreover there is only one directed indirect path, it goes through \textsf{CAS}, so we should not condition on \textsf{CAS} if we are to identify total  causal effect of \textsf{IC} on attacks, including the impact  mediated by its impact on comments (unless we care about the direct effect of \textsf{IC}  and \textsf{IT} on \textsf{AAS}, but that's a separate question).
+This is in line with the adjustment set identified algorithmically using by the \textsf{dagitty} package.
+
+The situation is somewhat  different when it comes to evaluating the *direct* effect of intervention.
+Then, we also need to block indirect causal paths from the intervention to the outcome.
+For such an evaluation we need to also condition on \textsf{CAS}, which is what we will do when we turn to the study of the direct effects of the interventions.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+paths(dag, from = c("IC"), to = "AAS")
+adjustmentSets(dag, exposure = c("IC", "IT"), outcome = "AAS", type = "all")
+```
+\normalsize
+
+In fact, we will be predicting the difference between attacks before and after, and the difference between comments, before and after, but the general points about the nodes involved apply also to defined nodes.
+Finding a maximal sensible set (canonical) of covariates suggests including \textsf{CDS} and \textsf{ABS}.
+As already discussed, we do not include \textsf{CDS} because of its strong correlation with \textsf{CBS}.
+We also do not condition on \textsf{ABS}---not only because it has a pretty strong correlation with another predictor (\textsf{ADS}), but rather mainly because it is used to define the output variable.
+In such a set-up, it is clear that a model including \textsf{ABS} would have better predictive power, but since a definitional connection is present, thinking that its inclusion in the model tells us something about causality  would be misled.
+
+Otherwise, it's open season for the  other variables and interactions between them, and our decision to include or exclude them in the model will be guided by information-theoretic criteria of predictive power.
+
+# Before-and-after analysis: bayesian model building
+
+We build and compared  multiple additive models where the outcome variable is normally distributed around the predicted mean, which is a linear function of predictors (possibly with  interactions).
+Bayesian information criteria  (WAIC)\footnote{
+Here's a more detailed explanation of the model comparison method we used, uninterested reader is invited to skip forward. Let  $y$ be the observations and $\Theta$  a posterior distribution.
+First, log-pointwise-predictive-density is defined by:
+\begin{align*}
+\mathsf{lppd}(y, \Theta) & = \sum_i log\frac{1}{S}\sum_s p (y_i\vert \Theta_s)
+\end{align*}
+\noindent where $S$ is the number of samples in the posterior, and $\Theta_s$ 
+is the $s$-th combination of sampled parameter values in the posterior distribution. That is, 
+for each observation and each combination of 
+parameters in the posterior we first compute its density, then 
+we take the average density of that observation over all combinations of parameters in the posterior,
+and  then take the logarithm.
+Finally, we sum these values up for all the observations.
+Crucially, when comparing posterior distributions with respect to the same dataset, \textsf{lppd}s are proportional
+ to unbiased estimates of their divergence from the real distribution (note that it is \emph{only} 
+ proportional, and for this reason can be used for comparison of distributions 
+ only and makes no intuitive sense on its own).  However, \textsf{lppd} always improves
+  as the model gets more complex, so for model comparison it makes more sense to use 
+ the Widely Applicable Information Criterion (WAIC), which is an approximation of the out-of-sample deviance that converges to the cross-validation approximation in a large sample. It  is defined as
+ the log-posterior-predictive-density with an additional
+  penalty proportional to the variance in the
+  posterior predictions:
+  \begin{align*}
+\mathsf{WAIC(y, \Theta)} & = -2 (\mathsf{lppd} - \overbrace{\sum_i var_\theta \mathsf{log} p (y_i \vert \theta)}^{\mathsf{penalty}})
+  \end{align*}
+\noindent  Thus to construct the penalty, we calculate the variance in log-probabilities for each observation and sum them up.
+Because of the analogy to Akaike's criterion, the penalty is sometimes called the effective number of parameters, $p_{\mathsf{WAIC}}$.
+How does WAIC compare to other information criteria?
+AIC uses MAP estimates instead of the posterior and requires that priors be flat or overwhelmed by the likelihood, and assumes that the posterior distribution is approximately multivariate Gaussian and the sample size is  much greater  than the number of parameters used in the model.
+Bayesian Information Criterion (BIC) also requires flat priors and uses MAP estimates.
+WAIC does not make these assumptions, and provides almost exactly the same results as AIC, when AIC’s assumptions are met.}  applied to a wide selection of predictors lead to the model, whose specification is as follows (we also selected regularizing prior parameters using prior predictive checks to avoid unreasonably narrow overall prior distributions):
+
+\vspace{-2mm}
+
+\begin{align*}
+\mathsf{AdiffS} & \sim \textsf{Norm}(\mu, \sigma)\\
+\mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
+ \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
+ & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS}\\
+ \alpha & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{ADS}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{group}_i} & \sim \textsf{Norm}(0,.3)\\
+\beta_{\mathsf{IC}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{ADSIC}} & \sim \textsf{Norm}(0,.3)\\
+ \beta_{\mathsf{CBS}}[\mathsf{group}_i]& \sim \textsf{Norm}(0,.3)\\
+\end{align*}
+
+That is, we take the resulting mean to be the result of the general average ($\alpha$) and the impact of the following coefficients: group-specific coefficient for \textsf{ADS}, group coefficient, group-specific coefficient for \textsf{IC}, interaction coefficient for \textsf{ADS} and \textsf{IC}, and group-specific coefficient for \textsf{CBS}.
+This is plausible \emph{prima facie} which group a user belongs to might have impact on  how attacks during the treatment is related to attacks after, the role  of the intervention count, and the role of comments before.
+Moreover, the levels of aggressive behavior displayed by the user during treatment might have impact on the role played by the intervention count.
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
+# building model with sd=1
+InteractionsModelDiffSD1 <- ulam(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+
+    bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,1),
+    bADS[groupID] ~ dnorm(0,1),
+    bADSIC ~ dnorm(0,1),
+    bCBS[groupID] ~ dnorm(0,1),
+    bIT[groupID] ~ dnorm(0,1),
+    bIC[groupID] ~ dnorm(0,1),
+    sigma  ~ dexp(1)
+  ),
+  data = summaries
+ )
+
+#saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")
+InteractionsModelDiffSD1 <- readRDS(file = "models/InteractionsModelDiffSD1.rds")
+
+#now model with prior sd = .3
+InteractionsModelDiff <- ulam(
+  alist(
+    AdiffS ~ dnorm( mu, sigma ),
+    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
+    bADSIC * ADS * IC+ bCBS[groupID] *CBS,
+    a ~ dnorm (0,0.3),
+    bADS[groupID] ~ dnorm(0,.3),
+    bADSIC ~ dnorm(0,.3),
+    bCBS[groupID] ~ dnorm(0,.3),
+    bIT[groupID] ~ dnorm(0,.3),
+    bIC[groupID] ~ dnorm(0,.3),
+    sigma  ~ dexp(1)
+  ),
+  data = summaries
+)
+
+#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")
+
+InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
+
+#prior predictive checks sd =1
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link( InteractionsModelDiffSD1 , post=prior , data=data )
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+
+priorGroupsSD1 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+
+  theme_tufte()+xlab("")+
+  labs(title = "Simulated priors by group",
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = 1)")+
+  ylab("change in attacks (standardized)")
+
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 0:20
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link(InteractionsModelDiffSD1 , post=prior , data=data )
+mu.mean <- apply( mu , 2, mean )
+mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
+priorDF <- cbind(data, mu.mean, mu.HPDI)
+priorDF$groupID <- as.factor(groupID)
+levels(priorDF$groupID) <- c("control", "empathy", "normative")
+colnames(priorDF)[2]<- "group"
+
+priorICSD1  <- ggplot(priorDF, aes(x = IC, y  = mu.mean,  fill = group))+
+  geom_line()+geom_ribbon(aes(ymin = X.0.89, ymax = X0.89.), alpha = 0.2)+
+  theme_tufte()+ylab("change in attacks (standardized)")+
+  labs(title = "Simulated priors for AAS vs IC",
+      subtitle = "(at ADS = CBS = 0, sd = 1)")+xlab("interventions")
+
+priorJoint1 <- ggarrange(priorGroupsSD1,priorICSD1, ncol = 2)
+priorJoint1Titled <- annotate_figure(priorJoint1,
+  top = text_grob("Predictive priors with sd=1 are insanely wide",
+                  size = 14))
+priorJoint1Titled
+
+#Some experimentation leads to the value of $\sigma =.3$, which leads to the following priors:
+
+prior predictive check sd =.3
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiff, n = 1e4)
+mu <- link(InteractionsModelDiff , post=prior , data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+head(muLong)
+
+priorGroupSD03 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+theme_tufte()+
+  xlab("")+
+  labs(title = "Simulated priors  by group", 
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = .3)")+
+  ylab("change in attacks (standarized)")
+
+ADS <- 0
+CBS <- 0
+groupID <- 1:3
+IC <- 5  #mean for interventions in treatment
+data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
+prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
+mu <- link( InteractionsModelDiffSD1 , post=prior , data=data ) 
+colnames(mu) <- levels(summaries$group)
+muLong <- melt(mu)
+colnames(muLong) <- c("id", "group", "AdiffS")
+head(muLong)
+
+priorICSD03 <- ggplot(muLong)+
+  geom_violin(aes(x = group, y = AdiffS))+
+  theme_tufte()+xlab("")+
+  labs(title = "Simulated priors by group", 
+  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = 1)")+
+  ylab("change in attacks (standardized)")
+
+priorJoint03 <- ggarrange(priorGroupSD03,priorICSD03, ncol = 2) 
+priorJoint03Titled <- annotate_figure(priorJoint03, 
+  top = text_grob("Predictive priors with sd=.3 seem sensible",
+                  size = 14))
+priorJoint03Titled
+```
+\normalsize
+
+Now, some model diagnostics before we move on (Figure \ref{fig:traceplot}).
+What we are witnessing is (1) stationarity (the chains stay mostly in the most probable regions), (2) good mixing (they explore a range of options in the beginning), and (3) convergence (they stabilize as they progress).
+We also need to   inspect the distribution of residuals, expecting them to be more or less normally distributed, which they are (Figure \ref{fig:residuals}).
+
+\begin{figure}
+```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results = "hide"}
+InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
+traceplot( InteractionsModelDiff )
+```
+\caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.}
+\label{fig:traceplot}
+\end{figure}
+
+\vspace{1mm}
+\footnotesize
+```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", results = "hide"}
+mu <- link(InteractionsModelDiff)
+mu_mean <- apply( mu , 2 , mean )
+mu_resid <- summaries$AdiffS - mu_mean
+ggplot()+geom_density(aes(x = mu_resid))+theme_tufte()+ theme(plot.title.position = "plot") +
+  ggtitle("Residuals are approximately normally distributed")+xlab("residuals")
+```
+\caption{Distribution of residuals from the selected model.}
+\label{fig:residuals}
+\end{figure}
+
+# Before-and-after analysis: results
 

### 2021-12-21 technicalReport/technicalReport4.tex
started technical report

--- 2021-09-16 bayesianAnalysis/bayesianReport.tex
@@
-\documentclass[10pt,dvipsnames,enabledeprecatedfontcommands]{scrartcl}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  10pt,
+  dvipsnames, enabledeprecatedfontcommands]{scrartcl}
+\title{Bayesian analysis of the NESTA study of interventions against
+verbal aggression online \linebreak  Technical Report}
+\author{Rafal Urbaniak}
+\date{}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
-            pdftitle={Bayesian analysis of the NESTA study of interventions against verbal aggression online},
+  pdftitle={Bayesian analysis of the NESTA study of interventions against verbal aggression online Technical Report},
   pdfauthor={Rafal Urbaniak},
   colorlinks=true,
-            linkcolor=Maroon,
-            citecolor=Blue,
-            urlcolor=blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={blue},
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{color}
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-%\documentclass{article}
-
-% %packages
- \usepackage{booktabs}
-
-\usepackage{multirow}
-
-\usepackage{graphicx}
-
-\usepackage{longtable}
-\usepackage{ragged2e}
-\usepackage{etex}
-%\usepackage{yfonts}
-\usepackage{marvosym}
-\usepackage[notextcomp]{kpfonts}
-\usepackage{nicefrac}
-\newcommand*{\QED}{\hfill \footnotesize {\sc Q.e.d.}}
-\usepackage{floatrow}
-
-\usepackage[textsize=footnotesize]{todonotes}
-%\linespread{1.5}
-\usepackage{pdfpages}
-\setlength{\parindent}{10pt}
-\setlength{\parskip}{1pt}
-
-%language
-\usepackage{times}
-\usepackage{t1enc}
-%\usepackage[utf8x]{inputenc}
-%\usepackage[polish]{babel}
-%\usepackage{polski}
-\usepackage[utf8]{inputenc}
-\usepackage{mathptmx}
-\usepackage[scaled=0.88]{helvet}
-
-%AMS
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{mathtools}
-
-\usepackage{geometry}
- \geometry{a4paper,left=35mm,top=20mm,}
-
-%environments
-\newtheorem{fact}{Fact}
-
-%abbreviations
-\newcommand{\ra}{\rangle}
-\newcommand{\la}{\langle}
-\newcommand{\n}{\neg}
-\newcommand{\et}{\wedge}
-\newcommand{\jt}{\rightarrow}
-\newcommand{\ko}[1]{\forall  #1\,}
-\newcommand{\ro}{\leftrightarrow}
-\newcommand{\exi}[1]{\exists\, {_{#1}}}
-\newcommand{\pr}[1]{\mathsf{P}(#1)}
-\newcommand{\cost}{\mathsf{cost}}
-
-\newcommand{\odds}{\mathsf{Odds}}
-\newcommand{\ind}{\mathsf{Ind}}
-\newcommand{\nf}[2]{\nicefrac{#1\,}{#2}}
-\newcommand{\R}[1]{\texttt{#1}}
-\newcommand{\prr}[1]{\mbox{$\mathtt{P}_{prior}(#1)$}}
-\newcommand{\prp}[1]{\mbox{$\mathtt{P}_{posterior}(#1)$}}
-
-\newtheorem{q}{\color{blue}Question}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-
-%technical intermezzo
-%---------------------
-
-\newcommand{\intermezzoa}{
-	\begin{minipage}[c]{13cm}
-	\begin{center}\rule{10cm}{0.4pt}
-
-	\tiny{\sc Optional Content Starts}
-
-	\vspace{-1mm}
-
-	\rule{10cm}{0.4pt}\end{center}
-	\end{minipage}\nopagebreak 
-	}
-
-\newcommand{\intermezzob}{\nopagebreak 
-	\begin{minipage}[c]{13cm}
-	\begin{center}\rule{10cm}{0.4pt}
-
-	\tiny{\sc Optional Content Ends}
-
-	\vspace{-1mm}
-
-	\rule{10cm}{0.4pt}\end{center}
-	\end{minipage}
-	}
-%--------------------
-
-\newtheorem*{reply*}{Reply}
-\usepackage{enumitem}
-\newcommand{\question}[1]{\begin{enumerate}[resume,leftmargin=0cm,labelsep=0cm,align=left]
-\item #1
-\end{enumerate}}
-
-\usepackage{float}
-
-% \setbeamertemplate{blocks}[rounded][shadow=true]
-% \setbeamertemplate{itemize items}[ball]
-% \AtBeginPart{}
-% \AtBeginSection{}
-% \AtBeginSubsection{}
-% \AtBeginSubsubsection{}
-% \setlength{\emergencystretch}{0em}
-% \setlength{\parskip}{0pt}
-
-\usepackage[authoryear]{natbib}
-
-%\bibliographystyle{apalike}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{booktabs}
@@
 
-\section{Exploration}\label{exploration}
-
-Load the dataset and take a look first.
-
-\vspace{1mm} \footnotesize
+\hypertarget{data-and-exploration}{%
+\section{Data and exploration}\label{data-and-exploration}}
+
+\vspace{1mm}
+\scriptsize
 
@@
 \begin{Highlighting}[]
-\NormalTok{summaries <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\DataTypeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(summaries) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{kable}\NormalTok{( }\StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}\StringTok{ }
-\StringTok{  }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }\StringTok{"scale_down"}\NormalTok{) ,}\DataTypeTok{font_size =} \DecValTok{9}\NormalTok{)}
+\NormalTok{Hate }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/RAWNESTA/Hate.rds"}\NormalTok{)}
+\NormalTok{Comments }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/RAWNESTA/Comments.rds"}\NormalTok{)}
+\NormalTok{summaries }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/Summaries.csv"}\NormalTok{)}
+
+\NormalTok{dates }\OtherTok{\textless{}{-}} \FunctionTok{colnames}\NormalTok{(Hate)[}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]}
+\NormalTok{dates }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(dates)}
+\NormalTok{startDate }\OtherTok{\textless{}{-}}\NormalTok{ dates[}\DecValTok{1}\NormalTok{]}
+\NormalTok{interventionDate }\OtherTok{\textless{}{-}} \StringTok{"2020{-}07{-}08"}
+\NormalTok{observationDate }\OtherTok{\textless{}{-}} \StringTok{"2020{-}09{-}09"}
+\NormalTok{end }\OtherTok{\textless{}{-}}\NormalTok{ dates[}\FunctionTok{length}\NormalTok{(dates)]}
+
+\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{(}\FunctionTok{length}\NormalTok{(dates))}
+\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textless{}}\NormalTok{ interventionDate, }\StringTok{"pre{-}treatment"}\NormalTok{, periods)}
+\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textgreater{}=}\NormalTok{ interventionDate }\SpecialCharTok{\&}\NormalTok{ dates }\SpecialCharTok{\textless{}}\NormalTok{ observationDate,}
+    \StringTok{"treatment"}\NormalTok{, periods)}
+\NormalTok{periods }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(dates }\SpecialCharTok{\textgreater{}=}\NormalTok{ observationDate, }\StringTok{"post{-}treatment"}\NormalTok{, periods)}
+
+\NormalTok{hateTS }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(Hate[, }\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]))}
+\NormalTok{hateTS}\SpecialCharTok{$}\NormalTok{date }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(}\FunctionTok{rownames}\NormalTok{(hateTS))}
+\FunctionTok{rownames}\NormalTok{(hateTS) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
+\FunctionTok{colnames}\NormalTok{(hateTS) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"attacks"}\NormalTok{, }\StringTok{"date"}\NormalTok{)}
+\NormalTok{hateTS}\SpecialCharTok{$}\NormalTok{periods }\OtherTok{\textless{}{-}}\NormalTok{ periods}
+
+\NormalTok{interventions }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"datasets/interventions.rds"}\NormalTok{)}
+\NormalTok{interventionsTS }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{table}\NormalTok{(interventions}\SpecialCharTok{$}\NormalTok{day))}
+\NormalTok{interventionsTS}\SpecialCharTok{$}\NormalTok{Var1 }\OtherTok{\textless{}{-}} \FunctionTok{as.Date}\NormalTok{(interventionsTS}\SpecialCharTok{$}\NormalTok{Var1)}
+\FunctionTok{colnames}\NormalTok{(interventionsTS) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"date"}\NormalTok{, }\StringTok{"interventions"}\NormalTok{)}
+
+\NormalTok{periodsDF }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hateTS, }\AttributeTok{y =}\NormalTok{ interventionsTS, }\AttributeTok{by =} \StringTok{"date"}\NormalTok{, }\AttributeTok{all.x =} \ConstantTok{TRUE}\NormalTok{)}
+
+\NormalTok{idx }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FunctionTok{diff}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}
+\NormalTok{i2 }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FunctionTok{which}\NormalTok{(idx }\SpecialCharTok{!=} \DecValTok{1}\NormalTok{), }\FunctionTok{nrow}\NormalTok{(periodsDF) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{)}
+\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{grp }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(}\FunctionTok{diff}\NormalTok{(i2)), }\FunctionTok{diff}\NormalTok{(i2))}
+
+\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{interventions[}\FunctionTok{is.na}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{interventions) }\SpecialCharTok{\&}\NormalTok{ periodsDF}\SpecialCharTok{$}\NormalTok{periods }\SpecialCharTok{==}
+    \StringTok{"treatment"}\NormalTok{] }\OtherTok{\textless{}{-}} \DecValTok{0}
+
+\NormalTok{periodsPlot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(periodsDF) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date, }\AttributeTok{y =}\NormalTok{ attacks,}
+    \AttributeTok{group =}\NormalTok{ grp), }\AttributeTok{alpha =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.6}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date, }\AttributeTok{y =}\NormalTok{ interventions,}
+    \AttributeTok{group =}\NormalTok{ grp), }\AttributeTok{alpha =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.6}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =}\NormalTok{ startDate,}
+    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(interventionDate),}
+    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(observationDate),}
+    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept =} \FunctionTok{as.Date}\NormalTok{(end),}
+    \AttributeTok{lty =} \DecValTok{2}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Attacks and interventions time series"}\NormalTok{,}
+    \AttributeTok{subtitle =} \StringTok{"no line at data gaps"}\NormalTok{, }\AttributeTok{caption =} \StringTok{"days with data: 81 (pre{-}treatment), 62 (treatment), 72 (post{-}treatment)"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(), }\AttributeTok{plot.caption =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{hjust =} \FloatTok{0.5}\NormalTok{,}
+    \AttributeTok{face =} \StringTok{"italic"}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{scale\_x\_date}\NormalTok{(}\AttributeTok{date\_labels =} \StringTok{"\%b \%d"}\NormalTok{, }\AttributeTok{breaks =} \FunctionTok{c}\NormalTok{(startDate,}
+    \FunctionTok{as.Date}\NormalTok{(startDate), }\FunctionTok{as.Date}\NormalTok{(interventionDate), }\FunctionTok{as.Date}\NormalTok{(observationDate),}
+\NormalTok{    end), }\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(startDate }\SpecialCharTok{{-}} \DecValTok{30}\NormalTok{, end }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"count"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"rect"}\NormalTok{,}
+    \AttributeTok{xmin =} \FunctionTok{as.Date}\NormalTok{(interventionDate), }\AttributeTok{xmax =} \FunctionTok{as.Date}\NormalTok{(observationDate),}
+    \AttributeTok{ymin =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{, }\AttributeTok{ymax =} \DecValTok{360}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{fill =} \StringTok{"darkgreen"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}
+    \DecValTok{370}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"pre{-}treatment"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(startDate) }\SpecialCharTok{+}
+    \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"treatment"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(interventionDate) }\SpecialCharTok{+}
+    \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"post{-}treatment"}\NormalTok{,}
+    \AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(observationDate) }\SpecialCharTok{+} \DecValTok{2}\NormalTok{, }\AttributeTok{y =} \DecValTok{370}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{,}
+    \AttributeTok{label =} \StringTok{"interventions:"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(interventionDate) }\SpecialCharTok{{-}} \DecValTok{55}\NormalTok{, }\AttributeTok{y =} \DecValTok{15}\NormalTok{,}
+    \AttributeTok{hjust =} \DecValTok{0}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{annotate}\NormalTok{(}\StringTok{"text"}\NormalTok{, }\AttributeTok{label =} \StringTok{"attacks:"}\NormalTok{, }\AttributeTok{x =} \FunctionTok{as.Date}\NormalTok{(startDate) }\SpecialCharTok{{-}}
+    \DecValTok{30}\NormalTok{, }\AttributeTok{y =} \DecValTok{215}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{0}\NormalTok{)}
+
+\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weekdays }\OtherTok{\textless{}{-}} \FunctionTok{weekdays}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}
+\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weeks }\OtherTok{\textless{}{-}} \FunctionTok{week}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{date))}
+
+\NormalTok{periodsDF}\SpecialCharTok{$}\NormalTok{weekdays }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{weekdays)}
+\FunctionTok{levels}\NormalTok{(periodsDF}\SpecialCharTok{$}\NormalTok{weekdays) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Monday"}\NormalTok{, }\StringTok{"Tuesday"}\NormalTok{, }\StringTok{"Wednesday"}\NormalTok{, }\StringTok{"Thursday"}\NormalTok{,}
+    \StringTok{"Friday"}\NormalTok{, }\StringTok{"Saturday"}\NormalTok{, }\StringTok{"Sunday"}\NormalTok{)}
+\NormalTok{weeksPlot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(periodsDF) }\SpecialCharTok{+} \FunctionTok{geom\_smooth}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ weekdays, }\AttributeTok{y =}\NormalTok{ attacks,}
+    \AttributeTok{group =} \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ weekdays, }\AttributeTok{y =}\NormalTok{ attacks, }\AttributeTok{group =}\NormalTok{ weeks),}
+    \AttributeTok{alpha =} \FloatTok{0.1}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Personal attacks throught weekdays (six months)"}\NormalTok{,}
+    \AttributeTok{subtitle =} \StringTok{"No weekly patterns"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"count"}\NormalTok{)}
 \end{Highlighting}
@@
 
+\normalsize
+
+For the duration of the project we selected 486 Reddit users and tracked
+their activity (with some breaks resulting from API restrictions and
+technical issues, which were mostly sorted out in the observation
+period), starting on \texttt{r}startDate`, beginning the intervention
+period on 2020-07-08, leading to a further observation period starting
+on 2020-09-09 and ending on 2020-11-20. The time series of attacks
+observed and of interventions conducted can be inspected in Figure
+\ref{fig:periodsPlot}.
+
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/periodsPlot-1} \end{center}
+\caption{Daily sums of attacks and interventions throughout the three experimental periods, with GAM smoothing (blue).}
+\label{fig:periodsPlot}
+\end{figure}
+
+Interestingly, no weekly patterns of overall aggressive behavior seem
+apparent, as can be seen from plotting multiple weeks alongside, as in
+Figure \ref{fig:weeksPlot}.
+
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/weeksPlot-1} \end{center}
+\caption{Attack sums from all  weeks in the experimental period plotted against week days. No pattern seems to arise.}
+\label{fig:weeksPlot}
+\end{figure}
+
+We analyzed the data from two perspective: we ran a before-and after
+analysis, comparing the summarized aggression levels before and after
+the intervention period (with various additional predictors), and a
+time-series perspective, which took a more fine-grained perspective. For
+now, we will focus on the Bayesian before-and-after analysis, for which
+the data were cleaned and converted into a summarized form, involving
+the variables listed in Table \ref{tab:baaVars}.
+
+\vspace{1mm}
+\footnotesize
+
+\normalsize
+
 \begin{table}
-\centering\begingroup\fontsize{9}{11}\selectfont
-
-\resizebox{\linewidth}{!}{
-\begin{tabular}{rlrrrrrrrrrrlr}
-\toprule
-X & author & AB & AD & AA & CB & CD & CA & Adiff & Cdiff & AdiffS & CdiffS & group & IC\\
-\midrule
-\cellcolor{gray!6}{1} & \cellcolor{gray!6}{\_swf} & \cellcolor{gray!6}{19} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{720} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{28} & \cellcolor{gray!6}{-19} & \cellcolor{gray!6}{-692} & \cellcolor{gray!6}{-0.0245122} & \cellcolor{gray!6}{-0.3501491} & \cellcolor{gray!6}{normative} & \cellcolor{gray!6}{1}\\
-2 & -Allergic & 24 & 24 & 8 & 1614 & 1451 & 1237 & -16 & -377 & 0.0719197 & 0.1057675 & normative & 3\\
-\cellcolor{gray!6}{3} & \cellcolor{gray!6}{-funny-username-} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{12} & \cellcolor{gray!6}{847} & \cellcolor{gray!6}{497} & \cellcolor{gray!6}{721} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-126} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{0.4690535} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
-4 & -Johnny- & 18 & 2 & 8 & 1465 & 408 & 684 & -10 & -781 & 0.2647835 & -0.4789637 & empathy & 2\\
-\cellcolor{gray!6}{5} & \cellcolor{gray!6}{1secwhileiyeet3} & \cellcolor{gray!6}{15} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{1384} & \cellcolor{gray!6}{198} & \cellcolor{gray!6}{120} & \cellcolor{gray!6}{-11} & \cellcolor{gray!6}{-1264} & \cellcolor{gray!6}{0.2326395} & \cellcolor{gray!6}{-1.1780359} & \cellcolor{gray!6}{control} & \cellcolor{gray!6}{0}\\
-\addlinespace
-6 & 20CharsIsNotEnough & 16 & 10 & 25 & 779 & 907 & 972 & 9 & 193 & 0.8755188 & 0.9307596 & empathy & 4\\
-\bottomrule
-\end{tabular}}
-\endgroup{}
-\end{table}
-
-\normalsize
-
-The basic variables we are dealing with are in the following table.
-
-\begin{table}
-\centering\begingroup\fontsize{9}{11}\selectfont
-
+\centering
 \begin{tabular}{ll}
@@
 \cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
-\addlinespace
 CA & comments after\\
@@
 \end{tabular}
-\endgroup{}
+
+\caption{Variables involved in the before-and-after analysis.}
+\label{tab:baaVars}
 \end{table}
 
-Further variables are defined in terms of those, in particular, we will
+Further variables were defined in terms of those, in particular, we will
 be predicting \textsf{AdiffS} which is the standardized difference
 \textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized
-difference \textsf{CA}-\textsf{CB}. Before we proceed, we will also
-standardize the predictors, and add a numerical index for the group:
-
-\vspace{1mm} \footnotesize
+difference \textsf{CA}-\textsf{CB}. The predictors were also
+standardized (and named \(\langle\)variable\char`\_name\(\rangle\)S),
+and a numerical index for the group (\textsf{groupID}) has been
+introduced.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{ABS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AB)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CBS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CB)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{AAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AA)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CAS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CA)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{CDS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{CD)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{ADS <-}\StringTok{ }\KeywordTok{standardize}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{AD)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{summaries}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{  }\KeywordTok{as.integer}\NormalTok{( }\KeywordTok{as.factor}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group) )}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ABS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AB)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CBS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CB)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{AAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AA)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CAS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CA)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{CDS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{CD)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{ADS }\OtherTok{\textless{}{-}} \FunctionTok{standardize}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{AD)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{group }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{summaries}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{as.factor}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group))}
 \end{Highlighting}
@@
 
-First, let's take a look at the distribution of \textsf{IC} in the
-treatment groups:
-
-\vspace{1mm} \footnotesize
+The distribution of \textsf{IC} in the treatment groups is visualized in
+Figure \ref{fig:interventionsDistro}. Note that the distributions are
+somewhat different, even though the total intervention counts are
+similar (110 for empathy and 119 for normative). The issue is discussed
+in Section XXXXX.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\KeywordTok{ggplot}\NormalTok{(summaries[summaries}\OperatorTok{$}\NormalTok{group }\OperatorTok{!=}\StringTok{ "control"}\NormalTok{,], }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_bar}\NormalTok{()}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions received"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Intervention counts in treatment groups"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}\DataTypeTok{breaks =} \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{40}\NormalTok{,}\DecValTok{5}\NormalTok{))}
+\NormalTok{interventionsDistro }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries[summaries}\SpecialCharTok{$}\NormalTok{group }\SpecialCharTok{!=} \StringTok{"control"}\NormalTok{, ],}
+    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+} \FunctionTok{geom\_bar}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{xlab}\NormalTok{(}\StringTok{"interventions received"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Intervention counts in treatment groups"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}
+    \DecValTok{40}\NormalTok{, }\DecValTok{5}\NormalTok{))}
 \end{Highlighting}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/treatmentHist-1} \end{center}
-
 \normalsize
 
-\todo{Note there were much more empathetic interventions, this needs an explanation}
-
-\todo{Question: intervention counts by group}
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/interventionsDistro-1} \end{center}
+\caption{Distribution of daily interventions, by treatment group.}
+\label{fig:interventionsDistro}
+\end{figure}
 
@@
 attacks, when restricted to (-1,1), the peaks of distributions are
-shifted a bit, with lowest median for the normative group, but not too
-much:
-
-\vspace{1mm} \footnotesize
+shifted a bit between the groups, with lowest median for the normative
+group, but the differences seem minor (Figure \ref{fig:violJoint}). This
+might suggest no impact of the interventions, but this conclusion would
+be too hasty, as the impact of other predictor variables and
+interactions involved can mask actual associations. We will take a
+closer look at this issue in our analysis.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\NormalTok{violAdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
-\NormalTok{violJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violAdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
-\NormalTok{              violAdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
+\NormalTok{violAdiffS }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS)) }\SpecialCharTok{+} \FunctionTok{geom\_violin}\NormalTok{() }\SpecialCharTok{+}
+    \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{)}
+\NormalTok{violJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(violAdiffS }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{), violAdiffS }\SpecialCharTok{+}
+    \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{geom\_boxplot}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.2}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"restricted to ({-}1,1)"}\NormalTok{)) }\SpecialCharTok{+}
+    \FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{)}
+\NormalTok{violJointTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(violJoint, }\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in attacks (standardized)"}\NormalTok{,}
+    \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Warning: Removed 58 rows containing non-finite values (stat_ydensity).
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: Removed 58 rows containing non-finite values (stat_boxplot).
-\end{verbatim}
+\normalsize
+
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/violJoint-1} \end{center}
+\caption{Empirical distribution of change in attacks, by treatment group.}
+\label{fig:violJoint}
+\end{figure}
+
+To see how this masking can occur, let's inspect changes in attacks
+against intervention counts. It turns out that restricting attention to
+various aggression levels in fairly strong changes to the regression
+lines (Figure \ref{fig:linearShift}). This suggests we should keep an
+eye out for interactions in the analysis, and that the initial
+comparison of means or medians between groups might be misleading if the
+effects in different volume groups are different and cancel each other.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\NormalTok{violJointTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in attacks (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-\NormalTok{violJointTitled}
+\NormalTok{icplot1 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ AdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
+    \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.8}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{25}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{,}
+    \DecValTok{2}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}2,2)"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{,}
+    \FloatTok{0.2}\NormalTok{))}
+
+\NormalTok{icplot2 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(summaries, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y =}\NormalTok{ AdiffS, }\AttributeTok{color =}\NormalTok{ group, }\AttributeTok{fill =}\NormalTok{ group)) }\SpecialCharTok{+}
+    \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{size =} \FloatTok{0.8}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_tufte}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{method =} \StringTok{"lm"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{xlim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{25}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{,}
+    \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to ({-}1,1)"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{,}
+    \FloatTok{0.2}\NormalTok{))}
+
+\NormalTok{icplotJoint }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(icplot1, icplot2)}
+\NormalTok{icplotTitled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(icplotJoint, }\AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Change in attacks (standardized) vs interventions received"}\NormalTok{,}
+    \AttributeTok{size =} \DecValTok{12}\NormalTok{))}
 \end{Highlighting}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEmpiricalAdiff-1} \end{center}
-
 \normalsize
 
-Analogous plot for comments does not reveal this slight downward shift
-for normative, but otherwise the visualisation migth suggest no strong
-impact of interventions on attacks, and no impact on comments.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{violCdiffS <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{group, }\DataTypeTok{y =}\NormalTok{ CdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{() }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{() }
-\NormalTok{violJointC <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(violCdiffS}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"whole range"}\NormalTok{),}
-\NormalTok{              violCdiffS }\OperatorTok{+}\StringTok{ }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{geom_boxplot}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{              }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"restricted to (-1,1)"}\NormalTok{)) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Warning: Removed 90 rows containing non-finite values (stat_ydensity).
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: Removed 90 rows containing non-finite values (stat_boxplot).
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{violJointCTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(violJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Empirical distribution of change in comments (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-\NormalTok{violJointCTitled}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/violEpmiricalCdiff-1} \end{center}
-
-\normalsize
-
-However, plotting changes against intervention counts reveals that
-restricting attention to various activity levels drastically changes the
-regression lines.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{icplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ AdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icplot1, icplot2) }
-\NormalTok{icplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icplotJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in attacks (standardized) vs interventions received"}\NormalTok{,  }\DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-\NormalTok{icplotTitled}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/ic-1} \end{center}
-
-\normalsize
-
-Some interactions are also suggested by the differences in linear
-smoothing when attention is restricted when it comes to change in
-comments.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{icCplot1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-2,2)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icCplot2 <-}\StringTok{  }\KeywordTok{ggplot}\NormalTok{(summaries, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ CdiffS, }\DataTypeTok{color =}\NormalTok{ group, }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_jitter}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\NormalTok{.}\DecValTok{8}\NormalTok{)}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{25}\NormalTok{))}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{))}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"sd restricted to (-1,1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.65}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
-
-\NormalTok{icCplotJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(icCplot1, icCplot2) }
-\NormalTok{icCplotTitled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(icCplotJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Change in comments (standardized) vs interventions received"}\NormalTok{,}
-   \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-\NormalTok{icCplotTitled}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/icc-1} \end{center}
-
-\normalsize
-
-This suggests we should keep an eye out for interactions in the
-analysis, and that the intial comparison of means or medians between
-groups might be misleading if the effects in different volume groups are
-different and cancel each other.
-
-Now, let's inspect correlations between the variables involved in the
-model:
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{summariesCorr <-}\StringTok{ }\KeywordTok{select}\NormalTok{(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)}
-\KeywordTok{ggcorr}\NormalTok{(summariesCorr, }\DataTypeTok{method =} \KeywordTok{c}\NormalTok{(}\StringTok{"pairwise"}\NormalTok{),}
-       \DataTypeTok{digits =} \DecValTok{4}\NormalTok{, }\DataTypeTok{low =} \StringTok{"steelblue"}\NormalTok{, }\DataTypeTok{mid =} \StringTok{"white"}\NormalTok{,}
-       \DataTypeTok{high =} \StringTok{"darkred"}\NormalTok{, }\DataTypeTok{midpoint =}\DecValTok{0}\NormalTok{,}
-       \DataTypeTok{geom =} \StringTok{"tile"}\NormalTok{, }\DataTypeTok{label =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{label_size=}\DecValTok{4}\NormalTok{, }\DataTypeTok{label_round =}\DecValTok{2}\NormalTok{, }\DataTypeTok{layout.exp =}\DecValTok{1}\NormalTok{,}
-       \DataTypeTok{label_alpha =} \OtherTok{FALSE}\NormalTok{,}\DataTypeTok{hjust =} \FloatTok{0.75}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/correlations-1} \end{center}
-
-\normalsize
-
-This tells us that almost no predictors are strongly correlated, except
-for pairs \textsf{CBS}-\textsf{CDS}, so we drop CDS from the analysis
-and avoid using them in the same model to avoid multicolinearity issues.
-These are just comments during the intervention period, which,
-unsurprisingly are also a good proxy for comments before and comments
-after.
-
-\section{Causal inference}\label{causal-inference}
+\begin{figure}
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/fig:linearShift-1} \end{center}
+\caption{Change in attacks vs intervention counts by treatment group, jittered with  linear smoothing. Change of range of aggression levels results in different linear smoothings.}
+\label{fig:linearShift}
+\end{figure}
+
+Let's now inspect correlations between the variables involved in the
+model (Figure \ref{fig:correlations}). Almost no predictors are strongly
+correlated, except for \textsf{CBS}, \textsf{CAS} and \textsf{CDS}. We
+are not interested in using \textsf{CAS} as a predictor, as it occurs
+\emph{after} the interventions, and we drop \textsf{CDS} from the
+analysis, generally avoiding using these variables in the same model to
+avoid statistical issues resulting from multicolinearity. In fact, it is
+no surprise that users' general activity in a period is a decent proxy
+for their general activity in other periods.
+
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/correlations-1} \end{center}
+\caption{Correlations between predictors used in the before-and-after analysis.}
+\label{fig:correlations}
+\end{figure}
+
+\hypertarget{causal-inference-and-variable-selection}{%
+\section{Causal inference and variable
+selection}\label{causal-inference-and-variable-selection}}
 
@@
 identify the causal effect of the interventions, we first need to think
-about the causal structure of the problem. Here's a plausible causal
-structure that we will be working with:
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{dag <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
-\StringTok{  dag\{}
-\StringTok{  CDS -> ADS -> IC  }
-\StringTok{               U [unobserved]   }
-\StringTok{               U -> CBS -> ABS  }
-\StringTok{               U -> ABS        }
-\StringTok{               U -> CDS -> ADS  }
-\StringTok{               U -> ADS         }
-\StringTok{               U -> CAS -> AAS    }
-\StringTok{               U -> AAS                        }
-\StringTok{               IC -> AAS        }
-\StringTok{               IC -> CAS        }
-\StringTok{               IT -> CAS        }
-\StringTok{               IT -> AAS}
-\StringTok{               CBS -> CDS -> CAS}
-\StringTok{               ABS -> ADS -> AAS}
-\StringTok{               \}"}\NormalTok{)}
-\KeywordTok{coordinates}\NormalTok{(dag)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## $x
-## AAS ABS ADS CAS CBS CDS  IC  IT   U 
-##  NA  NA  NA  NA  NA  NA  NA  NA  NA 
-## 
-## $y
-## AAS ABS ADS CAS CBS CDS  IC  IT   U 
-##  NA  NA  NA  NA  NA  NA  NA  NA  NA
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{coordinates}\NormalTok{( dag ) <-}\StringTok{ }\KeywordTok{list}\NormalTok{( }\DataTypeTok{x=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{CDS=}\DecValTok{1}\NormalTok{,}\DataTypeTok{ADS=}\DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{2}\NormalTok{,}
-                    \DataTypeTok{AAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{U =} \FloatTok{.5}\NormalTok{) ,}
-\DataTypeTok{y=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS =}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS =} \DecValTok{1}\NormalTok{,}\DataTypeTok{CDS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{ADS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{1}\NormalTok{, }
-    \DataTypeTok{IT =} \FloatTok{.3}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{.7}\NormalTok{, }\DataTypeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{) )}
-\KeywordTok{drawdag}\NormalTok{(dag)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag1-1} \end{center}
-
-\normalsize
-
+about the causal structure of the problem. A plausible causal structure
+that we will be working with is visualized in Figure \ref{fig:causal}.
 Comments during impact attacks during, which trigger interventions.
@@
 before, and also attacks before directly. Comments during (their impact
-on ADS is areadly included) impact attacks during during directly and
+on ADS is already included) impact attacks during during directly and
 comments after, which impact attacks after and attacks after directly.
@@
 
-We already know not to condition on CDS if we condition on CAS or CBS.
-What else? \textsf{IT} has no bacwkard paths, but \textsf{IC} does.
-Let's identify all paths from \textsf{IC} to \textsf{AAS}:
-
-\vspace{1mm} \footnotesize
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\KeywordTok{paths}\NormalTok{(dag, }\DataTypeTok{from =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{), }\DataTypeTok{to =} \StringTok{"AAS"}\NormalTok{)}
+\NormalTok{dag }\OtherTok{\textless{}{-}} \FunctionTok{dagitty}\NormalTok{(}\StringTok{"}
+\StringTok{  dag\{}
+\StringTok{  CDS {-}\textgreater{} ADS {-}\textgreater{} IC  }
+\StringTok{               U [unobserved]   }
+\StringTok{               U {-}\textgreater{} CBS {-}\textgreater{} ABS  }
+\StringTok{               U {-}\textgreater{} ABS        }
+\StringTok{               U {-}\textgreater{} CDS {-}\textgreater{} ADS  }
+\StringTok{               U {-}\textgreater{} ADS         }
+\StringTok{               U {-}\textgreater{} CAS {-}\textgreater{} AAS    }
+\StringTok{               U {-}\textgreater{} AAS                        }
+\StringTok{               IC {-}\textgreater{} AAS        }
+\StringTok{               IC {-}\textgreater{} CAS        }
+\StringTok{               IT {-}\textgreater{} CAS        }
+\StringTok{               IT {-}\textgreater{} AAS}
+\StringTok{               CBS {-}\textgreater{} CDS {-}\textgreater{} CAS}
+\StringTok{               ABS {-}\textgreater{} ADS {-}\textgreater{} AAS}
+\StringTok{               \}"}\NormalTok{)}
+\FunctionTok{coordinates}\NormalTok{(dag) }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{ABS =} \DecValTok{0}\NormalTok{, }\AttributeTok{CDS =} \DecValTok{1}\NormalTok{, }\AttributeTok{ADS =} \DecValTok{1}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{2}\NormalTok{,}
+    \AttributeTok{AAS =} \DecValTok{2}\NormalTok{, }\AttributeTok{IT =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{IC =} \FloatTok{1.5}\NormalTok{, }\AttributeTok{U =} \FloatTok{0.5}\NormalTok{), }\AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\AttributeTok{CBS =} \DecValTok{0}\NormalTok{, }\AttributeTok{ABS =} \DecValTok{1}\NormalTok{, }\AttributeTok{CDS =} \DecValTok{0}\NormalTok{,}
+    \AttributeTok{ADS =} \DecValTok{1}\NormalTok{, }\AttributeTok{CAS =} \DecValTok{0}\NormalTok{, }\AttributeTok{AAS =} \DecValTok{1}\NormalTok{, }\AttributeTok{IT =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{IC =} \FloatTok{0.7}\NormalTok{, }\AttributeTok{U =} \FloatTok{0.5}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\normalsize
+
+\begin{figure}[H]
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/unnamed-chunk-5-1} \end{center}
+\caption{A causal model used in the before-and-after analysis.}
+\label{fig:causal}
+\end{figure}
+
+We already know not to condition on CDS if we condition on CAS or CBS
+(multicolinearity). What else can we learn from the causal model?
+\textsf{IT} has no backdoor paths, but \textsf{IC} does, so we need to
+make sure these are closed to avoid including spurious correlations in
+our analysis. There are in fact 65 different paths from \textsf{IC} to
+\textsf{AAC}. Crucially, all backdoor paths go through \textsf{ADS},
+which then becomes either a fork or a pipe, so all backdoor paths can be
+closed by conditioning on \textsf{ADS}. Moreover there is only one
+directed indirect path, it goes through \textsf{CAS}, so we should not
+condition on \textsf{CAS} if we are to identify total causal effect of
+\textsf{IC} on attacks, including the impact mediated by its impact on
+comments (unless we care about the direct effect of \textsf{IC} and
+\textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
+line with the adjustment set identified algorithmically using by the
+\textsf{dagitty} package.
+
+The situation is somewhat different when it comes to evaluating the
+\emph{direct} effect of intervention. Then, we also need to block
+indirect causal paths from the intervention to the outcome. For such an
+evaluation we need to also condition on \textsf{CAS}, which is what we
+will do when we turn to the study of the direct effects of the
+interventions.
+
+\vspace{1mm}
+\footnotesize
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{paths}\NormalTok{(dag, }\AttributeTok{from =} \FunctionTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{), }\AttributeTok{to =} \StringTok{"AAS"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\normalsize
-
-Crucially, all backdoor paths go through \textsf{ADS}, which then
-becomes either a fork or a pipe, so all backdoor paths can be closed by
-conditioning on \textsf{ADS}. Moreover there is only one directed
-indirect path, it goes through \textsf{CAS}, so we should not condition
-on it if we are to identify causal effect on attacks mediated by impact
-on comments (unless we care about the direct effect of \textsf{IC} and
-\textsf{IT} on \textsf{AAS}, but that's a separate question). This is in
-line with the adjustment set identified algorithmically.
-
-\vspace{1mm} \footnotesize
-
 \begin{Shaded}
 \begin{Highlighting}[]
-\KeywordTok{adjustmentSets}\NormalTok{(dag, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AAS"}\NormalTok{, }\DataTypeTok{type =} \StringTok{"all"}\NormalTok{)}
+\FunctionTok{adjustmentSets}\NormalTok{(dag, }\AttributeTok{exposure =} \FunctionTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\AttributeTok{outcome =} \StringTok{"AAS"}\NormalTok{, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}
 \end{Highlighting}
@@
 In fact, we will be predicting the difference between attacks before and
-after, and the difference between comments, before and after. Let's add
-them to the dag to double-check our selection of variables.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{dag2 <-}\StringTok{ }\KeywordTok{dagitty}\NormalTok{(}\StringTok{"}
-\StringTok{  dag\{}
-\StringTok{                CDS -> ADS -> IC  }
-\StringTok{                U [unobserved]   }
-\StringTok{                U -> CBS -> ABS  }
-\StringTok{                U -> ABS        }
-\StringTok{                U -> CDS -> ADS  }
-\StringTok{                U -> ADS         }
-\StringTok{                U -> CAS -> AAS    }
-\StringTok{                U -> AAS                        }
-\StringTok{                IC -> AAS        }
-\StringTok{                IC -> CAS        }
-\StringTok{                IT -> CAS        }
-\StringTok{                IT -> AAS}
-\StringTok{                CBS -> CDS -> CAS}
-\StringTok{                ABS -> ADS -> AAS}
-\StringTok{                ABS -> AdiffS}
-\StringTok{                AAS -> AdiffS}
-\StringTok{                CBS -> CdiffS}
-\StringTok{                CAS -> CdiffS}
-\StringTok{                \}"}\NormalTok{)}
-\KeywordTok{coordinates}\NormalTok{( dag2 ) <-}\StringTok{ }\KeywordTok{list}\NormalTok{( }\DataTypeTok{x=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS=}\DecValTok{0}\NormalTok{,}\DataTypeTok{CDS=}\DecValTok{1}\NormalTok{,}\DataTypeTok{ADS=}\DecValTok{1}\NormalTok{,}
-    \DataTypeTok{CAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{U =} \FloatTok{.5}\NormalTok{, }\DataTypeTok{AdiffS=} \FloatTok{2.5}\NormalTok{, }\DataTypeTok{CdiffS =} \FloatTok{2.5}\NormalTok{) ,}
-\DataTypeTok{y=}\KeywordTok{c}\NormalTok{(}\DataTypeTok{CBS =}\DecValTok{0}\NormalTok{,}\DataTypeTok{ABS =} \DecValTok{1}\NormalTok{,}\DataTypeTok{CDS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{ADS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{CAS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{AAS =} \DecValTok{1}\NormalTok{, }\DataTypeTok{IT =} \FloatTok{.3}\NormalTok{, }\DataTypeTok{IC =} \FloatTok{.7}\NormalTok{, }\DataTypeTok{U =}\NormalTok{.}\DecValTok{5}\NormalTok{, }\DataTypeTok{CdiffS =} \FloatTok{-.2}\NormalTok{,  }\DataTypeTok{AdiffS =} \FloatTok{1.2}\NormalTok{) )}
-
-\KeywordTok{drawdag}\NormalTok{(dag2)}
-\KeywordTok{adjustmentSets}\NormalTok{(dag2, }\DataTypeTok{exposure =} \KeywordTok{c}\NormalTok{(}\StringTok{"IC"}\NormalTok{, }\StringTok{"IT"}\NormalTok{), }\DataTypeTok{outcome =} \StringTok{"AdiffS"}\NormalTok{, }\DataTypeTok{type =} \StringTok{"canonical"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## { ABS, ADS, CBS, CDS }
-\end{verbatim}
-
-\begin{center}\includegraphics[width=0.8\linewidth]{bayesianReport_files/figure-latex/dag2-1} \end{center}
-
+after, and the difference between comments, before and after, but the
+general points about the nodes involved apply also to defined nodes.
 Finding a maximal sensible set (canonical) of covariates suggests
-inlcuding \textsf{CDS} and \textsf{ABS}. As already discussed, we do not
+including \textsf{CDS} and \textsf{ABS}. As already discussed, we do not
 include \textsf{CDS} because of its strong correlation with
@@
 (\textsf{ADS}), but rather mainly because it is used to define the
-output variable. In such a set-up, of course that a model including
+output variable. In such a set-up, it is clear that a model including
 \textsf{ABS} would have better predictive power, but since a
@@
 
-It's open season for the other variables (and interactions between
-them), and our decision to include them in the model will be guided by
-information-theoretic criteria of predictive power.
-
-\section{Bayesian models, priors and
-diagnostics}\label{bayesian-models-priors-and-diagnostics}
-
-We will focus on a class of additive models where the outcome variable
-is normally distributed around the predicted mean, which is a linear
-function of predictors (possibly with some interactions). To spoil the
-story, we will end up using a model, whose specification is as follows:
+Otherwise, it's open season for the other variables and interactions
+between them, and our decision to include or exclude them in the model
+will be guided by information-theoretic criteria of predictive power.
+
+\hypertarget{before-and-after-analysis-bayesian-model-building}{%
+\section{Before-and-after analysis: bayesian model
+building}\label{before-and-after-analysis-bayesian-model-building}}
+
+We build and compared multiple additive models where the outcome
+variable is normally distributed around the predicted mean, which is a
+linear function of predictors (possibly with interactions). Bayesian
+information criteria (WAIC)\footnote{
+Here's a more detailed explanation of the model comparison method we used, uninterested reader is invited to skip forward. Let  $y$ be the observations and $\Theta$  a posterior distribution.
+First, log-pointwise-predictive-density is defined by:
+\begin{align*}
+\mathsf{lppd}(y, \Theta) & = \sum_i log\frac{1}{S}\sum_s p (y_i\vert \Theta_s)
+\end{align*}
+\noindent where $S$ is the number of samples in the posterior, and $\Theta_s$ 
+is the $s$-th combination of sampled parameter values in the posterior distribution. That is, 
+for each observation and each combination of 
+parameters in the posterior we first compute its density, then 
+we take the average density of that observation over all combinations of parameters in the posterior,
+and  then take the logarithm.
+Finally, we sum these values up for all the observations.
+Crucially, when comparing posterior distributions with respect to the same dataset, \textsf{lppd}s are proportional
+ to unbiased estimates of their divergence from the real distribution (note that it is \emph{only} 
+ proportional, and for this reason can be used for comparison of distributions 
+ only and makes no intuitive sense on its own).  However, \textsf{lppd} always improves
+  as the model gets more complex, so for model comparison it makes more sense to use 
+ the Widely Applicable Information Criterion (WAIC), which is an approximation of the out-of-sample deviance that converges to the cross-validation approximation in a large sample. It  is defined as
+ the log-posterior-predictive-density with an additional
+  penalty proportional to the variance in the
+  posterior predictions:
+  \begin{align*}
+\mathsf{WAIC(y, \Theta)} & = -2 (\mathsf{lppd} - \overbrace{\sum_i var_\theta \mathsf{log} p (y_i \vert \theta)}^{\mathsf{penalty}})
+  \end{align*}
+\noindent  Thus to construct the penalty, we calculate the variance in log-probabilities for each observation and sum them up.
+Because of the analogy to Akaike's criterion, the penalty is sometimes called the effective number of parameters, $p_{\mathsf{WAIC}}$.
+How does WAIC compare to other information criteria?
+AIC uses MAP estimates instead of the posterior and requires that priors be flat or overwhelmed by the likelihood, and assumes that the posterior distribution is approximately multivariate Gaussian and the sample size is  much greater  than the number of parameters used in the model.
+Bayesian Information Criterion (BIC) also requires flat priors and uses MAP estimates.
+WAIC does not make these assumptions, and provides almost exactly the same results as AIC, when AIC’s assumptions are met.}
+applied to a wide selection of predictors lead to the model, whose
+specification is as follows (we also selected regularizing prior
+parameters using prior predictive checks to avoid unreasonably narrow
+overall prior distributions):
+
+\vspace{-2mm}
 
@@
 group-specific coefficient for \textsf{IC}, interaction coefficient for
-\textsf{ADS} and \textsf{IC}, and group-specific coeffient for
-\textsf{CBS}. This is plausible prima facie which group a user belongs
-to might have impact on how attacks during the treatment is related to
-attacks after, the role of the intervention count, and the role of
-comments before. Moreover, the levels of agressive behavior displayed by
-the user during treament might have impact on the role played by the
-intervention count. Later on we will see that there are
-information-theoretic reasons to include these interactions.
-
-Now for the priors. One might be suspicious of \(\sigma =.3\) we
-employed and suggest using standard normal distributions with
-\(\sigma = 1\) instead. However, a quick prior predictive check shows
-that this results in insanely wide priors that are competely
-unrealistic. (For computational reasons, instead of running the
-simulations, we load pre-compiled models, but we include the code used
-to build them).
-
-\vspace{1mm} \footnotesize
+\textsf{ADS} and \textsf{IC}, and group-specific coefficient for
+\textsf{CBS}. This is plausible \emph{prima facie} which group a user
+belongs to might have impact on how attacks during the treatment is
+related to attacks after, the role of the intervention count, and the
+role of comments before. Moreover, the levels of aggressive behavior
+displayed by the user during treatment might have impact on the role
+played by the intervention count.
+
+\vspace{1mm}
+\footnotesize
 
@@
 \begin{Highlighting}[]
-\CommentTok{# building model with sd=1}
-\CommentTok{# InteractionsModelDiffSD1 <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+}
-\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,1),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bADSIC ~ dnorm(0,1),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,1),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,1),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ), }
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-\CommentTok{# }
-\CommentTok{# saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")}
-\NormalTok{InteractionsModelDiffSD1 <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiffSD1.rds"}\NormalTok{)}
-
-\CommentTok{#now model with prior sd = .3}
-\CommentTok{# InteractionsModelDiff <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +}
-\CommentTok{#     bADSIC * ADS * IC+ bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,0.3),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bADSIC ~ dnorm(0,.3),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ), }
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-
-\CommentTok{#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")}
-
-\NormalTok{InteractionsModelDiff <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/InteractionsModelDiff.rds"}\NormalTok{)}
-
-\NormalTok{##prior predictive checks sd =1}
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-
-\NormalTok{priorGroupsSD1 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{,}
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{0}\OperatorTok{:}\DecValTok{20}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## recompiling to avoid crashing R session
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{mu.mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{, mean )}
-\NormalTok{mu.HPDI <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI )))}
-\NormalTok{priorDF <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data, mu.mean, mu.HPDI)}
-\NormalTok{priorDF}\OperatorTok{$}\NormalTok{groupID <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(groupID)}
-\KeywordTok{levels}\NormalTok{(priorDF}\OperatorTok{$}\NormalTok{groupID) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{)}
-\KeywordTok{colnames}\NormalTok{(priorDF)[}\DecValTok{2}\NormalTok{]<-}\StringTok{ "group"}
-
-\NormalTok{priorICSD1  <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(priorDF, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y  =}\NormalTok{ mu.mean,  }\DataTypeTok{fill =}\NormalTok{ group))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_line}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_ribbon}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ X.}\FloatTok{0.89}\NormalTok{, }\DataTypeTok{ymax =}\NormalTok{ X0.}\FloatTok{89.}\NormalTok{), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors for AAS vs IC"}\NormalTok{,}
-      \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, sd = 1)"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"interventions"}\NormalTok{)}
-
-\NormalTok{priorJoint1 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupsSD1,priorICSD1, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
-\NormalTok{priorJoint1Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint1, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=1 are insanely wide"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+\CommentTok{\# building model with sd=1}
+\NormalTok{InteractionsModelDiffSD1 }\OtherTok{\textless{}{-}} \FunctionTok{ulam}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}
+\NormalTok{    bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ),}
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{ )}
+
+\CommentTok{\#saveRDS(InteractionsModelDiffSD1, file = "models/InteractionsModelDiffSD1.rds")}
+\NormalTok{InteractionsModelDiffSD1 }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/InteractionsModelDiffSD1.rds"}\NormalTok{)}
+
+\CommentTok{\#now model with prior sd = .3}
+\NormalTok{InteractionsModelDiff }\OtherTok{\textless{}{-}} \FunctionTok{ulam}\NormalTok{(}
+  \FunctionTok{alist}\NormalTok{(}
+\NormalTok{    AdiffS }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{( mu, sigma ),}
+\NormalTok{    mu }\OtherTok{\textless{}{-}}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ bADS[groupID] }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{+}\NormalTok{  bIT[groupID] }\SpecialCharTok{+}\NormalTok{ bIC[groupID] }\SpecialCharTok{*}\NormalTok{ IC }\SpecialCharTok{+}
+\NormalTok{    bADSIC }\SpecialCharTok{*}\NormalTok{ ADS }\SpecialCharTok{*}\NormalTok{ IC}\SpecialCharTok{+}\NormalTok{ bCBS[groupID] }\SpecialCharTok{*}\NormalTok{CBS,}
+\NormalTok{    a }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
+\NormalTok{    bADS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bADSIC }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bCBS[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIT[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    bIC[groupID] }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
+\NormalTok{    sigma  }\SpecialCharTok{\textasciitilde{}} \FunctionTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
+\NormalTok{  ),}
+  \AttributeTok{data =}\NormalTok{ summaries}
+\NormalTok{)}
+
+\CommentTok{\#saveRDS(InteractionsModelDiff, file = "models/InteractionsModelDiff.rds")}
+
+\NormalTok{InteractionsModelDiff }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =} \StringTok{"models/InteractionsModelDiff.rds"}\NormalTok{)}
+
+\CommentTok{\#prior predictive checks sd =1}
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data )}
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+
+\NormalTok{priorGroupsSD1 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{,}
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{0}\SpecialCharTok{:}\DecValTok{20}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{(InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data )}
+\NormalTok{mu.mean }\OtherTok{\textless{}{-}} \FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{, mean )}
+\NormalTok{mu.HPDI }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{t}\NormalTok{(}\FunctionTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI )))}
+\NormalTok{priorDF }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(data, mu.mean, mu.HPDI)}
+\NormalTok{priorDF}\SpecialCharTok{$}\NormalTok{groupID }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(groupID)}
+\FunctionTok{levels}\NormalTok{(priorDF}\SpecialCharTok{$}\NormalTok{groupID) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{)}
+\FunctionTok{colnames}\NormalTok{(priorDF)[}\DecValTok{2}\NormalTok{]}\OtherTok{\textless{}{-}} \StringTok{"group"}
+
+\NormalTok{priorICSD1  }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(priorDF, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ IC, }\AttributeTok{y  =}\NormalTok{ mu.mean,  }\AttributeTok{fill =}\NormalTok{ group))}\SpecialCharTok{+}
+  \FunctionTok{geom\_line}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{geom\_ribbon}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{ymin =}\NormalTok{ X.}\FloatTok{0.89}\NormalTok{, }\AttributeTok{ymax =}\NormalTok{ X0.}\FloatTok{89.}\NormalTok{), }\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors for AAS vs IC"}\NormalTok{,}
+      \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{"interventions"}\NormalTok{)}
+
+\NormalTok{priorJoint1 }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(priorGroupsSD1,priorICSD1, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{)}
+\NormalTok{priorJoint1Titled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(priorJoint1,}
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=1 are insanely wide"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{14}\NormalTok{))}
 \NormalTok{priorJoint1Titled}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-6-1} \end{center}
-
-\normalsize
-
-Some experimentation leads to the value of \(\sigma =.3\), which leads
-to the following priors:
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{#prior predictive check sd =.3}
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiff, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(muLong)}
-
-\NormalTok{priorGroupSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors  by group"}\NormalTok{, }
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = .3)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standarized)"}\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{CBS <-}\StringTok{ }\DecValTok{0}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5}  \CommentTok{#mean for interventions in treatment}
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{prior <-}\StringTok{ }\KeywordTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\DataTypeTok{n =} \FloatTok{1e4}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\DataTypeTok{post=}\NormalTok{prior , }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\KeywordTok{head}\NormalTok{(muLong)}
-
-\NormalTok{priorICSD03 <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{, }
-  \DataTypeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
-
-\NormalTok{priorJoint03 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(priorGroupSD03,priorICSD03, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{) }
-\NormalTok{priorJoint03Titled <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(priorJoint03, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=.3 seem sensible"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{14}\NormalTok{))}
+
+\CommentTok{\#Some experimentation leads to the value of $\textbackslash{}sigma =.3$, which leads to the following priors:}
+
+\NormalTok{prior predictive check sd }\OtherTok{=}\NormalTok{.}\DecValTok{3}
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiff, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{(InteractionsModelDiff , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorGroupSD03 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}\FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors  by group"}\NormalTok{, }
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = .3)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standarized)"}\NormalTok{)}
+
+\NormalTok{ADS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{CBS }\OtherTok{\textless{}{-}} \DecValTok{0}
+\NormalTok{groupID }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{3}
+\NormalTok{IC }\OtherTok{\textless{}{-}} \DecValTok{5}  \CommentTok{\#mean for interventions in treatment}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{ADS =}\NormalTok{ ADS,}\AttributeTok{groupID =}\NormalTok{ groupID, }\AttributeTok{CBS =}\NormalTok{ CBS, }\AttributeTok{IC =}\NormalTok{  IC)}
+\NormalTok{prior }\OtherTok{\textless{}{-}} \FunctionTok{extract.prior}\NormalTok{(InteractionsModelDiffSD1, }\AttributeTok{n =} \FloatTok{1e4}\NormalTok{)}
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{link}\NormalTok{( InteractionsModelDiffSD1 , }\AttributeTok{post=}\NormalTok{prior , }\AttributeTok{data=}\NormalTok{data ) }
+\FunctionTok{colnames}\NormalTok{(mu) }\OtherTok{\textless{}{-}} \FunctionTok{levels}\NormalTok{(summaries}\SpecialCharTok{$}\NormalTok{group)}
+\NormalTok{muLong }\OtherTok{\textless{}{-}} \FunctionTok{melt}\NormalTok{(mu)}
+\FunctionTok{colnames}\NormalTok{(muLong) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
+\FunctionTok{head}\NormalTok{(muLong)}
+
+\NormalTok{priorICSD03 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(muLong)}\SpecialCharTok{+}
+  \FunctionTok{geom\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ group, }\AttributeTok{y =}\NormalTok{ AdiffS))}\SpecialCharTok{+}
+  \FunctionTok{theme\_tufte}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Simulated priors by group"}\NormalTok{, }
+  \AttributeTok{subtitle =} \StringTok{"(at ADS = CBS = 0, IC at mean = 5, sd = 1)"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ylab}\NormalTok{(}\StringTok{"change in attacks (standardized)"}\NormalTok{)}
+
+\NormalTok{priorJoint03 }\OtherTok{\textless{}{-}} \FunctionTok{ggarrange}\NormalTok{(priorGroupSD03,priorICSD03, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{) }
+\NormalTok{priorJoint03Titled }\OtherTok{\textless{}{-}} \FunctionTok{annotate\_figure}\NormalTok{(priorJoint03, }
+  \AttributeTok{top =} \FunctionTok{text\_grob}\NormalTok{(}\StringTok{"Predictive priors with sd=.3 seem sensible"}\NormalTok{,}
+                  \AttributeTok{size =} \DecValTok{14}\NormalTok{))}
 \NormalTok{priorJoint03Titled}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-7-1} \end{center}
-
 \normalsize
 
-Now, some model diagnostics before we move on. What we are witnessing is
-(1) stationarity (the chains stay mostly in the most probable regions),
-(2) good mixing (they explore a range of options in the beginning), and
-(3) convergence (they stabilize as they progress).
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{traceplot}\NormalTok{( InteractionsModelDiff )}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-8-1} \end{center}
-
-\normalsize
-
-Finally, let's inspect the distribution of residuals. That is, we
-calculate all predictions, their distance from the actual values, and
-inspect the distribution of the distances:
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{(InteractionsModelDiff)}
-\NormalTok{mu_mean <-}\StringTok{ }\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , mean )}
-\NormalTok{mu_resid <-}\StringTok{ }\NormalTok{summaries}\OperatorTok{$}\NormalTok{AdiffS }\OperatorTok{-}\StringTok{ }\NormalTok{mu_mean}
-\KeywordTok{ggplot}\NormalTok{()}\OperatorTok{+}\KeywordTok{geom_density}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ mu_resid))}\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"Residuals are approximately normally distributed"}\NormalTok{)}\OperatorTok{+}\KeywordTok{xlab}\NormalTok{(}\StringTok{"residuals"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-9-1} \end{center}
-
-\normalsize
-
-\section{Model selection}\label{model-selection}
-
-How did we get to this fairly complicated model though? Once preliminary
-causal considerations guided our restrictions on variable selection, we
-proceed by building models of increasing complexity, and comparing them
-in terms of Widely Acceptable Information Criterion. The models differ
-mostly in the underlying linear formulae. For computational ease we will
-here use quadratic approximations, while in the final analysis we will
-deploy Hamiltionian Monte Carlo. The names are meant to decode the model
-structure: the predictors are listed before dashes, whereas interactions
-are listed after dashes.
-
-\begin{align}
-\tag{Null}  \mu_i & = \alpha\\
-\tag{ADS}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS}\\
-\tag{ADSIC}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
-\tag{IT}  \mu_i & = \beta_{\mathsf{group}[i]} \\
-\tag{ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]}\\
-\tag{ADSITIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
-\tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITIC-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
- \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
-\tag{ADSITIC-ADSIT-ITIC-ADSIC}   \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times \mathsf{ADS} + \beta_{\mathsf{group}[i]} +  
-\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ \nonumber & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
-\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
- \mathsf{ADS}  + \beta_{\mathsf{group}[i]} +   \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC} + \\ & \nonumber  + \beta_{\mathsf{CBS}} \times \mathsf{CBS} +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}  \\
-\tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
- & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber\\
- \tag{tooFAr} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
- & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} + \beta_{\mathsf{CBSIC}}\times
- \mathsf{CBS} \times \mathsf{IC}\end{align}
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{null <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries  }
-\NormalTok{)}
-
-\NormalTok{ADS <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS}\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{IT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{  }\NormalTok{bIT[groupID] ,}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID],}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIC_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSIT_ADSIT <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] ,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-    \CommentTok{#bADSIC ~ dnorm(0,.5),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-    \CommentTok{#bIC ~ dnorm(0,.5),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITIC_ADSIT_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{ADSITICCBS_ITIC_ADSIC <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS }\OperatorTok{*}\NormalTok{CBS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{Final <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS,}
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-
-\NormalTok{tooFar <-}\StringTok{ }\KeywordTok{quap}\NormalTok{(}
-  \KeywordTok{alist}\NormalTok{(}
-\NormalTok{    AdiffS }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{( mu, sigma ),}
-\NormalTok{    mu <-}\StringTok{ }\NormalTok{a }\OperatorTok{+}\StringTok{ }\NormalTok{bADS[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{+}\StringTok{  }\NormalTok{bIT[groupID] }\OperatorTok{+}\StringTok{ }\NormalTok{bIC[groupID] }\OperatorTok{*}\StringTok{ }\NormalTok{IC }\OperatorTok{+}\StringTok{ }
-\StringTok{      }\NormalTok{bADSIC }\OperatorTok{*}\StringTok{ }\NormalTok{ADS }\OperatorTok{*}\StringTok{ }\NormalTok{IC}\OperatorTok{+}\StringTok{ }\NormalTok{bCBS[groupID] }\OperatorTok{*}\NormalTok{CBS }\OperatorTok{+}\StringTok{ }\NormalTok{bCBSIC }\OperatorTok{*}\StringTok{ }\NormalTok{CBS }\OperatorTok{*}\StringTok{ }\NormalTok{IC, }
-\NormalTok{    a }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{ (}\DecValTok{0}\NormalTok{,}\FloatTok{0.3}\NormalTok{),}
-\NormalTok{    bADS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bADSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bCBS[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIT[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{    bIC[groupID] }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{,.}\DecValTok{3}\NormalTok{),}
-\NormalTok{     bCBSIC }\OperatorTok{~}\StringTok{ }\KeywordTok{dnorm}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{.3}\NormalTok{),}
-\NormalTok{    sigma  }\OperatorTok{~}\StringTok{ }\KeywordTok{dexp}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\NormalTok{  ), }
-  \DataTypeTok{data =}\NormalTok{ summaries}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{comparison<-}\StringTok{ }\KeywordTok{compare}\NormalTok{(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,}
-\NormalTok{                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,}
-\NormalTok{                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)}
-\KeywordTok{mykable}\NormalTok{(}\KeywordTok{data.frame}\NormalTok{(comparison )) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}
-\centering\begingroup\fontsize{9}{11}\selectfont
-
-\begin{tabular}{lrrrrrr}
-\toprule
-  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
-\midrule
-\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.641} & \cellcolor{gray!6}{89.47387} & \cellcolor{gray!6}{0.000000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.85809} & \cellcolor{gray!6}{0.8345169}\\
-tooFar & 1189.123 & 90.35400 & 4.481669 & 2.882584 & 29.76051 & 0.0887673\\
-\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1189.414} & \cellcolor{gray!6}{87.19709} & \cellcolor{gray!6}{4.773490} & \cellcolor{gray!6}{5.762571} & \cellcolor{gray!6}{25.62296} & \cellcolor{gray!6}{0.0767158}\\
-null & 1344.835 & 144.95033 & 160.193855 & 132.894118 & 17.16957 & 0.0000000\\
-\cellcolor{gray!6}{IT} & \cellcolor{gray!6}{1345.879} & \cellcolor{gray!6}{144.64185} & \cellcolor{gray!6}{161.237934} & \cellcolor{gray!6}{132.478842} & \cellcolor{gray!6}{19.27433} & \cellcolor{gray!6}{0.0000000}\\
-\addlinespace
-ADSIT & 1348.714 & 142.29377 & 164.072877 & 130.485213 & 23.06652 & 0.0000000\\
-\cellcolor{gray!6}{ADS} & \cellcolor{gray!6}{1349.706} & \cellcolor{gray!6}{145.13624} & \cellcolor{gray!6}{165.065051} & \cellcolor{gray!6}{133.323101} & \cellcolor{gray!6}{23.10634} & \cellcolor{gray!6}{0.0000000}\\
-ADSIT\_ADSIT & 1350.941 & 153.88118 & 166.300056 & 139.579270 & 32.04695 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1352.972} & \cellcolor{gray!6}{154.55405} & \cellcolor{gray!6}{168.331385} & \cellcolor{gray!6}{140.054704} & \cellcolor{gray!6}{30.65579} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC & 1353.603 & 147.38084 & 168.962571 & 134.581071 & 28.54365 & 0.0000000\\
-\addlinespace
-\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1355.210} & \cellcolor{gray!6}{148.15271} & \cellcolor{gray!6}{170.568848} & \cellcolor{gray!6}{135.609996} & \cellcolor{gray!6}{27.22326} & \cellcolor{gray!6}{0.0000000}\\
-ADSITIC\_ADSIC\_ADSIT & 1355.353 & 156.53444 & 170.712149 & 142.268677 & 33.80858 & 0.0000000\\
-\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.442} & \cellcolor{gray!6}{155.55820} & \cellcolor{gray!6}{170.800602} & \cellcolor{gray!6}{140.950680} & \cellcolor{gray!6}{34.03861} & \cellcolor{gray!6}{0.0000000}\\
-\bottomrule
-\end{tabular}
-\endgroup{}
-\end{table}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{plot}\NormalTok{(comparison)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-11-1} \end{center}
-
-\normalsize
-
-The three models that stand out differ in including \(\mathsf{CBS}\) as
-a predictor. Moreover the final model includes an interaction between
-treatment group and \(\mathsf{CBS}\). Adding a further interaction
-between \(\mathsf{CBS}\) and \(\mathsf{IC}\) takes us too far.
-\(WAIC\)-based weighing assigns the weight of \(83\%\) to the final
-model, and the standard errors for the difference in WAIC for the top
-three models is fairly low, so we will employ the top model
-(\(\mathsf{Final}\)) in further analyses.
-
-\section{Inspecting the model and effect
-sizes}\label{inspecting-the-model-and-effect-sizes}
-
-We start by using the \textsf{Final} model formula to build a model,
-this time using Hamiltionian Monte Carlo. We leave the code commented
-out and load a pre-compiled model for computational convenience
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# FinalHMC <- ulam(}
-\CommentTok{#   alist(}
-\CommentTok{#     AdiffS ~ dnorm( mu, sigma ),}
-\CommentTok{#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +}
-\CommentTok{#     bIC[groupID] * IC + bADSIC * ADS * IC+}
-\CommentTok{#     bCBS[groupID] *CBS,}
-\CommentTok{#     a ~ dnorm (0,0.3),}
-\CommentTok{#     bADS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bADSIC ~ dnorm(0,.3),}
-\CommentTok{#     bCBS[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIT[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     bIC[groupID] ~ dnorm(0,.3),}
-\CommentTok{#     sigma  ~ dexp(1)}
-\CommentTok{#   ),}
-\CommentTok{#   data = summaries}
-\CommentTok{# )}
-\CommentTok{# saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
-
-\CommentTok{#saveRDS(FinalHMC, file = "models/FinalHMC.rds")}
-
-\NormalTok{FinalHMC <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\DataTypeTok{file =} \StringTok{"models/FinalHMC.rds"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\normalsize
-First, let's take a look at the best model coefficients.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}
-
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.0414089\\
-\hline
-0.1979211\\
-\hline
-0.2484756\\
-\hline
--0.1097667\\
-\hline
--0.0042060\\
-\hline
--0.5142899\\
-\hline
--0.0919148\\
-\hline
--0.5302840\\
-\hline
--0.0212337\\
-\hline
-0.1482970\\
-\hline
--0.0686005\\
-\hline
--0.0037630\\
-\hline
--0.0117801\\
-\hline
-0.0118155\\
-\hline
-0.7945882\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.1562753\\
-\hline
-0.0568494\\
-\hline
-0.1546028\\
-\hline
-0.1014546\\
-\hline
-0.0051643\\
-\hline
-0.0414267\\
-\hline
-0.1245614\\
-\hline
-0.1088835\\
-\hline
-0.1630179\\
-\hline
-0.1857528\\
-\hline
-0.1776783\\
-\hline
-0.3161707\\
-\hline
-0.0256771\\
-\hline
-0.0185521\\
-\hline
-0.0277774\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
--0.2037740\\
-\hline
-0.1086423\\
-\hline
-0.0036955\\
-\hline
--0.2678764\\
-\hline
--0.0122338\\
-\hline
--0.5776731\\
-\hline
--0.2965873\\
-\hline
--0.7023272\\
-\hline
--0.2603815\\
-\hline
--0.1246834\\
-\hline
--0.3448157\\
-\hline
--0.5084313\\
-\hline
--0.0529960\\
-\hline
--0.0192521\\
-\hline
-0.7535960\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.2796946\\
-\hline
-0.2907669\\
-\hline
-0.4942282\\
-\hline
-0.0628934\\
-\hline
-0.0040408\\
-\hline
--0.4463925\\
-\hline
-0.1059034\\
-\hline
--0.3593766\\
-\hline
-0.2295494\\
-\hline
-0.4367149\\
-\hline
-0.2099344\\
-\hline
-0.4981378\\
-\hline
-0.0290304\\
-\hline
-0.0412303\\
-\hline
-0.8434971\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-228.1593\\
-\hline
-768.4216\\
-\hline
-526.1494\\
-\hline
-418.0876\\
-\hline
-361.1195\\
-\hline
-722.3116\\
-\hline
-671.6673\\
-\hline
-823.7157\\
-\hline
-219.0190\\
-\hline
-304.7859\\
-\hline
-295.3412\\
-\hline
-829.2326\\
-\hline
-488.1809\\
-\hline
-612.3810\\
-\hline
-693.5845\\
-\hline
-\end{tabular}
-\centering
-\begin{tabular}[t]{r}
-\hline
-x\\
-\hline
-0.9980513\\
-\hline
-1.0013137\\
-\hline
-0.9995921\\
-\hline
-0.9980791\\
-\hline
-0.9983620\\
-\hline
-0.9991926\\
-\hline
-0.9998084\\
-\hline
-0.9980583\\
-\hline
-0.9980137\\
-\hline
-0.9980345\\
-\hline
-0.9980482\\
-\hline
-1.0011451\\
-\hline
-0.9994090\\
-\hline
-0.9986804\\
-\hline
-0.9982674\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{plot}\NormalTok{(}\KeywordTok{precis}\NormalTok{(FinalHMC, }\DataTypeTok{depth =} \DecValTok{2}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-13-1} \end{center}
-
-\normalsize
-
-These, however, are notoriously hard to interpret in models with
-interactions. For this reason, it is better to plot predicted effects
-for various combinations of predictors.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visGroup <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{ (model, ADS, CBS, }\DataTypeTok{xmin =}\DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-3}\NormalTok{)}
-\NormalTok{\{}
-\NormalTok{groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{IC <-}\StringTok{ }\DecValTok{5} 
-\NormalTok{data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}\DataTypeTok{ADS =}\NormalTok{ ADS,}\DataTypeTok{groupID =}\NormalTok{ groupID, }\DataTypeTok{CBS =}\NormalTok{ CBS, }\DataTypeTok{IC =}\NormalTok{  IC)}
-\NormalTok{posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\KeywordTok{colnames}\NormalTok{(mu) <-}\StringTok{ }\KeywordTok{levels}\NormalTok{(summaries}\OperatorTok{$}\NormalTok{group)}
-\NormalTok{muLong <-}\StringTok{ }\KeywordTok{melt}\NormalTok{(mu)}
-\KeywordTok{colnames}\NormalTok{(muLong) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"group"}\NormalTok{, }\StringTok{"AdiffS"}\NormalTok{)}
-\NormalTok{means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{2}\NormalTok{)}
-\NormalTok{mu_HPDI <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{2}\NormalTok{)}
-\NormalTok{means <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(means)}
-\NormalTok{means}\OperatorTok{$}\NormalTok{group <-}\StringTok{ }\KeywordTok{rownames}\NormalTok{(means)}
-\KeywordTok{rownames}\NormalTok{(means) <-}\StringTok{ }\OtherTok{NULL}
-\NormalTok{meansDisp <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(mu_HPDI)))}
-\NormalTok{meansDisp <-}\StringTok{ }\NormalTok{meansDisp[,}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{4}\NormalTok{)]}
-
-\NormalTok{plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS,  }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
-\CommentTok{#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
-\KeywordTok{return}\NormalTok{(plot)}
-\NormalTok{\}}
-
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}
-\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
-
-\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
-\NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}
-
-\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
-\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
-\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{ )}
-
-\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{) , visGroupA2C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),visGroupA2C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{), }
-\NormalTok{          visGroupA0C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
-\NormalTok{          visGroupA2C_}\DecValTok{2}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C0}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C2}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visGroupJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-4,4), IC at the rounded mean = 5)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visGroupJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint2, }
-  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted change in attacks by activity type and treatment groups (standardized)"}\NormalTok{,}
-                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-
-\NormalTok{visGroupJoint3 }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-14-1} \end{center}
-
-\normalsize
-
-To gain more clarity, let's look at predicted contrasts, here understood
-as distances from the control group mean, by activity types, first
-versus CBS, then versus ADS.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsCBS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =}\NormalTok{ ADS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{,}
-                            \DataTypeTok{CBS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
-\NormalTok{  \{}
-\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(ADS, groupID, IC , CBS)}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-  \KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrast <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrast)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrast <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
-\NormalTok{  cLow <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
-\NormalTok{  cHigh <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
-\NormalTok{  \}}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
-\NormalTok{  \}}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrast}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
-\NormalTok{  \}}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
-                          \KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-
-\NormalTok{  visContrastTreatment <-}\StringTok{ }\NormalTok{visContrast[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
-        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{, }
-        \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{,}
-        \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{))}\OperatorTok{+}
-\StringTok{          }\KeywordTok{theme_tufte}\NormalTok{())}
-\NormalTok{\}}
-
-\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
-\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\NormalTok{removeY,}
-        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{)}\OperatorTok{+}
-\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
-\StringTok{        }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visContrastCBSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint, }
-      \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
-                                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastCBSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint2, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. CBS  (standardized)"}\NormalTok{,}
-                                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-
-\NormalTok{visContrastCBSJoint3}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
-
-\normalsize
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsADS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{, }
-                            \DataTypeTok{ADS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
-\NormalTok{\{}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrastADS <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrastADS)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrastADS <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastADS))}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
-\NormalTok{  \}}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{    contrastADS[i] <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
-\NormalTok{  \}}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastADS}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{means}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{    visContrastADS}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
-\NormalTok{  \}}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastADS}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrastADS}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
-                             \KeywordTok{nrow}\NormalTok{(visContrastADS)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-\NormalTok{  visContrastTreatmentADS <-}\StringTok{ }\NormalTok{visContrastADS[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentADS, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ ADS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.05}\NormalTok{,}
-                  \DataTypeTok{fatten =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{, }
-                  \DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width =} \FloatTok{.8}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
-\NormalTok{\}}
-
-\NormalTok{visContrastADSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{                                   }\NormalTok{removeY,}
-                                 \KeywordTok{visContrastsADS}\NormalTok{(FinalHMC,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}
-                                 \OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}
-\StringTok{                                   }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
-\StringTok{                                   }\NormalTok{removeY, }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}
-
-\NormalTok{visContrastADSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
-                                                        \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastADSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastADSJoint2, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. ADS (standardized)"}\NormalTok{,}
-                                                        \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-
-\NormalTok{visContrastADSJoint3}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-16-1} \end{center}
-
-\normalsize
-
-Now, let's inspect the impact of intervention counts by treatment type
-by looking at contrasts (distances from the control group mean) with
-89\% HPDIs by IC.
-
-\vspace{1mm} \footnotesize
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{visContrastsIC <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{CBS =}\NormalTok{ CBS , }\DataTypeTok{IC =}  \KeywordTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{30}\NormalTok{,}\DataTypeTok{by =} \DecValTok{1}\NormalTok{), }\DataTypeTok{ADS =}\NormalTok{ ADS)}
-\NormalTok{\{}
-\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
-\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(CBS, groupID, IC , ADS)}
-\NormalTok{  data}
-  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"CBS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"ADS"}\NormalTok{)}
-\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
-\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
-\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
-\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
-\NormalTok{  visContrastIC <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}
-
-\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
-\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
-\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}
-
-  \KeywordTok{colnames}\NormalTok{(visContrastIC)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
-\NormalTok{  contrastIC <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrastIC))}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
-\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
-\NormalTok{  \}}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
-\NormalTok{    contrastIC[i] <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
-\NormalTok{  \}}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrastIC}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{means}
-  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
-\NormalTok{    visContrastIC}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
-\NormalTok{  \}}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrastIC}\OperatorTok{$}\NormalTok{shift}
-
-\NormalTok{  visContrastIC}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }\KeywordTok{nrow}\NormalTok{(visContrastIC)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
-\NormalTok{  visContrastTreatmentIC <-}\StringTok{ }\NormalTok{visContrastIC[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}
-
-  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatmentIC, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ IC, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
-\StringTok{    }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{)}\OperatorTok{+}
-\StringTok{    }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{)) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
-\NormalTok{\}}
-
-\NormalTok{visContrastsICJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
-\StringTok{               }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.3}\NormalTok{, }\FloatTok{0.9}\NormalTok{),}
-                     \DataTypeTok{legend.key.size =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.key.height =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.key.width =} \KeywordTok{unit}\NormalTok{(.}\DecValTok{3}\NormalTok{, }\StringTok{'cm'}\NormalTok{),}
-                     \DataTypeTok{legend.title=} \KeywordTok{element_blank}\NormalTok{())}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),  }
-\KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{)}\OperatorTok{+}
-\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
-    \KeywordTok{visContrastsIC}\NormalTok{(}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{, }\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{), }
-\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}
-\NormalTok{)}
-
-\NormalTok{visContrastsICJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint, }
-\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-3,3))"}\NormalTok{, }
-                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
-\NormalTok{visContrastsICJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastsICJoint2, }
- \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. IC (standardized)"}\NormalTok{,}
-                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}
-
-\NormalTok{visContrastsICJoint3}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-17-1} \end{center}
-
-\normalsize
-
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\vspace{-3mm}
+Now, some model diagnostics before we move on (Figure
+\ref{fig:traceplot}). What we are witnessing is (1) stationarity (the
+chains stay mostly in the most probable regions), (2) good mixing (they
+explore a range of options in the beginning), and (3) convergence (they
+stabilize as they progress). We also need to inspect the distribution of
+residuals, expecting them to be more or less normally distributed, which
+they are (Figure \ref{fig:residuals}).
+
+\begin{figure}
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/traceplot-1} \end{center}
+\caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.}
+\label{fig:traceplot}
+\end{figure}
+
+\vspace{1mm}
+\footnotesize
+
+\begin{center}\includegraphics[width=1\linewidth]{technicalReport4_files/figure-latex/unnamed-chunk-8-1} \end{center}
+\caption{Distribution of residuals from the selected model.}
+\label{fig:residuals}
+
+\textbackslash end\{figure\}
+
+\hypertarget{before-and-after-analysis-results}{%
+\section{Before-and-after analysis:
+results}\label{before-and-after-analysis-results}}
 

### 2021-12-21 timeSeries/arimaStrategy.R

@@ -1,0 +1,289 @@
+library(rethinking)
+library(tidyverse)
+library(ggthemes)
+library(stats)
+library(forecast)
+
+getwd()
+
+
+data <- read.csv("quittingFinalAnon.csv")
+attacked <- data[data$sumHighBefore >=1,]
+
+
+userArimaDFs <- list()
+
+for(i in 1:nrow(attacked)){
+user <- attacked[i,]
+activity <- as.integer(t(user[,c(paste("au",1:15, sep = ""))]))
+attacks <- as.integer(t(user[,c(paste("h",1:15, sep = ""))]))
+
+postAttacks <- as.integer(t(user[,c(paste("ph",1:15, sep = ""))]))
+commentAttacks <-  as.integer(t(user[,c(paste("h",1:15, sep = ""))])) - as.integer(t(user[,c(paste("ph",1:15, sep = ""))]))
+
+userDF <- data.frame(activity,postAttacks,commentAttacks, attacks)
+userDF <-userDF %>% mutate(attacksCumulative = cumsum(attacks))
+userDF <-userDF %>% mutate(attacksLag = lag(attacks,1))
+cumlag <- cumsum(ifelse(is.na(userDF$attacksLag), 0, userDF$attacksLag))
+userDF <-userDF %>% mutate(attacksLagCumulative = cumlag)
+userArimaDFs[[i]] <- userDF
+}
+
+#build bare arimas
+bareArimas <- list()
+for (i in 1:length(userArimaDFs)){
+bareArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],stationary=TRUE)
+}
+
+#collectbare akaike scores
+bareAIC <- numeric(length(userArimaDFs))
+for (i in 1:length(userArimaDFs)){
+bareAIC[i] <- bareArimas[[i]][["aicc"]]
+}
+
+#build arimas with today attacks
+
+todayArimas <- list()
+#for (i in 15:length(userArimaDFs)){
+#  todayArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],
+#                                 xreg=userArimaDFs[[i]]$attacks[2:14],stationary=TRUE)
+#}
+
+for (i in 1:length(userArimaDFs)){
+skip_to_next <- FALSE
+
+tryCatch(   todayArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],
[…]

### 2021-12-21 timeSeries/timeSeriesAnalysis.R

@@ -1,0 +1,31 @@
+library(rethinking)
+library(tidyverse)
+library(ggthemes)
+library(stats)
+library(forecast)
+
+getwd()
+summaries <- read.csv(file = "datasets/Summaries.csv")
+
+head(summaries)
+
+
+
+hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
+comments <- readRDS(file = "datasets/RAWNESTA/Comments.rds")
+interventions <- readRDS(file = "datasets/interventions.rds")
+
+interventionsByAuthorDate <- as.data.frame(xtabs(~ author + day, data = interventions))
+
+str(interventionsByAuthorDate)
+hate$author  <- as.character(hate$author)
+comments$author  <- as.character(comments$author)
+interventionsByAuthorDate$author  <- as.character(interventionsByAuthorDate$author)
+
+
+
+mean(hate$author %in% comments$author)
+mean(comments$author %in% hate$author)
+mean(interventionsByAuthorDate$author %in% hate$author)
+
+

### 2023-01-16 nestaVolunteers/nestaVolunteers/reportVolunteers.Rmd
added datasets folder and nesta volunteers

---
title: "Volunteers in NESTA experiment \\linebreak  Technical Report"
author: "Rafal Urbaniak"
output:
  pdf_document:
    keep_tex: yes
  number_sections: yes
  df_print: kable
includes:
  in_header: Rafal_latex8.sty
html_document:
  df_print: paged
word_document: default
classoption: dvipsnames, enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)
library(ggrepel)

```

The winning model, given our model selection method, is specified as follows:

\begin{align*}
\mathsf{interventions} \sim \mathsf{NegativeBinomial} (\lambda,\phi) \\
log(\lambda) = l_\mathsf{volunteerID[i]} + enth_\mathsf{ volunteerID[i]} \times \mathsf{daysOfProject} + comp_\mathsf{volunteerID[i]} \times \mathsf{competition}\\  
l_\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(lbar,lsigmabar) \\
lbar \sim \mathsf{Norm}(2, .9)\\
lsigmabar, enthsigmabar, compsigmabar \sim  \mathsf{Exp}(.5) \\
enth _\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(enthbar, enthsigmabar)\\
comp_\mathsf{ volunteerID[i] } \sim \mathsf{Norm}(compbar, compsigmabar) \\
enthbar, compbar \sim  \mathsf{Norm}(0, .3)\\
 \phi =  puser_\mathsf{ volunteerID[i] }  \\
 puser_\mathsf{ volunteerID[i] } \sim \mathsf{Exp}(1)
\end{align*}

Intuitively, volunteer interventions are assumed to have negative binomial distribution around their own expected value $\lambda$ and individualized dispersion parameters $\phi$. On each day each a user has their own daily expected value, which is determined by the following factors:
\begin{itemize}
\item First, there's user's individual baseline activity for the whole treatment period, $l_\mathsf{ volunteerID[i] }$.
\item next, each user has their own dispersion parameter,  $puser_\mathsf{ volunteerID[i] }$.
\item then, there is (usually dwindling) enthusiasm: the impact of time on that user, $enth_\mathsf{volunteerID[i]} $ to be (after exponentiation) multiplied by the number of days that have passed since the experiment started,
\item finally, we have the impact that the presence of competitions made on a user, $comp_\mathsf{ volunteerID[i] }$, which (after exponentiation) becomes the activity multiplier to be applied during competitions only.
\end{itemize}

\noindent Moreover, the model is hierarchical: the individual level parameters are drawn from distributions whose parameters are in turn to be estimated as well. Thus, $lbar$ is the overall baseline for the whole group, $enthbar$ is the overall estimated group enthusiasm coefficient, and $compbar$ is the overall estimated competition impact coefficient (all of them come with their own nuisance sigma parameters).

\noindent All of these parameters are given priors in a manner analogous to the introduction of priors for the other time series models, as explained in the appendix.^[Interestingly, if we are interested in the causal effect of competitions, we should not use an auto-regressive predictor. If we auto-regress on a lag in the $[1,7]$ range, for some days we will be conditioning on interventions conducted during the same competition, which will already contain some information about the impact of that competition. In other words, auto-regression with short lags would lead to post-treatment bias. On the other hand, auto-regression with longer lags would either lead to dropping a lot of data in the beginning (where lagged information is not available), or degenerate the analysis by using 0s for missing lagged values in a long initial period. All this without much gain, as we have already inspected null models with  auto-regression with large lags and they do not lead to performance improvement.]

Raw data and daily means are illustrated in Figure \ref{fig:volunteersBasic}, and the individualized totals with the key coefficients based on the trained model are illustrated in Figure \ref{fig:volunteersModel}.

```{r volunteersVis,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
volunteersLong <- read_csv(file = "nestaVolunteers/volunteersLong.csv")
competitionModel<- readRDS( "nestaVolunteers/competitionModel.rds")
volunteersJoint <- readRDS( file = "nestaVolunteers/datasets/volunteersJoint.rds")

profile <- c("low", "low", "low", "low",
             "initial", "initial", "initial",  "selective",
             "dynamic", "initial","selective","selective",
             "dynamic","dynamic", "selective")

volunteers <- unique(volunteersJoint$volunteer)
volunteersIDs <- unique(volunteersJoint$volunteerID)

volunteersSummary <- volunteersJoint %>%
  group_by(volunteer) %>%
  summarise(totalActivity = sum(interventions))

volunteersSummary$volunteerID <- as.factor(volunteersIDs)

volunteersSummary$profile <- factor(profile, levels = c("dynamic","active", "selective", "initial", "low"))
volunteersSummary <- as.data.frame(volunteersSummary)

meanRunning <- volunteersJoint  %>%
  group_by(Date) %>%
  summarise(competition = mean(competition), meanInterventions = mean(interventions))

volunteersDailyMeansPlot <- ggplot(data = meanRunning)+ 
  geom_violin(aes(x= as.factor(competition), y = meanInterventions,
                  color = as.factor(competition)))+
  theme_tufte(base_size = 10)+xlab("competition")+
  ylab("mean daily interventions")+
  ggtitle("Daily intervention means were higher during competitions")+
  geom_jitter(width = .3, aes(x= as.factor(competition),
              y = meanInterventions, 
              color =  as.factor(competition), shape = Date < "2020-07-16",
              size = meanInterventions)
              , alpha = .6)+
  theme(plot.title.position = "plot",legend.position = c(0.09, 0.8), legend.key.size = unit(.3, "cm") )+
  scale_size(range = c(1,4))+guides(size = "none", color = "none")+
  scale_color_manual(values = c("orangered", "grey"),
                     labels = c("yes", "no"), name = "competition",
                     breaks = c("1", "0"))+
  guides(shape = guide_legend(title = "First week"))

volunteersDailyPlot <- ggplot(volunteersJoint)+geom_point(aes(x = Date, y = interventions, color = as.factor(competition), size = interventions), alpha = .8)+
  theme_tufte(base_size = 10)+
  scale_color_manual(values = c("orangered", "grey"), labels = c("yes", "no"), name = "competition", breaks = c("1", "0"))+xlab("")+
  theme(plot.title.position = "plot",legend.position = c(0.09, 0.9), legend.key.size = unit(.3, "cm") )+ 
  scale_size(range = c(.5,2))+guides(size = "none")+labs(title = "After initial enthusiasm, volunteer engagement was higher during competitions")+ 
  geom_line(data = meanRunning, aes(x = Date, y = meanInterventions))

```

\begin{figure}
```{r fig:volunteersBasic5,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
grid.arrange(volunteersDailyPlot, volunteersDailyMeansPlot, ncol = 1)
```
\caption{Daily individual voilunteer intervention counts accross time with competition periods marked (top) and daily group intervention means grouped by whether a competition was ongoing (bottom). Note most of high means in the non-competition period are in the first week.}
\label{fig:volunteersBasic}
\end{figure}

```{r fig:volunteersModelPrep,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}

annotsize <- 2.5

sumsPlot  <- ggplot(volunteersSummary) +geom_bar(aes(x = reorder(as.factor(volunteerID), totalActivity)
                                        , y = totalActivity, fill = profile), stat = "identity")+
  coord_flip()+theme_tufte(base_size = 8)+ylab("total interventions")+xlab("")+
  ggtitle("Total engagement")+
  scale_fill_manual(values = c("darkred", "orangered", "darkgoldenrod", "bisque2", "azure4"),
                    labels = c("active, more during competitions","active throughout" , "active only during competitions", "initial enthusiasm died", "almost no activity"))+
  theme(plot.title.position = "plot", legend.key.size = unit(.25, "cm"),legend.key.width = unit(.3,"cm") , legend.position = c(.35, 1.15),
        legend.title = element_blank())+xlab("volunteer ID")

precis <- precis(competitionModel, depth = 2)
lIndividual <- precis[grep("l\\[",rownames(precis)),]
lGroup <- exp(precis[grep("lbar",rownames(precis)),])

lmean <- exp(lIndividual$mean)
llow <- exp(lIndividual$`5.5%`)
lhigh <- exp(lIndividual$`94.5%`)

eIndividual <- precis[grep("enth\\[",rownames(precis)),]
enthmean <- exp(eIndividual$mean)
enthlow <- exp(eIndividual$`5.5%`)
enthhigh <- exp(eIndividual$`94.5%`)

eGroup <- exp(precis[grep("enthbar",rownames(precis)),])

cIndividual <- precis[grep("comp\\[",rownames(precis)),]
cmean <- exp(cIndividual$mean)
clow <- exp(cIndividual$`5.5%`)
chigh <- exp(cIndividual$`94.5%`)

cGroup <- exp(precis[grep("compbar",rownames(precis)),])

volunteersDF <- data.frame(volunteer = volunteers, totalActivity = 
                             volunteersSummary$totalActivity ,
          profile = volunteersSummary$profile , 
          profileID = as.integer(volunteersSummary$profile ),
           volunteerID = as.integer(as.factor(volunteers)),
           lmean = lmean, llow = llow, lhigh = lhigh,
           emean = enthmean, elow = enthlow, ehigh = enthhigh,
           cmean = cmean, clow = clow, chigh = chigh)

lambdaPlot <- ggplot(volunteersDF)+geom_pointrange(aes(x = reorder(as.factor(volunteerID), totalActivity),y = lmean, ymin  = llow, ymax = lhigh,
                                                       color = profile))+
coord_flip()+theme_tufte(base_size = 8)+xlab("")+ylab(expression(lambda))+theme(axis.text.y =
                element_blank(), axis.ticks.y = element_blank())+ggtitle("Daily baseline")+
  scale_color_manual(values = c("darkred", "orangered", "darkgoldenrod", "bisque2", "azure4"),
                    labels = c("active, more during competitions","active throughout" , 
                               "active only during competitions", "initial enthusiasm died", "almost no activity"))+
  guides(color = "none")+geom_hline(yintercept = lGroup$mean, alpha = .8)+
  annotate("rect", ymin = lGroup$`5.5%`, ymax = lGroup$`94.5%`,
           xmin = 0, xmax = 16.5,
           alpha = .2,fill = "grey")+
  annotate("label", label =  round(lGroup$mean,2), y = lGroup$mean+1, x = 16, size = annotsize)

enthusiasmPlot <- ggplot(volunteersDF)+geom_pointrange(aes(x = reorder(as.factor(volunteerID), totalActivity),y = emean, ymin  = elow, ymax = ehigh,
                                                       color = profile))+
  coord_flip()+theme_tufte(base_size = 8)+xlab("")+ylab("multiplier per day passed")+theme(axis.text.y =
                                                                       element_blank(), axis.ticks.y = element_blank())+
  ggtitle("Enthusiasm change per day")+
  scale_color_manual(values = c("darkred", "orangered", "darkgoldenrod", "bisque2", "azure4"),
                     labels = c("active, more during competitions","active throughout" , 
                                "active only during competitions", "initial enthusiasm died", "almost no activity"))+
  guides(color = "none")+geom_hline(yintercept = 1, alpha = .6, color = "grey", lty = 2)+
  geom_hline(yintercept = eGroup$mean, alpha = .9)+
  annotate("rect", ymin = eGroup$`5.5%`, ymax = eGroup$`94.5%`,
           xmin = 0, xmax = 16.5,
           alpha = .2,fill = "grey")+
  annotate("label", label =  round(eGroup$mean,2), y = eGroup$mean+.02, x = 16, size = annotsize)

competitionPlot <- ggplot(volunteersDF)+geom_pointrange(aes(x = reorder(as.factor(volunteerID), totalActivity),y = cmean, ymin  = clow, ymax = chigh,
                                                           color = profile))+
  coord_flip()+theme_tufte(base_size = 8)+xlab("")+ylab("multiplier if competition is on")+theme(axis.text.y =
                                                                                element_blank(), axis.ticks.y = element_blank())+
  ggtitle("Impact of competitions")+
  scale_color_manual(values = c("darkred", "orangered", "darkgoldenrod", "bisque2", "azure4"),
                     labels = c("active, more during competitions","active throughout" , 
                                "active only during competitions", "initial enthusiasm died", "almost no activity"))+
  guides(color = "none")+geom_hline(yintercept = 1, alpha = .6, color = "grey", lty = 2)+
  geom_hline(yintercept = cGroup$mean, alpha = .9)+
  annotate("rect", ymin = cGroup$`5.5%`, ymax = cGroup$`94.5%`,
           xmin = 0, xmax = 16.5,
           alpha = .2,fill = "grey")+
  annotate("label", label =  round(cGroup$mean,2), 
           y = cGroup$mean+1, x = 16, size = annotsize)

sumsPlotGrob <- ggplotGrob(sumsPlot)
lambdaPlotGrob <- ggplotGrob(lambdaPlot)
enthusiasmPlotGrob <- ggplotGrob(enthusiasmPlot)
competitionPlotGrob <- ggplotGrob(competitionPlot)

```

\begin{figure}
```{r fig:volunteersModel17,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "250%", out.extra='angle=90', warning = FALSE, message = FALSE}
ggplot(data.frame(a=1)) + xlim(1, 38) + ylim(1, 10)+theme_void()+
annotation_custom(sumsPlotGrob, xmin = 1, xmax = 10, ymin =1.2, ymax = 9.56)+
annotation_custom(lambdaPlotGrob, xmin = 10, xmax = 20, ymin =1, ymax = 10)+
annotation_custom(enthusiasmPlotGrob, xmin = 18, xmax = 28, ymin = 1, ymax = 10)+
annotation_custom(competitionPlotGrob, xmin = 28.5, xmax = 38.5, ymin =1, ymax = 10)
```
\caption{Volunteer total engagement with their daily baseline and multipliers for enthusiasm and impact of competition. Pointranges represent individual level coefficients, group coefficients are represented by black lines with shaded 89\% HPDI areas.}
\label{fig:volunteersModel}
\end{figure}

### 2023-01-16 nestaVolunteers/nestaVolunteers/reportVolunteers.tex
added datasets folder and nesta volunteers

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames, enabledeprecatedfontcommands]{scrartcl}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Volunteers in NESTA experiment Technical Report},
  pdfauthor={Rafal Urbaniak},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Volunteers in NESTA experiment \linebreak  Technical Report}
\author{Rafal Urbaniak}
\date{}

\begin{document}
\maketitle

The winning model, given our model selection method, is specified as
follows:

\begin{align*}
\mathsf{interventions} \sim \mathsf{NegativeBinomial} (\lambda,\phi) \\
log(\lambda) = l_\mathsf{volunteerID[i]} + enth_\mathsf{ volunteerID[i]} \times \mathsf{daysOfProject} + comp_\mathsf{volunteerID[i]} \times \mathsf{competition}\\  
l_\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(lbar,lsigmabar) \\
lbar \sim \mathsf{Norm}(2, .9)\\
lsigmabar, enthsigmabar, compsigmabar \sim  \mathsf{Exp}(.5) \\
enth _\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(enthbar, enthsigmabar)\\
comp_\mathsf{ volunteerID[i] } \sim \mathsf{Norm}(compbar, compsigmabar) \\
enthbar, compbar \sim  \mathsf{Norm}(0, .3)\\
 \phi =  puser_\mathsf{ volunteerID[i] }  \\
 puser_\mathsf{ volunteerID[i] } \sim \mathsf{Exp}(1)
\end{align*}

Intuitively, volunteer interventions are assumed to have negative
binomial distribution around their own expected value \(\lambda\) and
individualized dispersion parameters \(\phi\). On each day each a user
has their own daily expected value, which is determined by the following
factors:

\begin{itemize}
\item First, there's user's individual baseline activity for the whole treatment period, $l_\mathsf{ volunteerID[i] }$.
\item next, each user has their own dispersion parameter,  $puser_\mathsf{ volunteerID[i] }$.
\item then, there is (usually dwindling) enthusiasm: the impact of time on that user, $enth_\mathsf{volunteerID[i]} $ to be (after exponentiation) multiplied by the number of days that have passed since the experiment started,
\item finally, we have the impact that the presence of competitions made on a user, $comp_\mathsf{ volunteerID[i] }$, which (after exponentiation) becomes the activity multiplier to be applied during competitions only.
\end{itemize}

\noindent Moreover, the model is hierarchical: the individual level
parameters are drawn from distributions whose parameters are in turn to
be estimated as well. Thus, \(lbar\) is the overall baseline for the
whole group, \(enthbar\) is the overall estimated group enthusiasm
coefficient, and \(compbar\) is the overall estimated competition impact
coefficient (all of them come with their own nuisance sigma parameters).

\noindent All of these parameters are given priors in a manner analogous
to the introduction of priors for the other time series models, as
explained in the appendix.\footnote{Interestingly, if we are interested
  in the causal effect of competitions, we should not use an
  auto-regressive predictor. If we auto-regress on a lag in the
  \([1,7]\) range, for some days we will be conditioning on
  interventions conducted during the same competition, which will
  already contain some information about the impact of that competition.
  In other words, auto-regression with short lags would lead to
  post-treatment bias. On the other hand, auto-regression with longer
  lags would either lead to dropping a lot of data in the beginning
  (where lagged information is not available), or degenerate the
  analysis by using 0s for missing lagged values in a long initial
  period. All this without much gain, as we have already inspected null
  models with auto-regression with large lags and they do not lead to
  performance improvement.}

Raw data and daily means are illustrated in Figure
\ref{fig:volunteersBasic}, and the individualized totals with the key
coefficients based on the trained model are illustrated in Figure
\ref{fig:volunteersModel}.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{reportVolunteers_files/figure-latex/fig:volunteersBasic5-1} \end{center}
\caption{Daily individual voilunteer intervention counts accross time with competition periods marked (top) and daily group intervention means grouped by whether a competition was ongoing (bottom). Note most of high means in the non-competition period are in the first week.}
\label{fig:volunteersBasic}
\end{figure}

\begin{figure}

\begin{center}\includegraphics[width=2.5\linewidth,angle=90]{reportVolunteers_files/figure-latex/fig:volunteersModel17-1} \end{center}
\caption{Volunteer total engagement with their daily baseline and multipliers for enthusiasm and impact of competition. Pointranges represent individual level coefficients, group coefficients are represented by black lines with shaded 89\% HPDI areas.}
\label{fig:volunteersModel}
\end{figure}

\end{document}

### 2023-01-16 nestaVolunteers/nestaVolunteers/engagementOverTime.R

@@ -1,0 +1,254 @@
+library(data.table)
+library(tidyverse)
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(janitor)
+
+
+# #setwd("~/Desktop/nestaVolunteers")
+# 
+# volunteers <- read.csv(file = "volunteers.csv")
+# 
+# head(volunteers, n = 20)
+# nrow(volunteers) #1755
+# 
+# #remove empty rows
+# 
+# volunteersCleaned <- volunteers[!apply(volunteers == "", 1, all), ] 
+# 
+# nrow(volunteersCleaned)
+# head(volunteersCleaned)
+# 
+# #now I want to convert the format and have one day as one variable and count of interventions per day
+# 
+# 
+# volunteersDate <- t(xtabs(~Volunteer.name + Date, data=volunteersCleaned))
+# 
+# head(volunteersDate)
+# ncol(volunteersDate)
+# nrow(volunteersDate)
+# str(volunteersDate)
+# 
+# write.csv(volunteersDate, "volunteersDate.csv")
+# 
+# #I had to write and read csv to get rid of the xtabs format
+# volunteersDateCSV <- read.csv(file = "volunteersDate.csv")
+# 
+# 
+# head(volunteersDateCSV)
+# str(volunteersDateCSV)
+# 
+# #removing first column and first row
+# volunteersDateCSVRemove <- volunteersDateCSV[,-2]
+# head(volunteersDateCSVRemove)
+# nrow(volunteersDateCSVRemove)
+# 
+# colnames(volunteersDateCSVRemove)[1] <- "Date"
+# 
+# str(volunteersDateCSVRemove)
+# 
+# volunteersDateCSVRemove$Date <- as.Date(volunteersDateCSVRemove$Date)
+# 
+# 
+# #competition 1
+# xmin <- as.Date("2020-07-24")
+# xmax <- as.Date("2020-07-31")
+# 
+# competition1 <- ifelse( xmin <= volunteersDateCSVRemove$Date &
+#                           volunteersDateCSVRemove$Date <= xmax, 1, 0)
+# 
+# #competition 2
+# xmin2 <- as.Date("2020-08-14")
+# xmax2 <- as.Date("2020-08-21")
+# 
+# competition2 <- ifelse( xmin2 <= volunteersDateCSVRemove$Date &
+#                           volunteersDateCSVRemove$Date <= xmax2, 1, 0)
+# 
+# #competition 3
[…]

### 2023-01-16 nestaVolunteers/nestaVolunteers/engagementSetup.R

@@ -1,0 +1,348 @@
+library(data.table)
+library(tidyverse)
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(janitor)
+library(spatstat.utils)
+library(useful)
+library(ggthemes)
+
+#setwd("~/Desktop/nestaVolunteers")
+
+
+volunteers <- read.csv(file = "volunteers.csv")
+
+head(volunteers, n = 20)
+nrow(volunteers) #1755
+
+
+#remove empty rows
+
+volunteersCleaned <- volunteers[!apply(volunteers == "", 1, all), ] 
+
+nrow(volunteersCleaned)
+head(volunteersCleaned)
+
+#interventions per day
+volunteersDate <- t(xtabs(~Volunteer.name + Date, data=volunteersCleaned))
+
+head(volunteersDate)
+ncol(volunteersDate)
+nrow(volunteersDate)
+str(volunteersDate)
+
+sort(colnames(volunteersDate))
+
+write.csv(volunteersDate, "volunteersDate.csv")
+
+#write and read csv to get rid of the xtabs format
+volunteersDateCSV <- read.csv(file = "volunteersDate.csv")
+
+head(volunteersDateCSV)
+str(volunteersDateCSV)
+ncol(volunteersDateCSV)
+colnames(volunteersDateCSV)
+
+
+volunteersDateCSVRemove <- volunteersDateCSV[,-2]
+head(volunteersDateCSVRemove)
+nrow(volunteersDateCSVRemove)
+
+colnames(volunteersDateCSVRemove)[1] <- "Date"
+
+str(volunteersDateCSVRemove)
+
+volunteersDateCSVRemove$bicycleflossing
+
+volunteersDateCSVRemove$Date <- as.Date(volunteersDateCSVRemove$Date)
+
+
+sort(colnames(volunteersDateCSVRemove))
+
+head(volunteersDateCSVRemove)
+nrow(volunteersDateCSV)
+
+
+#now additional info about joint identities
+joinDates <- read_csv("joinDates.csv")
+head(joinDates)
+
+
+# 
+# volunteersDateCSVRemove %>% select(Date,ChubbyhappyBuddha, PipperPapper)
+# 
+# volunteersDateCSVRemove <- volunteersDateCSVRemove %>% 
+#   mutate(ChubbyhappyBuddhaPipperPapper = ChubbyhappyBuddha + PipperPapper) %>%
[…]

### 2023-01-16 nestaVolunteers/nestaVolunteers/readmeVolunteers.R

@@ -1,0 +1,24 @@
+#DATASETS
+
+
+
+#PROCESS
+#cleaning and preparing data is here 
+file.edit("engagementSetup.R")
+#now the working dataset is ""datasets/volunteersJoint.rds" 
+#and in the list form for model processing as"datasets/volunteerDat.rds"
+
+
+# building visualisations in vVisualisations.R
+file.edit("vVisualisations.R")
+
+
+
+
+#then we're building a null model
+
+file.edit("vNull.R")
+
+#then we compare to models with predictors
+file.edit("vPred.R")
+

### 2023-01-16 nestaVolunteers/nestaVolunteers/vNull.R

@@ -1,0 +1,358 @@
+library(rethinking)
+library(ggplot2)
+library(data.table)
+library(dplyr)
+
+
+#playMusic <- browseURL('https://www.youtube.com/watch?v=Lx1iH8DgrLE&list=RDLx1iH8DgrLE&start_radio=1')
+
+
+
+volunteersSeparate <- readRDS("datasets/volunteersSeparate.rds")
+volunteersJoint <- rbindlist(volunteersSeparate, fill=FALSE, idcol=NULL)
+
+mean(apply(volunteersJoint,2, function(x) is.na(x)))
+
+
+dat <- readRDS("datasets/volunteerDat.rds")
+
+
+str(dat)
+
+
+nullPoisson <-  ulam(
+  alist(
+    interventions ~ dpois( lambda),
+    log(lambda) <- l,
+    l ~ dnorm(3,1.4)
+  ), data=dat, log_lik = TRUE,
+  constraints = list(
+    l = "lower = 0, upper = 100"
+  )
+  )
+
+
+prior <- extract.prior( nullPoisson , n=1e4 )
+lambda <- exp(prior$l) 
+priorPlot <- ggplot()+geom_density(aes(x = lambda))+xlim(c(0,80))+
+  ggtitle("Lambda")+theme_tufte()
+
+priorPlot
+
+
+#null with volunteer-specific lambdas
+
+nullPoissonVolunteer <-  ulam(
+  alist(
+    interventions ~ dpois( lambda),
+    log(lambda) <- l[volunteerID],
+    l[volunteerID] ~ dnorm(3,1.4)
+  ), data=dat, log_lik = TRUE,
+  constraints = list(
+    l = "lower = 0, upper = 100"
+  )
+  )
+
+
+nullPoissonHierarchical <-  ulam(
+  alist(
+    interventions ~ dpois( lambda),
+    log(lambda) <- l[volunteerID],
+    l[volunteerID] ~ dnorm(lbar,lsigmabar),
+    lbar ~ dnorm(3, .3),
+    lsigmabar ~ dexp(.5)
+  ), data=dat, log_lik = TRUE,
+  constraints = list(
+    l = "lower = 0, upper = 100",
+    lbar = "lower = 0, upper = 100",
+    lsigmabar = "lower = 0, upper = 100"
+  )
+)
+
+
+
+prior <- extract.prior( nullPoissonHierarchical , n=1e4 )
+lambda <- exp(prior$l) 
[…]

### 2023-01-16 nestaVolunteers/nestaVolunteers/vPred.R

@@ -1,0 +1,373 @@
+library(rethinking)
+library(ggplot2)
+
+
+playmusic <- browseURL('https://www.youtube.com/watch?v=Lx1iH8DgrLE&list=RDLx1iH8DgrLE&start_radio=1')
+
+
+
+#volunteersSeparate <- readRDS("datasets/volunteersSeparate.rds")
+
+
+#mean(apply(volunteersJoint,2, function(x) is.na(x)))
+
+
+dat <- readRDS("datasets/volunteerDat.rds")
+
+str(dat)
+
+
+
+start.time <- Sys.time()
+competitionModel <-  ulam(
+  alist(
+    interventions ~ dgampois(lambda,phi),
+    log(lambda) <- l[volunteerID] + enth[volunteerID] * daysOfProject +
+    comp[volunteerID] * competition,
+    l[volunteerID] ~ dnorm(lbar,lsigmabar),
+    lbar ~ dnorm(2, .9),
+    lsigmabar ~ dexp(.5),
+    enth[volunteerID] ~ dnorm(enthbar, enthsigmabar),
+    enthbar ~ dnorm(0, .3),
+    enthsigmabar ~ dexp(.5),
+    comp[volunteerID] ~ dnorm(compbar, compsigmabar),
+    compbar ~ dnorm(0, .3),
+    compsigmabar ~ dexp(.5),
+    phi <- puser[volunteerID],
+    puser[volunteerID] ~ dexp(1)
+  ), data=dat, log_lik = TRUE, 
+  chains = 2, cores = 2, 
+  iter = 5000,
+  constraints = list(
+    lambda = "lower = 0.0001, upper = 5",
+    l = "lower = 0.0001, upper = 5",
+    lbar = "lower = 0.1, upper = 5",
+    lsigmabar = "lower =  0.0001, upper = 5",
+    enth = "lower = -1.5, upper = 5",
+    enthbar = "lower = -1.5, upper = 5",
+    enthsigmabar = "lower = 0.0001, upper = 5",
+    comp = "lower = -1.5, upper = 5",
+    compbar = "lower = -1.5, upper = 5",
+    compsigmabar = "lower = 0.0001, upper = 5"
+  ),
+  control =
+    list(max_treedepth = 14, adapt_delta = 0.9),
+  #   cmdstan = TRUE
+)
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+time.taken
+playMusic
+
+
[…]

### 2023-01-16 nestaVolunteers/nestaVolunteers/vPredCom.R

@@ -1,0 +1,102 @@
+library(rethinking)
+library(ggplot2)
+library(data.table)
+library(tidyverse)
+library(scales)
+library(dplyr)
+library(janitor)
+library(spatstat.utils)
+library(useful)
+library(ggthemes)
+
+
+
+volunteersSeparate <- readRDS("datasets/volunteersSeparate.rds")
+volunteersJoint <- rbindlist(volunteersSeparate, fill=FALSE, idcol=NULL)
+volunteersCompetition <- readRDS("datasets/volunteersCompetition.rds")
+
+
+users <- colnames(cbind(volunteersCompetition[2:19],volunteersCompetition[21:27]) )
+sums <- colSums(cbind(volunteersCompetition[2:19],volunteersCompetition[21:27]))
+
+
+
+
+
+plotVolunteer <- function(i){
+ggplot(volunteersSeparate[[i]])+geom_point(aes(x = Date, y = interventions, color = as.factor(competition), size = interventions), alpha = .8)+
+  theme_tufte(base_size = 7)+
+  scale_color_manual(values = c("orangered", "grey"), labels = c("yes", "no"), name = "competition", breaks = c("1", "0"))+xlab("")+
+  theme(plot.title.position = "plot",legend.position = c(0.09, 0.9), legend.key.size = unit(.25, "cm") )+ 
+  scale_size(range = c(.5,2))+guides(size = "none")+ggtitle(paste("Interventions of volunteer", i, sep = " "))
+}
+
+profile <- c("low", "low", "low", "initial", "initial", 
+             "low", "low", "low", "dynamic","initial",
+             "low","initial","initial","low","dynamic",
+             "selective", "active","initial", "selective", "selective",
+             "active", "selective", "selective", "initial",
+             "active")
+
+#low rarely, none otherwise
+plotVolunteer(1) #low
+plotVolunteer(2)  #low
+plotVolunteer(3) #low
+plotVolunteer(4) #initial
+plotVolunteer(5) #initial
+plotVolunteer(6) #low
+plotVolunteer(7) #low
+plotVolunteer(8) #low
+plotVolunteer(9) #dynamic
+plotVolunteer(10) #initial
+plotVolunteer(11) #low
+plotVolunteer(12) #initial
+plotVolunteer(13) #initial
+plotVolunteer(14) #low
+plotVolunteer(15) #dynamic
+plotVolunteer(16)  #selective
+plotVolunteer(17)  #active
+plotVolunteer(18) #initial
[…]

### 2023-01-16 nestaVolunteers/nestaVolunteers/vVisualisations.R

@@ -1,0 +1,265 @@
+library(data.table)
+library(tidyverse)
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(janitor)
+library(spatstat.utils)
+library(useful)
+library(ggthemes)
+library(tidyquant)
+library(gridExtra)
+
+
+volunteersLong <- read_csv(file = "volunteersLong.csv")
+volunteersSeparate <- readRDS(file =  "datasets/volunteersSeparate.rds")
+volunteersJoint <- readRDS( file = "datasets/volunteersJoint.rds")
+competitionModel<- readRDS( "competitionModel.rds")
+
+
+
+
+plotVolunteer <- function(i){
+  ggplot(volunteersSeparate[[i]])+geom_point(aes(x = Date, y = interventions, color = as.factor(competition), size = interventions), alpha = .8)+
+    theme_tufte(base_size = 7)+
+    scale_color_manual(values = c("orangered", "grey"), labels = c("yes", "no"), name = "competition", breaks = c("1", "0"))+xlab("")+
+    theme(plot.title.position = "plot",legend.position = c(0.09, 0.9), legend.key.size = unit(.25, "cm") )+ 
+    scale_size(range = c(.5,2))+guides(size = "none")+ggtitle(paste("Interventions of volunteer", i, sep = " "))
+}
+
+
+
+#volunteersSeparate <- readRDS("datasets/volunteersSeparate.rds")
+#volunteersCompetition <- readRDS("datasets/volunteersCompetition.rds")
+
+
+# #low rarely, none otherwise
+# plotVolunteer(1) #low
+# plotVolunteer(2)  #low
+# plotVolunteer(3) #low
+# plotVolunteer(4) #low
+# plotVolunteer(5) #initial
+# plotVolunteer(6) #initial
+# plotVolunteer(7) #initial
+# plotVolunteer(8) #selective
+# plotVolunteer(9) #dynamic
+# plotVolunteer(10) #initial
+# plotVolunteer(11) #selective
+# plotVolunteer(12) #selective
+# plotVolunteer(13) #dynamic
+# plotVolunteer(14) #dynamic
+# plotVolunteer(15) #selective
+
+
+
+profile <- c("low", "low", "low", "low",
+             "initial", "initial", "initial",  "selective",
+             "dynamic", "initial","selective","selective",
+             "dynamic","dynamic", "selective")
+
+
+
[…]

### 2023-01-16 nestaVolunteers/vVisualisations.R

@@ -1,0 +1,9 @@
+library(data.table)
+library(tidyverse)
+library(ggplot2)
+library(scales)
+library(dplyr)
+library(janitor)
+library(spatstat.utils)
+library(useful)
+library(ggthemes)

### 2023-01-16 paperSubmission/paperSubmission1.tex
added paper submission

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{todonotes}

\journal{Information Processing \ Management}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{We need to beat namespotting, no idea how}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author{Us}

\affiliation{organization={},%Department and Organization
            addressline={}, 
            city={},
            postcode={}, 
            state={},
            country={}}

\begin{abstract}
Abstract goes here.

\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
Not sure what graphical abstract is supposed to be, but it goes here. 
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

\begin{keyword}
 keyword \sep keyword

\PACS PACScode \sep PACScode

\MSC MSCcode \sep MSCcode
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\tableofcontents

%% \linenumbers

%% main text

\section{Data analysis}\label{sec{analysis}}

\subsection{Exploration and data}\label{subsec:data-and-exploration}

For the duration of the project we selected 486 Reddit users\todo{how?} and tracked
their activity (with some breaks resulting from API restrictions and
technical issues, which were mostly sorted out in the observation
period), starting on 2020-03-09, beginning the intervention period on
2020-07-08, leading to a further observation period starting on
2020-09-09 and ending on 2020-11-20. The time series of attacks observed
and of interventions conducted can be inspected in Figure
\ref{fig:periodsPlot}, along with a quick search for weekly patterns.
Some of the users turned out to be bots, a few ceased to be active
during the experiment (with no strong reason to think this happened due
to them receiving an intervention) and a few received treatment of two
different types by accident (we relied on multiple volunteers and such
mistakes were likely to happen). Ultimately, in the time series data, we
ended up with data on 440 users.

\begin{figure}
\begin{center}\includegraphics[width=0.88\linewidth]{figures/periodsPlot-1}

\includegraphics[width=0.88\linewidth]{figures/periodsPlot-2} \end{center}
\caption{Daily sums of attacks and interventions throughout the three experimental periods, with GAM smoothing (left) and daily attack sums from all  weeks in the experimental period plotted against week days (right)---no pattern seems to arise.}
\label{fig:periodsPlot}
\end{figure}

We analyzed the data from three perspectives: we used the daily data to
(1) build seven time series models estimating the impact of individual
interventions at lags 1-7 days, and (2) to study the impact of the
cumulative number of total interventions received as the experiment
progressed, and (3) we used aggregated data to run a long term
before-and after analysis, comparing the summarized aggression levels
before and after the intervention period.

Before we move to the analysis, let us inspect the data. First, at the
aggregated level, the data involve the variables listed in Table
\ref{tab:baaVars}.\footnote{Further variables were defined in terms of those, in particular, we will be predicting \textsf{AdiffS} which is the standardized difference  \textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized difference \textsf{CA}-\textsf{CB}.The  standardized variables are systematically named  $\langle$variable\char`_name$\rangle$S.} The distribution of \textsf{IC} in the treatment groups is visualized in
Figure \ref{fig:interventionsDistro}. Note that the distributions are
somewhat different, even though the total intervention counts are
similar. The issue is discussed in Section XXXXX.\todo{add ref}

\vspace{1mm}
\footnotesize

\normalsize

\begin{table}
\centering
\begin{tabular}{ll}
\toprule
variable  explanation\\
\midrule
\cellcolor{gray!6}{AB}  \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD  attacks during (the treatment period)\\
\cellcolor{gray!6}{AA}  \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB  comments before\\
\cellcolor{gray!6}{CD}  \cellcolor{gray!6}{comments during}\\
CA  comments after\\
\cellcolor{gray!6}{group}  \cellcolor{gray!6}{treatment group}\\
IC  intervention count\\
\bottomrule
\end{tabular}

\caption{Variables involved in the before-and-after analysis.}
\label{tab:baaVars}
\end{table}

\begin{figure}

\begin{center}\includegraphics[width=.88\linewidth]{figures/interventionsDistroPlot-1} \end{center}
\caption{Distribution of daily interventions (by treatment group).}
\label{fig:interventionsDistro}
\end{figure}

Second, in the distribution of standardized difference in attacks, the
peaks of distributions are shifted a bit between the groups, with lowest
median for the normative group, but the differences seem minor (Figure
\ref{fig:violJoint}). This might suggest no impact of the interventions.
This conclusion would be too hasty, as the impact of other predictor
variables and interactions involved can mask actual associations.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{figures/violJoint-1} \end{center}
\caption{Empirical distribution of change in attacks (by treatment group).}
\label{fig:violJoint}
\end{figure}

To see how this masking can occur, let us inspect changes in attacks
against intervention counts. It turns out that restricting attention to
various aggression levels in the before period results in fairly strong
changes to the regression lines (Figure \ref{fig:linearShift}). This
suggests we should keep an eye out for interactions with aggression
before in the analysis, and that the initial comparison of means or
medians between groups might be misleading if the effects in different
volume groups are different and to some extent cancel each other.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{figures/fig:linearShift-1} \end{center}
\caption{Change in attacks vs the number of interventions received by treatment group, jittered with  linear smoothing.}
\label{fig:linearShift}
\end{figure}

\normalsize

Further insights, undermining the initial impression suggested by Figure
\ref{fig:violJoint}, can be obtained by visualizing individual time
series. Figure \ref{fig:tsVis} contains six fairly typical examples.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{figures/fig:tsVisPlot6-1} \end{center}
\caption{Examples of individual time series. Black points are attacks (smoothed in blue), red lines represent the cumulative number of interventions received (lag 3) divided by 10, gray lines represent overall activity level divided by a variable divider listed in the subtitle. Divisions introduced for visual comparability of general trends.}
\label{fig:tsVis}
\end{figure}

\normalsize

The general phenomenon is that while in the control group attacks tend
not to diminish, unless activity itself diminishes, they tend to
diminish in the normative group (although the more aggressive the user
is, the less of an impact can be observed), and in the empathetic group
if the user is not very aggressive. Of course, visualization of
individual cases (which the reader might suspect to be cherry-picked) is
no replacement for statistical analysis, to which we will now move.

\subsection{Causal thinking, choice of variables and
models}\label{subsec:causal-thinking-choice-of-variables-and-models}

First, we inspect correlations between predictors to avoid multicolinearity, as highly correlated predictors do not improve predictive performance and artificially inflate uncertainty in their corresponding coefficients in the models. We then develop
a plausible causal model of the situation (Figure
\ref{fig:correlations}). It turns out that to avoid multicolinearity we
cannot condition on CDS if we condition on CAS or CBS. Similarly, for
the time series data, since activity levels in particular day slices are
correlated, it will not be useful to condition on more than one
auto-regressive element (and since the predictive power is the highest
for lag 1 with no discoverable weekly patterns, we will not go further
than lag 1).

To choose the right variables to condition (or not condition) on to
identify the causal effect of the interventions, we need to think about
the causal structure of the problem. Comments during (the intervention period) impact attacks
during, which trigger interventions. Unmeasured user features cause
comments before (the intervention period), which impact attacks before directly. Comments during
(their impact on ADS is already included) impact attacks during directly
and comments after, which impact attacks after and attacks after
directly. Intervention count impacts attacks after and comments after.
The same directions of impact are included for intervention type.
Finally, comments through time are connected causally, and so are
attacks. The structure for the time series data is analogous, except now
instead of before and after, we have multiple daily indices.

\begin{figure}

\begin{center}\includegraphics[width=0.48\linewidth]{figures/correlations-1} \includegraphics[width=0.48\linewidth]{figures/correlations-2} \end{center}

\caption{Correlations between predictors (left) and a plausible causal model (right) used in the before-and-after analysis.}
\label{fig:correlations}
\end{figure}

What do we learn from causal considerations? \textsf{IT} has no backdoor
paths, but \textsf{IC} does, so we need to make sure these are closed to
avoid including spurious correlations in our analysis. There are in fact
65 different paths from \textsf{IC} to \textsf{AAC}. Crucially, all
backdoor paths go through \textsf{ADS}, which then becomes either a fork
or a pipe, so all backdoor paths can be closed by conditioning on
\textsf{ADS}. Moreover there is only one directed indirect path, it goes
through \textsf{CAS}, so we should not condition on \textsf{CAS} if we
are to identify total causal effect of \textsf{IC} on attacks, including
the impact mediated by its impact on comments. We might be interested in
the direct effect of \textsf{IC} and \textsf{IT} on \textsf{AAS}, but
then we also need to block indirect causal paths from the intervention
to the outcome. For such an evaluation we would need to also condition
on \textsf{CAS} and block all backdoor paths from \textsf{CAS} to
\textsf{AAS}. This, however, given the causal model, cannot be achieved,
as it would required conditioning on unobserved user features. That is,
we do not think direct causal effect is identifiable.

Analogous considerations apply to the time series model for the total
impact of individual interventions received exactly \(k\) days before
(in our case, \(k\in \{1, \dots, 7\}\)). The situation, however, is
somewhat different for the impact of the total number of cumulative
interventions received so far. The trouble is, for example, that if a
user received so far a number of interventions until yesterday, some of
them had been received before yesterday and those had already impacted
their aggression level yesterday. In other words, conditioning on lagged
attacks leads to the post-treatment bias and should be
avoided.\footnote{In fact, in the aggregated data analysis, we will be predicting the standardized difference between attacks before and after (\textsf{ADiffS}), and the standardized difference between comments, before and after (\textsf{CDiffS}), but the general points about the nodes involved apply also to defined nodes.  As already discussed, we do not include \textsf{CDS} because of its strong correlation with \textsf{CBS}. We also do not condition on \textsf{ABS} when modeling \textsf{ADiffS} (or on \textsf{CBS} when modeling \textsf{CDiffS})---not only because it has a pretty strong correlation with another predictor (\textsf{ADS}), but rather also because it is used to define the output variable. In such a set-up, it is clear that a model including \textsf{ABS} would have better predictive power, but since a definitional connection is present, thinking that its inclusion in the model tells us something about causality  would be misled.}

Otherwise, it's open season for the other variables and interactions
between them, and our decision to include or exclude them in the model
will be guided by information-theoretic criterion of predictive power, whose more detailed explanation is  included in the appendix, the so-called
Widely Acceptable Information Criterion:
\[
\mathsf{WAIC(y, \Theta)}  = -2 (\mathsf{lppd} - \overbrace{\sum_i var_\theta \mathsf{log} p (y_i \vert \theta)}^{\mathsf{penalty}})
\]
We also use  posterior predictive checks in cases in which the likelihood
functions used by the models to be compared are different and
information-theoretic calculations might be misleading. In such cases we
investigated the ratio of actual observations included in the 50\% and
in the 89\% posterior predictive distribution, and the models for which
higher ratios were observed in both were selected (no case of diverging
evaluation for the two criteria has been observed).

In our model building we used the \textsf{rethinking} package,
except for the cumulative impact time series models, where it becomes
computationally unfeasible, in which case we built models in
\textsf{Rstan} directly. Moreover, for the time series analysis we will
build hierarchical Bayesian models which tend to have around
\(u \times 2p + 2p\) parameters (we will explain later why), which means
that for 440 users our final model with interaction with six predictors
would have \(440 \times 12 + 12 = 5292\) parameters, and 
have to be trained on daily data for 7 variables collected for six months. The
building of such a model on a modern computer takes days. Since in
reaching this model we needed to build multiple somewhat simpler models
or models with different structures and test their performance, model
selection on the full data set was unfeasible. That is, in the time
series analysis in model selection at each step we compared models
(sometimes built with quadratic approximation) with respect to three
independent samples for \(40, 60\) and \(60\) users. We made the
decision only if a given model structure performed better on all these
subsets (which was usually the case, so the model selection criteria
gave us pretty robust answers). For the most complicated model of the
impact of cumulative number of interventions, building a single model
for the whole data set was not computationally feasible (computation
time does not increase linearly with the number of users included in the
dataset), so we randomly split the dataset 
and provided results for the subgrous---the results were not very divergent and the highest posterior density intervals were not very wide.

For the time series, the model that the procedure led us to is as follows (see the appendix for a detailed explanation of how this model has been reached):

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \mathsf{NegativeBinomial}(\lambda_i, \phi_{\mathsf{userID[i]}} ) $\\
$log(\lambda_i)  =  l_{\mathsf{userID[i]}} +
                  a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} +
                  c_{\mathsf{userID[i]}} \times \mathsf{act} + $\\
$                   + 
       i1control_{\mathsf{userID[i]}} \times  \mathsf{control} \times \mathsf{intL1D}  +$ \\$         +  i1emp_{\mathsf{userID[i]}} \times  \mathsf{emp} \times \mathsf{intL1D}  +$ \\$
              +  i1norm_{\mathsf{userID[i]}} \times  \mathsf{norm} \times \mathsf{intL1D}
                          $\\ 
$  l_{\mathsf{userID[i]}}   \sim \textsf{Norm}(\bar{l}, \bar{\sigma_l}) $\\
$  a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(\bar{a}, \bar{\sigma_a}) $\\
$  c_{\mathsf{userID[i]}}  \sim \textsf{Norm}(\bar{c}, \bar{\sigma_c}) $\\
 $ i1control_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(i1controlOverall,\bar{\sigma_{i1}})$ \\
$   i1emp_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(i1empOverall, \bar{\sigma_{i1}})$\\  
 $ i1norm_{\mathsf{userID[i]}}   \sim  
     \textsf{Norm}(i1normOverall, \bar{\sigma_{i1}})$\\
$     i1controlOverall  \sim  \textsf{Norm}(0,.2)$\\
$    i1empOverall   \sim  \textsf{Norm}(0,.2) $\\
$    i1normOverall   \sim  \textsf{Norm}(0,.2) $\\
$    \bar{\lambda}   \sim  \textsf{Norm}(.00001, 2.5) $\\
$    \bar{\sigma_l}  \sim  \mathsf{Exp}(1.5)$\\
$    \bar{a}  \sim \textsf{Norm}(0, .2) $\\
$    \bar{\sigma_a}  \sim  \mathsf{Exp}(5) $\\
$    \bar{c}  \sim  \mathsf{Norm}(0, .2)$\\
$    \bar{\sigma_c}  \sim \mathsf{Exp}(5) $\\
$    \bar{\sigma_{i1}}  \sim  \mathsf{Exp}(5)
$
\end{tabular}
\end{center}

\normalsize

\noindent This might seem somewhat confusing, so let us disentangle this maze:

\begin{itemize}
\item Each user has their own baseline aggression level, $l_{\mathsf{userID[i]}}$. \item However, these individual aggression levels are not disconnected, they come from a distribution themselves, $\textsf{Norm}(\bar{l}, \bar{\sigma_l})$. $\bar{l}$ is the mean baseline aggression level for the whole population, and $\bar{\sigma_l}$ is the standard deviation of this distribution. These general parameters are to be estimated along with the individual ones.
\item Then  there are individual auto regression coefficients     $a_{\mathsf{userID[i]}}$, which capture the correlation between  yesterday's attacks with today's attacks, so to speak. These also come from a general distribution \linebreak  $\textsf{Norm}(\bar{a}, \bar{\sigma_a})$, with its own general parameters to be estimated.
\item Next, there are individual user's coefficients connecting the user's activity on a given day with their aggression on the same day,  $c_{\mathsf{userID[i]}}$, all coming from a general distribution $\textsf{Norm}(\bar{c}, \bar{\sigma_c})$ whose parameters are also to be estimated.
\item For any particular treatment group, say, empathy, we have a user level coefficient $i1emp_{\mathsf{userID[i]}}$, which is activated if the user is in the empathy group (that is, we multiply by the indicator variable $\mathsf{emp}$) and then applied to the number of interventions received the day before (lag 1). Similarly for the two other groups. These user-level parameters come from the distribution $\textsf{Norm}(i1empOverall, \bar{\sigma_{i1}})$, whose parameters are to be estimated.
\item Finally, prior predictive check was used to choose priors for the general coefficients. 
\end{itemize}

For the impact of the cumulative number of interventions (we will only
use lag 3 for reasons that will become clear), since the range of values
of the predictor is wider, for computational feasibility we further
needed to restrict coefficients to lie between -3 and 2, but these
values are not plausible values of the parameters anyway
(\(exp(-3) \approx 0.04\) and \(exp(2) \approx 7.38\)). The model for
the cumulative impact was tested with and without interaction with
overall aggression in the before period, without the use of attacks on a
given day (as already explained, to avoid the post-treatment bias). The
two relevant options   are:

\footnotesize

\begin{center}
\begin{tabular}{c}
$log(\lambda_i)  =  l_{\mathsf{userID[i]}}  + c_{\mathsf{userID[i]}} \times \mathsf{act} + 
      ic3control_{\mathsf{userID[i]}} \times  \mathsf{control} \times \mathsf{intCL3D}  + $\\$  + 
            ic3emp_{\mathsf{userID[i]}} \times  \mathsf{emp} \times \mathsf{intCL3D}  + $\\  
    $  ic3norm_{\mathsf{userID[i]}} \times  \mathsf{norm} \times \mathsf{intCL3D}$\\
$log(\lambda_i)  =  l_{\mathsf{userID[i]}}  + c_{\mathsf{userID[i]}} \times  act + $\\$  + 
      ic3control_{\mathsf{userID[i]}} \times   \mathsf{control} \times  \mathsf{intCL3D}  + $\\$  + icabst3control_{\mathsf{userID[i]}} \times   \mathsf{control} \times  \mathsf{intCL3D} \times  \mathsf{abst} + $\\ 
        \end{tabular}
\end{center}

\begin{center}
\begin{tabular}{c}
  $log(\lambda_i)  =  l_{\mathsf{userID[i]}}  + c_{\mathsf{userID[i]}} \times \mathsf{act} + 
      ic3control_{\mathsf{userID[i]}} \times  \mathsf{control} \times \mathsf{intCL3D}  + $\\ $ +    ic3emp_{\mathsf{userID[i]}} \times   \mathsf{emp} \times  \mathsf{intCL3D}  + $\\$  + icabst3emp_{\mathsf{userID[i]}} \times   \mathsf{emp} \times  \mathsf{intCL3D}  \times  \mathsf{abst} + $\\ $ +
        ic3norm_{\mathsf{userID[i]}}] \times   \mathsf{norm} \times  \mathsf{intCL3D} + $\\ $ + icabst3norm_{\mathsf{userID[i]}} \times   \mathsf{norm} \times  \mathsf{intCL3D} \times  \mathsf{abst} 
        $
        \end{tabular}
\end{center}

\normalsize

The models employing the second formula were superior in performance. It
is not surprising that once attacks on a given day were removed from
predictor, the overall aggression levels in the before period became
predictive. The price to pay, however, is that now to obtain a
user-specific multiplicative interpretation of the impact of cumulative
interventions, we need to put the two elements together while
multiplying one by the user's overall aggression and only then
exponentiate, that is we need to inspect, for instance,
\(exp(ic3emp_{\mathsf{userID[i]}} + icabst3emp_{\mathsf{userID[i]}} \times \mathsf{abst}[i])\),
instead of simply looking at \(exp(ic3emp_{\mathsf{userID[i]}})\).

Finally, in the before-and-after analysis, we put aside the time series
element, look at aggregated counts before and after the treatment
period, thus obtaining a more of a long-term effect analysis. Moreover,
this time we standardize counts, obtaining continuous variables and
employing normal distribution in the likelihoods, thus also making sure
the overall results are robust under a spectrum of modeling choices. We
build and compared multiple additive models where the outcome variable
is normally distributed around the predicted mean, which is a linear
function of predictors (possibly with interactions). Our general criteria
led to the model whose specification is as follows (we also selected
regularizing prior parameters using prior predictive checks to avoid
unreasonably narrow overall prior distributions, see the appendix for a longer explanation):

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{AdiffS}  \sim \textsf{Norm}(\mu, \sigma)$\\
$\mu_i  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
 \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + $\\
$  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS}$\\
$ \alpha  \sim \textsf{Norm}(0,.3)$\\
$\beta_{\mathsf{ADS}}[\mathsf{group}_i]  \sim \textsf{Norm}(0,.3)$\\
$\beta_{\mathsf{group}_i}  \sim \textsf{Norm}(0,.3)$\\
$\beta_{\mathsf{IC}}[\mathsf{group}_i]  \sim \textsf{Norm}(0,.3)$\\
$ \beta_{\mathsf{ADSIC}}  \sim \textsf{Norm}(0,.3)$\\
$ \beta_{\mathsf{CBS}}[\mathsf{group}_i] \sim \textsf{Norm}(0,.3)$\\
\end{tabular}
\end{center}

\normalsize

That is, we take the resulting mean to be the result of the general
average (\(\alpha\)) and the impact of the following coefficients:
group-specific coefficient for \textsf{ADS}, group coefficient,
group-specific coefficient for \textsf{IC}, interaction coefficient for
\textsf{ADS} and \textsf{IC}, and group-specific coefficient for
\textsf{CBS}. This is plausible \emph{prima facie}, as which group a
user belongs to might have impact on how the number of attacks during
the treatment are related to the number of attacks after, the role of
the intervention count, and the role of comments before. Moreover, the
levels of aggressive behavior displayed by the user during treatment
might have impact on the role played by the intervention count.

\subsection{Results}\label{subsec:resultss}

\subsubsection{Interventions on a given
day}\label{subsubsec:interventions-on-a-given-day}

We built seven separate models for the impact of interventions \(k\)
days ago, \(1\leq k \leq 7\). In Figure \ref{fig:dailyResults} we
visualize the results for the three groups, with jitter based on user
aggression in the before period.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/fig:dailyResultsPlot-1} \end{center}
\caption{Impact of interventions received lag $1\leq k \leq 7$ on attacks on a given day. High-level coefficients are pictured in black.}
\label{fig:dailyResults}
\end{figure}

Notice that in short term, interventions actually increase aggression
the next day (even taking the user's yesterday's aggression and today's
activity in consideration). The effect, however, quickly wears off.

\subsubsection{Cumulative sum of
interventions}\label{subsubsec:cumulative-sum-of-interventions}

In our analysis of the effect of the cumulative number of interventions
received so far, however, we intend separate this short-term effect from
the long-term effect. To achieve this, we lag the cumulative
interventions variable by 3, so that we're giving the user the minimal
number of days needed for the short-term effect to wane. The individual
users' multiplicative impact coefficients are visualized in Figure
\ref{fig:cumulativeResultsPlot}.

\begin{figure}

\begin{center}\includegraphics[width=.8\linewidth]{ figures/fig:cumulativeResultsPlot-1} \includegraphics[width=.8\linewidth]{ figures/fig:cumulativeResultsPlot-2} \end{center}
\caption{Multiplicative impact of cumulative interventions lag 3 on attacks. Individual users' coefficents only, full range (top), and with attention restricted to the bulk of the sample. Sub-sample coefficients depend on aggression and are represented as lines, colored by sub-sample. Note low number and high uncertainty for highly aggressive users, which motivate the restriction of the $x$ axis for inspection.}
\label{fig:cumulativeResultsPlot}
\end{figure}

\normalsize

The efficiency of normative interventions seems overall higher, except
for low-aggression users, for which empathetic interventions might be
equally or more useful. Importantly, linear extrapolation to extreme
values might be misleading, so let us inspect on what happens with the
general level multiplicative coefficients at the levels of aggression
which are actually quite common, that is, at the 1st, 2nd and 3rd
quartile (with respect to \(\mathsf{abst}\)). This indicates that for
the bulk of the sample the impact of cumulative interventions has been
negative, slightly more so on users with lower aggression levels.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/fig:cumulativeResultsGeenralPlot-1} \end{center}
\caption{Multiplicative impact of cumulative interventions lag 3 on attacks. General level coefficents only, in three quantiles (.25, .5, .75). Colored by sub-sample.}
\label{fig:cumulativeResultsGeneralPlot}
\end{figure}

\subsubsection{Long term before/after
analysis}\label{subsubsec:long-term-beforeafter-analysis}

The general problem with interpreting  models of this complexity involving
interaction is  that coefficients are not directly interpretable. For this reason, it is better
to plot predicted effects for various combinations of predictors. In the
construction of the plots we rely on the following:

\begin{itemize}
\item The values \textsf{ADS} range from -.67 to 10, with approximately 30\% below -.5, around 80\% below .3, and around 95\% below 1.7, so we use these three settings of this variable in our visualizations.

\item The values \textsf{CBS} range from -.82 to 18.3, with approximately 30\% below -.4, around 80\% below .3, and around 95\% below 1.3, so we use these three settings of this variable in our visualizations.

\end{itemize}

% \begin{figure}
% \begin{center}\includegraphics[width=1\linewidth]{ figures/unnamed-chunk-3-1} \end{center}
% \caption{The final model coefficients.}
% \label{fig:coeffs}
% \end{figure}

Grouped before-and-after predicted change of attacks by the levels we
just listed are visualized in Figure \ref{fig:predictedChange}. For more clarity, let's inspect predicted contrasts, here understood as
distances from the control group mean, by activity level, first versus
CBS (comments before, standardized, Figure \ref{fig:ContrastCBS}), then
versus ADS (attacks during, standardized, Figure \ref{fig:ContrastADS}).

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/unnamed-chunk-5-1} \end{center}
\caption{Predicted change in attacks, depending on user’s activity level
(CBS: comments before, standardized) and how aggressive overall they
were (ADS: attacks during, standardized). The more aggressive and active
the users, the higher the attacks drop in the normative group, slight drop
correlated with emotive interventions for not too active users.}
\label{fig:predictedChange}
\end{figure}

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/unnamed-chunk-7-1} \end{center}
\caption{Predicted contrasts (difference in attacks as compared to the control group)
for the two treatment groups vs activity before the treatment. Notice that
empathetic interventions correlated with decreased attacks for less active
users, but performed worse than normative interventions for more active
users. Normative interventions, in contrast, seem to have better impact on
 more active users.}
\label{fig:ContrastCBS}
\end{figure}

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/unnamed-chunk-9-1} \end{center}
\caption{Predicted contrasts (difference in attacks as compared to the control group)
for the two treatment groups vs aggression during the treatment period.
Notice that empathetic interventions correlated with decreased attacks for
less aggressive users, but performed worse than normative interventions for
more aggressive users. Normative interventions, in contrast, seem to have
better impact on  more aggressive users.}
\label{fig:ContrastADS}
\end{figure}

Now, let's inspect the impact of intervention counts by treatment type
by looking at contrasts (distances from the control group mean) with
89\% HPDIs by IC (intervention count). Notice the predicted effect of IC
is weaker than group membership, so for visibility the \(y\)-axis has a
smaller range. Also, not enough data was available to reliably estimate
uncertainty for IC above 20, hence the restriction on the \(x\)-axis
(already at lower values, lack of estimates is visible for the more
extreme settings).

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/visICPlot-1} \end{center}
\caption{Contrasts (change in attacks as compared to the control group) vs the number
of interventions received. Note that repeating empathetic interventions
correlates with decreased attacks, while repeating normative interventions
is counterproductive.}
\label{fig:ContrastsIC}
\end{figure}

\section{Discussion}

\section{Volunteer engagement and impact of competitions}

\subsection{The challenge of keeping volunteers engaged}

\subsection{Volunteer activity  data analysis}

The winning model, given our model selection method, is specified as
follows:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{interventions} \sim \mathsf{NegativeBinomial} (\lambda,\phi) $\\
$log(\lambda) = l_\mathsf{volunteerID[i]} + enth_\mathsf{ volunteerID[i]} \times \mathsf{daysOfProject} + comp_\mathsf{volunteerID[i]} \times \mathsf{competition}$\\  
$l_\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(lbar,lsigmabar) $\\
$lbar \sim \mathsf{Norm}(2, .9)$\\
$lsigmabar, enthsigmabar, compsigmabar \sim  \mathsf{Exp}(.5) $\\
$enth _\mathsf{ volunteerID[i] }  \sim \mathsf{Norm}(enthbar, enthsigmabar)$\\
$comp_\mathsf{ volunteerID[i] } \sim \mathsf{Norm}(compbar, compsigmabar) $\\
$enthbar, compbar \sim  \mathsf{Norm}(0, .3)$\\
$ \phi =  puser_\mathsf{ volunteerID[i] } $ \\
$ puser_\mathsf{ volunteerID[i] } \sim \mathsf{Exp}(1)$
\end{tabular}
\end{center}

\normalsize

Intuitively, volunteer interventions are assumed to have negative
binomial distribution around their own expected value \(\lambda\) and
individualized dispersion parameters \(\phi\). On each day each a user
has their own daily expected value, which is determined by the following
factors:

\begin{itemize}
\item First, there's user's individual baseline activity for the whole treatment period, $l_\mathsf{ volunteerID[i] }$.
\item next, each user has their own dispersion parameter,  $puser_\mathsf{ volunteerID[i] }$.
\item then, there is (usually dwindling) enthusiasm: the impact of time on that user, $enth_\mathsf{volunteerID[i]} $ to be (after exponentiation) multiplied by the number of days that have passed since the experiment started,
\item finally, we have the impact that the presence of competitions made on a user, $comp_\mathsf{ volunteerID[i] }$, which (after exponentiation) becomes the activity multiplier to be applied during competitions only.
\end{itemize}

\noindent Moreover, the model is hierarchical: the individual level
parameters are drawn from distributions whose parameters are in turn to
be estimated as well. Thus, \(lbar\) is the overall baseline for the
whole group, \(enthbar\) is the overall estimated group enthusiasm
coefficient, and \(compbar\) is the overall estimated competition impact
coefficient (all of them come with their own nuisance sigma parameters).

\noindent All of these parameters are given priors in a manner analogous
to the introduction of priors for the other time series models, as
explained in the appendix.\footnote{Interestingly, if we are interested
  in the causal effect of competitions, we should not use an
  auto-regressive predictor. If we auto-regress on a lag in the
  \([1,7]\) range, for some days we will be conditioning on
  interventions conducted during the same competition, which will
  already contain some information about the impact of that competition.
  In other words, auto-regression with short lags would lead to
  post-treatment bias. On the other hand, auto-regression with longer
  lags would either lead to dropping a lot of data in the beginning
  (where lagged information is not available), or degenerate the
  analysis by using 0s for missing lagged values in a long initial
  period. All this without much gain, as we have already inspected null
  models with auto-regression with large lags and they do not lead to
  performance improvement.}

Raw data and daily means are illustrated in Figure
\ref{fig:volunteersBasic}, and the individualized totals with the key
coefficients based on the trained model are illustrated in Figure
\ref{fig:volunteersModel}.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{figures/fig:volunteersBasic5-1} \end{center}
\caption{Daily individual voilunteer intervention counts accross time with competition periods marked (top) and daily group intervention means grouped by whether a competition was ongoing (bottom). Note most of high means in the non-competition period are in the first week.}
\label{fig:volunteersBasic}
\end{figure}

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth,angle=90]{figures/fig:volunteersModel17-1} \end{center}
\caption{Volunteer total engagement with their daily baseline and multipliers for enthusiasm and impact of competition. Pointranges represent individual level coefficients, group coefficients are represented by black lines with shaded 89\% HPDI areas.}
\label{fig:volunteersModel}
\end{figure}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Explanation of WAIC}

 Let  $y$ be the observations and $\Theta$  a posterior distribution.
First, log-pointwise-predictive-density is defined by:
\[
\mathsf{lppd}(y, \Theta)  = \sum_i log\frac{1}{S}\sum_s p (y_i\vert \Theta_s)
\]
\noindent where $S$ is the number of samples in the posterior, and $\Theta_s$ 
is the $s$-th combination of sampled parameter values in the posterior distribution. That is, 
for each observation and each combination of 
parameters in the posterior we first compute its density, then 
we take the average density of that observation over all combinations of parameters in the posterior,
and  then take the logarithm. Finally, we sum these values up for all the observations. Crucially, when comparing posterior distributions with respect to the same dataset, \textsf{lppd}s are proportional
 to unbiased estimates of their divergence from the real distribution (note that it is \emph{only} 
 proportional, and for this reason can be used for comparison of distributions 
 only and makes no intuitive sense on its own).  However, \textsf{lppd} always improves
  as the model gets more complex, so for model comparison it makes more sense to use 
 the Widely Applicable Information Criterion (WAIC), which is an approximation of the out-of-sample deviance that converges to the cross-validation approximation in a large sample. It  is defined as
 the log-posterior-predictive-density with an additional
  penalty proportional to the variance in the
  posterior predictions:
\[
\mathsf{WAIC(y, \Theta)} = -2 (\mathsf{lppd} - \overbrace{\sum_i var_\theta \mathsf{log} p (y_i \vert \theta)}^{\mathsf{penalty}})
 \]
\noindent  Thus to construct the penalty, we calculate the variance in log-probabilities for each observation and sum them up. Because of the analogy to Akaike's criterion, the penalty is sometimes called the effective number of parameters, $p_{\mathsf{WAIC}}$. 
How does WAIC compare to other information criteria?  AIC uses MAP estimates instead of the posterior and requires that priors be flat or overwhelmed by the likelihood, and assumes that the posterior distribution is approximately multivariate Gaussian and the sample size is  much greater  than the number of parameters used in the model. Bayesian Information Criterion (BIC) also requires flat priors and uses MAP estimates. WAIC does not make these assumptions, and provides almost exactly the same results as AIC, when AIC’s assumptions are met.

\section{Time series model
selection}\label{sec:time-series-model-selection}

Suppose we are interested in the impact of interventions received \(n\)
days ago. We started with a simple null model that uses the Poisson
distribution, with either uses a single \(\lambda\) for all the users,
or user-specific \(\lambda\)s. The first Bayesian model has the
following structure:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks_i}  \sim  \textsf{Poisson}( \lambda)$\\$
    log(\lambda)   =  l $\\$
    l  \sim  \textsf{Norm}(.05,2.8)$
\end{tabular}
\end{center}

\normalsize

and the user-specific coefficient model had the following structure:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{Poisson}( \lambda_i)$\\$ 
    log(\lambda_i)   =  l_{\mathsf{userID[i]}} $\\$
    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.8)$
\end{tabular}
\end{center}

\normalsize

The priors were chosen using prior predictive check, so that the 89\%
density intervals reached between 0 and 34, with median around 1. Given
our prior experience with similar user datasets this is a fairly wide
informative prior. The comparison, unsurprisingly, preferred the
user-specific \(\lambda\)s.

Next, we introduced the auto-regressive element, conditioning on
yesterday's attacks. The choice of priors for the auto-regression
coefficient is guided by the visualization (intuitive direct
understanding of the values is made difficult by the fact that the
predictors work on the logarithmic scale) and the fact that larger
values would result in a unreasonably extreme impact of yesterday's
attacks.

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{Poisson}( \lambda_i)$\\$ 
    log(\lambda_i)   =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1}$\\$
    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.8)$\\$
    a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(0,.2)$
\end{tabular}
\end{center}

\normalsize

Next, we added today's activity level as a predictor, with user-specific
coefficients. Adding activity levels helps. Note also that our priors
taken separately were made more narrow, to preserve the overall width of
the prior predictive distribution (this will be the usual strategy as we
progress).

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{Poisson}( \lambda_i)$\\ 
$    log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} + c \times \mathsf{act}$\\ 
$    l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c   \sim  \textsf{Norm}(0,.1)$
\end{tabular}
\end{center}

\normalsize

\noindent Unsurprisingly, it helps even more if the
coefficients are user-specific:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{Poisson}( \lambda_i)$\\ 
 $   log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times  \mathsf{attacksL1} + c_{\mathsf{userID[i]}} \times \mathsf{act}$\\ 
  $  l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
 $   a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(0,.1)$
\end{tabular}
\end{center}

\normalsize

A relatively large number of zeros suggests that moving to a
zero-inflated Poisson distribution would be a good idea. It was not, so
the following model structure was tested and abandoned:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{ZiPoisson}(p, \lambda_i)$\\ 
$    log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}}  \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}}  \times \mathsf{act}$\\ 
$    l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(0,.1) $\\
$    logit(p)   = \pi$\\
$    \pi   \sim Norm(-1.5,1) $
\end{tabular}
\end{center}

\normalsize

Then we considered the negative binomial distribution, and the addition
of week days as a predictor (both with general and user-level
coefficients). While moving to the negative binomial distribution
resulted in an improvement, adding week days did not improve the model
performance, perhaps because we already conditioned on activity, and
whatever the impact of weekdays was, has been already mediated through
activity (in a sense, we committed a post-treatment bias with respect to
weekdays; but that's fine, we did not really care about the impact of
weekdays).

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}}  \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}}  \times \mathsf{act}$\\ 
$    l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(0,.1) $\\
$    \phi  \sim \mathsf{Exp}(1)$\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}}  \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}}  \times \mathsf{act} + w  \times \mathsf{weekday}$\\ 
  $  l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(0,.1) $\\
$    w   \sim \textsf{Norm}(0,.1) $\\
$    \phi   \sim \mathsf{Exp}(1)$
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i   \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)    =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}}  \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}}  \times \mathsf{act} + w_{\mathsf{userID[i]}}  \times \mathsf{weekday}$\\ 
$    l_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}   \sim  \textsf{Norm}(0,.1) $\\
$    w_{\mathsf{userID[i]}}   \sim \textsf{Norm}(0,.1) $\\
$   \phi   \sim \mathsf{Exp}(1)$\\
\end{tabular}
\end{center}

\normalsize

We also considered adding overall aggression in before period as a
predictor, but the addition did not lead to improvement. One reason this
is interesting is that interaction of interventions with overall
aggression will turn out to be important for long-term effects.

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)   =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}} \times \mathsf{act} + act + ab_{\mathsf{userID[i]}} \times \textsf{ABS}$\\ 
$    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(0,.1) $\\
$    ab_{\mathsf{userID[i]}}    \sim  \textsf{Norm}(0,.1) $\\
$    \phi  \sim \mathsf{Exp}(1)$\\
\end{tabular}
\end{center}

\normalsize

\noindent So, ultimately, the negative binomial model without week days
or aggression before became our null model to which we considered adding
intervention count and intervention types as predictors. For now,
consider intervention type and interventions received with lag 1 (note
that if, for instance, we are interested in the impact of interventions
lag 2, we cannot condition on interventions lag 1, as this would lead to
post-treatment bias). So what we will say about lag 1 will be exactly
mirrored in the models for other lag values.

Adding intervention count, and adding intervention count with
distinguishing intervention types resulted in improvements.

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)   =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}} \times \mathsf{act} +
      i1 \times \mathsf{intL1D}$\\ 
$    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(0,.1) $\\
$    i1  \sim  \textsf{Norm}(0,.1) $\\
$    \phi  \sim \mathsf{Exp}(1)$
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)$\\ 
$    log(\lambda_i)   =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}} \times \mathsf{act} +
      i1_{\mathsf{type[i]}} \times \mathsf{intL1D}$\\ 
$    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(0,.1) $\\
$    i1_{\mathsf{type[i]}}  \sim  \textsf{Norm}(0,.1) $\\
$    \phi  \sim \mathsf{Exp}(1)$
\end{tabular}
\end{center}

\normalsize

Taking \(\phi\) parameters to be user-relative also resulted in
improvement:

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \textsf{NegativeBinomial}(\lambda_i, \phi_{\mathsf{userID[i]}} )$\\
$    log(\lambda_i)   =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} + c_{\mathsf{userID[i]}} \times \mathsf{act} + i1 \times \mathsf{intL1D}$\\
$    l_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(.05,2.3)$\\
$    a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(0,.1)$\\
$    c_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(0,.1)$ \\
$    i1_{\mathsf{type[i]}}  \sim  \textsf{Norm}(0,.1)$ \\
$    \phi_{\mathsf{userID[i]}}   \sim \mathsf{Exp}(1)$
\end{tabular}
\end{center}

\normalsize

Finally, we made a crucial move to deploy hierarchical modeling. The
general idea is that while we do keep user-specific coefficients
wherever we had them, we also do not assume that they are independent,
but rather that they come from their respective distributions, and we
estimate the general features of those distributions at the same time.
Also, for convenience this time we used treatment type indicator
variables.

\footnotesize

\begin{center}
\begin{tabular}{c}
$\mathsf{attacks}_i  \sim  \mathsf{NegativeBinomial}(\lambda_i, \phi_{\mathsf{userID[i]}} ) $\\
$log(\lambda_i)  =  l_{\mathsf{userID[i]}} +
                  a_{\mathsf{userID[i]}} \times \mathsf{attacksL1} +
                  c_{\mathsf{userID[i]}} \times \mathsf{act} + $\\
$                   + 
       i1control_{\mathsf{userID[i]}} \times  \mathsf{control} \times \mathsf{intL1D}  +$ \\$         +  i1emp_{\mathsf{userID[i]}} \times  \mathsf{emp} \times \mathsf{intL1D}  +$ \\$
              +  i1norm_{\mathsf{userID[i]}} \times  \mathsf{norm} \times \mathsf{intL1D}
                          $\\ 
$  l_{\mathsf{userID[i]}}   \sim \textsf{Norm}(\bar{l}, \bar{\sigma_l}) $\\
$  a_{\mathsf{userID[i]}}  \sim \textsf{Norm}(\bar{a}, \bar{\sigma_a}) $\\
$  c_{\mathsf{userID[i]}}  \sim \textsf{Norm}(\bar{c}, \bar{\sigma_c}) $\\
 $ i1control_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(i1controlOverall,\bar{\sigma_{i1}})$ \\
$   i1emp_{\mathsf{userID[i]}}  \sim  \textsf{Norm}(i1empOverall, \bar{\sigma_{i1}})$\\  
 $ i1norm_{\mathsf{userID[i]}}   \sim  
     \textsf{Norm}(i1normOverall, \bar{\sigma_{i1}})$\\
$     i1controlOverall  \sim  \textsf{Norm}(0,.2)$\\
$    i1empOverall   \sim  \textsf{Norm}(0,.2) $\\
$    i1normOverall   \sim  \textsf{Norm}(0,.2) $\\
$    \bar{\lambda}   \sim  \textsf{Norm}(.00001, 2.5) $\\
$    \bar{\sigma_l}  \sim  \mathsf{Exp}(1.5)$\\
$    \bar{a}  \sim \textsf{Norm}(0, .2) $\\
$    \bar{\sigma_a}  \sim  \mathsf{Exp}(5) $\\
$    \bar{c}  \sim  \mathsf{Norm}(0, .2)$\\
$    \bar{\sigma_c}  \sim \mathsf{Exp}(5) $\\
$    \bar{\sigma_{i1}}  \sim  \mathsf{Exp}(5)
$\end{tabular}
\end{center}

\normalsize

Now, let us rethink the priors. The coefficients need to be exponentiated to be understood multiplicatively. For instance, the prior for
\(i1empOverall\) is \(\textsf{Norm}(0,.2)\). To understand what priors
for the exponentiated individual coefficients this entails, we can
simulate: (1) draw 1e4 values \(i1bar\) of the mean from
\(\textsf{Norm}(0,.2)\), (2) draw 1e4 values \(i1sigmabar\) of the
standard deviation parameter from \(\mathsf{Exp(5)}\), and each time (3)
draw 1e4 parameters from \(\mathsf{Norm}(i1bar,i1sigmabar)\). The
resulting distribution looks as in Figure \ref{fig:priori1plot}. This is
still a very wide prior for the multiplicative impact of emphatetic
interventions, centered around 1, allowing even extremely unlikely
values close to 0 or 2 (upon reflection: you really should not expect a
single intervention to reduce aggression to zero or to double it in
everyone). In the cumulative model for computation reasons we will need
to narrow down the distributions, but the general point hold: prior
predictive check still ensures that they are centered around neutral
values and that they allow for a very reasonable range of values.

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/priori1plot-1} \end{center}
\caption{Simulated priors for the individual i1 coefficients, and prior for the cumulative impact model with larger input variability (hence, the prior is more narrow to eliminate unrealistically huge impact).}
\label{fig:priori1plot}
\end{figure}

\section{Model choice for the long term analysis}\label{sec:priors}

let us elaborate on how we decided to use to the seemingly fairly
complicated model we already described in the body of the paper. Once preliminary causal considerations guided our
restrictions on variable selection, we proceed by building models of
increasing complexity, and comparing them in terms of Widely Acceptable
Information Criterion (which we have already discussed). The models
differ mostly in the underlying linear formulae. For computational ease
we will here use quadratic approximations, while in the final analysis
we will deploy Hamiltionian Monte Carlo. The names are meant to decode
the model structure: the predictors are listed before dashes, whereas
interactions are listed after dashes. The comparison results are in
Table \ref{tab:comparison} and plotted in Figure
\ref{fig:modelComparisonPlot}. Notice that there are ways of building a
complicated models that do not result in improvement, as they rather
lead to expected performance lower than that of the null model.

\footnotesize

\begin{center}
\begin{tabular}{p{5cm}l}
Null & $\mu_i  = \alpha$\\
ADS & $ \mu_i  = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS}$\\
ADSIC & $ \mu_i  = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +    \beta_{\mathsf{IC}}\times \mathsf{IC}$\\
IT & $ \mu_i  = \beta_{\mathsf{group}[i]} $\\
ADSIT & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]}$\\
ADSITIC & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC}$\\
ADSITIC-ADSIC & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + $\\
& $  +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}$\\
ADSITIC-ADSIC-ADSIT & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} + $ \\
& $  +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}$\\
ADSIT-ADSIT  & $ \mu_i   = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
 \mathsf{ADS} + \beta_{\mathsf{group}[i]} $\\
ADSITIC-ADSIT-ITIC-ADSIC  & $ \mu_i   = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times \mathsf{ADS} + \beta_{\mathsf{group}[i]} + $ \\ 
& $ + 
\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}     + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}$\\
ADSITICCBS-ITIC-ADSIC & $\mu_i   = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
 \mathsf{ADS}  + \beta_{\mathsf{group}[i]} + $ \\ 
 &$ +    \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}    + \beta_{\mathsf{CBS}} \times \mathsf{CBS} +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}$  \\
Final & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  $ \\ & $ +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + $\\
&  $ + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber$\\
tooFar & $\mu_i  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + $ \\ & $ +  \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} +$ \\
 & $ + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + $ \\ & $ +  \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} + \beta_{\mathsf{CBSIC}}\times
  \mathsf{CBS} \times \mathsf{IC} \nonumber$ 
\end{tabular}
\end{center}

\normalsize

\footnotesize

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont
\begin{tabular}{lrrrrrr}
\toprule
  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
\midrule
\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.829} & \cellcolor{gray!6}{89.779} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.871} & \cellcolor{gray!6}{0.590}\\
tooFar & 1186.126 & 89.413 & 1.297 & 2.758 & 28.181 & 0.308\\
\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1188.337} & \cellcolor{gray!6}{87.058} & \cellcolor{gray!6}{3.508} & \cellcolor{gray!6}{6.184} & \cellcolor{gray!6}{24.822} & \cellcolor{gray!6}{0.102}\\
IT & 1345.087 & 144.443 & 160.259 & 132.802 & 18.104 & 0.000\\
\cellcolor{gray!6}{null} & \cellcolor{gray!6}{1345.550} & \cellcolor{gray!6}{145.960} & \cellcolor{gray!6}{160.721} & \cellcolor{gray!6}{134.243} & \cellcolor{gray!6}{18.616} & \cellcolor{gray!6}{0.000}\\
ADS & 1348.696 & 143.821 & 163.867 & 132.558 & 22.718 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1351.556} & \cellcolor{gray!6}{152.861} & \cellcolor{gray!6}{166.728} & \cellcolor{gray!6}{139.154} & \cellcolor{gray!6}{29.070} & \cellcolor{gray!6}{0.000}\\
ADSIT & 1351.646 & 145.161 & 166.817 & 133.795 & 25.032 & 0.000\\
\cellcolor{gray!6}{ADSITIC} & \cellcolor{gray!6}{1352.087} & \cellcolor{gray!6}{146.835} & \cellcolor{gray!6}{167.258} & \cellcolor{gray!6}{134.608} & \cellcolor{gray!6}{27.254} & \cellcolor{gray!6}{0.000}\\
ADSIT\_ADSIT & 1352.672 & 155.862 & 167.844 & 142.092 & 31.855 & 0.000\\
\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1352.892} & \cellcolor{gray!6}{146.359} & \cellcolor{gray!6}{168.064} & \cellcolor{gray!6}{134.313} & \cellcolor{gray!6}{26.421} & \cellcolor{gray!6}{0.000}\\
ADSITIC\_ADSIC\_ADSIT & 1355.482 & 155.522 & 170.653 & 141.405 & 33.558 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.783} & \cellcolor{gray!6}{155.273} & \cellcolor{gray!6}{170.954} & \cellcolor{gray!6}{141.128} & \cellcolor{gray!6}{33.771} & \cellcolor{gray!6}{0.000}\\
\bottomrule
\end{tabular}
\endgroup{}
\caption{Model comparison results.}
\label{tab:comparison}
\end{table}

\normalsize

\begin{figure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/fig:modelComparison-1} \end{center}
\caption{Model comparison, WAIC scores. The filled points are the in-sample deviance values. The open points are the WAIC values. The line segments represent standard errors of the WAIC scores. really want however is the standard error of the difference in WAIC
between the two models. The triangle is the difference to the top rated model, and the line segment going through it is the standard error of this difference.}
\label{fig:modelComparisonPlot}
\end{figure}

The three models that stand out differ in including \(\mathsf{CBS}\) as
a predictor. Moreover the final model includes an interaction between
treatment group and \(\mathsf{CBS}\). Adding a further interaction
between \(\mathsf{CBS}\) and \(\mathsf{IC}\) takes us too far. We will
employ the top model (\(\mathsf{Final}\)) in further analyses.

Now, to sensibly set up our priors, let's  build two models with the general structure reached. One with fairly
wide priors that one might initially think are appropriate, one with
regularizing priors. The key phenomenon to watch out for in such
contexts (slightly complex models with interactions) is that it is hard
to intuitively predict the impact of coefficient priors on prior
predictions. For this reason, we run prior predictive checks for both
models, and we select the priors that do not result in unrealistically wide prior predictions.

\begin{figure}

\begin{center}\includegraphics[width=0.8\linewidth]{ figures/fig:priorCheck-1} \includegraphics[width=0.8\linewidth]{ figures/fig:priorCheck-2} \end{center}

\caption{Prior predictive check for two different sets of priors.}
\label{fig:priors}
\end{figure}

%% \section{}
%% \label{}

%% For citations use: 
%%       \citet{<label>} ==> Jones et al. [21]
%%       \citep{<label>} ==> [21]
%%

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%%\begin{thebibliography}{00}

%% \bibitem[Author(year)]{label}
%% Text of bibliographic item

%%\bibitem[ ()]{}

%%\end{thebibliography}

%\bibliographystyle{elsarticle-num-names}
%\bibliography{attacks}

\end{document}

\endinput
%%
%% End of file `elsarticle-template-num-names.tex'.

### 2023-01-16 paperSubmission/paperSubmission1.tex
implemented Patrycja's comments

@@
 \usepackage{todonotes}
+\usepackage{rotating}
 
@@
 interventions at lags 1-7 days, and (2) to study the impact of the
-cumulative number of total interventions received as the experiment
+cumulative number of  interventions received as the experiment
 progressed, and (3) we used aggregated data to run a long term
@@
 \ref{fig:correlations}). It turns out that to avoid multicolinearity we
-cannot condition on CDS if we condition on CAS or CBS. Similarly, for
+cannot condition on CDS (comments during, standardized) if we condition on CAS (comments after, standardized) or CBS (comments before, standardized). Similarly, for
 the time series data, since activity levels in particular day slices are
@@
 (their impact on ADS is already included) impact attacks during directly
-and comments after, which impact attacks after and attacks after
+and comments after, which impact attacks after
 directly. Intervention count impacts attacks after and comments after.
@@
 Finally, in the before-and-after analysis, we put aside the time series
-element, look at aggregated counts before and after the treatment
+element, and look at aggregated counts before and after the treatment
 period, thus obtaining a more of a long-term effect analysis. Moreover,
@@
 \textsf{CBS}. This is plausible \emph{prima facie}, as which group a
-user belongs to might have impact on how the number of attacks during
-the treatment are related to the number of attacks after, the role of
+user belongs to might have an impact on how the number of attacks during
+the treatment is related to the number of attacks after, the role of
 the intervention count, and the role of comments before. Moreover, the
 levels of aggressive behavior displayed by the user during treatment
-might have impact on the role played by the intervention count.
+might have an impact on the role played by the intervention count.
 
@@
 
-\begin{figure}
+\begin{sidewaysfigure}
 
@@
 \label{fig:dailyResults}
-\end{figure}
+\end{sidewaysfigure}
 
@@
 
-let us elaborate on how we decided to use to the seemingly fairly
+Let us elaborate on how we decided to use  the seemingly fairly
 complicated model we already described in the body of the paper. Once preliminary causal considerations guided our

### 2023-01-16 paperSubmission/paperSubmission1.tex
added data collection and Marysias, needs fix

@@
 \usepackage{rotating}
+\usepackage{url}
 
@@
 
+\section{Counter-speech interventions}
+%counter-speech def
+
+The term counter-speech refers to the use of means of communication to counteract hate speech or other forms of harmful or extremist speech.
+It is a form of counter-narrative that seeks to challenge and undermine the messages of hate and extremism, and to promote alternative, positive, and inclusive narratives.
+It can be broadly defined as citizens’ response to hate speech with the purpose of stopping it and reducing its consequences \citep{leader2016dangerous, garland2020countering}.
+Hate speech is a type of speech used with the intention to insult, offend, or intimidate a person based on their identity (such as race, religion, sexual orientation, national origin, or disability) \citep{dictionary2002merriam}.
+This type of speech is often used to spread hateful or discriminatory ideas, both offline and online, and can take many forms, such as name-calling, threats, or slurs.
+Social media platforms often recommend their users to employ counter speech as a way to stop hate speech from spreading, conveniently handing the problem out to dedicated users to avoid creating new technologies or investing in manual moderation \citep{schieb2016governing}.
+
+\citet{benesch2016considerations} defined successful counter-speech in two ways.
+The first type has a favorable impact on the hateful user, for example by shifting their discourse or beliefs, and the second one impacts the whole audience of counter-speech, by shifting the norm of the conversation.
+\citep{rieger2018hate} proposed a three-layered classification of counter-speech: primary prevention, where counter-voices are being disseminated to the general public in order to educate and promote civic behavior; secondary prevention, where counter-speech is being directed at specific groups, for example, those more vulnerable to harmful effects of online hate, and tertiary prevention where counter-voices respond directly to those spreading hate.
+Our responses fulfilled all these functions, as they were publicly visible comments sent as direct responses to hateful users.
+
+When it comes to the effectiveness of online counter-speech there is just a handful of large-scale classification studies.
+One of them used a special situation in Germany, where groups that label themselves as hateful or counter-speaking talked about immigration and elections.
+Results based on analysis of 130,000 Twitter conversations suggest that counter speech can help make discussions less divisive, encourage more counter-speech and lead to fewer hateful responses \citep{garland2020countering}.
+
+Another study by \citet{ziegele2018journalistic} looked at almost 10,000 comments on the Facebook pages of 15 news organizations in Germany to investigate the patterns, determinants, and potential effects of interactive moderation.
+The authors found that the moderation style of initial comments was related to the presence of incivility in users' subsequent reply comments.
+Specifically, a sociable moderation style was associated with a decrease in incivility in reply comments, while a regulative style was associated with an increase in incivility.
+This shows that the style of counter responses can also determine their effectiveness.
+
+Moreover, the work by \citet{ziems2020racism} looked at the dynamics of the spread of racial hate during a pandemic and the role of counter speech in mitigating this spread.
+Using a hand-labeled data set of 3,355 tweets, they trained a text classifier to identify hate and counter speech tweets and conducted a longitudinal analysis of tweets and users.
+Interestingly, hateful and counter speech users interacted and engaged extensively with one another, rather than staying in isolated, polarized communities.
+Results revealed that Twitter users were more likely to become hateful after being exposed to hateful content and that counter speech messages may discourage users from becoming hateful, suggesting that consistent counter speech could be a potential solution for effects of hate on social media platforms.
+
+ \citep{xie2011social} examined the influence of committed minorities, and looked at how a small group of people with an opinion different from the majority can quickly change the whole group's opinion.
+They found that if more than 10 percent of the group expresses another viewpoint, there is a dramatic decrease in the time taken for the entire population to adopt it.
+In other words, a relatively small group of committed individuals can have a significant impact on the opinion of the majority.
+
+Similarly, \citep{schieb2016governing} used a computer simulation to study whether counter-speech can curb hate speech on Facebook.
+They found that even a small group of users speaking out against hate can influence a much larger group, as long as there are enough people in the audience who do not hold extreme opinions.
+They also emphasized the potential negative effects of counter-voices, especially when they do not hold to the same standards of civic discussion but instead act in an authoritative or mocking way towards those expressing extremist ideologies.
+
+Although some studies suggest censorship and elimination of hateful content to be a more effective strategy of toxicity reduction \citep{alvarez2018normative}, it also also collide with civil liberties and diffuse rather than reduce hate \citep{chandrasekharan2017you}.
+Therefore counter-speech seems to be a golden means for reducing antisocial behavior while preserving civil liberties.
+
+In our study, we have employed counter-speaking strategies to see whether they can be applied to a slightly different phenomenon, namely personal attacks.
+Personal attacks are instances of speech that are intended to hurt, offend, or belittle a specific person or group.
+This can include name-calling, insults, or other types of derogatory language that is directed at an individual or group \citep{bilewicz2021artificial}.
+While personal attacks and hate speech can sometimes overlap, the main difference between the two is that personal attacks are focused on an individual or a specific group of people, whereas hate speech is aimed at an entire group of people based on their identity.
+
+% we have previously studied the effectiveness of counter-speech in lowering the use of personal attacks on Reddit using an automatic intervention system  \citep{bilewicz2021artificial}.
+
+%In this follow-up study we wanted to see whether
+
+%\citet{benesch2016considerations} recommend counter-speech strategies based on empathy and affiliation, employing humor, warning of consequences of such behavior, labeling and shaming.
+%Although censorship and hateful content elimination has shown to be a more effective strategy of toxicity reduction @alvarez2018normative, it can also collide with civil liberties and diffuse rather than reduce hate @chandrasekharan2017you.
+Therefore counter-speech seems to be a golden mean for reducing antisocial behavior while preserving civil liberties.
+Although counter-speech can be an effective strategy for toxic discourse mitigation, it usually occurs as a spontaneous act, as it is determined by personal motivations of the counter-speaking party.
+For example, \citet{brauer2010descriptive} found that being personally implicated by a counter-normative behavior was a primary determinant of the bystander reaction.
+
+Apart from that, the more public the space, the less likely it is that someone will step up, as studies on bystander interventions consistently show that presence of other people in critical situations reduces the probability of assistance from bystanders \citep{fischer2011bystander}.
+%It is much less likely to happen in natural settings then in a laboratory.
+@?
+
+Moreover, even if a bystander decides to react, they will not necessarily choose the most effective strategy, which can lead to potentially undesirable side-effects.
+For instance,  counter-voices that do not hold up to civic standards themselves but act in an authoritative manner or mock those falling for extremist ideologies, can actually strengthen the underlying attitudes \citep{ziegele2018journalistic, schieb2016governing, legault2011ironic}.
+%empathy here somewhere
+
+The issue of low bystander reactivity has been addressed in our study by engaging volunteers personally committed to lowering online violence, and creating an opportunity structure for quick response, by real-time notifications about the occurrences of personal attacks that they should respond to (see however our section on volunteer engagement for a discussion of difficulties with this strategy).
+
+To maximize the potential impact of our interventions and to minimize  accidental instigation of more verbal aggression, we decided to educate the volunteers on scientifically grounded strategies for normative influence and persuasive messaging.
+Let us elaborate.
+ Social norms are agreed to be powerful determinants of human behavior. 
+According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common}, \citep{cialdini1990focus}.
+A good deal of studies have found that perceptions of what others are doing causes us to behave similarly.
+Norms can be applied to exert persuasive impact, for example to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.
+
+%Researchers have repeatedly found that perceptions of what others are doing influences subjects to behave similarly, for example when it comes to choosing consumer product (venkatesen, 1966), or looking at the sky (milgram, bichman, berkowitz, 1969).
+
+%Reasons why social norms have such strong influence on peoples decisions, attitudes, and the way they express them are still disputed. %cytowanie
+
+Some scholars propose that perceived social norms serve as shortcuts helping us quickly adapt to new environments \citep{cialdini1990focus}.
+Others say that we are only motivated by norms we have internalized during socialization, so the normative influence can only be exerted if the norm resonates with our internal value system \citep{morris2018common}.
+Focus Theory of Normative Conduct \citep{kallgren2000focus} is a psychological, theoretical framework used for understanding best conditions and practices for exerting normative influence.
+Its main assumption is that norms that are focal in attention are likely to influence behavior.
+%explain on an example cialdini experiment
+To achieve persuasive impact a distinction between two types of norms has to be made.
+While it might sound strange to talk about desriptive norms, this is the way the terminology in the field developed, so we will keep using such terms.
+A descriptive norm refers to what is typically done, by showing  examples of  normal behavior in a given situation, and injunctive or prescriptive norm refers to what is commonly approved, such the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.
+A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while injuctive norm motivates by informing which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.
+
+%This has important implications for normative influence practitioners, as the same behavior can be prescriptively normative and descriptively not normative, and vice versa.
+In other words, something may be the right thing to do but few people actually do it  \citep{brauer2010descriptive}.
+%truism. say more
+
+The positive influence of injunctive and descriptive norms on unwanted social behavior was first presented in a study on littering in public spaces conducted by \citet{cialdini1990focus}.
+Study subjects were exposed to either descriptive or injunctive anti-littering norm, and the impact on the littering behavior was observed.
+In the descriptive condition the subjects were exposed to a clean or littered environment, serving as a proof of choices made by others.
+In the injunctive condition participants received messages stating the anti-littering norm.
+
+Injunctive messages directly asking not to litter had significantly reduced littering, and subjects littered more in a highly littered environment, and littered less in a clean environment although these effects were not statistically significant.
+%which ones
+Although seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.
+
+%Some of these results were replicated \citep {berquisr2021replicating} \citep {berger2016norm} %say more
+
+A descriptive norm can be also evoked by providing a written information about what others usually do.
+\citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about reuse of hotel towels (“the majority of guests reuse their towels”).
+This strategy has been proven superior to traditional appeals focusing on environmental protection.
+Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to the so-called local norms.
+
+The information about how others think and behave can also have an impact on prejudice and its expression.
+For example, positive information about the racial beliefs of others produced stereotype change in message recipients \citep{stangor2001changing}, and public expression of prejudice, and reactions to hostile jokes were highly correlated with social approval of these expressions \citep{crandall2002social}.
+
+When it comes to the online realm, group norm promotion and social sanctioning of online racist harassment resulted in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male).
+In other words, sending direct, counter-speech messages to users with similar identities,  resulted in a decrease in their use of hate speech on Twitter \citep{munger2017tweetment}.
+Moreover, in a study conducted by \citet{bilewicz2021artificial}, a bot disguised as a Reddit user, equipped with normative and empathetic interventions, significantly decreased the number of personal attacks generated in this forum.
+In addition, types of statements made by people in online political discussions influenced the way others expressed their opinions \citep{price2006normative}, and the expression of online hate-speech in  \citep{alvarez2018normative} was strongly dependant on the amount of hate-speech already present in a given environment.
+
+The context of online interactions can also contribute to the spread of counter-normative behaviors.
+For example, negative mood and prior exposition to troll content was the strongest predictor for trolling behavior in \citep{cheng2017anyone}.
+
+%On the other hand, when it comes to pro-environmental choices, people are more likely to conform to information about what others don't do rather than what others do, building on an evolutionary predisposition to more urgently attend to negative rather than positive stimuli @bergquist2019and.
+%Stosujemy normatywne i empatyczne interwencje - w literaturze te mechanizmy psychologiczne są opisane jako skuteczne w obniżaniu agresji - cytujemy literature. 
+%W jakich innych badaniach counter speech wykorzystywali empatie i norme - nas (Bilewicz study), Munger, Roma racist, itp..+opisać jak nasze obecne badanie sie rozni - po raz pierwszy wykorztstyujemy collective intelligence ludzie + AI
+%describe hypothesis i give argument behind the hypothesis
+
+ In line with this discussion, for the purpose of our study we have distinguished two types of counter responses to personal attacks: ``empathetic'' and ``normative''.
+The empathetic approach is aimed at countering the so-called desensitization to violence.
+It is a very dangerous process, finally leading to dehumanization of stigmatized groups.
+%Unfortunately, the impersonal structure of online space makes it very easy for the desensitization to occur.
+ Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice.
+By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.
+
+The normative approach stems from the  aforementioned psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted.
+Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms - what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.
+
+%To put it in an example, there is a general rule that we should not litter in public spaces (injunctive norm), but we are much more likely to leave our garbage, when there’s evidence that other people did not follow the rule - the space is littered with trash (descriptive norm).
+We hope that our interventions will provide constructive social cues about acceptable forms of communication and influence the way users converse in a given community.
+
+%Another phenomenon illustrating the power of the context is the bystander effect.
+The bystander theory  states that individuals are less likely to offer help to a victim when there are other people present - the greater the number of bystanders, the less likely it is that one of them will help.
+But it takes only one helpful volunteer for others to follow.
+The study by Machackova and others (2015) have shown the bystander effect also takes place online.
+and a more recent study has shown that ordinary people, with no habit of trolling, will engage in trolling behavior under proper circumstances.
+
 \section{Data analysis}\label{sec{analysis}}
 
-\subsection{Exploration and data}\label{subsec:data-and-exploration}
-
-For the duration of the project we selected 486 Reddit users\todo{how?} and tracked
-their activity (with some breaks resulting from API restrictions and
-technical issues, which were mostly sorted out in the observation
-period), starting on 2020-03-09, beginning the intervention period on
-2020-07-08, leading to a further observation period starting on
-2020-09-09 and ending on 2020-11-20. The time series of attacks observed
+\subsection{Data collection and exploration}\label{subsec:data-and-exploration}
+
+We conducted a 6-months field experiment in a digital setting conducted on a popular Q\&A and news forum, Reddit (\url{www.reddit.com}).
+We formed treatment and control groups based on three main criteria:
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+ \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct approximately 10 interventions a day.
+So, we needed approximately 200 attacks daily generated by the treatment groups.
+\item We first conducted a preliminary identification of users who regularly attack others to test interventions on them.
+The key issue here is that such users are not too common, and attacks are rather rare among other users.
+If instead we simply picked a random group of users with the intention of intervening in response to their online attacks, the sample size would have to be extremely large, and still the chance of observing enough attacks to draw any interesing conclusions from the reactions to our interventions would be low.
+Thus, we need to keep in mind that the group studied is not just users of Reddit, but rather users who for a least a few weeks tended to systematically attack others.
+
+\item The identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
+ \end{enumerate}
+
+\noindent The user identification process was as follows:
+
+\renewcommand{\labelenumii}{\Roman{enumii}}
+ \begin{enumerate}
+   \item First, we obtained 1 week of real-time umoderated data from Reddit (February 15-22.
+2020), unmoderated data from Reddit.
+The content was downloaded from the data stream provided by pushshift.io.
+   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify those users who attacked others at least once within this period.
+This resulted in the identification of 93966 users.
+   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string).
+This resulted in the removal of 388 users, thus 93578 were left on our list.
+   \item Next, we removed those users who generated only 1 personal attack during the week.
+This step resulted in the removal of users generating the number of personal attacks below the third quartile (Q3).
+20124 users were left in our group.
+   \item We removed users who generated less than 14 comments during this week.
+It was not a lot, since 14 comments were below the 1st quartile (Q1: 28 comments), but such a criterion moved us in the direction of identification of those who are relatively active.
+This resulted in the removal of 2192 users, so 17932 were left.
+   \item We discarded users whose personal attacks to all comments ratio was below 2\%.
+This means the inclusion in the sample of users above the 1st quartile of personal attacks to all comments ratio.
+4422 users were removed, leaving us with a group of 13510.
+   \item The next step of the process begun on  March 9, 2020, and lasted until May 5, 2020 (9 weeks).
+During this period we have monitored the activity of the identified group of 13510 users and applied further selection criteria to make sure we select those who were regularly active and attacked other users.
+   \item The period of monitoring was divided into weeks.
+We have discarded those weeks during which technical difficulties occurred with \linebreak \url{pushshift.io} (resulting in missing data).
+So we have taken into consideration only 6 full weeks for the period.
+   \item Users who generated at least 1 attack per week during 5 out of 6 weeks were identified.
+Initially, we planned to restrict the list to only those users who generate at least 1 attack during each week (6/6), but such a restrictive criterion led to only 255 users left, which was not enough for the study.
+The less restrictive criterion (at least 1 attack generated during 5/6 weeks) resulted in 694 people.
+   \item Next, we calculated the daily average number of personal attacks generated by the resulting group (357 attacks per day).
+   \item Knowing that we need around 200 attacks per day  per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic).
+The rest was delegated as a control group (304 users).
+   \item Some of those were further removed as t data visualisation  and content inspection helped to identify them as bots, or they ceased their activity during the period.
+We were left with the data on 440 users.
+
+ \end{enumerate}
+
+The duration of the experiment, 6 months, was divided into three 2-months periods.
+The first two months served as a monitoring period to properly select groups and establish baselines.
+The next 2 months served as a treatment period, during which groups received counter-speech comments from volunteers in response to personal attacks detected by the Artificial Intelligence-based system.
+The last 2-months served as the post-treatment monitoring period to gather the data needed to evaluate the effectiveness of interventions.
+We started with an observation period on March 9, 2020, leading to  the intervention period starting on July 8, 2020,  following with  a further observation period starting on September 9, 2020,
+and ending on November 20, 2020. The time series of attacks observed
 and of interventions conducted can be inspected in Figure
@@
 
+%update when done
+
+\begin{thebibliography}{91}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+\providecommand{\url}[1]{\texttt{#1}}
+\providecommand{\href}[2]{#2}
+\providecommand{\path}[1]{#1}
+\providecommand{\DOIprefix}{doi:}
+\providecommand{\ArXivprefix}{arXiv:}
+\providecommand{\URLprefix}{URL: }
+\providecommand{\Pubmedprefix}{pmid:}
+\providecommand{\doi}[1]{\href{http://dx.doi.org/#1}{\path{#1}}}
+\providecommand{\Pubmed}[1]{\href{pmid:#1}{\path{#1}}}
+\providecommand{\bibinfo}[2]{#2}
+\ifx\xfnm\relax \def\xfnm[#1]{\unskip,\space#1}\fi
+%Type = Misc
+\bibitem[{Laub(2019)}]{Zachary_hate}
+\bibinfo{author}{Z.~Laub}, \bibinfo{title}{Hate {Speech} on {Social} {Media}:
+  {Global} {Comparisons}}, \bibinfo{year}{2019}. \URLprefix
+  \url{https://www.cfr.org/backgrounder/hate-speech-social-media-global-comparisons}.
+%Type = Article
+\bibitem[{Sorrentino et~al.(2019)Sorrentino, Baldry, Farrington, and
+  Blaya}]{sorrentino2019epidemiology}
+\bibinfo{author}{A.~Sorrentino}, \bibinfo{author}{A.~C. Baldry},
+  \bibinfo{author}{D.~P. Farrington}, \bibinfo{author}{C.~Blaya},
+\newblock \bibinfo{title}{Epidemiology of cyberbullying across europe:
+  Differences between countries and genders},
+\newblock \bibinfo{journal}{Educational Sciences: Theory \& Practice}
+  \bibinfo{volume}{19} (\bibinfo{year}{2019}).
+%Type = Misc
+\bibitem[{Vogels(2021)}]{vogels_state_2021}
+\bibinfo{author}{E.~A. Vogels}, \bibinfo{title}{The {State} of {Online}
+  {Harassment}}, \bibinfo{year}{2021}. \URLprefix
+  \url{https://www.pewresearch.org/internet/2021/01/13/the-state-of-online-harassment/}.
+%Type = Article
+\bibitem[{Barlett et~al.(2021)Barlett, Simmers, Roth, and
+  Gentile}]{barlett2021comparing}
+\bibinfo{author}{C.~P. Barlett}, \bibinfo{author}{M.~M. Simmers},
+  \bibinfo{author}{B.~Roth}, \bibinfo{author}{D.~Gentile},
+\newblock \bibinfo{title}{Comparing cyberbullying prevalence and process before
+  and during the covid-19 pandemic},
+\newblock \bibinfo{journal}{The Journal of Social Psychology}
+  (\bibinfo{year}{2021}) \bibinfo{pages}{1--11}.
+%Type = Misc
+\bibitem[{Grant(2021)}]{grant_2021}
+\bibinfo{author}{J.~Grant}, \bibinfo{title}{Australia’s esafety commissioner
+  targets abuse online as covid-19 supercharges cyberbullying | the
+  strategist}, \bibinfo{year}{2021}. \URLprefix
+  \url{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}.
+%Type = Misc
+\bibitem[{L1ght(2020)}]{noauthor_l1ght_2020}
+\bibinfo{author}{L1ght}, \bibinfo{title}{L1ght releases groundbreaking report
+  on corona-related hate speech and online toxicity}, \bibinfo{year}{2020}.
+  \URLprefix
+  \url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}.
+%Type = Misc
+\bibitem[{Bhattacharya(2021)}]{bhattacharya}
+\bibinfo{author}{A.~Bhattacharya}, \bibinfo{title}{How {Covid}-19 lockdowns
+  weakened {Facebook}'s content moderation algorithms}, \bibinfo{year}{2021}.
+  \URLprefix
+  \url{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}.
+%Type = Article
+\bibitem[{Gerrard(2020)}]{gerrard2020covid19}
+\bibinfo{author}{Y.~Gerrard},
+\newblock \bibinfo{title}{<? covid19?> the covid-19 mental health content
+  moderation conundrum},
+\newblock \bibinfo{journal}{Social Media+ Society} \bibinfo{volume}{6}
+  (\bibinfo{year}{2020}) \bibinfo{pages}{2056305120948186}.
+%Type = Article
+\bibitem[{Yang et~al.(2021)Yang, Wang, Sun, Xu, Wang, Chen, Yu, Zhang, Zhu, Dai
+  et~al.}]{yang2021consequences}
+\bibinfo{author}{B.~Yang}, \bibinfo{author}{B.~Wang}, \bibinfo{author}{N.~Sun},
+  \bibinfo{author}{F.~Xu}, \bibinfo{author}{L.~Wang},
+  \bibinfo{author}{J.~Chen}, \bibinfo{author}{S.~Yu},
+  \bibinfo{author}{Y.~Zhang}, \bibinfo{author}{Y.~Zhu},
+  \bibinfo{author}{T.~Dai}, et~al.,
+\newblock \bibinfo{title}{The consequences of cyberbullying and traditional
+  bullying victimization among adolescents: gender differences in psychological
+  symptoms, self-harm and suicidality},
+\newblock \bibinfo{journal}{Psychiatry research} \bibinfo{volume}{306}
+  (\bibinfo{year}{2021}) \bibinfo{pages}{114219}.
+%Type = Article
+\bibitem[{Hinduja and Patchin(2010)}]{hinduja2010bullying}
+\bibinfo{author}{S.~Hinduja}, \bibinfo{author}{J.~W. Patchin},
+\newblock \bibinfo{title}{Bullying, cyberbullying, and suicide},
+\newblock \bibinfo{journal}{Archives of suicide research} \bibinfo{volume}{14}
+  (\bibinfo{year}{2010}) \bibinfo{pages}{206--221}.
+%Type = Article
+\bibitem[{Alhujailli et~al.(2020)Alhujailli, Karwowski, Wan, and
+  Hancock}]{alhujailli2020affective}
+\bibinfo{author}{A.~Alhujailli}, \bibinfo{author}{W.~Karwowski},
+  \bibinfo{author}{T.~T. Wan}, \bibinfo{author}{P.~Hancock},
+\newblock \bibinfo{title}{Affective and stress consequences of cyberbullying},
+\newblock \bibinfo{journal}{Symmetry} \bibinfo{volume}{12}
+  (\bibinfo{year}{2020}) \bibinfo{pages}{1536}.
+%Type = Article
+\bibitem[{Kowalski and Limber(2013)}]{kowalski2013psychological}
+\bibinfo{author}{R.~M. Kowalski}, \bibinfo{author}{S.~P. Limber},
+\newblock \bibinfo{title}{Psychological, physical, and academic correlates of
+  cyberbullying and traditional bullying},
+\newblock \bibinfo{journal}{Journal of adolescent health} \bibinfo{volume}{53}
+  (\bibinfo{year}{2013}) \bibinfo{pages}{S13--S20}.
+%Type = Article
+\bibitem[{Lee and Leets(2002)}]{lee2002persuasive}
+\bibinfo{author}{E.~Lee}, \bibinfo{author}{L.~Leets},
+\newblock \bibinfo{title}{Persuasive storytelling by hate groups online:
+  Examining its effects on adolescents},
+\newblock \bibinfo{journal}{American behavioral scientist} \bibinfo{volume}{45}
+  (\bibinfo{year}{2002}) \bibinfo{pages}{927--957}.
+%Type = Article
+\bibitem[{Williams(2019)}]{williams2019hatred}
+\bibinfo{author}{M.~Williams},
+\newblock \bibinfo{title}{Hatred behind the screens: A report on the rise of
+  online hate speech}  (\bibinfo{year}{2019}).
+%Type = Article
+\bibitem[{Fink(2018)}]{fink2018dangerous}
+\bibinfo{author}{C.~Fink},
+\newblock \bibinfo{title}{Dangerous speech, anti-muslim violence, and facebook
+  in myanmar},
+\newblock \bibinfo{journal}{Journal of International Affairs}
+  \bibinfo{volume}{71} (\bibinfo{year}{2018}) \bibinfo{pages}{43--52}.
+%Type = Article
+\bibitem[{Soral et~al.(2018)Soral, Bilewicz, and Winiewski}]{soral2018exposure}
+\bibinfo{author}{W.~Soral}, \bibinfo{author}{M.~Bilewicz},
+  \bibinfo{author}{M.~Winiewski},
+\newblock \bibinfo{title}{Exposure to hate speech increases prejudice through
+  desensitization},
+\newblock \bibinfo{journal}{Aggressive behavior} \bibinfo{volume}{44}
+  (\bibinfo{year}{2018}) \bibinfo{pages}{136--146}.
+  \DOIprefix\doi{10.1002/ab.21737}.
+%Type = Article
+\bibitem[{{\'A}lvarez-Benjumea and Winter(2018)}]{alvarez2018normative}
+\bibinfo{author}{A.~{\'A}lvarez-Benjumea}, \bibinfo{author}{F.~Winter},
+\newblock \bibinfo{title}{Normative change and culture of hate: An experiment
+  in online environments},
+\newblock \bibinfo{journal}{European Sociological Review} \bibinfo{volume}{34}
+  (\bibinfo{year}{2018}) \bibinfo{pages}{223--237}.
+  \DOIprefix\doi{10.2139/ssrn.3126089}.
+%Type = Article
+\bibitem[{Williams et~al.(2020)Williams, Burnap, Javed, Liu, and
+  Ozalp}]{williams2020hate}
+\bibinfo{author}{M.~L. Williams}, \bibinfo{author}{P.~Burnap},
+  \bibinfo{author}{A.~Javed}, \bibinfo{author}{H.~Liu},
+  \bibinfo{author}{S.~Ozalp},
+\newblock \bibinfo{title}{Hate in the machine: anti-black and anti-muslim
+  social media posts as predictors of offline racially and religiously
+  aggravated crime},
+\newblock \bibinfo{journal}{The British Journal of Criminology}
+  \bibinfo{volume}{60} (\bibinfo{year}{2020}) \bibinfo{pages}{93--117}.
+  \DOIprefix\doi{10.1093/bjc/azz049}.
+%Type = Article
+\bibitem[{Urbaniak et~al.(2022)Urbaniak, Ptaszy{\'n}ski, Tempska, Leliwa,
+  Brochocki, and Wroczy{\'n}ski}]{urbaniak2022personal}
+\bibinfo{author}{R.~Urbaniak}, \bibinfo{author}{M.~Ptaszy{\'n}ski},
+  \bibinfo{author}{P.~Tempska}, \bibinfo{author}{G.~Leliwa},
+  \bibinfo{author}{M.~Brochocki}, \bibinfo{author}{M.~Wroczy{\'n}ski},
+\newblock \bibinfo{title}{Personal attacks decrease user activity in social
+  networking platforms},
+\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{126}
+  (\bibinfo{year}{2022}) \bibinfo{pages}{106972}.
+%Type = Article
+\bibitem[{Tworek(2021)}]{tworek2021fighting}
+\bibinfo{author}{H.~J. Tworek},
+\newblock \bibinfo{title}{Fighting hate with speech law: Media and german
+  visions of democracy},
+\newblock \bibinfo{journal}{The Journal of Holocaust Research}
+  \bibinfo{volume}{35} (\bibinfo{year}{2021}) \bibinfo{pages}{106--122}.
+%Type = Article
+\bibitem[{Trengove et~al.(2022)Trengove, Kazim, Almeida, Hilliard, Zannone, and
+  Lomas}]{trengove2022critical}
+\bibinfo{author}{M.~Trengove}, \bibinfo{author}{E.~Kazim},
+  \bibinfo{author}{D.~Almeida}, \bibinfo{author}{A.~Hilliard},
+  \bibinfo{author}{S.~Zannone}, \bibinfo{author}{E.~Lomas},
+\newblock \bibinfo{title}{A critical review of the online safety bill},
+\newblock \bibinfo{journal}{Patterns}  (\bibinfo{year}{2022})
+  \bibinfo{pages}{100544}.
+%Type = Misc
+\bibitem[{cnb(2020)}]{cnbc_2020}
+\bibinfo{title}{Facebook frustrates advertisers as boycott over hate speech
+  kicks off}, \bibinfo{year}{2020}. \URLprefix
+  \url{https://www.cnbc.com/2020/07/01/facebook-frustrates-advertisers-as-boycott-over-hate-speech-kicks-off.html}.
+%Type = Misc
+\bibitem[{Newton(2013)}]{newton_2013}
+\bibinfo{author}{C.~Newton}, \bibinfo{title}{Killer app: Why do anonymous
+   networks keep leading to suicides?}, \bibinfo{year}{2013}.
+  \URLprefix
+  \url{https://www.theverge.com/2013/9/17/4740902/no-good-answers-why-didnt-ask-fm-learn-from-the-formspring-suicides}.
+%Type = Misc
+\bibitem[{Failory(2022)}]{failory_2022}
+\bibinfo{author}{Failory}, \bibinfo{title}{Yik yak's shut down: Why did the
+  location-based app failed?}, \bibinfo{year}{2022}. \URLprefix
+  \url{https://www.failory.com/cemetery/yik-yak}.
+%Type = Misc
+\bibitem[{los(2021)}]{los_angeles_times_2021}
+\bibinfo{title}{A teen who was bullied on snapchat died. his mom is suing to
+  hold social media liable}, \bibinfo{year}{2021}. \URLprefix
+  \url{https://www.latimes.com/business/story/2021-05-10/lawsuit-snap-teen-suicide-yolo-lmk}.
+%Type = Misc
+\bibitem[{Seifert(2013)}]{seifert_2013}
+\bibinfo{author}{D.~Seifert}, \bibinfo{title}{Social question and answer site
+  formspring to shut down on March 31st}, \bibinfo{year}{2013}. \URLprefix
+  \url{https://www.theverge.com/2013/3/15/4110196/social-question-answer-site-formspring-shut-down-march-31st}.
+%Type = Article
+\bibitem[{MacAvaney et~al.(2019)MacAvaney, Yao, Yang, Russell, Goharian, and
+  Frieder}]{macavaney2019hate}
+\bibinfo{author}{S.~MacAvaney}, \bibinfo{author}{H.-R. Yao},
+  \bibinfo{author}{E.~Yang}, \bibinfo{author}{K.~Russell},
+  \bibinfo{author}{N.~Goharian}, \bibinfo{author}{O.~Frieder},
+\newblock \bibinfo{title}{Hate speech detection: Challenges and solutions},
+\newblock \bibinfo{journal}{PloS one} \bibinfo{volume}{14}
+  (\bibinfo{year}{2019}) \bibinfo{pages}{e0221152}.
+%Type = Inproceedings
+\bibitem[{Schmidt and Wiegand(2017)}]{schmidt2017survey}
+\bibinfo{author}{A.~Schmidt}, \bibinfo{author}{M.~Wiegand},
+\newblock \bibinfo{title}{A survey on hate speech detection using natural
+  language processing},
+\newblock in: \bibinfo{booktitle}{Proceedings of the fifth international
+  workshop on natural language processing for social media},
+  \bibinfo{year}{2017}, pp. \bibinfo{pages}{1--10}.
+%Type = Article
+\bibitem[{Jordan and Mitchell(2015)}]{jordan2015machine}
+\bibinfo{author}{M.~I. Jordan}, \bibinfo{author}{T.~M. Mitchell},
+\newblock \bibinfo{title}{Machine learning: Trends, perspectives, and
+  prospects},
+\newblock \bibinfo{journal}{Science} \bibinfo{volume}{349}
+  (\bibinfo{year}{2015}) \bibinfo{pages}{255--260}.
+%Type = Article
+\bibitem[{LeCun et~al.(2015)LeCun, Bengio, and Hinton}]{lecun2015deep}
+\bibinfo{author}{Y.~LeCun}, \bibinfo{author}{Y.~Bengio},
+  \bibinfo{author}{G.~Hinton},
+\newblock \bibinfo{title}{Deep learning},
+\newblock \bibinfo{journal}{nature} \bibinfo{volume}{521}
+  (\bibinfo{year}{2015}) \bibinfo{pages}{436--444}.
+%Type = Article
+\bibitem[{Sejnowski(2020)}]{sejnowski2020unreasonable}
+\bibinfo{author}{T.~J. Sejnowski},
+\newblock \bibinfo{title}{The unreasonable effectiveness of deep learning in
+  artificial intelligence},
+\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
+  \bibinfo{volume}{117} (\bibinfo{year}{2020}) \bibinfo{pages}{30033--30038}.
+%Type = Inproceedings
+\bibitem[{Binns et~al.(2017)Binns, Veale, Van~Kleek, and
+  Shadbolt}]{binns2017like}
+\bibinfo{author}{R.~Binns}, \bibinfo{author}{M.~Veale},
+  \bibinfo{author}{M.~Van~Kleek}, \bibinfo{author}{N.~Shadbolt},
+\newblock \bibinfo{title}{Like trainer, like bot? inheritance of bias in
+  algorithmic content moderation},
+\newblock in: \bibinfo{booktitle}{International conference on social
+  informatics}, \bibinfo{organization}{Springer}, \bibinfo{year}{2017}, pp.
+  \bibinfo{pages}{405--415}.
+%Type = Article
+\bibitem[{Geva et~al.(2019)Geva, Goldberg, and Berant}]{geva2019we}
+\bibinfo{author}{M.~Geva}, \bibinfo{author}{Y.~Goldberg},
+  \bibinfo{author}{J.~Berant},
+\newblock \bibinfo{title}{Are we modeling the task or the annotator? an
+  investigation of annotator bias in natural language understanding datasets},
+\newblock \bibinfo{journal}{arXiv preprint arXiv:1908.07898}
+  (\bibinfo{year}{2019}).
+%Type = Article
+\bibitem[{Mehrabi et~al.(2021)Mehrabi, Morstatter, Saxena, Lerman, and
+  Galstyan}]{mehrabi2021survey}
+\bibinfo{author}{N.~Mehrabi}, \bibinfo{author}{F.~Morstatter},
+  \bibinfo{author}{N.~Saxena}, \bibinfo{author}{K.~Lerman},
+  \bibinfo{author}{A.~Galstyan},
+\newblock \bibinfo{title}{A survey on bias and fairness in machine learning},
+\newblock \bibinfo{journal}{ACM Computing Surveys (CSUR)} \bibinfo{volume}{54}
+  (\bibinfo{year}{2021}) \bibinfo{pages}{1--35}.
+%Type = Inproceedings
+\bibitem[{Sap et~al.(2019)Sap, Card, Gabriel, Choi, and Smith}]{sap_risk_2019}
+\bibinfo{author}{M.~Sap}, \bibinfo{author}{D.~Card},
+  \bibinfo{author}{S.~Gabriel}, \bibinfo{author}{Y.~Choi},
+  \bibinfo{author}{N.~A. Smith},
+\newblock \bibinfo{title}{The {Risk} of {Racial} {Bias} in {Hate} {Speech}
+  {Detection}},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 57th {Annual} {Meeting} of
+  the {Association} for {Computational} {Linguistics}},
+  \bibinfo{publisher}{Association for Computational Linguistics},
+  \bibinfo{address}{Florence, Italy}, \bibinfo{year}{2019}, pp.
+  \bibinfo{pages}{1668--1678}. \URLprefix
+  \url{https://aclanthology.org/P19-1163}.
+  \DOIprefix\doi{10.18653/v1/P19-1163}.
+%Type = Misc
+\bibitem[{Vanian(2019)}]{jigsaw2019}
+\bibinfo{author}{J.~Vanian}, \bibinfo{title}{Google's {Hate} {Speech}
+  {Detection} {A}.{I}. {Has} a {Racial} {Bias} {Problem}},
+  \bibinfo{year}{2019}. \URLprefix
+  \url{https://fortune.com/2019/08/16/google-jigsaw-perspective-racial-bias/}.
+%Type = Inproceedings
+\bibitem[{Gr{\"o}ndahl et~al.(2018)Gr{\"o}ndahl, Pajola, Juuti, Conti, and
+  Asokan}]{grondahl2018all}
+\bibinfo{author}{T.~Gr{\"o}ndahl}, \bibinfo{author}{L.~Pajola},
+  \bibinfo{author}{M.~Juuti}, \bibinfo{author}{M.~Conti},
+  \bibinfo{author}{N.~Asokan},
+\newblock \bibinfo{title}{All you need is" love" evading hate speech
+  detection},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 11th ACM workshop on
+  artificial intelligence and security}, \bibinfo{year}{2018}, pp.
+  \bibinfo{pages}{2--12}.
+%Type = Article
+\bibitem[{Rosa et~al.(2019)Rosa, Pereira, Ribeiro, Ferreira, Carvalho,
+  Oliveira, Coheur, Paulino, Sim{\~a}o, and Trancoso}]{rosa2019automatic}
+\bibinfo{author}{H.~Rosa}, \bibinfo{author}{N.~Pereira},
+  \bibinfo{author}{R.~Ribeiro}, \bibinfo{author}{P.~C. Ferreira},
+  \bibinfo{author}{J.~P. Carvalho}, \bibinfo{author}{S.~Oliveira},
+  \bibinfo{author}{L.~Coheur}, \bibinfo{author}{P.~Paulino},
+  \bibinfo{author}{A.~V. Sim{\~a}o}, \bibinfo{author}{I.~Trancoso},
+\newblock \bibinfo{title}{Automatic cyberbullying detection: A systematic
+  review},
+\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{93}
+  (\bibinfo{year}{2019}) \bibinfo{pages}{333--345}.
+%Type = Article
+\bibitem[{Yin and Zubiaga(2021)}]{yin2021towards}
+\bibinfo{author}{W.~Yin}, \bibinfo{author}{A.~Zubiaga},
+\newblock \bibinfo{title}{Towards generalisable hate speech detection: a review
+  on obstacles and solutions},
+\newblock \bibinfo{journal}{PeerJ Computer Science} \bibinfo{volume}{7}
+  (\bibinfo{year}{2021}) \bibinfo{pages}{e598}.
+%Type = Inproceedings
+\bibitem[{Wu et~al.(2019)Wu, Ribeiro, Heer, and Weld}]{wu2019errudite}
+\bibinfo{author}{T.~Wu}, \bibinfo{author}{M.~T. Ribeiro},
+  \bibinfo{author}{J.~Heer}, \bibinfo{author}{D.~S. Weld},
+\newblock \bibinfo{title}{Errudite: Scalable, reproducible, and testable error
+  analysis},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 57th Annual Meeting of the
+  Association for Computational Linguistics}, \bibinfo{year}{2019}, pp.
+  \bibinfo{pages}{747--763}.
+%Type = Article
+\bibitem[{Lipton and Steinhardt(2019)}]{lipton2019troubling}
+\bibinfo{author}{Z.~C. Lipton}, \bibinfo{author}{J.~Steinhardt},
+\newblock \bibinfo{title}{Troubling trends in machine learning scholarship:
+  Some ml papers suffer from flaws that could mislead the public and stymie
+  future research.},
+\newblock \bibinfo{journal}{Queue} \bibinfo{volume}{17} (\bibinfo{year}{2019})
+  \bibinfo{pages}{45--77}.
+%Type = Inproceedings
+\bibitem[{Musgrave et~al.(2020)Musgrave, Belongie, and
+  Lim}]{musgrave2020metric}
+\bibinfo{author}{K.~Musgrave}, \bibinfo{author}{S.~Belongie},
+  \bibinfo{author}{S.-N. Lim},
+\newblock \bibinfo{title}{A metric learning reality check},
+\newblock in: \bibinfo{booktitle}{European Conference on Computer Vision},
+  \bibinfo{organization}{Springer}, \bibinfo{year}{2020}, pp.
+  \bibinfo{pages}{681--699}.
+%Type = Inproceedings
+\bibitem[{Steinhardt et~al.(2017)Steinhardt, Koh, and
+  Liang}]{steinhardt2017certified}
+\bibinfo{author}{J.~Steinhardt}, \bibinfo{author}{P.~W. Koh},
+  \bibinfo{author}{P.~Liang},
+\newblock \bibinfo{title}{Certified defenses for data poisoning attacks},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 31st International
+  Conference on Neural Information Processing Systems}, \bibinfo{year}{2017},
+  pp. \bibinfo{pages}{3520--3532}.
+%Type = Article
+\bibitem[{Melis et~al.(2017)Melis, Dyer, and Blunsom}]{melis2017state}
+\bibinfo{author}{G.~Melis}, \bibinfo{author}{C.~Dyer},
+  \bibinfo{author}{P.~Blunsom},
+\newblock \bibinfo{title}{On the state of the art of evaluation in neural
+  language models},
+\newblock \bibinfo{journal}{arXiv preprint arXiv:1707.05589}
+  (\bibinfo{year}{2017}).
+%Type = Inproceedings
+\bibitem[{Steinhardt and Liang(2015)}]{steinhardt2015learning}
+\bibinfo{author}{J.~Steinhardt}, \bibinfo{author}{P.~Liang},
+\newblock \bibinfo{title}{Learning fast-mixing models for structured
+  prediction},
+\newblock in: \bibinfo{booktitle}{International Conference on Machine
+  Learning}, \bibinfo{organization}{PMLR}, \bibinfo{year}{2015}, pp.
+  \bibinfo{pages}{1063--1072}.
+%Type = Article
+\bibitem[{Esteva et~al.(2017)Esteva, Kuprel, Novoa, Ko, Swetter, Blau, and
+  Thrun}]{esteva_dermatologist-level_2017}
+\bibinfo{author}{A.~Esteva}, \bibinfo{author}{B.~Kuprel},
+  \bibinfo{author}{R.~A. Novoa}, \bibinfo{author}{J.~Ko},
+  \bibinfo{author}{S.~M. Swetter}, \bibinfo{author}{H.~M. Blau},
+  \bibinfo{author}{S.~Thrun},
+\newblock \bibinfo{title}{Dermatologist-level classification of skin cancer
+  with deep neural networks},
+\newblock \bibinfo{journal}{Nature} \bibinfo{volume}{542}
+  (\bibinfo{year}{2017}) \bibinfo{pages}{115--118}. \URLprefix
+  \url{http://www.nature.com/articles/nature21056}.
+  \DOIprefix\doi{10.1038/nature21056}.
+%Type = Article
+\bibitem[{R{\"o}ttger et~al.(2020)R{\"o}ttger, Vidgen, Nguyen, Waseem,
+  Margetts, and Pierrehumbert}]{rottger2020hatecheck}
+\bibinfo{author}{P.~R{\"o}ttger}, \bibinfo{author}{B.~Vidgen},
+  \bibinfo{author}{D.~Nguyen}, \bibinfo{author}{Z.~Waseem},
+  \bibinfo{author}{H.~Margetts}, \bibinfo{author}{J.~Pierrehumbert},
+\newblock \bibinfo{title}{Hatecheck: Functional tests for hate speech detection
+  models},
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2012.15606}
+  (\bibinfo{year}{2020}).
+%Type = Misc
+\bibitem[{onl(????)}]{onlinesafetydata}
+\bibinfo{title}{About the online safety data initiative}, ????
+%Type = Misc
+\bibitem[{noa(2012)}]{noauthor_facebook:_2012}
+\bibinfo{title}{Facebook: 3.2 {Billion} {Likes} \& {Comments} {Every} {Day}},
+  \bibinfo{year}{2012}. \URLprefix
+  \url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}.
+%Type = Misc
+\bibitem[{noa(2021)}]{noauthor_10_2021}
+\bibinfo{title}{10 {Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in
+  2021 [{Infographic}]}, \bibinfo{year}{2021}. \URLprefix
+  \url{https://www.oberlo.com/blog/twitter-statistics}.
+%Type = Misc
+\bibitem[{noa(2020)}]{noauthor_reddit_nodate}
+\bibinfo{title}{Reddit in 2020}, \bibinfo{year}{2020}. \URLprefix
+  \url{https://www.reddit.com/r/blog/comments/k967mm/reddit_in_2020/}.
+%Type = Book
+\bibitem[{Roberts(2014)}]{roberts2014behind}
+\bibinfo{author}{S.~T. Roberts}, \bibinfo{title}{Behind the screen: The hidden
+  digital labor of commercial content moderation},
+  \bibinfo{publisher}{University of Illinois at Urbana-Champaign},
+  \bibinfo{year}{2014}.
+%Type = Article
+\bibitem[{Roberts(2016)}]{roberts2016commercial}
+\bibinfo{author}{S.~T. Roberts},
+\newblock \bibinfo{title}{Commercial content moderation: Digital laborers'
+  dirty work}  (\bibinfo{year}{2016}).
+%Type = Inproceedings
+\bibitem[{Karunakaran and Ramakrishan(2019)}]{karunakaran2019testing}
+\bibinfo{author}{S.~Karunakaran}, \bibinfo{author}{R.~Ramakrishan},
+\newblock \bibinfo{title}{Testing stylistic interventions to reduce emotional
+  impact of content moderation workers},
+\newblock in: \bibinfo{booktitle}{Proceedings of the AAAI Conference on Human
+  Computation and Crowdsourcing}, volume~\bibinfo{volume}{7},
+  \bibinfo{year}{2019}, pp. \bibinfo{pages}{50--58}.
+%Type = Inproceedings
+\bibitem[{Steiger et~al.(2021)Steiger, Bharucha, Venkatagiri, Riedl, and
+  Lease}]{steiger2021psychological}
+\bibinfo{author}{M.~Steiger}, \bibinfo{author}{T.~J. Bharucha},
+  \bibinfo{author}{S.~Venkatagiri}, \bibinfo{author}{M.~J. Riedl},
+  \bibinfo{author}{M.~Lease},
+\newblock \bibinfo{title}{The psychological well-being of content moderators},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 2021 CHI Conference on
+  Human Factors in Computing Systems, CHI}, volume~\bibinfo{volume}{21},
+  \bibinfo{year}{2021}.
+%Type = Misc
+\bibitem[{Newton(2020)}]{newton_facebook_2020}
+\bibinfo{author}{C.~Newton}, \bibinfo{title}{Facebook will pay \$52 million in
+  settlement with moderators who developed {PTSD} on the job},
+  \bibinfo{year}{2020}. \URLprefix
+  \url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}.
+%Type = Article
+\bibitem[{Parks(2019)}]{parks2019dirty}
+\bibinfo{author}{L.~Parks},
+\newblock \bibinfo{title}{Dirty data: content moderation, regulatory
+  outsourcing, and the cleaners},
+\newblock \bibinfo{journal}{Film Quarterly} \bibinfo{volume}{73}
+  (\bibinfo{year}{2019}) \bibinfo{pages}{11--18}.
+%Type = Article
+\bibitem[{Stepanikova(2012)}]{stepanikova2012racial}
+\bibinfo{author}{I.~Stepanikova},
+\newblock \bibinfo{title}{Racial-ethnic biases, time pressure, and medical
+  decisions},
+\newblock \bibinfo{journal}{Journal of health and social behavior}
+  \bibinfo{volume}{53} (\bibinfo{year}{2012}) \bibinfo{pages}{329--343}.
+%Type = Misc
+\bibitem[{Koetsier(2020)}]{koetsier_report}
+\bibinfo{author}{J.~Koetsier}, \bibinfo{title}{Report: {Facebook} {Makes}
+  300,000 {Content} {Moderation} {Mistakes} {Every} {Day}},
+  \bibinfo{year}{2020}. \URLprefix
+  \url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/}.
+%Type = Article
+\bibitem[{Hoff and Mitchell(2009)}]{hoff2009cyberbullying}
+\bibinfo{author}{D.~L. Hoff}, \bibinfo{author}{S.~N. Mitchell},
+\newblock \bibinfo{title}{Cyberbullying: Causes, effects, and remedies},
+\newblock \bibinfo{journal}{Journal of Educational Administration}
+  (\bibinfo{year}{2009}).
+%Type = Book
+\bibitem[{Keipi et~al.(2016)Keipi, N{\"a}si, Oksanen, and
+  R{\"a}s{\"a}nen}]{keipi2016online}
+\bibinfo{author}{T.~Keipi}, \bibinfo{author}{M.~N{\"a}si},
+  \bibinfo{author}{A.~Oksanen}, \bibinfo{author}{P.~R{\"a}s{\"a}nen},
+  \bibinfo{title}{Online hate and harmful content: Cross-national
+  perspectives}, \bibinfo{publisher}{Taylor \& Francis}, \bibinfo{year}{2016}.
+%Type = Article
+\bibitem[{Wachs et~al.(2019)Wachs, Wright, Sittichai, Singh, Biswal, Kim, Yang,
+  G{\'a}mez-Guadix, Almendros, Flora et~al.}]{wachs2019associations}
+\bibinfo{author}{S.~Wachs}, \bibinfo{author}{M.~F. Wright},
+  \bibinfo{author}{R.~Sittichai}, \bibinfo{author}{R.~Singh},
+  \bibinfo{author}{R.~Biswal}, \bibinfo{author}{E.-m. Kim},
+  \bibinfo{author}{S.~Yang}, \bibinfo{author}{M.~G{\'a}mez-Guadix},
+  \bibinfo{author}{C.~Almendros}, \bibinfo{author}{K.~Flora}, et~al.,
+\newblock \bibinfo{title}{Associations between witnessing and perpetrating
+  online hate in eight countries: The buffering effects of problem-focused
+  coping},
+\newblock \bibinfo{journal}{International journal of environmental research and
+  public health} \bibinfo{volume}{16} (\bibinfo{year}{2019})
+  \bibinfo{pages}{3992}.
+%Type = Misc
+\bibitem[{French(2021)}]{french_as_2021}
+\bibinfo{author}{C.~French}, \bibinfo{title}{As the pandemic forces us online,
+  {LGBTQ2S}+ teens deal with cyberbullying}, \bibinfo{year}{2021}. \URLprefix
+  \url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}.
+%Type = Misc
+\bibitem[{League(2020)}]{ADL_free}
+\bibinfo{author}{A.-D. League}, \bibinfo{title}{Free to {Play}? {Hate},
+  {Harassment} and {Positive} {Social} {Experience} in {Online} {Games} 2020},
+  \bibinfo{year}{2020}. \URLprefix \url{https://www.adl.org/free-to-play-2020}.
+%Type = Misc
+\bibitem[{noa(2017)}]{noauthor_:game_nodate}
+\bibinfo{title}{In:{Game} {Abuse}}, \bibinfo{year}{2017}. \URLprefix
+  \url{https://www.ditchthelabel.org/research-papers/ingame-abuse/}.
+%Type = Article
+\bibitem[{Leader~Maynard and Benesch(2016)}]{leader2016dangerous}
+\bibinfo{author}{J.~Leader~Maynard}, \bibinfo{author}{S.~Benesch},
+\newblock \bibinfo{title}{Dangerous speech and dangerous ideology: An
+  integrated model for monitoring and prevention},
+\newblock \bibinfo{journal}{Genocide Studies and Prevention}
+  \bibinfo{volume}{9} (\bibinfo{year}{2016}).
+%Type = Article
+\bibitem[{Garland et~al.(2020)Garland, Ghazi-Zahedi, Young,
+  H{\'e}bert-Dufresne, and Galesic}]{garland2020countering}
+\bibinfo{author}{J.~Garland}, \bibinfo{author}{K.~Ghazi-Zahedi},
+  \bibinfo{author}{J.-G. Young}, \bibinfo{author}{L.~H{\'e}bert-Dufresne},
+  \bibinfo{author}{M.~Galesic},
+\newblock \bibinfo{title}{Countering hate on social media: Large scale
+  classification of hate and counter speech},
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2006.01974}
+  (\bibinfo{year}{2020}).
+%Type = Article
+\bibitem[{Dictionary(2002)}]{dictionary2002merriam}
+\bibinfo{author}{M.-W. Dictionary},
+\newblock \bibinfo{title}{Merriam-webster},
+\newblock \bibinfo{journal}{On-line at http://www. mw. com/home. htm}
+  \bibinfo{volume}{8} (\bibinfo{year}{2002}) \bibinfo{pages}{2}.
+%Type = Inproceedings
+\bibitem[{Schieb and Preuss(2016)}]{schieb2016governing}
+\bibinfo{author}{C.~Schieb}, \bibinfo{author}{M.~Preuss},
+\newblock \bibinfo{title}{Governing hate speech by means of counterspeech on
+  facebook},
+\newblock in: \bibinfo{booktitle}{66th ica annual conference, at fukuoka,
+  japan}, \bibinfo{year}{2016}, pp. \bibinfo{pages}{1--23}.
+%Type = Article
+\bibitem[{Benesch et~al.(2016)Benesch, Ruths, Dillon, Saleem, and
+  Wright}]{benesch2016considerations}
+\bibinfo{author}{S.~Benesch}, \bibinfo{author}{D.~Ruths},
+  \bibinfo{author}{K.~P. Dillon}, \bibinfo{author}{H.~M. Saleem},
+  \bibinfo{author}{L.~Wright},
+\newblock \bibinfo{title}{Considerations for successful counterspeech},
+\newblock \bibinfo{journal}{Dangerous Speech Project}  (\bibinfo{year}{2016}).
+%Type = Article
+\bibitem[{Rieger et~al.(2018)Rieger, Schmitt, and Frischlich}]{rieger2018hate}
+\bibinfo{author}{D.~Rieger}, \bibinfo{author}{J.~B. Schmitt},
+  \bibinfo{author}{L.~Frischlich},
+\newblock \bibinfo{title}{Hate and counter-voices in the internet: Introduction
+  to the special isssue},
+\newblock \bibinfo{journal}{Studies in Communication and Media}
+  (\bibinfo{year}{2018}) \bibinfo{pages}{459--472}.
+%Type = Article
+\bibitem[{Ziegele et~al.(2018)Ziegele, Jost, Bormann, and
+  Heinbach}]{ziegele2018journalistic}
+\bibinfo{author}{M.~Ziegele}, \bibinfo{author}{P.~Jost},
+  \bibinfo{author}{M.~Bormann}, \bibinfo{author}{D.~Heinbach},
+\newblock \bibinfo{title}{Journalistic counter-voices in comment sections:
+  Patterns, determinants, and potential consequences of interactive moderation
+  of uncivil user comments},
+\newblock \bibinfo{journal}{SCM Studies in Communication and Media}
+  \bibinfo{volume}{7} (\bibinfo{year}{2018}) \bibinfo{pages}{525--554}.
+%Type = Article
+\bibitem[{Ziems et~al.(2020)Ziems, He, Soni, and Kumar}]{ziems2020racism}
+\bibinfo{author}{C.~Ziems}, \bibinfo{author}{B.~He}, \bibinfo{author}{S.~Soni},
+  \bibinfo{author}{S.~Kumar},
+\newblock \bibinfo{title}{Racism is a virus: Anti-asian hate and counterhate in
+  social media during the covid-19 crisis},
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2005.12423}
+  (\bibinfo{year}{2020}).
+%Type = Article
+\bibitem[{Xie et~al.(2011)Xie, Sreenivasan, Korniss, Zhang, Lim, and
+  Szymanski}]{xie2011social}
+\bibinfo{author}{J.~Xie}, \bibinfo{author}{S.~Sreenivasan},
+  \bibinfo{author}{G.~Korniss}, \bibinfo{author}{W.~Zhang},
+  \bibinfo{author}{C.~Lim}, \bibinfo{author}{B.~K. Szymanski},
+\newblock \bibinfo{title}{Social consensus through the influence of committed
+  minorities},
+\newblock \bibinfo{journal}{Physical Review E} \bibinfo{volume}{84}
+  (\bibinfo{year}{2011}) \bibinfo{pages}{011130}.
+%Type = Article
+\bibitem[{Chandrasekharan et~al.(2017)Chandrasekharan, Pavalanathan,
+  Srinivasan, Glynn, Eisenstein, and Gilbert}]{chandrasekharan2017you}
+\bibinfo{author}{E.~Chandrasekharan}, \bibinfo{author}{U.~Pavalanathan},
+  \bibinfo{author}{A.~Srinivasan}, \bibinfo{author}{A.~Glynn},
+  \bibinfo{author}{J.~Eisenstein}, \bibinfo{author}{E.~Gilbert},
+\newblock \bibinfo{title}{You can't stay here: The efficacy of {R}eddit's 2015
+  ban examined through hate speech},
+\newblock \bibinfo{journal}{Proceedings of the ACM on Human-Computer
+  Interaction} \bibinfo{volume}{1} (\bibinfo{year}{2017})
+  \bibinfo{pages}{1--22}.
+%Type = Article
+\bibitem[{Bilewicz et~al.(2021)Bilewicz, Tempska, Leliwa, Dowgiałło, Tańska,
+  Urbaniak, and Wroczyński}]{bilewicz2021artificial}
+\bibinfo{author}{M.~Bilewicz}, \bibinfo{author}{P.~Tempska},
+  \bibinfo{author}{G.~Leliwa}, \bibinfo{author}{M.~Dowgiałło},
+  \bibinfo{author}{M.~Tańska}, \bibinfo{author}{R.~Urbaniak},
+  \bibinfo{author}{M.~Wroczyński},
+\newblock \bibinfo{title}{Artificial intelligence against hate: Intervention
+  reducing verbal aggression in the social network environment},
+\newblock \bibinfo{journal}{Aggressive Behavior} \bibinfo{volume}{47}
+  (\bibinfo{year}{2021}) \bibinfo{pages}{260--266}. \URLprefix
+  \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/ab.21948}.
+  \DOIprefix\doi{https://doi.org/10.1002/ab.21948}.
+  \href{http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/ab.21948}{{\tt
+  arXiv:https://onlinelibrary.wiley.com/doi/pdf/10.1002/ab.21948}}.
+%Type = Article
+\bibitem[{Brauer and Chaurand(2010)}]{brauer2010descriptive}
+\bibinfo{author}{M.~Brauer}, \bibinfo{author}{N.~Chaurand},
+\newblock \bibinfo{title}{Descriptive norms, prescriptive norms, and social
+  control: An intercultural comparison of people's reactions to uncivil
+  behaviors},
+\newblock \bibinfo{journal}{European Journal of Social Psychology}
+  \bibinfo{volume}{40} (\bibinfo{year}{2010}) \bibinfo{pages}{490--499}.
+%Type = Article
+\bibitem[{Fischer et~al.(2011)Fischer, Krueger, Greitemeyer, Vogrincic,
+  Kastenm{\""u}ller, Frey, Heene, Wicher, and
+  Kainbacher}]{fischer2011bystander}
+\bibinfo{author}{P.~Fischer}, \bibinfo{author}{J.~I. Krueger},
+  \bibinfo{author}{T.~Greitemeyer}, \bibinfo{author}{C.~Vogrincic},
+  \bibinfo{author}{A.~Kastenm{\""u}ller}, \bibinfo{author}{D.~Frey},
+  \bibinfo{author}{M.~Heene}, \bibinfo{author}{M.~Wicher},
+  \bibinfo{author}{M.~Kainbacher},
+\newblock \bibinfo{title}{The bystander-effect: a meta-analytic review on
+  bystander intervention in dangerous and non-dangerous emergencies.},
+\newblock \bibinfo{journal}{Psychological bulletin} \bibinfo{volume}{137}
+  (\bibinfo{year}{2011}) \bibinfo{pages}{517}.
+%Type = Article
+\bibitem[{Legault et~al.(2011)Legault, Gutsell, and
+  Inzlicht}]{legault2011ironic}
+\bibinfo{author}{L.~Legault}, \bibinfo{author}{J.~N. Gutsell},
+  \bibinfo{author}{M.~Inzlicht},
+\newblock \bibinfo{title}{Ironic effects of antiprejudice messages: How
+  motivational interventions can reduce (but also increase) prejudice},
+\newblock \bibinfo{journal}{Psychological Science} \bibinfo{volume}{22}
+  (\bibinfo{year}{2011}) \bibinfo{pages}{1472--1477}.
+%Type = Article
+\bibitem[{Morris and Cushman(2018)}]{morris2018common}
+\bibinfo{author}{A.~Morris}, \bibinfo{author}{F.~Cushman},
+\newblock \bibinfo{title}{A common framework for theories of norm compliance},
+\newblock \bibinfo{journal}{Social Philosophy and Policy} \bibinfo{volume}{35}
+  (\bibinfo{year}{2018}) \bibinfo{pages}{101--127}.
+%Type = Article
+\bibitem[{Cialdini et~al.(1990)Cialdini, Reno, and
+  Kallgren}]{cialdini1990focus}
+\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{R.~R. Reno},
+  \bibinfo{author}{C.~A. Kallgren},
+\newblock \bibinfo{title}{A focus theory of normative conduct: Recycling the
+  concept of norms to reduce littering in public places.},
+\newblock \bibinfo{journal}{Journal of personality and social psychology}
+  \bibinfo{volume}{58} (\bibinfo{year}{1990}) \bibinfo{pages}{1015}.
+%Type = Article
+\bibitem[{Cialdini et~al.(2006)Cialdini, Demaine, Sagarin, Barrett, Rhoads, and
+  Winter}]{cialdini2006managing}
+\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{L.~J. Demaine},
+  \bibinfo{author}{B.~J. Sagarin}, \bibinfo{author}{D.~W. Barrett},
+  \bibinfo{author}{K.~Rhoads}, \bibinfo{author}{P.~L. Winter},
+\newblock \bibinfo{title}{Managing social norms for persuasive impact},
+\newblock \bibinfo{journal}{Social influence} \bibinfo{volume}{1}
+  (\bibinfo{year}{2006}) \bibinfo{pages}{3--15}.
+%Type = Article
+\bibitem[{Goldstein et~al.(2008)Goldstein, Cialdini, and
+  Griskevicius}]{goldstein2008room}
+\bibinfo{author}{N.~J. Goldstein}, \bibinfo{author}{R.~B. Cialdini},
+  \bibinfo{author}{V.~Griskevicius},
+\newblock \bibinfo{title}{A room with a viewpoint: Using social norms to
+  motivate environmental conservation in hotels},
+\newblock \bibinfo{journal}{Journal of consumer Research} \bibinfo{volume}{35}
+  (\bibinfo{year}{2008}) \bibinfo{pages}{472--482}.
+%Type = Article
+\bibitem[{Kallgren et~al.(2000)Kallgren, Reno, and
+  Cialdini}]{kallgren2000focus}
+\bibinfo{author}{C.~A. Kallgren}, \bibinfo{author}{R.~R. Reno},
+  \bibinfo{author}{R.~B. Cialdini},
+\newblock \bibinfo{title}{A focus theory of normative conduct: When norms do
+  and do not affect behavior},
+\newblock \bibinfo{journal}{Personality and social psychology bulletin}
+  \bibinfo{volume}{26} (\bibinfo{year}{2000}) \bibinfo{pages}{1002--1012}.
+%Type = Article
+\bibitem[{Cialdini and Goldstein(2004)}]{cialdini2004social}
+\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{N.~J. Goldstein},
+\newblock \bibinfo{title}{Social influence: Compliance and conformity},
+\newblock \bibinfo{journal}{Annual review of psychology} \bibinfo{volume}{55}
+  (\bibinfo{year}{2004}) \bibinfo{pages}{591--621}.
+%Type = Article
+\bibitem[{Stangor et~al.(2001)Stangor, Sechrist, and
+  Jost}]{stangor2001changing}
+\bibinfo{author}{C.~Stangor}, \bibinfo{author}{G.~B. Sechrist},
+  \bibinfo{author}{J.~T. Jost},
+\newblock \bibinfo{title}{Changing racial beliefs by providing consensus
+  information},
+\newblock \bibinfo{journal}{Personality and Social Psychology Bulletin}
+  \bibinfo{volume}{27} (\bibinfo{year}{2001}) \bibinfo{pages}{486--496}.
+%Type = Article
+\bibitem[{Crandall et~al.(2002)Crandall, Eshleman, and
+  O'brien}]{crandall2002social}
+\bibinfo{author}{C.~S. Crandall}, \bibinfo{author}{A.~Eshleman},
+  \bibinfo{author}{L.~O'brien},
+\newblock \bibinfo{title}{Social norms and the expression and suppression of
+  prejudice: the struggle for internalization.},
+\newblock \bibinfo{journal}{Journal of personality and social psychology}
+  \bibinfo{volume}{82} (\bibinfo{year}{2002}) \bibinfo{pages}{359}.
+%Type = Article
+\bibitem[{Munger(2017)}]{munger2017tweetment}
+\bibinfo{author}{K.~Munger},
+\newblock \bibinfo{title}{Tweetment effects on the tweeted: Experimentally
+  reducing racist harassment},
+\newblock \bibinfo{journal}{Political Behavior} \bibinfo{volume}{39}
+  (\bibinfo{year}{2017}) \bibinfo{pages}{629--649}.
+  \DOIprefix\doi{10.1007/s11109-016-9373-5}.
+%Type = Article
+\bibitem[{Price et~al.(2006)Price, Nir, and Cappella}]{price2006normative}
+\bibinfo{author}{V.~Price}, \bibinfo{author}{L.~Nir}, \bibinfo{author}{J.~N.
+  Cappella},
+\newblock \bibinfo{title}{Normative and informational influences in online
+  political discussions},
+\newblock \bibinfo{journal}{Communication Theory} \bibinfo{volume}{16}
+  (\bibinfo{year}{2006}) \bibinfo{pages}{47--74}.
+%Type = Inproceedings
+\bibitem[{Cheng et~al.(2017)Cheng, Bernstein, Danescu-Niculescu-Mizil, and
+  Leskovec}]{cheng2017anyone}
+\bibinfo{author}{J.~Cheng}, \bibinfo{author}{M.~Bernstein},
+  \bibinfo{author}{C.~Danescu-Niculescu-Mizil}, \bibinfo{author}{J.~Leskovec},
+\newblock \bibinfo{title}{Anyone can become a troll: Causes of trolling
+  behavior in online discussions},
+\newblock in: \bibinfo{booktitle}{Proceedings of the 2017 ACM conference on
+  computer supported cooperative work and social computing},
+  \bibinfo{year}{2017}, pp. \bibinfo{pages}{1217--1230}.
+%Type = Incollection
+\bibitem[{Cialdini et~al.(1991)Cialdini, Kallgren, and
+  Reno}]{cialdini_focus_1991}
+\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{C.~A. Kallgren},
+  \bibinfo{author}{R.~R. Reno},
+\newblock \bibinfo{title}{A {Focus} {Theory} of {Normative} {Conduct}: {A}
+  {Theoretical} {Refinement} and {Reevaluation} of the {Role} of {Norms} in
+  {Human} {Behavior}},
+\newblock in: \bibinfo{booktitle}{Advances in {Experimental} {Social}
+  {Psychology}}, volume~\bibinfo{volume}{24}, \bibinfo{publisher}{Elsevier},
+  \bibinfo{year}{1991}, pp. \bibinfo{pages}{201--234}. \URLprefix
+  \url{https://linkinghub.elsevier.com/retrieve/pii/S0065260108603305}.
+  \DOIprefix\doi{10.1016/S0065-2601(08)60330-5}.
+
+\end{thebibliography}
+
 \end{document}

### 2023-01-16 paperSubmission/paperSubmission1.tex
small changes

@@
 By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.
-
-The normative approach stems from the  aforementioned psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted.
-Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms - what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.
+The normative approach
 
@@
 and a more recent study has shown that ordinary people, with no habit of trolling, will engage in trolling behavior under proper circumstances.
+
+\todo{To sie nie klei ta koncowka, trzeba cos zmienic}
 

### 2023-01-17 paperSubmission/paperSubmission1.tex
added three sections

@@
 
-\section{Counter-speech interventions}
+\section{Automated versus human-based moderation}\label{sec:automated-versus-human}
+
+The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around the technology performance \citep{macavaney2019hate, schmidt2017survey}.
+State-of-the-art solutions are mostly governed by statistical methods, including deep learning and machine learning \citep{jordan2015machine, lecun2015deep, sejnowski2020unreasonable}.
+Their performance is inherently tied to the amount of data being fed to the system and annotation quality.
+
+At different stages of the process, from data gathering and preparation, annotation,  to the training or algorithms themselves, biases seem to be omnipresent \citep{binns2017like, geva2019we, mehrabi2021survey}.
+For instance, \citet{sap_risk_2019} examined how the lack of knowledge of data annotators about the dialect of minorities can lead to the amplification of bias against those minorities.
+When improperly trained, annotators repeatedly make incorrect judgments about comments expressed in African American English dialect, those mistakes are repeated by algorithms once the model learns to identify hate speech using such datasets.
+Since algorithms are getting more control in the decision-making process of who can participate in discussions online, such errors can have detrimental effects on people of African-American descent, who can be excluded from certain communities.
+
+Yet another bias can result from the technical shortcomings of statistical methods such as deep learning and machine learning.
+For instance, Perspective API,\footnote{\url{https://perspectiveapi.com}} a tool for detection of verbal aggression online, was repeatedly judging neutral sentences such as: “I am a woman”, “I am a Jew”, or “I am a black gay woman”, as highly toxic \citep{jigsaw2019}.
+Such errors are inextricably related to the foundations of deep learning and machine learning models, which learn directly from the annotated data.
+Since women and minorities are frequently a target of attacks, such algorithms, which have no understanding about the structure of the sentence and the grammar behind it, make statistical approximation and incorrectly give a high toxicity score because of the occurrence of “sensitive” keywords—woman, Jew, black, gay, and so on.
+
+Users of online services are also creative in their strategies of circumventing automated content moderation systems, and as shown by \citet{grondahl2018all}, current techniques are vulnerable to the most common evasions such as word changes (inserting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words).
+For instance, in the evaluation of seven state-of-the-art models trained for hate speech detection, adding “love” to abusive sentences---a word which is negatively correlated with hate speech---resulted in the F1 score\footnote{This is  an overall measure of a model’s accuracy that combines precision and recall.} preformance decrease to almost  0\% in the majority of models tested.
+
+Lack of generalizability of the models---the ability to perform well on datasets coming from sources other than the one used for training---is a severe shortcoming as well \citep{rosa2019automatic, yin2021towards}.
+As shown again by \citet{grondahl2018all}, models trained on a dataset coming from Wikipedia, which achieve 86\% of F1 score, perform below 50\% F1 on Twitter (between 24\% to 50\% depending on the model and the Twitter sample).
+The adaptability from Twitter to Wikipedia looks even worse.
+One of the models trained on a Twitter sample with a performance of 83\% F1 dropped to 14\% on a Wikipedia sample.
+
+As shown by \citet{wu2019errudite, lipton2019troubling, musgrave2020metric} in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility.
+This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being announced to a wider public.
+Specifically, \citet{lipton2019troubling} distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike:
+
+\begin{enumerate}
+    \item First, the inability to draw a clear distinction between speculation and explanation, with the former often being disguised as the latter.
+For instance, in \citet{steinhardt2017certified} the author admitted to stating that “the high dimensionality and abundance of irrelevant features...give the attacker more room to construct attacks”---although no experiments were conducted to measure the effect of dimensionality of the neural network on its attackability.
+    \item Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect).
+As was shown by \citet{melis2017state}, some improvements in language modeling, which originally were ascribed to complex innovations in the architecture of the network, stem from hyperparameter tuning.
+As mentioned by \citet{lipton2019troubling}, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
+    \item Third, “mathiness”---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon.
+Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang \citet{steinhardt2015learning} with an irrelevant theorem to amplify the empirical results.
+They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm, which was the main subject of a paper.
+    \item Last but not least, misuse of language.
+This includes suggestive definitions without proper explanations of what they mean in the context (e.g., calling good performance in simple NLP tasks a human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g.
+consciousness).
+In one of the examples described, empirical results reported by \citet{esteva_dermatologist-level_2017} in which a classifier achieved low error on independent and identically distributed test data was described as “dermatologist-level classification of skin cancer,” omitting the fact that dermatologists judge cases of much wider variety.
+\end{enumerate}
+
+Yet another obstacle in the process is the lack of gold standard in dataset construction and taxonomies of abusive language being used, for instance, in the process of annotating different datasets.
+Frequently people obtain data from various sources and do not follow any universally used instructions when it comes to annotation, what results in lack of annotation coherency across various datasets related to one phenomenon (e.g., hate speech).
+The lack of expert annotators and proper annotation criteria and instructions are also widespread, with the common practice of hiring untrained workers from Mechanical Turk or other crowdsourcing platforms.
+
+Although there are some initiatives developed in response, most notably, functional tests for Hate Speech Detection Models created by \citet{rottger2020hatecheck}, or the Online Safety Data Initiative (OSDI) \citep{onlinesafetydata}, focused on projects related to improving access to data, standardizing the description of online harms, as well as creating tools and benchmarks for evaluation of technologies focused on safety, much effort must be made before wider adoption of such solutions comes into force.
+
+At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms.
+On Facebook, there are more than 3B comments and likes daily \citep{noauthor_facebook:_2012}, 500M tweets are sent daily on Twitter \citep{noauthor_10_2021}, and over 2B comments made by users of Reddit in 2020 \citep{noauthor_reddit_nodate}, which is almost 3M comments made daily.
+With this amount of content, it’s either impossible or extremely costly to scale the moderation workforce.
+One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being.
+Being submersed in the cyber-Augean stables takes a toll on many---as examined by \citet{roberts2014behind, roberts2016commercial}.
+Workers hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they’ve seen in secret under restrictive NDAs.
+This in turn, makes the research in the area extremely difficult, since moderators are not allowed to talk about their work conditions or any other related subject.
+Those who decide to break the NDA risk a penalty.
+
+Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases.
+This can lead to serious psychological damage, such as depression or PTSD \citep{roberts2014behind}.
+Although there are certain initiatives being developed or introduced to reduce the emotional impact of the moderation, such as stylistic alterations to  content (for instance, applying grayscale or blurring to images
+ \citep{karunakaran2019testing}, workplace wellness programs, clinical support, or psychological training \citep{steiger2021psychological}, none of the methods can eliminate the psychological distress completely.
+Some of the employees filed a lawsuit against Facebook, and as a result, the company agreed to pay \$52M in compensation for mental health issues developed during the job \citep{newton_facebook_2020}.
+Also, as described by \citet{parks2019dirty}, the work is often performed under time pressure, reviewing 25K pieces of content per day.
+Spending on average three to five seconds on each image reported for moderation might not lead to the most thoughtful decisions, and as shown by \citet{stepanikova2012racial}, high time pressure can amplify human biases.
+Considering that Facebook employs 15K moderators \citep{koetsier_report} and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a carefully thought-out collaboration between humans and machines in this area seems indispensable and highly demanded.
+
+\section{Different approaches to content moderation}\label{sec:content-moderation}
+
+There are different approaches when it comes to the moderation of online content.
+One can follow the workflow of reactive moderation, which happens once the content is published.
+Harmful messages can be either reported by the users of the platforms or identified by automated methods and then sent for review to moderators.
+A set of actions can then be taken depending on the platform, its community guidelines, on the content, or on the user level.
+A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them.
+Depending on the type and amount of infraction, a particular user can be warned, muted, shadowbanned, or banned from further participation in the community for a period of time.
+The weakness of the reactive method is that the damage is already done.
+Whoever is the recipient of the abusive message has the chance to see it and potentially suffer \citep{hoff2009cyberbullying, keipi2016online, wachs2019associations}.
+Yet another weakness connected with relying solely on human reports is the content that is harmful but unreported by its recipient or bystanders.
+Although the exact scale of unreported negative content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online \citep{french_as_2021, ADL_free, noauthor_:game_nodate}.
+
+Yet another type of moderation is pro-active moderation.
+On this approach, automated methods used are either based on Artificial Intelligence or other less sophisticated tools (e.g., blacklists) and can screen the content before it gets published.
+If a harmful message is detected, it can be removed before reaching the recipient.
+Due to the aforementioned dubious performance of state-of-the-art statistical methods, particularly low precision, such tools are rarely used autonomously, and serve as additional support to content moderators.
+Alternatively, all content can be reviewed by moderators before it gets published on a website, although such a process is rarely implemented, as it stifles the discussion.
+
+Another categorization can be obtained by looking at who is engaged in the moderation of the content.
+In a distributed or decentralized moderation system, the community members decide which content gets taken down, as opposed to a centralized moderation system, in which professionals hired by a particular service are in charge.
+Some services use a hybrid approach, with Reddit being one of such cases.
+Consisting of numerous communities initiated by Reddit's users, the owners of the so-called subreddits (mods) are in control of the moderation within the subreddit.
+At the same time, Reddit hires a small centralized team of moderators (admins) that enforce content policy on a broader scale.
+
+\section{Counter-speech interventions}\label{sec:counter-speech}
 %counter-speech def
@@
 \todo{To sie nie klei ta koncowka, trzeba cos zmienic}
+
+\section{Technology applied for personal attack detection}
+\label{sec:technology}
+
+To perform the research at a scale sufficient for statistically reliable analysis, we needed to apply a technology for the initial automatic detection of personal attacks, to be further forwarded to human moderators for deeper analysis and making decisions regarding the outcome of the moderation (e.g., deletion of the post, sending a warning to an abusive user, banning the user, etc.).
+As we already mentioned in sections \ref{sec:automated-versus-human}, \ref{sec:content-moderation} and \ref{sec:collective-intelligence}, performing the moderation relying on the assumption that the moderator will read through all of the posts and comments is unrealistic, while moderation based solely on  other users' reporting could lead to a large number of abusive messages remaining unreported.
+This problem, present   in the literature \citep{ptaszynski2018automatic,urbaniak2022personal} and in  the mass media\footnote{\url{https://www.japantimes.co.jp/news/2022/12/03/business/tech/twitter-harmful-content/}}\textsuperscript{,}\footnote{\url{https://www.forbes.com/sites/forbestechcouncil/2022/06/14/the-growing-role-of-ai-in-content-moderation/}} has lead to an increase in the number or automatic tools being developed  and deployed to support content moderators in their work.\footnote{\url{https://influencermarketinghub.com/content-moderation-tools/}.}
+
+In our research  we applied Samurai detection software, a
+proprietary technology developed Samurai Labs.\footnote{\url{https://www.samurailabs.ai/},
+  described in (Ptaszyński, Leliwa, Piech, \& Smywiński-Pohl, 2018;
+  Wroczynski \& Leliwa, 2019).} The technology comprises a combination
+of symbolic and statistical methods, where each statistical component
+(e.g., a deep learning model) is governed by a symbolic component
+utilizing a variety of natural language processing methods (e.g.,
+tokenization, syntactic parsing, etc.). Symbolic components are used to
+determine if a potentially abusive utterance is not a part of a broader
+utterance indicating that the first one should not be considered
+abusive. For example, an utterance ``you are an idiot'' is potentially
+abusive, but in reality it is not, if it appears as a part of some broader context
+such as ``I cannot believe he said you are an idiot.'' Another
+example of using symbolic components is determining if an abusive phrase
+is targeted against an interlocutor (e.g.~using a linking verb to assign
+the abusive phrase with a second person as in the ``you are an idiot''
+example).
+
+Samurai has already been applied in a variety of studies, including suicidal text detection \citep{ijerph182211759}, detection of toxic usernames \citep{URBANIAK2022107371}, and detection of personal attacks on Reddit \citep{urbaniak2022personal}.
+For the  research presented in this paper we used the module of the system developed for the detection of personal attacks.
+
+\textit{Personal attacks} are defined as any
+kind of abusive remark made in relation to a person
+(\textit{ad hominem}) rather than to the content of the argument
+expressed by that person in a discussion. The definition of `personal
+attack' subsumes the use of specific terms which compare other people to
+animals or objects or making nasty insinuations without providing
+evidence. Three examples of typical personal attacks are as follows:
+
+\begin{itemize} 
+\item \emph{You are legit mentally retarded homie.}
+\item \emph {Eat a bag of dicks, fuckstick.}
+\item \emph {Fuck off with your sensitivity you douche.} 
+\end{itemize}
+
+Figure \ref{fig:samuraiexample} illustrates how an  input text (such as ``ccant
+believ he sad ur an id10+\ldots!'') is processed step-by-step utilizing
+both statistical and symbolic methods.
+The performance of Samurai has been measured on a number of occasions and evaluated as sufficiently reliable for practical use \citep{ptaszynski2018cyberbullying,ijerph182211759,urbaniak2022personal,URBANIAK2022107371}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{example.eps}
+    \caption{Example of processing of one sentence by the applied Samurai technology.}
+    \label{fig:samuraiexample}
+\end{figure}
+
+% In practice, this means that a whole variety of constructions can be
+% detected without the need to construct a fixed list of dictionary words
+% defined \textit{a priori}. Due to utilizing symbolic components that
+% oversee statistical components, \{\textsf Samurai\} recognizes complex
+% linguistic phenomena (such as indirect speech, rhetorical figures or
+% counter-factual expressions) to distinguish personal attacks from normal
+% communication, greatly reducing the number of false alarms as compared
+% to others systems used for violence detection. An example of a comparison \todo{of what with what}
+% can be seen in Figure \ref{fig:samuraiexample}, and a full benchmark was
+% presented in (Ptaszyński et al., 2018).
+
+% The detection models utilized in this research were designed to detect
+% personal attacks targeted against a second person (e.g.~interlocutor,
+% original author of a post) and a third person/group (e.g., other
+% participants in the conversation, people not involved in the
+% conversation, social groups, professional groups), except for public figures
+% (e.g.~politicians, celebrities). With regards to the symbolic component of
+% the system, by ``models'' we mean separate rules (such as, specifying a
+% candidate for the presence of personal attack, such as the aggressive
+% word ``idiot,'' which is further disambiguated with a syntactic rule of
+% citation, e.g., ``{[}he\(\vert\)she\(\vert\)they{]} said {[}SUBJECT{]}
+% {[}PREDICATE{]}'') or sets of rules, as seen in Figure
+% \ref{fig:samuraiexample}, e.g.~normalization model contains rules for
+% transcription normalization, citation detection model contains rules for
+% citation, etc. With regards to the statistical component, by ``models''
+% we refer to machine learning models trained on large data to classify an
+% entry into one of the categories (e.g., true personal attack, or false
+% positive) \todo{this doesn't make sense, Rafals comment}.
+
+% Moreover, the symbolic component of the system uses two types of
+% symbolic rules, namely ``narrow rules'' and ``wide rules.'' The former
+% have smaller coverage (e.g., are triggered less often), but detect
+% messages containing personal attacks with high
+% a precision.\footnote{Precision is defined traditionally as the ratio of correctly detected instances among all detected instances.}
+% The latter have wider coverage, but their precision is lower. We
+% decided to set apart the ``narrow'' and ``wide'' subgroups of the
+% detection models in order to increase the granularity of the analysis.
+% Firstly, we took only the detection models designed to detect personal
+% attacks targeted against second person. Secondly, we used these models
+% on a dataset of 320,000 Reddit comments collected on 2019/05/06.
+% Thirdly, we randomly picked at most hundred returned results for each
+% low-level
+% model\footnote{Low-level models are responsible for detecting low-level categories. Similarly, mid-level models detect mid-level categories, by combining several low-level models, etc.}
+% (some models are triggered very often while others rarely, so using all
+% instances would create too much bias). There were 390 low-level models
+% but many of them returned less than 100 results. We verified them
+% manually with the help of expert annotators trained in detection of
+% personal attacks and selected only those models that achieved at least
+% 90\% of precision. The models with fewer than 100 results were
+% excluded from the selection. After this step, the ``narrow'' subgroup
+% contained 43 out of 390 low-level models. Finally, we tested all of the
+% ``narrow'' models on a large dataset of 477,851 Reddit comments
+% collected between 2019/06/01 and 2019/08/31 from two subreddits
+% (r/MensRights and r/TooAfraidToAsk). Each result of the ``narrow''
+% models was verified manually by a trained annotator and the ``narrow''
+% models collectively achieved the precision of 93.3\%. We also tested
+% the rest of the ``wide'' models on random samples of 100 results for
+% each model (from the previous dataset of 320,000 Reddit comments) and we
+% excluded the models that achieved less than 80\% precision. The models
+% with fewer than 100 results were not excluded from the ``wide'' group.
+% In this simple setup we detected 24,251 texts containing ``wide''
+% attacks, where:
+
+% \begin{itemize}
+% \item  5,717 (23.6\%) contained personal attacks against second person detected by the "narrow" models,
+% \item  8,837 (36.4\%) contained personal attacks against second person detected by "wide" models
+% % the models other than "narrow",
+% \item  10,023 (41.3\%) contained personal attacks against third persons / groups.
+% The sum exceeds 100\% because some of the comments contained personal attacks against both second person and third person / groups.
+For example, a comment ``Fu$\ast\ast$ you a$\ast\ast$hole, you know that girls from this school are real bit$\ast\ast$es" contains both types of personal attack.
+% \end{itemize}
+% \todo{table with recall precision tests - Rafals comment}
 

### 2023-01-26 paperSubmission/paperSubmission1.tex
some additions

@@
 Let us elaborate.
- Social norms are agreed to be powerful determinants of human behavior. 
-According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common}, \citep{cialdini1990focus}.
-A good deal of studies have found that perceptions of what others are doing causes us to behave similarly.
-Norms can be applied to exert persuasive impact, for example to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.
+
+ocial norms are agreed to be powerful determinants of human behavior. 
+According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common, cialdini1990focus}.
+
+Multiple studies have found that perceptions of what others are doing cause us to behave similarly.
+Norms can be applied to exert persuasive impact, for example, to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.
 
@@
 Others say that we are only motivated by norms we have internalized during socialization, so the normative influence can only be exerted if the norm resonates with our internal value system \citep{morris2018common}.
-Focus Theory of Normative Conduct \citep{kallgren2000focus} is a psychological, theoretical framework used for understanding best conditions and practices for exerting normative influence.
+%cytowania
+
+The Focus Theory of Normative Conduct \citep{kallgren2000focus} is a  theoretical psychological  framework used for understanding best conditions and practices for exerting normative influence.
 Its main assumption is that norms that are focal in attention are likely to influence behavior.
-%explain on an example cialdini experiment
-To achieve persuasive impact a distinction between two types of norms has to be made.
-While it might sound strange to talk about desriptive norms, this is the way the terminology in the field developed, so we will keep using such terms.
-A descriptive norm refers to what is typically done, by showing  examples of  normal behavior in a given situation, and injunctive or prescriptive norm refers to what is commonly approved, such the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.
-A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while injuctive norm motivates by informing which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.
+One important distinction made within this approach is between two types of norms: a descriptive norm refers to what is typically done, by showing an example of normal behavior in a given situation, and an injunctive or prescriptive norm refers to what is commonly approved, such as the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.
+
+A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while an injunctive norm motivates by informing the agent which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.
 
@@
 The positive influence of injunctive and descriptive norms on unwanted social behavior was first presented in a study on littering in public spaces conducted by \citet{cialdini1990focus}.
-Study subjects were exposed to either descriptive or injunctive anti-littering norm, and the impact on the littering behavior was observed.
-In the descriptive condition the subjects were exposed to a clean or littered environment, serving as a proof of choices made by others.
-In the injunctive condition participants received messages stating the anti-littering norm.
-
-Injunctive messages directly asking not to litter had significantly reduced littering, and subjects littered more in a highly littered environment, and littered less in a clean environment although these effects were not statistically significant.
-%which ones
-Although seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.
+The study subjects were exposed to either descriptive or injunctive anti-littering norms, and the impact on the littering behavior was observed.
+In the descriptive condition, the subjects were exposed to a clean or littered environment, serving as proof of choices made by others.
+In the injunctive condition, the participants received messages stating the anti-littering norm.
+
+Injunctive messages directly asking not to litter had significantly reduced littering.
+The subjects littered more in a highly littered environment and littered less in a clean environment, although these effects were not statistically significant.\footnote{It is also worth noticing that  seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.}
 
@@
 
-A descriptive norm can be also evoked by providing a written information about what others usually do.
+A descriptive norm can be also evoked by providing written information about what others usually do.
 \citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about reuse of hotel towels (“the majority of guests reuse their towels”).
 This strategy has been proven superior to traditional appeals focusing on environmental protection.
-Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to the so-called local norms.
+Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to, so called, local norms.
 
@@
 
-%On the other hand, when it comes to pro-environmental choices, people are more likely to conform to information about what others don't do rather than what others do, building on an evolutionary predisposition to more urgently attend to negative rather than positive stimuli @bergquist2019and.
-%Stosujemy normatywne i empatyczne interwencje - w literaturze te mechanizmy psychologiczne są opisane jako skuteczne w obniżaniu agresji - cytujemy literature. 
-%W jakich innych badaniach counter speech wykorzystywali empatie i norme - nas (Bilewicz study), Munger, Roma racist, itp..+opisać jak nasze obecne badanie sie rozni - po raz pierwszy wykorztstyujemy collective intelligence ludzie + AI
-%describe hypothesis i give argument behind the hypothesis
-
- In line with this discussion, for the purpose of our study we have distinguished two types of counter responses to personal attacks: ``empathetic'' and ``normative''.
+In line with the above discussion, for the purpose of this study we have distinguished two types of responses to personal attacks: "empathetic" and "normative".
 The empathetic approach is aimed at countering the so-called desensitization to violence.
-It is a very dangerous process, finally leading to dehumanization of stigmatized groups.
-%Unfortunately, the impersonal structure of online space makes it very easy for the desensitization to occur.
- Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice.
-By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.
-The normative approach
-
-%To put it in an example, there is a general rule that we should not litter in public spaces (injunctive norm), but we are much more likely to leave our garbage, when there’s evidence that other people did not follow the rule - the space is littered with trash (descriptive norm).
-We hope that our interventions will provide constructive social cues about acceptable forms of communication and influence the way users converse in a given community.
-
-%Another phenomenon illustrating the power of the context is the bystander effect.
-The bystander theory  states that individuals are less likely to offer help to a victim when there are other people present - the greater the number of bystanders, the less likely it is that one of them will help.
-But it takes only one helpful volunteer for others to follow.
-The study by Machackova and others (2015) have shown the bystander effect also takes place online.
-and a more recent study has shown that ordinary people, with no habit of trolling, will engage in trolling behavior under proper circumstances.
-
-\todo{To sie nie klei ta koncowka, trzeba cos zmienic}
+It is a very dangerous process, finally leading to the dehumanization of stigmatized groups.
+ Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result, we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice.
+By sending empathetic interventions we hoped to evoke compassion and self-reflection, and  to humanize the person on the other side of the screen \citep{bilewicz2021artificial}.
+
+The normative approach stems from the  already discussed psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted.
+Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms---what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.
 
@@
 \end{figure}
+
+\section{Managing volunteers}\label{volunteers}
+
+For two months of the treatment period, interventions were conducted by 19 volunteers, recruited  online on an ongoing basis.
+The call for volunteers was promoted on social media channels, and groups related to volunteering and sent out to 30+ NGOs and organizations with social impact, 10 out of which shared it via their social networks or distributed it among their employees and partners.
+%(Tolerado, CEJI (A Jewish Contribution to an Inclusive Europe), INACH (International Network Against Cyberhate), Humanity in Action Poland, Gdansk Business Week among others).
+
+We expected that each volunteer would conduct around 10 interventions a day.
+Unfortunately, only a few people got engaged to such an extent at the beginning.
+Thus, we have implemented various incentives and gamification to increase volunteer engagement.
+Those included leaderboards, motivational statistics, and week-long contests with a prize.
+As you can see in Fig \ref{fig:volunteersBasic}, the drop in volunteer engagement is noticeable within the first 2 weeks from the beginning of the treatment period.
+The introduction of the first competition with an economic incentive (Amazon Gift Card for the most active volunteers) increased the engagement only temporarily.
+It then dropped dramatically outside of the contest.
+This forced us to keep repeating contests regularly until the end of the treatment period.
+Obviously, this is not an optimal and sustainable long-term strategy.
+
+Figure 15 \ref{fig:volunteersModel}  visualizes the result of a Bayesian model of volunteer engagement based on the resulting observational data, with daily baselines and multipliers for enthusiasm and impact of competitions.
+Four distinct groups emerge from this picture.
+Those, who are active, and even  more  so during competitions.
+Those who are evenly active throughout the treatment period.
+Those, who are active only during competitions, and volunteers whose initial enthusiasm died completely very soon.
+The multiplier of the volunteer engagement during the competition is only 1.31 which means that their engagement increases by around 30\% during that time.
+But the enthusiasm of  some of the volunteers had  its drop multiplier even below .9 \textbf{per day of experiment}.
+It accumulates as time progresses, which means that competitions might not be  effective in volunteer activity resuscitation, especially in the long run.
+
+If we were to conduct a similar experiment with volunteers again, we would test  non-economic motivational schemes---for instance, creating an obligation by signing an agreement with volunteers on conducting at least 10 interventions daily, or creating more engaging content and training during the treatment period.
+
+Besides the issue connected to  low volunteer engagement, we have experienced cases in which people reported negative effects of interventions or even started to get aggressive while responding to attackers.
+Although we've taken extra measures to support volunteers (a psychologist available to all participants,  and distribution of and guide to their well-being), this aspect cannot be eliminated completely.
+
+Additionally, many volunteers started to intervene in a repetitive manner, which resulted in accusations of behaving like an automated account (bot).
+During the process, we prepared an additional guide for our volunteers "How to write Powerful Interventions" and rewarded creativity during the contests.
+Both led to a noticeable increase in creativity, especially when it comes to the most engaged volunteers.
+
+We need to mention at this point that in this experiment, the negative side of the collective intelligence approach outweighs the positive one.
+In our future endeavors, we will be further exploring the opportunity to employ bots to conduct counter-speech.
+Even though AI is not endowed with empathy, it can be a powerful ally in evoking empathetic responses and maintaining civil behavior online.
+An ally, who under the condition of being precise enough to act autonomously, can take the burden off of the shoulders of moderators and the community, not requiring them to  screen through a multitude of potentially aggressive comments.
+
+Another scenario worth considering is a collective intelligence approach in which 90\% of interventions are conducted by an AI while 10\% of the most difficult cases are taken care of by humans, trained professionals, such as moderators.
+During the study, we had one extraordinary volunteer who was engaged and creative to such an extent that no machine could compete.
+Collaborating with people like them would considerably optimize the process.
+Such a trained, engaged, and resilient person could supervise the interventions run by AI and deal with  extreme cases.
 

### 2023-01-30 paperSubmission/paperSubmission1.tex
small changes

@@
 Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms---what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.
+
+\section{Collective Intelligence and  moderation}\label{collective-intelligence-approach-to-counter-speech}
+
+The main objective of the experiment was to test whether the level of verbal aggression (personal attacks) of a group of users regularly attacking others on Reddit can be significantly decreased by community-driven, counter-speech interventions conducted by volunteers in partnership with Artificial Intelligence (collective intelligence approach).
+
+Verbal aggression was defined in this experiment as a personal attack---any kind of verbal harassment, insult, or threat directed against the interlocutor in a text-based conversation online.
+Those were detected using Samurai Labs' cyberviolence detection system, describe in detail in Section \ref{sec:technology}.
+
+Traditionally, collective intelligence has been defined as "a group or a team's combined capacity and capability to perform a wide variety of tasks and solve diverse problems" \citep{woolley2015collective}.
+In our paper and in the theoretical underpinnings of the experiment itself, we will be relying on a collective intelligence scope proposed by Nesta, an innovation foundation (\url{https://www.nesta.org.uk}), which focuses on a collaboration between human and machine intelligence to develop innovative solutions to social challenges.
+
+Instead of using a negative motivation system, the assumption was to test a positive one—convincing verbally violent users to refrain from using cyberviolence based on civic education—peer-pressure regulation and experiential learning of a positive set of norms and empathy.
+Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its members.
+Volunteers, after receiving a notification on Slack, could then react with a proper intervention.
+Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence—utilizing human + machine intelligence to develop solutions to social challenges.
+
+Normative interventions can refer either to general social norms of civility and respect, community standards, a particular subreddit rule, or a descriptive norm among others.
+Empathetic interventions can refer to the emotional state of the recipient or the sender of the attack or both.
+They are designed to evoke an empathetic response.
+Here are some examples of interventions that were used during the experiment:
+\begin{itemize}
+  \item \emph{Insulting others is against Reddit's policy.} (normative)
+  \item \emph{Hey there, we do not call each other like that here.} (normative)
+  \item \emph{There is a human being on the other side who might be hurt by your words.} (empathetic)
+  \item \emph{I see you are frustrated but remember the human.} (empathetic)
+\end{itemize}
+
+Our hypotheses were as follows:
+
+\vspace{2mm}
+
+\begin{tabular}{lp{11cm}}
+H1 & If a group of human volunteers, notified by an AI-based 
+detection system about verbal aggression generated by the treatment group users, responds with counter-speech interventions, this will result in a decreased verbal aggression level for the whole group after the intervention period.\\
+H2 &  If two groups receive different types of interventions (empathy-based or normative), then the decrease in verbal aggression will be larger in the case of normative interventions in comparison to the empathy-based ones.
+\end{tabular}
+
+%the reasoning behind H2
+Although empathy has been found to be helpful in the reduction of aggressive behavior \citep{bjorkqvist2000social}, and the improvement of intergroup relations \citep{stephan1999role}, there are also important arguments and evidence concerning its limits.
+Specifically, Paul Bloom in his book \emph{}Against Empathy: The Case for Rational Compassion} \citep{bloom2017against}, stresses that empathy can have a very narrow focus and can be prone to biases.
+For instance, it’s easier to be empathetic towards those who are close or similar to us.
+Since conversations on Reddit are anonymous and usually occur between strangers, we expected  empathetic interventions to  be less effective than normative interventions in curbing personal attacks.
 

### 2023-02-01 paperSubmission/paperSubmission1.tex
final version of the paper in zip

@@
 \begin{abstract}
-Abstract goes here.
-
+During a six-month experiment conducted on Reddit, we studied the impact  of  counter-speech interventions against personal attacks on the number of personal attacks sent by  440  users regularly attacking others.
+We used two types of interventions, normative---which referred to social norms, and empathetic---which referred to emotions and encouraged perspective-taking.
+We employed a  collective intelligence approach---the collaboration between human and machine intelligence.
+Artificial Intelligence was used to detect verbal aggression and notify human volunteers, who then performed the interventions.
+We analyzed the data from three perspectives.
+We used time series models (1) of the short-term impact of individual interventions, and of (2) the cumulative impact of interventions received as the experiment progressed.
+We also (3) used aggregated  data for a long-term before/after analysis.
+The short-term effect of interventions is damaging: users tend to be on average around 26\% more aggressive the next day, but the effect does not last beyond two days.
+The cumulative effect of interventions is helpful: each intervention (up to around 8-10 total, the effectiveness of more interventions tends to be lower) decreases daily aggression by 4\% on average and the effects accumulate and  balance out the short-term effect in the long run.
+The effectiveness of normative interventions seems overall higher, except for the less aggressive offenders, for which empathetic interventions might be equally or more useful.
 \end{abstract}
@@
 \begin{keyword}
- keyword \sep keyword
+counter-speech\sep artificial intelligence\sep collective intelligence\sep  peaceful interventions\sep  Reddit\sep   no i nie wiem jeszcze który do przemocy słownej: online aggression\sep  online abuse\sep  personal attacks
 
@@
 %% main text
+
+\section{Introduction}\label{introduction}
+
+Much effort has been made to tackle the problem of verbal aggression and harassment online, but looking at various reports and surveys \citep{Zachary_hate, sorrentino2019epidemiology, vogels_state_2021}, it remains a common hindrance for people who engage with social media in their everyday lives.
+The problem was exacerbated during the COVID-19 pandemic, during which much of our social life moved to cyberspace.
+This shift was followed by an increase in cyberbullying attitudes and perpetration \citep{barlett2021comparing}, 90\% increase in public reports of illegal online content \citep{grant_2021}, including 114\% increase in non-consensual sharing of intimate images, 30\% increase in cyberbullying, as well as 40\% of increase in adults reporting online harassment.
+According to a report by company L1ght \citep{noauthor_l1ght_2020}, hate speech directed towards China and the Chinese went up by 900\% on Twitter.
+Gaming platforms were in the spotlight as well, with a 40\% increase in toxicity on Discord.\footnote{In both reports, the increase is reported as a relative change between the years 2019 and 2020, with no absolute indicators.}
+
+Unfortunately, the growing need for even more efficient and proactive moderation was not followed by an increased capacity to execute it, forcing companies and policymakers to rethink the current model of moderation processes and workforce.
+Due to the COVID-19 restrictions, including social distancing, a lot of those serving the role of moderators had to be sent home \citep{bhattacharya} without the ability to work remotely because of the constraints affiliated with restrictive non-disclosure agreements (NDA), among others.
+Curtailing the moderators’ workforce was accompanied by more agency given to algorithms and AI-based moderation.
+As argued by \citet{gerrard2020covid19}, those changes are a serious safety red flag for all the users of online platforms.
+At the same time, looking at the prevalence of online violence and the scope of the problem, cooperation between humans and algorithms seems to be inevitable.
+The question is how to execute such a partnership, taking into consideration the technological constraints and human limitations, and the strong suits of both.
+
+The matter in question is of great significance, as online violence (including cyberbullying, sexual harassment, hate speech, or any other type of abuse online) poses a great risk to individuals and groups alike with its harrowing consequences.
+On an individual level, online abuse was found to correlate with anxiety, lower self-esteem, feeling of hopelessness, isolation, substance abuse, decreased academic performance, and in more extreme cases self-harm, suicidal ideation, or suicide \citep{yang2021consequences, hinduja2010bullying, alhujailli2020affective, kowalski2013psychological}.
+On a group level, it has been linked to group polarisation and radicalization \citep{lee2002persuasive, williams2019hatred}.
+Online hatred running rampant on social media platforms can incite atrocities such as genocide---The Rohingya genocide was preceded by an increase in anti-Muslim rhetoric and a genocidal campaign occurring on Facebook \citep{fink2018dangerous}.
+There is also research on how the prevalence of hate speech can lead to desensitization---a decreased ability to judge hateful statements as hateful, and in turn to an increase of prejudice \citep{soral2018exposure}, and of social acceptability of hate speech \citep{alvarez2018normative}, or increase of offline hate crime \citep{williams2020hate}.
+Online abuse is also a threat to the stability of online services and their communities.
+It can contribute to lower user engagement or churn \citep{urbaniak2022personal}, directly impacting the profitability of companies.
+In some countries, there are new regulations that introduce severe fines for companies not reacting to reported hate speech or other types of online harm \citep{tworek2021fighting, trengove2022critical}.
+In the past, there were also instances in which companies pulled their ads from online platforms, where violent speech was prevalent \citep{cnbc_2020}.
+On the more extreme side, some companies were sued or even shut down because of online abuse and suicides related to it \citep{newton_2013}.
+Cyberbullying and gun-related threats have been found to play a major role in YikYak decline and shutdown \citep{failory_2022}.
+Snapchat was sued by a mother of a teen who committed suicide after being bullied on a platform \citep{los_angeles_times_2021}, while Formspring closed down in 2013 after a series of suicides among its users \citep{seifert_2013}.
+
+In this paper, we describe  a novel experiment in the collective intelligence paradigm designed to reduce the level of verbal aggression on the Q\&A forum Reddit.
+The collective intelligence approach in its underlying principles entails cooperation between humans and machines to solve a particular problem.
+Detection  algorithms were used to automatically detect verbal aggression in the form of personal attacks and to notify human volunteers, who then responded with counter-speech interventions aimed at the reduction of verbal aggression in  study  participants.
+
+This paper is organized as follows: first, we will sketch the landscape of online content moderation and locate the techniques we used  within it.
+Second, we will outline the theoretical underpinnings of counter-speech interventions utilized in the experiment.
+Then, we describe the experiment itself.
+Having done this, we wrap up  with a  short discussion of  volunteer engagement in this experiment.
 
@@
 It is a form of counter-narrative that seeks to challenge and undermine the messages of hate and extremism, and to promote alternative, positive, and inclusive narratives.
-It can be broadly defined as citizens’ response to hate speech with the purpose of stopping it and reducing its consequences \citep{leader2016dangerous, garland2020countering}.
-Hate speech is a type of speech used with the intention to insult, offend, or intimidate a person based on their identity (such as race, religion, sexual orientation, national origin, or disability) \citep{dictionary2002merriam}.
+It can be broadly defined as citizens’ response to hate speech aimed to stop it and reduce its consequences \citep{leader2016dangerous, garland2020countering}.
+Hate speech is a type of speech used to insult, offend, or intimidate a person based on their identity (such as race, religion, sexual orientation, national origin, or disability) \citep{dictionary2002merriam}.
 This type of speech is often used to spread hateful or discriminatory ideas, both offline and online, and can take many forms, such as name-calling, threats, or slurs.
@@
 The first type has a favorable impact on the hateful user, for example by shifting their discourse or beliefs, and the second one impacts the whole audience of counter-speech, by shifting the norm of the conversation.
-\citep{rieger2018hate} proposed a three-layered classification of counter-speech: primary prevention, where counter-voices are being disseminated to the general public in order to educate and promote civic behavior; secondary prevention, where counter-speech is being directed at specific groups, for example, those more vulnerable to harmful effects of online hate, and tertiary prevention where counter-voices respond directly to those spreading hate.
+\citet{rieger2018hate} proposed a three-layered classification of counter-speech: primary prevention, where counter-voices are being disseminated to the general public to educate and promote civic behavior; secondary prevention, where counter-speech is being directed at specific groups, for example, those more vulnerable to harmful effects of online hate, and tertiary prevention where counter-voices respond directly to those spreading hate.
 Our responses fulfilled all these functions, as they were publicly visible comments sent as direct responses to hateful users.
 
-When it comes to the effectiveness of online counter-speech there is just a handful of large-scale classification studies.
+When it comes to the effectiveness of online counter-speech there is just a handful of large-scale  studies, and even fewer of those who distinguish between different types thereof.
 One of them used a special situation in Germany, where groups that label themselves as hateful or counter-speaking talked about immigration and elections.
-Results based on analysis of 130,000 Twitter conversations suggest that counter speech can help make discussions less divisive, encourage more counter-speech and lead to fewer hateful responses \citep{garland2020countering}.
+Results based on analysis of 130,000 Twitter conversations suggest that counter-speech can help make discussions less divisive, encourage more counter-speech, and lead to fewer hateful responses \citep{garland2020countering}.
 
@@
 Specifically, a sociable moderation style was associated with a decrease in incivility in reply comments, while a regulative style was associated with an increase in incivility.
-This shows that the style of counter responses can also determine their effectiveness.
-
-Moreover, the work by \citet{ziems2020racism} looked at the dynamics of the spread of racial hate during a pandemic and the role of counter speech in mitigating this spread.
-Using a hand-labeled data set of 3,355 tweets, they trained a text classifier to identify hate and counter speech tweets and conducted a longitudinal analysis of tweets and users.
-Interestingly, hateful and counter speech users interacted and engaged extensively with one another, rather than staying in isolated, polarized communities.
-Results revealed that Twitter users were more likely to become hateful after being exposed to hateful content and that counter speech messages may discourage users from becoming hateful, suggesting that consistent counter speech could be a potential solution for effects of hate on social media platforms.
-
- \citep{xie2011social} examined the influence of committed minorities, and looked at how a small group of people with an opinion different from the majority can quickly change the whole group's opinion.
+This shows that the style of counter-responses can also determine their effectiveness.
+
+Moreover,  \citet{ziems2020racism} looked at the dynamics of the spread of racial hate during a pandemic  and the role of counter-speech in mitigating this spread.
+Using a hand-labeled data set of 3,355 tweets, the authors trained a text classifier to identify hate and counter-speech tweets and conducted a longitudinal analysis of tweets and users.
+Interestingly, hateful and counter-speech users interacted and engaged extensively with one another, rather than staying in isolated, polarized communities.
+Results revealed that Twitter users were more likely to become hateful after being exposed to hateful content and that counter-speech messages may discourage users from becoming hateful, suggesting that consistent counter-speech could be a potential remedy for hate on social media platforms.
+
+\citet{xie2011social} examined the influence of committed minorities and looked at how a small group of people with an opinion different from the majority can quickly change the whole group's opinion.
 They found that if more than 10 percent of the group expresses another viewpoint, there is a dramatic decrease in the time taken for the entire population to adopt it.
@@
 
-Similarly, \citep{schieb2016governing} used a computer simulation to study whether counter-speech can curb hate speech on Facebook.
+Similarly, \citet{schieb2016governing} used a computer simulation to study whether counter-speech can curb hate speech on Facebook.
 They found that even a small group of users speaking out against hate can influence a much larger group, as long as there are enough people in the audience who do not hold extreme opinions.
@@
 
-Although some studies suggest censorship and elimination of hateful content to be a more effective strategy of toxicity reduction \citep{alvarez2018normative}, it also also collide with civil liberties and diffuse rather than reduce hate \citep{chandrasekharan2017you}.
-Therefore counter-speech seems to be a golden means for reducing antisocial behavior while preserving civil liberties.
-
-In our study, we have employed counter-speaking strategies to see whether they can be applied to a slightly different phenomenon, namely personal attacks.
+Although some studies suggest censorship and elimination of hateful content to be a more effective strategy of toxicity reduction \citep{alvarez2018normative}, such methods also collide with civil liberties and diffuse rather than reduce hate \citep{chandrasekharan2017you}.
+Therefore, at least \emph{prima facie}, counter-speech seems to be a golden means for reducing antisocial behavior while preserving civil liberties.
+
+In our study, we have applied counter-speech interventions to a slightly different phenomenon, namely personal attacks.
 Personal attacks are instances of speech that are intended to hurt, offend, or belittle a specific person or group.
-This can include name-calling, insults, or other types of derogatory language that is directed at an individual or group \citep{bilewicz2021artificial}.
+These can include name-calling, insults, or other types of derogatory language that is directed at an individual or group \citep{bilewicz2021artificial}.
 While personal attacks and hate speech can sometimes overlap, the main difference between the two is that personal attacks are focused on an individual or a specific group of people, whereas hate speech is aimed at an entire group of people based on their identity.
 
-% we have previously studied the effectiveness of counter-speech in lowering the use of personal attacks on Reddit using an automatic intervention system  \citep{bilewicz2021artificial}.
-
-%In this follow-up study we wanted to see whether
-
-%\citet{benesch2016considerations} recommend counter-speech strategies based on empathy and affiliation, employing humor, warning of consequences of such behavior, labeling and shaming.
-%Although censorship and hateful content elimination has shown to be a more effective strategy of toxicity reduction @alvarez2018normative, it can also collide with civil liberties and diffuse rather than reduce hate @chandrasekharan2017you.
-Therefore counter-speech seems to be a golden mean for reducing antisocial behavior while preserving civil liberties.
 Although counter-speech can be an effective strategy for toxic discourse mitigation, it usually occurs as a spontaneous act, as it is determined by personal motivations of the counter-speaking party.
 For example, \citet{brauer2010descriptive} found that being personally implicated by a counter-normative behavior was a primary determinant of the bystander reaction.
-
-Apart from that, the more public the space, the less likely it is that someone will step up, as studies on bystander interventions consistently show that presence of other people in critical situations reduces the probability of assistance from bystanders \citep{fischer2011bystander}.
-%It is much less likely to happen in natural settings then in a laboratory.
-@?
-
-Moreover, even if a bystander decides to react, they will not necessarily choose the most effective strategy, which can lead to potentially undesirable side-effects.
-For instance,  counter-voices that do not hold up to civic standards themselves but act in an authoritative manner or mock those falling for extremist ideologies, can actually strengthen the underlying attitudes \citep{ziegele2018journalistic, schieb2016governing, legault2011ironic}.
-%empathy here somewhere
-
-The issue of low bystander reactivity has been addressed in our study by engaging volunteers personally committed to lowering online violence, and creating an opportunity structure for quick response, by real-time notifications about the occurrences of personal attacks that they should respond to (see however our section on volunteer engagement for a discussion of difficulties with this strategy).
+Apart from that, the more public the space, the less likely it is that someone will step up, as studies on bystander interventions consistently show that the presence of other people in critical situations reduces the probability of assistance from bystanders \citep{fischer2011bystander}.
+Moreover, even if a bystander decides to react, they will not necessarily choose the most effective strategy, which can lead to potentially undesirable side effects.
+For instance, counter-voices that do not hold up to civic standards themselves but act in an authoritative manner or mock those falling for extremist ideologies can actually strengthen the underlying attitudes \citep{ziegele2018journalistic, schieb2016governing, legault2011ironic}.
 
 To maximize the potential impact of our interventions and to minimize accidental instigation of more verbal aggression, we decided to educate the volunteers on scientifically grounded strategies for normative influence and persuasive messaging.
-Let us elaborate.
-
-ocial norms are agreed to be powerful determinants of human behavior. 
-According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common, cialdini1990focus}.
-
-Multiple studies have found that perceptions of what others are doing cause us to behave similarly.
-Norms can be applied to exert persuasive impact, for example, to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.
-
-%Researchers have repeatedly found that perceptions of what others are doing influences subjects to behave similarly, for example when it comes to choosing consumer product (venkatesen, 1966), or looking at the sky (milgram, bichman, berkowitz, 1969).
-
-%Reasons why social norms have such strong influence on peoples decisions, attitudes, and the way they express them are still disputed. %cytowanie
-
-Some scholars propose that perceived social norms serve as shortcuts helping us quickly adapt to new environments \citep{cialdini1990focus}.
+Drawing from research on social compliance and aggressive behavior, we have created two intervention categories---empathetic and normative---each based on a different mechanism of influence.
+We have used the distinction from our previous experiment where normative and empathetic interventions were automatically generated by a bot in response to personal attacks on Reddit.
+Both types of responses significantly decreased the prevalence of personal attacks, although the study had its limitations.
+For example, the interventions (in a form of public comments) were sent within certain subreddits, so we could not control if the users from one intervention group have not seen interventions from another group
+\citep{bilewicz2021artificial}.
+The current study addresses these limitations by employing a fully randomized experimental design and extending the study to the entire Reddit platform.
+Coming back to our example, this means that the probability that a subject encouters an intervention directed at someone else is much lower.
+
+Another difference is that in the previous study, the interventions were generated automatically, and in this study replies were written and sent by human volunteers.
+We have engaged volunteers personally committed to lowering online violence and created an opportunity structure for quick response, by providing real-time notifications about personal attacks that should receive an intervention.
+We hoped that choosing intrinsically motivated volunteers, and providing them with guidance and AI assistance would solve the issue of bystander apathy (see however our section on volunteer engagement for a discussion of difficulties with this strategy).
+
+\textbf{Empathetic interventions.} Empathetic interventions were thoughtful responses delivered in a gentle and straightforward manner,  empathizing with either the sender of the personal attack, the user who received it, or the both of them.
+We hypothesized that presenting hostile individuals with empathy and kindness would reduce further attacks by interfering with their script of aggressive behavior.
+However, we had no way of verifying the direct effects of our interventions other than the change in the number of personal attacks generated by users.
+
+According to literature, empathy can decrease the tendency to act in a hateful and derogatory manner 
+\citep{zaki2014empathy}.
+Studies on desensitization to hate-speech against refugees conducted by \citet{bilewicz2016psychological} and \citet{soral2022role} found empathy to be an effective countermeasure to this phenomenon.
+Hate-speech desensitization is a lowered sensitivity to hate speech caused by frequent exposition to it.
+As a result, the agent stops perceiving such speech as harmful, which in turn increases their prejudice towards the victims, and, in extreme cases, leads to the dehumanization of stigmatized groups.
+Empathy-inducing interventions made subjects more sensitive to hateful content and more supportive of hate-speech prohibition.
+
+Research on peer aggression has shown that both cognitive and affective empathy can reduce bullying behavior and increase the likelihood of a bystander helping a victim \citep{van2015empathy}.
+A study looking at predictors of either engaging in defending or remaining an outsider in bullying situations, found empathy to be a strong predictor of defending behaviors \citep{nickerson2008attachment}.
+Empathy was also investigated as a factor that can mitigate the negative effects of high social status on bullying behavior amongst 461 primary and secondary school students.
+The results confirmed that high levels of empathy suppressed involvement in bullying and moderated the relationship between bullying and social status
+ \citep{caravita2009unique}.
+
+Similar results were obtained regarding online aggression. For instance, online aggression towards celebrities was shown to be linked to low levels of empathy and high levels of moral disengagement 
+\citep{ouvrein2018online}, and a survey of 2070 secondary school students found that cyberbullies had less empathy \citep{steffgen2011cyberbullies}. 
+A study \citep{barlinska2018cyberbullying} looking at empathy and cyber-bystanding behavior among adolescents, found both affective and cognitive empathy to be positively related to prosocial cyber bystander behavior, with affective empathy being a stronger predictor than cognitive empathy.
+Moreover, the study investigating the bystander effect in cyberbullying has shown that factors such as empathic concern and immediate empathic response increased provided
+ support \citep{machackova2015brief}.
+
+ \citet{wright2021does} conducted a longitudinal analysis of the consequences of being a bystander to homophobic cyberbullying on a sample of 1067 adolescent students.
+According to their findings, witnessing homophobic cyberbullying led to increased perpetration of homophobic cyberbullying, but this effect was moderated by empathy and toxic online disinhibition.
+In other words, high empathy level was one of the factors preventing students from perpetrating online aggression.
+
+Finally, \citet{chin2020empathy} investigated how conversational agents (such as chatbots and smart speakers) should respond to being verbally abused by their users.
+Specifically, they wanted to understand what kind of response style has the most positive impact on emotions that mitigate users’ aggressive behaviors.
+The authors hypothesized that empathetic responses addressing the harm caused by the users will reduce further abuse of the agent by eliciting feelings of guilt in the abusers.
+Indeed, the empathetic response style was most effective in reducing verbal abuse towards the conversational agent, although the feeling of guilt was not directly measured in this study.
+
+\textbf{Normative interventions.} The normative interventions were based on the principle of normative influence.
+Their objective was to reduce personal attacks by lowering the perceived acceptability of such behavior in a particular online setting.
+The normative approach stems from the psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted.
+
+Research has repeatedly shown that perceptions of what others are doing cause us to behave similarly.
+Some scholars propose that it is because perceived social norms serve as shortcuts helping us to quickly adapt to new environments \citep{cialdini1990focus}.
 Others say that we are only motivated by norms we have internalized during socialization, so the normative influence can only be exerted if the norm resonates with our internal value system \citep{morris2018common}.
-%cytowania
-
-The Focus Theory of Normative Conduct \citep{kallgren2000focus} is a  theoretical psychological  framework used for understanding best conditions and practices for exerting normative influence.
-Its main assumption is that norms that are focal in attention are likely to influence behavior.
-One important distinction made within this approach is between two types of norms: a descriptive norm refers to what is typically done, by showing an example of normal behavior in a given situation, and an injunctive or prescriptive norm refers to what is commonly approved, such as the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.
-
-A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while an injunctive norm motivates by informing the agent which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.
-
-%This has important implications for normative influence practitioners, as the same behavior can be prescriptively normative and descriptively not normative, and vice versa.
-In other words, something may be the right thing to do but few people actually do it  \citep{brauer2010descriptive}.
-%truism. say more
-
-The positive influence of injunctive and descriptive norms on unwanted social behavior was first presented in a study on littering in public spaces conducted by \citet{cialdini1990focus}.
-The study subjects were exposed to either descriptive or injunctive anti-littering norms, and the impact on the littering behavior was observed.
+Either way, social norms are agreed to be powerful determinants of human behavior that can be applied to solve social problems, such as littering or resource waste \citep{cialdini2006managing, cialdini1990focus, goldstein2008room, morris2018common}.
+
+One important distinction made within this approach is between two types of norms: 
+descriptive norms that refer to what is typically done and are related to  how others behave, and prescriptive (or injunctive) norms that explicitly describe what is commonly approved, for example, the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.
+In other words, a descriptive norm motivates compliance by providing evidence about what is likely to be effective and adaptive action, while a prescriptive  norm motivates by informing the agent which actions are approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.
+
+In a study on littering in public spaces conducted by \citet{cialdini1990focus}, study subjects were exposed to either descriptive or injunctive anti-littering norms, and the impact on the littering behavior was observed.
 In the descriptive condition, the subjects were exposed to a clean or littered environment, serving as proof of choices made by others.
 In the injunctive condition, the participants received messages stating the anti-littering norm.
-
-Injunctive messages directly asking not to litter had significantly reduced littering.
-The subjects littered more in a highly littered environment and littered less in a clean environment, although these effects were not statistically significant.\footnote{It is also worth noticing that  seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.}
-
-%Some of these results were replicated \citep {berquisr2021replicating} \citep {berger2016norm} %say more
-
-A descriptive norm can be also evoked by providing written information about what others usually do.
-\citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about reuse of hotel towels (“the majority of guests reuse their towels”).
+Results have shown that prescriptive messages directly asking not to litter had significantly reduced littering, and the subjects littered more in a highly littered environment and littered less in a clean environment, although these effects were not statistically significant.\footnote{It is also worth noticing that seeing litter in an otherwise clean environment could have also engaged a prescriptive norm, as it might have reminded subjects about societal objections to littering.}
+
+Descriptive norms can also be evoked by providing written information about what others usually do.
+\citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about the reuse of hotel towels (“the majority of guests reuse their towels”).
 This strategy has been proven superior to traditional appeals focusing on environmental protection.
-Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to, so called, local norms.
-
-The information about how others think and behave can also have an impact on prejudice and its expression.
-For example, positive information about the racial beliefs of others produced stereotype change in message recipients \citep{stangor2001changing}, and public expression of prejudice, and reactions to hostile jokes were highly correlated with social approval of these expressions \citep{crandall2002social}.
-
-When it comes to the online realm, group norm promotion and social sanctioning of online racist harassment resulted in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male).
-In other words, sending direct, counter-speech messages to users with similar identities,  resulted in a decrease in their use of hate speech on Twitter \citep{munger2017tweetment}.
-Moreover, in a study conducted by \citet{bilewicz2021artificial}, a bot disguised as a Reddit user, equipped with normative and empathetic interventions, significantly decreased the number of personal attacks generated in this forum.
-In addition, types of statements made by people in online political discussions influenced the way others expressed their opinions \citep{price2006normative}, and the expression of online hate-speech in  \citep{alvarez2018normative} was strongly dependant on the amount of hate-speech already present in a given environment.
-
-The context of online interactions can also contribute to the spread of counter-normative behaviors.
-For example, negative mood and prior exposition to troll content was the strongest predictor for trolling behavior in \citep{cheng2017anyone}.
-
-In line with the above discussion, for the purpose of this study we have distinguished two types of responses to personal attacks: "empathetic" and "normative".
-The empathetic approach is aimed at countering the so-called desensitization to violence.
-It is a very dangerous process, finally leading to the dehumanization of stigmatized groups.
- Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result, we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice.
-By sending empathetic interventions we hoped to evoke compassion and self-reflection, and  to humanize the person on the other side of the screen \citep{bilewicz2021artificial}.
-
-The normative approach stems from the  already discussed psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted.
-Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms---what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.
-
-\section{Collective Intelligence and  moderation}\label{collective-intelligence-approach-to-counter-speech}
+Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel room”), and so referred to, so-called, local norms.
+
+The information about how others behave or think can also have an impact on prejudice and its expression.
+For example, positive information about the racial beliefs of others produced stereotype change in message recipients \citep{stangor2001changing}, and public expression of prejudice, as well as reactions to hostile jokes were highly correlated with social approval of these expressions \citep{crandall2002social}.
+
+When it comes to the use of normative influence to reduce uncivil behavior online, several norms were activated trough social sanctions,  peer presure and context.
+In a study by  \citet{munger2017tweetment} social sanctioning of racist tweets in the form of messages reminding about the human and labeling the behavior, resulted in the reduction of racist tweets, although only in the condition in which a white male with high followers  approached another white male \citep{munger2017tweetment}.
+In addition, types of statements made by people in online political discussions influenced the way others expressed their opinions \citep{price2006normative}, prior exposure to troll content was a strong predictor for trolling behavior \citep{cheng2017anyone}, and the expression of online hate-speech in \citep{alvarez2018normative} was strongly dependent on the amount of hate-speech already present in a given environment.
+
+We have included both descriptive and prescriptive norms among normative interventions.
+Descriptive norms were expressed by informing the attacker about the prevalence of civil behavior in this community, and prescriptive norms were expressed by informing about the rules of  this community.
+
+\section{Collective Intelligence and  moderation}\label{sec:collective-intelligence}
 
@@
 Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its members.
-Volunteers, after receiving a notification on Slack, could then react with a proper intervention.
+Volunteers, after receiving a notification on Slack, could then react with an appropriate intervention.
 Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence—utilizing human + machine intelligence to develop solutions to social challenges.
@@
 Here are some examples of interventions that were used during the experiment:
+
 \begin{itemize}
@@
 Although empathy has been found to be helpful in the reduction of aggressive behavior \citep{bjorkqvist2000social}, and the improvement of intergroup relations \citep{stephan1999role}, there are also important arguments and evidence concerning its limits.
-Specifically, Paul Bloom in his book \emph{}Against Empathy: The Case for Rational Compassion} \citep{bloom2017against}, stresses that empathy can have a very narrow focus and can be prone to biases.
+Specifically, Paul Bloom in his book \emph{Against Empathy: The Case for Rational Compassion} \citep{bloom2017against}, stresses that empathy can have a very narrow focus and can be prone to biases.
 For instance, it’s easier to be empathetic towards those who are close or similar to us.
@@
 attack' subsumes the use of specific terms which compare other people to
-animals or objects or making nasty insinuations without providing
+animals or objects or make nasty insinuations without providing
 evidence. Three examples of typical personal attacks are as follows:
@@
 \begin{itemize} 
-\item \emph{You are legit mentally retarded homie.}
-\item \emph {Eat a bag of dicks, fuckstick.}
-\item \emph {Fuck off with your sensitivity you douche.} 
+\item \emph{You sound like a whiney bitch.}
+\item \emph {Proof my dick in your ass u flairless fucken hoe.}
+\item \emph {Go cuddle your anime pillow dipshit.} 
 \end{itemize}
@@
 
-We conducted a 6-months field experiment in a digital setting conducted on a popular Q\&A and news forum, Reddit (\url{www.reddit.com}).
-We formed treatment and control groups based on three main criteria:
+We conducted a 6-month  experiment in a digital setting conducted on a popular Q\&A and news forum, Reddit (\url{www.reddit.com}). We formed treatment and control groups based on three main criteria:
 
@@
 
-The efficiency of normative interventions seems overall higher, except
+The effectiveness of normative interventions seems overall higher, except
 for low-aggression users, for which empathetic interventions might be
@@
 
-%% \section{}
-%% \label{}
-
-%% For citations use: 
-%%       \citet{<label>} ==> Jones et al. [21]
-%%       \citep{<label>} ==> [21]
-%%
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-%%\begin{thebibliography}{00}
-
-%% \bibitem[Author(year)]{label}
-%% Text of bibliographic item
-
-%%\bibitem[ ()]{}
-
-%%\end{thebibliography}
+% %% \section{}
+% %% \label{}
+
+% %% For citations use: 
+% %%       \citet{<label>} ==> Jones et al. [21]
+% %%       \citep{<label>} ==> [21]
+% %%
+
+% %% If you have bibdatabase file and want bibtex to generate the
+% %% bibitems, please use
+% %%
+
+% %% else use the following coding to input the bibitems directly in the
+% %% TeX file.
+
+% %%\begin{thebibliography}{00}
+
+% %% \bibitem[Author(year)]{label}
+% %% Text of bibliographic item
+
+% %%\bibitem[ ()]{}
+
+% %%\end{thebibliography}
 
@@
 
-%update when done
-
-\begin{thebibliography}{91}
+\begin{thebibliography}{115}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 \ifx\xfnm\relax \def\xfnm[#1]{\unskip,\space#1}\fi
+%Type = Article
+\bibitem[{Alhujailli et~al.(2020)Alhujailli, Karwowski, Wan and
+  Hancock}]{alhujailli2020affective}
+\bibinfo{author}{Alhujailli, A.}, \bibinfo{author}{Karwowski, W.},
+  \bibinfo{author}{Wan, T.T.}, \bibinfo{author}{Hancock, P.},
+  \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Affective and stress consequences of cyberbullying}.
+\newblock \bibinfo{journal}{Symmetry} \bibinfo{volume}{12},
+  \bibinfo{pages}{1536}.
+%Type = Article
+\bibitem[{{\'A}lvarez-Benjumea and Winter(2018)}]{alvarez2018normative}
+\bibinfo{author}{{\'A}lvarez-Benjumea, A.}, \bibinfo{author}{Winter, F.},
+  \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Normative change and culture of hate: An experiment
+  in online environments}.
+\newblock \bibinfo{journal}{European Sociological Review} \bibinfo{volume}{34},
+  \bibinfo{pages}{223--237}.
+%Type = Article
+\bibitem[{Barlett et~al.(2021)Barlett, Simmers, Roth and
+  Gentile}]{barlett2021comparing}
+\bibinfo{author}{Barlett, C.P.}, \bibinfo{author}{Simmers, M.M.},
+  \bibinfo{author}{Roth, B.}, \bibinfo{author}{Gentile, D.},
+  \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Comparing cyberbullying prevalence and process before
+  and during the covid-19 pandemic}.
+\newblock \bibinfo{journal}{The Journal of Social Psychology} ,
+  \bibinfo{pages}{1--11}.
+%Type = Article
+\bibitem[{Barli{\'n}ska et~al.(2018)Barli{\'n}ska, Szuster and
+  Winiewski}]{barlinska2018cyberbullying}
+\bibinfo{author}{Barli{\'n}ska, J.}, \bibinfo{author}{Szuster, A.},
+  \bibinfo{author}{Winiewski, M.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Cyberbullying among adolescent bystanders: Role of
+  affective versus cognitive empathy in increasing prosocial cyberbystander
+  behavior}.
+\newblock \bibinfo{journal}{Frontiers in psychology} \bibinfo{volume}{9},
+  \bibinfo{pages}{799}.
+%Type = Article
+\bibitem[{Benesch et~al.(2016)Benesch, Ruths, Dillon, Saleem and
+  Wright}]{benesch2016considerations}
+\bibinfo{author}{Benesch, S.}, \bibinfo{author}{Ruths, D.},
+  \bibinfo{author}{Dillon, K.P.}, \bibinfo{author}{Saleem, H.M.},
+  \bibinfo{author}{Wright, L.}, \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Considerations for successful counterspeech}.
+\newblock \bibinfo{journal}{Dangerous Speech Project} .
+%Type = Misc
+\bibitem[{Bhattacharya(2021)}]{bhattacharya}
+\bibinfo{author}{Bhattacharya, A.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{How {Covid}-19 lockdowns weakened {Facebook}'s
+  content moderation algorithms}.
+\newblock \URLprefix
+  \url{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}.
+%Type = Article
+\bibitem[{Bilewicz(2016)}]{bilewicz2016psychological}
+\bibinfo{author}{Bilewicz, M.}, \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Psychological antecedents of social distance. what
+  leads to contact avoidance?}
+\newblock \bibinfo{journal}{NAUKA} .
+%Type = Article
+\bibitem[{Bilewicz et~al.(2021)Bilewicz, Tempska, Leliwa, Dowgia{\l}{\l}o,
+  Ta{\'n}ska, Urbaniak and Wroczy{\'n}ski}]{bilewicz2021artificial}
+\bibinfo{author}{Bilewicz, M.}, \bibinfo{author}{Tempska, P.},
+  \bibinfo{author}{Leliwa, G.}, \bibinfo{author}{Dowgia{\l}{\l}o, M.},
+  \bibinfo{author}{Ta{\'n}ska, M.}, \bibinfo{author}{Urbaniak, R.},
+  \bibinfo{author}{Wroczy{\'n}ski, M.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Artificial intelligence against hate: Intervention
+  reducing verbal aggression in the social network environment}.
+\newblock \bibinfo{journal}{Aggressive behavior} \bibinfo{volume}{47},
+  \bibinfo{pages}{260--266}.
+%Type = Inproceedings
+\bibitem[{Binns et~al.(2017)Binns, Veale, Van~Kleek and
+  Shadbolt}]{binns2017like}
+\bibinfo{author}{Binns, R.}, \bibinfo{author}{Veale, M.},
+  \bibinfo{author}{Van~Kleek, M.}, \bibinfo{author}{Shadbolt, N.},
+  \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Like trainer, like bot? inheritance of bias in
+  algorithmic content moderation}, in: \bibinfo{booktitle}{International
+  conference on social informatics}, \bibinfo{organization}{Springer}. pp.
+  \bibinfo{pages}{405--415}.
+%Type = Article
+\bibitem[{Bj{\"o}rkqvist et~al.(2000)Bj{\"o}rkqvist, {\"O}sterman and
+  Kaukiainen}]{bjorkqvist2000social}
+\bibinfo{author}{Bj{\"o}rkqvist, K.}, \bibinfo{author}{{\"O}sterman, K.},
+  \bibinfo{author}{Kaukiainen, A.}, \bibinfo{year}{2000}.
+\newblock \bibinfo{title}{Social intelligence-empathy= aggression?}
+\newblock \bibinfo{journal}{Aggression and violent behavior}
+  \bibinfo{volume}{5}, \bibinfo{pages}{191--200}.
+%Type = Book
+\bibitem[{Bloom(2017)}]{bloom2017against}
+\bibinfo{author}{Bloom, P.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Against empathy: The case for rational compassion}.
+\newblock \bibinfo{publisher}{Random House}.
+%Type = Article
+\bibitem[{Brauer and Chaurand(2010)}]{brauer2010descriptive}
+\bibinfo{author}{Brauer, M.}, \bibinfo{author}{Chaurand, N.},
+  \bibinfo{year}{2010}.
+\newblock \bibinfo{title}{Descriptive norms, prescriptive norms, and social
+  control: An intercultural comparison of people's reactions to uncivil
+  behaviors}.
+\newblock \bibinfo{journal}{European Journal of Social Psychology}
+  \bibinfo{volume}{40}, \bibinfo{pages}{490--499}.
+%Type = Article
+\bibitem[{Caravita et~al.(2009)Caravita, Di~Blasio and
+  Salmivalli}]{caravita2009unique}
+\bibinfo{author}{Caravita, S.C.}, \bibinfo{author}{Di~Blasio, P.},
+  \bibinfo{author}{Salmivalli, C.}, \bibinfo{year}{2009}.
+\newblock \bibinfo{title}{Unique and interactive effects of empathy and social
+  status on involvement in bullying}.
+\newblock \bibinfo{journal}{Social development} \bibinfo{volume}{18},
+  \bibinfo{pages}{140--163}.
+%Type = Article
+\bibitem[{Chandrasekharan et~al.(2017)Chandrasekharan, Pavalanathan,
+  Srinivasan, Glynn, Eisenstein and Gilbert}]{chandrasekharan2017you}
+\bibinfo{author}{Chandrasekharan, E.}, \bibinfo{author}{Pavalanathan, U.},
+  \bibinfo{author}{Srinivasan, A.}, \bibinfo{author}{Glynn, A.},
+  \bibinfo{author}{Eisenstein, J.}, \bibinfo{author}{Gilbert, E.},
+  \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{You can't stay here: The efficacy of {R}eddit's 2015
+  ban examined through hate speech}.
+\newblock \bibinfo{journal}{Proceedings of the ACM on Human-Computer
+  Interaction} \bibinfo{volume}{1}, \bibinfo{pages}{1--22}.
+%Type = Inproceedings
+\bibitem[{Cheng et~al.(2017)Cheng, Bernstein, Danescu-Niculescu-Mizil and
+  Leskovec}]{cheng2017anyone}
+\bibinfo{author}{Cheng, J.}, \bibinfo{author}{Bernstein, M.},
+  \bibinfo{author}{Danescu-Niculescu-Mizil, C.}, \bibinfo{author}{Leskovec,
+  J.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Anyone can become a troll: Causes of trolling
+  behavior in online discussions}, in: \bibinfo{booktitle}{Proceedings of the
+  2017 ACM conference on computer supported cooperative work and social
+  computing}, pp. \bibinfo{pages}{1217--1230}.
+%Type = Inproceedings
+\bibitem[{Chin et~al.(2020)Chin, Molefi and Yi}]{chin2020empathy}
+\bibinfo{author}{Chin, H.}, \bibinfo{author}{Molefi, L.W.},
+  \bibinfo{author}{Yi, M.Y.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Empathy is all you need: How a conversational agent
+  should respond to verbal abuse}, in: \bibinfo{booktitle}{Proceedings of the
+  2020 CHI conference on human factors in computing systems}, pp.
+  \bibinfo{pages}{1--13}.
+%Type = Article
+\bibitem[{Cialdini et~al.(2006)Cialdini, Demaine, Sagarin, Barrett, Rhoads and
+  Winter}]{cialdini2006managing}
+\bibinfo{author}{Cialdini, R.B.}, \bibinfo{author}{Demaine, L.J.},
+  \bibinfo{author}{Sagarin, B.J.}, \bibinfo{author}{Barrett, D.W.},
+  \bibinfo{author}{Rhoads, K.}, \bibinfo{author}{Winter, P.L.},
+  \bibinfo{year}{2006}.
+\newblock \bibinfo{title}{Managing social norms for persuasive impact}.
+\newblock \bibinfo{journal}{Social influence} \bibinfo{volume}{1},
+  \bibinfo{pages}{3--15}.
+%Type = Article
+\bibitem[{Cialdini and Goldstein(2004)}]{cialdini2004social}
+\bibinfo{author}{Cialdini, R.B.}, \bibinfo{author}{Goldstein, N.J.},
+  \bibinfo{year}{2004}.
+\newblock \bibinfo{title}{Social influence: Compliance and conformity}.
+\newblock \bibinfo{journal}{Annual review of psychology} \bibinfo{volume}{55},
+  \bibinfo{pages}{591--621}.
+%Type = Article
+\bibitem[{Cialdini et~al.(1990)Cialdini, Reno and Kallgren}]{cialdini1990focus}
+\bibinfo{author}{Cialdini, R.B.}, \bibinfo{author}{Reno, R.R.},
+  \bibinfo{author}{Kallgren, C.A.}, \bibinfo{year}{1990}.
+\newblock \bibinfo{title}{A focus theory of normative conduct: Recycling the
+  concept of norms to reduce littering in public places.}
+\newblock \bibinfo{journal}{Journal of personality and social psychology}
+  \bibinfo{volume}{58}, \bibinfo{pages}{1015}.
+%Type = Article
+\bibitem[{Crandall et~al.(2002)Crandall, Eshleman and
+  O'brien}]{crandall2002social}
+\bibinfo{author}{Crandall, C.S.}, \bibinfo{author}{Eshleman, A.},
+  \bibinfo{author}{O'brien, L.}, \bibinfo{year}{2002}.
+\newblock \bibinfo{title}{Social norms and the expression and suppression of
+  prejudice: the struggle for internalization.}
+\newblock \bibinfo{journal}{Journal of personality and social psychology}
+  \bibinfo{volume}{82}, \bibinfo{pages}{359}.
+%Type = Misc
+\bibitem[{Data(2021)}]{onlinesafetydata}
+\bibinfo{author}{Data, O.S.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{About the online safety data initiative}.
+\newblock \URLprefix \url{https://onlinesafetydata.blog.gov.uk/about-us/}.
+%Type = Misc
+\bibitem[{Dean(2021)}]{los_angeles_times_2021}
+\bibinfo{author}{Dean, S.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{A teen who was bullied on snapchat died. his mom is
+  suing to hold social media liable}.
+\newblock \URLprefix
+  \url{https://www.latimes.com/business/story/2021-05-10/lawsuit-snap-teen-suicide-yolo-lmk}.
+%Type = Article
+\bibitem[{D{\'\i}az-Narv{\'a}ez et~al.(2015)D{\'\i}az-Narv{\'a}ez, Coronado,
+  Bilbao, Gonz{\'a}lez, Padilla, Howard, Silva, Bullen, Gutierrez, de~Villalba
+  et~al.}]{diaz2015empathy}
+\bibinfo{author}{D{\'\i}az-Narv{\'a}ez, V.P.}, \bibinfo{author}{Coronado,
+  A.M.E.}, \bibinfo{author}{Bilbao, J.L.}, \bibinfo{author}{Gonz{\'a}lez, F.},
+  \bibinfo{author}{Padilla, M.}, \bibinfo{author}{Howard, M.},
+  \bibinfo{author}{Silva, M.G.}, \bibinfo{author}{Bullen, M.},
+  \bibinfo{author}{Gutierrez, F.}, \bibinfo{author}{de~Villalba, T.V.}, et~al.,
+  \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Empathy gender in dental students in latin america:
+  an exploratory and cross-sectional study}.
+\newblock \bibinfo{journal}{Health} \bibinfo{volume}{7}, \bibinfo{pages}{1527}.
+%Type = Article
+\bibitem[{Dictionary(2002)}]{dictionary2002merriam}
+\bibinfo{author}{Dictionary, M.W.}, \bibinfo{year}{2002}.
+\newblock \bibinfo{title}{Merriam-webster}.
+\newblock \bibinfo{journal}{On-line at http://www. mw. com/home. htm}
+  \bibinfo{volume}{8}, \bibinfo{pages}{2}.
+%Type = Article
+\bibitem[{Esteva et~al.(2017)Esteva, Kuprel, Novoa, Ko, Swetter, Blau and
+  Thrun}]{esteva_dermatologist-level_2017}
+\bibinfo{author}{Esteva, A.}, \bibinfo{author}{Kuprel, B.},
+  \bibinfo{author}{Novoa, R.A.}, \bibinfo{author}{Ko, J.},
+  \bibinfo{author}{Swetter, S.M.}, \bibinfo{author}{Blau, H.M.},
+  \bibinfo{author}{Thrun, S.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Dermatologist-level classification of skin cancer
+  with deep neural networks}.
+\newblock \bibinfo{journal}{Nature} \bibinfo{volume}{542},
+  \bibinfo{pages}{115--118}.
+\newblock \URLprefix \url{http://www.nature.com/articles/nature21056},
+  \DOIprefix\doi{10.1038/nature21056}.
+%Type = Misc
+\bibitem[{Failory(2022)}]{failory_2022}
+\bibinfo{author}{Failory}, \bibinfo{year}{2022}.
+\newblock \bibinfo{title}{Yik yak's shut down: Why did the location-based app
+  failed?}
+\newblock \URLprefix \url{https://www.failory.com/cemetery/yik-yak}.
+%Type = Article
+\bibitem[{Fink(2018)}]{fink2018dangerous}
+\bibinfo{author}{Fink, C.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Dangerous speech, anti-muslim violence, and facebook
+  in myanmar}.
+\newblock \bibinfo{journal}{Journal of International Affairs}
+  \bibinfo{volume}{71}, \bibinfo{pages}{43--52}.
+%Type = Article
+\bibitem[{Fischer et~al.(2011)Fischer, Krueger, Greitemeyer, Vogrincic,
+  Kastenm{\""u}ller, Frey, Heene, Wicher and Kainbacher}]{fischer2011bystander}
+\bibinfo{author}{Fischer, P.}, \bibinfo{author}{Krueger, J.I.},
+  \bibinfo{author}{Greitemeyer, T.}, \bibinfo{author}{Vogrincic, C.},
+  \bibinfo{author}{Kastenm{\""u}ller, A.}, \bibinfo{author}{Frey, D.},
+  \bibinfo{author}{Heene, M.}, \bibinfo{author}{Wicher, M.},
+  \bibinfo{author}{Kainbacher, M.}, \bibinfo{year}{2011}.
+\newblock \bibinfo{title}{The bystander-effect: a meta-analytic review on
+  bystander intervention in dangerous and non-dangerous emergencies.}
+\newblock \bibinfo{journal}{Psychological bulletin} \bibinfo{volume}{137},
+  \bibinfo{pages}{517}.
+%Type = Misc
+\bibitem[{French(2021)}]{french_as_2021}
+\bibinfo{author}{French, C.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{As the pandemic forces us online, {LGBTQ2S}+ teens
+  deal with cyberbullying}.
+\newblock \URLprefix
+  \url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}.
+%Type = Article
+\bibitem[{Garland et~al.(2020)Garland, Ghazi-Zahedi, Young, H{\'e}bert-Dufresne
+  and Galesic}]{garland2020countering}
+\bibinfo{author}{Garland, J.}, \bibinfo{author}{Ghazi-Zahedi, K.},
+  \bibinfo{author}{Young, J.G.}, \bibinfo{author}{H{\'e}bert-Dufresne, L.},
+  \bibinfo{author}{Galesic, M.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Countering hate on social media: Large scale
+  classification of hate and counter speech}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2006.01974} .
+%Type = Article
+\bibitem[{Gerrard(2020)}]{gerrard2020covid19}
+\bibinfo{author}{Gerrard, Y.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{<? covid19?> the covid-19 mental health content
+  moderation conundrum}.
+\newblock \bibinfo{journal}{Social Media+ Society} \bibinfo{volume}{6},
+  \bibinfo{pages}{2056305120948186}.
+%Type = Article
+\bibitem[{Geva et~al.(2019)Geva, Goldberg and Berant}]{geva2019we}
+\bibinfo{author}{Geva, M.}, \bibinfo{author}{Goldberg, Y.},
+  \bibinfo{author}{Berant, J.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Are we modeling the task or the annotator? an
+  investigation of annotator bias in natural language understanding datasets}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:1908.07898} .
+%Type = Article
+\bibitem[{Goldstein et~al.(2008)Goldstein, Cialdini and
+  Griskevicius}]{goldstein2008room}
+\bibinfo{author}{Goldstein, N.J.}, \bibinfo{author}{Cialdini, R.B.},
+  \bibinfo{author}{Griskevicius, V.}, \bibinfo{year}{2008}.
+\newblock \bibinfo{title}{A room with a viewpoint: Using social norms to
+  motivate environmental conservation in hotels}.
+\newblock \bibinfo{journal}{Journal of consumer Research} \bibinfo{volume}{35},
+  \bibinfo{pages}{472--482}.
+%Type = Misc
+\bibitem[{Grant(2021)}]{grant_2021}
+\bibinfo{author}{Grant, J.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Australia’s esafety commissioner targets abuse
+  online as covid-19 supercharges cyberbullying | the strategist}.
+\newblock \URLprefix
+  \url{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}.
+%Type = Inproceedings
+\bibitem[{Gr{\"o}ndahl et~al.(2018)Gr{\"o}ndahl, Pajola, Juuti, Conti and
+  Asokan}]{grondahl2018all}
+\bibinfo{author}{Gr{\"o}ndahl, T.}, \bibinfo{author}{Pajola, L.},
+  \bibinfo{author}{Juuti, M.}, \bibinfo{author}{Conti, M.},
+  \bibinfo{author}{Asokan, N.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{All you need is" love" evading hate speech
+  detection}, in: \bibinfo{booktitle}{Proceedings of the 11th ACM workshop on
+  artificial intelligence and security}, pp. \bibinfo{pages}{2--12}.
+%Type = Article
+\bibitem[{Hasson et~al.(2018)Hasson, Tamir, Brahms, Cohrs and
+  Halperin}]{hasson2018liberals}
+\bibinfo{author}{Hasson, Y.}, \bibinfo{author}{Tamir, M.},
+  \bibinfo{author}{Brahms, K.S.}, \bibinfo{author}{Cohrs, J.C.},
+  \bibinfo{author}{Halperin, E.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Are liberals and conservatives equally motivated to
+  feel empathy toward others?}
+\newblock \bibinfo{journal}{Personality and Social Psychology Bulletin}
+  \bibinfo{volume}{44}, \bibinfo{pages}{1449--1459}.
+%Type = Article
+\bibitem[{Hinduja and Patchin(2010)}]{hinduja2010bullying}
+\bibinfo{author}{Hinduja, S.}, \bibinfo{author}{Patchin, J.W.},
+  \bibinfo{year}{2010}.
+\newblock \bibinfo{title}{Bullying, cyberbullying, and suicide}.
+\newblock \bibinfo{journal}{Archives of suicide research} \bibinfo{volume}{14},
+  \bibinfo{pages}{206--221}.
+%Type = Article
+\bibitem[{Hoff and Mitchell(2009)}]{hoff2009cyberbullying}
+\bibinfo{author}{Hoff, D.L.}, \bibinfo{author}{Mitchell, S.N.},
+  \bibinfo{year}{2009}.
+\newblock \bibinfo{title}{Cyberbullying: Causes, effects, and remedies}.
+\newblock \bibinfo{journal}{Journal of Educational Administration} .
+%Type = Article
+\bibitem[{Jordan and Mitchell(2015)}]{jordan2015machine}
+\bibinfo{author}{Jordan, M.I.}, \bibinfo{author}{Mitchell, T.M.},
+  \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Machine learning: Trends, perspectives, and
+  prospects}.
+\newblock \bibinfo{journal}{Science} \bibinfo{volume}{349},
+  \bibinfo{pages}{255--260}.
+%Type = Article
+\bibitem[{Kallgren et~al.(2000)Kallgren, Reno and Cialdini}]{kallgren2000focus}
+\bibinfo{author}{Kallgren, C.A.}, \bibinfo{author}{Reno, R.R.},
+  \bibinfo{author}{Cialdini, R.B.}, \bibinfo{year}{2000}.
+\newblock \bibinfo{title}{A focus theory of normative conduct: When norms do
+  and do not affect behavior}.
+\newblock \bibinfo{journal}{Personality and social psychology bulletin}
+  \bibinfo{volume}{26}, \bibinfo{pages}{1002--1012}.
+%Type = Inproceedings
+\bibitem[{Karunakaran and Ramakrishan(2019)}]{karunakaran2019testing}
+\bibinfo{author}{Karunakaran, S.}, \bibinfo{author}{Ramakrishan, R.},
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Testing stylistic interventions to reduce emotional
+  impact of content moderation workers}, in: \bibinfo{booktitle}{Proceedings of
+  the AAAI Conference on Human Computation and Crowdsourcing}, pp.
+  \bibinfo{pages}{50--58}.
+%Type = Book
+\bibitem[{Keipi et~al.(2016)Keipi, N{\"a}si, Oksanen and
+  R{\"a}s{\"a}nen}]{keipi2016online}
+\bibinfo{author}{Keipi, T.}, \bibinfo{author}{N{\"a}si, M.},
+  \bibinfo{author}{Oksanen, A.}, \bibinfo{author}{R{\"a}s{\"a}nen, P.},
+  \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Online hate and harmful content: Cross-national
+  perspectives}.
+\newblock \bibinfo{publisher}{Taylor \& Francis}.
+%Type = Misc
+\bibitem[{Koetsier(2020)}]{koetsier_report}
+\bibinfo{author}{Koetsier, J.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Report: {Facebook} {Makes} 300,000 {Content}
+  {Moderation} {Mistakes} {Every} {Day}}.
+\newblock \URLprefix
+  \url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/}.
+%Type = Article
+\bibitem[{Kowalski and Limber(2013)}]{kowalski2013psychological}
+\bibinfo{author}{Kowalski, R.M.}, \bibinfo{author}{Limber, S.P.},
+  \bibinfo{year}{2013}.
+\newblock \bibinfo{title}{Psychological, physical, and academic correlates of
+  cyberbullying and traditional bullying}.
+\newblock \bibinfo{journal}{Journal of adolescent health} \bibinfo{volume}{53},
+  \bibinfo{pages}{S13--S20}.
+%Type = Misc
+\bibitem[{L1ght(2020)}]{noauthor_l1ght_2020}
+\bibinfo{author}{L1ght}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{L1ght releases groundbreaking report on
+  corona-related hate speech and online toxicity}.
+\newblock \URLprefix
+  \url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}.
+%Type = Misc
+\bibitem[{the Label(2017)}]{noauthor_:game_nodate}
+\bibinfo{author}{the Label, D.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{In:{Game} {Abuse}}.
+\newblock \URLprefix
+  \url{https://www.ditchthelabel.org/research-papers/ingame-abuse/}.
 %Type = Misc
 \bibitem[{Laub(2019)}]{Zachary_hate}
-\bibinfo{author}{Z.~Laub}, \bibinfo{title}{Hate {Speech} on {Social} {Media}:
-  {Global} {Comparisons}}, \bibinfo{year}{2019}. \URLprefix
+\bibinfo{author}{Laub, Z.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Hate {Speech} on {Social} {Media}: {Global}
+  {Comparisons}}.
+\newblock \URLprefix
   \url{https://www.cfr.org/backgrounder/hate-speech-social-media-global-comparisons}.
 %Type = Article
-\bibitem[{Sorrentino et~al.(2019)Sorrentino, Baldry, Farrington, and
+\bibitem[{Leader~Maynard and Benesch(2016)}]{leader2016dangerous}
+\bibinfo{author}{Leader~Maynard, J.}, \bibinfo{author}{Benesch, S.},
+  \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Dangerous speech and dangerous ideology: An
+  integrated model for monitoring and prevention}.
+\newblock \bibinfo{journal}{Genocide Studies and Prevention}
+  \bibinfo{volume}{9}.
+%Type = Misc
+\bibitem[{League(2020)}]{ADL_free}
+\bibinfo{author}{League, A.D.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Free to {Play}? {Hate}, {Harassment} and {Positive}
+  {Social} {Experience} in {Online} {Games} 2020}.
+\newblock \URLprefix \url{https://www.adl.org/free-to-play-2020}.
+%Type = Article
+\bibitem[{LeCun et~al.(2015)LeCun, Bengio and Hinton}]{lecun2015deep}
+\bibinfo{author}{LeCun, Y.}, \bibinfo{author}{Bengio, Y.},
+  \bibinfo{author}{Hinton, G.}, \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Deep learning}.
+\newblock \bibinfo{journal}{nature} \bibinfo{volume}{521},
+  \bibinfo{pages}{436--444}.
+%Type = Article
+\bibitem[{Lee and Leets(2002)}]{lee2002persuasive}
+\bibinfo{author}{Lee, E.}, \bibinfo{author}{Leets, L.}, \bibinfo{year}{2002}.
+\newblock \bibinfo{title}{Persuasive storytelling by hate groups online:
+  Examining its effects on adolescents}.
+\newblock \bibinfo{journal}{American behavioral scientist}
+  \bibinfo{volume}{45}, \bibinfo{pages}{927--957}.
+%Type = Article
+\bibitem[{Legault et~al.(2011)Legault, Gutsell and
+  Inzlicht}]{legault2011ironic}
+\bibinfo{author}{Legault, L.}, \bibinfo{author}{Gutsell, J.N.},
+  \bibinfo{author}{Inzlicht, M.}, \bibinfo{year}{2011}.
+\newblock \bibinfo{title}{Ironic effects of antiprejudice messages: How
+  motivational interventions can reduce (but also increase) prejudice}.
+\newblock \bibinfo{journal}{Psychological Science} \bibinfo{volume}{22},
+  \bibinfo{pages}{1472--1477}.
+%Type = Misc
+\bibitem[{Lin(2021)}]{noauthor_10_2021}
+\bibinfo{author}{Lin, Y.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{10 {Twitter} {Statistics} {Every} {Marketer} {Should}
+  {Know} in 2021 [{Infographic}]}.
+\newblock \URLprefix \url{https://www.oberlo.com/blog/twitter-statistics}.
+%Type = Article
+\bibitem[{Lipton and Steinhardt(2019)}]{lipton2019troubling}
+\bibinfo{author}{Lipton, Z.C.}, \bibinfo{author}{Steinhardt, J.},
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Troubling trends in machine learning scholarship:
+  Some ml papers suffer from flaws that could mislead the public and stymie
+  future research.}
+\newblock \bibinfo{journal}{Queue} \bibinfo{volume}{17},
+  \bibinfo{pages}{45--77}.
+%Type = Article
+\bibitem[{MacAvaney et~al.(2019)MacAvaney, Yao, Yang, Russell, Goharian and
+  Frieder}]{macavaney2019hate}
+\bibinfo{author}{MacAvaney, S.}, \bibinfo{author}{Yao, H.R.},
+  \bibinfo{author}{Yang, E.}, \bibinfo{author}{Russell, K.},
+  \bibinfo{author}{Goharian, N.}, \bibinfo{author}{Frieder, O.},
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Hate speech detection: Challenges and solutions}.
+\newblock \bibinfo{journal}{PloS one} \bibinfo{volume}{14},
+  \bibinfo{pages}{e0221152}.
+%Type = Article
+\bibitem[{Machackova et~al.(2015)Machackova, Dedkova and
+  Mezulanikova}]{machackova2015brief}
+\bibinfo{author}{Machackova, H.}, \bibinfo{author}{Dedkova, L.},
+  \bibinfo{author}{Mezulanikova, K.}, \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Brief report: The bystander effect in cyberbullying
+  incidents}.
+\newblock \bibinfo{journal}{Journal of adolescence} \bibinfo{volume}{43},
+  \bibinfo{pages}{96--99}.
+%Type = Misc
+\bibitem[{McGee(2012)}]{noauthor_facebook:_2012}
+\bibinfo{author}{McGee, M.}, \bibinfo{year}{2012}.
+\newblock \bibinfo{title}{Facebook: 3.2 {Billion} {Likes} \& {Comments} {Every}
+  {Day}}.
+\newblock \URLprefix
+  \url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}.
+%Type = Article
+\bibitem[{Mehrabi et~al.(2021)Mehrabi, Morstatter, Saxena, Lerman and
+  Galstyan}]{mehrabi2021survey}
+\bibinfo{author}{Mehrabi, N.}, \bibinfo{author}{Morstatter, F.},
+  \bibinfo{author}{Saxena, N.}, \bibinfo{author}{Lerman, K.},
+  \bibinfo{author}{Galstyan, A.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{A survey on bias and fairness in machine learning}.
+\newblock \bibinfo{journal}{ACM Computing Surveys (CSUR)} \bibinfo{volume}{54},
+  \bibinfo{pages}{1--35}.
+%Type = Article
+\bibitem[{Melis et~al.(2017)Melis, Dyer and Blunsom}]{melis2017state}
+\bibinfo{author}{Melis, G.}, \bibinfo{author}{Dyer, C.},
+  \bibinfo{author}{Blunsom, P.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{On the state of the art of evaluation in neural
+  language models}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:1707.05589} .
+%Type = Article
+\bibitem[{Morris and Cushman(2018)}]{morris2018common}
+\bibinfo{author}{Morris, A.}, \bibinfo{author}{Cushman, F.},
+  \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{A common framework for theories of norm compliance}.
+\newblock \bibinfo{journal}{Social Philosophy and Policy} \bibinfo{volume}{35},
+  \bibinfo{pages}{101--127}.
+%Type = Article
+\bibitem[{Munger(2017)}]{munger2017tweetment}
+\bibinfo{author}{Munger, K.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Tweetment effects on the tweeted: Experimentally
+  reducing racist harassment}.
+\newblock \bibinfo{journal}{Political Behavior} \bibinfo{volume}{39},
+  \bibinfo{pages}{629--649}.
+%Type = Inproceedings
+\bibitem[{Musgrave et~al.(2020)Musgrave, Belongie and Lim}]{musgrave2020metric}
+\bibinfo{author}{Musgrave, K.}, \bibinfo{author}{Belongie, S.},
+  \bibinfo{author}{Lim, S.N.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{A metric learning reality check}, in:
+  \bibinfo{booktitle}{European Conference on Computer Vision},
+  \bibinfo{organization}{Springer}. pp. \bibinfo{pages}{681--699}.
+%Type = Misc
+\bibitem[{Newton(2013)}]{newton_2013}
+\bibinfo{author}{Newton, C.}, \bibinfo{year}{2013}.
+\newblock \bibinfo{title}{Killer app: Why do anonymous q\&a networks keep
+  leading to suicides?}
+\newblock \URLprefix
+  \url{https://www.theverge.com/2013/9/17/4740902/no-good-answers-why-didnt-ask-fm-learn-from-the-formspring-suicides}.
+%Type = Misc
+\bibitem[{Newton(2020)}]{newton_facebook_2020}
+\bibinfo{author}{Newton, C.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Facebook will pay \$52 million in settlement with
+  moderators who developed {PTSD} on the job}.
+\newblock \URLprefix
+  \url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}.
+%Type = Article
+\bibitem[{Nickerson et~al.(2008)Nickerson, Mele and
+  Princiotta}]{nickerson2008attachment}
+\bibinfo{author}{Nickerson, A.B.}, \bibinfo{author}{Mele, D.},
+  \bibinfo{author}{Princiotta, D.}, \bibinfo{year}{2008}.
+\newblock \bibinfo{title}{Attachment and empathy as predictors of roles as
+  defenders or outsiders in bullying interactions}.
+\newblock \bibinfo{journal}{Journal of school psychology} \bibinfo{volume}{46},
+  \bibinfo{pages}{687--703}.
+%Type = Article
+\bibitem[{Ouvrein et~al.(2018)Ouvrein, De~Backer and
+  Vandebosch}]{ouvrein2018online}
+\bibinfo{author}{Ouvrein, G.}, \bibinfo{author}{De~Backer, C.J.},
+  \bibinfo{author}{Vandebosch, H.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Online celebrity aggression: A combination of low
+  empathy and high moral disengagement? the relationship between empathy and
+  moral disengagement and adolescents' online celebrity aggression}.
+\newblock \bibinfo{journal}{Computers in human behavior} \bibinfo{volume}{89},
+  \bibinfo{pages}{61--69}.
+%Type = Article
+\bibitem[{Parks(2019)}]{parks2019dirty}
+\bibinfo{author}{Parks, L.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Dirty data: content moderation, regulatory
+  outsourcing, and the cleaners}.
+\newblock \bibinfo{journal}{Film Quarterly} \bibinfo{volume}{73},
+  \bibinfo{pages}{11--18}.
+%Type = Article
+\bibitem[{Price et~al.(2006)Price, Nir and Cappella}]{price2006normative}
+\bibinfo{author}{Price, V.}, \bibinfo{author}{Nir, L.},
+  \bibinfo{author}{Cappella, J.N.}, \bibinfo{year}{2006}.
+\newblock \bibinfo{title}{Normative and informational influences in online
+  political discussions}.
+\newblock \bibinfo{journal}{Communication Theory} \bibinfo{volume}{16},
+  \bibinfo{pages}{47--74}.
+%Type = Article
+\bibitem[{Ptaszy{\'n}ski et~al.(2018)Ptaszy{\'n}ski, Leliwa, Piech and
+  Smywi{\'n}ski-Pohl}]{ptaszynski2018cyberbullying}
+\bibinfo{author}{Ptaszy{\'n}ski, M.}, \bibinfo{author}{Leliwa, G.},
+  \bibinfo{author}{Piech, M.}, \bibinfo{author}{Smywi{\'n}ski-Pohl, A.},
+  \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Cyberbullying detection--technical report 2/2018,
+  {Department of Computer Science AGH, University of Science and Technology}}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:1808.00926} .
+%Type = Article
+\bibitem[{Ptaszynski et~al.(2021)Ptaszynski, Zasko-Zielinska, Marcinczuk,
+  Leliwa, Fortuna, Soliwoda, Dziublewska, Hubert, Skrzek, Piesiewicz,
+  Karbowska, Dowgiallo, Eronen, Tempska, Brochocki, Godny and
+  Wroczynski}]{ijerph182211759}
+\bibinfo{author}{Ptaszynski, M.}, \bibinfo{author}{Zasko-Zielinska, M.},
+  \bibinfo{author}{Marcinczuk, M.}, \bibinfo{author}{Leliwa, G.},
+  \bibinfo{author}{Fortuna, M.}, \bibinfo{author}{Soliwoda, K.},
+  \bibinfo{author}{Dziublewska, I.}, \bibinfo{author}{Hubert, O.},
+  \bibinfo{author}{Skrzek, P.}, \bibinfo{author}{Piesiewicz, J.},
+  \bibinfo{author}{Karbowska, P.}, \bibinfo{author}{Dowgiallo, M.},
+  \bibinfo{author}{Eronen, J.}, \bibinfo{author}{Tempska, P.},
+  \bibinfo{author}{Brochocki, M.}, \bibinfo{author}{Godny, M.},
+  \bibinfo{author}{Wroczynski, M.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Looking for razors and needles in a haystack:
+  Multifaceted analysis of suicidal declarations on social media—a
+  pragmalinguistic approach}.
+\newblock \bibinfo{journal}{International Journal of Environmental Research and
+  Public Health} \bibinfo{volume}{18}.
+\newblock \URLprefix \url{https://www.mdpi.com/1660-4601/18/22/11759},
+  \DOIprefix\doi{10.3390/ijerph182211759}.
+%Type = Book
+\bibitem[{Ptaszynski and Masui(2018)}]{ptaszynski2018automatic}
+\bibinfo{author}{Ptaszynski, M.E.}, \bibinfo{author}{Masui, F.},
+  \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Automatic Cyberbullying Detection: Emerging Research
+  and Opportunities: Emerging Research and Opportunities}.
+\newblock \bibinfo{publisher}{IGI Global}.
+%Type = Misc
+\bibitem[{reddit(2020)}]{noauthor_reddit_nodate}
+\bibinfo{author}{reddit}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Reddit in 2020}.
+\newblock \URLprefix
+  \url{https://www.reddit.com/r/blog/comments/k967mm/reddit_in_2020/}.
+%Type = Misc
+\bibitem[{Reuters(2020)}]{cnbc_2020}
+\bibinfo{author}{Reuters}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Facebook frustrates advertisers as boycott over hate
+  speech kicks off}.
+\newblock \URLprefix
+  \url{https://www.cnbc.com/2020/07/01/facebook-frustrates-advertisers-as-boycott-over-hate-speech-kicks-off.html}.
+%Type = Article
+\bibitem[{Rieger et~al.(2018)Rieger, Schmitt and Frischlich}]{rieger2018hate}
+\bibinfo{author}{Rieger, D.}, \bibinfo{author}{Schmitt, J.B.},
+  \bibinfo{author}{Frischlich, L.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Hate and counter-voices in the internet: Introduction
+  to the special isssue}.
+\newblock \bibinfo{journal}{Studies in Communication and Media} ,
+  \bibinfo{pages}{459--472}.
+%Type = Book
+\bibitem[{Roberts(2014)}]{roberts2014behind}
+\bibinfo{author}{Roberts, S.T.}, \bibinfo{year}{2014}.
+\newblock \bibinfo{title}{Behind the screen: The hidden digital labor of
+  commercial content moderation}.
+\newblock \bibinfo{publisher}{University of Illinois at Urbana-Champaign}.
+%Type = Article
+\bibitem[{Roberts(2016)}]{roberts2016commercial}
+\bibinfo{author}{Roberts, S.T.}, \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Commercial content moderation: Digital laborers'
+  dirty work}.
+\newblock \bibinfo{journal}{Noble and Tynes} .
+%Type = Article
+\bibitem[{Rosa et~al.(2019)Rosa, Pereira, Ribeiro, Ferreira, Carvalho,
+  Oliveira, Coheur, Paulino, Sim{\~a}o and Trancoso}]{rosa2019automatic}
+\bibinfo{author}{Rosa, H.}, \bibinfo{author}{Pereira, N.},
+  \bibinfo{author}{Ribeiro, R.}, \bibinfo{author}{Ferreira, P.C.},
+  \bibinfo{author}{Carvalho, J.P.}, \bibinfo{author}{Oliveira, S.},
+  \bibinfo{author}{Coheur, L.}, \bibinfo{author}{Paulino, P.},
+  \bibinfo{author}{Sim{\~a}o, A.V.}, \bibinfo{author}{Trancoso, I.},
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Automatic cyberbullying detection: A systematic
+  review}.
+\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{93},
+  \bibinfo{pages}{333--345}.
+%Type = Article
+\bibitem[{R{\"o}ttger et~al.(2020)R{\"o}ttger, Vidgen, Nguyen, Waseem, Margetts
+  and Pierrehumbert}]{rottger2020hatecheck}
+\bibinfo{author}{R{\"o}ttger, P.}, \bibinfo{author}{Vidgen, B.},
+  \bibinfo{author}{Nguyen, D.}, \bibinfo{author}{Waseem, Z.},
+  \bibinfo{author}{Margetts, H.}, \bibinfo{author}{Pierrehumbert, J.},
+  \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Hatecheck: Functional tests for hate speech detection
+  models}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2012.15606} .
+%Type = Inproceedings
+\bibitem[{Sap et~al.(2019)Sap, Card, Gabriel, Choi and Smith}]{sap_risk_2019}
+\bibinfo{author}{Sap, M.}, \bibinfo{author}{Card, D.},
+  \bibinfo{author}{Gabriel, S.}, \bibinfo{author}{Choi, Y.},
+  \bibinfo{author}{Smith, N.A.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{The {Risk} of {Racial} {Bias} in {Hate} {Speech}
+  {Detection}}, in: \bibinfo{booktitle}{Proceedings of the 57th {Annual}
+  {Meeting} of the {Association} for {Computational} {Linguistics}},
+  \bibinfo{publisher}{Association for Computational Linguistics},
+  \bibinfo{address}{Florence, Italy}. pp. \bibinfo{pages}{1668--1678}.
+\newblock \URLprefix \url{https://aclanthology.org/P19-1163},
+  \DOIprefix\doi{10.18653/v1/P19-1163}.
+%Type = Inproceedings
+\bibitem[{Schieb and Preuss(2016)}]{schieb2016governing}
+\bibinfo{author}{Schieb, C.}, \bibinfo{author}{Preuss, M.},
+  \bibinfo{year}{2016}.
+\newblock \bibinfo{title}{Governing hate speech by means of counterspeech on
+  facebook}, in: \bibinfo{booktitle}{66th ica annual conference, at fukuoka,
+  japan}, pp. \bibinfo{pages}{1--23}.
+%Type = Inproceedings
+\bibitem[{Schmidt and Wiegand(2017)}]{schmidt2017survey}
+\bibinfo{author}{Schmidt, A.}, \bibinfo{author}{Wiegand, M.},
+  \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{A survey on hate speech detection using natural
+  language processing}, in: \bibinfo{booktitle}{Proceedings of the fifth
+  international workshop on natural language processing for social media}, pp.
+  \bibinfo{pages}{1--10}.
+%Type = Misc
+\bibitem[{Seifert(2013)}]{seifert_2013}
+\bibinfo{author}{Seifert, D.}, \bibinfo{year}{2013}.
+\newblock \bibinfo{title}{Social question and answer site {F}ormspring to shut
+  down on {M}arch 31st}.
+\newblock \URLprefix
+  \url{https://www.theverge.com/2013/3/15/4110196/social-question-answer-site-formspring-shut-down-march-31st}.
+%Type = Article
+\bibitem[{Sejnowski(2020)}]{sejnowski2020unreasonable}
+\bibinfo{author}{Sejnowski, T.J.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{The unreasonable effectiveness of deep learning in
+  artificial intelligence}.
+\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
+  \bibinfo{volume}{117}, \bibinfo{pages}{30033--30038}.
+%Type = Article
+\bibitem[{Soral et~al.(2018)Soral, Bilewicz and Winiewski}]{soral2018exposure}
+\bibinfo{author}{Soral, W.}, \bibinfo{author}{Bilewicz, M.},
+  \bibinfo{author}{Winiewski, M.}, \bibinfo{year}{2018}.
+\newblock \bibinfo{title}{Exposure to hate speech increases prejudice through
+  desensitization}.
+\newblock \bibinfo{journal}{Aggressive behavior} \bibinfo{volume}{44},
+  \bibinfo{pages}{136--146}.
+\newblock \DOIprefix\doi{10.1002/ab.21737}.
+%Type = Article
+\bibitem[{Soral et~al.(2022)Soral, Malinowska and Bilewicz}]{soral2022role}
+\bibinfo{author}{Soral, W.}, \bibinfo{author}{Malinowska, K.},
+  \bibinfo{author}{Bilewicz, M.}, \bibinfo{year}{2022}.
+\newblock \bibinfo{title}{The role of empathy in reducing hate speech
+  proliferation. two contact-based interventions in online and off-line
+  settings.}
+\newblock \bibinfo{journal}{Peace and Conflict: Journal of Peace Psychology} .
+%Type = Article
+\bibitem[{Sorrentino et~al.(2019)Sorrentino, Baldry, Farrington and
   Blaya}]{sorrentino2019epidemiology}
-\bibinfo{author}{A.~Sorrentino}, \bibinfo{author}{A.~C. Baldry},
-  \bibinfo{author}{D.~P. Farrington}, \bibinfo{author}{C.~Blaya},
+\bibinfo{author}{Sorrentino, A.}, \bibinfo{author}{Baldry, A.C.},
+  \bibinfo{author}{Farrington, D.P.}, \bibinfo{author}{Blaya, C.},
+  \bibinfo{year}{2019}.
 \newblock \bibinfo{title}{Epidemiology of cyberbullying across europe:
-  Differences between countries and genders},
+  Differences between countries and genders}.
 \newblock \bibinfo{journal}{Educational Sciences: Theory \& Practice}
-  \bibinfo{volume}{19} (\bibinfo{year}{2019}).
+  \bibinfo{volume}{19}.
+%Type = Article
+\bibitem[{Stangor et~al.(2001)Stangor, Sechrist and Jost}]{stangor2001changing}
+\bibinfo{author}{Stangor, C.}, \bibinfo{author}{Sechrist, G.B.},
+  \bibinfo{author}{Jost, J.T.}, \bibinfo{year}{2001}.
+\newblock \bibinfo{title}{Changing racial beliefs by providing consensus
+  information}.
+\newblock \bibinfo{journal}{Personality and Social Psychology Bulletin}
+  \bibinfo{volume}{27}, \bibinfo{pages}{486--496}.
+%Type = Article
+\bibitem[{Steffgen et~al.(2011)Steffgen, K{\"o}nig, Pfetsch and
+  Melzer}]{steffgen2011cyberbullies}
+\bibinfo{author}{Steffgen, G.}, \bibinfo{author}{K{\"o}nig, A.},
+  \bibinfo{author}{Pfetsch, J.}, \bibinfo{author}{Melzer, A.},
+  \bibinfo{year}{2011}.
+\newblock \bibinfo{title}{Are cyberbullies less empathic? adolescents'
+  cyberbullying behavior and empathic responsiveness}.
+\newblock \bibinfo{journal}{Cyberpsychology, Behavior, and Social Networking}
+  \bibinfo{volume}{14}, \bibinfo{pages}{643--648}.
+%Type = Inproceedings
+\bibitem[{Steiger et~al.(2021)Steiger, Bharucha, Venkatagiri, Riedl and
+  Lease}]{steiger2021psychological}
+\bibinfo{author}{Steiger, M.}, \bibinfo{author}{Bharucha, T.J.},
+  \bibinfo{author}{Venkatagiri, S.}, \bibinfo{author}{Riedl, M.J.},
+  \bibinfo{author}{Lease, M.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{The psychological well-being of content moderators},
+  in: \bibinfo{booktitle}{Proceedings of the 2021 CHI Conference on Human
+  Factors in Computing Systems, CHI}, pp. \bibinfo{pages}{1--14}.
+%Type = Article
+\bibitem[{Steindl et~al.(2015)Steindl, Jonas, Sittenthaler, Traut-Mattausch and
+  Greenberg}]{steindl2015understanding}
+\bibinfo{author}{Steindl, C.}, \bibinfo{author}{Jonas, E.},
+  \bibinfo{author}{Sittenthaler, S.}, \bibinfo{author}{Traut-Mattausch, E.},
+  \bibinfo{author}{Greenberg, J.}, \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Understanding psychological reactance}.
+\newblock \bibinfo{journal}{Zeitschrift f{\"u}r Psychologie} .
+%Type = Inproceedings
+\bibitem[{Steinhardt et~al.(2017)Steinhardt, Koh and
+  Liang}]{steinhardt2017certified}
+\bibinfo{author}{Steinhardt, J.}, \bibinfo{author}{Koh, P.W.},
+  \bibinfo{author}{Liang, P.}, \bibinfo{year}{2017}.
+\newblock \bibinfo{title}{Certified defenses for data poisoning attacks}, in:
+  \bibinfo{booktitle}{Proceedings of the 31st International Conference on
+  Neural Information Processing Systems}, pp. \bibinfo{pages}{3520--3532}.
+%Type = Inproceedings
+\bibitem[{Steinhardt and Liang(2015)}]{steinhardt2015learning}
+\bibinfo{author}{Steinhardt, J.}, \bibinfo{author}{Liang, P.},
+  \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Learning fast-mixing models for structured
+  prediction}, in: \bibinfo{booktitle}{International Conference on Machine
+  Learning}, \bibinfo{organization}{PMLR}. pp. \bibinfo{pages}{1063--1072}.
+%Type = Article
+\bibitem[{Stepanikova(2012)}]{stepanikova2012racial}
+\bibinfo{author}{Stepanikova, I.}, \bibinfo{year}{2012}.
+\newblock \bibinfo{title}{Racial-ethnic biases, time pressure, and medical
+  decisions}.
+\newblock \bibinfo{journal}{Journal of health and social behavior}
+  \bibinfo{volume}{53}, \bibinfo{pages}{329--343}.
+%Type = Article
+\bibitem[{Stephan and Finlay(1999)}]{stephan1999role}
+\bibinfo{author}{Stephan, W.G.}, \bibinfo{author}{Finlay, K.},
+  \bibinfo{year}{1999}.
+\newblock \bibinfo{title}{The role of empathy in improving intergroup
+  relations}.
+\newblock \bibinfo{journal}{Journal of Social issues} \bibinfo{volume}{55},
+  \bibinfo{pages}{729--743}.
+%Type = Article
+\bibitem[{Trengove et~al.(2022)Trengove, Kazim, Almeida, Hilliard, Zannone and
+  Lomas}]{trengove2022critical}
+\bibinfo{author}{Trengove, M.}, \bibinfo{author}{Kazim, E.},
+  \bibinfo{author}{Almeida, D.}, \bibinfo{author}{Hilliard, A.},
+  \bibinfo{author}{Zannone, S.}, \bibinfo{author}{Lomas, E.},
+  \bibinfo{year}{2022}.
+\newblock \bibinfo{title}{A critical review of the online safety bill}.
+\newblock \bibinfo{journal}{Patterns} , \bibinfo{pages}{100544}.
+%Type = Article
+\bibitem[{Tworek(2021)}]{tworek2021fighting}
+\bibinfo{author}{Tworek, H.J.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Fighting hate with speech law: Media and german
+  visions of democracy}.
+\newblock \bibinfo{journal}{The Journal of Holocaust Research}
+  \bibinfo{volume}{35}, \bibinfo{pages}{106--122}.
+%Type = Article
+\bibitem[{Urbaniak et~al.(2022a)Urbaniak, Ptaszy{\'n}ski, Tempska, Leliwa,
+  Brochocki and Wroczy{\'n}ski}]{urbaniak2022personal}
+\bibinfo{author}{Urbaniak, R.}, \bibinfo{author}{Ptaszy{\'n}ski, M.},
+  \bibinfo{author}{Tempska, P.}, \bibinfo{author}{Leliwa, G.},
+  \bibinfo{author}{Brochocki, M.}, \bibinfo{author}{Wroczy{\'n}ski, M.},
+  \bibinfo{year}{2022}a.
+\newblock \bibinfo{title}{Personal attacks decrease user activity in social
+  networking platforms}.
+\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{126},
+  \bibinfo{pages}{106972}.
+%Type = Article
+\bibitem[{Urbaniak et~al.(2022b)Urbaniak, Tempska, Dowgiałło, Ptaszyński,
+  Fortuna, Marcińczuk, Piesiewicz, Leliwa, Soliwoda, Dziublewska,
+  Sulzhytskaya, Karnicka, Skrzek, Karbowska, Brochocki and
+  Wroczyński}]{URBANIAK2022107371}
+\bibinfo{author}{Urbaniak, R.}, \bibinfo{author}{Tempska, P.},
+  \bibinfo{author}{Dowgiałło, M.}, \bibinfo{author}{Ptaszyński, M.},
+  \bibinfo{author}{Fortuna, M.}, \bibinfo{author}{Marcińczuk, M.},
+  \bibinfo{author}{Piesiewicz, J.}, \bibinfo{author}{Leliwa, G.},
+  \bibinfo{author}{Soliwoda, K.}, \bibinfo{author}{Dziublewska, I.},
+  \bibinfo{author}{Sulzhytskaya, N.}, \bibinfo{author}{Karnicka, A.},
+  \bibinfo{author}{Skrzek, P.}, \bibinfo{author}{Karbowska, P.},
+  \bibinfo{author}{Brochocki, M.}, \bibinfo{author}{Wroczyński, M.},
+  \bibinfo{year}{2022}b.
+\newblock \bibinfo{title}{Namespotting: Username toxicity and actual toxic
+  behavior on reddit}.
+\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{136},
+  \bibinfo{pages}{107371}.
+\newblock \URLprefix
+  \url{https://www.sciencedirect.com/science/article/pii/S0747563222001935},
+  \DOIprefix\doi{https://doi.org/10.1016/j.chb.2022.107371}.
+%Type = Article
+\bibitem[{Van~Noorden et~al.(2015)Van~Noorden, Haselager, Cillessen and
+  Bukowski}]{van2015empathy}
+\bibinfo{author}{Van~Noorden, T.H.}, \bibinfo{author}{Haselager, G.J.},
+  \bibinfo{author}{Cillessen, A.H.}, \bibinfo{author}{Bukowski, W.M.},
+  \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Empathy and involvement in bullying in children and
+  adolescents: A systematic review}.
+\newblock \bibinfo{journal}{Journal of youth and adolescence}
+  \bibinfo{volume}{44}, \bibinfo{pages}{637--657}.
+%Type = Misc
+\bibitem[{Vanian(2019)}]{jigsaw2019}
+\bibinfo{author}{Vanian, J.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Google's {Hate} {Speech} {Detection} {A}.{I}. {Has} a
+  {Racial} {Bias} {Problem}}.
+\newblock \URLprefix
+  \url{https://fortune.com/2019/08/16/google-jigsaw-perspective-racial-bias/}.
 %Type = Misc
 \bibitem[{Vogels(2021)}]{vogels_state_2021}
-\bibinfo{author}{E.~A. Vogels}, \bibinfo{title}{The {State} of {Online}
-  {Harassment}}, \bibinfo{year}{2021}. \URLprefix
+\bibinfo{author}{Vogels, E.A.}, \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{The {State} of {Online} {Harassment}}.
+\newblock \URLprefix
   \url{https://www.pewresearch.org/internet/2021/01/13/the-state-of-online-harassment/}.
 %Type = Article
-\bibitem[{Barlett et~al.(2021)Barlett, Simmers, Roth, and
-  Gentile}]{barlett2021comparing}
-\bibinfo{author}{C.~P. Barlett}, \bibinfo{author}{M.~M. Simmers},
-  \bibinfo{author}{B.~Roth}, \bibinfo{author}{D.~Gentile},
-\newblock \bibinfo{title}{Comparing cyberbullying prevalence and process before
-  and during the covid-19 pandemic},
-\newblock \bibinfo{journal}{The Journal of Social Psychology}
-  (\bibinfo{year}{2021}) \bibinfo{pages}{1--11}.
-%Type = Misc
-\bibitem[{Grant(2021)}]{grant_2021}
-\bibinfo{author}{J.~Grant}, \bibinfo{title}{Australia’s esafety commissioner
-  targets abuse online as covid-19 supercharges cyberbullying | the
-  strategist}, \bibinfo{year}{2021}. \URLprefix
-  \url{https://www.aspistrategist.org.au/australias-esafety-commissioner-targets-abuse-online-as-covid-19-supercharges-cyberbullying/}.
-%Type = Misc
-\bibitem[{L1ght(2020)}]{noauthor_l1ght_2020}
-\bibinfo{author}{L1ght}, \bibinfo{title}{L1ght releases groundbreaking report
-  on corona-related hate speech and online toxicity}, \bibinfo{year}{2020}.
-  \URLprefix
-  \url{https://l1ght.com/l1ght-releases-groundbreaking-report-on-corona-related-hate-speech-and-online-toxicity/}.
-%Type = Misc
-\bibitem[{Bhattacharya(2021)}]{bhattacharya}
-\bibinfo{author}{A.~Bhattacharya}, \bibinfo{title}{How {Covid}-19 lockdowns
-  weakened {Facebook}'s content moderation algorithms}, \bibinfo{year}{2021}.
-  \URLprefix
-  \url{https://qz.com/india/1976450/facebook-covid-19-lockdowns-hurt-content-moderation-algorithms/}.
-%Type = Article
-\bibitem[{Gerrard(2020)}]{gerrard2020covid19}
-\bibinfo{author}{Y.~Gerrard},
-\newblock \bibinfo{title}{<? covid19?> the covid-19 mental health content
-  moderation conundrum},
-\newblock \bibinfo{journal}{Social Media+ Society} \bibinfo{volume}{6}
-  (\bibinfo{year}{2020}) \bibinfo{pages}{2056305120948186}.
+\bibitem[{Wachs et~al.(2019)Wachs, Wright, Sittichai, Singh, Biswal, Kim, Yang,
+  G{\'a}mez-Guadix, Almendros, Flora et~al.}]{wachs2019associations}
+\bibinfo{author}{Wachs, S.}, \bibinfo{author}{Wright, M.F.},
+  \bibinfo{author}{Sittichai, R.}, \bibinfo{author}{Singh, R.},
+  \bibinfo{author}{Biswal, R.}, \bibinfo{author}{Kim, E.m.},
+  \bibinfo{author}{Yang, S.}, \bibinfo{author}{G{\'a}mez-Guadix, M.},
+  \bibinfo{author}{Almendros, C.}, \bibinfo{author}{Flora, K.}, et~al.,
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Associations between witnessing and perpetrating
+  online hate in eight countries: The buffering effects of problem-focused
+  coping}.
+\newblock \bibinfo{journal}{International journal of environmental research and
+  public health} \bibinfo{volume}{16}, \bibinfo{pages}{3992}.
+%Type = Article
+\bibitem[{Williams(2019)}]{williams2019hatred}
+\bibinfo{author}{Williams, M.}, \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Hatred behind the screens: A report on the rise of
+  online hate speech}.
+\newblock \bibinfo{journal}{Mishcon de Reya} .
+%Type = Article
+\bibitem[{Williams et~al.(2020)Williams, Burnap, Javed, Liu and
+  Ozalp}]{williams2020hate}
+\bibinfo{author}{Williams, M.L.}, \bibinfo{author}{Burnap, P.},
+  \bibinfo{author}{Javed, A.}, \bibinfo{author}{Liu, H.},
+  \bibinfo{author}{Ozalp, S.}, \bibinfo{year}{2020}.
+\newblock \bibinfo{title}{Hate in the machine: anti-black and anti-muslim
+  social media posts as predictors of offline racially and religiously
+  aggravated crime}.
+\newblock \bibinfo{journal}{The British Journal of Criminology}
+  \bibinfo{volume}{60}, \bibinfo{pages}{93--117}.
+\newblock \DOIprefix\doi{10.1093/bjc/azz049}.
+%Type = Article
+\bibitem[{Woolley et~al.(2015)Woolley, Aggarwal and
+  Malone}]{woolley2015collective}
+\bibinfo{author}{Woolley, A.W.}, \bibinfo{author}{Aggarwal, I.},
+  \bibinfo{author}{Malone, T.W.}, \bibinfo{year}{2015}.
+\newblock \bibinfo{title}{Collective intelligence and group performance}.
+\newblock \bibinfo{journal}{Current Directions in Psychological Science}
+  \bibinfo{volume}{24}, \bibinfo{pages}{420--424}.
+%Type = Article
+\bibitem[{Wright and Wachs(2021)}]{wright2021does}
+\bibinfo{author}{Wright, M.F.}, \bibinfo{author}{Wachs, S.},
+  \bibinfo{year}{2021}.
+\newblock \bibinfo{title}{Does empathy and toxic online disinhibition moderate
+  the longitudinal association between witnessing and perpetrating homophobic
+  cyberbullying?}
+\newblock \bibinfo{journal}{International journal of bullying prevention}
+  \bibinfo{volume}{3}, \bibinfo{pages}{66--74}.
+%Type = Inproceedings
+\bibitem[{Wu et~al.(2019)Wu, Ribeiro, Heer and Weld}]{wu2019errudite}
+\bibinfo{author}{Wu, T.}, \bibinfo{author}{Ribeiro, M.T.},
+  \bibinfo{author}{Heer, J.}, \bibinfo{author}{Weld, D.S.},
+  \bibinfo{year}{2019}.
+\newblock \bibinfo{title}{Errudite: Scalable, reproducible, and testable error
+  analysis}, in: \bibinfo{booktitle}{Proceedings of the 57th Annual Meeting of
+  the Association for Computational Linguistics}, pp.
+  \bibinfo{pages}{747--763}.
+%Type = Article
+\bibitem[{Xie et~al.(2011)Xie, Sreenivasan, Korniss, Zhang, Lim and
+  Szymanski}]{xie2011social}
+\bibinfo{author}{Xie, J.}, \bibinfo{author}{Sreenivasan, S.},
+  \bibinfo{author}{Korniss, G.}, \bibinfo{author}{Zhang, W.},
+  \bibinfo{author}{Lim, C.}, \bibinfo{author}{Szymanski, B.K.},
+  \bibinfo{year}{2011}.
+\newblock \bibinfo{title}{Social consensus through the influence of committed
+  minorities}.
+\newblock \bibinfo{journal}{Physical Review E} \bibinfo{volume}{84},
+  \bibinfo{pages}{011130}.
 %Type = Article
@@
   et~al.}]{yang2021consequences}
-\bibinfo{author}{B.~Yang}, \bibinfo{author}{B.~Wang}, \bibinfo{author}{N.~Sun},
-  \bibinfo{author}{F.~Xu}, \bibinfo{author}{L.~Wang},
-  \bibinfo{author}{J.~Chen}, \bibinfo{author}{S.~Yu},
-  \bibinfo{author}{Y.~Zhang}, \bibinfo{author}{Y.~Zhu},
-  \bibinfo{author}{T.~Dai}, et~al.,
+\bibinfo{author}{Yang, B.}, \bibinfo{author}{Wang, B.}, \bibinfo{author}{Sun,
+  N.}, \bibinfo{author}{Xu, F.}, \bibinfo{author}{Wang, L.},
+  \bibinfo{author}{Chen, J.}, \bibinfo{author}{Yu, S.}, \bibinfo{author}{Zhang,
+  Y.}, \bibinfo{author}{Zhu, Y.}, \bibinfo{author}{Dai, T.}, et~al.,
+  \bibinfo{year}{2021}.
 \newblock \bibinfo{title}{The consequences of cyberbullying and traditional
   bullying victimization among adolescents: gender differences in psychological
-  symptoms, self-harm and suicidality},
-\newblock \bibinfo{journal}{Psychiatry research} \bibinfo{volume}{306}
-  (\bibinfo{year}{2021}) \bibinfo{pages}{114219}.
-%Type = Article
-\bibitem[{Hinduja and Patchin(2010)}]{hinduja2010bullying}
-\bibinfo{author}{S.~Hinduja}, \bibinfo{author}{J.~W. Patchin},
-\newblock \bibinfo{title}{Bullying, cyberbullying, and suicide},
-\newblock \bibinfo{journal}{Archives of suicide research} \bibinfo{volume}{14}
-  (\bibinfo{year}{2010}) \bibinfo{pages}{206--221}.
-%Type = Article
-\bibitem[{Alhujailli et~al.(2020)Alhujailli, Karwowski, Wan, and
-  Hancock}]{alhujailli2020affective}
-\bibinfo{author}{A.~Alhujailli}, \bibinfo{author}{W.~Karwowski},
-  \bibinfo{author}{T.~T. Wan}, \bibinfo{author}{P.~Hancock},
-\newblock \bibinfo{title}{Affective and stress consequences of cyberbullying},
-\newblock \bibinfo{journal}{Symmetry} \bibinfo{volume}{12}
-  (\bibinfo{year}{2020}) \bibinfo{pages}{1536}.
-%Type = Article
-\bibitem[{Kowalski and Limber(2013)}]{kowalski2013psychological}
-\bibinfo{author}{R.~M. Kowalski}, \bibinfo{author}{S.~P. Limber},
-\newblock \bibinfo{title}{Psychological, physical, and academic correlates of
-  cyberbullying and traditional bullying},
-\newblock \bibinfo{journal}{Journal of adolescent health} \bibinfo{volume}{53}
-  (\bibinfo{year}{2013}) \bibinfo{pages}{S13--S20}.
-%Type = Article
-\bibitem[{Lee and Leets(2002)}]{lee2002persuasive}
-\bibinfo{author}{E.~Lee}, \bibinfo{author}{L.~Leets},
-\newblock \bibinfo{title}{Persuasive storytelling by hate groups online:
-  Examining its effects on adolescents},
-\newblock \bibinfo{journal}{American behavioral scientist} \bibinfo{volume}{45}
-  (\bibinfo{year}{2002}) \bibinfo{pages}{927--957}.
-%Type = Article
-\bibitem[{Williams(2019)}]{williams2019hatred}
-\bibinfo{author}{M.~Williams},
-\newblock \bibinfo{title}{Hatred behind the screens: A report on the rise of
-  online hate speech}  (\bibinfo{year}{2019}).
-%Type = Article
-\bibitem[{Fink(2018)}]{fink2018dangerous}
-\bibinfo{author}{C.~Fink},
-\newblock \bibinfo{title}{Dangerous speech, anti-muslim violence, and facebook
-  in myanmar},
-\newblock \bibinfo{journal}{Journal of International Affairs}
-  \bibinfo{volume}{71} (\bibinfo{year}{2018}) \bibinfo{pages}{43--52}.
-%Type = Article
-\bibitem[{Soral et~al.(2018)Soral, Bilewicz, and Winiewski}]{soral2018exposure}
-\bibinfo{author}{W.~Soral}, \bibinfo{author}{M.~Bilewicz},
-  \bibinfo{author}{M.~Winiewski},
-\newblock \bibinfo{title}{Exposure to hate speech increases prejudice through
-  desensitization},
-\newblock \bibinfo{journal}{Aggressive behavior} \bibinfo{volume}{44}
-  (\bibinfo{year}{2018}) \bibinfo{pages}{136--146}.
-  \DOIprefix\doi{10.1002/ab.21737}.
-%Type = Article
-\bibitem[{{\'A}lvarez-Benjumea and Winter(2018)}]{alvarez2018normative}
-\bibinfo{author}{A.~{\'A}lvarez-Benjumea}, \bibinfo{author}{F.~Winter},
-\newblock \bibinfo{title}{Normative change and culture of hate: An experiment
-  in online environments},
-\newblock \bibinfo{journal}{European Sociological Review} \bibinfo{volume}{34}
-  (\bibinfo{year}{2018}) \bibinfo{pages}{223--237}.
-  \DOIprefix\doi{10.2139/ssrn.3126089}.
-%Type = Article
-\bibitem[{Williams et~al.(2020)Williams, Burnap, Javed, Liu, and
-  Ozalp}]{williams2020hate}
-\bibinfo{author}{M.~L. Williams}, \bibinfo{author}{P.~Burnap},
-  \bibinfo{author}{A.~Javed}, \bibinfo{author}{H.~Liu},
-  \bibinfo{author}{S.~Ozalp},
-\newblock \bibinfo{title}{Hate in the machine: anti-black and anti-muslim
-  social media posts as predictors of offline racially and religiously
-  aggravated crime},
-\newblock \bibinfo{journal}{The British Journal of Criminology}
-  \bibinfo{volume}{60} (\bibinfo{year}{2020}) \bibinfo{pages}{93--117}.
-  \DOIprefix\doi{10.1093/bjc/azz049}.
-%Type = Article
-\bibitem[{Urbaniak et~al.(2022)Urbaniak, Ptaszy{\'n}ski, Tempska, Leliwa,
-  Brochocki, and Wroczy{\'n}ski}]{urbaniak2022personal}
-\bibinfo{author}{R.~Urbaniak}, \bibinfo{author}{M.~Ptaszy{\'n}ski},
-  \bibinfo{author}{P.~Tempska}, \bibinfo{author}{G.~Leliwa},
-  \bibinfo{author}{M.~Brochocki}, \bibinfo{author}{M.~Wroczy{\'n}ski},
-\newblock \bibinfo{title}{Personal attacks decrease user activity in social
-  networking platforms},
-\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{126}
-  (\bibinfo{year}{2022}) \bibinfo{pages}{106972}.
-%Type = Article
-\bibitem[{Tworek(2021)}]{tworek2021fighting}
-\bibinfo{author}{H.~J. Tworek},
-\newblock \bibinfo{title}{Fighting hate with speech law: Media and german
-  visions of democracy},
-\newblock \bibinfo{journal}{The Journal of Holocaust Research}
-  \bibinfo{volume}{35} (\bibinfo{year}{2021}) \bibinfo{pages}{106--122}.
-%Type = Article
-\bibitem[{Trengove et~al.(2022)Trengove, Kazim, Almeida, Hilliard, Zannone, and
-  Lomas}]{trengove2022critical}
-\bibinfo{author}{M.~Trengove}, \bibinfo{author}{E.~Kazim},
-  \bibinfo{author}{D.~Almeida}, \bibinfo{author}{A.~Hilliard},
-  \bibinfo{author}{S.~Zannone}, \bibinfo{author}{E.~Lomas},
-\newblock \bibinfo{title}{A critical review of the online safety bill},
-\newblock \bibinfo{journal}{Patterns}  (\bibinfo{year}{2022})
-  \bibinfo{pages}{100544}.
-%Type = Misc
-\bibitem[{cnb(2020)}]{cnbc_2020}
-\bibinfo{title}{Facebook frustrates advertisers as boycott over hate speech
-  kicks off}, \bibinfo{year}{2020}. \URLprefix
-  \url{https://www.cnbc.com/2020/07/01/facebook-frustrates-advertisers-as-boycott-over-hate-speech-kicks-off.html}.
-%Type = Misc
-\bibitem[{Newton(2013)}]{newton_2013}
-\bibinfo{author}{C.~Newton}, \bibinfo{title}{Killer app: Why do anonymous
-   networks keep leading to suicides?}, \bibinfo{year}{2013}.
-  \URLprefix
-  \url{https://www.theverge.com/2013/9/17/4740902/no-good-answers-why-didnt-ask-fm-learn-from-the-formspring-suicides}.
-%Type = Misc
-\bibitem[{Failory(2022)}]{failory_2022}
-\bibinfo{author}{Failory}, \bibinfo{title}{Yik yak's shut down: Why did the
-  location-based app failed?}, \bibinfo{year}{2022}. \URLprefix
-  \url{https://www.failory.com/cemetery/yik-yak}.
-%Type = Misc
-\bibitem[{los(2021)}]{los_angeles_times_2021}
-\bibinfo{title}{A teen who was bullied on snapchat died. his mom is suing to
-  hold social media liable}, \bibinfo{year}{2021}. \URLprefix
-  \url{https://www.latimes.com/business/story/2021-05-10/lawsuit-snap-teen-suicide-yolo-lmk}.
-%Type = Misc
-\bibitem[{Seifert(2013)}]{seifert_2013}
-\bibinfo{author}{D.~Seifert}, \bibinfo{title}{Social question and answer site
-  formspring to shut down on March 31st}, \bibinfo{year}{2013}. \URLprefix
-  \url{https://www.theverge.com/2013/3/15/4110196/social-question-answer-site-formspring-shut-down-march-31st}.
-%Type = Article
-\bibitem[{MacAvaney et~al.(2019)MacAvaney, Yao, Yang, Russell, Goharian, and
-  Frieder}]{macavaney2019hate}
-\bibinfo{author}{S.~MacAvaney}, \bibinfo{author}{H.-R. Yao},
-  \bibinfo{author}{E.~Yang}, \bibinfo{author}{K.~Russell},
-  \bibinfo{author}{N.~Goharian}, \bibinfo{author}{O.~Frieder},
-\newblock \bibinfo{title}{Hate speech detection: Challenges and solutions},
-\newblock \bibinfo{journal}{PloS one} \bibinfo{volume}{14}
-  (\bibinfo{year}{2019}) \bibinfo{pages}{e0221152}.
-%Type = Inproceedings
-\bibitem[{Schmidt and Wiegand(2017)}]{schmidt2017survey}
-\bibinfo{author}{A.~Schmidt}, \bibinfo{author}{M.~Wiegand},
-\newblock \bibinfo{title}{A survey on hate speech detection using natural
-  language processing},
-\newblock in: \bibinfo{booktitle}{Proceedings of the fifth international
-  workshop on natural language processing for social media},
-  \bibinfo{year}{2017}, pp. \bibinfo{pages}{1--10}.
-%Type = Article
-\bibitem[{Jordan and Mitchell(2015)}]{jordan2015machine}
-\bibinfo{author}{M.~I. Jordan}, \bibinfo{author}{T.~M. Mitchell},
-\newblock \bibinfo{title}{Machine learning: Trends, perspectives, and
-  prospects},
-\newblock \bibinfo{journal}{Science} \bibinfo{volume}{349}
-  (\bibinfo{year}{2015}) \bibinfo{pages}{255--260}.
-%Type = Article
-\bibitem[{LeCun et~al.(2015)LeCun, Bengio, and Hinton}]{lecun2015deep}
-\bibinfo{author}{Y.~LeCun}, \bibinfo{author}{Y.~Bengio},
-  \bibinfo{author}{G.~Hinton},
-\newblock \bibinfo{title}{Deep learning},
-\newblock \bibinfo{journal}{nature} \bibinfo{volume}{521}
-  (\bibinfo{year}{2015}) \bibinfo{pages}{436--444}.
-%Type = Article
-\bibitem[{Sejnowski(2020)}]{sejnowski2020unreasonable}
-\bibinfo{author}{T.~J. Sejnowski},
-\newblock \bibinfo{title}{The unreasonable effectiveness of deep learning in
-  artificial intelligence},
-\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
-  \bibinfo{volume}{117} (\bibinfo{year}{2020}) \bibinfo{pages}{30033--30038}.
-%Type = Inproceedings
-\bibitem[{Binns et~al.(2017)Binns, Veale, Van~Kleek, and
-  Shadbolt}]{binns2017like}
-\bibinfo{author}{R.~Binns}, \bibinfo{author}{M.~Veale},
-  \bibinfo{author}{M.~Van~Kleek}, \bibinfo{author}{N.~Shadbolt},
-\newblock \bibinfo{title}{Like trainer, like bot? inheritance of bias in
-  algorithmic content moderation},
-\newblock in: \bibinfo{booktitle}{International conference on social
-  informatics}, \bibinfo{organization}{Springer}, \bibinfo{year}{2017}, pp.
-  \bibinfo{pages}{405--415}.
-%Type = Article
-\bibitem[{Geva et~al.(2019)Geva, Goldberg, and Berant}]{geva2019we}
-\bibinfo{author}{M.~Geva}, \bibinfo{author}{Y.~Goldberg},
-  \bibinfo{author}{J.~Berant},
-\newblock \bibinfo{title}{Are we modeling the task or the annotator? an
-  investigation of annotator bias in natural language understanding datasets},
-\newblock \bibinfo{journal}{arXiv preprint arXiv:1908.07898}
-  (\bibinfo{year}{2019}).
-%Type = Article
-\bibitem[{Mehrabi et~al.(2021)Mehrabi, Morstatter, Saxena, Lerman, and
-  Galstyan}]{mehrabi2021survey}
-\bibinfo{author}{N.~Mehrabi}, \bibinfo{author}{F.~Morstatter},
-  \bibinfo{author}{N.~Saxena}, \bibinfo{author}{K.~Lerman},
-  \bibinfo{author}{A.~Galstyan},
-\newblock \bibinfo{title}{A survey on bias and fairness in machine learning},
-\newblock \bibinfo{journal}{ACM Computing Surveys (CSUR)} \bibinfo{volume}{54}
-  (\bibinfo{year}{2021}) \bibinfo{pages}{1--35}.
-%Type = Inproceedings
-\bibitem[{Sap et~al.(2019)Sap, Card, Gabriel, Choi, and Smith}]{sap_risk_2019}
-\bibinfo{author}{M.~Sap}, \bibinfo{author}{D.~Card},
-  \bibinfo{author}{S.~Gabriel}, \bibinfo{author}{Y.~Choi},
-  \bibinfo{author}{N.~A. Smith},
-\newblock \bibinfo{title}{The {Risk} of {Racial} {Bias} in {Hate} {Speech}
-  {Detection}},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 57th {Annual} {Meeting} of
-  the {Association} for {Computational} {Linguistics}},
-  \bibinfo{publisher}{Association for Computational Linguistics},
-  \bibinfo{address}{Florence, Italy}, \bibinfo{year}{2019}, pp.
-  \bibinfo{pages}{1668--1678}. \URLprefix
-  \url{https://aclanthology.org/P19-1163}.
-  \DOIprefix\doi{10.18653/v1/P19-1163}.
-%Type = Misc
-\bibitem[{Vanian(2019)}]{jigsaw2019}
-\bibinfo{author}{J.~Vanian}, \bibinfo{title}{Google's {Hate} {Speech}
-  {Detection} {A}.{I}. {Has} a {Racial} {Bias} {Problem}},
-  \bibinfo{year}{2019}. \URLprefix
-  \url{https://fortune.com/2019/08/16/google-jigsaw-perspective-racial-bias/}.
-%Type = Inproceedings
-\bibitem[{Gr{\"o}ndahl et~al.(2018)Gr{\"o}ndahl, Pajola, Juuti, Conti, and
-  Asokan}]{grondahl2018all}
-\bibinfo{author}{T.~Gr{\"o}ndahl}, \bibinfo{author}{L.~Pajola},
-  \bibinfo{author}{M.~Juuti}, \bibinfo{author}{M.~Conti},
-  \bibinfo{author}{N.~Asokan},
-\newblock \bibinfo{title}{All you need is" love" evading hate speech
-  detection},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 11th ACM workshop on
-  artificial intelligence and security}, \bibinfo{year}{2018}, pp.
-  \bibinfo{pages}{2--12}.
-%Type = Article
-\bibitem[{Rosa et~al.(2019)Rosa, Pereira, Ribeiro, Ferreira, Carvalho,
-  Oliveira, Coheur, Paulino, Sim{\~a}o, and Trancoso}]{rosa2019automatic}
-\bibinfo{author}{H.~Rosa}, \bibinfo{author}{N.~Pereira},
-  \bibinfo{author}{R.~Ribeiro}, \bibinfo{author}{P.~C. Ferreira},
-  \bibinfo{author}{J.~P. Carvalho}, \bibinfo{author}{S.~Oliveira},
-  \bibinfo{author}{L.~Coheur}, \bibinfo{author}{P.~Paulino},
-  \bibinfo{author}{A.~V. Sim{\~a}o}, \bibinfo{author}{I.~Trancoso},
-\newblock \bibinfo{title}{Automatic cyberbullying detection: A systematic
-  review},
-\newblock \bibinfo{journal}{Computers in Human Behavior} \bibinfo{volume}{93}
-  (\bibinfo{year}{2019}) \bibinfo{pages}{333--345}.
+  symptoms, self-harm and suicidality}.
+\newblock \bibinfo{journal}{Psychiatry research} \bibinfo{volume}{306},
+  \bibinfo{pages}{114219}.
+%Type = Article
+\bibitem[{Yanovitzky and Rimal(2006a)}]{yanowitzky2006communication}
+\bibinfo{author}{Yanovitzky, I.}, \bibinfo{author}{Rimal, R.},
+  \bibinfo{year}{2006}a.
+\newblock \bibinfo{title}{Communication and normative influence: An
+  introduction to the special issue}.
+\newblock \bibinfo{journal}{Communication Theory} \bibinfo{volume}{16},
+  \bibinfo{pages}{1--6}.
+%Type = Article
+\bibitem[{Yanovitzky and Rimal(2006b)}]{yanovitzky2006communication}
+\bibinfo{author}{Yanovitzky, I.}, \bibinfo{author}{Rimal, R.N.},
+  \bibinfo{year}{2006}b.
+\newblock \bibinfo{title}{Communication and normative influence: An
+  introduction to the special issue}.
+\newblock \bibinfo{journal}{Communication Theory} \bibinfo{volume}{16},
+  \bibinfo{pages}{1--6}.
 %Type = Article
 \bibitem[{Yin and Zubiaga(2021)}]{yin2021towards}
-\bibinfo{author}{W.~Yin}, \bibinfo{author}{A.~Zubiaga},
+\bibinfo{author}{Yin, W.}, \bibinfo{author}{Zubiaga, A.}, \bibinfo{year}{2021}.
 \newblock \bibinfo{title}{Towards generalisable hate speech detection: a review
-  on obstacles and solutions},
-\newblock \bibinfo{journal}{PeerJ Computer Science} \bibinfo{volume}{7}
-  (\bibinfo{year}{2021}) \bibinfo{pages}{e598}.
-%Type = Inproceedings
-\bibitem[{Wu et~al.(2019)Wu, Ribeiro, Heer, and Weld}]{wu2019errudite}
-\bibinfo{author}{T.~Wu}, \bibinfo{author}{M.~T. Ribeiro},
-  \bibinfo{author}{J.~Heer}, \bibinfo{author}{D.~S. Weld},
-\newblock \bibinfo{title}{Errudite: Scalable, reproducible, and testable error
-  analysis},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 57th Annual Meeting of the
-  Association for Computational Linguistics}, \bibinfo{year}{2019}, pp.
-  \bibinfo{pages}{747--763}.
-%Type = Article
-\bibitem[{Lipton and Steinhardt(2019)}]{lipton2019troubling}
-\bibinfo{author}{Z.~C. Lipton}, \bibinfo{author}{J.~Steinhardt},
-\newblock \bibinfo{title}{Troubling trends in machine learning scholarship:
-  Some ml papers suffer from flaws that could mislead the public and stymie
-  future research.},
-\newblock \bibinfo{journal}{Queue} \bibinfo{volume}{17} (\bibinfo{year}{2019})
-  \bibinfo{pages}{45--77}.
-%Type = Inproceedings
-\bibitem[{Musgrave et~al.(2020)Musgrave, Belongie, and
-  Lim}]{musgrave2020metric}
-\bibinfo{author}{K.~Musgrave}, \bibinfo{author}{S.~Belongie},
-  \bibinfo{author}{S.-N. Lim},
-\newblock \bibinfo{title}{A metric learning reality check},
-\newblock in: \bibinfo{booktitle}{European Conference on Computer Vision},
-  \bibinfo{organization}{Springer}, \bibinfo{year}{2020}, pp.
-  \bibinfo{pages}{681--699}.
-%Type = Inproceedings
-\bibitem[{Steinhardt et~al.(2017)Steinhardt, Koh, and
-  Liang}]{steinhardt2017certified}
-\bibinfo{author}{J.~Steinhardt}, \bibinfo{author}{P.~W. Koh},
-  \bibinfo{author}{P.~Liang},
-\newblock \bibinfo{title}{Certified defenses for data poisoning attacks},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 31st International
-  Conference on Neural Information Processing Systems}, \bibinfo{year}{2017},
-  pp. \bibinfo{pages}{3520--3532}.
-%Type = Article
-\bibitem[{Melis et~al.(2017)Melis, Dyer, and Blunsom}]{melis2017state}
-\bibinfo{author}{G.~Melis}, \bibinfo{author}{C.~Dyer},
-  \bibinfo{author}{P.~Blunsom},
-\newblock \bibinfo{title}{On the state of the art of evaluation in neural
-  language models},
-\newblock \bibinfo{journal}{arXiv preprint arXiv:1707.05589}
-  (\bibinfo{year}{2017}).
-%Type = Inproceedings
-\bibitem[{Steinhardt and Liang(2015)}]{steinhardt2015learning}
-\bibinfo{author}{J.~Steinhardt}, \bibinfo{author}{P.~Liang},
-\newblock \bibinfo{title}{Learning fast-mixing models for structured
-  prediction},
-\newblock in: \bibinfo{booktitle}{International Conference on Machine
-  Learning}, \bibinfo{organization}{PMLR}, \bibinfo{year}{2015}, pp.
-  \bibinfo{pages}{1063--1072}.
-%Type = Article
-\bibitem[{Esteva et~al.(2017)Esteva, Kuprel, Novoa, Ko, Swetter, Blau, and
-  Thrun}]{esteva_dermatologist-level_2017}
-\bibinfo{author}{A.~Esteva}, \bibinfo{author}{B.~Kuprel},
-  \bibinfo{author}{R.~A. Novoa}, \bibinfo{author}{J.~Ko},
-  \bibinfo{author}{S.~M. Swetter}, \bibinfo{author}{H.~M. Blau},
-  \bibinfo{author}{S.~Thrun},
-\newblock \bibinfo{title}{Dermatologist-level classification of skin cancer
-  with deep neural networks},
-\newblock \bibinfo{journal}{Nature} \bibinfo{volume}{542}
-  (\bibinfo{year}{2017}) \bibinfo{pages}{115--118}. \URLprefix
-  \url{http://www.nature.com/articles/nature21056}.
-  \DOIprefix\doi{10.1038/nature21056}.
-%Type = Article
-\bibitem[{R{\"o}ttger et~al.(2020)R{\"o}ttger, Vidgen, Nguyen, Waseem,
-  Margetts, and Pierrehumbert}]{rottger2020hatecheck}
-\bibinfo{author}{P.~R{\"o}ttger}, \bibinfo{author}{B.~Vidgen},
-  \bibinfo{author}{D.~Nguyen}, \bibinfo{author}{Z.~Waseem},
-  \bibinfo{author}{H.~Margetts}, \bibinfo{author}{J.~Pierrehumbert},
-\newblock \bibinfo{title}{Hatecheck: Functional tests for hate speech detection
-  models},
-\newblock \bibinfo{journal}{arXiv preprint arXiv:2012.15606}
-  (\bibinfo{year}{2020}).
-%Type = Misc
-\bibitem[{onl(????)}]{onlinesafetydata}
-\bibinfo{title}{About the online safety data initiative}, ????
-%Type = Misc
-\bibitem[{noa(2012)}]{noauthor_facebook:_2012}
-\bibinfo{title}{Facebook: 3.2 {Billion} {Likes} \& {Comments} {Every} {Day}},
-  \bibinfo{year}{2012}. \URLprefix
-  \url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}.
-%Type = Misc
-\bibitem[{noa(2021)}]{noauthor_10_2021}
-\bibinfo{title}{10 {Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in
-  2021 [{Infographic}]}, \bibinfo{year}{2021}. \URLprefix
-  \url{https://www.oberlo.com/blog/twitter-statistics}.
-%Type = Misc
-\bibitem[{noa(2020)}]{noauthor_reddit_nodate}
-\bibinfo{title}{Reddit in 2020}, \bibinfo{year}{2020}. \URLprefix
-  \url{https://www.reddit.com/r/blog/comments/k967mm/reddit_in_2020/}.
-%Type = Book
-\bibitem[{Roberts(2014)}]{roberts2014behind}
-\bibinfo{author}{S.~T. Roberts}, \bibinfo{title}{Behind the screen: The hidden
-  digital labor of commercial content moderation},
-  \bibinfo{publisher}{University of Illinois at Urbana-Champaign},
-  \bibinfo{year}{2014}.
-%Type = Article
-\bibitem[{Roberts(2016)}]{roberts2016commercial}
-\bibinfo{author}{S.~T. Roberts},
-\newblock \bibinfo{title}{Commercial content moderation: Digital laborers'
-  dirty work}  (\bibinfo{year}{2016}).
-%Type = Inproceedings
-\bibitem[{Karunakaran and Ramakrishan(2019)}]{karunakaran2019testing}
-\bibinfo{author}{S.~Karunakaran}, \bibinfo{author}{R.~Ramakrishan},
-\newblock \bibinfo{title}{Testing stylistic interventions to reduce emotional
-  impact of content moderation workers},
-\newblock in: \bibinfo{booktitle}{Proceedings of the AAAI Conference on Human
-  Computation and Crowdsourcing}, volume~\bibinfo{volume}{7},
-  \bibinfo{year}{2019}, pp. \bibinfo{pages}{50--58}.
-%Type = Inproceedings
-\bibitem[{Steiger et~al.(2021)Steiger, Bharucha, Venkatagiri, Riedl, and
-  Lease}]{steiger2021psychological}
-\bibinfo{author}{M.~Steiger}, \bibinfo{author}{T.~J. Bharucha},
-  \bibinfo{author}{S.~Venkatagiri}, \bibinfo{author}{M.~J. Riedl},
-  \bibinfo{author}{M.~Lease},
-\newblock \bibinfo{title}{The psychological well-being of content moderators},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 2021 CHI Conference on
-  Human Factors in Computing Systems, CHI}, volume~\bibinfo{volume}{21},
-  \bibinfo{year}{2021}.
-%Type = Misc
-\bibitem[{Newton(2020)}]{newton_facebook_2020}
-\bibinfo{author}{C.~Newton}, \bibinfo{title}{Facebook will pay \$52 million in
-  settlement with moderators who developed {PTSD} on the job},
-  \bibinfo{year}{2020}. \URLprefix
-  \url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}.
-%Type = Article
-\bibitem[{Parks(2019)}]{parks2019dirty}
-\bibinfo{author}{L.~Parks},
-\newblock \bibinfo{title}{Dirty data: content moderation, regulatory
-  outsourcing, and the cleaners},
-\newblock \bibinfo{journal}{Film Quarterly} \bibinfo{volume}{73}
-  (\bibinfo{year}{2019}) \bibinfo{pages}{11--18}.
-%Type = Article
-\bibitem[{Stepanikova(2012)}]{stepanikova2012racial}
-\bibinfo{author}{I.~Stepanikova},
-\newblock \bibinfo{title}{Racial-ethnic biases, time pressure, and medical
-  decisions},
-\newblock \bibinfo{journal}{Journal of health and social behavior}
-  \bibinfo{volume}{53} (\bibinfo{year}{2012}) \bibinfo{pages}{329--343}.
-%Type = Misc
-\bibitem[{Koetsier(2020)}]{koetsier_report}
-\bibinfo{author}{J.~Koetsier}, \bibinfo{title}{Report: {Facebook} {Makes}
-  300,000 {Content} {Moderation} {Mistakes} {Every} {Day}},
-  \bibinfo{year}{2020}. \URLprefix
-  \url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/}.
-%Type = Article
-\bibitem[{Hoff and Mitchell(2009)}]{hoff2009cyberbullying}
-\bibinfo{author}{D.~L. Hoff}, \bibinfo{author}{S.~N. Mitchell},
-\newblock \bibinfo{title}{Cyberbullying: Causes, effects, and remedies},
-\newblock \bibinfo{journal}{Journal of Educational Administration}
-  (\bibinfo{year}{2009}).
-%Type = Book
-\bibitem[{Keipi et~al.(2016)Keipi, N{\"a}si, Oksanen, and
-  R{\"a}s{\"a}nen}]{keipi2016online}
-\bibinfo{author}{T.~Keipi}, \bibinfo{author}{M.~N{\"a}si},
-  \bibinfo{author}{A.~Oksanen}, \bibinfo{author}{P.~R{\"a}s{\"a}nen},
-  \bibinfo{title}{Online hate and harmful content: Cross-national
-  perspectives}, \bibinfo{publisher}{Taylor \& Francis}, \bibinfo{year}{2016}.
-%Type = Article
-\bibitem[{Wachs et~al.(2019)Wachs, Wright, Sittichai, Singh, Biswal, Kim, Yang,
-  G{\'a}mez-Guadix, Almendros, Flora et~al.}]{wachs2019associations}
-\bibinfo{author}{S.~Wachs}, \bibinfo{author}{M.~F. Wright},
-  \bibinfo{author}{R.~Sittichai}, \bibinfo{author}{R.~Singh},
-  \bibinfo{author}{R.~Biswal}, \bibinfo{author}{E.-m. Kim},
-  \bibinfo{author}{S.~Yang}, \bibinfo{author}{M.~G{\'a}mez-Guadix},
-  \bibinfo{author}{C.~Almendros}, \bibinfo{author}{K.~Flora}, et~al.,
-\newblock \bibinfo{title}{Associations between witnessing and perpetrating
-  online hate in eight countries: The buffering effects of problem-focused
-  coping},
-\newblock \bibinfo{journal}{International journal of environmental research and
-  public health} \bibinfo{volume}{16} (\bibinfo{year}{2019})
-  \bibinfo{pages}{3992}.
-%Type = Misc
-\bibitem[{French(2021)}]{french_as_2021}
-\bibinfo{author}{C.~French}, \bibinfo{title}{As the pandemic forces us online,
-  {LGBTQ2S}+ teens deal with cyberbullying}, \bibinfo{year}{2021}. \URLprefix
-  \url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}.
-%Type = Misc
-\bibitem[{League(2020)}]{ADL_free}
-\bibinfo{author}{A.-D. League}, \bibinfo{title}{Free to {Play}? {Hate},
-  {Harassment} and {Positive} {Social} {Experience} in {Online} {Games} 2020},
-  \bibinfo{year}{2020}. \URLprefix \url{https://www.adl.org/free-to-play-2020}.
-%Type = Misc
-\bibitem[{noa(2017)}]{noauthor_:game_nodate}
-\bibinfo{title}{In:{Game} {Abuse}}, \bibinfo{year}{2017}. \URLprefix
-  \url{https://www.ditchthelabel.org/research-papers/ingame-abuse/}.
-%Type = Article
-\bibitem[{Leader~Maynard and Benesch(2016)}]{leader2016dangerous}
-\bibinfo{author}{J.~Leader~Maynard}, \bibinfo{author}{S.~Benesch},
-\newblock \bibinfo{title}{Dangerous speech and dangerous ideology: An
-  integrated model for monitoring and prevention},
-\newblock \bibinfo{journal}{Genocide Studies and Prevention}
-  \bibinfo{volume}{9} (\bibinfo{year}{2016}).
-%Type = Article
-\bibitem[{Garland et~al.(2020)Garland, Ghazi-Zahedi, Young,
-  H{\'e}bert-Dufresne, and Galesic}]{garland2020countering}
-\bibinfo{author}{J.~Garland}, \bibinfo{author}{K.~Ghazi-Zahedi},
-  \bibinfo{author}{J.-G. Young}, \bibinfo{author}{L.~H{\'e}bert-Dufresne},
-  \bibinfo{author}{M.~Galesic},
-\newblock \bibinfo{title}{Countering hate on social media: Large scale
-  classification of hate and counter speech},
-\newblock \bibinfo{journal}{arXiv preprint arXiv:2006.01974}
-  (\bibinfo{year}{2020}).
-%Type = Article
-\bibitem[{Dictionary(2002)}]{dictionary2002merriam}
-\bibinfo{author}{M.-W. Dictionary},
-\newblock \bibinfo{title}{Merriam-webster},
-\newblock \bibinfo{journal}{On-line at http://www. mw. com/home. htm}
-  \bibinfo{volume}{8} (\bibinfo{year}{2002}) \bibinfo{pages}{2}.
-%Type = Inproceedings
-\bibitem[{Schieb and Preuss(2016)}]{schieb2016governing}
-\bibinfo{author}{C.~Schieb}, \bibinfo{author}{M.~Preuss},
-\newblock \bibinfo{title}{Governing hate speech by means of counterspeech on
-  facebook},
-\newblock in: \bibinfo{booktitle}{66th ica annual conference, at fukuoka,
-  japan}, \bibinfo{year}{2016}, pp. \bibinfo{pages}{1--23}.
-%Type = Article
-\bibitem[{Benesch et~al.(2016)Benesch, Ruths, Dillon, Saleem, and
-  Wright}]{benesch2016considerations}
-\bibinfo{author}{S.~Benesch}, \bibinfo{author}{D.~Ruths},
-  \bibinfo{author}{K.~P. Dillon}, \bibinfo{author}{H.~M. Saleem},
-  \bibinfo{author}{L.~Wright},
-\newblock \bibinfo{title}{Considerations for successful counterspeech},
-\newblock \bibinfo{journal}{Dangerous Speech Project}  (\bibinfo{year}{2016}).
-%Type = Article
-\bibitem[{Rieger et~al.(2018)Rieger, Schmitt, and Frischlich}]{rieger2018hate}
-\bibinfo{author}{D.~Rieger}, \bibinfo{author}{J.~B. Schmitt},
-  \bibinfo{author}{L.~Frischlich},
-\newblock \bibinfo{title}{Hate and counter-voices in the internet: Introduction
-  to the special isssue},
-\newblock \bibinfo{journal}{Studies in Communication and Media}
-  (\bibinfo{year}{2018}) \bibinfo{pages}{459--472}.
-%Type = Article
-\bibitem[{Ziegele et~al.(2018)Ziegele, Jost, Bormann, and
+  on obstacles and solutions}.
+\newblock \bibinfo{journal}{PeerJ Computer Science} \bibinfo{volume}{7},
+  \bibinfo{pages}{e598}.
+%Type = Article
+\bibitem[{Zaki(2014)}]{zaki2014empathy}
+\bibinfo{author}{Zaki, J.}, \bibinfo{year}{2014}.
+\newblock \bibinfo{title}{Empathy: a motivated account.}
+\newblock \bibinfo{journal}{Psychological bulletin} \bibinfo{volume}{140},
+  \bibinfo{pages}{1608}.
+%Type = Article
+\bibitem[{Ziegele et~al.(2018)Ziegele, Jost, Bormann and
   Heinbach}]{ziegele2018journalistic}
-\bibinfo{author}{M.~Ziegele}, \bibinfo{author}{P.~Jost},
-  \bibinfo{author}{M.~Bormann}, \bibinfo{author}{D.~Heinbach},
+\bibinfo{author}{Ziegele, M.}, \bibinfo{author}{Jost, P.},
+  \bibinfo{author}{Bormann, M.}, \bibinfo{author}{Heinbach, D.},
+  \bibinfo{year}{2018}.
 \newblock \bibinfo{title}{Journalistic counter-voices in comment sections:
   Patterns, determinants, and potential consequences of interactive moderation
-  of uncivil user comments},
+  of uncivil user comments}.
 \newblock \bibinfo{journal}{SCM Studies in Communication and Media}
-  \bibinfo{volume}{7} (\bibinfo{year}{2018}) \bibinfo{pages}{525--554}.
-%Type = Article
-\bibitem[{Ziems et~al.(2020)Ziems, He, Soni, and Kumar}]{ziems2020racism}
-\bibinfo{author}{C.~Ziems}, \bibinfo{author}{B.~He}, \bibinfo{author}{S.~Soni},
-  \bibinfo{author}{S.~Kumar},
+  \bibinfo{volume}{7}, \bibinfo{pages}{525--554}.
+%Type = Article
+\bibitem[{Ziems et~al.(2020)Ziems, He, Soni and Kumar}]{ziems2020racism}
+\bibinfo{author}{Ziems, C.}, \bibinfo{author}{He, B.}, \bibinfo{author}{Soni,
+  S.}, \bibinfo{author}{Kumar, S.}, \bibinfo{year}{2020}.
 \newblock \bibinfo{title}{Racism is a virus: Anti-asian hate and counterhate in
-  social media during the covid-19 crisis},
-\newblock \bibinfo{journal}{arXiv preprint arXiv:2005.12423}
-  (\bibinfo{year}{2020}).
-%Type = Article
-\bibitem[{Xie et~al.(2011)Xie, Sreenivasan, Korniss, Zhang, Lim, and
-  Szymanski}]{xie2011social}
-\bibinfo{author}{J.~Xie}, \bibinfo{author}{S.~Sreenivasan},
-  \bibinfo{author}{G.~Korniss}, \bibinfo{author}{W.~Zhang},
-  \bibinfo{author}{C.~Lim}, \bibinfo{author}{B.~K. Szymanski},
-\newblock \bibinfo{title}{Social consensus through the influence of committed
-  minorities},
-\newblock \bibinfo{journal}{Physical Review E} \bibinfo{volume}{84}
-  (\bibinfo{year}{2011}) \bibinfo{pages}{011130}.
-%Type = Article
-\bibitem[{Chandrasekharan et~al.(2017)Chandrasekharan, Pavalanathan,
-  Srinivasan, Glynn, Eisenstein, and Gilbert}]{chandrasekharan2017you}
-\bibinfo{author}{E.~Chandrasekharan}, \bibinfo{author}{U.~Pavalanathan},
-  \bibinfo{author}{A.~Srinivasan}, \bibinfo{author}{A.~Glynn},
-  \bibinfo{author}{J.~Eisenstein}, \bibinfo{author}{E.~Gilbert},
-\newblock \bibinfo{title}{You can't stay here: The efficacy of {R}eddit's 2015
-  ban examined through hate speech},
-\newblock \bibinfo{journal}{Proceedings of the ACM on Human-Computer
-  Interaction} \bibinfo{volume}{1} (\bibinfo{year}{2017})
-  \bibinfo{pages}{1--22}.
-%Type = Article
-\bibitem[{Bilewicz et~al.(2021)Bilewicz, Tempska, Leliwa, Dowgiałło, Tańska,
-  Urbaniak, and Wroczyński}]{bilewicz2021artificial}
-\bibinfo{author}{M.~Bilewicz}, \bibinfo{author}{P.~Tempska},
-  \bibinfo{author}{G.~Leliwa}, \bibinfo{author}{M.~Dowgiałło},
-  \bibinfo{author}{M.~Tańska}, \bibinfo{author}{R.~Urbaniak},
-  \bibinfo{author}{M.~Wroczyński},
-\newblock \bibinfo{title}{Artificial intelligence against hate: Intervention
-  reducing verbal aggression in the social network environment},
-\newblock \bibinfo{journal}{Aggressive Behavior} \bibinfo{volume}{47}
-  (\bibinfo{year}{2021}) \bibinfo{pages}{260--266}. \URLprefix
-  \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/ab.21948}.
-  \DOIprefix\doi{https://doi.org/10.1002/ab.21948}.
-  \href{http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/ab.21948}{{\tt
-  arXiv:https://onlinelibrary.wiley.com/doi/pdf/10.1002/ab.21948}}.
-%Type = Article
-\bibitem[{Brauer and Chaurand(2010)}]{brauer2010descriptive}
-\bibinfo{author}{M.~Brauer}, \bibinfo{author}{N.~Chaurand},
-\newblock \bibinfo{title}{Descriptive norms, prescriptive norms, and social
-  control: An intercultural comparison of people's reactions to uncivil
-  behaviors},
-\newblock \bibinfo{journal}{European Journal of Social Psychology}
-  \bibinfo{volume}{40} (\bibinfo{year}{2010}) \bibinfo{pages}{490--499}.
-%Type = Article
-\bibitem[{Fischer et~al.(2011)Fischer, Krueger, Greitemeyer, Vogrincic,
-  Kastenm{\""u}ller, Frey, Heene, Wicher, and
-  Kainbacher}]{fischer2011bystander}
-\bibinfo{author}{P.~Fischer}, \bibinfo{author}{J.~I. Krueger},
-  \bibinfo{author}{T.~Greitemeyer}, \bibinfo{author}{C.~Vogrincic},
-  \bibinfo{author}{A.~Kastenm{\""u}ller}, \bibinfo{author}{D.~Frey},
-  \bibinfo{author}{M.~Heene}, \bibinfo{author}{M.~Wicher},
-  \bibinfo{author}{M.~Kainbacher},
-\newblock \bibinfo{title}{The bystander-effect: a meta-analytic review on
-  bystander intervention in dangerous and non-dangerous emergencies.},
-\newblock \bibinfo{journal}{Psychological bulletin} \bibinfo{volume}{137}
-  (\bibinfo{year}{2011}) \bibinfo{pages}{517}.
-%Type = Article
-\bibitem[{Legault et~al.(2011)Legault, Gutsell, and
-  Inzlicht}]{legault2011ironic}
-\bibinfo{author}{L.~Legault}, \bibinfo{author}{J.~N. Gutsell},
-  \bibinfo{author}{M.~Inzlicht},
-\newblock \bibinfo{title}{Ironic effects of antiprejudice messages: How
-  motivational interventions can reduce (but also increase) prejudice},
-\newblock \bibinfo{journal}{Psychological Science} \bibinfo{volume}{22}
-  (\bibinfo{year}{2011}) \bibinfo{pages}{1472--1477}.
-%Type = Article
-\bibitem[{Morris and Cushman(2018)}]{morris2018common}
-\bibinfo{author}{A.~Morris}, \bibinfo{author}{F.~Cushman},
-\newblock \bibinfo{title}{A common framework for theories of norm compliance},
-\newblock \bibinfo{journal}{Social Philosophy and Policy} \bibinfo{volume}{35}
-  (\bibinfo{year}{2018}) \bibinfo{pages}{101--127}.
-%Type = Article
-\bibitem[{Cialdini et~al.(1990)Cialdini, Reno, and
-  Kallgren}]{cialdini1990focus}
-\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{R.~R. Reno},
-  \bibinfo{author}{C.~A. Kallgren},
-\newblock \bibinfo{title}{A focus theory of normative conduct: Recycling the
-  concept of norms to reduce littering in public places.},
-\newblock \bibinfo{journal}{Journal of personality and social psychology}
-  \bibinfo{volume}{58} (\bibinfo{year}{1990}) \bibinfo{pages}{1015}.
-%Type = Article
-\bibitem[{Cialdini et~al.(2006)Cialdini, Demaine, Sagarin, Barrett, Rhoads, and
-  Winter}]{cialdini2006managing}
-\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{L.~J. Demaine},
-  \bibinfo{author}{B.~J. Sagarin}, \bibinfo{author}{D.~W. Barrett},
-  \bibinfo{author}{K.~Rhoads}, \bibinfo{author}{P.~L. Winter},
-\newblock \bibinfo{title}{Managing social norms for persuasive impact},
-\newblock \bibinfo{journal}{Social influence} \bibinfo{volume}{1}
-  (\bibinfo{year}{2006}) \bibinfo{pages}{3--15}.
-%Type = Article
-\bibitem[{Goldstein et~al.(2008)Goldstein, Cialdini, and
-  Griskevicius}]{goldstein2008room}
-\bibinfo{author}{N.~J. Goldstein}, \bibinfo{author}{R.~B. Cialdini},
-  \bibinfo{author}{V.~Griskevicius},
-\newblock \bibinfo{title}{A room with a viewpoint: Using social norms to
-  motivate environmental conservation in hotels},
-\newblock \bibinfo{journal}{Journal of consumer Research} \bibinfo{volume}{35}
-  (\bibinfo{year}{2008}) \bibinfo{pages}{472--482}.
-%Type = Article
-\bibitem[{Kallgren et~al.(2000)Kallgren, Reno, and
-  Cialdini}]{kallgren2000focus}
-\bibinfo{author}{C.~A. Kallgren}, \bibinfo{author}{R.~R. Reno},
-  \bibinfo{author}{R.~B. Cialdini},
-\newblock \bibinfo{title}{A focus theory of normative conduct: When norms do
-  and do not affect behavior},
-\newblock \bibinfo{journal}{Personality and social psychology bulletin}
-  \bibinfo{volume}{26} (\bibinfo{year}{2000}) \bibinfo{pages}{1002--1012}.
-%Type = Article
-\bibitem[{Cialdini and Goldstein(2004)}]{cialdini2004social}
-\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{N.~J. Goldstein},
-\newblock \bibinfo{title}{Social influence: Compliance and conformity},
-\newblock \bibinfo{journal}{Annual review of psychology} \bibinfo{volume}{55}
-  (\bibinfo{year}{2004}) \bibinfo{pages}{591--621}.
-%Type = Article
-\bibitem[{Stangor et~al.(2001)Stangor, Sechrist, and
-  Jost}]{stangor2001changing}
-\bibinfo{author}{C.~Stangor}, \bibinfo{author}{G.~B. Sechrist},
-  \bibinfo{author}{J.~T. Jost},
-\newblock \bibinfo{title}{Changing racial beliefs by providing consensus
-  information},
-\newblock \bibinfo{journal}{Personality and Social Psychology Bulletin}
-  \bibinfo{volume}{27} (\bibinfo{year}{2001}) \bibinfo{pages}{486--496}.
-%Type = Article
-\bibitem[{Crandall et~al.(2002)Crandall, Eshleman, and
-  O'brien}]{crandall2002social}
-\bibinfo{author}{C.~S. Crandall}, \bibinfo{author}{A.~Eshleman},
-  \bibinfo{author}{L.~O'brien},
-\newblock \bibinfo{title}{Social norms and the expression and suppression of
-  prejudice: the struggle for internalization.},
-\newblock \bibinfo{journal}{Journal of personality and social psychology}
-  \bibinfo{volume}{82} (\bibinfo{year}{2002}) \bibinfo{pages}{359}.
-%Type = Article
-\bibitem[{Munger(2017)}]{munger2017tweetment}
-\bibinfo{author}{K.~Munger},
-\newblock \bibinfo{title}{Tweetment effects on the tweeted: Experimentally
-  reducing racist harassment},
-\newblock \bibinfo{journal}{Political Behavior} \bibinfo{volume}{39}
-  (\bibinfo{year}{2017}) \bibinfo{pages}{629--649}.
-  \DOIprefix\doi{10.1007/s11109-016-9373-5}.
-%Type = Article
-\bibitem[{Price et~al.(2006)Price, Nir, and Cappella}]{price2006normative}
-\bibinfo{author}{V.~Price}, \bibinfo{author}{L.~Nir}, \bibinfo{author}{J.~N.
-  Cappella},
-\newblock \bibinfo{title}{Normative and informational influences in online
-  political discussions},
-\newblock \bibinfo{journal}{Communication Theory} \bibinfo{volume}{16}
-  (\bibinfo{year}{2006}) \bibinfo{pages}{47--74}.
-%Type = Inproceedings
-\bibitem[{Cheng et~al.(2017)Cheng, Bernstein, Danescu-Niculescu-Mizil, and
-  Leskovec}]{cheng2017anyone}
-\bibinfo{author}{J.~Cheng}, \bibinfo{author}{M.~Bernstein},
-  \bibinfo{author}{C.~Danescu-Niculescu-Mizil}, \bibinfo{author}{J.~Leskovec},
-\newblock \bibinfo{title}{Anyone can become a troll: Causes of trolling
-  behavior in online discussions},
-\newblock in: \bibinfo{booktitle}{Proceedings of the 2017 ACM conference on
-  computer supported cooperative work and social computing},
-  \bibinfo{year}{2017}, pp. \bibinfo{pages}{1217--1230}.
-%Type = Incollection
-\bibitem[{Cialdini et~al.(1991)Cialdini, Kallgren, and
-  Reno}]{cialdini_focus_1991}
-\bibinfo{author}{R.~B. Cialdini}, \bibinfo{author}{C.~A. Kallgren},
-  \bibinfo{author}{R.~R. Reno},
-\newblock \bibinfo{title}{A {Focus} {Theory} of {Normative} {Conduct}: {A}
-  {Theoretical} {Refinement} and {Reevaluation} of the {Role} of {Norms} in
-  {Human} {Behavior}},
-\newblock in: \bibinfo{booktitle}{Advances in {Experimental} {Social}
-  {Psychology}}, volume~\bibinfo{volume}{24}, \bibinfo{publisher}{Elsevier},
-  \bibinfo{year}{1991}, pp. \bibinfo{pages}{201--234}. \URLprefix
-  \url{https://linkinghub.elsevier.com/retrieve/pii/S0065260108603305}.
-  \DOIprefix\doi{10.1016/S0065-2601(08)60330-5}.
+  social media during the covid-19 crisis}.
+\newblock \bibinfo{journal}{arXiv preprint arXiv:2005.12423} .
 

### 2023-12-18 technical_report/nesta_study_technical_report.Rmd
clean up

---
title: "Bayesian analysis of the NESTA study of interventions against  verbal aggression online \\linebreak  Technical Report"
author: "Rafal Urbaniak"
output:
  pdf_document:
  number_sections: yes
  keep_tex: yes
df_print: kable
includes:
  in_header: Rafal_latex8.sty
html_document:
  df_print: paged
word_document: default
classoption: dvipsnames, enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/attacks.bib
csl: ../references/apa-6th-edition.csl
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)
library(ggrepel)

mykable <- function(object) {kable(object, "latex", booktabs = T,linesep = "") %>% kable_styling(latex_options = "striped",font_size = 9)}

removeX <-   theme(axis.title.x=element_blank(),
                   axis.text.x=element_blank(),
                   axis.ticks.x=element_blank())

removeY <-   theme(axis.title.y=element_blank(),
                   axis.text.y=element_blank(),
                   axis.ticks.y=element_blank())

knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 70), tidy = FALSE)

#kable(table(data$group), "latex", booktabs = T, col.names = c("Group", "n")) %>% 
#  kable_styling(latex_options = c("striped","HOLD_position"),font_size = 9) 
```

\tableofcontents

# Data and exploration

\vspace{1mm}
\scriptsize

```{r periodsVisualisationPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
summaries <- read.csv(file = "datasets/Summaries.csv")

summaries$ABS <- standardize(summaries$AB)
summaries$CBS <- standardize(summaries$CB)
summaries$AAS <- standardize(summaries$AA)
summaries$CAS <- standardize(summaries$CA)
summaries$CDS <- standardize(summaries$CD)
summaries$ADS <- standardize(summaries$AD)
summaries$group <- as.factor(summaries$group)
summaries$groupID <-  as.integer( as.factor(summaries$group) )

dates <- colnames(Hate)[-1]
dates <- as.Date(dates)
startDate <- dates[1]
interventionDate <- "2020-07-08"
observationDate <- "2020-09-09"
end <- dates[length(dates)]

periods<- numeric(length(dates))
periods <- ifelse(dates < interventionDate,"pre-treatment",periods)
periods <- ifelse(dates >= interventionDate & dates < observationDate,"treatment",periods)
periods <- ifelse(dates >= observationDate,"post-treatment",periods)

hateTS <- as.data.frame(colSums(Hate[,-1]))
hateTS$date <- as.Date(rownames(hateTS))
rownames(hateTS) <- NULL
colnames(hateTS) <- c("attacks","date")
hateTS$periods <- periods

interventions <- readRDS(file = "datasets/interventions.rds")
interventionsTS <- as.data.frame(table(interventions$day))
interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
colnames(interventionsTS) <- c("date", "interventions")

periodsDF <- merge(x = hateTS, y = interventionsTS, by = "date", all.x = TRUE)

idx <- c(1, diff(periodsDF$date))
i2 <- c(1,which(idx != 1), nrow(periodsDF)+1)
periodsDF$grp <- rep(1:length(diff(i2)), diff(i2))

periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "treatment"] <- 0

periodsPlot <- ggplot(periodsDF)+
  geom_line(aes(x=date, y = attacks, group = grp),
             alpha = 0.8, size = .6)+
  geom_line(aes(x=date, y = interventions, group = grp),
            alpha = 0.8, size = .6)+
  geom_vline(xintercept = startDate, lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept = as.Date(interventionDate), lty =2, size =.2, alpha=0.5)+
  geom_vline(xintercept =  as.Date(observationDate), lty = 2, size =.2, alpha=0.5 )+
  geom_vline(xintercept = as.Date(end), lty =2, size =.2, alpha=0.5)+
  labs(title = "Personal attacks and interventions time series",
       subtitle = "no line at data gaps", 
       caption = 
    "days with data: 81 (pre-treatment), 62 (treatment), 72 (post-treatment)")+
  theme_tufte() + theme(axis.title.x=element_blank(), 
  plot.caption = element_text(hjust = 0.5,  face= "italic"),
  plot.title = element_text(size=17),
  plot.title.position = "plot")+
  scale_x_date(date_labels = "%b %d", breaks = c(startDate, as.Date(startDate),
              as.Date(interventionDate),  as.Date(observationDate), end), 
              limits = c(startDate-30,end+10))+ylab("count")+
  annotate("rect", xmin = as.Date(interventionDate), xmax = as.Date(observationDate),
           ymin = -1, ymax = 360,
           alpha = .2,fill = "darkgreen")+ylim(c(-1,370))+
  annotate("text", label = "pre-treatment", x = as.Date(startDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "treatment", x = as.Date(interventionDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "post-treatment", x = as.Date(observationDate)+2, y = 370, hjust =0 )+
  annotate("text", label = "interventions:", x = as.Date(interventionDate)-55, y = 15, hjust =0 )+
  annotate("text", label = "attacks:", x = as.Date(startDate)-30, y = 215, hjust =0 )

periodsDF$weekdays <-  weekdays(as.Date(periodsDF$date))
periodsDF$weeks <-  week(as.Date(periodsDF$date))

periodsDF$weekdays <- as.factor(periodsDF$weekdays)
levels(periodsDF$weekdays) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday",
                                "Saturday", "Sunday")
weeksPlot <- ggplot(periodsDF)+
  geom_smooth(aes(x = weekdays, y = attacks, group =1))+
  geom_line(aes(x = weekdays, y = attacks, group = weeks),alpha = 0.1)+
  theme_tufte()+labs(title="Personal attacks vs weekdays (six months)", subtitle = "no weekly patterns")+xlab("")+
  ylab("attacks per day")+ theme(plot.title.position = "plot",
  plot.title = element_text(size=17))
```
\normalsize

For the duration of the project we selected `r length(unique(summaries$author))` Reddit users  and tracked their activity (with some breaks resulting from API restrictions and technical issues, which were mostly sorted out in the observation period), starting on 
`r startDate`, beginning the intervention period on `r interventionDate`, leading to a further observation period starting on  `r observationDate` and ending on  `r end`. The time series of attacks observed and of interventions conducted can be inspected in Figure \ref{fig:periodsPlot}, along with a quick search for weekly patterns. Some of the users turned out to be bots, a few ceased to be active during the experiment (with no strong reason to think this happened due to them receiving an intervention) and a few received treatment of two different types by accident (we relied on multiple volunteers and such mistakes were likely to happen). Ultimately, in the time series data, we ended up with  data on 440 users.

\begin{figure}[H]
```{r periodsPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "48%", warning = FALSE, message = FALSE}
periodsPlot
weeksPlot
```
\caption{Daily sums of attacks and interventions throughout the three experimental periods, with GAM smoothing (left) and daily attack sums from all  weeks in the experimental period plotted against week days (right)---no pattern seems to arise.}
\label{fig:periodsPlot}
\end{figure}

We analyzed the data from three perspectives: we used the daily data to (1) build seven time series models estimating the impact of individual interventions at lags 1-7 days, and (2) to study the impact of the cumulative number of total interventions received as the experiment progressed, and then we used aggregated data to run a long term before-and after analysis, comparing the summarized aggression levels before and after the intervention period.

Before we move to the analysis, let us inspect the data. First, at the aggregated level, the data involve the variables listed in Table \ref{tab:baaVars}.\footnote{Further variables were defined in terms of those, in particular, we will be predicting \textsf{AdiffS} which is the standardized difference  \textsf{AA}-\textsf{AB}, and \textsf{AdiffS}, which is the standardized difference \textsf{CA}-\textsf{CB}.The  standardized variables are systematically named  $\langle$variable\char`_name$\rangle$S.}

\vspace{1mm}
\footnotesize
```{r varsTablePrep,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
variable <- c("AB", "AD", "AA", "CB", "CD", "CA", "group", "IC")
explanation <- c("attacks before (pre-treatment)", "attacks during (the treatment period)",
                 "attacks after (post-treatment)", "comments before", "comments during",
                 "comments after", "treatment group", "intervention count")
vars <- data.frame(variable, explanation)
#mykable(vars)
```
\normalsize

\begin{table}
\centering
\begin{tabular}{ll}
\toprule
variable & explanation\\
\midrule
\cellcolor{gray!6}{AB} & \cellcolor{gray!6}{attacks before (pre-treatment)}\\
AD & attacks during (the treatment period)\\
\cellcolor{gray!6}{AA} & \cellcolor{gray!6}{attacks after (post-treatment)}\\
CB & comments before\\
\cellcolor{gray!6}{CD} & \cellcolor{gray!6}{comments during}\\
CA & comments after\\
\cellcolor{gray!6}{group} & \cellcolor{gray!6}{treatment group}\\
IC & intervention count\\
\bottomrule
\end{tabular}

\caption{Variables involved in the before-and-after analysis.}
\label{tab:baaVars}
\end{table}

The distribution of \textsf{IC} in the treatment groups is visualized in Figure \ref{fig:interventionsDistro}. Note that the distributions are somewhat different, even though the total intervention counts are similar. The issue is discussed in Section XXXXX.

<!-- TODO REF -->

\vspace{1mm}
\footnotesize
```{r interventionsDistroPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
interventionsDistro2 <- ggplot(summaries[summaries$group != "control",],
  aes(x = IC, fill = group))+
  geom_bar()+theme_tufte()+
  xlab("interventions received")+
  labs(title = "Total intervention counts by users and treatment groups")+
  scale_x_continuous(breaks = seq(0,40,5))+ 
  theme(plot.title.position = "plot",legend.position = c(0.8, 0.8))+
  scale_fill_manual(values=c("dodgerblue4", "orangered"))+ylab("number of users")
```
\normalsize

\begin{figure}[H]
```{r interventionsDistroPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
interventionsDistro2
```
\caption{Distribution of daily interventions (by treatment group).}
\label{fig:interventionsDistro}
\end{figure}

Second, in the distribution of standardized difference in attacks,  the peaks of distributions are shifted a bit between the groups, with lowest median for the normative group, but the differences seem minor (Figure \ref{fig:violJoint}).  This might suggest no impact of the interventions. This conclusion would be too hasty, as the impact of  other predictor variables and interactions involved can mask actual associations.

\vspace{1mm}
\footnotesize
```{r violEmpiricalAdiff,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
violAdiffS3 <- ggplot(summaries, aes(x=group, y = AdiffS, color = group))+
  geom_violin() +theme_tufte() +theme(plot.title.position = "plot")+
  ylab("change in attacks (standardized)")+  
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
  theme(legend.position = c(0.8, 0.2))

violAddifS3restr <- violAdiffS3 + ylim(c(-1,1))+geom_boxplot(width = .2)+ 
  ggtitle("restricted to (-1,1)") + 
  theme(plot.title.position = "plot", legend.position = "none")

 violJoint3 <- ggarrange(violAdiffS3+ggtitle("whole range")+
  theme(plot.title.position = "plot"),  violAddifS3restr)

violJointTitled3 <- annotate_figure(violJoint3,
  top = text_grob("Empirical distribution of change in attacks (standardized)",
                   size = 12))
```
\normalsize

\begin{figure}[H]
```{r violJoint,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
violJointTitled3
```
\caption{Empirical distribution of change in attacks (by treatment group).}
\label{fig:violJoint}
\end{figure}

To see how this masking can occur, let us inspect changes in attacks against intervention
counts. It turns out that restricting attention to various aggression levels in the before period results in
fairly strong changes to the regression lines (Figure \ref{fig:linearShift}). This suggests we should keep an eye out for interactions with aggression before in the analysis, and that the initial comparison of means or medians between groups might be misleading if the effects in different volume groups are different and to some extent cancel each other.

\vspace{1mm}
\footnotesize
```{r icPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
icplot1b <- ggplot(summaries, 
          aes(x = IC, y = AdiffS, color = group, fill = group)) +
      geom_jitter(alpha = 0.6, size = 0.8) +
      theme_tufte() +
      geom_smooth(alpha = 0.2, method = "lm", size = .5) + 
      xlim(c(0, 25)) + ylim(c(-2, 2)) +
      ggtitle("y restricted to (-2,2)") + 
      theme(legend.position = c(0.65, 0.2), plot.title.position = "plot") +
      ylab("change in attacks (standardized)")+  
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+  
  scale_fill_manual(values=c("darkgreen", "dodgerblue4", "orangered"))

icplot2b <- ggplot(summaries, 
          aes(x = IC, y = AdiffS, color = group, fill = group)) +
      geom_jitter(alpha = 0.6, size = 0.8) + 
      theme_tufte() +
      geom_smooth(alpha = 0.2, method = "lm", size = .5) + 
      xlim(c(0, 25)) + ylim(c(-1, 1)) + 
      ggtitle("y restricted to (-1,1)") + 
      theme(plot.title.position = "plot",legend.position = "none") +  
      ylab("change in attacks (standardized)")+  
      scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
      scale_fill_manual(values=c("darkgreen", "dodgerblue4", "orangered"))

icplotJointb <- ggarrange(icplot1b, icplot2b) 
icplotTitledb <- annotate_figure(icplotJointb, 
  top = text_grob("Change in attacks (standardized) vs interventions received", 
                  size = 12))
```

\begin{figure}
```{r fig:linearShift,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
icplotTitledb 
```
\caption{Change in attacks vs the number of interventions received by treatment group, jittered with  linear smoothing.}
\label{fig:linearShift}
\end{figure}

\normalsize 
Further insights, undermining the initial impression suggested by Figure \ref{fig:violJoint}, can be obtained by visualizing individual time series. Figure \ref{fig:tsVis} contains  six fairly typical examples.

\vspace{1mm}
\footnotesize
```{r tsVisPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
hateDFs <- readRDS("datasets/hateDFsNoDropouts.RDS")

start <- as.Date("2020-03-09")
treatment <- as.Date("2020-07-08")
observation <- as.Date("2020-09-09")
end <- as.Date("2020-11-20")

plotUser <- function(user, divider =5){
  ggplot(hateDFs[[user]])+
    geom_point(aes(x = day, y = attacks, group = user), alpha = .4, size = .4)+
    geom_smooth(aes(x = day, y = attacks), size = .5)+
    geom_line(aes(x = day, y = intCL3D/10), color = "orangered", alpha = .8)+
    theme_tufte(base_size = 7)+xlab("")+ 
    geom_vline(xintercept = as.Date("2020-07-08"),
               lty = 2, size = 0.2, alpha = 0.5)+
    geom_vline(xintercept = as.Date("2020-09-09"),
               lty = 2, size = 0.2, alpha = 0.5)+
    annotate("rect", xmin = as.Date("2020-07-08"),
             xmax = as.Date("2020-09-09"), ymin = -.5, 
             ymax = max(hateDFs[[user]]$attacks* 1.05),
             alpha = 0.2,  fill = "darkgreen")+
    geom_smooth(aes(x = day, y = act/divider), 
                color = "grey", alpha = .5, se = FALSE, size = .4)+
    ggtitle(paste("User ", user, " (", ifelse(hateDFs[[user]]$type[1] == "emp",
                                              "empathy", ifelse(hateDFs[[user]]$type[1] == "norm",
                                                                "normative", "control")),")", sep = ""))+
    labs(subtitle = paste("ABS =", round(hateDFs[[user]]$ABS[1],3),
                          ", activity divider=", divider,sep = ""))+
    theme(plot.title.position = "plot", plot.title = element_text(size=16))  + 
    annotate("text", x = as.Date("2020-05-11"), y = -.7, label = "pre-treatment", size = 3.5)+ 
    annotate("text", x = as.Date("2020-08-11"), y = -.7, label = "treatment", size = 3.5)+ 
    annotate("text", x = as.Date("2020-10-11"), y = -.7, label = "post-treatment", size = 3.5)+
    theme(plot.title.position = "plot")+
    scale_x_date(date_labels = "%b %d", breaks = c(start, treatment, observation,  end))
}

c1plot <- plotUser(34, divider = 10)
c2plot <- plotUser(22, divider = 4)
n1plot <- plotUser(39, divider = 8)
n2plot <- plotUser(2, divider = 6)
e1plot <- plotUser(231, divider = 4)
e2plot <- plotUser(112, divider = 4) + ylim(0,1.5)

individualTSplot3 <- ggarrange(c1plot, e1plot, n1plot, c2plot, e2plot,  n2plot)
individualTSplotTitled3 <- annotate_figure(individualTSplot3,
  top = text_grob("Individual time series by group and activity (examples)",  
                  size = 12))
```

\begin{figure}
```{r fig:tsVisPlot,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
individualTSplotTitled3
```
\caption{Examples of individual time series. Black points are attacks (smoothed in blue), red lines represent the cumulative number of interventions received (lag 3) divided by 10, gray lines represent overall activity level divided by a variable divider listed in the subtitle. Divisions introduced for visual comparability of general trends.}
\label{fig:tsVis}
\end{figure}

\normalsize

The general phenomenon is that while in the control group attacks tend not to diminish, unless activity itself diminishes, they tend to diminish in the normative group (although the more aggressive the user is, the less of an impact can be observed), and in the empathetic group if the user is not very aggressive. Of course, visualization of individual cases (which the reader might suspect to be cherry-picked) is no replacement for statistical analysis, to which we will now move.

# Causal thinking, choice of variables and models

First, we inspect correlations between predictors to avoid, and develop a plausible causal model of the situation (Figure \ref{fig:correlations}). It turns out that to avoid multicolinearity we cannot  condition on CDS if we condition on CAS or CBS. Similarly, for the time series data, since activity levels in  particular day slices are correlated, it will  not be useful to condition on more than one auto-regressive element (and since the predictive power is the highest for lag 1 with no discoverable weekly patterns, we will not go further than lag 1).

To identify the right variables to condition (or not condition) on to identify the causal effect of the interventions, we need to think about the causal structure of the problem. Comments during impact attacks during, which trigger interventions. Unmeasured user features cause comments before, which impact attacks before directly. Comments during (their impact on ADS is already included)  impact attacks during  directly and  comments after, which impact attacks after and   attacks after directly.  Intervention count impacts attacks after  and comments after. The same directions of impact are included for intervention type. Finally, comments through time are connected causally, and so are attacks. The structure for the time series data is analogous, except now instead of before and after, we have multiple daily indices.

\vspace{1mm}
\footnotesize
```{r dag1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%"}
dag <- dagitty("
  dag{
  CDS -> ADS -> IC  
               U [unobserved]   
               U -> CBS -> ABS  
               U -> ABS        
               U -> CDS -> ADS  
               U -> ADS         
               U -> CAS -> AAS    
               U -> AAS                        
               IC -> AAS        
               IC -> CAS        
               IT -> CAS        
               IT -> AAS
               CBS -> CDS -> CAS
               ABS -> ADS -> AAS
               }")
coordinates( dag ) <- list(x=c(CBS=0,ABS=0,CDS=1,ADS=1, CAS = 2,
                               AAS = 2, IT = 1.5, IC = 1.5, U = .5) ,
                            y=c(CBS =0,ABS = 1,CDS = 0,ADS = 1,
                                CAS = 0, AAS = 1, IT = .3, IC = .7, U =.5) )
```
\normalsize

\begin{figure}[H]
```{r correlations,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "48%",   message = FALSE, warning = FALSE, results = FALSE}
summariesCorr <- select(summaries, IC, ABS, CBS, AAS, CAS, CDS, ADS)
ggcorr(summariesCorr, method = c("pairwise"),
       digits = 4, low = "steelblue", mid = "white",
       high = "darkred", midpoint =0,
       geom = "tile", label = TRUE, label_size=4, label_round =2, layout.exp =1,
       label_alpha = FALSE,hjust = 0.75)+ggtitle("Only activity levels through time are strongly correlated")

drawdag(dag)  
```

\caption{Correlations between predictors (left) and a plausible causal model (right) used in the before-and-after analysis.}
\label{fig:correlations}
\end{figure}

What do we learn from  causal considerations? \textsf{IT} has no backdoor paths, but \textsf{IC} does, so we need to make sure these are closed to avoid including spurious correlations in our analysis. There are in fact 65 different paths from \textsf{IC} to \textsf{AAC}. Crucially,  all backdoor paths go through \textsf{ADS}, which then becomes either a fork or a pipe, so all backdoor paths can be closed by conditioning on \textsf{ADS}. Moreover there is only one directed indirect path, it goes through \textsf{CAS}, so we should not condition on \textsf{CAS} if we are to identify total  causal effect of \textsf{IC} on attacks, including the impact  mediated by its impact on comments. We might be interested in  the direct effect of \textsf{IC}  and \textsf{IT} on \textsf{AAS}, but then we also need to block indirect causal paths from the intervention to the outcome. For such an evaluation we would need to also condition on \textsf{CAS} and block all backdoor paths from \textsf{CAS} to \textsf{AAS}. This, however, given the causal model, cannot be achieved, as it would required conditioning on unobserved user features. That is, we do not think direct causal effect is identifiable.

Analogous considerations apply to the time series model for the total impact of individual interventions received exactly $k$ days before (in our case, $k\in \{1, \dots, 7\}$). The situation, however, is somewhat different for the impact of the total number of cumulative interventions received so far. The trouble is, for example, that if a user received so far a number  interventions until yesterday, some of them had been received before yesterday and those had already impacted the aggression level yesterday. In other words, conditioning on lagged attacks leads to the post-treatment bias and should be avoided.\footnote{In fact, in the aggregated data analysis, we will be predicting the standardized difference between attacks before and after (\textsf{ADiffS}), and the standardized difference between comments, before and after (\textsf{CDiffS}), but the general points about the nodes involved apply also to defined nodes.  As already discussed, we do not include \textsf{CDS} because of its strong correlation with \textsf{CBS}. We also do not condition on \textsf{ABS} when modeling \textsf{ADiffS} (or on \textsf{CBS} when modeling \textsf{CDiffS})---not only because it has a pretty strong correlation with another predictor (\textsf{ADS}), but rather also because it is used to define the output variable. In such a set-up, it is clear that a model including \textsf{ABS} would have better predictive power, but since a definitional connection is present, thinking that its inclusion in the model tells us something about causality  would be misled.}

Otherwise, it's open season for the  other variables and interactions between them, and our decision to include or exclude them in the model will be guided by    information-theoretic criteria of predictive power (\textsf{WAIC}, the so-called \emph{Widely Acceptable Information Criterion}),\footnote{
Here's a more detailed explanation of the model comparison method we used, uninterested reader is invited to skip forward. Let  $y$ be the observations and $\Theta$  a posterior distribution.
First, log-pointwise-predictive-density is defined by:
\begin{align*}
\mathsf{lppd}(y, \Theta) & = \sum_i log\frac{1}{S}\sum_s p (y_i\vert \Theta_s)
\end{align*}
\noindent where $S$ is the number of samples in the posterior, and $\Theta_s$ 
is the $s$-th combination of sampled parameter values in the posterior distribution. That is, 
for each observation and each combination of 
parameters in the posterior we first compute its density, then 
we take the average density of that observation over all combinations of parameters in the posterior,
and  then take the logarithm. Finally, we sum these values up for all the observations. Crucially, when comparing posterior distributions with respect to the same dataset, \textsf{lppd}s are proportional
 to unbiased estimates of their divergence from the real distribution (note that it is \emph{only} 
 proportional, and for this reason can be used for comparison of distributions 
 only and makes no intuitive sense on its own).  However, \textsf{lppd} always improves
  as the model gets more complex, so for model comparison it makes more sense to use 
 the Widely Applicable Information Criterion (WAIC), which is an approximation of the out-of-sample deviance that converges to the cross-validation approximation in a large sample. It  is defined as
 the log-posterior-predictive-density with an additional
  penalty proportional to the variance in the
  posterior predictions:
  \begin{align*}
\mathsf{WAIC(y, \Theta)} & = -2 (\mathsf{lppd} - \overbrace{\sum_i var_\theta \mathsf{log} p (y_i \vert \theta)}^{\mathsf{penalty}})
  \end{align*}
\noindent  Thus to construct the penalty, we calculate the variance in log-probabilities for each observation and sum them up. Because of the analogy to Akaike's criterion, the penalty is sometimes called the effective number of parameters, $p_{\mathsf{WAIC}}$. 
How does WAIC compare to other information criteria?  AIC uses MAP estimates instead of the posterior and requires that priors be flat or overwhelmed by the likelihood, and assumes that the posterior distribution is approximately multivariate Gaussian and the sample size is  much greater  than the number of parameters used in the model. Bayesian Information Criterion (BIC) also requires flat priors and uses MAP estimates. WAIC does not make these assumptions, and provides almost exactly the same results as AIC, when AIC’s assumptions are met.} or posterior predictive checks in cases in which the  likelihood functions used by the models to be compared are different and information-theoretic calculations might be misleading. In such cases we investigated the ratio of actual observations included in the 50\% and in the 89\% posterior predictive distribution, and the models for which higher ratios were observed in both were selected (no case of diverging evaluation for the two criteria has been observed).

In our model building we will be using the \textsf{rethinking} package, except for the cumulative impact time series models, where it becomes computationally unfeasible, in which case we build models in \textsf{Rstan} directly. Moreover, for the time series analysis we will build hierarchical Bayesian models which tend to have around $u \times 2p + 2p$ parameters (we will explain later why), which means that for 440 users our final model with interaction with six predictors would have $440 \times 12 + 12 = 5292$ parameters, and the model would have to be trained on six months of daily data for 7 variables. The building of such a model on a modern computer takes days. Since in reaching this model we needed to build multiple somewhat simpler models or models with  different structures and test their performance, model selection on the full data set was unfeasible. That is, in the time series analysis in model selection at each step we compared models (sometimes built with quadratic approximation) with respect to three independent samples for $40, 60$ and $60$ users. We made the decision only if a given model structure performed better in all these subsets (which was usually the case, so the model selection criteria gave us pretty robust answers). For the most complicated model of the impact of cumulative number of interventions, building a single model for the whole data set was not computationally feasible (computation time does not increase linearly with the number of users included in the dataset), so we randomly split the dataset into four and provided results for all of them. The results were not very divergent.

# Time series model selection

Suppose we are interested in the impact of interventions received $n$ days ago. We started with a simple null model that uses the Poisson distribution, with either uses a single $\lambda$ for all the users, or user-specific $\lambda$s. The first Bayesian model has the following structure:
\begin{align*}
\mathsf{attacks_i} & \sim  \textsf{Poisson}( \lambda)\\ 
    log(\lambda)  & =  l \\
    l & \sim  \textsf{Norm}(.05,2.8)
\end{align*}

and the user-specific coefficient model had the following structure:
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{Poisson}( \lambda_i)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} \\
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.8)
\end{align*}

\footnotesize
```{r nullTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
dat <- readRDS(file = "datasets/dat.RDS")

lmu <- .05
lsigma <- 2.8

nullPoisson <-  quap(
  alist(
    attacks ~ dpois( lambda),
    log(lambda) <- l,
    l ~ dnorm(lmu,lsigma)
  ), data=datA)

#prior predictive check
prior <- extract.prior( nullPoisson , n=1e4 )
lambda <- exp(prior$l) 
priorPlot <- ggplot()+ geom_density(aes(x = lambda))+xlim(c(0,50))+
  ggtitle("Lambda")+theme_tufte()

nullPoissonUser <-  quap(
  alist(
    attacks ~ dpois( lambda),
    log(lambda) <- l[userID],
    l[userID] ~ dnorm(lmu,lsigma)
  ), data=dat)

compare(nullPoisson, nullPoissonUser)
```
\normalsize

The priors were chosen using prior predictive check, so that the 89\% density intervals reached between 0 and 34, with median around 1. Given our prior experience with similar user datasets this is a fairly wide informative prior. The comparison, unsurprisingly, preferred the user-specific $\lambda$s.

Next, we introduced the auto-regressive element, conditioning on yesterday's attacks. The choice of priors for the auto-regression coefficient is guided by the visualization (intuitive direct understanding of the values is made difficult by the fact that the predictors work on the logarithmic scale) and the fact that larger values would result in a unreasonably  extreme impact of yesterday's attacks. 
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{Poisson}( \lambda_i)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.8)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.2)
\end{align*}

\footnotesize
```{r AR1TSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
amu <- 0
asigma <- .2

AR1Poisson <-  quap(
  alist(
    attacks ~ dpois( lambda),
    log(lambda) <- l[userID] + a[userID] * attacksL1,
    l[userID] ~ dnorm(lmu,lsigma),
    a[userID] ~ dnorm(amu, asigma)
  ), data=dat)

prior <- extract.prior( AR1Poisson , n=1e4 )

N <- 300
plot( NULL , xlim=c(0,40) , ylim=c(0,200) )
for ( i in 1:N ) curve( exp( prior$l[i,1] + prior$a[i,1]*x ) , add=TRUE , col=grau() )

compare(AR1Poisson,nullPoissonUser)
```
\normalsize

Next,  we  added today's activity level as a predictor, with  user-specific coefficients. Adding activity levels helps. Note also that our priors taken separately were made more narrow, to preserve the overall width of the prior predictive distribution (this will be the usual strategy as we progress).
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{Poisson}( \lambda_i)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c * \mathsf{act}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c & \sim  \textsf{Norm}(0,.1)
\end{align*}
\noindent Unsurprisingly, it helps even more if the coefficients are user-specific:
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{Poisson}( \lambda_i)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1)
\end{align*}

\footnotesize
```{r AR1CTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
lmu <- .05
lsigma <- 2.3
amu <- 0
asigma <- .1
cmu <- 0
csigma <- .1

AR1CSimplePoisson <-  quap(
  alist(
    attacks ~ dpois( lambda),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c * act,
    l[userID] ~ dnorm(lmu,lsigma),
    a[userID] ~ dnorm(amu, asigma),
    c ~ dnorm(cmu, csigma)
  ), data=dat)

AR1CPoisson <-  quap(
  alist(
    attacks ~ dpois( lambda),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act,
    l[userID] ~ dnorm(lmu,lsigma),
    a[userID] ~ dnorm(amu, asigma),
    c[userID] ~ dnorm(cmu, csigma)
  ), data=dat)
```
\normalsize

A relatively large number of zeros  suggests that  moving to a zero-inflated Poisson distribution would be a good idea. It was not, so the following model structure was tested and abandoned:
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{ZiPoisson}(p, \lambda_i)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    logit(p) & = \pi\\
    \pi & \sim Norm(-1.5,1) 
\end{align*}

\footnotesize
```{r AR1CZiTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
AR1Czi <-  quap(
  alist(
    attacks ~ dzipois(p, lambda),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act,
    l[userID] ~ dnorm(lmu,lsigma),
    a[userID] ~ dnorm(amu, asigma),
    c[userID] ~ dnorm(cmu, csigma),
    logit(p) <- pp,
    pp ~ dnorm(-1.5,1)
  ), data=dat)
```
\normalsize

Then we considered the negative binomial distribution, and the addition of week days as a predictor (both with general and user-level coefficients). While moving to the negative binomial distribution resulted in an improvement, adding week days did not improve the model performance, perhaps because we already conditioned on activity, and whatever the impact of weekdays was, has been already  mediated through activity (in a sense, we committed a post-treatment bias with respect to weekdays; but that's fine, we did not really care about the impact of weekdays).
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    \phi& \sim Exp(1)\\
\end{align*}
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} + w * \mathsf{weekday}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    w & \sim \textsf{Norm}(0,.1) \\
    \phi & \sim Exp(1)\\
\end{align*}
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} + w_{\mathsf{userID[i]}} * \mathsf{weekday}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    w_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1) \\
    \phi & \sim Exp(1)\\
\end{align*}

\footnotesize
```{r AR1CnBinomTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
AR1CnBinomUlam <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)

AR1CnBinomUlamW <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act + w * weekday,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    w ~ dnorm(0,.1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)

AR1CnBinomUlamWu <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act +
      w[userID] * weekday,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    w[userID] ~ dnorm(0,.1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)
```
\normalsize

We also considered adding overall aggression in before period as a predictor, but the addition did not lead to improvement. One reason this is interesting is that interaction of interventions with overall aggression will  turn out to be important for long-term effects.
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} + act + ab_{\mathsf{userID[i]}} * \textsf{ABS}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    ab_{\mathsf{userID[i]}} &   \sim  \textsf{Norm}(0,.1) \\
    \phi & \sim Exp(1)\\
\end{align*}

\footnotesize
```{r AR1CnBinomTSmodelsAB,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
AR1nBinomAB <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act +
      abs[userID] * abs,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    abs[userID] ~ dnorm(0, .1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)
```
\normalsize

\noindent So, ultimately, the negative binomial model without week days or aggression before became our null model to which we considered adding intervention count and intervention types as predictors. For now, consider intervention type and interventions received with lag 1 (note that if, for instance, we are interested in the impact of interventions lag 2, we cannot condition on interventions lag 1, as this would lead to post-treatment bias). So what we will say about lag 1 will be exactly mirrored in the models for other lag values.

Adding intervention count, and adding intervention count with distinguishing intervention types resulted in improvements.
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} +
      i1 * \mathsf{intL1D}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    i1 & \sim  \textsf{Norm}(0,.1) \\
    \phi & \sim Exp(1)\\
\end{align*}
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi)\\ 
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} +
      i1_{\mathsf{type[i]}} * \mathsf{intL1D}\\ 
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    i1_{\mathsf{type[i]}} & \sim  \textsf{Norm}(0,.1) \\
    \phi & \sim Exp(1)\\
\end{align*}

\footnotesize
```{r D1TSmodels1,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
daysL1notype <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act + 
        i1 * intL1D,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    i1 ~ dnorm(0, .1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)

daysL1 <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act +
        i1[type] * intL1D,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    i1[type] ~ dnorm(0, .1),
    phi ~ dexp(1)
  ), data=dat, log_lik = TRUE)
```
\normalsize

Taking  $\phi$ parameters to be  user-relative also resulted in improvement:
\begin{align*}
\mathsf{attacks}_i & \sim  \textsf{NegativeBinomial}(\lambda_i, \phi_{\mathsf{userID[i]}} )\\
    log(\lambda_i)  & =  l_{\mathsf{userID[i]}} + a_{\mathsf{userID[i]}} * \mathsf{attacksL1} + c_{\mathsf{userID[i]}} * \mathsf{act} + i1 * \mathsf{intL1D}\\
    l_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(.05,2.3)\\
    a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(0,.1)\\
    c_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(0,.1) \\
    i1_{\mathsf{type[i]}} & \sim  \textsf{Norm}(0,.1) \\
    \phi_{\mathsf{userID[i]}}  & \sim Exp(1)\\
\end{align*}

\footnotesize
```{r D1TSmodels2,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
daysL1phiuser <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act +
        i1[type] * intL1D,
    l[userID] ~ dnorm(.05,2.3),
    a[userID] ~ dnorm(0, .1),
    c[userID] ~ dnorm(0, .1),
    i1[type] ~ dnorm(0, .1),
    phi <- puser[userID],
    puser[userID] ~ dexp(1)
  ), data=dat, log_lik = TRUE)
```
\normalsize

Finally, we made a crucial move to deploy hierarchical modeling. The general idea is that while we do keep user-specific coefficients wherever we had them, we also do not assume that they are independent, but rather that they come from their respective distributions, and we estimate the general features of those distributions at the same time. Also, for convenience this time we used treatment type indicator variables.

\begin{align*}
\mathsf{attacks}_i & \sim  \mathsf{NegativeBinomial}(\lambda_i, \phi_{\mathsf{userID[i]}} ) \\
log(\lambda_i) & =  l_{\mathsf{userID[i]}} +
                  a_{\mathsf{userID[i]}} * \mathsf{attacksL1} +
                  c_{\mathsf{userID[i]}} * \mathsf{act} + \\
                  & + 
      i1control_{\mathsf{userID[i]}} *  \mathsf{control} * \mathsf{intL1D}  + \\&         +  i1emp_{\mathsf{userID[i]}} *  \mathsf{emp} * \mathsf{intL1D}  + \\
      & +  i1norm_{\mathsf{userID[i]}} *  \mathsf{norm} * \mathsf{intL1D}
                   \\ 
  l_{\mathsf{userID[i]}} &  \sim \textsf{Norm}(\bar{l}, \bar{\sigma_l}) \\
  a_{\mathsf{userID[i]}} & \sim \textsf{Norm}(\bar{a}, \bar{\sigma_a}) \\
  c_{\mathsf{userID[i]}} & \sim \textsf{Norm}(\bar{c}, \bar{\sigma_c}) \\
  i1control_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(i1controlOverall,\bar{\sigma_{i1}}) \\
   i1emp_{\mathsf{userID[i]}} & \sim  \textsf{Norm}(i1empOverall, \bar{\sigma_{i1}})\\  
  i1norm_{\mathsf{userID[i]}}  & \sim  
    \textsf{Norm}(i1normOverall, \bar{\sigma_{i1}})\\
     i1controlOverall & \sim  \textsf{Norm}(0,.2)\\
    i1empOverall  & \sim  \textsf{Norm}(0,.2) \\
    i1normOverall  & \sim  \textsf{Norm}(0,.2) \\
    \bar{\lambda}  & \sim  \textsf{Norm}(.00001, 2.5) \\
    \bar{\sigma_l} & \sim  \mathsf{Exp}(1.5)\\
    \bar{a} & \sim \textsf{Norm}(0, .2) \\
    \bar{\sigma_a} & \sim  \mathsf{Exp}(5) \\
    \bar{c} & \sim  \mathsf{Norm}(0, .2)\\
    \bar{\sigma_c} & \sim \mathsf{Exp}(5) \\
    \bar{\sigma_{i1}} & \sim  \mathsf{Exp}(5)
\end{align*}

\footnotesize
```{r D1TSmodelFinal,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
d1full <-  ulam(
  alist(
    attacks ~ dgampois( lambda, phi),
    log(lambda) <- l[userID] + a[userID] * attacksL1 + c[userID] * act + 
      i1control[userID] *  control * intL1D  +
      i1emp[userID] *  emp * intL1D  +
      i1norm[userID] *  norm * intL1D,
    l[userID] ~ dnorm(lbar, lsigmabar),
    a[userID] ~ dnorm(abar, asigmabar),
    c[userID] ~ dnorm(cbar, csigmabar),
    i1control[userID] ~  dnorm(i1controlOverall, i1sigmabar),
    i1emp[userID] ~  dnorm(i1empOverall, i1sigmabar),
    i1norm[userID] ~  dnorm(i1normOverall, i1sigmabar),
    i1controlOverall ~ dnorm(0,.2),
    i1empOverall ~ dnorm(0,.2),
    i1normOverall ~ dnorm(0,.2),
    phi <- puser[userID],
    puser[userID] ~ dexp(pbar),
    lbar ~ dnorm(.00001, 2.5),
    lsigmabar ~ dexp(1.5),
    abar ~ dnorm(0, .2),
    asigmabar ~ dexp(5),
    cbar ~ dnorm(0, .2),
    csigmabar ~ dexp(5),
    i1sigmabar ~ dexp(5),
    pbar ~ dexp(5)   
  ), data=dat, log_lik = TRUE,
  chains = 2, iter = 8000,
  control = list(adapt_delta = 0.9), cores = 8)
```
\normalsize

This might seem somewhat confusing, so let us disentangle this maze:

\begin{itemize}
\item Each user has their own baseline aggression level, $l_{\mathsf{userID[i]}}$. \item However, these individual aggression levels are not disconnected, they come from a distribution themselves, $\textsf{Norm}(\bar{l}, \bar{\sigma_l})$. $\bar{l}$ is the mean baseline aggression level for the whole population, and $\bar{\sigma_l}$ is the standard deviation of this distribution. These general parameters are to be estimated along with the individual ones.
\item Then  there are individual auto regression coefficients     $a_{\mathsf{userID[i]}}$, which capture the correlation between  yesterday's attacks with today's attacks, so to speak. These also come from a general distribution $\textsf{Norm}(\bar{a}, \bar{\sigma_a})$, with its own general parameters to be estimated.
\item Next, there are individual user's coefficients connecting the user's activity on a given day with their aggression on the same day,  $c_{\mathsf{userID[i]}}$, all coming from a general distribution $\textsf{Norm}(\bar{c}, \bar{\sigma_c})$ whose parameters are also to be estimated.
\item For any particular treatment group, say, empathy, we have a user level coefficient $i1emp_{\mathsf{userID[i]}}$, which is activated if the user is in the empathy group (that is, we multiply by the indicator variable $\mathsf{emp}$) and then applied to the number of interventions received the day before (lag 1). Similarly for the two other groups. These user-level parameters come from the distribution $\textsf{Norm}(i1empOverall, \bar{\sigma_{i1}})$, whose parameters are to be estimated.
\item Finally, prior predictive check was used to choose priors for the general coefficients. 
\end{itemize}
As already mentioned, the coefficients need to be exponentiated to be understood multiplicatively.  For instance, the prior for $i1empOverall$ is $\textsf{Norm}(0,.2)$. To understand what priors for the exponentiated individual coefficients this entails, we can simulate: (1) draw 1e4 values $i1bar$ of the mean from  $\textsf{Norm}(0,.2)$,  (2) draw 1e4 values $i1sigmabar$  of the standard deviation parameter from $\mathsf{Exp(5)}$, and each time (3) draw 1e4 parameters from $\mathsf{Norm}(i1bar,i1sigmabar)$. The resulting distribution looks as in Figure \ref{fig:priori1plot}. This is still a very wide prior for the multiplicative impact of emphatetic interventions, centered around 1, allowing even extremely unlikely values close to 0 or 2 (upon reflection: you really should not expect a single intervention to reduce aggression to zero or to double it in everyone). In the cumulative model for computation reasons we will need to narrow down the distributions, but the general point hold: prior predictive check still ensures that they are centered around neutral values and that they allow for a very reasonable range of values.

\footnotesize
```{r priori1,echo=TRUE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
set.seed(45)
i1bar <- rnorm(1e5,  0, .2)
i1sigmabar <- rexp(1e5, 5)
i1 <- rnorm(1e5, i1bar, i1sigmabar)
priorPlot2e <- ggplot()+geom_histogram(aes(x=exp(i1)), bins = 60)+xlim(0,2)+
  theme_tufte()

i3bar <- rnorm(1e5,  0, .1)
i3sigmabar <- rexp(1e5, 5)
i3 <- rnorm(1e5, i3bar, i3sigmabar)
priorPlot3e <- ggplot()+geom_histogram(aes(x=exp(i3)), bins = 60)+xlim(0,2)+
  theme_tufte()

```
\normalsize

\begin{figure}
```{r priori1plot,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
grid.arrange(priorPlot2e, priorPlot3e)
```
\caption{Simulated priors for the individual i1 coefficients, and prior for the cumulative impact model with larger input variability (hence, the prior is more narrow to eliminate unrealistically huge impact).}
\label{fig:priori1plot}
\end{figure}

For the impact of the cumulative number of interventions (we will only use lag 3 for reasons that will become clear), since the range of values of the predictor is wider, for computational feasibility we further needed to restrict coefficients to lie between -3 and 2, but these values are not plausible values of the parameters anyway ($exp(-3) \approx 0.04$ and $exp(2) \approx 7.38$). The model for the cumulative impact was tested with and without interaction with overall aggression in the before period, without the use of attacks on a given day (as already explained, to avoid the post-treatment bias). The two relevant lines in the models are:

\begin{align*}
log(\lambda_i) & =  l_{\mathsf{userID[i]}}  + c_{\mathsf{userID[i]}} \times \mathsf{act} + 
      ic3control_{\mathsf{userID[i]}} \times  \mathsf{control} \times \mathsf{intCL3D}  + \\ & + 
      ic3emp_{\mathsf{userID[i]}} \times  \mathsf{emp} \times \mathsf{intCL3D}  + \\ & 
      ic3norm_{\mathsf{userID[i]}} \times  \mathsf{norm} \times \mathsf{intCL3D}\\
log(\lambda_i) & =  l_{\mathsf{userID[i]}}  + c_{\mathsf{userID[i]}} \times  act + \\ & + 
      ic3control_{\mathsf{userID[i]}} \times   \mathsf{control} \times  \mathsf{intCL3D}  + \\ & + icabst3control_{\mathsf{userID[i]}} \times   \mathsf{control} \times  \mathsf{intCL3D} \times  \mathsf{abst} + \\ & 
      ic3emp_{\mathsf{userID[i]}} \times   \mathsf{emp} \times  \mathsf{intCL3D}  + \\ & + icabst3emp_{\mathsf{userID[i]}} \times   \mathsf{emp} \times  \mathsf{intCL3D}  \times  \mathsf{abst} + \\ & +
      ic3norm_{\mathsf{userID[i]}}] \times   \mathsf{norm} \times  \mathsf{intCL3D} + \\ & + icabst3norm_{\mathsf{userID[i]}} \times   \mathsf{norm} \times  \mathsf{intCL3D} \times  \mathsf{abst} 
\end{align*}

The models employing the second formula were superior in performance. It is not surprising that once attacks on a given day were removed from predictor, the overall aggression levels in the before period became predictive. The price to pay, however, is that now to obtain a user-specific multiplicative interpretation of the impact of cumulative interventions, we need to put the two elements together while multiplying one by the user's overall aggression and only then exponentiate, that is we need to inspect, for instance, $exp(ic3emp_{\mathsf{userID[i]}}  +  icabst3emp_{\mathsf{userID[i]}} \times \mathsf{abst}[i])$,
instead of simply looking at $exp(ic3emp_{\mathsf{userID[i]}})$.

\footnotesize
```{r rstanCumupative,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
#RStan model code for cumulative interventions lag 3
data{
  int<lower=0> N;
  int<lower=0> U;
  vector[N] abst;
  int interventions[N];
  int type[N];
  int intCL1D[N];
  int intCL2D[N];
  int intCL3D[N];
  int intCL4D[N];
  int intCL5D[N];
  int intCL6D[N];
  int intCL7D[N];
  int intL1D[N];
  int intL2D[N];
  int intL3D[N];
  int intL4D[N];
  int intL5D[N];
  int intL6D[N];
  int intL7D[N];
  int attacksL1[N];
  int attacksL2[N];
  int attacksL3[N];
  int attacksL4[N];
  int attacksL5[N];
  int attacksL6[N];
  int attacksL7[N];
  int weekday[N];
  int attacks[N];
  int norm[N];
  int emp[N];
  int control[N];
  int act[N];
  int userID[N];
}
parameters{
  vector<lower = -80>[U] l;
  vector<lower=-3,upper=2>[U] c;
  vector<lower=-3,upper=2>[U] ic3control;
  vector<lower=-3,upper=2>[U] icabst3control;
  vector<lower=-3,upper=2>[U] ic3emp;
  vector<lower=-3,upper=2>[U] icabst3emp;
  vector<lower=-3,upper=2>[U] ic3norm;
  vector<lower=-3,upper=2>[U] icabst3norm;
  real<lower=-3,upper=2> ic3controlOverall;
  real<lower=-3,upper=2> ic3empOverall;
  real<lower=-3,upper=2> ic3normOverall;
  real<lower=-3,upper=2> icabst3controlOverall;
  real<lower=-3,upper=2> icabst3empOverall;
  real<lower=-3,upper=2> icabst3normOverall;
  vector<lower=0>[U] puser;
  real<lower = -3, upper = 2> lbar;
  real<lower=0> lsigmabar;
  real<lower = -3, upper = 2> cbar;
  real<lower=0> csigmabar;
  real<lower=0> ic3sigmabar;
  real<lower=0> icabst3sigmabar;
  real<lower=0> pbar;
}
model{
  vector[N] lambda;
  vector[N] phi;
  pbar ~ exponential( 5 );
  icabst3sigmabar ~ exponential( 25 );
  ic3sigmabar ~ exponential( 25 );
  csigmabar ~ exponential( 5 );
  cbar ~ normal( 0.1 , 0.1 );
  lsigmabar ~ exponential( 0.5 );
  lbar ~ normal( 0 , 0.5 );
  puser ~ exponential( pbar );
  for ( i in 1:N ) {
    phi[i] = puser[userID[i]];
  }
  icabst3normOverall ~ normal( 0 , 0.1 );
  icabst3empOverall ~ normal( 0 , 0.1 );
  icabst3controlOverall ~ normal( 0 , 0.1 );
  ic3normOverall ~ normal( 0 , 0.1 );
  ic3empOverall ~ normal( 0 , 0.1 );
  ic3controlOverall ~ normal( 0 , 0.1 );
  icabst3norm ~ normal( icabst3normOverall , icabst3sigmabar );
  ic3norm ~ normal( ic3normOverall , ic3sigmabar );
  icabst3emp ~ normal( icabst3empOverall , icabst3sigmabar );
  ic3emp ~ normal( ic3empOverall , ic3sigmabar );
  icabst3control ~ normal( icabst3controlOverall , icabst3sigmabar );
  ic3control ~ normal( ic3controlOverall , ic3sigmabar );
  c ~ normal( cbar , csigmabar );
  l ~ normal( lbar , lsigmabar );
  for ( i in 1:N ) {
    lambda[i] = l[userID[i]] + c[userID[i]] * act[i] +
      ic3control[userID[i]] * control[i] * intCL3D[i] +
      icabst3control[userID[i]] * control[i] * intCL3D[i] * abst[i] +
      ic3emp[userID[i]] * emp[i] * intCL3D[i] + 
      icabst3emp[userID[i]] * emp[i] * intCL3D[i] * abst[i] +
      ic3norm[userID[i]] * norm[i] * intCL3D[i] + 
      icabst3norm[userID[i]] * norm[i] * intCL3D[i] * abst[i];
    lambda[i] = exp(lambda[i]);
  }
  attacks ~ neg_binomial_2( lambda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lambda;
  vector[N] phi;
  for ( i in 1:N ) {
    phi[i] = puser[userID[i]];
  }
  for ( i in 1:N ) {
    lambda[i] = l[userID[i]] + c[userID[i]] * act[i] + 
      ic3control[userID[i]] * control[i] * intCL3D[i] + 
      icabst3control[userID[i]] * control[i] * intCL3D[i] * abst[i] +
      ic3emp[userID[i]] * emp[i] * intCL3D[i] + 
      icabst3emp[userID[i]] * emp[i] * intCL3D[i] * abst[i] + 
      ic3norm[userID[i]] * norm[i] * intCL3D[i] +
      icabst3norm[userID[i]] * norm[i] * intCL3D[i] * abst[i];
    lambda[i] = exp(lambda[i]);
  }
  for ( i in 1:N ) log_lik[i] = neg_binomial_2_lpmf( attacks[i] | lambda[i] , phi[i] );
}
```
\normalsize

Finally, in the before-and-after analysis, we put aside the time series element, look at aggregated counts before and after the treatment period, thus obtaining a more of a long-term effect analysis. Moreover, this time we standardize counts, obtaining continuous variables and employing normal distribution in the likelihoods, thus also making sure the overall results are robust under a spectrum of modeling choices.  We build and compared  multiple additive models where the outcome variable is normally distributed around the predicted mean, which is a linear function of predictors (possibly with  interactions). Bayesian information criteria  (WAIC)  applied to a wide selection of predictors lead to the model, whose specification is as follows (we also selected regularizing prior parameters using prior predictive checks to avoid unreasonably narrow overall prior distributions):

\vspace{-8mm}

\begin{align*}
\mathsf{AdiffS} & \sim \textsf{Norm}(\mu, \sigma)\\
\mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +
 \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
 & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS}\\
 \alpha & \sim \textsf{Norm}(0,.3)\\
\beta_{\mathsf{ADS}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
\beta_{\mathsf{group}_i} & \sim \textsf{Norm}(0,.3)\\
\beta_{\mathsf{IC}}[\mathsf{group}_i] & \sim \textsf{Norm}(0,.3)\\
 \beta_{\mathsf{ADSIC}} & \sim \textsf{Norm}(0,.3)\\
 \beta_{\mathsf{CBS}}[\mathsf{group}_i]& \sim \textsf{Norm}(0,.3)\\
\end{align*}

\vspace{-9mm}

That is, we take the resulting mean to be the result of the general average ($\alpha$) and the impact of the following coefficients: group-specific coefficient for \textsf{ADS}, group coefficient, group-specific coefficient for \textsf{IC}, interaction coefficient for \textsf{ADS} and \textsf{IC}, and group-specific coefficient for \textsf{CBS}. This is plausible \emph{prima facie}, as which group a user belongs to might have impact on  how the number of attacks during the treatment are related to  the number of attacks after, the role  of the intervention count, and the role of comments before. Moreover, the levels of aggressive behavior displayed by the user during treatment might have impact on the role played by the intervention count.

Now, let's build two models with this general structure, one with fairly wide priors that one might initially think are appropriate, one with regularizing priors. The key phenomenon to watch out for in such contexts (slightly complex models with interactions) is that it is hard to intuitively predict the impact of coefficient priors on prior predictions. For this reason, we run prior predictive checks for both models.

\footnotesize 
```{r priorModels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
# building model with sd=1
InteractionsModelDiffSD1 <- ulam(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC+
    bADSIC * ADS * IC+ bCBS[groupID] *CBS,
    a ~ dnorm (0,1),
    bADS[groupID] ~ dnorm(0,1),
    bADSIC ~ dnorm(0,1),
    bCBS[groupID] ~ dnorm(0,1),
    bIT[groupID] ~ dnorm(0,1),
    bIC[groupID] ~ dnorm(0,1),
    sigma  ~ dexp(1)
  ),
  data = summaries
 )

#now model with prior sd = .3
InteractionsModelDiff <- ulam(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
    bADSIC * ADS * IC+ bCBS[groupID] *CBS,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bCBS[groupID] ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)
```

\vspace{1mm}
\footnotesize
```{r priorModels2,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
InteractionsModelDiffSD1 <- readRDS(file = "models/InteractionsModelDiffSD1.rds")
InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")

#prior predictive checks sd =1
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "datasets/prior1.RDS")
prior <- readRDS(file = "datasets/prior1.RDS")
mu <- link( InteractionsModelDiffSD1 , post=prior , data=data )
colnames(mu) <- levels(summaries$group)
muLong <- melt(mu)
colnames(muLong) <- c("id", "group", "AdiffS")

priorGroupsSD1 <- ggplot(muLong)+
  geom_violin(aes(x = group, color = group, y = AdiffS))+
  theme_tufte()+xlab("")+
  labs(title = "Simulated priors by group",
  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = 1)")+
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
  guides(color = "none")+
  ylab("change in attacks (standardized)")+theme(plot.title.position = "plot")

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "datasets/prior2.RDS")
prior <- readRDS(file = "datasets/prior2.RDS")
mu <- link(InteractionsModelDiffSD1 , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

priorICSD1  <- ggplot(priorDF, aes(x = IC, y  = mu.mean,  fill = group))+
  geom_line()+geom_ribbon(aes(ymin = X.0.89, ymax = X0.89.), alpha = 0.2)+
  theme_tufte()+ylab("change in attacks (standardized)")+
  labs(title = "Simulated priors for AAS vs IC",
      subtitle = "(at ADS = CBS = 0, sd = 1)")+xlab("interventions")+
  scale_fill_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
  theme(plot.title.position = "plot")

priorJoint1 <- ggarrange(priorGroupsSD1,priorICSD1, ncol = 2)
priorJoint1Titled <- annotate_figure(priorJoint1,
  top = text_grob("Predictive priors with sd=1 are insanely wide",
                  size = 14))

#Some experimentation leads to the value of $\sigma =.3$, which leads to the following priors:
#prior predictive check sd =.3
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "datasets/prior3.RDS")
prior <- readRDS(file = "datasets/prior3.RDS")

mu <- link(InteractionsModelDiff , post=prior , data=data ) 
colnames(mu) <- levels(summaries$group)
muLong <- melt(mu)
colnames(muLong) <- c("id", "group", "AdiffS")

priorGroupSD03 <- ggplot(muLong)+
  geom_violin(aes(x = group, color = group, y = AdiffS))+theme_tufte()+
  xlab("")+
  labs(title = "Simulated priors  by group", 
  subtitle = "(at ADS = CBS = 0, IC at mean = 5, sd = .3)")+
  ylab("change in attacks (standarized)")+
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
  guides(color = "none")+
  theme(plot.title.position = "plot")

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "datasets/prior4.RDS")
prior <- readRDS(file = "datasets/prior4.RDS")
mu <- link(InteractionsModelDiff , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

priorICSD03  <- ggplot(priorDF, aes(x = IC, y  = mu.mean,  fill = group))+
  geom_line()+geom_ribbon(aes(ymin = X.0.89, ymax = X0.89.), alpha = 0.2)+
  theme_tufte()+ylab("change in attacks (standardized)")+
  scale_fill_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
  labs(title = "Simulated priors for AAS vs IC",
      subtitle = "(at ADS = CBS = 0, sd = .3)")+xlab("interventions")

priorJoint03 <- ggarrange(priorGroupSD03,priorICSD03, ncol = 2) 
priorJoint03Titled <- annotate_figure(priorJoint03, 
  top = text_grob("Predictive priors with sd=.3 seem sensible",
                  size = 14))
#priorJoint03Titled
```
\normalsize

\begin{figure}[H]
```{r fig:priorCheck,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "80%",   message = FALSE, warning = FALSE, results = FALSE}
priorJoint1Titled
priorJoint03Titled
```

\caption{Prior predictive check for two different sets of priors.}
\label{fig:priors}
\end{figure}

Now,  let's double-check if our model building tools behave appropriately for models of this sort on the data that we have---some model diagnostics before we move on (Figure \ref{fig:traceplot}). What we are witnessing is (1) stationarity (the chains stay mostly in the most probable regions), (2) good mixing (they explore a range of options in the beginning), and (3) convergence (they stabilize as they progress).  We also need to   inspect the distribution of residuals, expecting them to be more or less normally distributed, which they are (Figure \ref{fig:residuals}).

\begin{figure}
```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%", results = "hide"}
InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
traceplot( InteractionsModelDiff )
```
\caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.}
\label{fig:traceplot}
\end{figure}

\begin{figure}[H]
```{r residualsPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "60%", results = "hide"}
mu <- link(InteractionsModelDiff)
mu_mean <- apply( mu , 2 , mean )
mu_resid <- summaries$AdiffS - mu_mean
ggplot()+geom_density(aes(x = mu_resid))+theme_tufte()+ theme(plot.title.position = "plot", plot.title = element_text(size=15)) +
  ggtitle("Residuals are approximately normally distributed")+xlab("residuals")
```
\caption{Distribution of residuals from the selected model.}
\label{fig:residuals}
\end{figure}

Now, let us elaborate on how  we decided to use  to this seemingly fairly complicated model. Once preliminary causal considerations guided our restrictions on variable selection, we proceed by building models of increasing complexity, and comparing them in terms of Widely Acceptable Information Criterion (which we have already discussed). The models differ mostly in the underlying linear formulae. For computational ease we will here use quadratic approximations, while in the final analysis we will deploy Hamiltionian Monte Carlo. The names are meant to decode the model structure: the predictors are listed before dashes, whereas interactions are listed after dashes. The comparison results are in Table \ref{tab:comparison} and plotted in Figure \ref{fig:modelComparisonPlot}. Notice that there are ways of building a complicated models that do not result in improvement, as they rather lead to expected performance lower than that of the null model.

\begin{align}
\tag{Null}  \mu_i & = \alpha\\
\tag{ADS}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS}\\
\tag{ADSIC}  \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
\tag{IT}  \mu_i & = \beta_{\mathsf{group}[i]} \\
\tag{ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]}\\
\tag{ADSITIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC}\\
\tag{ADSITIC-ADSIC} \mu_i & = \alpha + \beta_{\mathsf{ADS}}\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +    \beta_{\mathsf{IC}}\times \mathsf{IC} + \\ & + \nonumber \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
\tag{ADSITIC-ADSIC-ADSIT} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} +  \beta_{\mathsf{group}[i]} +  \\ \nonumber & +  \beta_{\mathsf{IC}}\times \mathsf{IC} + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
\tag{ADSIT-ADSIT}   \mu_i &  = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
 \mathsf{ADS} + \beta_{\mathsf{group}[i]} \\
\tag{ADSITIC-ADSIT-ITIC-ADSIC}   \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times \mathsf{ADS} + \beta_{\mathsf{group}[i]} +  \\ & + 
\beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}   \nonumber  + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}\\
\tag{ADSITICCBS-ITIC-ADSIC} \mu_i &  = \alpha  +  \beta_{\mathsf{ADS}}[\mathsf{group}_i] \times
 \mathsf{ADS}  + \beta_{\mathsf{group}[i]} + \\ & +    \beta_{\mathsf{IC}}[\mathsf{group}_i] \times \mathsf{IC}  \nonumber  + \beta_{\mathsf{CBS}} \times \mathsf{CBS} +  \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC}  \\
\tag{Final} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
 & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} \nonumber\\
 \tag{tooFar} \mu_i & = \alpha + \beta_{\mathsf{ADS}}[\mathsf{group}_i]\times \mathsf{ADS} + \beta_{\mathsf{group}_i}  +  \beta_{\mathsf{IC}}[\mathsf{group}_i]\times \mathsf{IC} + \\
 & + \beta_{\mathsf{ADSIC}}\times \mathsf{ADS} \times \mathsf{IC} + \beta_{\mathsf{CBS}}[\mathsf{group}_i] \times \mathsf{CBS} + \beta_{\mathsf{CBSIC}}\times
 \mathsf{CBS} \times \mathsf{IC} \nonumber \end{align}

\vspace{1mm}
\footnotesize
```{r modelSelection1,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
null <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu ~ dnorm (0,0.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADS <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <-  a + bADS * ADS,
    a ~ dnorm (0,0.3),
    bADS ~ dnorm(0,0.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSIC <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <-  a + bADS * ADS+ bIC * IC,
    a ~ dnorm (0,0.3),
    bADS ~ dnorm(0,0.3),
    bIC ~ dnorm(0,0.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

IT <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <-  bIT[groupID] ,
    bIT[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSIT <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS * ADS +  bIT[groupID],
    a ~ dnorm (0,0.3),
    bADS ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSITIC <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC,
    a ~ dnorm (0,0.3),
    bADS ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSITIC_ADSIC <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC,
    a ~ dnorm (0,0.3),
    bADS ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSITIC_ADSIC_ADSIT <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC * IC + bADSIC * ADS * IC,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSIT_ADSIT <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] ,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    #bADSIC ~ dnorm(0,.5),
    bIT[groupID] ~ dnorm(0,.3),
    #bIC ~ dnorm(0,.5),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSITIC_ADSIT_ITIC_ADSIC <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
      bADSIC * ADS * IC,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

ADSITICCBS_ITIC_ADSIC <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
      bADSIC * ADS * IC+ bCBS *CBS,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bCBS ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

Final <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
      bADSIC * ADS * IC+ bCBS[groupID] *CBS,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bCBS[groupID] ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

tooFar <- quap(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] + bIC[groupID] * IC +
      bADSIC * ADS * IC+ bCBS[groupID] *CBS + bCBSIC * CBS * IC,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bCBS[groupID] ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
     bCBSIC ~ dnorm(0, .3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)

```
\normalsize

\vspace{1mm}
\footnotesize
```{r buildComparisons,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
comparison<- compare(null,ADS,ADSIC,IT,ADSIT,ADSITIC,ADSITIC_ADSIC,
                     ADSITIC_ADSIC_ADSIT,ADSIT_ADSIT,ADSITIC_ADSIT_ITIC_ADSIC,
                     ADSITICCBS_ITIC_ADSIC,Final, tooFar)
```

<!-- ```{r comparisonsTable,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"} -->
<!-- kable(round(data.frame(comparison ),3), "latex", booktabs = T,linesep = "") %>% kable_styling(latex_options = "striped",font_size = 9)   -->
<!-- ``` -->

\begin{table}
\centering\begingroup\fontsize{9}{11}\selectfont
\begin{tabular}{lrrrrrr}
\toprule
  & WAIC & SE & dWAIC & dSE & pWAIC & weight\\
\midrule
\cellcolor{gray!6}{Final} & \cellcolor{gray!6}{1184.829} & \cellcolor{gray!6}{89.779} & \cellcolor{gray!6}{0.000} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{26.871} & \cellcolor{gray!6}{0.590}\\
tooFar & 1186.126 & 89.413 & 1.297 & 2.758 & 28.181 & 0.308\\
\cellcolor{gray!6}{ADSITICCBS\_ITIC\_ADSIC} & \cellcolor{gray!6}{1188.337} & \cellcolor{gray!6}{87.058} & \cellcolor{gray!6}{3.508} & \cellcolor{gray!6}{6.184} & \cellcolor{gray!6}{24.822} & \cellcolor{gray!6}{0.102}\\
IT & 1345.087 & 144.443 & 160.259 & 132.802 & 18.104 & 0.000\\
\cellcolor{gray!6}{null} & \cellcolor{gray!6}{1345.550} & \cellcolor{gray!6}{145.960} & \cellcolor{gray!6}{160.721} & \cellcolor{gray!6}{134.243} & \cellcolor{gray!6}{18.616} & \cellcolor{gray!6}{0.000}\\
ADS & 1348.696 & 143.821 & 163.867 & 132.558 & 22.718 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIC} & \cellcolor{gray!6}{1351.556} & \cellcolor{gray!6}{152.861} & \cellcolor{gray!6}{166.728} & \cellcolor{gray!6}{139.154} & \cellcolor{gray!6}{29.070} & \cellcolor{gray!6}{0.000}\\
ADSIT & 1351.646 & 145.161 & 166.817 & 133.795 & 25.032 & 0.000\\
\cellcolor{gray!6}{ADSITIC} & \cellcolor{gray!6}{1352.087} & \cellcolor{gray!6}{146.835} & \cellcolor{gray!6}{167.258} & \cellcolor{gray!6}{134.608} & \cellcolor{gray!6}{27.254} & \cellcolor{gray!6}{0.000}\\
ADSIT\_ADSIT & 1352.672 & 155.862 & 167.844 & 142.092 & 31.855 & 0.000\\
\cellcolor{gray!6}{ADSIC} & \cellcolor{gray!6}{1352.892} & \cellcolor{gray!6}{146.359} & \cellcolor{gray!6}{168.064} & \cellcolor{gray!6}{134.313} & \cellcolor{gray!6}{26.421} & \cellcolor{gray!6}{0.000}\\
ADSITIC\_ADSIC\_ADSIT & 1355.482 & 155.522 & 170.653 & 141.405 & 33.558 & 0.000\\
\cellcolor{gray!6}{ADSITIC\_ADSIT\_ITIC\_ADSIC} & \cellcolor{gray!6}{1355.783} & \cellcolor{gray!6}{155.273} & \cellcolor{gray!6}{170.954} & \cellcolor{gray!6}{141.128} & \cellcolor{gray!6}{33.771} & \cellcolor{gray!6}{0.000}\\
\bottomrule
\end{tabular}
\endgroup{}
\caption{Model comparison results.}
\label{tab:comparison}
\end{table}

\begin{figure}[H]
```{r fig:modelComparison,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
plot(comparison)
```
\caption{Model comparison, WAIC scores. The filled points are the in-sample deviance values. The open points are the WAIC values. The line segments represent standard errors of the WAIC scores. really want however is the standard error of the difference in WAIC
between the two models. The triangle is the difference to the top rated model, and the line segment going through it is the standard error of this difference.}
\label{fig:modelComparisonPlot}
\end{figure}

\normalsize 
  The three models that stand out  differ in including $\mathsf{CBS}$ as a predictor.  Moreover the final model includes an interaction between  treatment group and $\mathsf{CBS}$. Adding a further interaction between $\mathsf{CBS}$ and $\mathsf{IC}$ takes us too far. We will employ the top model ($\mathsf{Final}$) in   further analyses.

Now that we have explained how and why our models were built and selected, we move on to the presentation of the results.

# Results

## Interventions on a given day

We build seven separate models for the impact of interventions $k$ days ago, $1\leq k \leq 7$. In Figure \ref{fig:dailyResults} we visualize the results for the three groups, with  jitter based on user aggression in the before period.

\footnotesize
```{r dailyResults,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}

hateDFs <- readRDS(file ="datasets/hateDFs2.RDS")
sampleDFs <- hateDFs

d1precis <- readRDS("timeSeriesDFs/d1precis.rds")
d2precis <- readRDS("timeSeriesDFs/d2precis.rds")
d3precis <- readRDS("timeSeriesDFs/d3precis.rds")
d4precis <- readRDS("timeSeriesDFs/d4precis.rds")
d5precis <- readRDS("timeSeriesDFs/d5precis.rds")
d6precis <- readRDS("timeSeriesDFs/d6precis.rds")
d7precis <- readRDS("timeSeriesDFs/d7precis.rds")

n <- length(hateDFs)
df <- list()
dfCleanList <- list()

dfextract <- function(precis, day){
  df[[day]] <- precis
  df[[day]] <- df[[day]][grep(paste("^i",day, sep = ""), rownames(df[[day]])),]
  df[[day]] <- df[[day]][- grep(paste("i",day,"sigmabar", sep = ""),
                                rownames(df[[day]])),]
  df[[day]]$day <- rep(day, nrow(df[[day]]))
  df[[day]]$expMean <- exp(df[[day]]$mean)
  df[[day]]$expLow <- exp(df[[day]]$`5.5%`)
  df[[day]]$expHigh <- exp(df[[day]]$`94.5%`)
  df[[day]]$expHigh <- ifelse( df[[day]]$expHigh <2, df[[day]]$expHigh, 2)

  df[[day]]$type <- as.factor(c(rep("control", n), rep("empathy", n),
                    rep("normative", n), c("control", "empathy", "normative")))
  abs <- numeric(3 * n +3)
  for(i in 1:n){
    abs[i] <- sampleDFs[[i]]$ABS[1]
  }
  abs <- c(abs[1:n],abs[1:n],abs[1:n], rep(NA,3))
  df[[day]]$abs <- abs

  dfc <- df[[day]][1:n,]
  dfe <- df[[day]][(n+1): (n+n),]
  dfn <- df[[day]][ ((2 *n)+1): ((2 *n) +n),]

  control <- numeric(n)
  emp <- numeric(n)
  norm <- numeric(n)
  for(i in 1:n){
    control[i] <- sampleDFs[[i]]$type[1] == "control"
    emp[i] <- sampleDFs[[i]]$type[1] == "emp"
    norm[i] <- sampleDFs[[i]]$type[1] == "norm"
  }

  dfClean <- rbind(dfc[control == TRUE,],dfe[emp == TRUE,],dfn[norm == TRUE,],
                   tail(df[[day]],3))

  return(dfClean)
}

dfCleanList[[1]] <-  dfextract(d1precis, day = 1)    
dfCleanList[[2]] <-  dfextract(d2precis, day = 2) 
dfCleanList[[3]] <-  dfextract(d3precis, day = 3)   
dfCleanList[[4]] <-  dfextract(d4precis, day = 4)
dfCleanList[[5]] <-  dfextract(d5precis, day = 5)
dfCleanList[[6]] <-  dfextract(d6precis, day = 6) 
dfCleanList[[7]] <-  dfextract(d7precis, day = 7)    
dfVis <- do.call(rbind, dfCleanList)

dfVisInd <- dfVis[!is.na(dfVis$abs),]
dfVisOv <- dfVis[is.na(dfVis$abs),]
dfVisInd$dayDF <- (dfVisInd$day * 5) - 5
dfVisOv$dayDF <- (dfVisOv$day * 5) - 5

daysPlot2 <- ggplot(dfVisInd)+theme_tufte()+
  labs(title = "Multiplicative impact of a single past intervention",
       subtitle  = "(with 89% posterior density intervals)", x = "days ago", 
       y = "multiplier")+
  scale_x_continuous(breaks = seq(0,30, by = 5), 
        labels = seq(1,7), limits = c(-.5,30))+ ylim(c(0.5,1.5))+
  facet_wrap(~type, ncol = 1)+
  geom_hline(aes(yintercept = 1), color = "gray", alpha = 0.7, lty =2, size =.5)+
  geom_pointrange(aes(x = dayDF + 0.4 * abs, y  = expMean, 
        color = abs, ymin = expLow, ymax = expHigh ), alpha = .2, size = .05)+
  geom_pointrange(data = dfVisOv, aes(x = dayDF -.4 , y  = expMean,
            ymin = expLow, ymax = expHigh), size = .3)+
  theme(plot.title.position = "plot",legend.position = "bottom")+
  geom_label_repel(data = dfVisOv, aes(x = dayDF -.4 , y  = expMean,
            label = round(expMean,2)), size = 2, box.padding = .8,
            label.padding = .15,label.size = .2,label.r = 0.2)

```

\begin{figure}[H]
```{r fig:dailyResultsPlot,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
daysPlot2
```
\caption{Impact of interventions received lag $1\leq k \leq 7$ on attacks on a given day. High-level coefficients are pictured in black.}
\label{fig:dailyResults}
\end{figure}

  \normalsize

Notice that in short term, interventions actually increase aggression the next day (even taking the user's yesterday's aggression and today's activity in consideration). The effect, however, quickly wears off.

## Cumulative sum of interventions

In our analysis of the effect of the cumulative number of interventions received so far, however, we intend separate this short-term effect from the long-term effect. To achieve this, we lag the cumulative interventions variable by 3, so that we're giving the user the minimal number of days needed for the short-term effect to wane. The individual users' multiplicative impact coefficients are visualized in Figure \ref{fig:cumulativeResultsPlot}.

\footnotesize
```{r cumulativeResults,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
getPrecisForParamOv <- function(object, i, group){
  samples <- as.data.frame(object[[i]])
  means <- as.data.frame(sapply(samples, mean))
  hpdis <- as.data.frame(t(sapply(samples, HPDI)))
  df <- cbind(means, hpdis)
  colnames(df) <- c("mean", "low", "high")
  df$param <- rep(names(object[i]), nrow(df))
  df$expMean <- exp(df$mean)
  df$expLow <- exp(df$low)
  df$expHigh <- exp(df$high)
  df$group <- rep(group, nrow(df))
  rownames(df) <- df$param
  return(df)
}

getPrecisForParamInd <- function(object, i, group, dat){
#  object <- samplesA; i <- 10; group = "A"; dat  = datA
  samples <- as.data.frame(object[[i]])
  head(samples)
  means <- as.data.frame(sapply(samples, mean))
  hpdis <- as.data.frame(t(sapply(samples, HPDI)))
  df <- cbind(means, hpdis)
  colnames(df) <- c("mean", "low", "high")
  df$expMean <- exp(df$mean)
  df$expLow <- exp(df$low)
  df$expHigh <- exp(df$high)
  df$user <- paste(group, "user",1:nrow(df), sep = "")
  df$userID <- 1:nrow(df)
  head(df)
  for (id in 1:nrow(df)){
  df$type[id] <- dat$type[dat$userID == id][1]
  }
  for(u in 1:nrow(df)){
    df$abst[u] <-   datA$abst[dat$user == u][1]
  }
  df$group <- rep(group, nrow(df))
  df$param <- rep(names(object[i]), nrow(df))
  df$paramType <- rep(0,nrow(df))
  df$paramType[grep("control",df$param)] <- 1 
  df$paramType[grep("emp",df$param)] <- 2 
  df$paramType[grep("norm",df$param)] <- 3
  df <- df[df$type == df$paramType,]
  return(df)
}

datA <- readRDS(file = "timeSeries/tsaStanCumulative/datA.RDS")
fitA <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitA.rds")
datB <- readRDS(file = "timeSeries/tsaStanCumulative/datB.RDS")
fitB <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitB.rds")
datC <- readRDS(file = "timeSeries/tsaStanCumulative/datC.RDS")
fitC <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitC.rds")
datD <- readRDS(file = "timeSeries/tsaStanCumulative/datD.RDS")
fitD <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitD.rds")

samplesA <- rstan::extract(fitA, permuted = TRUE,
                           inc_warmup = FALSE,  include = TRUE)
samplesB <- rstan::extract(fitB, permuted = TRUE,
                           inc_warmup = FALSE,  include = TRUE)
samplesC <- rstan::extract(fitC, permuted = TRUE,
                           inc_warmup = FALSE,  include = TRUE)
samplesD <- rstan::extract(fitD, permuted = TRUE,
                           inc_warmup = FALSE,  include = TRUE)

paramsIndividualIndices <- c(1,2,3,10,11,12)
paramsOverallIndices <- 4:9

precisAind <- list()
for (i in 1:6){
  precisAind[[i]] <- getPrecisForParamInd(samplesA, 
                     paramsIndividualIndices[i], "A", datA)
}
names(precisAind) <- names(samplesA)[c(1,2,3,10,11,12)]

precisAov <- list()
for (i in 1:6){
  precisAov[[i]] <- getPrecisForParamOv(samplesA,
                    paramsOverallIndices[i], "A")
}
names(precisAov) <- names(samplesA)[4:9]

#B
precisBind <- list()
for (i in 1:6){
  precisBind[[i]] <- getPrecisForParamInd(samplesB, 
                     paramsIndividualIndices[i], "B", datB)
}
names(precisBind) <- names(samplesB)[c(1,2,3,10,11,12)]

precisBov <- list()
for (i in 1:6){
  precisBov[[i]] <- getPrecisForParamOv(samplesB, 
                    paramsOverallIndices[i], "B")
}
names(precisBov) <- names(samplesB)[4:9]

#C
precisCind <- list()
for (i in 1:6){
  precisCind[[i]] <- getPrecisForParamInd(samplesC,
                    paramsIndividualIndices[i], "C", datC)
}
names(precisCind) <- names(samplesC)[c(1,2,3,10,11,12)]

precisCov <- list()
for (i in 1:6){
  precisCov[[i]] <- getPrecisForParamOv(samplesC, 
                    paramsOverallIndices[i], "C")
}
names(precisCov) <- names(samplesC)[4:9]

#D
precisDind <- list()
for (i in 1:6){
  precisDind[[i]] <- getPrecisForParamInd(samplesD, 
                     paramsIndividualIndices[i], "D", datD)
}
names(precisDind) <- names(samplesD)[c(1,2,3,10,11,12)]

precisDov <- list()
for (i in 1:6){
  precisDov[[i]] <- getPrecisForParamOv(samplesD, 
                    paramsOverallIndices[i], "D")
}
names(precisDov) <- names(samplesD)[4:9]

dfVisIndA <- do.call(rbind, precisAind)
dfVisIndB <- do.call(rbind, precisBind)
dfVisIndC <- do.call(rbind, precisCind)
dfVisIndD <- do.call(rbind, precisDind)
dfVisInd <- rbind(dfVisIndA,dfVisIndB,dfVisIndC, dfVisIndD)

dfVisOvA <-  do.call(rbind, precisAov)
dfVisOvB <-  do.call(rbind, precisBov)
dfVisOvC <-  do.call(rbind, precisCov)
dfVisOvD <-  do.call(rbind, precisDov)
dfVisOv <- rbind(dfVisOvA,dfVisOvB,dfVisOvC,dfVisOvD )

abstBaseline <- seq(-1,1.5, by = .01)
groups <- c("A", "B", "C", "D")
groupedPredictions <- list()

for(i in 1:4){
groupDF <- subset(dfVisOv, group == groups[i])
groupControlLow <- exp(groupDF$low[1] + groupDF$low[6] * abstBaseline) 
groupControlHigh <- exp(groupDF$high[1] + groupDF$high[6] * abstBaseline) 
groupControlMean <- exp(groupDF$mean[1] + groupDF$mean[6] * abstBaseline) 
groupControlType <- rep("control", length(groupControlMean))
groupControl <- data.frame(abst = abstBaseline, low = groupControlLow,
                           high = groupControlHigh, mean = groupControlMean, 
                           typeChar = groupControlType,
                           group = rep(groups[i], length(groupControlMean)))

groupEmpLow <- exp(groupDF$low[2] + groupDF$low[5] * abstBaseline) 
groupEmpHigh <- exp(groupDF$high[2] + groupDF$high[5] * abstBaseline) 
groupEmpMean <- exp(groupDF$mean[2] + groupDF$mean[5] * abstBaseline) 
groupEmpType <- rep("empathy", length(groupEmpMean))

groupEmp <- data.frame(abst = abstBaseline, low = groupEmpLow,
                           high = groupEmpHigh, mean = groupEmpMean,
                       typeChar = groupEmpType,
                       group = rep(groups[i], length(groupEmpMean)))

groupNormLow <- exp(groupDF$low[3] + groupDF$low[4] * abstBaseline) 
groupNormHigh <- exp(groupDF$high[3] + groupDF$high[4] * abstBaseline) 
groupNormMean <- exp(groupDF$mean[3] + groupDF$mean[4] * abstBaseline) 
groupNormType <- rep("normative", length(groupNormMean))

groupNorm <- data.frame(abst = abstBaseline, low = groupNormLow,
                       high = groupNormHigh, mean = groupNormMean,
                       typeChar = groupNormType, 
                       group = rep(groups[i], length(groupControlMean)))

groupJoint <- rbind(groupControl, groupEmp, groupNorm)

groupedPredictions[[i]]  <- groupJoint 
}

groupedPredictionsDF <- data.frame(do.call(rbind, groupedPredictions))

dfVisInd$userIndex <- as.integer(as.factor(dfVisInd$user))

jointLow <- numeric(440)
jointHigh <- numeric(440)
jointMean <- numeric(440)
jointAbst <- numeric(440)
jointUserIndex <- numeric(440)
jointType <- numeric(440)
for (index in 1:440){
    userDF <- dfVisInd[dfVisInd$userIndex == index,]
    userDF
    jointLow[index] <- exp(userDF$low[1] + userDF$low[2] * userDF$abst[2])
    jointHigh[index] <- exp(userDF$high[1] + userDF$high[2] * userDF$abst[2])
    jointMean[index] <- exp(userDF$mean[1] + userDF$mean[2] * userDF$abst[2])
    jointAbst[index] <- userDF$abst[1]
    jointUserIndex[index] <- userDF$userIndex[1]
    jointType[index] <-    userDF$type[1]
}

jointInd <- data.frame(userIndex = jointUserIndex, 
                       abst = jointAbst,
                       type = jointType, 
                       low = jointLow, 
                       mean = jointMean,
                       high = jointHigh)

jointInd$typeChar <- ifelse(jointInd$type == 3, "normative",
                            ifelse(jointInd$type == 2, "empathy", "control" ))

individualLeft <- ggplot(jointInd)+ 
  geom_pointrange(data = jointInd, aes(x = abst, y  = mean,
                                     ymin = low, ymax = high),
                  size = .3, color = "grey30",
                  position = position_jitter(width = 0.1), alpha = .4)+
  facet_wrap(~typeChar) +
  labs(title = "Multiplicative impact of cumulative  interventions")+
  xlab("aggression before (standardized)")+ ylab("multiplicative impact")+
  theme_tufte()+theme(plot.title.position = "plot")

individualRight <- ggplot(jointInd)+facet_wrap(~typeChar)+
  geom_hline(aes(yintercept = 1), color = "black",
             alpha = 0.7, lty =2, size =.5)+
  geom_pointrange(data = jointInd, aes(x = abst, 
             y  = mean, ymin = low, ymax = high),
             size = .3, color = "grey30", alpha = .4,
             position = position_jitter(width = 0.1))+
  xlim(-.9,1.2)+ylim(0.5,1.7)+
  labs(title = " ",
       subtitle = "x axis restricted to the bulk of the sample (colored by random groups)")+
  xlab("aggression before (standardized)")+ ylab("multiplicative impact")+
  theme_tufte()+
  geom_line(data = groupedPredictionsDF, aes(x = abst, y = mean, 
                  color = group))+
  geom_errorbar(data = groupedPredictionsDF, 
        aes(x = abst, ymin = low, ymax = high, color = group), alpha = .1)+ 
  guides(color = FALSE) +theme(plot.title.position = "plot")
```

\begin{figure}[H]
```{r fig:cumulativeResultsPlot,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
individualLeft

individualRight
```
\caption{Multiplicative impact of cumulative interventions lag 3 on attacks. Individual users' coefficents only, full range (top), and with attention restricted to the bulk of the sample. Sub-sample coefficients depend on aggression and are represented as lines, colored by sub-sample. Note low number and high uncertainty for highly aggressive users, which motivate the restriction of the $x$ axis for inspection.}
\label{fig:cumulativeResultsPlot}
\end{figure}

\normalsize 
The efficiency of normative interventions seems overall higher, except for low-aggression users, for  which empathetic interventions might be equally or more useful. Importantly, linear extrapolation to extreme values might be misleading, so let us inspect on what happens with the general level multiplicative coefficients at the levels of aggression which are actually quite common, that is, at the 1st, 2nd and 3rd quartile (with respect to $\mathsf{abst}$). This indicates that for the bulk of the sample the impact of cumulative interventions has been negative, slightly more so on users with lower aggression levels.

\footnotesize
```{r cumulativeResultsGeneral,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
hateJointDF <- do.call(rbind,hateDFs)
quantile(hateJointDF$ABS, c(.25, .5, .75))

groupedQuantiled <- groupedPredictionsDF[groupedPredictionsDF$abst == -.56 | 
                                        groupedPredictionsDF$abst == -.26 | 
      (groupedPredictionsDF$abst < 0.178 & groupedPredictionsDF$abst >= 0.16),]

groupedQuantiled$quantile <- ifelse( groupedQuantiled$abst == -.56, .25, 
                                     ifelse(groupedQuantiled$abst == -.26, .5,
                                            .75)
)

plotGeneralCumulative <- ggplot(groupedQuantiled)+ 
  geom_pointrange(aes(x = as.factor(quantile), y  = mean, ymin = low,
                  ymax = high, color = group), size = .4, alpha = 1, 
                  position = position_dodge(width = 0.4))+
  facet_wrap(~typeChar)+xlab("aggression before (quantile)")+
  ylab("coefficient")+theme_tufte()+ guides(color = "none")+
  labs(title = "Multiplicative impact of cumulative interventions in
                  three aggression quantiles")+
  geom_hline(aes(yintercept = 1), color = "black", 
                  alpha = 0.7, lty =2, size =.5)+
  geom_label_repel(aes(x = as.factor(quantile), y  = mean,
                  label = round(mean,2), color = group), size = 3) +
  theme(plot.title.position = "plot")
```

\normalsize

\begin{figure}[H]
```{r fig:cumulativeResultsGeenralPlot,echo=FALSE,eval=TRUE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
plotGeneralCumulative 
```
\caption{Multiplicative impact of cumulative interventions lag 3 on attacks. General level coefficents only, in three quantiles (.25, .5, .75). Colored by sub-sample.}
\label{fig:cumulativeResultsGeneralPlot}
\end{figure}

## Long term before/after analysis

The coefficient in the  \textsf{Final} model are as in Figure
\ref{fig:coeffs}.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
FinalHMC <- ulam(
  alist(
    AdiffS ~ dnorm( mu, sigma ),
    mu <- a + bADS[groupID] * ADS +  bIT[groupID] +
    bIC[groupID] * IC + bADSIC * ADS * IC+
    bCBS[groupID] *CBS,
    a ~ dnorm (0,0.3),
    bADS[groupID] ~ dnorm(0,.3),
    bADSIC ~ dnorm(0,.3),
    bCBS[groupID] ~ dnorm(0,.3),
    bIT[groupID] ~ dnorm(0,.3),
    bIC[groupID] ~ dnorm(0,.3),
    sigma  ~ dexp(1)
  ),
  data = summaries
)
```

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
FinalHMC <- readRDS(file = "models/FinalHMC.rds")
```

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
plot(precis(FinalHMC, depth = 2))
```
\caption{The final model coefficients.}
\label{fig:coeffs}
\end{figure}

\normalsize

The general problem is that in models of this complexity involving interaction, these are hard to interpret. For this reason, it is better to plot predicted effects for various combinations of predictors. In the construction of the plots we rely on   the following:
\begin{itemize}
\item The values \textsf{ADS} range from -.67 to 10, with approximately 30\% below -.5, around 80\% below .3, and around 95\% below 1.7, so we use these three settings of this variable in our visualizations.

\item The values \textsf{CBS} range from -.82 to 18.3, with approximately 30\% below -.4, around 80\% below .3, and around 95\% below 1.3, so we use these three settings of this variable in our visualizations.

\end{itemize}

\footnotesize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
visGroup <-function(model, ADS, CBS, IC, xmin = 2, ymax = -3){
      groupID <- 1:3
      data <- expand.grid(ADS = ADS, groupID = groupID,
                          CBS = CBS, IC = IC)
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      colnames(mu) <- levels(summaries$group)
      muLong <- melt(mu)
      colnames(muLong) <- c("id", "group", "AdiffS")
      means <- round(apply(mu, 2, mean), 2)
      mu_HPDI <- round(apply(mu, 2, HPDI), 2)
      means <- as.data.frame(means)
      means$group <- rownames(means)
      rownames(means) <- NULL
      meansDisp <- cbind(means, t(as.data.frame(mu_HPDI)))
      meansDisp <- meansDisp[, c(1, 3, 4)]
      at <- c(-2, -1, 0, 1, 2)
      labels <- at * sd(summaries$AdiffS)+     
      mean(summaries$AdiffS)

  plot <- ggplot(muLong) + 
      geom_violin(aes(x = group, color = group, y = AdiffS), alpha = 0.2) +
      xlab("") + scale_y_continuous(breaks = labels) +   
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
      ylab("predicted difference in attacks") +
    guides(color = "none")+
      labs(title = paste("ADS=", ADS, ", CBS=",
                          CBS, sep = "")) +   
      theme_tufte(base_size = 7) +
      ylim(c(-2, 2))
return(plot)
}

destandardize <- function(value, base) {
    round(value * sd(base) + mean(base), 1)
}

visGroupRight <- function(model, ADS, CBS, xmin = 2, ymax = -3, 
                          at = c(-2,-1, 0, 1, 2), base, basename) {
      groupID <- 1:3
      IC <- 5
      data <- expand.grid(ADS = ADS, groupID = groupID, CBS = CBS, IC = IC)
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      colnames(mu) <- levels(summaries$group)
      muLong <- melt(mu)
      colnames(muLong) <- c("id", "group", "AdiffS")
      means <- round(apply(mu, 2, mean), 2)
      mu_HPDI <- round(apply(mu, 2, HPDI), 2)
      means <- as.data.frame(means)
      means$group <- rownames(means)
      rownames(means) <- NULL
      meansDisp <- cbind(means, t(as.data.frame(mu_HPDI)))
      meansDisp <- meansDisp[, c(1, 3, 4)]
      labs <- destandardize(at, base)
  plot <- ggplot(muLong) + 
          geom_violin(aes(x = group, color = group, y = AdiffS), alpha = 0.2) +
          xlab("") + labs(title = paste("ADS=", ADS, ", CBS=", CBS, sep = "")) +
          theme_tufte(base_size = 7) +   
  scale_color_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
    guides(color = "none")

  plot <- plot + ylim(at[1], tail(at, 1)) +
        scale_y_continuous(breaks = NULL, labels = NULL, name = NULL,
                          sec.axis = sec_axis(~. * sd(base) + mean(base),
                          name = basename, breaks = c(labs, 0)), 
                          limits = c(at[1], tail(at, 1)))
  return(plot)
}

visGroupA5C4  <- visGroup(model = FinalHMC, ADS = -0.5, CBS = -0.4, IC = 5)
visGroupA5C3  <- visGroup(model = FinalHMC, ADS = -0.5, CBS = 0.3, IC = 5)
visGroupA5C13 <- visGroupRight(model = FinalHMC, ADS = -0.5, CBS = 1.3,
                 base = summaries$Adiff, basename = "Adiff")
visGroupA3C4  <- visGroup(model = FinalHMC, ADS = 0.3, CBS = -0.4, IC = 5)
visGroupA3C3  <- visGroup(model = FinalHMC, ADS = 0.3, CBS = 0.3, IC = 5)
visGroupA3C13 <- visGroupRight(model = FinalHMC, ADS = 0.3, CBS = 1.3,
                 base = summaries$Adiff, basename = "Adiff")
visGroupA17C4 <- visGroup(model = FinalHMC, ADS = 1.7, CBS = -0.4, IC = 5)
visGroupA17C3 <- visGroup(model = FinalHMC, ADS = 1.7, CBS = 0.3, IC = 5)
visGroupA17C13 <- visGroupRight(model = FinalHMC, ADS = 1.7, CBS = 1.3,
                 base = summaries$Adiff, basename = "Adiff")

visGroupJoint <- ggarrange(
      visGroupA17C4 + ylab("ADS = 1.7") + removeX +
      ggtitle("CBS = -.4"), 
      visGroupA17C3 + removeY + removeX + ggtitle("CBS = .3"), 
      visGroupA17C13 + removeX + ggtitle("CBS = 1.3"),
      visGroupA3C4 + removeX + ylab("ADS = .3") + ggtitle(""), 
      visGroupA3C3 + ggtitle("") + removeX + removeY,
      visGroupA3C13 + ggtitle("") + removeX,
      visGroupA5C4 + ylab("ADS = -.5") + ggtitle(""),
      visGroupA5C3 + removeY + ggtitle(""),
      visGroupA5C13 + ggtitle(""), ncol = 3, nrow = 3
      )
visGroupJoint2b <- annotate_figure(visGroupJoint, 
      top = text_grob(
  "(standardized (left) and original scale (right),IC at the rounded mean = 5)",
  size = 10))
visGroupJoint3b <- annotate_figure(visGroupJoint2b, 
top = text_grob(
    "Predicted change in attacks by activity level and treatment groups",
    size = 12))

```

Grouped before-and-after predicted change of attacks by the levels we just listed are visualized in Figure \ref{fig:predictedChange}.

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
visGroupJoint3b
```
\caption{Predicted change in attacks, depending on user’s activity level
(CBS: comments before, standardized) and how aggressive overall they
were (ADS: attacks during, standardized). The more aggressive and active
the users, the higher the attacks drop in the normative group, slight drop
correlated with emotive interventions for not too active users.}
\label{fig:predictedChange}
\end{figure}

\normalsize

For more clarity, let’s inspect predicted contrasts, here understood as distances from
the control group mean, by activity level, first versus CBS (comments before, standardized, Figure \ref{fig:ContrastCBS}), then versus ADS (attacks during, standardized, Figure \ref{fig:ContrastADS}).

\footnotesize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}

visContrastsCBS <- function(model = FinalHMC, ADS = ADS, IC = 5,
                    CBS = seq(-0.5, 1.5, by = 0.1)) {
      groupID <- 1:3
      data <- expand.grid(ADS, groupID, IC, CBS)
      colnames(data) <- c("ADS", "groupID", "IC", "CBS")
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      means <- round(apply(mu, 2, mean), 4)
      HPDIs <- round(apply(mu, 2, HPDI), 4)
      visContrast <- cbind(data, means, t(as.data.frame(HPDIs)))

      ones <- 3 * (1:(nrow(visContrast)/3)) - 2
      twos <- 3 * (1:(nrow(visContrast)/3)) - 1
      threes <- 3 * (1:(nrow(visContrast)/3))

      colnames(visContrast)[c(6, 7)] <- c("low", "high")
      contrast <- numeric(nrow(visContrast))
      cLow <- numeric(nrow(visContrast))
      cHigh <- numeric(nrow(visContrast))

      for (i in threes) {
                contrast[i] <- visContrast$means[i] - visContrast$means[i - 2]
      }

      for (i in twos) {
                contrast[i] <- visContrast$means[i] - visContrast$means[i - 1]
      }
      visContrast$contrast <- contrast
      visContrast$shift <- visContrast$contrast - visContrast$means

      for (i in ones) {
            visContrast$shift[i] <- 0
      }
      visContrast$cLow <- visContrast$low + visContrast$shift
      visContrast$cHigh <- visContrast$high + visContrast$shift
      visContrast$group = rep(c("control", "empathy", "normative"), 
                              nrow(visContrast)/3)
      visContrastTreatment <- visContrast[groupID != 1, ]

    return(ggplot(visContrastTreatment,
         aes(x = CBS, y = contrast, fill = group, lty = group)) +
         geom_line(se = FALSE) + 
         geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = 0.3) +
         theme_tufte(base_size = 7))+
        scale_fill_manual(values=c("dodgerblue4", "orangered"))

}

visContrastsCBSright <- function(model = FinalHMC, ADS = ADS, IC = 5,
                              CBS = seq(-0.5, 1.5, by = 0.1), 
                              at = c(-2, -1, 0, 1, 2), base, basename) {
      labs <- destandardize(at, base)
      groupID <- 1:3
      data <- expand.grid(ADS, groupID, IC, CBS)
      colnames(data) <- c("ADS", "groupID", "IC", "CBS")
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      means <- round(apply(mu, 2, mean), 4)
      HPDIs <- round(apply(mu, 2, HPDI), 4)
      visContrast <- cbind(data, means, t(as.data.frame(HPDIs)))
      colnames(visContrast)[c(6, 7)] <- c("low", "high")

      ones <- 3 * (1:(nrow(visContrast)/3)) - 2
      twos <- 3 * (1:(nrow(visContrast)/3)) - 1
      threes <- 3 * (1:(nrow(visContrast)/3))
      colnames(visContrast)[c(6, 7)] <- c("low", "high")
      contrast <- numeric(nrow(visContrast))
      cLow <- numeric(nrow(visContrast))
      cHigh <- numeric(nrow(visContrast))

      for (i in threes) {
          contrast[i] <- visContrast$means[i] - visContrast$means[i - 2]
      }

      for (i in twos) {
            contrast[i] <- visContrast$means[i] - visContrast$means[i - 1]
      }
      visContrast$contrast <- contrast
      visContrast$shift <- visContrast$contrast - visContrast$means

      for (i in ones) {
          visContrast$shift[i] <- 0
      }

      visContrast$cLow <- visContrast$low + visContrast$shift
      visContrast$cHigh <- visContrast$high + visContrast$shift
      visContrast$group = rep(c("control", "empathy", "normative"), 
                              nrow(visContrast)/3)
      visContrastTreatment <- visContrast[groupID != 1, ]

      plot <- ggplot(visContrastTreatment, aes(x = CBS, y = contrast, 
                                    fill = group, lty = group)) + geom_line() +
        geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = 0.3) + 
        theme_tufte(base_size = 7)+
        scale_fill_manual(values=c("dodgerblue4", "orangered"))

      plot <- plot + ylim(at[1], tail(at,1))
      plot <- plot + scale_y_continuous(breaks = NULL, labels = NULL, name = NULL,
              sec.axis = sec_axis(~.*sd(base)+ mean(base), 
                         name = basename, breaks = c(labs,0)),
              limits = c(at[1], tail(at,1)))
return(plot)
}

vcCBSa <-  visContrastsCBS(FinalHMC, ADS = -0.5) + ggtitle("ADS = -.5") +
                  ylim(c(-1.5, 2)) +  
        scale_fill_manual(values=c("dodgerblue4", "orangered"))+ 
                 guides(lty = "none", fill = "none")

vcCBSb <-  visContrastsCBS(FinalHMC, ADS = 0.3) + ggtitle("ADS = .3") + ylim(c(-1.5, 2)) +
        scale_fill_manual(values=c("dodgerblue4", "orangered"))+
        guides(lty = "none", fill  = "none") +
                  removeY

vcCBSc <-  visContrastsCBSright(FinalHMC, ADS = 1.7, at = c(-1.5, -1, -0.5, 0, 0.5, 1, 1.5),
                       base = summaries$Adiff, basename = "count") +
                  ggtitle("ADS = 1.7") +
                  theme(legend.position = c(0.75, 0.15))

vcCBS1 <- ggarrange(vcCBSa, vcCBSb, vcCBSc, ncol = 3)

vcCBS2 <- annotate_figure(vcCBS1, top = text_grob(
           "(IC at the rounded mean = 5)",  size = 10))

vcCBS3 <- annotate_figure(vcCBS2,
            top = text_grob(
            "Predicted distance from the control group mean vs. CBS (standardized)",
size = 12))

```
\normalsize

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
vcCBS3
```
\caption{Predicted contrasts (difference in attacks as compared to the control group)
for the two treatment groups vs activity before the treatment. Notice that
empathetic interventions correlated with decreased attacks for less active
users, but performed worse than normative interventions for more active
users. Normative interventions, in contrast, seem to have better impact on
 more active users.}
\label{fig:ContrastCBS}
\end{figure}

\normalsize

\footnotesize

```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
visContrastsADS <- function(model = FinalHMC, CBS = CBS, IC = 5,
                            ADS = seq(-0.5, 1.8, by = 0.1)) {
      data <- expand.grid(CBS, groupID, IC, ADS)
      colnames(data) <- c("CBS", "groupID", "IC", "ADS")
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      means <- round(apply(mu, 2, mean), 4)
      HPDIs <- round(apply(mu, 2, HPDI), 4)
      visContrastADS <- cbind(data, means, t(as.data.frame(HPDIs)))
      ones <- 3 * (1:(nrow(visContrastADS)/3)) - 2
      twos <- 3 * (1:(nrow(visContrastADS)/3)) - 1
      threes <- 3 * (1:(nrow(visContrastADS)/3))
      colnames(visContrastADS)[c(6, 7)] <- c("low", "high")
      contrastADS <- numeric(nrow(visContrastADS))
      for (i in threes) {
          contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i -2]
      }
      for (i in twos) {
          contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i - 1]
      }
      visContrastADS$contrast <- contrastADS
      visContrastADS$shift <- visContrastADS$contrast - visContrastADS$means
      for (i in ones) {
          visContrastADS$shift[i] <- 0
      }
      visContrastADS$cLow <- visContrastADS$low + visContrastADS$shift
      visContrastADS$cHigh <- visContrastADS$high + visContrastADS$shift
      visContrastADS$group = rep(c("control", "empathy", "normative"), nrow(visContrastADS)/3)
      visContrastTreatmentADS <- visContrastADS[groupID != 1, ]

return(
      ggplot(visContrastTreatmentADS,  aes(x = ADS, y = contrast, fill = group, lty = group)) +
         geom_line(se = FALSE) +
         geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = 0.3) +
         theme_tufte(base_size = 7) + guides(lty = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered"))
      )

}

visContrastsADSright <- function(model = FinalHMC, CBS = CBS, IC = 5,
  ADS = seq(-0.5, 1.8, by = 0.1), at = c(-1.5, 1, 0, 1, 1.5), base, basename) {
      labs <- destandardize(at, base)
      data <- expand.grid(CBS, groupID, IC, ADS)
      colnames(data) <- c("CBS", "groupID", "IC", "ADS")
      posterior <- extract.samples(model, n = 1e+05)
      mu <- link(model, data = data)
      means <- round(apply(mu, 2, mean), 4)
      HPDIs <- round(apply(mu, 2, HPDI), 4)
      visContrastADS <- cbind(data, means, t(as.data.frame(HPDIs)))
      ones <- 3 * (1:(nrow(visContrastADS)/3)) - 2
      twos <- 3 * (1:(nrow(visContrastADS)/3)) - 1
      threes <- 3 * (1:(nrow(visContrastADS)/3))
      colnames(visContrastADS)[c(6, 7)] <- c("low", "high")
      contrastADS <- numeric(nrow(visContrastADS))
      for (i in threes) {
          contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-2]
      }
      for (i in twos) {
          contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-1]
      }
      visContrastADS$contrast <- contrastADS
      visContrastADS$shift <- visContrastADS$contrast - visContrastADS$means
      for (i in ones) {
      visContrastADS$shift[i] <- 0
      }
      visContrastADS$cLow <- visContrastADS$low + visContrastADS$shift
      visContrastADS$cHigh <- visContrastADS$high + visContrastADS$shift
      visContrastADS$group = rep(c("control", "empathy", "normative"), nrow(visContrastADS)/3)
      visContrastTreatmentADS <- visContrastADS[groupID != 1, ]

  plot <- ggplot(visContrastTreatmentADS,
                 aes(x = ADS, y = contrast, fill = group, lty = group)) +
    geom_line(se = FALSE) +
    scale_fill_manual(values=c("dodgerblue4", "orangered"))+
    geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = 0.3) +
    theme_tufte(base_size = 7) + guides(lty = "none")

  plot <- plot + ylim(at[1], tail(at, 1))
  plot <- plot + scale_y_continuous(breaks = NULL, labels = NULL, name = NULL,
        sec.axis = sec_axis(~. * sd(base) + mean(base), name = basename,
        breaks = c(labs, 0)), limits = c(at[1], tail(at, 1)))
}

vcADSa <- visContrastsADS(FinalHMC, CBS = -0.4) + ggtitle("CBS = -.4") +
      ylim(c(-1.5, 1.5)) + 
      guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered"))

vcADSb <-  visContrastsADS(FinalHMC, CBS = 0.3) + ggtitle("CBS = .3") +
      ylim(c(-1.5, 1.5)) + scale_fill_discrete(guide = "none") +
      removeY + guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered"))

vcADSc <- visContrastsADSright(FinalHMC, CBS = 1.3, at = c(-1.5, -1, 0, 1, 1.5),
      base = summaries$Adiff, basename = "count") + ggtitle("CBS = 1.3") +
      theme(legend.position = c(0.75, 0.15))

vcADS1 <- ggarrange(
vcADSa, vcADSb, vcADSc,
ncol = 3)

vcADS2 <- annotate_figure(vcADS1, top = text_grob(
  "(IC at the rounded mean = 5)", size = 10))

vcADS3 <- annotate_figure(vcADS2, top = text_grob(
   "Predicted distance from the control group mean vs. ADS",
 size = 12))
```

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
vcADS3
```
\caption{Predicted contrasts (difference in attacks as compared to the control group)
for the two treatment groups vs aggression during the treatment period.
Notice that empathetic interventions correlated with decreased attacks for
less aggressive users, but performed worse than normative interventions for
more aggressive users. Normative interventions, in contrast, seem to have
better impact on  more aggressive users.}
\label{fig:ContrastADS}
\end{figure}

\normalsize

Now, let’s inspect the impact of intervention counts by treatment type by looking at
contrasts (distances from the control group mean) with 89\% HPDIs by IC (intervention
count). Notice the predicted effect of IC is weaker than group membership, so for
visibility the $y$-axis has a smaller range. Also, not enough data was available to reliably
estimate uncertainty for IC above 20, hence the restriction on the $x$-axis (already at
lower values, lack of estimates is visible for the more extreme settings).

\footnotesize

```{r visIC,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
visContrastsIC <- function(model = FinalHMC, CBS = CBS ,
                           IC = seq(0,20,by = 1), ADS = ADS) {
    groupID <- 1:3
    data <- expand.grid(CBS, groupID, IC , ADS)
    colnames(data) <- c("CBS", "groupID", "IC", "ADS")
    posterior <- extract.samples(model, n = 1e5)
    mu <- link( model, data=data )
    means <- round(apply(mu , 2 , mean ), 4)
    HPDIs <- round(apply( mu , 2 , HPDI ),4)
    visContrastIC <- cbind(data,means,t(as.data.frame(HPDIs)))
    ones <- 3 * (1:(nrow(visContrastIC)/3))-2
    twos <- 3 * (1:(nrow(visContrastIC)/3))-1
    threes <- 3 * (1:(nrow(visContrastIC)/3))
    colnames(visContrastIC)[c(6,7)] <- c("low", "high")
    contrastIC <- numeric(nrow(visContrastIC))
    for(i in threes){
        contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-2]
      }
    for(i in twos){
        contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-1]
      }
    visContrastIC$contrast <- contrastIC
    visContrastIC$shift <- visContrastIC$contrast - visContrastIC$means
    for(i in ones){
        visContrastIC$shift[i] <- 0
    }
    visContrastIC$cLow <- visContrastIC$low + visContrastIC$shift
    visContrastIC$cHigh <- visContrastIC$high + visContrastIC$shift
    visContrastIC$group = rep(c("control", "empathy", "normative"),
        nrow(visContrastIC)/3)
    visContrastTreatmentIC <- visContrastIC[groupID !=1,]

return(ggplot(visContrastTreatmentIC,
        aes(x = IC, y = contrast, fill = group, lty = group ))+
         scale_fill_manual(values=c("darkgreen", "dodgerblue4", "orangered"))+
        geom_line(se=FALSE)+
        geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = .3)+
        ylim(c(-1.2,1)) +theme_tufte(base_size = 7))

}

visContrastsICright <- function(model = FinalHMC, CBS = CBS ,
    IC = seq(0,20,by = 1), ADS = ADS, at = c(-1,.5,0,.5,1), base, basename){
      labs <- destandardize(at, base)
      groupID <- 1:3
      data <- expand.grid(CBS, groupID, IC , ADS)
      colnames(data) <- c("CBS", "groupID", "IC", "ADS")
      posterior <- extract.samples(model, n = 1e5)
      mu <- link( model, data=data )
      means <- round(apply(mu , 2 , mean ), 4)
      HPDIs <- round(apply( mu , 2 , HPDI ),4)
      visContrastIC <- cbind(data,means,t(as.data.frame(HPDIs)))
      ones <- 3 * (1:(nrow(visContrastIC)/3))-2
      twos <- 3 * (1:(nrow(visContrastIC)/3))-1
      threes <- 3 * (1:(nrow(visContrastIC)/3))

    colnames(visContrastIC)[c(6,7)] <- c("low", "high")
    contrastIC <- numeric(nrow(visContrastIC))
    for(i in threes){
        contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-2]
        }
    for(i in twos){
        contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-1]
        }
    visContrastIC$contrast <- contrastIC
    visContrastIC$shift <- visContrastIC$contrast - visContrastIC$means
    for(i in ones){
        visContrastIC$shift[i] <- 0
      }
    visContrastIC$cLow <- visContrastIC$low + visContrastIC$shift
    visContrastIC$cHigh <- visContrastIC$high + visContrastIC$shift
    visContrastIC$group = rep(c("control", "empathy", "normative"),
        nrow(visContrastIC)/3)
    visContrastTreatmentIC <- visContrastIC[groupID !=1,]

  plot <- ggplot(visContrastTreatmentIC,
                   aes(x = IC, y = contrast, fill = group, lty = group ))+
    scale_fill_manual(values=c("dodgerblue4", "orangered"))+
    geom_line(se=FALSE)+
    geom_ribbon(mapping = aes(ymin = cLow, ymax = cHigh), alpha = .3)+
    theme_tufte(base_size = 7)

  plot <- plot+ylim(at[1],tail(at,1))
  plot <- plot+scale_y_continuous(breaks = NULL, labels = NULL,
        name = NULL, sec.axis= sec_axis(~. * sd(base) + mean(base),
        name = basename, breaks = c(labs,0)),
        limits = c(at[1]-.2,tail(at,1)))
}

visContrastsICJointD <- ggarrange(
    visContrastsIC(ADS = 1.7, CBS = -.4)+removeX+
          theme(legend.position = c(0.3, 0.9),
          legend.key.size = unit(.3, 'cm'),
          legend.key.height = unit(.3, 'cm'),
          legend.key.width = unit(.3, 'cm'),
          legend.title= element_blank())+
          ggtitle("CBS = -.4")+ ylab("ADS = 1.7")+ guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsIC(ADS = 1.7, CBS = .3)+removeY+removeX+
          scale_fill_discrete(guide="none")+
          ggtitle("CBS = .3")+ guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsICright(ADS = 1.7, CBS = 1.3, at = c(-2,-1,0,1,2),
                        base = summaries$Adiff, basename = "count")+
          removeX + guides(lty = "none", fill = "none")+
          ggtitle("CBS = 1.3"),
    visContrastsIC(ADS = .3, CBS = -.4)+removeX+
          scale_fill_discrete(guide="none")+
          ylab("ADS = .3")+ guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsIC(ADS = .3, CBS = .3)+removeY+removeX+
           guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsICright(ADS = .3, CBS = 1.3,at = c(-2,-1,0,1,2),
          base = summaries$Adiff, basename = "count")+
          removeX  + guides(lty = "none", fill = "none"),
    visContrastsIC(ADS = -.5, CBS = -.4)+
          ylab("ADS = -.5")+ guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsIC(ADS = -.5, CBS = .3)+removeY+
      guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
    visContrastsICright(ADS = -.5, CBS = 1.3,at = c(-2,-1,0,1,2),
                        base = summaries$Adiff, basename = "count") +
      guides(lty = "none", fill = "none")+
      scale_fill_manual(values=c("dodgerblue4", "orangered")),
  ncol = 3, nrow = 3
)

visContrastsICJoint2D <- annotate_figure(visContrastsICJointD,
top = text_grob("", size = 10))
visContrastsICJoint3D <- annotate_figure(visContrastsICJoint2D,
top = text_grob("Predicted distance from the control group vs. IC",
size = 12))
```

\begin{figure}
```{r visICPlot,echo=FALSE,eval=TRUE,fig.align = "center",cache=FALSE, fig.show = "hold", out.width = "100%"}
visContrastsICJoint3D
```
\caption{Contrasts (change in attacks as compared to the control group) vs the number
of interventions received. Note that repeating empathetic interventions
correlates with decreased attacks, while repeating normative interventions
is counterproductive.}
\label{fig:ContrastsIC}
\end{figure}

### 2023-12-18 bayesianModelsDiff.R

@@ -1,269 +1,0 @@
-source("utils/plotPriors.R")
-
-summaries <- readRDS(file = "datasets/Summaries.rds")
-
-
-
-summaries$ABS <- standardize(summaries$AB)
-summaries$CBS <- standardize(summaries$CB)
-summaries$AAS <- standardize(summaries$AA)
-summaries$CAS <- standardize(summaries$CA)
-summaries$CDS <- standardize(summaries$CD)
-summaries$ADS <- standardize(summaries$AD)
-summaries$groupID <-  as.integer( as.factor(summaries$group) )
-
-
-
-
-nullModelProps <- quap(
-  alist(
-    AdiffS ~ dnorm( mu, sigma ),
-    mu ~ dnorm (0,0.5),
-    sigma  ~ dexp(1)
-  ), 
-  data = summaries  
-)
-
-
-precis(nullModelProps)
-
-#ADS
-ADSModelProps <- quap(
-  alist(
-    ApropS ~ dnorm( mu, sigma ),
-    mu <-  a + bADS * ADS,
-    a ~ dnorm (0,0.5),
-    bADS ~ dnorm(0,0.2),
-    sigma  ~ dexp(1)
-  ), 
-  data = summaries
-)
-
-precis(ADSModelProps)
-
-
-compare(nullModelProps,ADSModelProps)
-
-
-
-
-ADSICModelProps <- quap(
-  alist(
-    ApropS ~ dnorm( mu, sigma ),
-    mu <-  a + bADS * ADS+ bIC * IC,
-    a ~ dnorm (0,0.5),
-    bADS ~ dnorm(0,0.2),
-    bIC ~ dnorm(0,0.2),
-    sigma  ~ dexp(1)
-  ), 
-  data = summaries
-)
-
-
-compare(ADSModelProps,ADSICModelProps)
-
-precis(ADSICModelProps)
-
-
-
-ITModelProps <- quap(
-  alist(
-    ApropS ~ dnorm( mu, sigma ),
-    mu <-  bIT[groupID] ,
-    bIT[groupID] ~ dnorm(0,1),
-    sigma  ~ dexp(1)
-  ), 
-  data = summaries
-)
-
-precis(ITModelProps, depth = 2)
-
-compare(ADSModelProps, ITModelProps)
-
-
-ADSITModelProps <- quap(
-  alist(
[…]

### 2023-12-18 caseStudy/caseCleaning.R

@@ -1,71 +1,0 @@
-library(rethinking)
-library(tidyverse)
-
-
-all <- read.csv(file = "datasets/RAWNESTA/allCleanComplete.rds")
-hate <- readRDS(file = "datasets/RAWNESTA/hateCleanComplete.rds")
-interventions <- readRDS(file = "datasets/interventions.rds")
-summaries <- read.csv(file = "datasets/Summaries.csv")
-
-nrow(all)
-nrow(hate)
-
-summaries$ABS <- standardize(summaries$AB)
-summaries$CBS <- standardize(summaries$CB)
-summaries$AAS <- standardize(summaries$AA)
-summaries$CAS <- standardize(summaries$CA)
-summaries$CDS <- standardize(summaries$CD)
-summaries$ADS <- standardize(summaries$AD)
-summaries$group <- as.factor(summaries$group)
-summaries$groupID <-  as.integer( as.factor(summaries$group) )
-
-
-head(interventions)
-
-
-ABS <- c("low", "medium", "high")
-CBS <- c("low", "medium", "high")
-
-groups <- expand.grid(ABS = ABS, CBS = CBS)
-
-groups
-
-head(summaries)
-
-min(summaries$ABS)
-max(summaries$ABS)
-min(summaries$CBS)
-max(summaries$CBS)
-
-
-
-ggplot(summaries, aes(x = ABS)) +geom_histogram()
-ggplot(summaries, aes(x = CBS)) +geom_histogram()
-
-
-
-
-ll <- summaries %>% filter(ABS < -.495 & CBS < -.495 & IC > 1)  # bottom 10
-
-ll
-
-user <- as.character(ll$author[10])
-
-user
-
-output <- all[all$author == user,]
-
-nrow(output)
-
-output$text  
-
-user
-
-attacks <- hate %>% filter(author == user) %>% select(day,id,text)
-
-
-attacks
-
-colnames(summaries)
-
-summaries[summaries$author == user,]

### 2023-12-18 cleanup/inspecting.R

@@ -1,151 +1,0 @@
-library(data.table)
-library(tidyverse)
-library(ggplot2)
-library(scales)
-library(dplyr)
-
-
-Nall <- as.data.frame(fread("nesta_all.txt",quote=""))
-NallCont <- as.data.frame(fread("nesta_all_cont.txt",quote = ""))
-NallTest <- as.data.frame(fread("nesta_all_test.txt",quote = ""))
-Nhate <- as.data.frame(fread("nesta_hate.txt",quote = ""))
-NhateCont <- as.data.frame(fread("nesta_hate_cont.txt",quote = ""))
-NhateTest <- as.data.frame(fread("nesta_hate_test.txt",quote = ""))
-NallNew <- as.data.frame(fread("nesta_3_all.txt",quote=""))
-NhateNew <- as.data.frame(fread("nesta_3_hate.txt",quote=""))
-
-head(Nall)
-head(NallCont)
-head(NallTest)
-head(Nhate)
-head(NhateCont)
-head(NhateTest)
-head(NallNew)
-head(NhateNew)
-
-colnames(Nall) <-  c("id", "timestamp", "author","text","subreddit")
-colnames(NallCont) <-  c("id", "timestamp", "author","text","subreddit")
-colnames(NallTest) <-  c("id", "timestamp", "author","text","subreddit")
-colnames(Nhate) <-  c("id", "timestamp", "author","text","subreddit", "redditFilter","violence", "rules")
-colnames(NhateCont) <-  c("id", "timestamp", "author","text","subreddit", "redditFilter","violence", "rules")
-colnames(NhateTest) <-  c("id", "timestamp", "author","text","subreddit", "redditFilter","violence", "rules")
-colnames(NallNew) <-  c("id", "timestamp", "author","text","subreddit")
-colnames(NhateNew) <-  c("id", "timestamp", "author","text","subreddit", "redditFilter","violence", "rules")
-
-
-head(Nall)
-head(NallCont)
-head(NallTest)
-head(Nhate)
-head(NhateCont)
-head(NhateTest)
-head(NallNew)
-head(NhateNew)
-
-nrow(NallNew)
-nrow(NhateNew)
-
-#convert time stamps to dates
[…]

### 2023-12-18 nestaVolunteers/nestaVolunteers/engagementSetup.R

@@ -1,348 +1,0 @@
-library(data.table)
-library(tidyverse)
-library(ggplot2)
-library(scales)
-library(dplyr)
-library(janitor)
-library(spatstat.utils)
-library(useful)
-library(ggthemes)
-
-#setwd("~/Desktop/nestaVolunteers")
-
-
-volunteers <- read.csv(file = "volunteers.csv")
-
-head(volunteers, n = 20)
-nrow(volunteers) #1755
-
-
-#remove empty rows
-
-volunteersCleaned <- volunteers[!apply(volunteers == "", 1, all), ] 
-
-nrow(volunteersCleaned)
-head(volunteersCleaned)
-
-#interventions per day
-volunteersDate <- t(xtabs(~Volunteer.name + Date, data=volunteersCleaned))
-
-head(volunteersDate)
-ncol(volunteersDate)
-nrow(volunteersDate)
-str(volunteersDate)
-
-sort(colnames(volunteersDate))
-
-write.csv(volunteersDate, "volunteersDate.csv")
-
-#write and read csv to get rid of the xtabs format
-volunteersDateCSV <- read.csv(file = "volunteersDate.csv")
-
-head(volunteersDateCSV)
-str(volunteersDateCSV)
-ncol(volunteersDateCSV)
-colnames(volunteersDateCSV)
-
-
-volunteersDateCSVRemove <- volunteersDateCSV[,-2]
-head(volunteersDateCSVRemove)
-nrow(volunteersDateCSVRemove)
-
-colnames(volunteersDateCSVRemove)[1] <- "Date"
-
-str(volunteersDateCSVRemove)
-
-volunteersDateCSVRemove$bicycleflossing
-
-volunteersDateCSVRemove$Date <- as.Date(volunteersDateCSVRemove$Date)
-
-
-sort(colnames(volunteersDateCSVRemove))
-
-head(volunteersDateCSVRemove)
-nrow(volunteersDateCSV)
-
-
-#now additional info about joint identities
-joinDates <- read_csv("joinDates.csv")
-head(joinDates)
-
-
-# 
-# volunteersDateCSVRemove %>% select(Date,ChubbyhappyBuddha, PipperPapper)
-# 
-# volunteersDateCSVRemove <- volunteersDateCSVRemove %>% 
-#   mutate(ChubbyhappyBuddhaPipperPapper = ChubbyhappyBuddha + PipperPapper) %>%
[…]

### 2023-12-18 nestaVolunteers/nestaVolunteers/vPred.R

@@ -1,373 +1,0 @@
-library(rethinking)
-library(ggplot2)
-
-
-playmusic <- browseURL('https://www.youtube.com/watch?v=Lx1iH8DgrLE&list=RDLx1iH8DgrLE&start_radio=1')
-
-
-
-#volunteersSeparate <- readRDS("datasets/volunteersSeparate.rds")
-
-
-#mean(apply(volunteersJoint,2, function(x) is.na(x)))
-
-
-dat <- readRDS("datasets/volunteerDat.rds")
-
-str(dat)
-
-
-
-start.time <- Sys.time()
-competitionModel <-  ulam(
-  alist(
-    interventions ~ dgampois(lambda,phi),
-    log(lambda) <- l[volunteerID] + enth[volunteerID] * daysOfProject +
-    comp[volunteerID] * competition,
-    l[volunteerID] ~ dnorm(lbar,lsigmabar),
-    lbar ~ dnorm(2, .9),
-    lsigmabar ~ dexp(.5),
-    enth[volunteerID] ~ dnorm(enthbar, enthsigmabar),
-    enthbar ~ dnorm(0, .3),
-    enthsigmabar ~ dexp(.5),
-    comp[volunteerID] ~ dnorm(compbar, compsigmabar),
-    compbar ~ dnorm(0, .3),
-    compsigmabar ~ dexp(.5),
-    phi <- puser[volunteerID],
-    puser[volunteerID] ~ dexp(1)
-  ), data=dat, log_lik = TRUE, 
-  chains = 2, cores = 2, 
-  iter = 5000,
-  constraints = list(
-    lambda = "lower = 0.0001, upper = 5",
-    l = "lower = 0.0001, upper = 5",
-    lbar = "lower = 0.1, upper = 5",
-    lsigmabar = "lower =  0.0001, upper = 5",
-    enth = "lower = -1.5, upper = 5",
-    enthbar = "lower = -1.5, upper = 5",
-    enthsigmabar = "lower = 0.0001, upper = 5",
-    comp = "lower = -1.5, upper = 5",
-    compbar = "lower = -1.5, upper = 5",
-    compsigmabar = "lower = 0.0001, upper = 5"
-  ),
-  control =
-    list(max_treedepth = 14, adapt_delta = 0.9),
-  #   cmdstan = TRUE
-)
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-time.taken
-playMusic
-
-
[…]

### 2023-12-18 nestaVolunteers/vVisualisations.R

@@ -1,9 +1,0 @@
-library(data.table)
-library(tidyverse)
-library(ggplot2)
-library(scales)
-library(dplyr)
-library(janitor)
-library(spatstat.utils)
-library(useful)
-library(ggthemes)

### 2023-12-18 oldCleanup/RcontrolCleanup.R

@@ -1,80 +1,0 @@
-library(data.table)
-library(tidyverse)
-library(ggplot2)
-library(scales)
-
-#_________ load files, select & rename columns, inspect attacks
-#we load twice to be able to inspect raw data at all times
-RcontrolAttacks <- as.data.frame(fread("Rcontrol_attacks_final.txt",quote = ""))
-RcontrolAttacksRaw <- as.data.frame(fread("Rcontrol_attacks_final.txt",quote = ""))
-
-
-# rename columns, use camelCase throughout the project!!
-colnames(RcontrolAttacks) <-  c("id", "utc", "author","text","subreddit", "parentID","link", "high", "low","rules", "receiver", "replyToPost")
-colnames(RcontrolAttacksRaw) <-  c("id", "utc", "author","text","subreddit", "parentID","link", "high", "low","rules", "receiver", "replyToPost")
-
-
-#take a look
-head(RcontrolAttacks)
-
-
-# remove columns not used in the aggregation
-RcontrolAttacksClean <-  RcontrolAttacks %>% select(-c(text,parentID,link,rules)) 
-
-#inspect again
-head(RcontrolAttacksClean)
-
-#convert time stamps to dates
-RcontrolAttacksClean$day <- as.Date(as.POSIXct(RcontrolAttacksClean$utc, origin="1970-01-01"))
-
-
-#inspect
-head(RcontrolAttacksClean)
-
-#double check the time range
-min(RcontrolAttacksClean$day)
-max(RcontrolAttacksClean$day) 
-
-
-#take a look at at distribution in time to look for anomalies
-ggplot(RcontrolAttacksClean, aes(x=day))+geom_histogram(bins = 15)+
-  scale_x_date(date_breaks = "days" , date_labels = "%d.%m")+
-  geom_vline(xintercept = as.Date("2020-07-02"))+ theme_minimal(base_size = 8)
-
-
-#save file for further use
-write.csv(RcontrolAttacksClean,"RcontrolAttacksClean.csv")
-
-#________________________________
-#now, similar cleaning for the comments; will rbind with removing duplicates later on
-RcontrolComments <- as.data.frame(fread("Rcontrol_comments_final.txt",quote = ""))
-
-head(RcontrolComments)
-
[…]

### 2023-12-18 oldCleanup/RcontrolToFrequency.R

@@ -1,254 +1,0 @@
-library(dplyr)
-library(tidyverse)
-library(WRS2)
-
-#load list of sampled users with bots removed
-RcontrolList<- read.csv("RcontrolListNoBots.csv",header=TRUE)[,1]
-
-#load the dataset
-RcontrolAttacks <- read.csv("RcontrolAttacksClean.csv")
-
-#load the comments dataset
-RcontrolCommentsNoRepeats <- read.csv("RcontrolCommentsNoRepeats.csv")
-
-#rbind
-RcontrolAll <- rbind(RcontrolAttacks,RcontrolCommentsNoRepeats)
-
-head(RcontrolAll)
-nrow(RcontrolAll)
-
-#double check to remove duplicates by ID
-RcontrolUnique <- RcontrolAll %>% distinct(RcontrolAll$id, .keep_all=TRUE)
-
-head(RcontrolUnique)
-
-#now drop the additional id column
-RcontrolUnique <- RcontrolUnique[,-11]
-
-#check length and colnames
-nrow(RcontrolUnique)
-colnames(RcontrolUnique)
-
-#rename for brevity
-Rcontrol <- RcontrolUnique
-
-#inspect 
-head(Rcontrol)
-
-#now we tabulate attacks of two types by day and receiver [mind your head! this is for attacks received, you need to do something slighlty different if you want activity counts and if you split by weeks etc]
-#_____ counting received: rl - received low, rh - received high,  rpl - received to post low, rph  - received to post high
-
-RcontrolFreqL <- xtabs(low  ~ receiver + day, data = Rcontrol)
-RcontrolFreqH <- xtabs(high  ~ receiver + day, data = Rcontrol)
-RcontrolFreqPl <- xtabs(low * replyToPost  ~ receiver + day, data = Rcontrol)
-RcontrolFreqPh <- xtabs(high * replyToPost  ~ receiver + day, data = Rcontrol)
-RcontrolFreqA <- xtabs(~ author + day, data = Rcontrol)
-
-
-
-head(RcontrolFreqL)
-head(RcontrolFreqH)
-head(RcontrolFreqPl)
-head(RcontrolFreqPh)
-head(RcontrolFreqA)
-
-# add day numbers pated after attack type as colnames
-colnames(RcontrolFreqL) <- paste("l",1:15,sep="")
[…]

### 2023-12-18 oldCleanup/cuttingBeforeAfter.R

@@ -1,36 +1,0 @@
-
-
-user1 <- c(0,0, 0, 1, 0, 1, 0, 0, 0)
-user2 <- c(0,0, 0, 0,  1, 1, 1, 0, 0)
-
-
-users <- list(user1, user2)
-
-starts <- numeric(length(users))
-ends <- numeric(length(users))
-for(i in 1: length(users)){
-starts[i] <- min(which(users[[i]] !=0 ))-2
-ends[i] <-  max(which(users[[i]] !=0 ))+2
-}
-
-starts
-ends
-
-cleanedUsers <- list()
-for(i in 1: length(users)){
-cleanedUsers[[i]] <- users[[i]][starts[i]:ends[i]]
-}
-
-
-cleanedUsers
-
-usersDF <- do.call("rbind", cleanedUsers)
-
-
-usersDF
-
-
-
-
-
-

### 2023-12-18 predictionInteractionsProps.R

@@ -1,593 +1,0 @@
-source("utils/plotPriors.R")
-
-removeX <-   theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())
-
-removeY <-   theme(axis.title.y=element_blank(),
-                   axis.text.y=element_blank(),
-                   axis.ticks.y=element_blank())
-
-
-summaries <- readRDS(file = "datasets/Summaries.rds")
-summaries$ABS <- standardize(summaries$AB)
-summaries$CBS <- standardize(summaries$CB)
-summaries$AAS <- standardize(summaries$AA)
-summaries$CAS <- standardize(summaries$CA)
-summaries$CDS <- standardize(summaries$CD)
-summaries$ADS <- standardize(summaries$AD)
-summaries$group <- as.factor(summaries$group)
-summaries$groupID <-  as.integer( as.factor(summaries$group) )
-#summaries$ApropS <- standardize(summaries$AA/summaries$AB)
-
-
-ggplot()+geom_histogram(aes(x=summaries$AdiffS))
-
-noChange <-(0 - mean(summaries$Adiff))/sd(summaries$Adiff)
-averageChange <- mean(summaries$Adiff[summaries$group == "control"])
-
-# FinalHMC <- ulam(
-#   alist(
-#     AdiffS ~ dnorm( mu, sigma ),
-#     mu <- a + bADS[groupID] * ADS + 
-#     bIT[groupID] + bIC[groupID] * IC + 
-#       bADSIC * ADS * IC+ bCBS[groupID] *CBS,
-#     a ~ dnorm (0,0.3),
-#     bADS[groupID] ~ dnorm(0,.3),
-#     bADSIC ~ dnorm(0,.3),
-#     bCBS[groupID] ~ dnorm(0,.3),
-#     bIT[groupID] ~ dnorm(0,.3),
-#     bIC[groupID] ~ dnorm(0,.3),
-#     sigma  ~ dexp(1)
-#   ),
-#   data = summaries
-# )
-
-# saveRDS(FinalHMC, file = "models/FinalHMC.rds")
-
-FinalHMC <- readRDS(file = "models/FinalHMC.rds")
-
-
-# InteractionsModelDiff <- ulam(
-#   alist(
-#     AdiffS ~ dnorm( mu, sigma ),
[…]

### 2023-12-18 timeSeries/arimaStrategy.R

@@ -1,289 +1,0 @@
-library(rethinking)
-library(tidyverse)
-library(ggthemes)
-library(stats)
-library(forecast)
-
-getwd()
-
-
-data <- read.csv("quittingFinalAnon.csv")
-attacked <- data[data$sumHighBefore >=1,]
-
-
-userArimaDFs <- list()
-
-for(i in 1:nrow(attacked)){
-user <- attacked[i,]
-activity <- as.integer(t(user[,c(paste("au",1:15, sep = ""))]))
-attacks <- as.integer(t(user[,c(paste("h",1:15, sep = ""))]))
-
-postAttacks <- as.integer(t(user[,c(paste("ph",1:15, sep = ""))]))
-commentAttacks <-  as.integer(t(user[,c(paste("h",1:15, sep = ""))])) - as.integer(t(user[,c(paste("ph",1:15, sep = ""))]))
-
-userDF <- data.frame(activity,postAttacks,commentAttacks, attacks)
-userDF <-userDF %>% mutate(attacksCumulative = cumsum(attacks))
-userDF <-userDF %>% mutate(attacksLag = lag(attacks,1))
-cumlag <- cumsum(ifelse(is.na(userDF$attacksLag), 0, userDF$attacksLag))
-userDF <-userDF %>% mutate(attacksLagCumulative = cumlag)
-userArimaDFs[[i]] <- userDF
-}
-
-#build bare arimas
-bareArimas <- list()
-for (i in 1:length(userArimaDFs)){
-bareArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],stationary=TRUE)
-}
-
-#collectbare akaike scores
-bareAIC <- numeric(length(userArimaDFs))
-for (i in 1:length(userArimaDFs)){
-bareAIC[i] <- bareArimas[[i]][["aicc"]]
-}
-
-#build arimas with today attacks
-
-todayArimas <- list()
-#for (i in 15:length(userArimaDFs)){
-#  todayArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],
-#                                 xreg=userArimaDFs[[i]]$attacks[2:14],stationary=TRUE)
-#}
-
-for (i in 1:length(userArimaDFs)){
-skip_to_next <- FALSE
-
-tryCatch(   todayArimas[[i]] <- auto.arima(userArimaDFs[[i]]$activity[2:14],
[…]

### 2023-12-18 timeSeries/timeSeriesAnalysis.R

@@ -1,31 +1,0 @@
-library(rethinking)
-library(tidyverse)
-library(ggthemes)
-library(stats)
-library(forecast)
-
-getwd()
-summaries <- read.csv(file = "datasets/Summaries.csv")
-
-head(summaries)
-
-
-
-hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
-comments <- readRDS(file = "datasets/RAWNESTA/Comments.rds")
-interventions <- readRDS(file = "datasets/interventions.rds")
-
-interventionsByAuthorDate <- as.data.frame(xtabs(~ author + day, data = interventions))
-
-str(interventionsByAuthorDate)
-hate$author  <- as.character(hate$author)
-comments$author  <- as.character(comments$author)
-interventionsByAuthorDate$author  <- as.character(interventionsByAuthorDate$author)
-
-
-
-mean(hate$author %in% comments$author)
-mean(comments$author %in% hate$author)
-mean(interventionsByAuthorDate$author %in% hate$author)
-
-

### 2023-12-18 utils/plotPriors.R

@@ -1,24 +1,0 @@
-library(reshape2)
-library(ggplot2)
-library(ggthemes)
-library(ggpubr)
-library(rethinking)
-library(dplyr)
-library(tidyverse)
-library(WRS2)
-library(purrr)
-
-
-visualisePriors <- function(model, dataAsList, N = 100)
-{
-  prior <- extract.prior( model, n = N )
-  mu <- link( model , post=prior, data=dataAsList)  
-  mut <- as.data.frame(t(mu))
-  mutLong <- melt(mut)
-  mutLong$x <- rep(c(-3,3),N)
-  ggplot(mutLong)+geom_line(aes(x = x, y = value, group = variable), alpha = 0.2)+theme_tufte()+xlab(names(data)[1])
-}
-
-#visualisePriors(100,ABSModel, list(ABS = c(-3,3)))
-
-

### 2023-12-18 visualisations/visualisePeriods.R

@@ -1,167 +1,0 @@
-library(ggplot2)
-library(ggthemes)
-
-
-getwd()
-Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
-Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
-
-
-dates <- colnames(Hate)[-1]
-dates <- as.Date(dates)
-
-
-
-startDate <- dates[1]
-interventionDate <- "2020-07-08"
-observationDate <- "2020-09-09"
-end <- dates[length(dates)]
-
-periods<- numeric(length(dates))
-periods <- ifelse(dates < interventionDate,"pre-treatment",periods)
-periods <- ifelse(dates >= interventionDate & dates < observationDate,"treatment",periods)
-periods <- ifelse(dates >= observationDate,"post-treatment",periods)
-periods
-
-
-
-length(periods)
-length(dates)
-
-
-
-hateTS <- as.data.frame(colSums(Hate[,-1]))
-hateTS$date <- as.Date(rownames(hateTS))
-rownames(hateTS) <- NULL
-colnames(hateTS) <- c("attacks","date")
-head(hateTS)
-hateTS$periods <- periods
-
-
-interventions <- readRDS(file = "datasets/interventions.rds")
-
-interventionsTS <- as.data.frame(table(interventions$day))
-
-interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
-
-colnames(interventionsTS) <- c("date", "interventions")
-
-interventionsTS
-
-periodsDF <- merge(x = hateTS, y = interventionsTS, by = "date", all.x = TRUE)
-
-idx <- c(1, diff(periodsDF$date))
-i2 <- c(1,which(idx != 1), nrow(periodsDF)+1)
-periodsDF$grp <- rep(1:length(diff(i2)), diff(i2))
-
-periodsDF$interventions[is.na(periodsDF$interventions) & periodsDF$periods == "treatment"] <- 0
-
-periodsDF
-
-
-ggplot(periodsDF)+
-  geom_line(aes(x=date, y = attacks, group = grp),
-             alpha = 0.8, size = .6)+
-  geom_line(aes(x=date, y = interventions, group = grp),
-            alpha = 0.8, size = .6)+
-  geom_vline(xintercept = startDate, lty =2, size =.2, alpha=0.5)+
[…]

### 2023-12-18 volunteers/reportVolunteers.Rmd
added volunteers

--- 2023-01-16 nestaVolunteers/nestaVolunteers/reportVolunteers.Rmd
@@
 library(ggrepel)
+library(rstan)
 
@@
 ```{r volunteersVis,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
-volunteersLong <- read_csv(file = "nestaVolunteers/volunteersLong.csv")
-competitionModel<- readRDS( "nestaVolunteers/competitionModel.rds")
-volunteersJoint <- readRDS( file = "nestaVolunteers/datasets/volunteersJoint.rds")
+volunteersLong <- read_csv(file = "data/volunteersLong.csv")
+competitionModel<- readRDS( "models/competitionModel.rds")
+volunteersJoint <- readRDS( file = "data/volunteersJoint.rds")
 

### 2023-12-18 technical_report/nesta_study_technical_report.Rmd

@@
 ```{r periodsVisualisationPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
-Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
-Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
-summaries <- read.csv(file = "datasets/Summaries.csv")
+Hate <- readRDS(file = "data/raw/Hate.rds")
+Comments <-   readRDS(file = "data/raw/Comments.rds")
+summaries <- read.csv(file = "data/Summaries.csv")
 
@@
 
-interventions <- readRDS(file = "datasets/interventions.rds")
+interventions <- readRDS(file = "data/interventions.rds")
 interventionsTS <- as.data.frame(table(interventions$day))
@@
 ```{r tsVisPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
-hateDFs <- readRDS("datasets/hateDFsNoDropouts.RDS")
+hateDFs <- readRDS("data/hateDFsNoDropouts.RDS")
 
@@
 ```{r nullTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
-dat <- readRDS(file = "datasets/dat.RDS")
+dat <- readRDS(file = "data/dat.RDS")
 
@@
 #prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
-#saveRDS(prior, file = "datasets/prior1.RDS")
-prior <- readRDS(file = "datasets/prior1.RDS")
+#saveRDS(prior, file = "data/prior1.RDS")
+prior <- readRDS(file = "data/prior1.RDS")
 mu <- link( InteractionsModelDiffSD1 , post=prior , data=data )
@@
 #prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
-#saveRDS(prior, file = "datasets/prior2.RDS")
-prior <- readRDS(file = "datasets/prior2.RDS")
+#saveRDS(prior, file = "data/prior2.RDS")
+prior <- readRDS(file = "data/prior2.RDS")
 mu <- link(InteractionsModelDiffSD1 , post=prior , data=data )
@@
 #prior <- extract.prior(InteractionsModelDiff, n = 1e4)
-#saveRDS(prior, file = "datasets/prior3.RDS")
-prior <- readRDS(file = "datasets/prior3.RDS")
+#saveRDS(prior, file = "data/prior3.RDS")
+prior <- readRDS(file = "data/prior3.RDS")
 
@@
 #prior <- extract.prior(InteractionsModelDiff, n = 1e4)
-#saveRDS(prior, file = "datasets/prior4.RDS")
-prior <- readRDS(file = "datasets/prior4.RDS")
+#saveRDS(prior, file = "data/prior4.RDS")
+prior <- readRDS(file = "data/prior4.RDS")
 mu <- link(InteractionsModelDiff , post=prior , data=data )
@@
 
-\begin{figure}
-```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%", results = "hide"}
-InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
-traceplot( InteractionsModelDiff )
-```
-\caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.}
-\label{fig:traceplot}
-\end{figure}
+<!-- ```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%", results = "hide"} -->
+<!-- InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds") -->
+<!-- traceplot( InteractionsModelDiff ) -->
+<!-- ``` -->
+<!-- \caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.} -->
+<!-- \label{fig:traceplot} -->
+<!-- \end{figure} -->
 
@@
 
-hateDFs <- readRDS(file ="datasets/hateDFs2.RDS")
+hateDFs <- readRDS(file ="data/hateDFs2.RDS")
 sampleDFs <- hateDFs
 
-d1precis <- readRDS("timeSeriesDFs/d1precis.rds")
-d2precis <- readRDS("timeSeriesDFs/d2precis.rds")
-d3precis <- readRDS("timeSeriesDFs/d3precis.rds")
-d4precis <- readRDS("timeSeriesDFs/d4precis.rds")
-d5precis <- readRDS("timeSeriesDFs/d5precis.rds")
-d6precis <- readRDS("timeSeriesDFs/d6precis.rds")
-d7precis <- readRDS("timeSeriesDFs/d7precis.rds")
+d1precis <- readRDS("data/timeSeriesDFs/d1precis.rds")
+d2precis <- readRDS("data/timeSeriesDFs/d2precis.rds")
+d3precis <- readRDS("data/timeSeriesDFs/d3precis.rds")
+d4precis <- readRDS("data/timeSeriesDFs/d4precis.rds")
+d5precis <- readRDS("data/timeSeriesDFs/d5precis.rds")
+d6precis <- readRDS("data/timeSeriesDFs/d6precis.rds")
+d7precis <- readRDS("data/timeSeriesDFs/d7precis.rds")
 
@@
 
-datA <- readRDS(file = "timeSeries/tsaStanCumulative/datA.RDS")
-fitA <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitA.rds")
-datB <- readRDS(file = "timeSeries/tsaStanCumulative/datB.RDS")
-fitB <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitB.rds")
-datC <- readRDS(file = "timeSeries/tsaStanCumulative/datC.RDS")
-fitC <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitC.rds")
-datD <- readRDS(file = "timeSeries/tsaStanCumulative/datD.RDS")
-fitD <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitD.rds")
+datA <- readRDS(file = "data/timeSeries/datA.RDS")
+fitA <- readRDS("data/timeSeries/c3interactionStanFitA.rds")
+datB <- readRDS(file = "data/timeSeries/datB.RDS")
+fitB <- readRDS("data/timeSeries/c3interactionStanFitB.rds")
+datC <- readRDS(file = "data/timeSeries/datC.RDS")
+fitC <- readRDS("data/timeSeries/c3interactionStanFitC.rds")
+datD <- readRDS(file = "data/timeSeries/datD.RDS")
+fitD <- readRDS("data/timeSeries/c3interactionStanFitD.rds")
 
